### 2023-03-21 paper/manuscript.Rmd
set up repo

---
title             : "Variation in gaze understanding across the life span: A process-level perspective"
shorttitle        : "modeling variation in gaze understanding"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"

  - name          : "Manuel Bohn"
    affiliation   : "1"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Abstract

keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
wordcount         : "xxx"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include = FALSE}
library("papaja")
library("ggplot2")
library("ggpubr")
library("tidyverse")
library("brms")
theme_set(theme_classic())
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r load_data}
# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
#   # determine order of factors
#   mutate(
#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
#     sample = factor(sample, levels = c("kids", "adults")), 
#     studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
#   )
```

# Introduction
- why do we care about developmental trajectory? ref to stat learning paper
- variation

# Lifespan 
- development & individual differences in gaze understanding
- verweis methods paper reliable differences kinder & adults. 
- kontinuerliche, systematische variation, wodrin? => model

# Computational cognitive model
- model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
- entwicklungsperspektive basierend auf model
- dann prozess-ebene => magnet

# Non-social vector following

## Analysis
All test trials without voice-over descriptions were included in our analyses.
We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].

```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
# knitr::include_graphics("../figures/screenshot.png")
```

\newpage

# Declarations

## Open practices statement

The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
All experiments were pre-registered (<https://osf.io/zjhsc/>).

## Funding

This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
We thank all the children, caregivers, and adults who participated in the study.
We thank Jana Jurkat for her help with data collection.

## Conflicts of interest

The authors declare that they have no conflict of interest.

## Consent to participate

Informed consent was obtained from all individual participants included in the study or their legal guardians.

## Authors' contributions

The authors made the following contributions:
### TODO

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```

### 2023-03-21 paper/manuscript.tex
set up repo

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: 6856}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
  pdflang={en-EN},
  pdfkeywords={social cognition, individual differences, gaze cues, cognitive development},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
\date{}

\shorttitle{assessing individual differences in gaze understanding}

\authornote{

Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany. E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

\abstract{%
Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5--10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants' click imprecision and is easily adaptable to different study requirements.
Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test--retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
Yet, there are always individual differences.
Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and designing interventions (Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).

Numerous studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities (e.g., Wellman \& Liu, 2004), and which factors drive the development of social cognition (Devine \& Hughes, 2018; e.g., Gola, 2012).
For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes (for an overview, see Repacholi, 2003).
Studies on social-cognitive abilities and family influences include the effect of parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce et al., 2014), and family background as parental education, occupation, sibling interaction and childcare (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991).
Another group of individual differences studies focuses on the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Carlson \& Moses, 2001; Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007; Milligan, Astington, \& Dack, 2007; Okumura et al., 2017).
Studies on social behavioral outcomes measured the interplay of social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), stereotypes, and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).

However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Poulin-Dubois, Goldman, Meltzer, \& Psaradellis, 2023; Sodian, 2023; Sodian et al., 2016).
This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).

To give an example: the most commonly applied prototypical measure for social cognition is the change-of-location false belief task (Baron-Cohen, Leslie, \& Frith, 1985; Wimmer \& Perner, 1983).
Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
A doll called Sally puts her marble into a basket.
After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
Participants then get asked where Sally will look for her marble once she returns.
The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).

However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (Repacholi, 2003).
Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
This has profound implications for what studies on individual differences using this task (or others) can show.
Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
For example, Sodian et al. (2016) neither found a correlation between two moral Theory of mind False Belief and Intention tasks at 60 months, nor a relationship between these two factors and implicit False Belief understanding at 18 months.

The ``Sandbox task'' is one of the few tasks that attempt to overcome these methodological challenges (Begeer, Bernstein, van Wijhe, Scheeren, \& Koot, 2012; Bernstein, Thornton, \& Sommerville, 2011; Coburn, Bernstein, \& Begeer, 2015; Mahy, Bernstein, Gerrard, \& Atance, 2017; Sommerville, Bernstein, \& Meltzoff, 2013).
This continuous FB task measures the degree to which the estimate of another's belief is biased by one's own knowledge.
Recent work questions the interpretation of this measure (Samuel, Legg, Lurz, \& Clayton, 2018a; Samuel, Legg, Lurz, \& Clayton, 2018b): it is unclear whether a smaller egocentric bias can be directly translated into a better mental state reasoning ability.
Another evaluation criterion should, therefore, be whether a task captures meaningful variability in performance; that is, differences in test scores should correspond to differences in the social-cognitive ability in question.

Thus, developmental psychology faces a dilemma: many research questions rely on measuring individuals' development, yet, there is a lack of tasks to measure these individual differences reliably.
To capture the emergence of social-cognitive abilities and their relation to social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).

Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish list'' for new social-cognitive paradigms.
They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
New tasks should capture variation across age groups, including older children and adults (Repacholi, 2003).
Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).

\hypertarget{a-new-measure-of-gaze-understanding}{%
\section{A new measure of gaze understanding}\label{a-new-measure-of-gaze-understanding}}

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
In our definition, gaze understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
As such, the eyes have been regarded as a ``window into the mind'' (Shepherd, 2010).
Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions (Bohn \& Köymen, 2018; Tomasello et al., 2007).
In addition, gaze and language development seem to be related (Brooks \& Meltzoff, 2005).
Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication (Hernik \& Broesch, 2019; Macdonald \& Tatler, 2013).
While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
However, many cognitive abilities continue to develop beyond early childhood (e.g., Gathercole, Pickering, Ambridge, \& Wearing, 2004 for working memory; Raviv \& Arnon, 2018 for visual statistical learning).
Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
Consequently, we aimed to assess the differentiation of the ability to understand gaze.
Our goal was not to establish the youngest age at which children understand gaze cues.
Rather, we wanted to examine how that ability changes with age.
To accurately measure developmental change, we were interested in capturing individual variability.

To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine-grained individual differences at different ages.
Second, we designed short trials that facilitate more than a dozen replicates per subject.
The result is more precise individual-level estimates.
Third, we systematically investigated the psychometric properties of the new task.

Designing this task required a new testing infrastructure.
We designed the task as an interactive web application.
Previous research has successfully used online study implementations that compare well to in-person data collection (Bohn, Le, Peloquin, Köymen, \& Frank, 2021; Bohn, Tessler, Merrick, \& Frank, 2021; Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016).
This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
Furthermore, because the task is largely self-contained, it is much more controlled and standardized.
Most importantly, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
As such, it provides a solid basis to study individual differences in gaze understanding across ages at scale.
We make the task and its source code openly accessible for other researchers to use and modify.

\hypertarget{task-design}{%
\section{Task design}\label{task-design}}

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

The code is open-source (\url{https://github.com/ccp-eva/tango-demo}), and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/tango-demo/}.

The web app was developed using \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS,} and \texttt{PHP}.
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
This way, the composition scales according to the user's viewport without loss of quality while keeping the aspect ratio and relative object positions constant.
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
This is needed for precisely calculating the exact pupil and target locations and sizes.
Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The web app generates two file types: (1) a text file (.json) containing metadata, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
These files can either be sent to a server or downloaded to the local device.
Personalized links can be created by passing on URL parameters.

\hypertarget{stimuli}{%
\subsection{Stimuli}\label{stimuli}}

Our newly implemented task asks children and adults to search for a balloon.
The events proceed as follows (see Figure \ref{fig:fig1}B and C).
An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
A balloon (i.e., target; blue, green, yellow, or red) is located in front of them.
The target then falls to the ground.
At all times, the agent's gaze tracks the movement of the target: the pupils and iris move so that their center aligns with the center of the target.
While the distance of the target's flight depends on the final location, the target moves at a constant speed.
Participants are then asked to locate the target: they respond by touching or clicking on the screen.
Visual access to the target's true location is manipulated by a hedge.
Participants either have full, partial, or no visual access to the true target location.
When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asked ``Where is the balloon?''.
To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

\hypertarget{trials}{%
\subsection{Trials}\label{trials}}

Trials differ in the amount of visual access that participants have to the final target position.
Before the test trials start, participants complete four training trials during which they familiarize themselves with touching the screen.
In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
In the second and third training trials, participants have partial access: they witness the target flight but cannot see the target's end location.
They are then asked to click on the hidden balloon, i.e., the location where they saw the target land.
In test trials, participants have no visual access to the target flight or the end location.
Participants are expected to use the agent's gaze as a cue to locate the target.
The first trial of each type comprises a voice-over description of the presented events.
The audio descriptions explicitly state that the agent is always looking at the target (see Supplements for audio script).
After the four training trials, participants receive 15 test trials.
The complete sequence of four training trials and 15 test trials can be easily completed within 5-10 minutes.

\hypertarget{study-versions}{%
\subsection{Study versions}\label{study-versions}}

We designed two study versions that differ in the target's final hiding place and, consequently, in the outcome measure: a \emph{hedge version} (continuous) and a \emph{box version} (discrete).
Both versions use the same first training trial and then differ in the consecutive training and test trials.
In the hedge version, participants have to indicate their estimated target location directly on a hedge.
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
In the box version, the target lands in a box, and participants are asked to click on the box that hides the target.
Researchers can choose how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
Note that in the test trials of both versions, the target flight is covered by a hedge.
In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
In the box version, the hedge shrinks completely.
The boxes then hide the target's final destination (see Figure \ref{fig:fig1}B and C).

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_procedure}

}

\caption{\textbf{Study setup}. (A) Infrastructure for online testing. (i) Subjects aged 3 to 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or in research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure in-house servers. (B) Hedge version (continuous) of the TANGO. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. Three exemplary target locations are shown to depict how indicative the agent's gaze cues are in determining the target's location. The transparent target is only shown for an illustrative purpose (not visible during the test). (C) Box version (discrete) of the TANGO. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
\end{figure}

\hypertarget{randomization}{%
\subsection{Randomization}\label{randomization}}

All agents and target colors appear equally often and are not repeated in more than two consecutive trials.
The randomization of the target end location depends on the study version.
In the hedge version, the full width of the screen is divided into ten bins.
Exact coordinates within each bin are then randomly generated.
In the box version, the target randomly lands in one of the boxes.
As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.

\hypertarget{individual-differences}{%
\section{Individual differences}\label{individual-differences}}

Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.

Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.

The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.

Participants were equally distributed across the two study versions.
Data were collected between May and October 2021.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig, Germany.
The in-person child sample consisted of 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.60 months, SD = 3.10, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).

We pre-registered the replacement for participants that finished fewer than four test trials.
This was not the case for any participant.
One child stopped participation after 12 test trials but was included in the sample due to the pre-registered replacement rule.
Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).

For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
Families received an email with a short study description and a personalized link.
If they had not participated in the study within two weeks, they received a reminder via email.
The response rate to invitations after the reminder was \textasciitilde50\%.

The remote child sample included 147 children, including 45 3-year-olds (mean = 42.62 months, SD = 3.35, range = 36 - 47, 14 girls), 47 4-year-olds (mean = 52.64 months, SD = 3.40, range = 48 - 59, 25 girls), and 55 5-year-olds (mean = 65.11 months, SD = 3.77, range = 60 - 71, 27 girls).
Of these, three families participated twice.
In these cases, we only kept the data sets from the first participation.

Four additional participants were recruited but not included in the study because they were already part of the in-person kindergarten sample (n=3), or because of unknown age (n = 1).

Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
They often live in nuclear two-generational families with few household members.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
The median individual monthly net income in the year 2021 was \textasciitilde{} 1,600€ for the city of Leipzig.

Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
\emph{Prolific} is an online participant recruitment service with a predominantly European and US-American subject pool.
100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females) were included.
Participants live in a variety of different countries: the UK, Italy, Spain, Poland, Netherlands, Canada, Australia, Ireland, South Africa, Norway, Portugal, France, Austria, Finland, Greece, Germany, the U.S., Mexico, Chile, Iceland, New Zealand, Czech Republic, Hungary, Latvia, and Switzerland.
In this sample, most participants resided in the United Kingdom (n = 47), South Africa (n = 8), and Portugal (n = 6).
Additional, detailed information can be found in the data set online.
For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten.
An experimenter guided the child through the study.

Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
At the beginning of the online study, families were invited to enter our ``virtual institute''.
We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
Then, caregivers were informed about data security and were asked for their informed consent.
They were asked to enable the sound and seat their child centrally in front of their device.
Before the study started, families were instructed on how to set up their webcam and enable the recording permissions.
We stressed that caregivers should not help their children.
Study participation was video recorded whenever possible in order to ensure that the children themselves generated the answers.
Depending on the participant's device, the website automatically presented the hedge or box version of the study.
For families that used a tablet with a touchscreen, the hedge version was shown.
Here, children could directly click on the touchscreen to indicate where the target is.
For families that used a computer without a touchscreen, the website presented the box version of the task.
We assumed that younger children in our sample would not be acquainted with using a computer mouse.
Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.

All participants received 15 test trials.
In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes, while adults were presented with eight boxes as possible target locations.

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

All test trials without voice-over descriptions were included in our analyses.
We ran all analyses in R version 4.2.2 (2022-10-31) (R Core Team, 2022).
Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).

To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}).\footnote{In the pre-registration (\url{https://osf.io/snju6}), we specified the following model structure: ``All models will include a fixed effect of target centrality and age, a random intercept for ID and a random slope for trial number by ID. For both study versions, we will compare the above specified null models with a model including data source (live vs.~online) as a fixed effect.'' Or, in R model formula: \texttt{R:\ performance\ \textasciitilde{}\ target\_centrality\ +\ age\ +\ (1\ \textbar{}\ ID)\ +\ (1\ +\ trial\ \textbar{}\ ID)}.
  In this paper, we added symmetricPosition (synonymous to target\_centrality) as a random slope because we expected that this item effect could vary between participants.
  To be better able to interpret trial number effects, we decided to include it as a fixed effect.
  Data collection mode (formerly named ``data source'') proved as a meaningful predictor and was accordingly added to the model.}

Here, \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.

For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.

\hypertarget{results}{%
\subsection{Results}\label{results}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_arrangedplot}

}

\caption{\textbf{Measuring inter-individual variation}. (A) Developmental trajectory in the continuous hedge version. Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. (B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample. (F) Developmental trajectory in the discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. The dotted black line shows the level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes). (G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample. For (A) and (F), regression lines show the predicted developmental trajectories (with 95\% CrI) based on GLMMs, with the line type indicating the data collection mode. For (B-E) and (G-J), regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}. Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). Small points show the mean performance for each subject averaged across trials. The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection. The color of data points denotes age group.}\label{fig:fig2}
\end{figure}

Children showed nearly perfect precision in the first training trial.
As visual access to the target location decreased in the subsequent training trials, imprecision levels increased (see Supplements).
Within test trials, children's imprecision levels did not vary as a function of trial number.
We take this as evidence that (A) children were comfortable touching the screen, (B) children understood the task instructions insofar as they aimed at locating the target, and (C) our experimental design successfully manipulated task difficulty.

We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
In the hedge version, children's click imprecision decreased with age, while in the box version, the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
Most participants in the box version performed above chance level.
By the end of their sixth year of life, children came close to the adult's proficiency level.
Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
For example, some three-year-olds were more precise in their responses than some five-year-olds.
Even though variation is smaller, we could even find inter-individual differences in the adult sample.

As Figure \ref{fig:fig2}A and F show, our remotely collected child data resembled the data from the kindergarten sample.
We found evidence that responses of children participating remotely were slightly more precise.
This difference was mainly driven by the younger participants and was especially prominent in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.\footnote{In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
  We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
  We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
  Based on our model comparison, we conclude that there is no clear evidence of a stable effect of parental interference.
  See Supplements for further detail.}

Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CrI {[}-0.42; -0.24{]}) and data collection mode -0.31 (95\% CrI {[}-0.49; -0.13{]}) were negative and reliably different from zero.
In the box version, the estimate of age (\(\beta\) =0.69 (95\% CrI {[}0.45; 0.98{]}) and the estimate of data collection mode (\(\beta\) = 1.10 (95\% CrI {[}0.66; 1.56{]}) were positive and reliably different from zero.
Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.

There was no effect of trial number (hedge version: \(\beta\) = 0.00; 95\% CrI {[}-0.02; 0.01{]}; box version: \(\beta\) = -0.02; 95\% CrI {[}-0.05; 0.01).
However, trials differed in difficulty depending on where the target landed (hedge version: \(\beta\) = 0.32; 95\% CrI {[}0.27; 0.37{]}; box version: \(\beta\) = -1.58; 95\% CrI {[}-1.87; -1.31).
When the target landed closer to the center of the screen, participants were more accurate in locating it.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

Our task measured inter-individual differences in both children and adults; that is, we found substantial variation in individuals across age groups.
For example, some three-year-olds showed greater precision levels than some five-year-olds.
This holds across both study versions.
However, due to the continuous study design, the hedge version was able to capture more fine-grained differences in individual performance.
We see substantial developmental gains: with increasing age, participants became on average more and more precise in locating the target.
The five-year-olds reached a proficiency level close to the adults' level.
For neither study version nor age group did we find any floor or ceiling effects.
The presentation as a web app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
This illustrates the flexibility of the task design.

\hypertarget{internal-consistency-and-test-retest-reliability}{%
\section{Internal consistency and test-retest reliability}\label{internal-consistency-and-test-retest-reliability}}

As a next step, we aimed to investigate whether the variation that we captured with the TANGO is reliable.
We assessed internal consistency (as split-half reliability) and test-retest reliability.
Task procedure, data collection, and sample sizes were pre-registered (\url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
Participants were equally distributed across the two study versions.
Data was collected between July 2021 and June 2022.

The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl. No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
The research adheres to the legal requirements of psychological research with children in Germany.

\hypertarget{participants-1}{%
\subsection{Participants}\label{participants-1}}

Participants were recruited in the same way as in the previous study.
The child sample consisted of 120 children, including 41 3-year-olds (mean = 42.34 months, SD = 3.10, range = 37 - 47, 20 girls), 41 4-year-olds (mean = 53.76 months, SD = 3.15, range = 48 - 59, 21 girls), and 38 5-year-olds (mean = 66.05 months, SD = 3.40, range = 60 - 71, 19 girls).

Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned \emph{Individual Differences} sample (n = 3), or children did not understand the task instructions (n = 1; manifested in too early clicking in the training trials while the instructions were still playing, and no clicking by themselves in the test trials).
Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.

The adult sample included 136 English speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females; see Supplements for further details).
Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).

\hypertarget{procedure-1}{%
\subsection{Procedure}\label{procedure-1}}

We applied the same procedure as in the first study, with the following differences.
Participants completed the study twice, with a delay of 14 ± 3 days.
The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
The child sample received 15 test trials.
In the hedge version, each bin occurred once, making up ten of the test trials.
For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bins 1 \& 2, bins 3 \& 4, etc.).
In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
Adults in the hedge version received 30 test trials, each of the ten bins occurring exactly three times.
Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
For the four training trials, we repeated a fixed order of random bins/boxes.
For the adult sample, we decided to increase the number of trials in order to get more accurate reliability estimates.
Trial numbers were multipliers of the possible target locations and therefore differed between hedge and box versions.
For the child sample, we stuck to the same number of trials to not risk higher attrition rates.

\hypertarget{analysis-1}{%
\subsection{Analysis}\label{analysis-1}}

We assessed reliability in two ways.
First, we focused on internal consistency by calculating split-half reliability coefficients.\footnote{The assessment of internal consistency was not pre-registered and was included as an additional measure of reliability.}
For each subject, trials were split into odd and even trials.
Performance was aggregated and then correlated using \emph{Pearson} coefficients.
For this, we used the data of the first test day.
Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.

Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
To compare our traditional approach of a simple odd-even split, we additionally calculated split-half reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).

Second, we assessed test-retest reliability.
We calculated performance scores (depending on the study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach (Rouder \& Haaf, 2019).
We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ (0\ +\ reliday\ \textbar{}\ subjID)}).
For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
The model computes a correlation between the participant-specific estimates for each test day.
This can be interpreted as the test-retest reliability.
By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates.
Most importantly, the model includes age as a fixed effect.
The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
This rules out the possibility that a high correlation between test days arises from domain-general cognitive development instead of study-specific inter-individual differences.
A high correlation between our participant-specific model estimates would indicate a high association between test days.

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

We found that the TANGO measured systematic variation: split-half and test-retest reliability was medium to high.
For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.

Figure \ref{fig:fig3} compares split-half reliability coefficients by splitting and stratification method (Pronk et al., 2021).
In the hedge version, the split-half reliability coefficients ranged from 0.65 to 0.93.
In the box version, split-half reliability coefficients ranged from 0.48 to 0.86.
Similar to the results of Pronk et al. (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
In most cases, stratifying by target position led to similar or even higher estimates compared to no stratification.
As expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_splithalf}

}

\caption{\textbf{Internal Consistency}. Reliability coefficients per splitting method, stratification level, study version, and age group. Error bars show the 95\% confidence intervals of the coefficient estimates, calculated with the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).}\label{fig:fig3}
\end{figure}

For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
  The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
  Including the two children yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.88.
  Including the two adults yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.73.}
See Supplements for reliability estimates by age group.

The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
In the hedge version, the correlation between test days was 0.89 (95\% CrI {[}0.66;1.00{]}).
In the box version, the correlation between test days was 0.91 (95\% CrI {[}0.69;1.00{]}).

For both study versions, reliability estimates based on the GLMM approach were higher than the \emph{Pearson} correlations.
The GLMM-based estimates are less noisy due to the fact that the model uses all available information (e.g., participant age) and does not rely on data aggregation across trials.

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}

Our results indicated that the measured variation was systematic.
As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.

\hypertarget{validity}{%
\section{Validity}\label{validity}}

After having probed our new testing infrastructure and the psychometric properties of the TANGO task, we aimed at establishing its validity.
One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
Social cognition is often described as developing in response to social interaction(Devine \& Hughes, 2018; Hughes \& Leekam, 2004).
It is assumed that opportunities to play, communicate and argue with peers help children to understand the human mind.
Therefore, many studies link social cognition to opportunities for social interaction captured in demographic variables such as parent-child interaction quality and quantity, mental state talk, and center-based childcare (Bulgarelli \& Molina, 2016; Dunn et al., 1991; Pavarini et al., 2013).
In particular, family constellation, the number and age of siblings, and their interaction have been linked to social cognition (Cassidy, Fineberg, Brown, \& Perkins, 2005; Dunn et al., 1991; Perner, Ruffman, \& Leekam, 1994; Peterson, 2000; Zhang, Yu, Long, \& Li, 2021).

To assess such external validity for out TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
109 families filled out the questionnaire and were included in the analysis.
We used parent's responses to construct different scores suggested in the literature (Cassidy et al., 2005; Peterson, 2000), capturing different aspects of children's opportunity for social interaction with adults and peers.
Figure \ref{fig:fig4}A shows that all predictor scores are positively linked to gaze understanding. Only the \texttt{predictor\ age\ of\ childcare\ entry} improved the model fit compared to the null model (for model comparisons, see Supplements). Albeit the effects are weak, they are consistent with the literature.

In addition, children's sensitivity to gaze has been linked to language acquisition (Brooks \& Meltzoff, 2005; Del Bianco et al., 2019; Okumura et al., 2017).
Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word (Tomasello, 2003).
For 117 children, we also collected data on a receptive vocabulary test (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022) approximately six months (mean = 0.52 years, sd = 0.08, range = 0.06 - 0.80)after their participation in the TANGO task.
We found a substantial relation between gaze understanding six month prior and receptive vocabulary, even when correcting for age (see Figure \ref{fig:fig4}B and C).
Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic for measures of social cognition.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_vali_arrangedplot}

}

\caption{\textbf{Validity of the TANGO task.} (A) Influence of age of childcare entry on gaze understanding. The older the children were when entering childcare, the less likely they are to respond correctly. (B) Influence of social-environmental factors on gaze understanding. Adding the predictors to the null model did not improve model fit. (B) Influence of gaze understanding on receptive vocabulary. (C) Influence of gaze understanding on receptive vocabulary by age. The regression line with 95\% CI shows a smooth conditional mean based on a linear model, with a \emph{Pearson}'s correlation coefficient \emph{r}. Dots show the mean performance for each subject averaged across trials. The color of dots denotes age group. For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model. Black dots represent means, thicker black lines 80\% CI and thinner black lines 95\% CI.}\label{fig:fig4}
\end{figure}

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
The web app (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) and its source code (\url{https://github.com/ccp-eva/tango-demo}) are freely accessible for use and modification.

Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change, revealing relations between different aspects of cognition and children's real-life social surroundings, and for meaningful comparisons across human cultures and across animal species.
Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building (Hedge et al., 2018).

Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
Both study versions exhibit high retest reliability, also when controlling for age.
Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf. Hughes et al. (2000); improved reliability through aggregation).
When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).

In the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher the reliability estimates are.
Therefore, we argue that future research should aim at implementing statistical analyses that mirror the complexity of the experimental design.
Theoretically informed, computational cognitive models are a promising approach forward (Haines et al., 2020).
Computational models take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).

The TANGO fulfills several demands that were proposed by Schaafsma et al. (2015)'s wish list: it measures proficiency on a continuum, avoids floor and ceiling effects, measures variation across age ranges, shows satisfactory reliability estimates, and has a high face value.

In addition to the new task design itself, we designed a new testing infrastructure.
The TANGO is presented as an interactive web app.
This enables presentation across devices without any prior installation.
Stimuli presentation is achieved through the use of SVGs.
This has several advantages: the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
The cartoon-like presentation makes the task engaging for children and adults alike.
Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
Presented agents, voice-over instructions, and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.

The browser-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
Test instructions are standardized, and with prior informed consent, the webcam records study participation.
This allows us to scale up data collection: testing is flexible, fast, and requires no further experimenter training.
We compared children participating in-person and supervised in kindergartens with children who participated remotely at home.
Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
Children in the remote sample were slightly more precise.
This effect was most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
Therefore, we recommend using a tablet for remote data collection.
Children can click for themselves, and caregivers have less chance to interfere.
The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.

With respect to validity, we found that performance in the TANGO task was related to relevant external variables and cognitive measures.
Family-level variables, capturing a child's opportunity for social interaction, systematically influenced gaze understanding. Even though the effects were small and confidence intervals were wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real-life variables.
In addition, we assessed the influence of gaze understanding on receptive vocabulary.
We found a substantial relationship between the two variables, even when correcting for age.
Taken together, this speaks to the validity of our TANGO task.

\hypertarget{limitations}{%
\section{Limitations}\label{limitations}}

First, we want to address the scope and interpretation of the TANGO task.
We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
This speaks to the face validity of the TANGO task and its focus on an inherently social stimulus.
However, we do not want to claim that the TANGO task does not also recruit other, domain general processes.
For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
From that perspective, gaze understanding could be seen as a particular case of vector-following that is learned and used in social interactions.
Future research could assess how much variation of the gaze understanding task is shared with a physical vector-following task.
In addition, computational cognitive models might prove helpful in defining children's behavior on a process-level and disentangling parameters that influence task performance (e.g., spatial acuity).

Second, the influence of testing modality requires further attention.
Remote data collection loosens the standardization of the experimental procedure, as we cannot prevent caregivers from interfering.
Steering the child's behavior becomes less possible when touchscreens are used, and the child can click on the screen directly.
This is why we recommend using tablets for remote data collection.
However, it should be noted that families' access to technological devices varies, both across socio-environmental as well as cultural settings.

Finally, we utilized subtle gaze cues in order to increase difficulty and capture individual differences.
However, in real-life settings, children could be more accustomed to a combination of head and eye orientation changes, and subtle gaze differences might be less common.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

We have presented a new experimental paradigm to study gaze understanding across the lifespan.
The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
The data sets and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
A demo version of the task is available at the following website (see Figure \ref{fig:fig5}): \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
The code base and respective assets can be accessed in the following repository: \url{https://github.com/ccp-eva/tango-demo}.
These resources allow interested researchers to use, extend and adapt the task.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_demo_screenshot}

}

\caption{\textbf{TANGO demo website.} We want to highlight that researchers are welcome to use and modify our task according to their needs. The number of training and test trials and the number of boxes can be adjusted within the JavaScript code, while agents and targets can be exchanged within the HTML code.}\label{fig:fig5}
\end{figure}

\newpage

\hypertarget{declarations}{%
\section{Declarations}\label{declarations}}

\hypertarget{open-practices-statement}{%
\subsection{Open practices statement}\label{open-practices-statement}}

The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository (\url{https://github.com/jprein/gazecues-methods}).
All experiments were pre-registered (\url{https://osf.io/zjhsc/}).

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
We thank all the children, caregivers, and adults who participated in the study.
We thank Jana Jurkat for her help with data collection.

\hypertarget{conflicts-of-interest}{%
\subsection{Conflicts of interest}\label{conflicts-of-interest}}

The authors declare that they have no conflict of interest.

\hypertarget{consent-to-participate}{%
\subsection{Consent to participate}\label{consent-to-participate}}

Informed consent was obtained from all individual participants included in the study or their legal guardians.

\hypertarget{authors-contributions}{%
\subsection{Authors' contributions}\label{authors-contributions}}

The authors made the following contributions.
Julia Prein: Conceptualization, Software, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Steven Kalinke: Software, Writing - Review \& Editing; Daniel Haun: Conceptualization, Writing - Review \& Editing.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., \ldots{} Gredebäck, G. (2020). Social and emotional contexts predict the development of gaze following in early infancy. \emph{Royal Society Open Science}, \emph{7}(9), 201178. \url{https://doi.org/10.1098/rsos.201178}

\leavevmode\vadjust pre{\hypertarget{ref-astor2021gaze}{}}%
Astor, K., Thiele, M., \& Gredebäck, G. (2021). Gaze following emergence relies on both perceptual cues and social awareness. \emph{Cognitive Development}, \emph{60}, 101121. \url{https://doi.org/10.1016/j.cogdev.2021.101121}

\leavevmode\vadjust pre{\hypertarget{ref-baron-cohen1985does}{}}%
Baron-Cohen, S., Leslie, A. M., \& Frith, U. (1985). Does the autistic child have a "theory of mind" ? \emph{Cognition}, \emph{21}, 37--46. \url{https://doi.org/10.1016/0010-0277(85)90022-8}

\leavevmode\vadjust pre{\hypertarget{ref-barrett2013early}{}}%
Barrett, H. C., Broesch, T., Scott, R. M., He, Z., Baillargeon, R., Wu, D., \ldots{} Laurence, S. (2013). Early false-belief understanding in traditional non-{Western} societies. \emph{Proceedings of the Royal Society B: Biological Sciences}. \url{https://doi.org/10.1098/rspb.2012.2654}

\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M. H. (2020). Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}. \emph{Frontiers in Psychology}, \emph{0}. \url{https://doi.org/10.3389/fpsyg.2019.02905}

\leavevmode\vadjust pre{\hypertarget{ref-begeer2012continuous}{}}%
Begeer, S., Bernstein, D. M., van Wijhe, J., Scheeren, A. M., \& Koot, H. M. (2012). A continuous false belief task reveals egocentric biases in children and adolescents with {Autism Spectrum Disorders}. \emph{Autism}, \emph{16}(4), 357--366. \url{https://doi.org/10.1177/1362361311434545}

\leavevmode\vadjust pre{\hypertarget{ref-benson2012individual}{}}%
Benson, J., Sabbagh, M., Carlson, S., \& Zelazo, P. (2012). Individual {Differences} in {Executive Functioning Predict Preschoolers}' {Improvement From Theory-of-Mind Training}. \emph{Developmental Psychology}, \emph{49}. \url{https://doi.org/10.1037/a0031056}

\leavevmode\vadjust pre{\hypertarget{ref-bernstein2011theory}{}}%
Bernstein, D. M., Thornton, W. L., \& Sommerville, J. A. (2011). Theory of {Mind Through} the {Ages}: {Older} and {Middle-Aged Adults Exhibit More Errors Than Do Younger Adults} on a {Continuous False Belief Task}. \emph{Experimental Aging Research}, \emph{37}(5), 481--502. \url{https://doi.org/10.1080/0361073X.2011.619466}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2021children}{}}%
Bohn, M., Le, K. N., Peloquin, B., Köymen, B., \& Frank, M. C. (2021). Children's interpretation of ambiguous pronouns based on prior discourse. \emph{Developmental Science}, \emph{24}(3), e13049. \url{https://doi.org/10.1111/desc.13049}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.

\leavevmode\vadjust pre{\hypertarget{ref-bohn2022individual}{}}%
Bohn, M., Tessler, M. H., Kordt, C., Hausmann, T., \& Frank, M. C. (2022). \emph{An individual differences perspective on the development of pragmatic abilities in the preschool years}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/s2e3p}

\leavevmode\vadjust pre{\hypertarget{ref-bohn2021how}{}}%
Bohn, M., Tessler, M. H., Merrick, M., \& Frank, M. C. (2021). How young children integrate information sources to infer the meaning of words. \emph{Nature Human Behaviour}, \emph{5}(8), 1046--1054. \url{https://doi.org/10.1038/s41562-021-01145-1}

\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
Brooks, R., \& Meltzoff, A. N. (2005). The development of gaze following and its relation to language. \emph{Developmental Science}, \emph{8}(6), 535--543. \url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}

\leavevmode\vadjust pre{\hypertarget{ref-bulgarelli2016social}{}}%
Bulgarelli, D., \& Molina, P. (2016). Social {Cognition} in {Preschoolers}: {Effects} of {Early Experience} and {Individual Differences}. \emph{Frontiers in Psychology}, \emph{7}. \url{https://doi.org/10.3389/fpsyg.2016.01762}

\leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1). \url{https://doi.org/10.18637/jss.v080.i01}

\leavevmode\vadjust pre{\hypertarget{ref-burkner2018advanced}{}}%
Bürkner, P.-C. (2018). Advanced {Bayesian Multilevel Modeling} with the {R Package} brms. \emph{The R Journal}, \emph{10}(1), 395. \url{https://doi.org/10.32614/RJ-2018-017}

\leavevmode\vadjust pre{\hypertarget{ref-buttelmann2021relations}{}}%
Buttelmann, D., Kühn, K., \& Zmyj, N. (2021). The {Relations} among {Theory} of {Mind}, {Inhibitory Control}, and {Aggressive Behavior} in 4-{Year-Old Children} \textendash{} {A Multi-Measure Multi-Informant Approach}. \emph{Journal of Cognition and Development}, \emph{0}(0), 1--24. \url{https://doi.org/10.1080/15248372.2021.1987240}

\leavevmode\vadjust pre{\hypertarget{ref-byers-heinlein2021development}{}}%
Byers-Heinlein, K., Tsui, R. K.-Y., van Renswoude, D., Black, A. K., Barr, R., Brown, A., \ldots{} Singh, L. (2021). The development of gaze following in monolingual and bilingual infants: {A} multi-laboratory study. \emph{Infancy}, \emph{26}(1), 4--38. \url{https://doi.org/10.1111/infa.12360}

\leavevmode\vadjust pre{\hypertarget{ref-callaghan2005synchrony}{}}%
Callaghan, T., Rochat, P., Lillard, A., Claux, M. L., Odden, H., Itakura, S., \ldots{} Singh, S. (2005). Synchrony in the onset of mental-state reasoning: {Evidence} from five cultures. \emph{Psychological Science}. \url{https://doi.org/10.1111/j.0956-7976.2005.01544.x}

\leavevmode\vadjust pre{\hypertarget{ref-carlson2001individual}{}}%
Carlson, S., \& Moses, L. J. (2001). Individual {Differences} in {Inhibitory Control} and {Children}'s {Theory} of {Mind}. \emph{Child Development}, \emph{72}(4), 1032--1053. Retrieved from \url{https://www.jstor.org/stable/1132428}

\leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
Carlson, S., Moses, L. J., \& Claxton, L. J. (2004). Individual differences in executive functioning and theory of mind: {An} investigation of inhibitory control and planning ability. \emph{Journal of Experimental Child Psychology}, \emph{87}(4), 299--319. \url{https://doi.org/10.1016/j.jecp.2004.01.002}

\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106. Retrieved from \url{https://www.jstor.org/stable/3696711}

\leavevmode\vadjust pre{\hypertarget{ref-coburn2015new}{}}%
Coburn, P. I., Bernstein, D. M., \& Begeer, S. (2015). A new paper and pencil task reveals adult false belief reasoning bias. \emph{Psychological Research}, \emph{79}(5), 739--749. \url{https://doi.org/10.1007/s00426-014-0606-0}

\leavevmode\vadjust pre{\hypertarget{ref-coelho2006searching}{}}%
Coelho, E., George, N., Conty, L., Hugueville, L., \& Tijus, C. (2006). Searching for asymmetries in the detection of gaze contact versus averted gaze under different head views: A behavioural study. \emph{Spatial Vision}, \emph{19}(6), 529--545. \url{https://doi.org/10.1163/156856806779194026}

\leavevmode\vadjust pre{\hypertarget{ref-cutting1999theory}{}}%
Cutting, A. L., \& Dunn, J. (1999). Theory of {Mind}, {Emotion Understanding}, {Language}, and {Family Background}: {Individual Differences} and {Interrelations}. \emph{Child Development}, \emph{70}(4), 853--865. \url{https://doi.org/10.1111/1467-8624.00061}

\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G. (2019). The {Developmental Origins} of {Gaze-Following} in {Human Infants}. \emph{Infancy}, \emph{24}(3), 433--454. \url{https://doi.org/10.1111/infa.12276}

\leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
Devine, R. T., \& Hughes, C. (2018). Family {Correlates} of {False Belief Understanding} in {Early Childhood}: {A Meta-Analysis}. \emph{Child Development}, \emph{89}(3), 971--987. \url{https://doi.org/10.1111/cdev.12682}

\leavevmode\vadjust pre{\hypertarget{ref-dunn1991young}{}}%
Dunn, J., Brown, J., Slomkowski, C., Tesla, C., \& Youngblade, L. (1991). \href{https://www.ncbi.nlm.nih.gov/pubmed/1786720}{Young children's understanding of other people's feelings and beliefs: Individual differences and their antecedents}. \emph{Child Development}, \emph{62}(6), 1352--1366.

\leavevmode\vadjust pre{\hypertarget{ref-frank2016using}{}}%
Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M. L., \& Yurovsky, D. (2016). Using {Tablets} to {Collect Data From Young Children}. \emph{Journal of Cognition and Development}, \emph{17}(1), 1--17. \url{https://doi.org/10.1080/15248372.2015.1061528}

\leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
Frischen, A., Bayliss, A. P., \& Tipper, S. P. (2007). Gaze cueing of attention: {Visual} attention, social cognition, and individual differences. \emph{Psychological Bulletin}, \emph{133}(4), 694--724. \url{https://doi.org/10.1037/0033-2909.133.4.694}

\leavevmode\vadjust pre{\hypertarget{ref-gathercole2004structure}{}}%
Gathercole, S. E., Pickering, S. J., Ambridge, B., \& Wearing, H. (2004). The {Structure} of {Working Memory From} 4 to 15 {Years} of {Age}. \emph{Developmental Psychology}, \emph{40}, 177--190. \url{https://doi.org/10.1037/0012-1649.40.2.177}

\leavevmode\vadjust pre{\hypertarget{ref-gola2012mental}{}}%
Gola, A. A. H. (2012). Mental verb input for promoting children's theory of mind: {A} training study. \emph{Cognitive Development}, \emph{27}(1), 64--76. \url{https://doi.org/10.1016/j.cogdev.2011.10.003}

\leavevmode\vadjust pre{\hypertarget{ref-gopnik1991young}{}}%
Gopnik, A., \& Slaughter, V. (1991). Young {Children}'s {Understanding} of {Changes} in {Their Mental States}. \emph{Child Development}, \emph{62}(1), 98. \url{https://doi.org/10.2307/1130707}

\leavevmode\vadjust pre{\hypertarget{ref-haines2020theoretically}{}}%
Haines, N., Kvam, P. D., Irving, L. H., Smith, C., Beauchaine, T. P., Pitt, M. A., \ldots{} Turner, B. M. (2020). \emph{Theoretically {Informed Generative Models Can Advance} the {Psychological} and {Brain Sciences}: {Lessons} from the {Reliability Paradox}}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/xr7y3}

\leavevmode\vadjust pre{\hypertarget{ref-happe2017structure}{}}%
Happé, F., Cook, J. L., \& Bird, G. (2017). The {Structure} of {Social Cognition}: {In}(ter)dependence of {Sociocognitive Processes}. \emph{Annual Review of Psychology}, \emph{68}(1), 243--267. \url{https://doi.org/10.1146/annurev-psych-010416-044046}

\leavevmode\vadjust pre{\hypertarget{ref-hedge2018reliability}{}}%
Hedge, C., Powell, G., \& Sumner, P. (2018). The reliability paradox: {Why} robust cognitive tasks do not produce reliable individual differences. \emph{Behavior Research Methods}, \emph{50}(3), 1166--1186. \url{https://doi.org/10.3758/s13428-017-0935-1}

\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
Hernik, M., \& Broesch, T. (2019). Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}. \emph{Developmental Science}, \emph{22}(4), e12779. \url{https://doi.org/10.1111/desc.12779}

\leavevmode\vadjust pre{\hypertarget{ref-herrmann2010structure}{}}%
Herrmann, E., Hernández-Lloreda, M. V., Call, J., Hare, B., \& Tomasello, M. (2010). The {Structure} of {Individual Differences} in the {Cognitive Abilities} of {Children} and {Chimpanzees}. \emph{Psychological Science}, \emph{21}(1), 102--110. \url{https://doi.org/10.1177/0956797609356511}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2000good}{}}%
Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A. (2000). Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}. \emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490. \url{https://doi.org/10.1111/1469-7610.00633}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2015individual}{}}%
Hughes, C., \& Devine, R. T. (2015). Individual {Differences} in {Theory} of {Mind From Preschool} to {Adolescence}: {Achievements} and {Directions}. \emph{Child Development Perspectives}, \emph{9}(3), 149--153. \url{https://doi.org/10.1111/cdep.12124}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2007executive}{}}%
Hughes, C., \& Ensor, R. (2007). Executive function and theory of mind: {Predictive} relations from ages 2 to 4. \emph{Developmental Psychology}, \emph{43}(6), 1447--1459. \url{https://doi.org/10.1037/0012-1649.43.6.1447}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2011individual}{}}%
Hughes, C., Ensor, R., \& Marks, A. (2011). Individual differences in false belief understanding are stable from 3 to 6 years of age and predict children's mental state talk with school friends. \emph{Journal of Experimental Child Psychology}, \emph{108}(1), 96--112. \url{https://doi.org/10.1016/j.jecp.2010.07.012}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2004links}{}}%
Hughes, C., \& Leekam, S. (2004). What are the {Links Between Theory} of {Mind} and {Social Relations}? {Review}, {Reflections} and {New Directions} for {Studies} of {Typical} and {Atypical Development}. \emph{Social Development}, \emph{13}(4), 590--619. \url{https://doi.org/10.1111/j.1467-9507.2004.00285.x}

\leavevmode\vadjust pre{\hypertarget{ref-imuta2016theory}{}}%
Imuta, K., Henry, J. D., Slaughter, V., Selcuk, B., \& Ruffman, T. (2016). Theory of mind and prosocial behavior in childhood: {A} meta-analytic review. \emph{Developmental Psychology}, \emph{52}(8), 1192--1205. \url{https://doi.org/10.1037/dev0000140}

\leavevmode\vadjust pre{\hypertarget{ref-itakura1998use}{}}%
Itakura, S., \& Tanaka, M. (1998). Use of experimenter-given cues during object-choice tasks by chimpanzees ({Pan} troglodytes), an orangutan ({Pongo} pygmaeus), and human infants ({Homo} sapiens). \emph{Journal of Comparative Psychology}, \emph{112}(2), 119--126. \url{https://doi.org/10.1037/0735-7036.112.2.119}

\leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
Kidd, E., Donnelly, S., \& Christiansen, M. H. (2018). Individual {Differences} in {Language Acquisition} and {Processing}. \emph{Trends in Cognitive Sciences}, \emph{22}(2), 154--169. \url{https://doi.org/10.1016/j.tics.2017.11.006}

\leavevmode\vadjust pre{\hypertarget{ref-lecce2014promoting}{}}%
Lecce, S., Bianco, F., Devine, R. T., Hughes, C., \& Banerjee, R. (2014). Promoting theory of mind during middle childhood: {A} training program. \emph{Journal of Experimental Child Psychology}, \emph{126}, 52--67. \url{https://doi.org/10.1016/j.jecp.2014.03.002}

\leavevmode\vadjust pre{\hypertarget{ref-lee1998children}{}}%
Lee, K., Eskritt, M., Symons, L. A., \& Muir, D. (1998). Children's use of triadic eye gaze information for "mind reading". \emph{Developmental Psychology}, \emph{34}(3), 525--539. \url{https://doi.org/10.1037//0012-1649.34.3.525}

\leavevmode\vadjust pre{\hypertarget{ref-macdonald2013eye}{}}%
Macdonald, R. G., \& Tatler, B. W. (2013). Do as eye say: {Gaze} cueing and language in a real-world social interaction. \emph{Journal of Vision}, \emph{13}(4), 6--6. \url{https://doi.org/10.1167/13.4.6}

\leavevmode\vadjust pre{\hypertarget{ref-mahy2017testing}{}}%
Mahy, C. E. V., Bernstein, D. M., Gerrard, L. D., \& Atance, C. M. (2017). Testing the validity of a continuous false belief task in 3- to 7-year-old children. \emph{Journal of Experimental Child Psychology}, \emph{160}, 50--66. \url{https://doi.org/10.1016/j.jecp.2017.03.010}

\leavevmode\vadjust pre{\hypertarget{ref-mayer2015weird}{}}%
Mayer, A., \& Träuble, B. (2015). The weird world of cross-cultural false-belief research: {A} true- and false-belief study among samoan children based on commands. \emph{Journal of Cognition and Development}, \emph{16}(4), 650--665. \url{https://doi.org/10.1080/15248372.2014.926273}

\leavevmode\vadjust pre{\hypertarget{ref-mayes1996testretest}{}}%
Mayes, L. C., Klin, A., Tercyak, K. P., Cicchetti, D. V., \& Cohen, D. J. (1996). Test-{Retest Reliability} for {False-Belief Tasks}. \emph{Journal of Child Psychology and Psychiatry}, \emph{37}(3), 313--319. \url{https://doi.org/10.1111/j.1469-7610.1996.tb01408.x}

\leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
McEwen, F., Happé, F., Bolton, P., Rijsdijk, F., Ronald, A., Dworzynski, K., \& Plomin, R. (2007). Origins of individual differences in imitation: Links with language, pretend play, and socially insightful behavior in two-year-old twins. \emph{Child Development}, \emph{78}(2), 474--492. \url{https://doi.org/10.1111/j.1467-8624.2007.01010.x}

\leavevmode\vadjust pre{\hypertarget{ref-milligan2007language}{}}%
Milligan, K., Astington, J. W., \& Dack, L. A. (2007). Language and {Theory} of {Mind}: {Meta-Analysis} of the {Relation Between Language Ability} and {False-belief Understanding}. \emph{Child Development}, \emph{78}(2), 622--646. \url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}

\leavevmode\vadjust pre{\hypertarget{ref-molleman2019unleashing}{}}%
Molleman, L., Kurvers, R. H. J. M., \& van den Bos, W. (2019). Unleashing the {BEAST}: A brief measure of human social information use. \emph{Evolution and Human Behavior}, \emph{40}(5), 492--499. \url{https://doi.org/10.1016/j.evolhumbehav.2019.06.005}

\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
Moore, C. (2008). The {Development} of {Gaze Following}. \emph{Child Development Perspectives}, \emph{2}(2), 66--70. \url{https://doi.org/10.1111/j.1750-8606.2008.00052.x}

\leavevmode\vadjust pre{\hypertarget{ref-mundy2007individual}{}}%
Mundy, P., Block, J., Delgado, C., Pomares, Y., Van Hecke, A. V., \& Parlade, M. V. (2007). Individual differences and the development of joint attention in infancy. \emph{Child Development}, \emph{78}(3), 938--954. \url{https://doi.org/10.1111/j.1467-8624.2007.01042.x}

\leavevmode\vadjust pre{\hypertarget{ref-okumura2017individual}{}}%
Okumura, Y., Kanakogi, Y., Kobayashi, T., \& Itakura, S. (2017). Individual differences in object-processing explain the relationship between early gaze-following and later language development. \emph{Cognition}, \emph{166}, 418--424. \url{https://doi.org/10.1016/j.cognition.2017.06.005}

\leavevmode\vadjust pre{\hypertarget{ref-palan2018prolific}{}}%
Palan, S., \& Schitter, C. (2018). Prolific.ac\textemdash{{A}} subject pool for online experiments. \emph{Journal of Behavioral and Experimental Finance}, \emph{17}, 22--27. \url{https://doi.org/10.1016/j.jbef.2017.12.004}

\leavevmode\vadjust pre{\hypertarget{ref-pavarini2013parental}{}}%
Pavarini, G., de Hollanda Souza, D., \& Hawk, C. K. (2013). Parental {Practices} and {Theory} of {Mind Development}. \emph{Journal of Child and Family Studies}, \emph{22}(6), 844--853. \url{https://doi.org/10.1007/s10826-012-9643-8}

\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
Perner, J., Ruffman, T., \& Leekam, S. R. (1994). Theory of {Mind Is Contagious}: {You Catch It} from {Your Sibs}. \emph{Child Development}, \emph{65}(4), 1228--1238. \url{https://doi.org/10.2307/1131316}

\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}

\leavevmode\vadjust pre{\hypertarget{ref-peterson2012mind}{}}%
Peterson, Wellman, H. M., \& Slaughter, V. (2012). The {Mind Behind} the {Message}: {Advancing Theory-of-Mind Scales} for {Typically Developing Children}, and {Those With Deafness}, {Autism}, or {Asperger Syndrome}: {\textbf{The Mind Behind}}{ \textbf{the} }{\textbf{Message}}. \emph{Child Development}, \emph{83}(2), 469--485. \url{https://doi.org/10.1111/j.1467-8624.2011.01728.x}

\leavevmode\vadjust pre{\hypertarget{ref-poulin-dubois2023discontinuity}{}}%
Poulin-Dubois, D., Goldman, E. J., Meltzer, A., \& Psaradellis, E. (2023). Discontinuity from implicit to explicit theory of mind from infancy to preschool age. \emph{Cognitive Development}, \emph{65}, 101273. \url{https://doi.org/10.1016/j.cogdev.2022.101273}

\leavevmode\vadjust pre{\hypertarget{ref-pronk2021methods}{}}%
Pronk, T., Molenaar, D., Wiers, R. W., \& Murre, J. (2021). Methods to split cognitive task data for estimating split-half reliability: {A} comprehensive review and systematic assessment. \emph{Psychonomic Bulletin \& Review}. \url{https://doi.org/10.3758/s13423-021-01948-3}

\leavevmode\vadjust pre{\hypertarget{ref-rcoreteam2022language}{}}%
R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.

\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}

\leavevmode\vadjust pre{\hypertarget{ref-raviv2018developmental}{}}%
Raviv, L., \& Arnon, I. (2018). The developmental trajectory of children's auditory and visual statistical learning abilities: Modality-based differences in the effect of age. \emph{Developmental Science}, \emph{21}(4), e12593. \url{https://doi.org/10.1111/desc.12593}

\leavevmode\vadjust pre{\hypertarget{ref-repacholi2003introduction}{}}%
Repacholi, V. S. \&. B. (2003). Introduction {Individual Differences} in {Theory} of {Mind}: {What Are We Investigating}? In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.

\leavevmode\vadjust pre{\hypertarget{ref-rizzo2018theory}{}}%
Rizzo, M. T., \& Killen, M. (2018). Theory of mind is related to children's resource allocations in gender stereotypic contexts. \emph{Developmental Psychology}, \emph{54}(3), 510. \url{https://doi.org/10.1037/dev0000439}

\leavevmode\vadjust pre{\hypertarget{ref-rouder2019psychometrics}{}}%
Rouder, J. N., \& Haaf, J. M. (2019). A psychometrics of individual differences in experimental tasks. \emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467. \url{https://doi.org/10.3758/s13423-018-1558-y}

\leavevmode\vadjust pre{\hypertarget{ref-samuel2018egocentric}{}}%
Samuel, S., Legg, E. W., Lurz, R., \& Clayton, N. S. (2018a). Egocentric bias across mental and non-mental representations in the {Sandbox Task}. \emph{Quarterly Journal of Experimental Psychology}, \emph{71}(11), 2395--2410. \url{https://doi.org/10.1177/1747021817742367}

\leavevmode\vadjust pre{\hypertarget{ref-samuel2018unreliability}{}}%
Samuel, S., Legg, E. W., Lurz, R., \& Clayton, N. S. (2018b). The unreliability of egocentric bias across self\textendash other and memory\textendash belief distinctions in the {Sandbox Task}. \emph{Royal Society Open Science}, \emph{5}(11), 181355. \url{https://doi.org/10.1098/rsos.181355}

\leavevmode\vadjust pre{\hypertarget{ref-schaafsma2015deconstructing}{}}%
Schaafsma, S. M., Pfaff, D. W., Spunt, R. P., \& Adolphs, R. (2015). Deconstructing and reconstructing theory of mind. \emph{Trends in Cognitive Sciences}, \emph{19}(2), 65--72. \url{https://doi.org/10.1016/j.tics.2014.11.007}

\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
Shepherd, S. (2010). Following {Gaze}: {Gaze-Following Behavior} as a {Window} into {Social Cognition}. \emph{Frontiers in Integrative Neuroscience}, \emph{4}.

\leavevmode\vadjust pre{\hypertarget{ref-slaughter2015theorya}{}}%
Slaughter, V. (2015). Theory of {Mind} in {Infants} and {Young Children}: {A Review}. \emph{Australian Psychologist}, \emph{50}(3), 169--172. \url{https://doi.org/10.1111/ap.12080}

\leavevmode\vadjust pre{\hypertarget{ref-sodian2023reply}{}}%
Sodian, B. (2023). Reply to {Poulin-Dubois} et al. (2023): {Replication} problems concerning both implicit and explicit false belief reasoning greatly reduced the chance of finding longitudinal correlations. \emph{Cognitive Development}, \emph{65}, 101294. \url{https://doi.org/10.1016/j.cogdev.2022.101294}

\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A. (2016). Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}. \emph{Child Development}, \emph{87}(4), 1221--1232. \url{https://doi.org/10.1111/cdev.12533}

\leavevmode\vadjust pre{\hypertarget{ref-sommerville2013measuring}{}}%
Sommerville, J. A., Bernstein, D. M., \& Meltzoff, A. N. (2013). Measuring {Beliefs} in {Centimeters}: {Private Knowledge Biases Preschoolers}' and {Adults}' {Representation} of {Others}' {Beliefs}. \emph{Child Development}, \emph{84}(6), 1846--1854. \url{https://doi.org/10.1111/cdev.12110}

\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003constructing}{}}%
Tomasello, M. (2003). \emph{Constructing a language: {A} usage-based theory of language acquisition} (pp. viii, 388). {Cambridge, MA, US}: {Harvard University Press}.

\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
Tomasello, M., Hare, B., Lehmann, H., \& Call, J. (2007). Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis. \emph{Journal of Human Evolution}, \emph{52}(3), 314--320. \url{https://doi.org/10.1016/j.jhevol.2006.10.001}

\leavevmode\vadjust pre{\hypertarget{ref-underwood1975individual}{}}%
Underwood, B. J. (1975). Individual differences as a crucible in theory construction. \emph{American Psychologist}, \emph{30}(2), 128--134. \url{https://doi.org/10.1037/h0076759}

\leavevmode\vadjust pre{\hypertarget{ref-walker2005gender}{}}%
Walker, S. (2005). Gender {Differences} in the {Relationship Between Young Children}'s {Peer-Related Social Competence} and {Individual Differences} in {Theory} of {Mind}. \emph{The Journal of Genetic Psychology}, \emph{166}(3), 297--312. \url{https://doi.org/10.3200/GNTP.166.3.297-312}

\leavevmode\vadjust pre{\hypertarget{ref-wellman2012theory}{}}%
Wellman, H. M. (2012). Theory of mind: {Better} methods, clearer findings, more development. \emph{European Journal of Developmental Psychology}, \emph{9}(3), 313--330. \url{https://doi.org/10.1080/17405629.2012.680297}

\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysis}{}}%
Wellman, H. M., Cross, D., \& Watson, J. (2001). Meta-analysis of theory-of-mind development: {The} truth about false belief. \emph{Child Development}, \emph{72}, 655--684. \url{https://doi.org/10.1111/1467-8624.00304}

\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}

\leavevmode\vadjust pre{\hypertarget{ref-wimmer1983beliefs}{}}%
Wimmer, H., \& Perner, J. (1983). Beliefs about beliefs: {Representation} and constraining function of wrong beliefs in young children's understanding of deception. \emph{Cognition}. \url{https://doi.org/10.1016/0010-0277(83)90004-5}

\leavevmode\vadjust pre{\hypertarget{ref-zhang2021worse}{}}%
Zhang, Z., Yu, H., Long, M., \& Li, H. (2021). Worse {Theory} of {Mind} in {Only-Children Compared} to {Children With Siblings} and {Its Intervention}. \emph{Frontiers in Psychology}, \emph{12}, 5073. \url{https://doi.org/10.3389/fpsyg.2021.754168}

\end{CSLReferences}

\endgroup

\end{document}

### 2023-03-21 stats/analysis.Rmd
set up repo

---
title: "Stats"
author: "Julia Prein"
date: "03/21/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(viridis) # col scales, plotting...
library(ggpubr)
library(ggthemes)
library(tidyboot) # for bootstrap CIs
library(brms) # modeling
library(tidybayes) # for stat_halfeye

options(scipen = 999)
theme_set(theme_classic())
# Seed for random number generation
set.seed(42)
```

```{r load_data}
# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
#   # determine order of factors
#   mutate(
#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
#     sample = factor(sample, levels = c("kids", "adults")), 
#     studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
#     
#     # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
#     # the smaller the value, the more central the position
#     symmetricPosition = ifelse(studyversion == "box", 
#                                # for box version
#                                case_when(
#                                   targetPosition == "box3" ~ 0, 
#                                   targetPosition == "box2" | targetPosition == "box4" ~ 1,
#                                   targetPosition == "box1" | targetPosition == "box5" ~ 2), 
#                                # for hedge version
#                                targetCentralityX
#                        ), 
#     
#     # distance between target and click in balloon widths (balloon width is 160 SVG units)
#     clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
#   )
```

### 2023-03-21 supplements/supplements.Rmd
set up repo

--- 2023-03-21 paper/manuscript.Rmd
@@
 ---
-title             : "Variation in gaze understanding across the life span: A process-level perspective"
-shorttitle        : "modeling variation in gaze understanding"
+title             : "Supplements for the manuscript  'Variation in gaze understanding across the life span: A process-level perspective'"
+shorttitle        : "Supplements"
 author:
@@
     affiliation   : "1"
-
 affiliation:
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
-authornote: |
-abstract: |
-  Abstract
-
-keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
-wordcount         : "xxx"
+floatsintext      : yes
 bibliography      : ["../../references.bib"]
-floatsintext      : yes
 figurelist        : no
@@
 library("papaja")
-library("ggplot2")
+library("tidyverse")
 library("ggpubr")
-library("tidyverse")
-library("brms")
+library("kableExtra")
 theme_set(theme_classic())
@@
 ```
-
-```{r load_data}
-# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-#   # determine order of factors
-#   mutate(
-#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
-#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-#     sample = factor(sample, levels = c("kids", "adults")), 
-#     studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
-#   )
-```
-
-# Introduction
-- why do we care about developmental trajectory? ref to stat learning paper
-- variation
-
-# Lifespan 
-- development & individual differences in gaze understanding
-- verweis methods paper reliable differences kinder & adults. 
-- kontinuerliche, systematische variation, wodrin? => model
-
-# Computational cognitive model
-- model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
-- entwicklungsperspektive basierend auf model
-- dann prozess-ebene => magnet
-
-# Non-social vector following
-
-## Analysis
-All test trials without voice-over descriptions were included in our analyses.
-We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
-Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
-
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-# knitr::include_graphics("../figures/screenshot.png")
-```
-
-\newpage
-
-# Declarations
-
-## Open practices statement
-
-The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
-All experiments were pre-registered (<https://osf.io/zjhsc/>).
-
-## Funding
-
-This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers, and adults who participated in the study.
-We thank Jana Jurkat for her help with data collection.
-
-## Conflicts of interest
-
-The authors declare that they have no conflict of interest.
-
-## Consent to participate
-
-Informed consent was obtained from all individual participants included in the study or their legal guardians.
-
-## Authors' contributions
-
-The authors made the following contributions:
-### TODO
 

### 2023-03-21 supplements/supplements.tex
set up repo

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
\date{}

\shorttitle{Supplements}

\authornote{

Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany. E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

\begin{document}
\maketitle

\hypertarget{effects-of-trial-type-and-trial-number}{%
\section{Effects of trial type and trial number}\label{effects-of-trial-type-and-trial-number}}

Children showed nearly perfect precision in the first training trial. As visual access to the target location decreased in the succeeding training trials, imprecision levels increased. Within test trials, children's imprecision levels did not vary as a function of trial number.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_trainingtrials}

}

\caption{\textbf{Imprecision by trial type, split by study version and sample}. The x axis represents the trial type. The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center. Small dots show the imprecision for each subject in each trial. Boxplots (boxes represent first to third quartiles of data; vertical lines indicate the median; horizontal black lines display the range) and a half violin plot show the data distribution.}\label{fig:fig1}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_acrosstrials}

}

\caption{\textbf{Imprecision across test trials, split by study version and sample}. The x axis represents trial number. The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center. The black dashed regression lines show smooth conditional means based on linear models. Small colored dots show the imprecision for each subject in each trial. Colored lines connect the trials of each individual.}\label{fig:fig2}
\end{figure}

\newpage

\hypertarget{webcam-coding-of-the-child-sample}{%
\section{Webcam coding of the child sample}\label{webcam-coding-of-the-child-sample}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_webcamcoding}

}

\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}. Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig3}
\end{figure}

Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
This difference was especially prominent in younger participants in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
A trial was defined as the time between two eye blinking sounds.
We transcribed all utterances by parents and children and counted the words uttered by each.
We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
We conducted a model comparison to estimate the effects of parental interference.
Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.

We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
We compared models using WAIC (widely applicable information criterion) scores and weights.
As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
In all cases, however, ELPD difference scores were smaller than their standard errors.
Similarly, 95\% CI of the model estimates included zero and were rather wide.
Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
\addlinespace
By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
\addlinespace
By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\hypertarget{reliability-by-age-group}{%
\section{Reliability by age group}\label{reliability-by-age-group}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_reli_byagegroup}

}

\caption{\textbf{Reliability split by age group}. (A) Internal consistency (odd-even split) in hedge child sample by age group. (B) Test-retest reliability in hedge child sample by age group. (C) Internal consistency (odd-even split) in box child sample by age group. (D) Test-retest reliability in box child sample by age group. For the hedge version, performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. For the box version, performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}. Dots show the performance for each subject. The color of data points denotes age group.}\label{fig:fig4}
\end{figure}

\newpage

\hypertarget{validity}{%
\section{Validity}\label{validity}}

\hypertarget{social-environmental-factors}{%
\subsection{Social-environmental factors}\label{social-environmental-factors}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We included all children where families filled out a short demographic questionnaire. This subsample consisted of 109 children, including 30 3-year-olds (mean = 41.80 months, SD = 3.44, range = 36 - 47),
36 4-year-olds (mean = 54.19 months, SD = 3.08, range = 48 - 59), and
43 5-year-olds (mean = 66.28 months, SD = 3.62, range = 60 - 71).

\hypertarget{analysis}{%
\subsubsection{Analysis}\label{analysis}}

To estimate social environmental influences on gaze understanding, we fitted GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (scaled), data collection mode (reference category: remote unsupervised) and study version (reference category: box version): \texttt{cor\_tango\ \textbar{}\ trials(n\_tango)\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
For the target position, we categorized two adjacent bins as one imaginary box.
To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
Across the two study versions, we could consequently model the number of participant's correct responses using a \texttt{Binomial} distribution.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
In addition, we calculated three index scores.
First, we calculated a sibling variety score according to Peterson (2000).
Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005).
Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare.
We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age of childcare entry & 571.62 & 28.13 & 0.73 & 0.00 & 0.00\\
Null model & 575.96 & 30.44 & 0.08 & -2.17 & 4.53\\
\# Children in household aged 0-18 & 577.60 & 29.63 & 0.04 & -2.99 & 4.74\\
Peer exposure index & 577.74 & 30.19 & 0.03 & -3.06 & 4.68\\
\# Children in household aged 1-12 & 578.07 & 29.93 & 0.03 & -3.22 & 4.70\\
\addlinespace
Sibling variety score (Cassidy et al., 2005) & 578.13 & 29.87 & 0.03 & -3.25 & 4.67\\
Sibling variety score (Peterson, 2000) & 578.29 & 29.87 & 0.03 & -3.33 & 4.66\\
\# Household members & 578.80 & 30.40 & 0.02 & -3.59 & 4.53\\
Average hours spent in childcare per day & 579.36 & 30.74 & 0.02 & -3.87 & 4.60\\
\bottomrule
\end{tabular}}
\end{table}

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrrrrr}
\toprule
  & n & mean & sd & min & max & skew & kurtosis & se\\
\midrule
Age of childcare entry in months & 109 & 14.96 & 5.54 & 1.0 & 40 & 1.72 & 5.65 & 0.53\\
Average hours spent in childcare per day & 109 & 7.50 & 0.92 & 3.5 & 9 & -0.67 & 1.92 & 0.09\\
\# Household members & 109 & 3.72 & 0.92 & 2.0 & 7 & 0.30 & 0.49 & 0.09\\
\# Children in household aged 0-18 & 109 & 0.83 & 0.79 & 0.0 & 4 & 0.87 & 1.09 & 0.08\\
\# Children in household aged 1-12 & 109 & 0.69 & 0.74 & 0.0 & 4 & 1.23 & 2.67 & 0.07\\
\addlinespace
Sibling variety score (Peterson, 2000) & 109 & 0.60 & 0.56 & 0.0 & 2 & 0.23 & -0.87 & 0.05\\
Sibling variety score (Cassidy et al., 2005) & 109 & 0.63 & 0.54 & 0.0 & 2 & 0.18 & -0.70 & 0.05\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{receptive-vocabulary}{%
\subsection{Receptive vocabulary}\label{receptive-vocabulary}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

Our sample consisted of 117 children, including 11 3-year-olds (mean = 45.05 months, SD = 1.58, range = 43 - 47,
26 4-year-olds (mean = 53.17 months, SD = 3.01, range = 48 - 57),
32 5-year-olds (mean = 65.80 months, SD = 3.23, range = 61 - 71),\\
36 6-year-olds (mean = 78.36 months, SD = 3.26, range = 72 - 84), and 12 7-year-olds (mean = 88.11 months, SD = 1.96, range = 84 - 91).

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022). Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).

Each trial presented four pictures: one target word alongside three distractors (1 phonological, 1 semantic, 1 unrelated distractor). A verbal prompt asked children to select one of the pictures (prompt: ``Zeige mir {[}target word{]}''; engl.: ``Show me {[}target word{]}''). The positioning of the target word and the three distractor types was counterbalanced across the four display positions (upper/lower and left/right corners). Children responded by clicking on one of the four pictures. The outcome measure consisted of the proportion of correct responses.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/orev_procedure}

}

\caption{Setup of the oREV. On each trial, participants heard a word and were asked to select the corresponding picture. Verbal prompts could be replayed by pressing the loudspeaker button.}\label{fig:fig5}
\end{figure}

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

Families received a personalized study link and completed the study at any location or time they wanted. Caregivers were asked to only provide technical support but no further help. Webcam recordings were done whenever consented and technically possible. We analyzed data of 20 trials per child. Children received the trials in two different orders. Performance across the two study orders did not differ. Hence, we decided to combine the data.

\hypertarget{analysis-1}{%
\subsubsection{Analysis}\label{analysis-1}}

To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: \texttt{cor\_clt\ \textbar{}\ trials(n\_clt)\ \textasciitilde{}\ age\_centered\ +\ mean\_gaze\_centered}). We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.

\hypertarget{results-1}{%
\subsubsection{Results}\label{results-1}}

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age (scaled), TANGO score (scaled) & 570.14 & 26.37 & 0.97 & 0.00 & 0.00\\
Age (scaled) & 577.22 & 27.11 & 0.03 & -3.54 & 4.15\\
Null model & 635.80 & 28.71 & 0.00 & -32.83 & 10.61\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\hypertarget{additional-information-for-the-adult-sample}{%
\section{Additional information for the adult sample}\label{additional-information-for-the-adult-sample}}

\begin{longtable}{llr}
\toprule
Current Country of Residence & studytype & n\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
Current Country of Residence & studytype & n\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
United Kingdom & vali & 47\\
South Africa & vali & 8\\
Portugal & vali & 6\\
Poland & vali & 5\\
Ireland & vali & 5\\
\addlinespace
Italy & vali & 4\\
Spain & vali & 4\\
Netherlands & vali & 4\\
Canada & vali & 2\\
Australia & vali & 2\\
\addlinespace
France & vali & 2\\
Austria & vali & 2\\
Norway & vali & 1\\
DATA EXPIRED & vali & 1\\
Finland & vali & 1\\
\addlinespace
Greece & vali & 1\\
Germany & vali & 1\\
United States & vali & 1\\
Mexico & vali & 1\\
South Africa & reli & 48\\
\addlinespace
United Kingdom & reli & 19\\
United States & reli & 14\\
Portugal & reli & 10\\
Italy & reli & 7\\
Canada & reli & 6\\
\addlinespace
Spain & reli & 5\\
Ireland & reli & 5\\
Poland & reli & 4\\
Greece & reli & 4\\
Netherlands & reli & 3\\
\addlinespace
CONSENT REVOKED & reli & 3\\
Germany & reli & 3\\
Australia & reli & 2\\
France & reli & 2\\
Czech Republic & reli & 2\\
\addlinespace
Hungary & reli & 2\\
Chile & reli & 1\\
Iceland & reli & 1\\
New Zealand & reli & 1\\*
\end{longtable}

\hypertarget{recruitment}{%
\subsection{Recruitment}\label{recruitment}}

We recruited participants using the online participant recruitment service \emph{Prolific} from the University of Oxford.
\emph{Prolific}'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
Therefore, study data was saved only on our internal servers, while \emph{Prolific} provided demographic information of the participants.
Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
This way, we could match participant demographic data to our study data.
The same technique was used to confirm study completion: we redirected participants from our study website back to the \emph{Prolific} website using URL parameters.
We used \emph{Prolific}'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.

\hypertarget{study-1---validation-hedge-version}{%
\subsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}

The aim of Study 1 was to validate the hedge version of our gaze understanding task.
The pre-registration can be found here: \url{https://osf.io/r3bhn}.
We recruited participants online by advertising the study on \emph{Prolific}.

50 adults participated in the study.
One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in May 2021.
Participants were compensated with £1.25 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
On average, participants took 05:56min to complete the study.
Participants were required to complete the study on a tablet or desktop.
Participation on mobile devices was disabled since the display would be too small and would harm click precision.
It was indicated that the study required audio sound.

We stored \emph{Prolific}'s internal demographic information, while not asking for additional personal information.

\hypertarget{study-2---validation-box-version}{%
\subsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}

As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
However, this time we focussed on validating the box version of the task in an adult sample.
Participants were presented with eight boxes in which the target could land.
50 adults participated in the study.
One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Data collection took place in June 2021.
Participants were compensated with £1.00 for completing the study.
We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
On average, participants took 04:43min to complete the study.

\hypertarget{study-3---reliability-hedge-version}{%
\subsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}

In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
The pre-registration can be found here: \url{https://osf.io/nu62m}.
We tested the same participants twice with a delay of two weeks.
The testing conditions were as specified in Study 1 and 2.
However, the target locations as well as the succession of animals and target colors was randomized once.
Each participant then received the same fixed randomized order of target location, animal, and target color.
Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.

In addition to the aforementioned prescreening settings, we used a whitelist.
\emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
Only these subjects are then invited to participate in a study.
This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.

In a first round, 60 participants took part on the first testday.
Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
The maximum time is calculated by \emph{Prolific}, based on the estimated average completion time.
For this study, the maximum time amounted to 41 minutes.
For the first testday, participants were compensated with £1.25.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
On average, participants took 07:11min to complete the first part.

Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Participants were compensated with £1.50 for completing the second part of the study.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
On average, participants took 06:36min to complete the second part of the study.

Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
On average, participants took 06:51min to complete the first part.

Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
On average, participants took 06:26min to complete the second part of the study.

\hypertarget{study-4---reliability-box-version}{%
\subsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}

As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
However, this time participants were presented with the box version of the task.
Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
As in study 2, we employed eight boxes in which the target could land.

In a first round, 60 participants took part on the first testday.
Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
For the first testday, participants were compensated with £1.25.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
On average, participants took 07:33min to complete the first part.

Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
Participants were compensated with £1.50 for completing the second part of the study.
We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
On average, participants took 07:50min to complete the second part of the study.

Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
On average, participants took 07:37min to complete the first part.

Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
On average, participants took 06:30min to complete the second part of the study.

\newpage

\hypertarget{instructions-and-voice-over-descriptions}{%
\section{Instructions and voice-over descriptions}\label{instructions-and-voice-over-descriptions}}

This is the content of our audio recordings that were played as instructions and during voice-over trials.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule()
\endhead
\textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
\textbf{welcome} & Hallo! Schön, dass du da bist. Wir spielen jetzt das Ballon-Spiel! Siehst du die Tiere auf dem Bild da? Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen. Was genau passiert, erklären wir dir jetzt ganz in Ruhe. & Hello! Great that you're here. We'll now play a balloon game. Can you see the animals in the picture over there? We want to play together with the animals using the balloon. We'll now talk you through exactly what will happen. & welcome.mp3 \\
\textbf{touch} & Schau mal, da steht ein Tier im Fenster. Und siehst du den Ballon da? Der Ballon fällt immer runter und landet auf dem Boden. Und du musst ihn dann finden. Das Tier hilft Dir und schaut immer den Ballon an. & Look, an animal is standing in the window. And can you see the balloon over there? The balloon always falls down and lands on the ground. And you have to find it! The animal helps you and always looks at the balloon. & touch-1.mp3 \\
& Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
\textbf{fam - HEDGE} & Klasse, das war super! Jetzt spielen wir weiter. Siehst du wieder das Tier und den Ballon da? Der Ballon fällt wieder runter. Diesmal fällt er hinter eine Hecke. Du musst ihn wieder finden. Das Tier hilft dir und schaut immer den Ballon an. & Perfect, that was great! Now, we'll continue playing. Can you see the animal and the balloon again? The balloon will fall down again. This time, it will fall behind a hedge. And you have to find it! The animal helps you and looks at the balloon. & fam-hedge-1.mp3 \\
& Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
\textbf{fam - BOX} & Klasse, das war super! Jetzt spielen wir weiter. Siehst du wieder das Tier und den Ballon da? Der Ballon fällt wieder runter. Diesmal fällt er in eine Kiste. Du musst ihn wieder finden. Das Tier hilft dir und schaut immer den Ballon an. & Perfect, that was great! Now, we'll continue playing. Can you see the animal and the balloon again? The balloon falls down again. This time, it falls into a box. And you have to find it! The animal helps you and looks at the balloon. & fam-box-1.mp3 \\
& Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
\textbf{test - HEDGE} & Klasse , das hast du toll gemacht! Nun spielen wir weiter. Da sind wieder der Ballon, das Tier und die Hecke. Die Hecke wächst jetzt hoch. & Nice, good job! Now, we'll continue playing. There is the balloon, the animal and the hedge. The hedge is growing a bit now. & test-hedge-1.mp3 \\
& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber! Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden. Denk dran - das Tier schaut immer den Ballon an. & The balloon is behind the hedge now. You can't see it - but the animal can! The balloon falls to the ground and you have to find it. Remember - the animal always looks at the balloon! & test-hedge-2.mp3 \\
& Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
\textbf{test - BOX} & Klasse , das hast du toll gemacht! Nun spielen wir weiter. Da sind wieder der Ballon, das Tier und die Kisten. Jetzt wächst eine Hecke hoch. & Nice, good job! Now, we'll continue playing. There is the balloon and the animal. Now, a hedge is growing. & test-box-1.mp3 \\
& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber! Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden. Denk dran - das Tier schaut immer den Ballon an. & The balloon is behind the hedge now. You can't see it - but the animal can! The balloon falls into a box and you have to find it. Remember - the animal always looks at the balloon! & test-box-2.mp3 \\
& Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
\textbf{goodbye} & Geschafft! Die Tiere sind schon ganz glücklich vom Spielen! Vielen Dank für deine Hilfe! Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf & The animals are super happy after playing. Thanks a lot for your help! See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
\textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
\textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
\textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
\textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
\textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
\textbf{sound of blinking eyes} & - & - & blink.mp3 \\
\textbf{sound for target click} & - & - & positive-feedback.mp3 \\
\bottomrule()
\end{longtable}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.

\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
Cassidy, K. W., Fineberg, D. S., Brown, K., \& Perkins, A. (2005). Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}. \emph{Child Development}, \emph{76}(1), 97--106. Retrieved from \url{https://www.jstor.org/stable/3696711}

\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.

\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}

\end{CSLReferences}

\endgroup

\end{document}

### 2023-03-22 paper/manuscript.Rmd
add already written notes/code

@@
 ```{r load_data}
-# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-#   # determine order of factors
-#   mutate(
-#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
-#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-#     sample = factor(sample, levels = c("kids", "adults")), 
-#     studytype = factor(studytype, levels = c("vali", "vali2", "reli"))
-#   )
+# TODO: only hedge version
+
+testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>%
+  mutate_if(is.character, as.factor) %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")),
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "teens", "adults")),
+    studytype = factor(studytype, levels = c("vali", "reli")),
+
+    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
+    # the smaller the value, the more central the position
+    symmetricPosition = case_when(
+                                  targetPosition == "5" | targetPosition == "6" ~ 1,
+                                  targetPosition == "4" | targetPosition == "7" ~ 2,
+                                  targetPosition == "3" | targetPosition == "8" ~ 3,
+                                  targetPosition == "2" | targetPosition == "9" ~ 4,
+                                  targetPosition == "1" | targetPosition == "10" ~ 5,
+                       ),
+
+    # distance between target and click in balloon widths (balloon width is 160 SVG units)
+    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
+  )
 ```
@@
 
+## Why do we need gaze understanding?
+
+How do humans learn about their environment and navigate through their social surroundings?
+One possibility to extract information from the environment is through following others' focus of attention.
+Building a common ground is considered especially important in communicative interactions and shared activities [@tomasello2007reliance].
+
+## How does gaze following emerge?
+
+Existing studies operationalize gaze following as the ability to follow another agent's line of sight.
+As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
+Infants as young as six months can attune their gaze to that of another agent [@dentremont1997demonstration].
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412].
+
+While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
+One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.However, many cognitive abilities develop with age [e.g., working memory, @gathercole2004structure].
+Similarly, visual processing appears to improve with age.
+Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
+
+## The scope of infants' gaze following ability
+
+Though these studies suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions of the other agent.
+Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.
+Butterworth & Jarrett's ecological and geometric mechanism, @butterworth1991minds].
+Therefore, it is crucial to study children's intentional understanding of gaze.
+
+@moore1997role showed that 9-month-olds followed an agent's gaze more, when it was accompanied by a dynamic head turn in comparison to a static head turn.
+
+In a hiding game with two search locations, @povinelli1997exploitation found that three-year-olds used gaze as a cue to locate the reward, while two-year-olds performed at chance level.
+
+In a similar object choice paradigm with two containers, @behne2005oneyearolds investigated whether infants understand the communicative intent behind pointing and gaze cues.
+In contrast to @povinelli1997exploitation, they found that already 14-month-olds used the agent's cues to select an object.
+In conditions with absent-minded 'cues', infants performed around chance.
+This could be interpreted as infants recognizing the nature of this joint activity: namely, that the adult's behavior was beneficial and relevant for their object choice.
+
+### Head vs eye direction
+
+It is important to note that in many existing gaze conditions, the experimenter shifted their eyes and head in synchrony (e.g., [@povinelli1997exploitation, @behne2005oneyearolds]).
+Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
+
+A handful of studies approached this potential confound by separately manipulating head and eye movement.
+@brooks2002importance implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
+
+Investigating the 'cooperative eye hypothesis', @tomasello2007reliance implemented six conditions, in which an experimenter oriented towards the ceiling with their eyes only, head only (eyes closed), both head and eyes, or neither.
+They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
+
+Importantly, the subjects were not presented with an object choice but their attention orientation was measured.
+
+- [@raviv2018developmental]
+- [@astor2022gaze]
+- [@colombo2001development]
+- [@scaife1975capacity]
+- [@itakura1998use]
+
+- [@carpenter1998social] "Several other studies have attempted to determine more precisely the cue that infants are using when they follow the gaze direction of others, that is, whether they use adults' head or eye orientation.
+In tasks comparing infants' responses when the experimenters turned their head and eyes together to targets with their responses when the experimenters directed their eyes to the targets but their head remained facing forward, Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) all found that only infants age 12 months and older responded correctly when eyes and head were oriented in the same direction and that infants at all ages (i.e., through 19 months) performed poorly when eye and head direction diverged" (p.10-11) object choice.
+
+- [@silverstein2021infants] for vertical plane
+- [@zhang2019role]
+- [@frischen2007gaze]
+- [@lee1998children]
+- [@coelho2006searching]
+
+## Aim of the current project
+
+### Developmental trajectory, measuring & modeling individual differences
+
+In this study, we were interested in the developmental trajectory of gaze understanding.
+While we expect the younger children to be able to follow gaze, we aimed at assessing the differentiation of their social-cognitive ability.
+Our goal was *not* to establish the youngest age at which children understand gaze cues.
+Rather, we wanted to examine how that ability changes with age.
+
+In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent's gaze.
+While language demands were kept low, the participants had to actively respond and, therefore, make use of the presented gaze cue.
+
+A unique contribution of this study is the richness of the data set.
+Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
+We could circumvent these issues by applying the exact same task for the entire life span.
+
 # Lifespan 
@@
 - kontinuerliche, systematische variation, wodrin? => model
+
+```{r dev_sample}
+dev_kids <- testtrials %>%
+  filter(studytype == "vali" & age < 18) %>%
+  group_by(datacollection, agegroup) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>%
+  summarise(
+    nTotal = n_distinct(subjID),
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
+  )
+
+dev_adults <- testtrials %>%
+  filter(studytype == "vali" & sample == "adults") %>%
+  ungroup() %>%
+  mutate(
+    gender = ifelse(is.na(gender), 0, paste(gender)),
+    female = ifelse(gender == "f", 1, 0),
+  ) %>%
+  summarise(
+    nTotal = n_distinct(subjID),
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
+  )
+```
+
+## Participants
+
+We collected data from an in-person child sample, a remote child an teenager sample, and a remote adult sample. In-person testing with children took place in kindergartens in Leipzig, Germany.
+
+The in-person child sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` girls).
+
+For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+
+The remote child and teenager sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` 6-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` 7-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` 8-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` 9-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` 10-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` 11-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` 12-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` 13-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` 14-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` 15-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` 16-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` 17-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` girls).
+
+Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+
+Adults were recruited via *Prolific* [@palan2018prolific].
+*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
+Participants consisted of `r dev_adults$nTotal` English-speakers with an average age of `r dev_adults$meanAge` years (SD = `r dev_adults$sdAge`, range = `r dev_adults$minAge` - `r dev_adults$maxAge`, `r dev_adults$nFemales` females).
+
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
+
+## Materials
+
+We used the TANGO task [@prein2022tango].
+The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
+The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; @prein2022tango].
+
+Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
+Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
+The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
+The target flight was covered so that participants could not see where the target landed.
+Participants' task was to locate the target by tracking the agent's gaze.
+They could respond by clicking or touching on the screen.
+
+Four familiarization trials ensured that participants understood the task and felt comfortable with the response format.
+Then, 15 test trials followed.
+Completing the 19 trials took approximately 5-10 minutes.
+
+The outcome measure depended on the task version.
+In the continuous *hedge version*, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
+In the discrete *box version*, we calculated the proportion of correct responses.
+
+The randomization of the final target location also depended on the task version.
+In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
+In the box version, the target randomly landed in one of the boxes.
+We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
+Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
+
+(ref:figlab1) **Setup of the TANGO**.
+(A) Infrastructure for online testing.
+(i) Subjects aged 3 -- 99+ can participate.
+Data collection can take place anywhere: online, in kindergartens, or research labs.
+(ii) The task is presented as a website that works across devices.
+(iii) The scripts for the website and the recorded data are stored on secure local servers.
+(B) Hedge version (continuous) of the gaze understanding task.
+(i) The agent stands in a window with the target in front of them.
+(ii) A hedge grows and covers the target.
+(iii) The target falls to a random location on the ground.
+The agent's eyes track the movement of the target.
+(C) Box version (discrete) of the gaze understanding task.
+Number of boxes (min.
+1; max.
+8) as potential hiding locations can be set according to the researcher's need.
+
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/tango_procedure.png")
+```
+
+## Procedure
+
+In the in-person sample, children were tested on a tablet in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+Half of the sample completed the continuous task version, while the other half completed the discrete task version.
+
+In the remote sample, children and teenagers received a personalized link to the study website.
+Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
+Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.
+
+In the remote sample for children from three to five years old, the family's presentation device determined the task version.
+Whenever a touchscreen was available, the continuous task version was presented.
+For families using a computer without touchscreen, the discrete task version was shown.
+Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.
+
+The number of teenagers in our internal database for recruiting families substantially decreased by age.
+To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
+Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.
+
+The remote adult sample was equally distributed across the two task versions.
+
+## Analysis
+
+-   TODO: non-linear model for development
+
+All test trials without voice-over description were included in our analyses.
+We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
+Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
+We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
+
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
+For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
+We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
+
+## Results
+
+(ref:figlab2) **Differentiation in gaze understanding**.
+Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics(c("../figures/tango_dev.png"))
+```
+
+## Discussion
+
+Three-year-olds were surprisingly inaccurate in their responses.
+One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze following.
+Contrasting our results with previous findings on infant gaze following, this explanation is unlikely.
+A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
+
+Another point to keep in mind is that we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel, therefore establishing a confound with greater (head) movement.
+Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
+
+The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
 
@@
 
-## Analysis
-All test trials without voice-over descriptions were included in our analyses.
-We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
-Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+# Limitations
 
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-# knitr::include_graphics("../figures/screenshot.png")
-```
+# Discussion
+
+# Conclusion
 

### 2023-03-22 stats/analysis.Rmd
add already written notes/code

@@
 ```{r load_data}
-# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-#   # determine order of factors
-#   mutate(
-#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
-#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-#     sample = factor(sample, levels = c("kids", "adults")), 
-#     studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
-#     
-#     # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
-#     # the smaller the value, the more central the position
-#     symmetricPosition = ifelse(studyversion == "box", 
-#                                # for box version
-#                                case_when(
-#                                   targetPosition == "box3" ~ 0, 
-#                                   targetPosition == "box2" | targetPosition == "box4" ~ 1,
-#                                   targetPosition == "box1" | targetPosition == "box5" ~ 2), 
-#                                # for hedge version
-#                                targetCentralityX
-#                        ), 
-#     
-#     # distance between target and click in balloon widths (balloon width is 160 SVG units)
-#     clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
-#   )
+testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>%
+  mutate_if(is.character, as.factor) %>% 
+  # determine order of factors
+  mutate(
+    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")),
+    studyversion = factor(studyversion, levels = c("hedge", "box")),
+    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
+    sample = factor(sample, levels = c("kids", "teens", "adults")),
+    studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
+
+    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
+    # the smaller the value, the more central the position
+    symmetricPosition = case_when(
+                                  targetPosition == "5" | targetPosition == "6" | targetPosition == "box3" ~ 1,
+                                  targetPosition == "4" | targetPosition == "7" | targetPosition == "box2" | targetPosition == "box4" ~ 2,
+                                  targetPosition == "3" | targetPosition == "8" | targetPosition == "box1" | targetPosition == "box5" ~ 3,
+                                  targetPosition == "2" | targetPosition == "9" ~ 4,
+                                  targetPosition == "1" | targetPosition == "10" ~ 5,
+                       ),
+
+    # distance between target and click in balloon widths (balloon width is 160 SVG units)
+    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
+  )
 ```
+
+```{r check_sample}
+# child sample 
+testtrials %>% 
+  filter(agegroup < 18) %>% 
+  group_by(datacollection, studytype, studyversion, agegroup) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
+  ) %>% View()
+
+# reli
+testtrials %>% 
+  filter(agegroup < 6 & completedReli) %>% 
+  group_by(datacollection, studyversion, agegroup) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
+  summarise(
+    nTotal = n_distinct(subjID), 
+    meanAge = mean(age, na.rm = T) %>% round(2),
+    sdAge = sd(age, na.rm = T) %>% round(2),
+    minAge = min(age, na.rm = T),
+    maxAge = max(age, na.rm = T),
+    nFemales = ceiling(sum(female/15)),
+  )
+```
+
+# DEVELOPMENTAL TRAJECTORY
+
+```{r variation_preparateData}
+variationInd <- testtrials %>% 
+  mutate(
+    age_centered = scale(age, center = TRUE, scale = TRUE)[,1],
+  ) %>% 
+  group_by(studyversion, sample, datacollection, age, agegroup, age_centered, subjID) %>%
+  summarise(mean = mean(clickDistInBalloons, na.rm = TRUE))
+
+# variation <- variationInd %>%
+#   group_by(sample, datacollection, ageInYears) %>%
+#   tidyboot_mean(column = mean)
+```
+
+```{r dev_model}
+mDataAgeHedge <- testtrials %>% 
+  filter(studyversion == "hedge" & studytype == "vali") %>% 
+  mutate(
+    # scaled (centered around mean, SD = 1, i.e., z-transformed)
+    age = scale(age, center = TRUE, scale = TRUE)[,1], 
+  ) %>% 
+  select(subjID, age, agegroup, datacollection, symmetricPosition, targetPosition, clickDistInBalloons)
+
+mAgeHedge <- brm(clickDistInBalloons ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition),
+                    data = mDataAgeHedge,
+                    family = lognormal(),
+                    warmup = 500, 
+                    iter   = 1000, # todo: increase once done
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 100)
+
+write.csv(mAgeHedge, "../saves/mAgeHedge.csv", quote = F, row.names = F)
+saveRDS(mAgeHedge, "../saves/mAgeHedge.rds")
+```
+
+```{r dev_plot}
+ggplot(data = variationInd, aes(x = age, y = mean, shape = datacollection, color = studyversion)) +
+  geom_point(alpha = 0.5) +
+  scale_color_manual(values = c("#006c66", "darkgrey")) +
+  geom_smooth(data = variationInd, aes(x = age, y = mean, group = studyversion, color = studyversion), method = "lm", size = 1, se=F) +
+  facet_wrap(. ~ sample, scales = "free") +
+  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1))
+
+ggsave("../figures/tango_dev.png", width = 8, height = 4)
+
+ggplot(data = variationInd, aes(x = age, y = mean, shape = datacollection, color = studyversion)) +
+  geom_point(alpha = 0.5) +
+  scale_color_manual(values = c("#006c66", "darkgrey")) +
+  geom_smooth(data = variationInd, aes(x = age, y = mean, group = studyversion, color = studyversion), size = 1, se=F) +
+  # facet_wrap(. ~ sample, scales = "free") +
+  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 1))
+ggsave("../figures/tango_dev_wofacets.png", width = 8, height = 4)
+```
+
+# COGNITIVE MODEL
+
+```{r gazefunnel_hedge}
+imprecisionBinHedge <- testtrials %>% 
+  filter(agegroup < 6 & studyversion == "hedge") %>% 
+  group_by(datacollection, targetPosition) %>% 
+  tidyboot_mean(col = clickDistInBalloons, na.rm = TRUE)
+
+imprecisionBinHedgeInd <- testtrials %>% 
+  filter(agegroup < 6 & studyversion == "hedge") %>% 
+  group_by(datacollection, targetPosition, subjID) %>% 
+  tidyboot_mean(col = clickDistInBalloons, na.rm = TRUE)
+
+ggplot() +
+  labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Data collection mode") +
+  # geom_point(data = imprecisionBinHedgeInd, aes(x = targetPosition, y = mean, col = datacollection), alpha = .1, position = position_dodge(width = 0.2)) +
+  geom_pointrange(data = imprecisionBinHedge, aes(x = targetPosition, y = mean, ymin = ci_lower, ymax = ci_upper, col = datacollection), pch = 1,  size = 0.7, position = position_dodge(width = .2)) +
+  scale_color_colorblind()
+
+```

### 2023-06-05 paper/manuscript.Rmd
add lifespan data

@@
 ```{r setup, include = FALSE}
+library("tidyverse")
 library("papaja")
-library("ggplot2")
-library("ggpubr")
-library("tidyverse")
-library("brms")
 theme_set(theme_classic())
@@
 ```{r load_data}
-# TODO: only hedge version
-
-testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>%
-  mutate_if(is.character, as.factor) %>% 
-  # determine order of factors
-  mutate(
-    targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")),
-    datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-    sample = factor(sample, levels = c("kids", "teens", "adults")),
-    studytype = factor(studytype, levels = c("vali", "reli")),
-
-    # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
-    # the smaller the value, the more central the position
-    symmetricPosition = case_when(
-                                  targetPosition == "5" | targetPosition == "6" ~ 1,
-                                  targetPosition == "4" | targetPosition == "7" ~ 2,
-                                  targetPosition == "3" | targetPosition == "8" ~ 3,
-                                  targetPosition == "2" | targetPosition == "9" ~ 4,
-                                  targetPosition == "1" | targetPosition == "10" ~ 5,
-                       ),
-
-    # distance between target and click in balloon widths (balloon width is 160 SVG units)
-    clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
-  )
+tango_lifespan <- readRDS("../data/tango-lifespan.rds")
+tango_model <- readRDS("../data/tango-model.rds")
+magnet <- readRDS("../data/magnet-data.rds")
 ```
@@
 ```{r dev_sample}
-dev_kids <- testtrials %>%
-  filter(studytype == "vali" & age < 18) %>%
-  group_by(datacollection, agegroup) %>%
+lifespan_sample <- tango_lifespan %>% 
+  group_by(age_group) %>%
   mutate(female = ifelse(gender == "f", 1, 0)) %>% 
   summarise(
-    nTotal = n_distinct(subjID),
-    meanAge = mean(age, na.rm = T) %>% round(2),
-    sdAge = sd(age, na.rm = T) %>% round(2),
-    minAge = min(age, na.rm = T),
-    maxAge = max(age, na.rm = T),
-    nFemales = ceiling(sum(female/15)),
-  )
-
-dev_adults <- testtrials %>%
-  filter(studytype == "vali" & sample == "adults") %>%
-  ungroup() %>%
-  mutate(
-    gender = ifelse(is.na(gender), 0, paste(gender)),
-    female = ifelse(gender == "f", 1, 0),
-  ) %>%
-  summarise(
-    nTotal = n_distinct(subjID),
-    meanAge = mean(age, na.rm = T) %>% round(2),
-    sdAge = sd(age, na.rm = T) %>% round(2),
-    minAge = min(age, na.rm = T),
-    maxAge = max(age, na.rm = T),
-    nFemales = ceiling(sum(female/15)),
+    n_total = n_distinct(subj_id), 
+    age_mean = mean(age, na.rm = T) %>% round(2),
+    age_sd = sd(age, na.rm = T) %>% round(2),
+    age_min = min(age, na.rm = T),
+    age_max = max(age, na.rm = T),
+    n_females = ceiling(sum(female/15)),
   )
@@
 
-We collected data from an in-person child sample, a remote child an teenager sample, and a remote adult sample. In-person testing with children took place in kindergartens in Leipzig, Germany.
-
-The in-person child sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "4"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "in-person - supervised" & dev_kids$agegroup == "5"])` girls).
-
+We collected data from a remote child, teenager and adult sample.
 For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
 
-The remote child and teenager sample consisted of `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised"])` children, including `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` 3-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "3"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` 4-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "4"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` 5-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "5"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` 6-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "6"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` 7-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "7"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` 8-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "8"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` 9-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "9"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` 10-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "10"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` 11-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "11"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` 12-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "12"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` 13-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "13"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` 14-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "14"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` 15-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "15"])` girls), `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` 16-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "16"])` girls), and `r sum(dev_kids$nTotal[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` 17-year-olds (mean = `r sum(dev_kids$meanAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` years, SD = `r sum(dev_kids$sdAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, range = `r sum(dev_kids$minAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` - `r sum(dev_kids$maxAge[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])`, `r sum(dev_kids$nFemales[dev_kids$datacollection == "remote - unsupervised" & dev_kids$agegroup == "17"])` girls).
+The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).
 
@@
 
-Adults were recruited via *Prolific* [@palan2018prolific].
+<!-- Adults were recruited via *Prolific* [@palan2018prolific].
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of `r dev_adults$nTotal` English-speakers with an average age of `r dev_adults$meanAge` years (SD = `r dev_adults$sdAge`, range = `r dev_adults$minAge` - `r dev_adults$maxAge`, `r dev_adults$nFemales` females).
+Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females).
+-->
 

### 2023-06-05 stats/analysis.Rmd
add lifespan data

--- 2023-03-21 stats/analysis.Rmd
@@
 theme_set(theme_classic())
+
 # Seed for random number generation
@@
 ```{r load_data}
-# testtrials <- readRDS(file = "../data/tango-testtrials.rds") %>% 
-#   # determine order of factors
-#   mutate(
-#     targetPosition = factor(targetPosition, levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "box1", "box2", "box3", "box4", "box5")), 
-#     studyversion = factor(studyversion, levels = c("hedge", "box")), 
-#     datacollection = factor(datacollection, levels = c("in-person - supervised", "remote - unsupervised")),
-#     sample = factor(sample, levels = c("kids", "adults")), 
-#     studytype = factor(studytype, levels = c("vali", "vali2", "reli")),
-#     
-#     # for models, summarize targetPositions in a way that it's symmetrical for left/ right side
-#     # the smaller the value, the more central the position
-#     symmetricPosition = ifelse(studyversion == "box", 
-#                                # for box version
-#                                case_when(
-#                                   targetPosition == "box3" ~ 0, 
-#                                   targetPosition == "box2" | targetPosition == "box4" ~ 1,
-#                                   targetPosition == "box1" | targetPosition == "box5" ~ 2), 
-#                                # for hedge version
-#                                targetCentralityX
-#                        ), 
-#     
-#     # distance between target and click in balloon widths (balloon width is 160 SVG units)
-#     clickDistInBalloons = abs(clickDistFromTargetCenterX)/160,
-#   )
+tango_lifespan <- readRDS("../data/tango-lifespan.rds")
+tango_model <- readRDS("../data/tango-model.rds")
+magnet <- readRDS("../data/magnet-data.rds")
 ```
+
+# DEVELOPMENTAL TRAJECTORY
+```{r lifespan_sample}
+lifespan_sample <- tango_lifespan %>% 
+  group_by(age_group) %>%
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
+  summarise(
+    n_total = n_distinct(subj_id), 
+    age_mean = mean(age, na.rm = T) %>% round(2),
+    age_sd = sd(age, na.rm = T) %>% round(2),
+    age_min = min(age, na.rm = T),
+    age_max = max(age, na.rm = T),
+    n_females = ceiling(sum(female/15)),
+  )
+```
+
+```{r variation_preparateData}
+lifespan_variation <- tango_lifespan %>% 
+  group_by(subj_id, age, age_group) %>%
+  summarise(mean = mean(click_dist_balloons, na.rm = TRUE))
+```
+
+```{r lifespan_plot}
+ggplot(data = lifespan_variation, aes(x = age, y = mean)) +
+  geom_point(color = "darkgrey", alpha = 0.5) +
+  geom_smooth(method = "loess", size = 1, se = F, color = "#006c66") + 
+  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
+  labs(x = "Age in years", y = "Average imprecision in target widths")
+
+ggsave("../figures/tango_lifespan.png", width = 8, height = 4, scale = 1.2)
+```
+
+```{r lifespan_model}
+mDataLifespan <- tango_lifespan %>% 
+  mutate(
+    symmetric_position = scale(symmetric_position),
+    trial_nr = trial_nr - min(trial_nr), 
+    click_dist = abs(click_dist_from_target_center_x),
+  ) %>% 
+  select(subj_id, age, age_centered, symmetric_position, trial_nr, click_dist, click_dist_balloons)
+
+mLifespanNull <- brm(click_dist_balloons ~ age_centered + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4)
+
+write.csv(mAgeHedge, "../saves/mLifespan.csv", quote = F, row.names = F)
+saveRDS(mAgeHedge, "../saves/mLifespan.rds")
+```
+
+# COGNITIVE MODEL
+
+```{r gazefunnel}
+target_position_impr <- tango_model %>% 
+  group_by(age_group, target_position) %>% 
+  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)
+
+target_position_impr_ind <- tango_model %>% 
+  group_by(subj_id, age_group, target_position) %>% 
+  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)
+
+ggplot() +
+  geom_point(data = target_position_impr_ind, aes(x = target_position, y = mean, col = as.factor(age_group)), alpha = .1, position = position_dodge(width = 0.3)) +
+
+  geom_pointrange(data = target_position_impr, aes(x = target_position, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(age_group)), pch = 18,  size = 1, position = position_dodge(width = .3)) +
+
+  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) + 
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+    labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")
+
+ggsave("../figures/tango_gazefunnel.png", width = 6, height = 4, scale = 1.2)
+```

### 2023-06-05 stats/magnet.Rmd
add lifespan data

---
title: "Stats"
author: "Julia Prein"
date: "03/21/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(corrr)
library(psych)
library(apaTables)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
magnet <- readRDS("../data/magnet-data.rds")
```

```{r scatterplots}
magnet %>% 
  ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
  geom_point(color = "#005555") +
  stat_cor(method = "pearson", label.x = 5, label.y = 6, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.5)) +
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.5)) +
  labs(x = "Magnet mean", y = "Tango mean")

magnet %>% 
  ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
  geom_abline(intercept = 0, slope = 1, col = "darkgrey", linetype = "longdash") +
  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
  geom_point(color = "#005555") +
  stat_cor(method = "pearson", label.x = 3.5, label.y = 3.25, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
  scale_x_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  scale_y_continuous(limits = c(0, 3.75), breaks = seq(0, 4, 0.5)) +
  labs(x = "Magnet mean", y = "Tango mean")
```

```{r corrplot}
magnet %>% 
  select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% 
  rename("Tango mean" = tango_mean, "Magnet mean" = magnet_mean, "ToM aggregate score" = tom_aggregate, "Perspective-taking score" = perspective_aggregate) %>% 
  cor() %>% 
  corrplot(diag = FALSE, type = 'upper', method = 'ellipse', order = 'FPC', col = COL2('BrBG'), tl.col = 'black', cl.ratio = 0.2, tl.srt = 30, addCoef.col ='black', number.cex = 0.8)
```

```{r cor_matrix}
tango_magnet <- magnet %>% select(tango_mean, magnet_mean) %>% corr.test(method = "pearson")
tango_tom <- magnet %>% select(tango_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")
magnet_tom <- magnet %>% select(magnet_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")

cor_matrix <- rbind(tango_magnet$ci, tango_tom$ci, magnet_tom$ci) %>% 
  mutate(Correlation = rownames(.)) %>%
  as.tibble()

cor_matrix <- cor_matrix %>%
  # remove tom - perspective correlations
  filter(Correlation != "tm_gg-prsp_1") %>%
  mutate(
    Correlation = recode(Correlation,
                  `tng_m-mgnt_` = "Tango x Magnet", 
                  `tng_m-tm_gg` = "Tango x ToM",
                  `tng_m-prsp_` = "Tango x Perspective-taking",
                  `mgnt_-tm_gg` = "Magnet x ToM",
                  `mgnt_-prsp_` = "Magnet x Perspective-taking", 
                  `tm_gg-prsp_` = "ToM x Perspective-taking")
  ) %>% 
  mutate(across(where(is.numeric), round, 2)) %>% 
  select(Correlation, r, lower, upper, p)

# apa table function only supports pearson corr so far
magnet %>% select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% apa.cor.table(filename = "APA_Correlation_Table.doc", table.number=1)
```

```{r plot_cor_ci}
cor_matrix %>% 
  filter(Correlation != "ToM x Perspective-taking") %>% 
  mutate(Correlation = fct_relevel(Correlation, "Magnet x Perspective-taking", "Magnet x ToM", "Tango x Perspective-taking", "Tango x ToM", "Tango x Magnet")) %>%
  ggplot(., aes(x=Correlation, y=r, ymin=lower, ymax=upper)) +
  geom_pointrange(color = "#005555", size = 0.8, linewidth = 1) +
  scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("") +
  coord_flip() +
  theme(axis.title.x = element_text(face="italic"))

ggsave("../figures/magnet_cor_ci.png", width = 5, height = 3)
```
```

### 2023-06-05 stats/analysis.Rmd
adjust lifespan plot

@@
   geom_point(color = "darkgrey", alpha = 0.5) +
-  geom_smooth(method = "loess", size = 1, se = F, color = "#006c66") + 
+  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
   scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 

### 2023-06-06 stats/analysis.Rmd
save model output from stats server

--- 2023-06-05 stats/analysis.Rmd
@@
 library(tidybayes) # for stat_halfeye
+library(cmdstanr)
+check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
 
@@
   )
-```
 
-```{r variation_preparateData}
-lifespan_variation <- tango_lifespan %>% 
-  group_by(subj_id, age, age_group) %>%
-  summarise(mean = mean(click_dist_balloons, na.rm = TRUE))
+mDataLifespan <- tango_lifespan %>% 
+  group_by(subj_id, age, age_centered) %>% 
+  summarize(mean_dist = mean(click_dist_balloons, na.rm = TRUE))
 ```
@@
 ```{r lifespan_plot}
-ggplot(data = lifespan_variation, aes(x = age, y = mean)) +
+tango_lifespan %>% 
+  group_by(subj_id, age, age_group) %>%
+  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
+  ggplot(., aes(x = age, y = mean)) +
   geom_point(color = "darkgrey", alpha = 0.5) +
-  geom_smooth(method = "loess", size = 1, se = F, color = "#006c66") + 
+  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
   scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
@@
 
-ggsave("../figures/tango_lifespan.png", width = 8, height = 4, scale = 1.2)
+# ggsave("../figures/tango_lifespan.png", width = 8, height = 4, scale = 1.2)
 ```
@@
 ```{r lifespan_model}
-mDataLifespan <- tango_lifespan %>% 
-  mutate(
-    symmetric_position = scale(symmetric_position),
-    trial_nr = trial_nr - min(trial_nr), 
-    click_dist = abs(click_dist_from_target_center_x),
-  ) %>% 
-  select(subj_id, age, age_centered, symmetric_position, trial_nr, click_dist, click_dist_balloons)
-
-mLifespanNull <- brm(click_dist_balloons ~ age_centered + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
+# model as in tango paper
+# except we use click_dist in pixel, lognormal needs > 0
+mLifespanLinear <- brm(mean_dist ~ age_centered,
                     data = mDataLifespan,
                     family = lognormal(),
-                    warmup = 1000, 
-                    iter   = 3000, 
+                    warmup = 2000, 
+                    iter   = 6000, 
                     chains = 4, 
-                    inits  = "random",
-                    cores  = 4)
+                    cores  = 4, 
+                    threads = threading(8), 
+                    control = list(adapt_delta = 0.95), 
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
 
-write.csv(mAgeHedge, "../saves/mLifespan.csv", quote = F, row.names = F)
-saveRDS(mAgeHedge, "../saves/mLifespan.rds")
+mLifespanLinear
+
+pp_check(mLifespanLinear)
+
+write.csv(mLifespanLinear, "../saves/mLifespanLinear.csv", quote = F, row.names = F)
+saveRDS(mLifespanLinear, "../saves/mLifespanLinear.rds")
+
+## squared age
+mLifespanQuadratic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000, 
+                    iter   = 6000, 
+                    chains = 4, 
+                    cores  = 4, 
+                    threads = threading(8), 
+                    control = list(adapt_delta = 0.95), 
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+mLifespanQuadratic
+
+pp_check(mLifespanQuadratic)
+
+conditional_effects(mLifespanQuadratic, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanQuadratic, "../saves/mLifespanQuadratic.csv", quote = F, row.names = F)
+saveRDS(mLifespanQuadratic, "../saves/mLifespanQuadratic.rds")
+
+## cubic age
+mLifespanCubic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2) + I(age_centered^3),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000, 
+                    iter   = 6000, 
+                    chains = 4, 
+                    cores  = 4, 
+                    threads = threading(8), 
+                    control = list(adapt_delta = 0.95), 
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+mLifespanCubic
+
+pp_check(mLifespanCubic)
+
+plot(mLifespanCubic)
+
+conditional_effects(mLifespanCubic, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanCubic, "../saves/mLifespanCubic.csv", quote = F, row.names = F)
+saveRDS(mLifespanCubic, "../saves/mLifespanCubic.rds")
+
+## gaussian process model
+mLifespanGP <- brm(mean_dist ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000, 
+                    iter   = 6000, 
+                    chains = 4, 
+                    cores  = 4, 
+                    threads = threading(8), 
+                    control = list(adapt_delta = 0.95), 
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+mLifespanGP
+
+pp_check(mLifespanGP)
+
+conditional_effects(mLifespanGP, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanGP, "../saves/mLifespanGP.csv", quote = F, row.names = F)
+saveRDS(mLifespanGP, "../saves/mLifespanGP.rds")
+
+## spline model
+# https://discourse.mc-stan.org/t/smooth-spline-modeling-with-brm/6364/2
+mLifespanS <- brm(mean_dist ~ s(age_centered),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000,
+                    iter   = 6000,
+                    chains = 4,
+                    cores  = 4,
+                    threads = threading(8),
+                    control = list(adapt_delta = 0.95),
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+mLifespanS
+
+pp_check(mLifespanS)
+
+conditional_effects(mLifespanS, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+conditional_smooths(mLifespanS2, effects = "weight")
+
+write.csv(mLifespanS, "../saves/mLifespanS.csv", quote = F, row.names = F)
+saveRDS(mLifespanS, "../saves/mLifespanS.rds")
+
+## playing around with parameters
+mLifespanS2 <- brm(mean_dist ~ s(age_centered, k = 2),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000,
+                    iter   = 6000,
+                    chains = 4,
+                    cores  = 4,
+                    threads = threading(8),
+                    control = list(adapt_delta = 0.95),
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+conditional_effects(mLifespanS2, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanS2, "../saves/mLifespanS2.csv", quote = F, row.names = F)
+saveRDS(mLifespanS2, "../saves/mLifespanS2.rds")
+
+# 3
+mLifespanS3 <- brm(mean_dist ~ s(age_centered, k = 3),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000,
+                    iter   = 6000,
+                    chains = 4,
+                    cores  = 4,
+                    threads = threading(8),
+                    control = list(adapt_delta = 0.95),
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+conditional_effects(mLifespanS3, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanS3, "../saves/mLifespanS3.csv", quote = F, row.names = F)
+saveRDS(mLifespanS3, "../saves/mLifespanS3.rds")
+
+# 4
+mLifespanS4 <- brm(mean_dist ~ s(age_centered, k = 4),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000,
+                    iter   = 6000,
+                    chains = 4,
+                    cores  = 4,
+                    threads = threading(8),
+                    control = list(adapt_delta = 0.95),
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+conditional_effects(mLifespanS4, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanS4, "../saves/mLifespanS4.csv", quote = F, row.names = F)
+saveRDS(mLifespanS4, "../saves/mLifespanS4.rds")
+
+# 5
+mLifespanS5 <- brm(mean_dist ~ s(age_centered, k = 5),
+                    data = mDataLifespan,
+                    family = lognormal(),
+                    warmup = 2000,
+                    iter   = 6000,
+                    chains = 4,
+                    cores  = 4,
+                    threads = threading(8),
+                    control = list(adapt_delta = 0.95),
+                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+
+conditional_effects(mLifespanS5, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+write.csv(mLifespanS5, "../saves/mLifespanS5.csv", quote = F, row.names = F)
+saveRDS(mLifespanS5, "../saves/mLifespanS5.rds")
+```
+
+```{r prediction_plot}
+# https://ourcodingclub.github.io/tutorials/brms/#plot
+library(tidybayes)
+
+mDataLifespan %>%
+  add_predicted_draws(mLifespanQuadratic) %>%  # adding the posterior distribution
+  ggplot(aes(x = age_centered, y = mean_dist)) +  
+  geom_jitter(data = mDataLifespan, colour = "grey", size = 1.5, alpha = 0.8) + 
+  stat_lineribbon(aes(y = .prediction), .width = c(.95, .80), alpha = 0.5, colour = "black") +
+  scale_fill_brewer(palette = "Greys") + 
+  scale_y_continuous(limits = c(0,4))
+```
+
+```{r lifespan_modelcomparison}
+# mLifespanLinear <- readRDS("../saves/mLifespanLinear.rds")
+# mLifespanQuadratic <- readRDS("../saves/mLifespanQuadratic.rds")
+# mLifespanCubic <- readRDS("../saves/mLifespanCubic.rds")
+# mLifespanGP <- readRDS("../saves/mLifespanGP.rds")
+# mLifespanS <- readRDS("../saves/mLifespanS.rds")
+
+mLifespanComparison <- loo_compare(mLifespanLinear, mLifespanQuadratic, mLifespanCubic, mLifespanGP, mLifespanS, mLifespanS2, mLifespanS3, mLifespanS4, mLifespanS5, criterion = "waic") %>% 
+  as_tibble(rownames = "model") %>%
+  left_join(as_tibble(model_weights(mLifespanLinear, mLifespanQuadratic, mLifespanCubic, mLifespanGP, mLifespanS, mLifespanS2, mLifespanS3, mLifespanS4, mLifespanS5, weights = "waic"), rownames = "model")) %>%
+  rename(modelweight = value)
+
+mLifespanComparison %>% 
+  select(-c(se_elpd_waic, p_waic, se_p_waic)) %>% 
+  mutate(across(where(is.numeric), round, 4))
+
+write.csv(mLifespanComparison, "../saves/mLifespanComparison.csv", quote = F, row.names = F)
+saveRDS(mLifespanComparison, "../saves/mLifespanComparison.rds")
+```
+
+```{r lifespan_posteriordraws}
+# lifespan_draws <- bind_rows(
+#   mLifespanNull %>% gather_draws(b_age_centered, b_trial_nr, b_symmetric_position) %>% mutate(model = "null model"), 
+#   # mOrevFull %>% gather_draws(b_age_centered, b_mean_tango_centered) %>% mutate(model = "full model"), 
+#   ) %>% 
+#   mutate(
+#     .variable = factor(.variable, levels = c("b_age_centered", "b_trial_nr", "b_symmetric_position"), labels = c("Age (scaled)", "Trial Nr", "Symmetric Position")), 
+#   ) %>% 
+#   rename(estimate = .value, predictor = .variable)
+```
+
+```{r lifespan_modelplot}
+# lifespan_modelplot <- lifespan_draws %>% 
+#   ggplot(., aes(x = estimate, y = predictor)) +
+#   tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_fill = "#006c66", slab_alpha = 0.4) +
+#     labs(x = "Posterior estimate when predicting oREV score", y = "") +
+#   guides(fill = "none")+
+#   geom_vline(xintercept = 0, linetype = "dashed") +
+#   coord_cartesian(expand = TRUE, xlim = c(-0.1, 0.6), ylim = c(1.5, 2.5)) +
+#   theme_classic()
+# 
+# lifespan_modelplot
+# 
+# saveRDS(lifespan_modelplot, file = "../saves/lifespan_modelplot.rds")
+# ggsave("../figures/lifespan_modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```
@@
 ```{r gazefunnel}
-target_position_impr <- tango_model %>% 
-  group_by(age_group, target_position) %>% 
-  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)
-
-target_position_impr_ind <- tango_model %>% 
-  group_by(subj_id, age_group, target_position) %>% 
-  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)
-
-ggplot() +
-  geom_point(data = target_position_impr_ind, aes(x = target_position, y = mean, col = as.factor(age_group)), alpha = .1, position = position_dodge(width = 0.3)) +
-
-  geom_pointrange(data = target_position_impr, aes(x = target_position, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(age_group)), pch = 18,  size = 1, position = position_dodge(width = .3)) +
-
-  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) + 
-  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
-    labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")
-
-ggsave("../figures/tango_gazefunnel.png", width = 6, height = 4, scale = 1.2)
+# target_position_impr <- tango_model %>% 
+#   group_by(age_group, target_position) %>% 
+#   tidyboot_mean(column = click_dist_balloons, na.rm = TRUE) 
+# 
+# target_position_impr_ind <- tango_model %>% 
+#   group_by(subj_id, age_group, target_position) %>% 
+#   tidyboot_mean(column = click_dist_balloons, na.rm = TRUE) 
+# 
+# ggplot() +
+#   geom_point(data = target_position_impr_ind, aes(x = target_position, y = mean, col = as.factor(age_group)), alpha = .1, position = position_dodge(width = 0.3)) +
+#   
+#   geom_pointrange(data = target_position_impr, aes(x = target_position, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(age_group)), pch = 18,  size = 1, position = position_dodge(width = .3)) +
+#   
+#   scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) + 
+#   scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+#     labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")
+# 
+# ggsave("../figures/tango_gazefunnel.png", width = 6, height = 4, scale = 1.2)
 ```

### 2023-06-07 paper/manuscript.Rmd
clean up analysis files

@@
 # Introduction
+
 -   why do we care about developmental trajectory? ref to stat learning paper
@@
 -   [@raviv2018developmental]
+
 -   [@astor2022gaze]
+
 -   [@colombo2001development]
+
 -   [@scaife1975capacity]
+
 -   [@itakura1998use]
@@
 -   [@silverstein2021infants] for vertical plane
+
 -   [@zhang2019role]
+
 -   [@frischen2007gaze]
+
 -   [@lee1998children]
+
 -   [@coelho2006searching]
@@
 # Lifespan
+
 -   development & individual differences in gaze understanding
 -   verweis methods paper reliable differences kinder & adults.
-- kontinuerliche, systematische variation, wodrin? => model
+-   kontinuerliche, systematische variation, wodrin? =\> model
+
+<https://osf.io/6yjz3>
 
@@
 ```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/tango_procedure.png")
+knitr::include_graphics("../figures/magnet_procedure.png")
 ```
@@
 # Computational cognitive model
+
 -   model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
 -   entwicklungsperspektive basierend auf model
-- dann prozess-ebene => magnet
+-   dann prozess-ebene =\> magnet
 
 # Non-social vector following
+
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.
+
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.
+2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+Data were collected between February and March 2023.
+
+-   gut, dass unser maß ind diff messen kann, das nutzen wir jetzt
+
+-   zsmhang mit vector following, aber nicht redundant
+
+-   perspective-taking auch, aber auch nicht relevant, nicht theory of mind score
+
+-   diskutieren dass die maße auch nict ind diff maße sind
+
+-   model vergleich: welche komponente stecken in gafo drin?,
+    welchen beitrag liefern die um score zu erklären?
+    welche wichtiger, tom oder nur perspective taking
+
+-   magnet versuch das vector following zu isolieren.
+    ist da noch was anderes außerhalb vector-following?
+
+-   aggregierte messungen immer besser, nur indikatoren für konstrukt
 
@@
 
-The authors made the following contributions:
-### TODO
+The authors made the following contributions: \### TODO
 

### 2023-06-07 stats/gazemodel.Rmd
clean up analysis files

---
title: "Gaze model analysis"
author: "Julia Prein"
date: "06/07/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidyboot) # for bootstrap CIs

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
gaze_data <- readRDS("../data/tango-model.rds")
```

```{r sample}
gazemodel_sample <- gaze_data %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )

gazemodel_sample

write.csv(gazemodel_sample, "../saves/gazemodel_sample.csv", quote = F, row.names = F)
saveRDS(gazemodel_sample, "../saves/gazemodel_sample.rds")
```

```{r plot}
dev_plot <- gaze_data %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "lm", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(3, 5), breaks = seq(3, 5, 0.5)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Age in years", y = "Average imprecision in target widths")

dev_plot

# ggsave("../figures/dev_plot.png", width = 8, height = 4, scale = 1.2)
```

```{r gazefunnel}
target_position_imprecision <- gaze_data %>%
  group_by(age_group, target_position) %>%
  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)

target_position_imprecision_ind <- gaze_data %>%
  group_by(subj_id, age_group, target_position) %>%
  summarize(mean = mean(click_dist_balloons, na.rm = TRUE))

gazefunnel <- ggplot() +
  geom_point(data = target_position_imprecision_ind, aes(x = target_position, y = mean, col = as.factor(age_group)), alpha = .1, position = position_dodge(width = 0.3)) +

  geom_pointrange(data = target_position_imprecision, aes(x = target_position, y = mean, ymin = ci_lower, ymax = ci_upper, col = as.factor(age_group)), pch = 18,  size = 1, position = position_dodge(width = .3)) +

  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
    labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")

gazefunnel

# ggsave("../figures/gazefunnel.png", width = 6, height = 4, scale = 1.2)
# saveRDS(gazefunnel, "../saves/gazefunnel.rds")
```

### 2023-06-07 stats/lifespan.Rmd
clean up analysis files

---
title: "Lifespan analysis"
author: "Julia Prein"
date: "03/21/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(brms) # modeling
library(cmdstanr) # modeling
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
lifespan_data <- readRDS("../data/tango-lifespan.rds")
```

```{r prepare_modeldata}
mdata <- lifespan_data %>% 
  group_by(subj_id, age, age_centered) %>% 
  summarize(mean_dist = mean(click_dist_balloons, na.rm = TRUE))
```

```{r sample}
lifespan_sample <- lifespan_data %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )

lifespan_sample

write.csv(lifespan_sample, "../saves/lifespan_sample.csv", quote = F, row.names = F)
saveRDS(lifespan_sample, "../saves/lifespan_sample.rds")
```

```{r plot}
lifespan <- lifespan_data %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan, "../saves/lifespan.rds")
```

```{r models, message=FALSE, warning=FALSE}
# linear age
mlinear <- brm(mean_dist ~ age_centered,
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

mlinear

pp_check(mlinear)

write.csv(mlinear, "../saves/mlinear.csv", quote = F, row.names = F)
saveRDS(mlinear, "../saves/mlinear.rds")

## quadratic age
mquadratic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

mquadratic

pp_check(mquadratic)

conditional_effects(mquadratic, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(mquadratic, "../saves/mquadratic.csv", quote = F, row.names = F)
saveRDS(mquadratic, "../saves/mquadratic.rds")

## cubic age
mcubic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2) + I(age_centered^3),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

mcubic

pp_check(mcubic)

plot(mcubic)

conditional_effects(mcubic, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(mcubic, "../saves/mcubic.csv", quote = F, row.names = F)
saveRDS(mcubic, "../saves/mcubic.rds")

## gaussian process model
mgaussianprocess <- brm(mean_dist ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

mgaussianprocess

pp_check(mgaussianprocess)

conditional_effects(mgaussianprocess, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(mgaussianprocess, "../saves/mgaussianprocess.csv", quote = F, row.names = F)
saveRDS(mgaussianprocess, "../saves/mgaussianprocess.rds")

## spline model
# https://discourse.mc-stan.org/t/smooth-spline-modeling-with-brm/6364/2
msplines <- brm(mean_dist ~ s(age_centered),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000,
                    iter   = 6000,
                    chains = 4,
                    cores  = 4,
                    threads = threading(8),
                    control = list(adapt_delta = 0.95),
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

msplines

pp_check(msplines)

conditional_effects(msplines, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

conditional_smooths(msplines2, effects = "weight")

write.csv(msplines, "../saves/msplines.csv", quote = F, row.names = F)
saveRDS(msplines, "../saves/msplines.rds")

## playing around with parameters
msplines2 <- brm(mean_dist ~ s(age_centered, k = 2),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000,
                    iter   = 6000,
                    chains = 4,
                    cores  = 4,
                    threads = threading(8),
                    control = list(adapt_delta = 0.95),
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

conditional_effects(msplines2, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(msplines2, "../saves/msplines2.csv", quote = F, row.names = F)
saveRDS(msplines2, "../saves/msplines2.rds")

# 3
msplines3 <- brm(mean_dist ~ s(age_centered, k = 3),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000,
                    iter   = 6000,
                    chains = 4,
                    cores  = 4,
                    threads = threading(8),
                    control = list(adapt_delta = 0.95),
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

conditional_effects(msplines3, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(msplines3, "../saves/msplines3.csv", quote = F, row.names = F)
saveRDS(msplines3, "../saves/msplines3.rds")

# 4
msplines4 <- brm(mean_dist ~ s(age_centered, k = 4),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000,
                    iter   = 6000,
                    chains = 4,
                    cores  = 4,
                    threads = threading(8),
                    control = list(adapt_delta = 0.95),
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

conditional_effects(msplines4, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(msplines4, "../saves/msplines4.csv", quote = F, row.names = F)
saveRDS(msplines4, "../saves/msplines4.rds")

# 5
msplines5 <- brm(mean_dist ~ s(age_centered, k = 5),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000,
                    iter   = 6000,
                    chains = 4,
                    cores  = 4,
                    threads = threading(8),
                    control = list(adapt_delta = 0.95),
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

conditional_effects(msplines5, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

write.csv(msplines5, "../saves/msplines5.csv", quote = F, row.names = F)
saveRDS(msplines5, "../saves/msplines5.rds")
```

```{r lifespan_modelcomparison}
# mlinear <- readRDS("../saves/mlinear.rds")
# mquadratic <- readRDS("../saves/mquadratic.rds")
# mcubic <- readRDS("../saves/mcubic.rds")
# mgaussianprocess <- readRDS("../saves/mgaussianprocess.rds")
# msplines <- readRDS("../saves/msplines.rds")

mcomparison <- loo_compare(mlinear, mquadratic, mcubic, mgaussianprocess, msplines, msplines2, msplines3, msplines4, msplines5, criterion = "waic") %>% 
  as_tibble(rownames = "model") %>%
  left_join(as_tibble(model_weights(mlinear, mquadratic, mcubic, mgaussianprocess, msplines, msplines2, msplines3, msplines4, msplines5, weights = "waic"), rownames = "model")) %>% 
  rename(modelweight = value)

mcomparison %>% 
  select(-c(se_elpd_waic, p_waic, se_p_waic)) %>% 
  mutate(across(where(is.numeric), round, 4))

write.csv(mcomparison, "../saves/mcomparison.csv", quote = F, row.names = F)
saveRDS(mcomparison, "../saves/mcomparison.rds")
```

```{r prediction_plot_winning_model}
prediction_plot <- mdata %>%
  add_predicted_draws(msplines) %>%  # adding the posterior distribution
  ggplot(aes(x = age_centered, y = mean_dist)) +  
  geom_jitter(data = mdata, colour = "grey", size = 1.5, alpha = 0.8) + 
  stat_lineribbon(aes(y = .prediction), .width = c(.95, .80), alpha = 0.5, colour = "black") +
  scale_fill_brewer(palette = "Greys") + 
  scale_y_continuous(limits = c(0,4))

prediction_plot

# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
# ggsave("../figures/lifespan_modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

### 2023-06-07 stats/magnet.Rmd
clean up analysis files

@@
 ---
-title: "Stats"
+title: "Magnet analysis"
 author: "Julia Prein"
-date: "03/21/2023"
+date: "06/07/2023"
 output: pdf_document
@@
 library(tidyverse) # data handling etc.
-library(corrr)
-library(psych)
-library(apaTables)
+library(psych) # corr.test
+library(brms) # modeling
+library(tidybayes) # modeling
+library(ggpubr) # stat_cor 
+library(corrplot) # corr plot
+library(apaTables) # as name says
 
@@
 ```{r load_data}
-magnet <- readRDS("../data/magnet-data.rds")
+magnet_data <- readRDS("../data/magnet-data.rds")
+```
+
+```{r sample}
+magnet_sample <- magnet_data %>% 
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
+  summarise(
+    n_total = n_distinct(subj_id), 
+    age_mean = mean(age, na.rm = T) %>% round(2),
+    age_sd = sd(age, na.rm = T) %>% round(2),
+    age_min = min(age, na.rm = T),
+    age_max = max(age, na.rm = T),
+    n_females = sum(female, na.rm = T),
+  )
+
+magnet_sample
+
+write.csv(magnet_sample, "../saves/magnet_sample.csv", quote = F, row.names = F)
+saveRDS(magnet_sample, "../saves/magnet_sample.rds")
 ```
@@
 ```{r scatterplots}
-magnet %>% 
+# doesnt make a difference whether we exclude outlier / "imprecise" kids
+magnet_data %>% 
   ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
@@
 
-magnet %>% 
+magnet_data %>% 
   ggplot(., aes(x = magnet_mean, y = tango_mean)) + 
@@
 ```{r corrplot}
-magnet %>% 
+magnet_data %>% 
   select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% 
-  rename("Tango mean" = tango_mean, "Magnet mean" = magnet_mean, "ToM aggregate score" = tom_aggregate, "Perspective-taking score" = perspective_aggregate) %>% 
+  rename("Tango mean" = tango_mean, "Magnet mean" = magnet_mean, "ToM score" = tom_aggregate, "Perspective-taking score" = perspective_aggregate) %>% 
   cor() %>% 
-  corrplot(diag = FALSE, type = 'upper', method = 'ellipse', order = 'FPC', col = COL2('BrBG'), tl.col = 'black', cl.ratio = 0.2, tl.srt = 30, addCoef.col ='black', number.cex = 0.8)
+  corrplot(diag = FALSE, type = 'lower', method = 'color', order = 'FPC', col = COL2('BrBG'), tl.col = 'black', cl.ratio = 0.2, tl.srt = 0, addCoef.col ='black', number.cex = 0.8)
 ```
@@
 ```{r cor_matrix}
-tango_magnet <- magnet %>% select(tango_mean, magnet_mean) %>% corr.test(method = "pearson")
-tango_tom <- magnet %>% select(tango_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")
-magnet_tom <- magnet %>% select(magnet_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")
+tango_magnet <- magnet_data %>% select(tango_mean, magnet_mean) %>% corr.test(method = "pearson")
+tango_tom <- magnet_data %>% select(tango_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")
+magnet_tom <- magnet_data %>% select(magnet_mean, tom_aggregate, perspective_aggregate) %>% corr.test(method = "spearman")
 
@@
 # apa table function only supports pearson corr so far
-magnet %>% select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% apa.cor.table(filename = "APA_Correlation_Table.doc", table.number=1)
+magnet_data %>% select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% apa.cor.table(filename = "../saves/magnet_corrtable.doc", table.number=1)
 ```
@@
 ```{r plot_cor_ci}
-cor_matrix %>% 
+cor_ci <- cor_matrix %>% 
   filter(Correlation != "ToM x Perspective-taking") %>% 
@@
 
-ggsave("../figures/magnet_cor_ci.png", width = 5, height = 3)
+cor_ci
+
+saveRDS(cor_ci, file = "../saves/magnet_cor_ci.rds")
+# ggsave("../figures/magnet_cor_ci.png", width = 5, height = 3)
 ```
+
+```{r check_tango_distribution}
+ggplot(magnet_data, aes(x = tango_mean)) + 
+  geom_density() + 
+  stat_function(fun = dnorm, 
+                args = with(magnet_data, c(mean = mean(tango_mean), sd = sd(tango_mean))), 
+                color = "red", linetype = "dotted") +
+
+  stat_function(fun = dlnorm, 
+                args = with(magnet_data, c(meanlog = mean(log(tango_mean)), sdlog = sd(log(tango_mean)))),
+                color = "blue", linetype = "dotted")
 ```
+
+```{r prepare_modeldata}
+mdata <- magnet_data %>% 
+  mutate(
+    magnet_scaled = scale(magnet_mean), 
+    tom_scaled = scale(tom_aggregate), 
+    perspective_scaled = scale(perspective_aggregate)
+  ) %>% 
+  select(subj_id, tango_mean, age_centered, magnet_scaled, tom_scaled, perspective_scaled)
+```
+
+```{r models, message=FALSE, warning=FALSE}
+mage <- brm(tango_mean ~ age_centered,
+                    data = mdata,
+                    family = lognormal(),
+                    warmup = 1000, 
+                    iter   = 3000, 
+                    chains = 4, 
+                    inits  = "random",
+                    cores  = 4) %>%
+  add_criterion(c("loo","waic"))
+
+mmagnet <- update(mage, formula. = ~ . + magnet_scaled, newdata = mdata) %>% 
+  add_criterion(c("loo","waic"))
+
+mtom <- update(mage, formula. = ~ . + tom_scaled, newdata = mdata) %>% 
+  add_criterion(c("loo","waic"))
+
+mperspective <- update(mage, formula. = ~ . + perspective_scaled, newdata = mdata) %>% 
+  add_criterion(c("loo","waic"))
+
+mmagnet_tom <- update(mage, formula. = ~ . + magnet_scaled + tom_scaled, newdata = mdata) %>% 
+  add_criterion(c("loo","waic"))
+
+mmagnet_perspective <- update(mage, formula. = ~ . + magnet_scaled + perspective_scaled, newdata = mdata) %>%
+  add_criterion(c("loo","waic"))
+```
+
+```{r modelcomparison}
+mcomparison <- loo_compare(mage, mmagnet, mtom, mperspective, mmagnet_tom, mmagnet_perspective, criterion = "waic") %>% as_tibble(rownames = "model") %>%
+  left_join(as_tibble(model_weights(mage, mmagnet, mtom, mperspective, mmagnet_tom, mmagnet_perspective, weights = "waic"), rownames = "model")) %>% 
+  rename(modelweight = value)
+
+mcomparison
+
+model_results <- mcomparison %>%
+  select(model, waic, se_waic, modelweight, elpd_diff, se_diff) %>%
+  rename(
+    Model = model, 
+    WAIC = waic, 
+    SE_WAIC = se_waic,
+    Weight = modelweight, 
+    ELPD_DIFF = elpd_diff, 
+    SE_ELPD_DIFF = se_diff,
+  ) %>% 
+  mutate(
+    Model = recode(Model, 
+                   "mage" = "Null model with Age (scaled)", 
+                   "mmagnet" = "Magnet mean (scaled)", 
+                   "mtom" = "ToM aggregate (scaled)", 
+                   "mperspective" = "Perspective-taking aggregate (scaled)", 
+                   "mmagnet_tom" = "Magnet mean (scaled) + ToM aggregate (scaled)", 
+                   "mmagnet_perspective" = "Magnet mean (scaled) + Perspective-taking aggregate (scaled)", 
+                   )
+  )
+
+write.csv(model_results, "../saves/magnet_modelresults.csv", quote = F, row.names = F)
+saveRDS(model_results, "../saves/magnet_modelresults.rds")
+```
+
+```{r magnet_draws}
+magnet_draws <-mmagnet_perspective %>% 
+  gather_draws(b_age_centered, b_magnet_scaled, b_perspective_scaled) %>% 
+  mutate(
+    .variable = factor(.variable, 
+                       levels = c("b_age_centered", "b_perspective_scaled", "b_magnet_scaled"), 
+                       labels = c("Age (scaled)", "Perspective-taking (scaled)", "Magnet mean (scaled)")), 
+  ) %>% 
+  rename(estimate = .value, predictor = .variable)
+
+write.csv(magnet_draws, "../saves/magnet_draws.csv", quote = F, row.names = F)
+saveRDS(magnet_draws, "../saves/magnet_draws.rds")
+```
+
+```{r modelplot}
+modelplot <- magnet_draws %>% 
+  mutate(
+    includes_zero = ifelse(predictor == "Age (scaled)", TRUE, FALSE)
+  ) %>%
+  ggplot(., aes(x = estimate, y = predictor, fill = includes_zero)) +
+ tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_alpha = 0.5) +
+    labs(x = "Posterior estimate when predicting TANGO mean", y = "") +
+  guides(fill = "none")+
+  geom_vline(xintercept = 0, linetype = "dashed") +
+  scale_fill_manual(values = c("#006c66", "#EBECEC")) +
+  coord_cartesian(expand = TRUE, xlim = c(-0.6, 0.4), ylim = c(1.5, 3.5)) +
+  theme_classic()
+
+modelplot
+
+saveRDS(modelplot, file = "../saves/magnet_modelplot.rds")
+# ggsave("../figures/modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
+```
+
+```{r arrange_plot}
+arrangedplot <- ggarrange(
+  cor_ci, 
+  modelplot, 
+  ncol = 2, 
+  labels = c("A", "B")
+)
+
+saveRDS(arrangedplot, file = "../saves/magnet_arrangedplot.rds")
+ggsave("../figures/magnet_arrangedplot.png", width = 6, height = 2, scale = 1.75, bg = "white")
+```

### 2023-06-07 stats/lifespan.Rmd
save lifespan models from server

@@
 ```{r plot}
-lifespan <- lifespan_data %>% 
+lifespan_plot <- lifespan_data %>% 
   group_by(subj_id, age, age_group) %>%
@@
 
-ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
-saveRDS(lifespan, "../saves/lifespan.rds")
+# ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
+saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
 ```
@@
 
-write.csv(mlinear, "../saves/mlinear.csv", quote = F, row.names = F)
-saveRDS(mlinear, "../saves/mlinear.rds")
+write.csv(mlinear, "../saves/lifespan_mlinear.csv", quote = F, row.names = F)
+saveRDS(mlinear, "../saves/lifespan_mlinear.rds")
 
@@
 
-write.csv(mquadratic, "../saves/mquadratic.csv", quote = F, row.names = F)
-saveRDS(mquadratic, "../saves/mquadratic.rds")
+write.csv(mquadratic, "../saves/lifespan_mquadratic.csv", quote = F, row.names = F)
+saveRDS(mquadratic, "../saves/lifespan_mquadratic.rds")
 
@@
 
-write.csv(mcubic, "../saves/mcubic.csv", quote = F, row.names = F)
-saveRDS(mcubic, "../saves/mcubic.rds")
+write.csv(mcubic, "../saves/lifespan_mcubic.csv", quote = F, row.names = F)
+saveRDS(mcubic, "../saves/lifespan_mcubic.rds")
 
@@
 
-write.csv(mgaussianprocess, "../saves/mgaussianprocess.csv", quote = F, row.names = F)
-saveRDS(mgaussianprocess, "../saves/mgaussianprocess.rds")
+write.csv(mgaussianprocess, "../saves/lifespan_mgaussianprocess.csv", quote = F, row.names = F)
+saveRDS(mgaussianprocess, "../saves/lifespan_mgaussianprocess.rds")
 
@@
 
-conditional_smooths(msplines2, effects = "weight")
-
-write.csv(msplines, "../saves/msplines.csv", quote = F, row.names = F)
-saveRDS(msplines, "../saves/msplines.rds")
+write.csv(msplines, "../saves/lifespan_msplines.csv", quote = F, row.names = F)
+saveRDS(msplines, "../saves/lifespan_msplines.rds")
 
@@
 
-write.csv(msplines2, "../saves/msplines2.csv", quote = F, row.names = F)
-saveRDS(msplines2, "../saves/msplines2.rds")
+write.csv(msplines2, "../saves/lifespan_msplines2.csv", quote = F, row.names = F)
+saveRDS(msplines2, "../saves/lifespan_msplines2.rds")
 
@@
 
-write.csv(msplines3, "../saves/msplines3.csv", quote = F, row.names = F)
-saveRDS(msplines3, "../saves/msplines3.rds")
+write.csv(msplines3, "../saves/lifespan_msplines3.csv", quote = F, row.names = F)
+saveRDS(msplines3, "../saves/lifespan_msplines3.rds")
 
@@
 
-write.csv(msplines4, "../saves/msplines4.csv", quote = F, row.names = F)
-saveRDS(msplines4, "../saves/msplines4.rds")
+write.csv(msplines4, "../saves/lifespan_msplines4.csv", quote = F, row.names = F)
+saveRDS(msplines4, "../saves/lifespan_msplines4.rds")
 
@@
 
-write.csv(msplines5, "../saves/msplines5.csv", quote = F, row.names = F)
-saveRDS(msplines5, "../saves/msplines5.rds")
+write.csv(msplines5, "../saves/lifespan_msplines5.csv", quote = F, row.names = F)
+saveRDS(msplines5, "../saves/lifespan_msplines5.rds")
 ```
@@
 ```{r lifespan_modelcomparison}
-# mlinear <- readRDS("../saves/mlinear.rds")
-# mquadratic <- readRDS("../saves/mquadratic.rds")
-# mcubic <- readRDS("../saves/mcubic.rds")
-# mgaussianprocess <- readRDS("../saves/mgaussianprocess.rds")
-# msplines <- readRDS("../saves/msplines.rds")
+# mlinear <- readRDS("../saves/lifespan_mlinear.rds")
+# mquadratic <- readRDS("../saves/lifespan_mquadratic.rds")
+# mcubic <- readRDS("../saves/lifespan_mcubic.rds")
+# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+# msplines <- readRDS("../saves/lifespan_msplines.rds")
 
@@
 
-write.csv(mcomparison, "../saves/mcomparison.csv", quote = F, row.names = F)
-saveRDS(mcomparison, "../saves/mcomparison.rds")
+write.csv(mcomparison, "../saves/lifespan_mcomparison.csv", quote = F, row.names = F)
+saveRDS(mcomparison, "../saves/lifespan_mcomparison.rds")
 ```
@@
 ```{r prediction_plot_winning_model}
-prediction_plot <- mdata %>%
-  add_predicted_draws(msplines) %>%  # adding the posterior distribution
-  ggplot(aes(x = age_centered, y = mean_dist)) +  
-  geom_jitter(data = mdata, colour = "grey", size = 1.5, alpha = 0.8) + 
-  stat_lineribbon(aes(y = .prediction), .width = c(.95, .80), alpha = 0.5, colour = "black") +
+ mdraws <- mdata %>%
+  add_predicted_draws(msplines) %>% 
+  ungroup() %>% 
+  select(-c(.row, .chain, .iteration)) %>%
+  rename(draw = .draw, predicted_value = .prediction)
+
+write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
+saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
+
+prediction_plot <- mdraws %>%
+  ggplot(aes(x = age)) +  
+  geom_jitter(aes(y = mean_dist), colour = "grey", size = 1.5, alpha = 0.8) + 
+  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66") +
   scale_fill_brewer(palette = "Greys") + 
-  scale_y_continuous(limits = c(0,4))
+  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) + 
+  scale_y_continuous(limits = c(0,4)) + 
+  guides(fill = "none") +
+  labs(x = "Age in years", y = "Mean click distance in target widths", fill = "")
 

### 2023-06-07 paper/manuscript.Rmd
play around with model plots; add lifespan sample descr to manuscript

@@
 
-```{r dev_sample}
-lifespan_sample <- tango_lifespan %>% 
-  group_by(age_group) %>%
-  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
-  summarise(
-    n_total = n_distinct(subj_id), 
-    age_mean = mean(age, na.rm = T) %>% round(2),
-    age_sd = sd(age, na.rm = T) %>% round(2),
-    age_min = min(age, na.rm = T),
-    age_max = max(age, na.rm = T),
-    n_females = ceiling(sum(female/15)),
-  )
+```{r lifespan_sample}
+lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
 ```
@@
 
-The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).
+The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "18"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "18"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "18"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "18"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "18"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "18"])` girls),
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "19"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "19"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "19"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "19"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "19"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "19"])` girls).
 
@@
 
-<!-- Adults were recruited via *Prolific* [@palan2018prolific].
+Adults were recruited via *Prolific* [@palan2018prolific].
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females).
--->
+Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision.
+The sample included `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "20"])` 20- to 29-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "20"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "20"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "20"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "20"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "20"])` female),
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "30"])` 30- to 39-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "30"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "30"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "30"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "30"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "30"])` female),
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "40"])` 40- to 49-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "40"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "40"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "40"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "40"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "40"])` female),
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "50"])` 50- to 59-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "50"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "50"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "50"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "50"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "50"])` female),
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "60"])` 60- to 69-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "60"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "60"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "60"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "60"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "60"])` female), and
+`r sum(lifespan_sample$n_total[lifespan_sample$age_group == "70"])` 70- to 79-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "70"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "70"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "70"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "70"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "70"])` female).
 
@@
 ```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/magnet_procedure.png")
+knitr::include_graphics("../figures/procedure.png")
 ```
@@
 ```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics(c("../figures/tango_dev.png"))
+knitr::include_graphics(c("../figures/lifespan_plot.png"))
 ```

### 2023-06-07 stats/lifespan.Rmd
play around with model plots; add lifespan sample descr to manuscript

@@
 library(tidybayes) # for stat_halfeye, add_predictive_draws
+library(tidyboot) # for bootstrapped CIs
 library(brms) # modeling
@@
 
-# ggsave("../figures/lifespan.png", width = 8, height = 4, scale = 1.2)
+lifespan_plot
+
+ggsave("../figures/lifespan_plot.png", width = 8, height = 4, scale = 1.2)
 saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
@@
 
-```{r prediction_plot_winning_model}
+```{r draws_winning_model}
+msplines <- readRDS("../saves/lifespan_msplines.rds")
+
 mdraws <- mdata %>%
@@
 saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
+```
 
-prediction_plot <- mdraws %>%
+```{r prediction_plot_winning_model}
+### this sections takes a while to run
+
+# mdraws <- readRDS("../saves/lifespan_mdraws.rds")
+
+mdraws %>%
   ggplot(aes(x = age)) +
-  geom_jitter(aes(y = mean_dist), colour = "grey", size = 1.5, alpha = 0.8) + 
-  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66") +
+  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66", fill = "lightgrey") +
+  geom_jitter(aes(y = mean_dist), colour = "darkgrey", size = 1.5, alpha = 0.8) +
+  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) +
+  scale_y_continuous(limits = c(0,4)) +
+  labs(x = "Age in years", y = "Mean click distance in target widths")
+
+# prediction_plot
+
+# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
+ggsave("../figures/lifespan_modelplot.png", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+```{r smooths}
+lifespan_smooths <- mdata %>%
+  ggplot(aes(x = age, y = mean_dist)) +  
+  geom_jitter(colour = "grey", size = 1.5, alpha = 0.8) + 
+  geom_smooth(method = lm, se = F, aes(colour = "A")) +
+  geom_smooth(method = lm, formula = y ~ poly(x, 2), se = F, aes(colour = "B")) +
+  geom_smooth(method = lm, formula = y ~ poly(x, 3), se = F, aes(colour = "C")) +
+  geom_smooth(method = loess, se = F, aes(colour = "D")) +
+  geom_smooth(method = lm, formula = y ~ splines::bs(x, 5), se = F, aes(colour = "E")) +
   scale_fill_brewer(palette = "Greys") + 
@@
   scale_y_continuous(limits = c(0,4)) + 
-  guides(fill = "none") +
-  labs(x = "Age in years", y = "Mean click distance in target widths", fill = "")
+  scale_color_manual(name = "Smooth method", 
+                     breaks = c("A", "B", "C", "D", "E"),
+                     values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"),
+                     labels = c("linear", "quadratic", "cubic", "loess", "splines (k=5)")) +
+  labs(x = "Age in years", y = "Mean click distance in target widths")
 
-prediction_plot
+lifespan_smooths
 
-# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
-# ggsave("../figures/lifespan_modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
+saveRDS(lifespan_smooths, file = "../saves/lifespan_smooths.rds")
+ggsave("../figures/lifespan_smooths.png", width = 10, height = 6, scale = 0.7, bg = "white")
 ```

### 2023-06-09 paper/manuscript.Rmd
add gazemodel data adults; write magnet sections

--- 2023-06-07 paper/manuscript.Rmd
@@
 ---
-title             : "Variation in gaze understanding across the life span: A process-level perspective"
-shorttitle        : "modeling variation in gaze understanding"
+title: "Variation in gaze understanding across the life span: A process-level perspective"
+shorttitle: "modeling variation in gaze understanding"
 author:
@@
     email         : "julia_prein@eva.mpg.de"
+    role          :
+      - Conceptualization
+      - Methodology
+      - Software
+      - Investigation
+      - Formal Analysis
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing
 
   - name          : "Manuel Bohn"
-    affiliation   : "1"
+    affiliation   : "1,2"
+    role          :
+      - Conceptualization
+      - Formal Analysis
+      - Writing - Original Draft Preparation
+      - Writing - Review & Editing
+
   - name          : "Luke Maurits"
     affiliation   : "1"
+    role          : 
+      - Formal Analysis
+      - Writing - Review & Editing
+
   - name          : "Annika Werwach"
     affiliation   : "1"
+    role          :
+      - Methodology
+      - Investigation
+      - Writing - Review & Editing
+
   - name          : "Daniel B. M. Haun"
     affiliation   : "1"
+    role          :
+      - Supervision
+      - Writing - Review & Editing
 
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+  - id            : "2"
+    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"  
 authornote: |
@@
 draft             : no
-documentclass     : "apa7"
+documentclass     : "apa6"
 classoption       : "man"
@@
 library("papaja")
+library("kableExtra")
+
 theme_set(theme_classic())
@@
 
-```{r analysis-preferences}
+```{r analysis_preferences}
 # Seed for random number generation
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-```{r load_data}
-tango_lifespan <- readRDS("../data/tango-lifespan.rds")
-tango_model <- readRDS("../data/tango-model.rds")
-magnet <- readRDS("../data/magnet-data.rds")
 ```
@@
 
-```{r dev_sample}
-lifespan_sample <- tango_lifespan %>% 
-  group_by(age_group) %>%
-  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
-  summarise(
-    n_total = n_distinct(subj_id), 
-    age_mean = mean(age, na.rm = T) %>% round(2),
-    age_sd = sd(age, na.rm = T) %>% round(2),
-    age_min = min(age, na.rm = T),
-    age_max = max(age, na.rm = T),
-    n_females = ceiling(sum(female/15)),
-  )
+```{r lifespan_sample, include = T, out.width = "100%"}
+lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
+
+lifespan_table <- lifespan_sample %>% 
+  mutate(
+    n = str_glue_data(., "{n_total} ({n_females} female)"), 
+    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
+  ) %>% 
+  rename(
+    `Age group` = age_group,
+    `Age SD` = age_sd, 
+    `Age mean` = age_mean
+  ) %>% 
+  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
+
+apa_table(lifespan_table)
 ```
@@
 
-The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "3"])` 3-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "3"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "3"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "3"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "3"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "3"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "4"])` 4-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "4"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "4"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "4"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "4"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "4"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "5"])` 5-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "5"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "5"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "5"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "5"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "5"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "6"])` 6-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "6"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "6"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "6"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "6"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "6"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "7"])` 7-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "7"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "7"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "7"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "7"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "7"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "8"])` 8-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "8"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "8"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "8"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "8"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "8"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "9"])` 9-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "9"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "9"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "9"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "9"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "9"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "10"])` 10-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "10"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "10"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "10"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "10"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "10"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "11"])` 11-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "11"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "11"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "11"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "11"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "11"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "12"])` 12-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "12"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "12"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "12"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "12"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "12"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "13"])` 13-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "13"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "13"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "13"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "13"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "13"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "14"])` 14-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "14"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "14"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "14"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "14"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "14"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "15"])` 15-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "15"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "15"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "15"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "15"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "15"])` girls), `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "16"])` 16-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "16"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "16"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "16"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "16"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "16"])` girls), and `r sum(lifespan_sample$n_total[lifespan_sample$age_group == "17"])` 17-year-olds (mean = `r sum(lifespan_sample$age_mean[lifespan_sample$age_group == "17"])` years, SD = `r sum(lifespan_sample$age_sd[lifespan_sample$age_group == "17"])`, range = `r sum(lifespan_sample$age_min[lifespan_sample$age_group == "17"])` - `r sum(lifespan_sample$age_max[lifespan_sample$age_group == "17"])`, `r sum(lifespan_sample$n_females[lifespan_sample$age_group == "17"])` girls).
+The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r lifespan_sample$n_total[lifespan_sample$age_group == "3"]` 3-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "3"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "3"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "3"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "3"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "3"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "4"]` 4-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "4"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "4"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "4"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "4"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "4"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "5"]` 5-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "5"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "5"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "5"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "5"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "5"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "6"]` 6-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "6"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "6"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "6"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "6"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "6"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "7"]` 7-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "7"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "7"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "7"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "7"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "7"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "8"]` 8-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "8"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "8"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "8"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "8"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "8"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "9"]` 9-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "9"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "9"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "9"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "9"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "9"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "10"]` 10-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "10"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "10"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "10"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "10"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "10"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "11"]` 11-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "11"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "11"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "11"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "11"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "11"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "12"]` 12-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "12"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "12"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "12"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "12"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "12"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "13"]` 13-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "13"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "13"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "13"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "13"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "13"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "14"]` 14-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "14"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "14"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "14"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "14"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "14"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "15"]` 15-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "15"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "15"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "15"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "15"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "15"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "16"]` 16-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "16"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "16"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "16"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "16"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "16"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "17"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "17"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "17"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "17"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "17"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "17"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "18"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "18"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "18"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "18"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "18"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "18"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "19"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "19"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "19"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "19"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "19"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "19"]` girls).
 
@@
 
-<!-- Adults were recruited via *Prolific* [@palan2018prolific].
+Adults were recruited via *Prolific* [@palan2018prolific].
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of `r lifespan_sample$n_total` English-speakers with an average age of `r lifespan_sample$age_mean` years (SD = `r lifespan_sample$age_sd`, range = `r lifespan_sample$age_min` - `r lifespan_sample$age_max`, `r lifespan_sample$n_females` females).
--->
+Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision.
+The sample included `r lifespan_sample$n_total[lifespan_sample$age_group == "20"]` 20- to 29-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "20"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "20"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "20"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "20"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "20"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "30"]` 30- to 39-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "30"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "30"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "30"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "30"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "30"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "40"]` 40- to 49-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "40"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "40"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "40"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "40"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "40"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "50"]` 50- to 59-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "50"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "50"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "50"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "50"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "50"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "60"]` 60- to 69-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "60"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "60"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "60"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "60"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "60"]` female), and `r lifespan_sample$n_total[lifespan_sample$age_group == "70"]` 70- to 79-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "70"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "70"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "70"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "70"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "70"]` female).
 
@@
 
-We used the TANGO task [@prein2022tango].
+We used the continuous version of the TANGO [@prein2022tango].
 The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; @prein2022tango].
+The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; @prein2022tango].
 
 Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
-Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
+The target then fell behind a hedge (continuous task version).
 The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
-The target flight was covered so that participants could not see where the target landed.
+In test trials, the target flight was covered so that participants could not see where the target landed.
 Participants' task was to locate the target by tracking the agent's gaze.
-They could respond by clicking or touching on the screen.
+They could respond by touching on the screen.
 
@@
 
-The outcome measure depended on the task version.
-In the continuous *hedge version*, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the discrete *box version*, we calculated the proportion of correct responses.
+The outcome measure was imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
+Target coordinates were randomly generated during runtime.
+Each target bin, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
 
-The randomization of the final target location also depended on the task version.
-In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
-In the box version, the target randomly landed in one of the boxes.
-We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
-Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
-
-(ref:figlab1) **Setup of the TANGO**.
-(A) Infrastructure for online testing.
-(i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens, or research labs.
-(ii) The task is presented as a website that works across devices.
-(iii) The scripts for the website and the recorded data are stored on secure local servers.
-(B) Hedge version (continuous) of the gaze understanding task.
-(i) The agent stands in a window with the target in front of them.
-(ii) A hedge grows and covers the target.
-(iii) The target falls to a random location on the ground.
+(ref:figlab1) **Setup of the TANGO and Magnet tasks**.
+(A) TANGO: Gaze understanding task.
+The agent stands in a window with the target in front of them.
+A hedge grows and covers the target.
+The target falls to a random location on the ground.
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task.
-Number of boxes (min.
-1; max.
-8) as potential hiding locations can be set according to the researcher's need.
+(B) Magnet task: non-social vector estimation.
 
 ```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/magnet_procedure.png")
+knitr::include_graphics("../figures/procedure.png")
 ```
@@
 
-In the in-person sample, children were tested on a tablet in a quiet room in their kindergarten.
-An experimenter guided the child through the study.
-Half of the sample completed the continuous task version, while the other half completed the discrete task version.
-
-In the remote sample, children and teenagers received a personalized link to the study website.
+Children and teenagers received a personalized link to the study website.
 Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
@@
 
-In the remote sample for children from three to five years old, the family's presentation device determined the task version.
-Whenever a touchscreen was available, the continuous task version was presented.
-For families using a computer without touchscreen, the discrete task version was shown.
-Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.
-
-The number of teenagers in our internal database for recruiting families substantially decreased by age.
-To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
-Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.
-
-The remote adult sample was equally distributed across the two task versions.
-
 ## Analysis
-
--   TODO: non-linear model for development
 
@@
 -   entwicklungsperspektive basierend auf model
--   dann prozess-ebene =\> magnet
+-   dann prozess-ebene = magnet
 
-# Non-social vector following
+```{r gazemodel_sample}
+gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
+```
+
+## Participants
+
+The sample included the `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` three- to five-year-old children and `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group == 18])` adults from our Lifespan study.
+For age distributions, see Participant section of the Lifespan Study.
+
+out of convenience, we only used ... since developmental chnage was minimial in adutls we used ...
+
+## Procedure
+
+## Analysis
+
+## Results
+
+(ref:figlab3) **Gaze funnel**
+
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gazefunnel_combined.png")
+```
+
+## Discussion
+
+# Components of gaze understanding
+
+Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
+In this study, we sought to inquire whether there are any other cognitive processes outside vector-following that constitute gaze understanding.
+We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
+
+First, we aimed at isolating the vector-following part of the gaze understanding task.
+For this, we designed a new non-social vector estimation task that shared all crucial design features of the understanding task.
+Additionally, we administered a ToM task battery, comprising 4 tasks from the ToM scale by Wellman and Liu (2004) and two additional perspective-taking tasks.
+
+Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
+This way, we can disentangle which components comprise gaze understanding.
+In this way, we can find out what contribution each component makes to explain gaze understanding.
 
 Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.
-
 The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
@@
 
--   gut, dass unser maß ind diff messen kann, das nutzen wir jetzt
+## Participants
 
--   zsmhang mit vector following, aber nicht redundant
+```{r magnet_sample}
+magnet_sample <- readRDS("../saves/magnet_sample.rds")
+```
 
--   perspective-taking auch, aber auch nicht relevant, nicht theory of mind score
+Testing took place in kindergartens in Leipzig, Germany.
+The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r sum(magnet_sample$age_sd)`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
 
--   diskutieren dass die maße auch nict ind diff maße sind
+## Procedure
 
--   model vergleich: welche komponente stecken in gafo drin?,
-    welchen beitrag liefern die um score zu erklären?
-    welche wichtiger, tom oder nur perspective taking
+Children were tested in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects design.
+All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task.
+Several reasons motivated the decision.
+First, we decided for a fixed order to be able to compare participant's performance straight-forwardly with each other.
+Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task, to tasks with personal interaction, back to a tablet task.
+Third, we showed the non-social vector estimation task before the gaze understanding task, so that participants would not be biased to interpret the presented stimuli as "eye- / "agent-like".
 
--   magnet versuch das vector following zu isolieren.
-    ist da noch was anderes außerhalb vector-following?
+### Non-social vector estimation
 
--   aggregierte messungen immer besser, nur indikatoren für konstrukt
+Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task.
+This task was also presented as a webapp and made use of the concept of magnetism.
+The setup looked as follows.
+On the upper part of the screen, there was a tube with a gearwheel, located in a circular window.
+On the floor, there laid a magnet.
+The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
+The gearwheel moved in a way that its center aligned with the center of the magnet.
+Participants were then asked to locate the magnet.
+Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
+When no information about the magnet location was accessible, participants were expected to use the gearwheel inside the window as a non-social cue to locate the magnet.
+
+As in the TANGO, there were three different trial types depending on the visual access to the true magnet location.
+In the touch training, participants had full visual access to the magnet's location (i.e., no wooden wall).
+In familiarization trials, participants had partial visual access, since the wooden wall was moved in front of the target after the magnet's location was already visible.
+In test trials, participants have no visual access to the magnet location, because the wall covers the magnet from the beginning of the trial.
+
+Children received 19 trials with one touch training, two familiarization trials, and 16 test trials each.
+The first trial of each type comprised a voice-over description of the presented events.
+We conducted our analysis with 15 test trials, excluding the touch, familiarization, and voice-over trials.
+The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click.
+Magnet coordinates were generated as follows.
+The full width of the screen was divided into ten bins.
+Each bin occurred equally often, while the same bin could occur in two consecutive trials.
+Exact coordinates within each bin were randomly generated.
+
+### Theory of Mind task battery
+
+We administered four tasks from the @wellman2004scaling Theory of Mind scale.
+We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
+Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga], with the aim of increasing the task battery's difficulty.
+See Supplements for further detail.
+The dependent variable was the aggregate score of all solved ToM tasks.
+In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
+
+### Gaze understanding
+
+As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. Children were tested on a tablet.
+
+## Analysis
+
+By design, both the gaze understanding task as well as the non-social vector estimation task involve vector estimation.
+On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate significantly.
+For these two tasks, we calculated the mean level of imprecision for each subject.
+We correlated these two scores using *Pearson's* correlation coefficients.
+
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we can imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expect that gaze understanding and ToM measures are more strongly correlated than non-social vector estimation and ToM measures.
+(B) If gaze understanding relies purely on task-specific processes, then the correlation between gaze understanding and ToM measures will be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficient.
+
+Furthermore, to estimate which components contribute to gaze understanding, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in\`R: tango_mean \~ age_centered + magnet_scaled + perspective_scaled\`).
+The outcome variable was modeled by a lognormal distribution.
+With this analysis, we wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value.
+
+## Results
+
+As expected, we found that gaze understanding as a social vector estimation task correlated with the non-social vector estimation task.
+Importantly, however, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
+
+Our model comparison corroborated this: evidently, gaze understanding was best predicted by non-social vector estimation and perspective-taking.
+This shows that the gaze understanding task recruits social-cognitive abilities beyond vector estimation.
+
+(ref:figlab4) **Components of gaze understanding**
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/magnet_arrangedplot.png")
+```
+
+## Discussion
+
+In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2022tango].
+Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
+
+It seems noteworthy to point out that lower correlations between ToM skills and gaze understanding could be grounded in the design features of the applied ToM tasks.
+The tasks we used to measure ToM skills were not designed to capture individual differences: they rely on an aggregate score of dichotomous measures.
+These sum scores can only capture limited variance, which may obscure potential correlations.
+However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
+The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
+
+# General discussion
 
 # Limitations
-
-# Discussion
 
@@
 ```
+\newpage

### 2023-06-09 paper/manuscript.tex
add gazemodel data adults; write magnet sections

@@
 \documentclass[
-  man,floatsintext]{apa7}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, cognitive development\newline\indent Word count: 6856}
+\keywords{social cognition, individual differences, gaze cues, cognitive modeling\newline\indent Word count: xxx}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
+  pdftitle={Variation in gaze understanding across the life span: A process-level perspective},
+  pdfauthor={Julia Prein1, Manuel Bohn1,2, Luke Maurits1, Annika Werwach1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
-  pdfkeywords={social cognition, individual differences, gaze cues, cognitive development},
+  pdfkeywords={social cognition, individual differences, gaze cues, cognitive modeling},
   hidelinks,
@@
 
-\title{TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
+\title{Variation in gaze understanding across the life span: A process-level perspective}
+\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
 \date{}
 
-\shorttitle{assessing individual differences in gaze understanding}
+\shorttitle{modeling variation in gaze understanding}
 
 \authornote{
+
+The authors made the following contributions.
+Julia Prein: Conceptualization, Methodology, Software, Investigation, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Luke Maurits: Formal Analysis, Writing - Review \& Editing; Annika Werwach: Methodology, Investigation, Writing - Review \& Editing; Daniel B.
+M.
+Haun: Supervision, Writing - Review \& Editing.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany}
 
 \abstract{%
-Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation \emph{between} individuals.
-Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx.
-5--10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues.
-Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
-Our interactive browser-based task works across devices and enables in-person and remote testing.
-The implemented spatial layout allows for discrete and continuous measures of participants' click imprecision and is easily adaptable to different study requirements.
-Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample.
-Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target.
-High internal consistency and test--retest reliability estimates underline that the captured variation is systematic.
-This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.
+Abstract
 }
@@
 
-Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the most-studied phenomena in developmental research.
-In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).
-Yet, there are always individual differences.
-Identifying variability in social-cognitive abilities and factors influencing their development is vital in theory building (e.g., to test causal predictions) and designing interventions (Happé, Cook, \& Bird, 2017; Kidd, Donnelly, \& Christiansen, 2018; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014; Mundy et al., 2007; Underwood, 1975).
-
-Numerous studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
-The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities (e.g., Wellman \& Liu, 2004), and which factors drive the development of social cognition (Devine \& Hughes, 2018; e.g., Gola, 2012).
-For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
-In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes (for an overview, see Repacholi, 2003).
-Studies on social-cognitive abilities and family influences include the effect of parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce et al., 2014), and family background as parental education, occupation, sibling interaction and childcare (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991).
-Another group of individual differences studies focuses on the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Carlson \& Moses, 2001; Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007; Milligan, Astington, \& Dack, 2007; Okumura et al., 2017).
-Studies on social behavioral outcomes measured the interplay of social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005), stereotypes, and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).
-
-However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally (e.g., Poulin-Dubois, Goldman, Meltzer, \& Psaradellis, 2023; Sodian, 2023; Sodian et al., 2016).
-This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
-A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or -- when they did -- showed mixed results on test-retest reliability (Hughes et al., 2000; Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).
-
-To give an example: the most commonly applied prototypical measure for social cognition is the change-of-location false belief task (Baron-Cohen, Leslie, \& Frith, 1985; Wimmer \& Perner, 1983).
-Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
-A doll called Sally puts her marble into a basket.
-After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
-Participants then get asked where Sally will look for her marble once she returns.
-The outcome measures false belief understanding in a dichotomous way: children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
-Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
-Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
-
-However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (Repacholi, 2003).
-Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences (cf.~``reliability paradox,'' Hedge, Powell, \& Sumner, 2018).
-As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
-This has profound implications for what studies on individual differences using this task (or others) can show.
-Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
-For example, Sodian et al.
-(2016) neither found a correlation between two moral Theory of mind False Belief and Intention tasks at 60 months, nor a relationship between these two factors and implicit False Belief understanding at 18 months.
-
-The ``Sandbox task'' is one of the few tasks that attempt to overcome these methodological challenges (Begeer, Bernstein, van Wijhe, Scheeren, \& Koot, 2012; Bernstein, Thornton, \& Sommerville, 2011; Coburn, Bernstein, \& Begeer, 2015; Mahy, Bernstein, Gerrard, \& Atance, 2017; Sommerville, Bernstein, \& Meltzoff, 2013).
-This continuous FB task measures the degree to which the estimate of another's belief is biased by one's own knowledge.
-Recent work questions the interpretation of this measure (Samuel, Legg, Lurz, \& Clayton, 2018a; Samuel, Legg, Lurz, \& Clayton, 2018b): it is unclear whether a smaller egocentric bias can be directly translated into a better mental state reasoning ability.
-Another evaluation criterion should, therefore, be whether a task captures meaningful variability in performance; that is, differences in test scores should correspond to differences in the social-cognitive ability in question.
-
-Thus, developmental psychology faces a dilemma: many research questions rely on measuring individuals' development, yet, there is a lack of tasks to measure these individual differences reliably.
-To capture the emergence of social-cognitive abilities and their relation to social factors in greater precision and detail, we must consequently address the methodological limitations of existing study designs (Hughes et al., 2011; Hughes \& Leekam, 2004).
-
-Schaafsma, Pfaff, Spunt, and Adolphs (2015) compiled a ``wish list'' for new social-cognitive paradigms.
-They advocated for parametric -- instead of dichotomous -- measures covering proficiency as a range, avoiding floor and ceiling effects, and showing satisfactory test-retest reliability estimates (see also Beaudoin et al., 2020; Hughes \& Devine, 2015).
-New tasks should capture variation across age groups, including older children and adults (Repacholi, 2003).
-Another goal in creating new tasks should be to focus on the ``face value'': measures should probe the underlying social-cognitive ability as straight-forward and directly as possible.
-Keeping task demands minimal is also beneficial for using the paradigm in a variety of different cultural, clinical, and demographic contexts (Molleman, Kurvers, \& van den Bos, 2019).
-The task should serve as a proxy for behavior as it appears in the real world and should be validated in relation to real-world experiences (Repacholi, 2003).
-
-\hypertarget{a-new-measure-of-gaze-understanding}{%
-\section{A new measure of gaze understanding}\label{a-new-measure-of-gaze-understanding}}
-
-Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
-We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
-The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively (Astor, Thiele, \& Gredebäck, 2021; Byers-Heinlein et al., 2021; Coelho, George, Conty, Hugueville, \& Tijus, 2006; Del Bianco, Falck-Ytter, Thorup, \& Gredebäck, 2019; Frischen, Bayliss, \& Tipper, 2007; Hernik \& Broesch, 2019; Itakura \& Tanaka, 1998; Lee, Eskritt, Symons, \& Muir, 1998; Moore, 2008; Shepherd, 2010; Tomasello, Hare, Lehmann, \& Call, 2007).
-In our definition, gaze understanding goes one step further by including the \emph{acting on the gaze-cued location} -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.
-
-Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a ``front end ability'' (Brooks \& Meltzoff, 2005, p. 535).
-Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
-As such, the eyes have been regarded as a ``window into the mind'' (Shepherd, 2010).
-Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions (Bohn \& Köymen, 2018; Tomasello et al., 2007).
-In addition, gaze and language development seem to be related (Brooks \& Meltzoff, 2005).
-Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication (Hernik \& Broesch, 2019; Macdonald \& Tatler, 2013).
+\begin{itemize}
+\tightlist
+\item
+  why do we care about developmental trajectory? ref to stat learning paper
+\item
+  variation
+\end{itemize}
+
+\hypertarget{why-do-we-need-gaze-understanding}{%
+\subsection{Why do we need gaze understanding?}\label{why-do-we-need-gaze-understanding}}
+
+How do humans learn about their environment and navigate through their social surroundings?
+One possibility to extract information from the environment is through following others' focus of attention.
+Building a common ground is considered especially important in communicative interactions and shared activities (Tomasello, Hare, Lehmann, \& Call, 2007).
+
+\hypertarget{how-does-gaze-following-emerge}{%
+\subsection{How does gaze following emerge?}\label{how-does-gaze-following-emerge}}
+
+Existing studies operationalize gaze following as the ability to follow another agent's line of sight.
+As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
+Infants as young as six months can attune their gaze to that of another agent (D'Entremont, Hains, \& Muir, 1997).
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access (Moll \& Tomasello, 2004).
+
 While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
-One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
-However, many cognitive abilities continue to develop beyond early childhood (e.g., Gathercole, Pickering, Ambridge, \& Wearing, 2004 for working memory; Raviv \& Arnon, 2018 for visual statistical learning).
-Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
-Consequently, we aimed to assess the differentiation of the ability to understand gaze.
-Our goal was not to establish the youngest age at which children understand gaze cues.
+One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.However, many cognitive abilities develop with age (e.g., working memory, Gathercole, Pickering, Ambridge, \& Wearing, 2004).
+Similarly, visual processing appears to improve with age.
+Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
+
+\hypertarget{the-scope-of-infants-gaze-following-ability}{%
+\subsection{The scope of infants' gaze following ability}\label{the-scope-of-infants-gaze-following-ability}}
+
+Though these studies suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions of the other agent.
+Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.~Butterworth \& Jarrett's ecological and geometric mechanism, Butterworth and Jarrett (1991){]}.
+Therefore, it is crucial to study children's intentional understanding of gaze.
+
+Moore, Angelopoulos, and Bennett (1997) showed that 9-month-olds followed an agent's gaze more, when it was accompanied by a dynamic head turn in comparison to a static head turn.
+
+In a hiding game with two search locations, Povinelli, Reaux, Bierschwale, Allain, and Simon (1997) found that three-year-olds used gaze as a cue to locate the reward, while two-year-olds performed at chance level.
+
+In a similar object choice paradigm with two containers, Behne, Carpenter, and Tomasello (2005) investigated whether infants understand the communicative intent behind pointing and gaze cues.
+In contrast to Povinelli et al. (1997), they found that already 14-month-olds used the agent's cues to select an object.
+In conditions with absent-minded `cues', infants performed around chance.
+This could be interpreted as infants recognizing the nature of this joint activity: namely, that the adult's behavior was beneficial and relevant for their object choice.
+
+\hypertarget{head-vs-eye-direction}{%
+\subsubsection{Head vs eye direction}\label{head-vs-eye-direction}}
+
+It is important to note that in many existing gaze conditions, the experimenter shifted their eyes and head in synchrony (e.g., Behne et al. (2005)).
+Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
+
+A handful of studies approached this potential confound by separately manipulating head and eye movement.
+Brooks and Meltzoff (2002) implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
+
+Investigating the `cooperative eye hypothesis', Tomasello et al.
+(2007) implemented six conditions, in which an experimenter oriented towards the ceiling with their eyes only, head only (eyes closed), both head and eyes, or neither.
+They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
+
+Importantly, the subjects were not presented with an object choice but their attention orientation was measured.
+
+\begin{itemize}
+\item
+  (Raviv \& Arnon, 2018)
+\item
+  (Astor \& Gredebäck, 2022)
+\item
+  (Colombo, 2001)
+\item
+  (Scaife \& Bruner, 1975)
+\item
+  (Itakura \& Tanaka, 1998)
+\item
+  (Carpenter, Nagell, \& Tomasello, 1998) ``Several other studies have attempted to determine more precisely the cue that infants are using when they follow the gaze direction of others, that is, whether they use adults' head or eye orientation.
+In tasks comparing infants' responses when the experimenters turned their head and eyes together to targets with their responses when the experimenters directed their eyes to the targets but their head remained facing forward, Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) all found that only infants age 12 months and older responded correctly when eyes and head were oriented in the same direction and that infants at all ages (i.e., through 19 months) performed poorly when eye and head direction diverged'' (p.10-11) object choice.
+\item
+  (Silverstein, Feng, Westermann, Parise, \& Twomey, 2021) for vertical plane
+\item
+  (Zhang, Zhang, Zhang, Tang, \& Liu, 2019)
+\item
+  (Frischen, Bayliss, \& Tipper, 2007)
+\item
+  (Lee, Eskritt, Symons, \& Muir, 1998)
+\item
+  (Coelho, George, Conty, Hugueville, \& Tijus, 2006)
+\end{itemize}
+
+\hypertarget{aim-of-the-current-project}{%
+\subsection{Aim of the current project}\label{aim-of-the-current-project}}
+
+\hypertarget{developmental-trajectory-measuring-modeling-individual-differences}{%
+\subsubsection{Developmental trajectory, measuring \& modeling individual differences}\label{developmental-trajectory-measuring-modeling-individual-differences}}
+
+In this study, we were interested in the developmental trajectory of gaze understanding.
+While we expect the younger children to be able to follow gaze, we aimed at assessing the differentiation of their social-cognitive ability.
+Our goal was \emph{not} to establish the youngest age at which children understand gaze cues.
 Rather, we wanted to examine how that ability changes with age.
-To accurately measure developmental change, we were interested in capturing individual variability.
-
-To address the psychometric shortcoming of earlier work, we implemented the following design features: First, we used a continuous measure which allowed us to capture fine-grained individual differences at different ages.
-Second, we designed short trials that facilitate more than a dozen replicates per subject.
-The result is more precise individual-level estimates.
-Third, we systematically investigated the psychometric properties of the new task.
-
-Designing this task required a new testing infrastructure.
-We designed the task as an interactive web application.
-Previous research has successfully used online study implementations that compare well to in-person data collection (Bohn, Le, Peloquin, Köymen, \& Frank, 2021; Bohn, Tessler, Merrick, \& Frank, 2021; Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016).
-This greatly increased the flexibility with which we could modify the stimuli on a trial-by-trial basis.
-Furthermore, because the task is largely self-contained, it is much more controlled and standardized.
-Most importantly, it makes the task portable: testing is possible in-person using tablets but also remotely via the internet (no installation needed).
-As such, it provides a solid basis to study individual differences in gaze understanding across ages at scale.
-We make the task and its source code openly accessible for other researchers to use and modify.
-
-\hypertarget{task-design}{%
-\section{Task design}\label{task-design}}
-
-\hypertarget{implementation}{%
-\subsection{Implementation}\label{implementation}}
-
-The code is open-source (\url{https://github.com/ccp-eva/tango-demo}), and a live demo version can be found under: \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
-
-The web app was developed using \texttt{JavaScript}, \texttt{HTML5}, \texttt{CSS,} and \texttt{PHP}.
-For stimulus presentation, a scalable vector graphic (SVG) composition was parsed.
-This way, the composition scales according to the user's viewport without loss of quality while keeping the aspect ratio and relative object positions constant.
-Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually.
-This is needed for precisely calculating the exact pupil and target locations and sizes.
-Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
-The web app generates two file types: (1) a text file (.json) containing metadata, trial specifications, and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording.
-These files can either be sent to a server or downloaded to the local device.
-Personalized links can be created by passing on URL parameters.
-
-\hypertarget{stimuli}{%
-\subsection{Stimuli}\label{stimuli}}
-
-Our newly implemented task asks children and adults to search for a balloon.
-The events proceed as follows (see Figure \ref{fig:fig1}B and C).
-An animated agent (a sheep, monkey, or pig) looks out of a window of a house.
-A balloon (i.e., target; blue, green, yellow, or red) is located in front of them.
-The target then falls to the ground.
-At all times, the agent's gaze tracks the movement of the target: the pupils and iris move so that their center aligns with the center of the target.
-While the distance of the target's flight depends on the final location, the target moves at a constant speed.
-Participants are then asked to locate the target: they respond by touching or clicking on the screen.
-Visual access to the target's true location is manipulated by a hedge.
-Participants either have full, partial, or no visual access to the true target location.
-When partial or no information about the target location is accessible, participants are expected to use the agent's gaze as a cue.
-
-To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
-Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130\%) and change in opacity (decrease to 75\%) for 0.3 sec.
-The landing of the target is accompanied by a tapping sound.
-Once the target landed, the instructor's voice asked ``Where is the balloon?''.
-To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
-Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
-If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.
-
-\hypertarget{trials}{%
-\subsection{Trials}\label{trials}}
-
-Trials differ in the amount of visual access that participants have to the final target position.
-Before the test trials start, participants complete four training trials during which they familiarize themselves with touching the screen.
-In the first training trial, participants have full visual access to the target flight and the target's end location and are simply asked to click on the visible balloon.
-In the second and third training trials, participants have partial access: they witness the target flight but cannot see the target's end location.
-They are then asked to click on the hidden balloon, i.e., the location where they saw the target land.
-In test trials, participants have no visual access to the target flight or the end location.
-Participants are expected to use the agent's gaze as a cue to locate the target.
-The first trial of each type comprises a voice-over description of the presented events.
-The audio descriptions explicitly state that the agent is always looking at the target (see Supplements for audio script).
-After the four training trials, participants receive 15 test trials.
-The complete sequence of four training trials and 15 test trials can be easily completed within 5-10 minutes.
-
-\hypertarget{study-versions}{%
-\subsection{Study versions}\label{study-versions}}
-
-We designed two study versions that differ in the target's final hiding place and, consequently, in the outcome measure: a \emph{hedge version} (continuous) and a \emph{box version} (discrete).
-Both versions use the same first training trial and then differ in the consecutive training and test trials.
-In the hedge version, participants have to indicate their estimated target location directly on a hedge.
-Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the box version, the target lands in a box, and participants are asked to click on the box that hides the target.
-Researchers can choose how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
-Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
-Note that in the test trials of both versions, the target flight is covered by a hedge.
-In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
-In the box version, the hedge shrinks completely.
-The boxes then hide the target's final destination (see Figure \ref{fig:fig1}B and C).
+
+In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent's gaze.
+While language demands were kept low, the participants had to actively respond and, therefore, make use of the presented gaze cue.
+
+A unique contribution of this study is the richness of the data set.
+Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
+We could circumvent these issues by applying the exact same task for the entire life span.
+
+\hypertarget{lifespan}{%
+\section{Lifespan}\label{lifespan}}
+
+\begin{itemize}
+\tightlist
+\item
+  development \& individual differences in gaze understanding
+\item
+  verweis methods paper reliable differences kinder \& adults.
+\item
+  kontinuerliche, systematische variation, wodrin? =\textgreater{} model
+\end{itemize}
+
+\url{https://osf.io/6yjz3}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:lifespan_sample}}
+
+\begin{tabular}{lllll}
+\toprule
+Age group & \multicolumn{1}{c}{n} & \multicolumn{1}{c}{Age mean} & \multicolumn{1}{c}{Age range} & \multicolumn{1}{c}{Age SD}\\
+\midrule
+3.00 & 19 (7 female) & 3.62 & 3.04 - 3.99 & 0.31\\
+4.00 & 17 (9 female) & 4.45 & 4.05 - 4.91 & 0.30\\
+5.00 & 22 (13 female) & 5.56 & 5.08 - 5.99 & 0.31\\
+6.00 & 24 (16 female) & 6.50 & 6.1 - 6.99 & 0.28\\
+7.00 & 39 (20 female) & 7.48 & 7.04 - 7.95 & 0.25\\
+8.00 & 41 (20 female) & 8.46 & 8.03 - 8.98 & 0.27\\
+9.00 & 56 (29 female) & 9.46 & 9.01 - 9.96 & 0.28\\
+10.00 & 35 (22 female) & 10.49 & 10.01 - 11 & 0.28\\
+11.00 & 54 (26 female) & 11.43 & 11.01 - 11.96 & 0.28\\
+12.00 & 43 (19 female) & 12.41 & 12.01 - 12.99 & 0.30\\
+13.00 & 42 (19 female) & 13.50 & 13.09 - 13.99 & 0.27\\
+14.00 & 20 (14 female) & 14.37 & 14.05 - 14.98 & 0.23\\
+15.00 & 21 (11 female) & 15.56 & 15.05 - 15.98 & 0.30\\
+16.00 & 19 (10 female) & 16.51 & 16.17 - 16.97 & 0.24\\
+17.00 & 19 (10 female) & 17.53 & 17.01 - 17.95 & 0.28\\
+18.00 & 2 (0 female) & 18.00 & 18 - 18 & 0.00\\
+19.00 & 5 (4 female) & 19.00 & 19 - 19 & 0.00\\
+20.00 & 40 (25 female) & 23.02 & 20 - 29 & 2.77\\
+30.00 & 40 (21 female) & 34.42 & 30 - 39 & 3.00\\
+40.00 & 40 (24 female) & 44.17 & 40 - 49 & 2.92\\
+50.00 & 40 (21 female) & 54.38 & 50 - 59 & 3.04\\
+60.00 & 40 (21 female) & 63.73 & 60 - 69 & 2.56\\
+70.00 & 40 (20 female) & 72.75 & 70 - 79 & 2.44\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+We collected data from a remote child, teenager and adult sample.
+For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+
+The remote child and teenager sample consisted of 471 children, including 19 3-year-olds (mean = 3.62 years, SD = 0.31, range = 3.04 - 3.99, 7 girls), 17 4-year-olds (mean = 4.45 years, SD = 0.30, range = 4.05 - 4.91, 9 girls), 22 5-year-olds (mean = 5.56 years, SD = 0.31, range = 5.08 - 5.99, 13 girls), 24 6-year-olds (mean = 6.50 years, SD = 0.28, range = 6.10 - 6.99, 16 girls), 39 7-year-olds (mean = 7.48 years, SD = 0.25, range = 7.04 - 7.95, 20 girls), 41 8-year-olds (mean = 8.46 years, SD = 0.27, range = 8.03 - 8.98, 20 girls), 56 9-year-olds (mean = 9.46 years, SD = 0.28, range = 9.01 - 9.96, 29 girls), 35 10-year-olds (mean = 10.49 years, SD = 0.28, range = 10.01 - 11, 22 girls), 54 11-year-olds (mean = 11.43 years, SD = 0.28, range = 11.01 - 11.96, 26 girls), 43 12-year-olds (mean = 12.41 years, SD = 0.30, range = 12.01 - 12.99, 19 girls), 42 13-year-olds (mean = 13.50 years, SD = 0.27, range = 13.09 - 13.99, 19 girls), 20 14-year-olds (mean = 14.37 years, SD = 0.23, range = 14.05 - 14.98, 14 girls), 21 15-year-olds (mean = 15.56 years, SD = 0.30, range = 15.05 - 15.98, 11 girls), 19 16-year-olds (mean = 16.51 years, SD = 0.24, range = 16.17 - 16.97, 10 girls), 19 17-year-olds (mean = 17.53 years, SD = 0.28, range = 17.01 - 17.95, 10 girls), 2 17-year-olds (mean = 18 years, SD = 0, range = 18 - 18, 0 girls),
+5 17-year-olds (mean = 19 years, SD = 0, range = 19 - 19, 4 girls).
+
+Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
+Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+
+Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
+\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
+Participants consisted of 240 English-speaking adults that reported to have normal or corrected-to-normal vision.
+The sample included 40 20- to 29-year-olds (mean = 23.02 years, SD = 2.77, range = 20 - 29, 25 female),
+40 30- to 39-year-olds (mean = 34.42 years, SD = 3, range = 30 - 39, 21 female),
+40 40- to 49-year-olds (mean = 44.17 years, SD = 2.92, range = 40 - 49, 24 female),
+40 50- to 59-year-olds (mean = 54.38 years, SD = 3.04, range = 50 - 59, 21 female),
+40 60- to 69-year-olds (mean = 63.73 years, SD = 2.56, range = 60 - 69, 21 female), and
+40 70- to 79-year-olds (mean = 72.75 years, SD = 2.44, range = 70 - 79, 20 female).
+
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+We used the TANGO task (Prein, Bohn, Kalinke, \& Haun, 2022).
+The task was presented as an interactive web application (see Figure \ref{fig:fig1}; live demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
+The TANGO showed satisfactory internal consistency and retest reliability {[}with reliability estimates \emph{Pearson's r} ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; Prein et al.
+(2022){]}.
+
+Each trial presented an agent standing in a window, watching a balloon (\emph{i.e.}, target) falling to the ground.
+Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
+The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
+The target flight was covered so that participants could not see where the target landed.
+Participants' task was to locate the target by tracking the agent's gaze.
+They could respond by clicking or touching on the screen.
+
+Four familiarization trials ensured that participants understood the task and felt comfortable with the response format.
+Then, 15 test trials followed.
+Completing the 19 trials took approximately 5-10 minutes.
+
+The outcome measure depended on the task version.
+In the continuous \emph{hedge version}, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
+In the discrete \emph{box version}, we calculated the proportion of correct responses.
+
+The randomization of the final target location also depended on the task version.
+In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
+In the box version, the target randomly landed in one of the boxes.
+We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
+Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_procedure}
+{\centering \includegraphics[width=1\linewidth]{../figures/procedure}
 
@@
 
-\caption{\textbf{Study setup}.
+\caption{\textbf{Setup of the TANGO}.
 (A) Infrastructure for online testing.
-(i) Subjects aged 3 to 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens, or in research labs.
+(i) Subjects aged 3 -- 99+ can participate.
+Data collection can take place anywhere: online, in kindergartens, or research labs.
 (ii) The task is presented as a website that works across devices.
-(iii) The scripts for the website and the recorded data are stored on secure in-house servers.
-(B) Hedge version (continuous) of the TANGO.
+(iii) The scripts for the website and the recorded data are stored on secure local servers.
+(B) Hedge version (continuous) of the gaze understanding task.
 (i) The agent stands in a window with the target in front of them.
@@
 The agent's eyes track the movement of the target.
-Three exemplary target locations are shown to depict how indicative the agent's gaze cues are in determining the target's location.
-The transparent target is only shown for an illustrative purpose (not visible during the test).
-(C) Box version (discrete) of the TANGO.
+(C) Box version (discrete) of the gaze understanding task.
 Number of boxes (min.
@@
 
-\hypertarget{randomization}{%
-\subsection{Randomization}\label{randomization}}
-
-All agents and target colors appear equally often and are not repeated in more than two consecutive trials.
-The randomization of the target end location depends on the study version.
-In the hedge version, the full width of the screen is divided into ten bins.
-Exact coordinates within each bin are then randomly generated.
-In the box version, the target randomly lands in one of the boxes.
-As with agent and color choice, each bin/box occurs equally often and can only occur twice in a row.
-
-\hypertarget{individual-differences}{%
-\section{Individual differences}\label{individual-differences}}
-
-Our first aim was to assess whether the TANGO captures inter-individual variation in a child and adult sample.
-Furthermore, we were interested in how the data collection mode (in-person vs.~remote) influences responses.
-
-Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/r3bhn} (adult sample).
-The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
-The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+In the in-person sample, children were tested on a tablet in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+Half of the sample completed the continuous task version, while the other half completed the discrete task version.
+
+In the remote sample, children and teenagers received a personalized link to the study website.
+Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
+Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.
+
+In the remote sample for children from three to five years old, the family's presentation device determined the task version.
+Whenever a touchscreen was available, the continuous task version was presented.
+For families using a computer without touchscreen, the discrete task version was shown.
+Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.
+
+The number of teenagers in our internal database for recruiting families substantially decreased by age.
+To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
+Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.
+
+The remote adult sample was equally distributed across the two task versions.
+
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+\begin{itemize}
+\tightlist
+\item
+  TODO: non-linear model for development
+\end{itemize}
+
+All test trials without voice-over description were included in our analyses.
+We ran all analyses in R version 4.3.0 (2023-04-21) (R Core Team, 2022).
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
+
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
+The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
+Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
+We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
+
+For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
+For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
+We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
+
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/lifespan_plot}
+
+}
+
+\caption{\textbf{Differentiation in gaze understanding}.
+Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.}\label{fig:fig2}
+\end{figure}
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+Three-year-olds were surprisingly inaccurate in their responses.
+One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze following.
+Contrasting our results with previous findings on infant gaze following, this explanation is unlikely.
+A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
+
+Another point to keep in mind is that we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel, therefore establishing a confound with greater (head) movement.
+Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
+
+The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
+
+\hypertarget{computational-cognitive-model}{%
+\section{Computational cognitive model}\label{computational-cognitive-model}}
+
+\begin{itemize}
+\tightlist
+\item
+  model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
+\item
+  entwicklungsperspektive basierend auf model
+\item
+  dann prozess-ebene = magnet
+\end{itemize}
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
+The sample included the 58 three- to five-year-old children and 240 adults from our Lifespan study. For age distributions, see Participant section of the Lifespan Study.
+
+\hypertarget{non-social-vector-following}{%
+\section{Non-social vector following}\label{non-social-vector-following}}
+
+Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/xsqkt}.
 
@@
 The research adheres to the legal requirements of psychological research with children in Germany.
-
-Participants were equally distributed across the two study versions.
-Data were collected between May and October 2021.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
-In-person testing with children took place in kindergartens in Leipzig, Germany.
-The in-person child sample consisted of 120 children, including 40 3-year-olds (mean = 41.45 months, SD = 3.85, range = 36 - 47, 22 girls), 40 4-year-olds (mean = 54.60 months, SD = 3.10, range = 48 - 59, 19 girls), and 40 5-year-olds (mean = 66.95 months, SD = 3.39, range = 60 - 71, 22 girls).
-
-We pre-registered the replacement for participants that finished fewer than four test trials.
-This was not the case for any participant.
-One child stopped participation after 12 test trials but was included in the sample due to the pre-registered replacement rule.
-Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).
-
-For our remote child sample, we recruited families via an internal database of children living in Leipzig, Germany, whose parents volunteered to participate in child development studies and who indicated an interest in online studies.
-Families received an email with a short study description and a personalized link.
-If they had not participated in the study within two weeks, they received a reminder via email.
-The response rate to invitations after the reminder was \textasciitilde50\%.
-
-The remote child sample included 147 children, including 45 3-year-olds (mean = 42.62 months, SD = 3.35, range = 36 - 47, 14 girls), 47 4-year-olds (mean = 52.64 months, SD = 3.40, range = 48 - 59, 25 girls), and 55 5-year-olds (mean = 65.11 months, SD = 3.77, range = 60 - 71, 27 girls).
-Of these, three families participated twice.
-In these cases, we only kept the data sets from the first participation.
-
-Four additional participants were recruited but not included in the study because they were already part of the in-person kindergarten sample (n=3), or because of unknown age (n = 1).
-
-Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
-They often live in nuclear two-generational families with few household members.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
-The median individual monthly net income in the year 2021 was \textasciitilde{} 1,600€ for the city of Leipzig.
-
-Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
-\emph{Prolific} is an online participant recruitment service with a predominantly European and US-American subject pool.
-100 English-speakers with an average age of 31.34 years (SD = 10.77, range = 18 - 63, 64 females) were included.
-Participants live in a variety of different countries: the UK, Italy, Spain, Poland, Netherlands, Canada, Australia, Ireland, South Africa, Norway, Portugal, France, Austria, Finland, Greece, Germany, the U.S., Mexico, Chile, Iceland, New Zealand, Czech Republic, Hungary, Latvia, and Switzerland.
-In this sample, most participants resided in the United Kingdom (n = 47), South Africa (n = 8), and Portugal (n = 6).
-Additional, detailed information can be found in the data set online.
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-Children in our in-person sample were tested on a tablet in a quiet room in their kindergarten.
-An experimenter guided the child through the study.
-
-Children in the remote sample received a personalized link to the study website, and families could participate at any time or location.
-At the beginning of the online study, families were invited to enter our ``virtual institute''.
-We welcomed them with a short introductory video of the study leader, describing the research background and further procedure.
-Then, caregivers were informed about data security and were asked for their informed consent.
-They were asked to enable the sound and seat their child centrally in front of their device.
-Before the study started, families were instructed on how to set up their webcam and enable the recording permissions.
-We stressed that caregivers should not help their children.
-Study participation was video recorded whenever possible in order to ensure that the children themselves generated the answers.
-Depending on the participant's device, the website automatically presented the hedge or box version of the study.
-For families that used a tablet with a touchscreen, the hedge version was shown.
-Here, children could directly click on the touchscreen to indicate where the target is.
-For families that used a computer without a touchscreen, the website presented the box version of the task.
-We assumed that younger children in our sample would not be acquainted with using a computer mouse.
-Therefore, we asked children to point to the screen, while caregivers were asked to act as the ``digital finger'' of their children and click on the indicated box.
-
-All participants received 15 test trials.
-In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes, while adults were presented with eight boxes as possible target locations.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-All test trials without voice-over descriptions were included in our analyses.
-We ran all analyses in R version 4.2.2 (2022-10-31) (R Core Team, 2022).
-Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
-
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}).\footnote{In the pre-registration (\url{https://osf.io/snju6}), we specified the following model structure: ``All models will include a fixed effect of target centrality and age, a random intercept for ID and a random slope for trial number by ID.
-For both study versions, we will compare the above specified null models with a model including data source (live vs.~online) as a fixed effect.'' Or, in R model formula: \texttt{R:\ performance\ \textasciitilde{}\ target\_centrality\ +\ age\ +\ (1\ \textbar{}\ ID)\ +\ (1\ +\ trial\ \textbar{}\ ID)}.
-  In this paper, we added symmetricPosition (synonymous to target\_centrality) as a random slope because we expected that this item effect could vary between participants.
-  To be better able to interpret trial number effects, we decided to include it as a fixed effect.
-  Data collection mode (formerly named ``data source'') proved as a meaningful predictor and was accordingly added to the model.}
-
-Here, \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
-
-For the hedge version, performance was defined as the absolute click distance between the target center and the click x coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
-For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
-We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_arrangedplot}
-
-}
-
-\caption{\textbf{Measuring inter-individual variation}.
-(A) Developmental trajectory in the continuous hedge version.
-Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
-(B) Internal consistency (odd-even split) in hedge child sample.
-(C) Internal consistency in hedge adult sample.
-(D) Test-retest reliability in hedge child sample.
-(E) Test-retest reliability in hedge adult sample.
-(F) Developmental trajectory in the discrete box version.
-Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
-The dotted black line shows the level of performance expected by chance (for child sample 20\%, i.e., 1 out of 5 boxes; for adult sample 12.5\%, i.e., 1 out of 8 boxes).
-(G) Internal consistency (odd-even split) in box child sample.
-(H) Internal consistency in box adult sample.
-(I) Test-retest reliability in box child sample.
-(J) Test-retest reliability in box adult sample.
-For (A) and (F), regression lines show the predicted developmental trajectories (with 95\% CrI) based on GLMMs, with the line type indicating the data collection mode.
-For (B-E) and (G-J), regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
-Large points with 95\% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year).
-Small points show the mean performance for each subject averaged across trials.
-The shape of data points represents data collection mode: opaque circles for in-person supervised data collection and translucent diamonds for remote unsupervised data collection.
-The color of data points denotes age group.}\label{fig:fig2}
-\end{figure}
-
-Children showed nearly perfect precision in the first training trial.
-As visual access to the target location decreased in the subsequent training trials, imprecision levels increased (see Supplements).
-Within test trials, children's imprecision levels did not vary as a function of trial number.
-We take this as evidence that (A) children were comfortable touching the screen, (B) children understood the task instructions insofar as they aimed at locating the target, and (C) our experimental design successfully manipulated task difficulty.
-
-We found a strong developmental effect: with increasing age, participants got more accurate in locating the target.
-In the hedge version, children's click imprecision decreased with age, while in the box version, the proportion of correct responses increased (see Figure \ref{fig:fig2}A and F).
-Most participants in the box version performed above chance level.
-By the end of their sixth year of life, children came close to the adult's proficiency level.
-Most importantly, however, we found substantial inter-individual variation across study versions and age groups.
-For example, some three-year-olds were more precise in their responses than some five-year-olds.
-Even though variation is smaller, we could even find inter-individual differences in the adult sample.
-
-As Figure \ref{fig:fig2}A and F show, our remotely collected child data resembled the data from the kindergarten sample.
-We found evidence that responses of children participating remotely were slightly more precise.
-This difference was mainly driven by the younger participants and was especially prominent in the box version of the task.
-It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.\footnote{In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-  We focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
-  We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-  Based on our model comparison, we conclude that there is no clear evidence of a stable effect of parental interference.
-  See Supplements for further detail.}
-
-Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age (\(\beta\) = -0.33; 95\% CrI {[}-0.42; -0.24{]}) and data collection mode -0.31 (95\% CrI {[}-0.49; -0.13{]}) were negative and reliably different from zero.
-In the box version, the estimate of age (\(\beta\) =0.69 (95\% CrI {[}0.45; 0.98{]}) and the estimate of data collection mode (\(\beta\) = 1.10 (95\% CrI {[}0.66; 1.56{]}) were positive and reliably different from zero.
-Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in that our remote sample performed more accurately than our in-person sample.
-
-There was no effect of trial number (hedge version: \(\beta\) = 0.00; 95\% CrI {[}-0.02; 0.01{]}; box version: \(\beta\) = -0.02; 95\% CrI {[}-0.05; 0.01).
-However, trials differed in difficulty depending on where the target landed (hedge version: \(\beta\) = 0.32; 95\% CrI {[}0.27; 0.37{]}; box version: \(\beta\) = -1.58; 95\% CrI {[}-1.87; -1.31).
-When the target landed closer to the center of the screen, participants were more accurate in locating it.
-
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-Our task measured inter-individual differences in both children and adults; that is, we found substantial variation in individuals across age groups.
-For example, some three-year-olds showed greater precision levels than some five-year-olds.
-This holds across both study versions.
-However, due to the continuous study design, the hedge version was able to capture more fine-grained differences in individual performance.
-We see substantial developmental gains: with increasing age, participants became on average more and more precise in locating the target.
-The five-year-olds reached a proficiency level close to the adults' level.
-For neither study version nor age group did we find any floor or ceiling effects.
-The presentation as a web app with cartoon-like features kept children interested and motivated throughout the 15 test trials.
-Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample.
-This illustrates the flexibility of the task design.
-
-\hypertarget{internal-consistency-and-test-retest-reliability}{%
-\section{Internal consistency and test-retest reliability}\label{internal-consistency-and-test-retest-reliability}}
-
-As a next step, we aimed to investigate whether the variation that we captured with the TANGO is reliable.
-We assessed internal consistency (as split-half reliability) and test-retest reliability.
-Task procedure, data collection, and sample sizes were pre-registered (\url{https://osf.io/xqm73} for the child sample and \url{https://osf.io/nu62m} for the adult sample).
-Participants were equally distributed across the two study versions.
-Data was collected between July 2021 and June 2022.
-
-The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
-No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
-
-\hypertarget{participants-1}{%
-\subsection{Participants}\label{participants-1}}
-
-Participants were recruited in the same way as in the previous study.
-The child sample consisted of 120 children, including 41 3-year-olds (mean = 42.34 months, SD = 3.10, range = 37 - 47, 20 girls), 41 4-year-olds (mean = 53.76 months, SD = 3.15, range = 48 - 59, 21 girls), and 38 5-year-olds (mean = 66.05 months, SD = 3.40, range = 60 - 71, 19 girls).
-
-Additional 65 children were recruited but not included in the analysis due to absence on the second test day (n = 49), canceled testing because of Covid cases in the kindergarten (n = 7), children did not want to participate a second time (n = 5), children already participated in the first data collection round and were included in the above-mentioned \emph{Individual Differences} sample (n = 3), or children did not understand the task instructions (n = 1; manifested in too early clicking in the training trials while the instructions were still playing, and no clicking by themselves in the test trials).
-Two additional children were recruited for the first day (as backup) in case another child would be absent on the second test day.
-
-The adult sample included 136 English speakers with an average age of 25.73 years (SD = 8.09, range = 18 - 71, 87 females; see Supplements for further details).
-Most participants resided in South Africa (n = 48), the United Kingdom (n = 19), and the United States (n = 14).
-
-\hypertarget{procedure-1}{%
-\subsection{Procedure}\label{procedure-1}}
-
-We applied the same procedure as in the first study, with the following differences.
-Participants completed the study twice, with a delay of 14 ± 3 days.
-The target locations, as well as the succession of agents and target colors, were randomized once and then held constant across participants.
-The child sample received 15 test trials.
-In the hedge version, each bin occurred once, making up ten of the test trials.
-For the remaining five test trials, we repeated one out of two adjacent bins (i.e., randomly chose between bins 1 \& 2, bins 3 \& 4, etc.).
-In the box version, we ensured that each of the five boxes occurred exactly three times during test trials.
-Adults in the hedge version received 30 test trials, each of the ten bins occurring exactly three times.
-Adults in the box version received 32 test trials, with each of the eight boxes occurring exactly four times.
-For the four training trials, we repeated a fixed order of random bins/boxes.
-For the adult sample, we decided to increase the number of trials in order to get more accurate reliability estimates.
-Trial numbers were multipliers of the possible target locations and therefore differed between hedge and box versions.
-For the child sample, we stuck to the same number of trials to not risk higher attrition rates.
-
-\hypertarget{analysis-1}{%
-\subsection{Analysis}\label{analysis-1}}
-
-We assessed reliability in two ways.
-First, we focused on internal consistency by calculating split-half reliability coefficients.\footnote{The assessment of internal consistency was not pre-registered and was included as an additional measure of reliability.}
-For each subject, trials were split into odd and even trials.
-Performance was aggregated and then correlated using \emph{Pearson} coefficients.
-For this, we used the data of the first test day.
-Performance was defined according to each study version: in the hedge version, performance referred to the mean absolute difference between the target center and the click coordinate, scaled according to target widths; in the box version, we computed the mean proportion of correct choices.
-
-Pronk, Molenaar, Wiers, and Murre (2021) recently compared various methods for computing split-half reliability that differ in how the trials are split into parts and whether they are combined with stratification by task design.
-To compare our traditional approach of a simple odd-even split, we additionally calculated split-half reliability estimates using first-second, odd-even, permutated, and Monte Carlo splits without and with stratification by target position.
-First-second and odd-even splits belong to single sample methods since each participant has a single pair of performance scores, while permutated (without replacement) and Monte Carlo (with replacement) splits make use of resampling.
-Analyses were run using the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).
-
-Second, we assessed test-retest reliability.
-We calculated performance scores (depending on the study version as described above) for each participant in each test session and correlated them using \emph{Pearson} correlation coefficients.
-Furthermore, for our child sample, we report an age-corrected correlation between the two test days using a GLMM-based approach (Rouder \& Haaf, 2019).
-We fit trial-by-trial data with a fixed effect of age, a random intercept for each subject, and a random slope for test day (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ (0\ +\ reliday\ \textbar{}\ subjID)}).
-For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function.
-The model computes a correlation between the participant-specific estimates for each test day.
-This can be interpreted as the test-retest reliability.
-By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information.
-Since the model uses hierarchical shrinkage, we obtain regularized, more accurate person-specific estimates.
-Most importantly, the model includes age as a fixed effect.
-The correlation between the two person-specific estimates is consequently the age-independent estimate for test-retest reliability.
-This rules out the possibility that a high correlation between test days arises from domain-general cognitive development instead of study-specific inter-individual differences.
-A high correlation between our participant-specific model estimates would indicate a high association between test days.
-
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
-
-We found that the TANGO measured systematic variation: split-half and test-retest reliability was medium to high.
-For internal consistency, we show traditional odd-even splits on our data and the corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}B, C, G, and H.
-
-Figure \ref{fig:fig3} compares split-half reliability coefficients by splitting and stratification method (Pronk et al., 2021).
-In the hedge version, the split-half reliability coefficients ranged from 0.65 to 0.93.
-In the box version, split-half reliability coefficients ranged from 0.48 to 0.86.
-Similar to the results of Pronk et al. (2021), we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients.
-In most cases, stratifying by target position led to similar or even higher estimates compared to no stratification.
-As expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_splithalf}
-
-}
-
-\caption{\textbf{Internal Consistency}.
-Reliability coefficients per splitting method, stratification level, study version, and age group.
-Error bars show the 95\% confidence intervals of the coefficient estimates, calculated with the function \texttt{by\_split} from the \texttt{splithalfr} package (Pronk et al., 2021).}\label{fig:fig3}
-\end{figure}
-
-For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding \emph{Pearson} correlation coefficients in Figure \ref{fig:fig2}D, E, I and J.\footnote{In the hedge version, we excluded one 3-year-old, one 5-year-old, and two adults from the test-retest analysis.
-  The performance of the mentioned participants was 3 standard deviations above/below the mean of each sample.
-  Including the two children yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.88.
-  Including the two adults yielded a \emph{Pearson} correlation coefficient of \emph{r} = 0.73.}
-See Supplements for reliability estimates by age group.
-
-The age-corrected, GLMM-based retest reliabilities for children yielded similar results.
-In the hedge version, the correlation between test days was 0.89 (95\% CrI {[}0.66;1.00{]}).
-In the box version, the correlation between test days was 0.91 (95\% CrI {[}0.69;1.00{]}).
-
-For both study versions, reliability estimates based on the GLMM approach were higher than the \emph{Pearson} correlations.
-The GLMM-based estimates are less noisy due to the fact that the model uses all available information (e.g., participant age) and does not rely on data aggregation across trials.
-
-\hypertarget{discussion-1}{%
-\subsection{Discussion}\label{discussion-1}}
-
-Our results indicated that the measured variation was systematic.
-As expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version.
-For children, the model-based reliability estimates showed that the task did capture individual differences even when correcting for age.
-This corroborates what we already see in Figure \ref{fig:fig2}: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean but is not the main source of individual differences.
-
-\hypertarget{validity}{%
-\section{Validity}\label{validity}}
-
-After having probed our new testing infrastructure and the psychometric properties of the TANGO task, we aimed at establishing its validity.
-One way to assess validity is to correlate the social-cognitive ability in question to concepts that are thought to be theoretically related.
-Social cognition is often described as developing in response to social interaction(Devine \& Hughes, 2018; Hughes \& Leekam, 2004).
-It is assumed that opportunities to play, communicate and argue with peers help children to understand the human mind.
-Therefore, many studies link social cognition to opportunities for social interaction captured in demographic variables such as parent-child interaction quality and quantity, mental state talk, and center-based childcare (Bulgarelli \& Molina, 2016; Dunn et al., 1991; Pavarini et al., 2013).
-In particular, family constellation, the number and age of siblings, and their interaction have been linked to social cognition (Cassidy, Fineberg, Brown, \& Perkins, 2005; Dunn et al., 1991; Perner, Ruffman, \& Leekam, 1994; Peterson, 2000; Zhang, Yu, Long, \& Li, 2021).
-
-To assess such external validity for out TANGO task, we handed out a brief demographic questionnaire to families of our kindergarten and online child sample and asked for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day.
-109 families filled out the questionnaire and were included in the analysis.
-We used parent's responses to construct different scores suggested in the literature (Cassidy et al., 2005; Peterson, 2000), capturing different aspects of children's opportunity for social interaction with adults and peers.
-Figure \ref{fig:fig4}A shows that all predictor scores are positively linked to gaze understanding.
-Only the \texttt{predictor\ age\ of\ childcare\ entry} improved the model fit compared to the null model (for model comparisons, see Supplements).
-Albeit the effects are weak, they are consistent with the literature.
-
-In addition, children's sensitivity to gaze has been linked to language acquisition (Brooks \& Meltzoff, 2005; Del Bianco et al., 2019; Okumura et al., 2017).
-Discovering the attentional focus of your counterpart is thought to facilitate word learning, for example by identifying the referent of a new word (Tomasello, 2003).
-For 117 children, we also collected data on a receptive vocabulary test (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022) approximately six months (mean = 0.52 years, sd = 0.08, range = 0.06 - 0.80)after their participation in the TANGO task.
-We found a substantial relation between gaze understanding six month prior and receptive vocabulary, even when correcting for age (see Figure \ref{fig:fig4}B and C).
-Taken together, our newly developed task shows connections to external variables and psychological constructs that are characteristic for measures of social cognition.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_vali_arrangedplot}
-
-}
-
-\caption{\textbf{Validity of the TANGO task.} (A) Influence of age of childcare entry on gaze understanding.
-The older the children were when entering childcare, the less likely they are to respond correctly.
-(B) Influence of social-environmental factors on gaze understanding.
-Adding the predictors to the null model did not improve model fit.
-(B) Influence of gaze understanding on receptive vocabulary.
-(C) Influence of gaze understanding on receptive vocabulary by age.
-The regression line with 95\% CI shows a smooth conditional mean based on a linear model, with a \emph{Pearson}'s correlation coefficient \emph{r}.
-Dots show the mean performance for each subject averaged across trials.
-The color of dots denotes age group.
-For (A), (B), and (C), the graphs show the posterior distributions for the respective predictor of each model.
-Black dots represent means, thicker black lines 80\% CI and thinner black lines 95\% CI.}\label{fig:fig4}
-\end{figure}
-
-\hypertarget{general-discussion}{%
-\section{General Discussion}\label{general-discussion}}
-
-We have presented a new experimental paradigm to study gaze understanding across the lifespan.
-This paper contributes to methodological advances in developmental psychology in the following ways: first, we captured fine-grained individual differences in gaze understanding at different ages -- from early childhood until adulthood.
-Individuals behaved consistently differently from one another (i.e., we find substantial variation between individuals across age groups).
-Second, our task showed satisfactory psychometric properties with respect to internal consistency and retest reliability estimates.
-Third, our new browser-based testing infrastructure ensures standardized, portable data collection at scale, both remotely as well as in person.
-In sum, the TANGO provides a step toward more robust and reliable research methods, especially with regard to measuring a developmental change in fundamental social-cognitive abilities.
-The web app (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) and its source code (\url{https://github.com/ccp-eva/tango-demo}) are freely accessible for use and modification.
-
-Our continuous measure of children's gaze understanding moves away from treating a social-cognitive ability as an all-or-nothing matter (e.g., dichotomous measures in pass/fail situations) toward an ability on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
-Identifying variability in social-cognitive abilities is vital for accurately quantifying developmental change, revealing relations between different aspects of cognition and children's real-life social surroundings, and for meaningful comparisons across human cultures and across animal species.
-Dedicated measures of individual differences will help us to design meaningful interventions and progress in psychological theory building (Hedge et al., 2018).
-
-Our continuous hedge version yields higher internal consistency estimates than the categorical box version.
-Both study versions exhibit high retest reliability, also when controlling for age.
-Therefore, when a sufficient number of trials is presented, the box version of the task can also yield reliable individual estimates (cf.
-Hughes et al.
-(2000); improved reliability through aggregation).
-When testing time is limited (and the number of trials might be low), we recommend using the continuous study version for higher internal consistency.
-However, the categorical box version demonstrates design features that might be preferable in some research contexts: for example, researchers could induce different levels of salience for each box.
-Our task could consequently be used to study bias, preferences, and diverse desires (e.g., matching the box appearance to some feature/behavioral characteristic of the agent).
-
-In the split-half reliability calculations, the more accurately the statistical method represents the task structure, the higher the reliability estimates are.
-Therefore, we argue that future research should aim at implementing statistical analyses that mirror the complexity of the experimental design.
-Theoretically informed, computational cognitive models are a promising approach forward (Haines et al., 2020).
-Computational models take advantage of all available information and model variation between and within individuals in an even more fine-grained and psychologically interpretable manner.
-Computational frameworks could also be used to model performance and their underlying cognitive processes across tasks.
-With nested hierarchical models, we could assess the systematic relation between various social-cognitive abilities and recover potentially shared structures between cognitive processes (Bohn, Tessler, Kordt, Hausmann, \& Frank, 2022).
-
-The TANGO fulfills several demands that were proposed by Schaafsma et al.
-(2015)'s wish list: it measures proficiency on a continuum, avoids floor and ceiling effects, measures variation across age ranges, shows satisfactory reliability estimates, and has a high face value.
-
-In addition to the new task design itself, we designed a new testing infrastructure.
-The TANGO is presented as an interactive web app.
-This enables presentation across devices without any prior installation.
-Stimuli presentation is achieved through the use of SVGs.
-This has several advantages: the aspect ratio and stimulus quality are kept constant no matter which size the web browser displays.
-The cartoon-like presentation makes the task engaging for children and adults alike.
-Most importantly, we can dynamically modify the stimulus details (e.g., target positions) on a trial-by-trial basis.
-Presented agents, voice-over instructions, and objects can be easily adapted for future task modifications or specific linguistic and cultural settings.
-
-The browser-based implementation allows for different data collection modes: participants can be tested in person with supervision or remotely at home.
-Test instructions are standardized, and with prior informed consent, the webcam records study participation.
-This allows us to scale up data collection: testing is flexible, fast, and requires no further experimenter training.
-We compared children participating in-person and supervised in kindergartens with children who participated remotely at home.
-Our results suggest a comparable developmental trajectory of gaze understanding in both samples.
-Children in the remote sample were slightly more precise.
-This effect was most pronounced in the three-year-olds in the box version (for an analysis of the webcam recordings, see Supplements).
-Therefore, we recommend using a tablet for remote data collection.
-Children can click for themselves, and caregivers have less chance to interfere.
-The design choices of the infrastructure underline how our study design can act as a versatile framework for addressing further research questions on social-cognitive development.
-
-With respect to validity, we found that performance in the TANGO task was related to relevant external variables and cognitive measures.
-Family-level variables, capturing a child's opportunity for social interaction, systematically influenced gaze understanding.
-Even though the effects were small and confidence intervals were wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real-life variables.
-In addition, we assessed the influence of gaze understanding on receptive vocabulary.
-We found a substantial relationship between the two variables, even when correcting for age.
-Taken together, this speaks to the validity of our TANGO task.
+Data were collected between February and March 2023.
+
+\hypertarget{participants-2}{%
+\subsection{Participants}\label{participants-2}}
+
+The sample consisted of 102 children (mean age = 4.54 years, SD = 0.31, range = 3.99 - 5.03, 54 girls),
+
+\begin{itemize}
+\item
+  gut, dass unser maß ind diff messen kann, das nutzen wir jetzt
+\item
+  zsmhang mit vector following, aber nicht redundant
+\item
+  perspective-taking auch, aber auch nicht relevant, nicht theory of mind score
+\item
+  diskutieren dass die maße auch nict ind diff maße sind
+\item
+  model vergleich: welche komponente stecken in gafo drin?,
+  welchen beitrag liefern die um score zu erklären?
+  welche wichtiger, tom oder nur perspective taking
+\item
+  magnet versuch das vector following zu isolieren.
+  ist da noch was anderes außerhalb vector-following?
+\item
+  aggregierte messungen immer besser, nur indikatoren für konstrukt
+\end{itemize}
 
@@
 
-First, we want to address the scope and interpretation of the TANGO task.
-We believe that solving the task requires locating the attentional focus of an agent as the gaze cues the target location.
-This speaks to the face validity of the TANGO task and its focus on an inherently social stimulus.
-However, we do not want to claim that the TANGO task does not also recruit other, domain general processes.
-For example, we believe that a considerable part of gaze understanding relies on vector-following: not just in our task but also in real life.
-From that perspective, gaze understanding could be seen as a particular case of vector-following that is learned and used in social interactions.
-Future research could assess how much variation of the gaze understanding task is shared with a physical vector-following task.
-In addition, computational cognitive models might prove helpful in defining children's behavior on a process-level and disentangling parameters that influence task performance (e.g., spatial acuity).
-
-Second, the influence of testing modality requires further attention.
-Remote data collection loosens the standardization of the experimental procedure, as we cannot prevent caregivers from interfering.
-Steering the child's behavior becomes less possible when touchscreens are used, and the child can click on the screen directly.
-This is why we recommend using tablets for remote data collection.
-However, it should be noted that families' access to technological devices varies, both across socio-environmental as well as cultural settings.
-
-Finally, we utilized subtle gaze cues in order to increase difficulty and capture individual differences.
-However, in real-life settings, children could be more accustomed to a combination of head and eye orientation changes, and subtle gaze differences might be less common.
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
 
@@
 
-We have presented a new experimental paradigm to study gaze understanding across the lifespan.
-The TANGO captures individual differences and shows highly satisfactory psychometric properties with respect to internal consistency and retest reliability.
-The browser-based testing infrastructure allows for standardized, portable data collection at scale, both remotely as well as in person.
-Ultimately, this work shows a promising way forward toward more precise measures of cognitive development.
-The data sets and the analysis code are freely available in the associated online repository (\url{https://github.com/ccp-eva/gazecues-methods}).
-A demo version of the task is available at the following website (see Figure \ref{fig:fig5}): \url{https://ccp-odc.eva.mpg.de/tango-demo/}.
-The code base and respective assets can be accessed in the following repository: \url{https://github.com/ccp-eva/tango-demo}.
-These resources allow interested researchers to use, extend and adapt the task.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_demo_screenshot}
-
-}
-
-\caption{\textbf{TANGO demo website.} We want to highlight that researchers are welcome to use and modify our task according to their needs.
-The number of training and test trials and the number of boxes can be adjusted within the JavaScript code, while agents and targets can be exchanged within the HTML code.}\label{fig:fig5}
-\end{figure}
-
 \newpage
@@
 The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
-The data sets generated during and/or analysed during the current study are available in the {[}gazecues-methods{]} repository (\url{https://github.com/jprein/gazecues-methods}).
+The data sets generated during and/or analysed during the current study are available in the {[}gazecues-modeling{]} repository (\url{https://github.com/ccp-eva/gazecues-modeling}).
 All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
@@
 
-The authors made the following contributions.
-Julia Prein: Conceptualization, Software, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Steven Kalinke: Software, Writing - Review \& Editing; Daniel Haun: Conceptualization, Writing - Review \& Editing.
+The authors made the following contributions: \#\#\# TODO
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
-Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., \ldots{} Gredebäck, G.
-(2020).
-Social and emotional contexts predict the development of gaze following in early infancy.
-\emph{Royal Society Open Science}, \emph{7}(9), 201178.
-\url{https://doi.org/10.1098/rsos.201178}
-
-\leavevmode\vadjust pre{\hypertarget{ref-astor2021gaze}{}}%
-Astor, K., Thiele, M., \& Gredebäck, G.
-(2021).
-Gaze following emergence relies on both perceptual cues and social awareness.
-\emph{Cognitive Development}, \emph{60}, 101121.
-\url{https://doi.org/10.1016/j.cogdev.2021.101121}
-
-\leavevmode\vadjust pre{\hypertarget{ref-baron-cohen1985does}{}}%
-Baron-Cohen, S., Leslie, A. M., \& Frith, U. (1985). Does the autistic child have a "theory of mind" ? \emph{Cognition}, \emph{21}, 37--46. \url{https://doi.org/10.1016/0010-0277(85)90022-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-barrett2013early}{}}%
-Barrett, H.
-C., Broesch, T., Scott, R.
-M., He, Z., Baillargeon, R., Wu, D., \ldots{} Laurence, S.
-(2013).
-Early false-belief understanding in traditional non-{Western} societies.
-\emph{Proceedings of the Royal Society B: Biological Sciences}.
-\url{https://doi.org/10.1098/rspb.2012.2654}
-
-\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
-Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M.
-H.
-(2020).
-Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}.
-\emph{Frontiers in Psychology}, \emph{0}.
-\url{https://doi.org/10.3389/fpsyg.2019.02905}
-
-\leavevmode\vadjust pre{\hypertarget{ref-begeer2012continuous}{}}%
-Begeer, S., Bernstein, D.
-M., van Wijhe, J., Scheeren, A.
-M., \& Koot, H.
-M.
-(2012).
-A continuous false belief task reveals egocentric biases in children and adolescents with {Autism Spectrum Disorders}.
-\emph{Autism}, \emph{16}(4), 357--366.
-\url{https://doi.org/10.1177/1362361311434545}
-
-\leavevmode\vadjust pre{\hypertarget{ref-benson2012individual}{}}%
-Benson, J., Sabbagh, M., Carlson, S., \& Zelazo, P.
-(2012).
-Individual {Differences} in {Executive Functioning Predict Preschoolers}' {Improvement From Theory-of-Mind Training}.
-\emph{Developmental Psychology}, \emph{49}.
-\url{https://doi.org/10.1037/a0031056}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bernstein2011theory}{}}%
-Bernstein, D.
-M., Thornton, W.
-L., \& Sommerville, J.
-A.
-(2011).
-Theory of {Mind Through} the {Ages}: {Older} and {Middle-Aged Adults Exhibit More Errors Than Do Younger Adults} on a {Continuous False Belief Task}.
-\emph{Experimental Aging Research}, \emph{37}(5), 481--502.
-\url{https://doi.org/10.1080/0361073X.2011.619466}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
-Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2021children}{}}%
-Bohn, M., Le, K.
-N., Peloquin, B., Köymen, B., \& Frank, M.
-C.
-(2021).
-Children's interpretation of ambiguous pronouns based on prior discourse.
-\emph{Developmental Science}, \emph{24}(3), e13049.
-\url{https://doi.org/10.1111/desc.13049}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
-Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2022individual}{}}%
-Bohn, M., Tessler, M.
-H., Kordt, C., Hausmann, T., \& Frank, M.
-C.
+\leavevmode\vadjust pre{\hypertarget{ref-astor2022gaze}{}}%
+Astor, K., \& Gredebäck, G.
 (2022).
-\emph{An individual differences perspective on the development of pragmatic abilities in the preschool years}.
-{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/s2e3p}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2021how}{}}%
-Bohn, M., Tessler, M.
-H., Merrick, M., \& Frank, M.
-C.
-(2021).
-How young children integrate information sources to infer the meaning of words.
-\emph{Nature Human Behaviour}, \emph{5}(8), 1046--1054.
-\url{https://doi.org/10.1038/s41562-021-01145-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
+Gaze following in infancy: {Five} big questions that the field should answer.
+In \emph{Advances in {Child Development} and {Behavior}} (p.
+S0065240722000192).
+{Elsevier}.
+\url{https://doi.org/10.1016/bs.acdb.2022.04.003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-behne2005oneyearolds}{}}%
+Behne, T., Carpenter, M., \& Tomasello, M.
+(2005).
+One-year-olds comprehend the communicative intentions behind gestures in a hiding game.
+\emph{Developmental Science}, \emph{8}(6), 492--499.
+\url{https://doi.org/10.1111/j.1467-7687.2005.00440.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brooks2002importance}{}}%
 Brooks, R., \& Meltzoff, A.
 N.
-(2005).
-The development of gaze following and its relation to language.
-\emph{Developmental Science}, \emph{8}(6), 535--543.
-\url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bulgarelli2016social}{}}%
-Bulgarelli, D., \& Molina, P.
-(2016).
-Social {Cognition} in {Preschoolers}: {Effects} of {Early Experience} and {Individual Differences}.
-\emph{Frontiers in Psychology}, \emph{7}.
-\url{https://doi.org/10.3389/fpsyg.2016.01762}
+(2002).
+The importance of eyes: {How} infants interpret adult looking behavior.
+\emph{Developmental Psychology}, \emph{38}(6), 958--966.
+\url{https://doi.org/10.1037/0012-1649.38.6.958}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buttelmann2021relations}{}}%
-Buttelmann, D., Kühn, K., \& Zmyj, N.
-(2021).
-The {Relations} among {Theory} of {Mind}, {Inhibitory Control}, and {Aggressive Behavior} in 4-{Year-Old Children} \textendash{} {A Multi-Measure Multi-Informant Approach}.
-\emph{Journal of Cognition and Development}, \emph{0}(0), 1--24.
-\url{https://doi.org/10.1080/15248372.2021.1987240}
-
-\leavevmode\vadjust pre{\hypertarget{ref-byers-heinlein2021development}{}}%
-Byers-Heinlein, K., Tsui, R.
-K.-Y., van Renswoude, D., Black, A.
-K., Barr, R., Brown, A., \ldots{} Singh, L.
-(2021).
-The development of gaze following in monolingual and bilingual infants: {A} multi-laboratory study.
-\emph{Infancy}, \emph{26}(1), 4--38.
-\url{https://doi.org/10.1111/infa.12360}
-
-\leavevmode\vadjust pre{\hypertarget{ref-callaghan2005synchrony}{}}%
-Callaghan, T., Rochat, P., Lillard, A., Claux, M.
-L., Odden, H., Itakura, S., \ldots{} Singh, S.
-(2005).
-Synchrony in the onset of mental-state reasoning: {Evidence} from five cultures.
-\emph{Psychological Science}.
-\url{https://doi.org/10.1111/j.0956-7976.2005.01544.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carlson2001individual}{}}%
-Carlson, S., \& Moses, L.
-J.
-(2001).
-Individual {Differences} in {Inhibitory Control} and {Children}'s {Theory} of {Mind}.
-\emph{Child Development}, \emph{72}(4), 1032--1053.
-Retrieved from \url{https://www.jstor.org/stable/1132428}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
-Carlson, S., Moses, L.
-J., \& Claxton, L.
-J.
-(2004).
-Individual differences in executive functioning and theory of mind: {An} investigation of inhibitory control and planning ability.
-\emph{Journal of Experimental Child Psychology}, \emph{87}(4), 299--319.
-\url{https://doi.org/10.1016/j.jecp.2004.01.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
-Cassidy, K.
-W., Fineberg, D.
-S., Brown, K., \& Perkins, A.
-(2005).
-Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}.
-\emph{Child Development}, \emph{76}(1), 97--106.
-Retrieved from \url{https://www.jstor.org/stable/3696711}
-
-\leavevmode\vadjust pre{\hypertarget{ref-coburn2015new}{}}%
-Coburn, P.
-I., Bernstein, D.
-M., \& Begeer, S.
-(2015).
-A new paper and pencil task reveals adult false belief reasoning bias.
-\emph{Psychological Research}, \emph{79}(5), 739--749.
-\url{https://doi.org/10.1007/s00426-014-0606-0}
+\leavevmode\vadjust pre{\hypertarget{ref-butterworth1991minds}{}}%
+Butterworth, G., \& Jarrett, N.
+(1991).
+What minds have in common is space: {Spatial} mechanisms serving joint visual attention in infancy.
+\emph{British Journal of Developmental Psychology}, \emph{9}(1), 55--72.
+\url{https://doi.org/10.1111/j.2044-835X.1991.tb00862.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
+Carpenter, M., Nagell, K., \& Tomasello, M.
+(1998).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/9835078}{Social cognition, joint attention, and communicative competence from 9 to 15 months of age}.
+\emph{Monographs of the Society for Research in Child Development}, \emph{63}(4), i--vi, 1--143.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cutting1999theory}{}}%
-Cutting, A.
-L., \& Dunn, J.
-(1999).
-Theory of {Mind}, {Emotion Understanding}, {Language}, and {Family Background}: {Individual Differences} and {Interrelations}.
-\emph{Child Development}, \emph{70}(4), 853--865.
-\url{https://doi.org/10.1111/1467-8624.00061}
-
-\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
-Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G.
-(2019).
-The {Developmental Origins} of {Gaze-Following} in {Human Infants}.
-\emph{Infancy}, \emph{24}(3), 433--454.
-\url{https://doi.org/10.1111/infa.12276}
-
-\leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
-Devine, R.
-T., \& Hughes, C.
-(2018).
-Family {Correlates} of {False Belief Understanding} in {Early Childhood}: {A Meta-Analysis}.
-\emph{Child Development}, \emph{89}(3), 971--987.
-\url{https://doi.org/10.1111/cdev.12682}
-
-\leavevmode\vadjust pre{\hypertarget{ref-dunn1991young}{}}%
-Dunn, J., Brown, J., Slomkowski, C., Tesla, C., \& Youngblade, L.
-(1991).
-\href{https://www.ncbi.nlm.nih.gov/pubmed/1786720}{Young children's understanding of other people's feelings and beliefs: Individual differences and their antecedents}.
-\emph{Child Development}, \emph{62}(6), 1352--1366.
-
-\leavevmode\vadjust pre{\hypertarget{ref-frank2016using}{}}%
-Frank, M.
-C., Sugarman, E., Horowitz, A.
-C., Lewis, M.
-L., \& Yurovsky, D.
-(2016).
-Using {Tablets} to {Collect Data From Young Children}.
-\emph{Journal of Cognition and Development}, \emph{17}(1), 1--17.
-\url{https://doi.org/10.1080/15248372.2015.1061528}
+\leavevmode\vadjust pre{\hypertarget{ref-colombo2001development}{}}%
+Colombo, J. (2001). The development of visual attention in infancy. \emph{Annual Review of Psychology}, \emph{52}, 337--367. \url{https://doi.org/10.1146/annurev.psych.52.1.337}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dentremont1997demonstration}{}}%
+D'Entremont, B., Hains, S.
+M.
+J., \& Muir, D.
+W.
+(1997).
+A demonstration of gaze following in 3- to 6-month-olds.
+\emph{Infant Behavior and Development}, \emph{20}(4), 569--572.
+\url{https://doi.org/10.1016/S0163-6383(97)90048-5}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gola2012mental}{}}%
-Gola, A.
-A.
-H.
-(2012).
-Mental verb input for promoting children's theory of mind: {A} training study.
-\emph{Cognitive Development}, \emph{27}(1), 64--76.
-\url{https://doi.org/10.1016/j.cogdev.2011.10.003}
-
-\leavevmode\vadjust pre{\hypertarget{ref-gopnik1991young}{}}%
-Gopnik, A., \& Slaughter, V. (1991). Young {Children}'s {Understanding} of {Changes} in {Their Mental States}. \emph{Child Development}, \emph{62}(1), 98. \url{https://doi.org/10.2307/1130707}
-
-\leavevmode\vadjust pre{\hypertarget{ref-haines2020theoretically}{}}%
-Haines, N., Kvam, P.
-D., Irving, L.
-H., Smith, C., Beauchaine, T.
-P., Pitt, M.
-A., \ldots{} Turner, B.
-M.
-(2020).
-\emph{Theoretically {Informed Generative Models Can Advance} the {Psychological} and {Brain Sciences}: {Lessons} from the {Reliability Paradox}}.
-{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/xr7y3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-happe2017structure}{}}%
-Happé, F., Cook, J.
-L., \& Bird, G.
-(2017).
-The {Structure} of {Social Cognition}: {In}(ter)dependence of {Sociocognitive Processes}.
-\emph{Annual Review of Psychology}, \emph{68}(1), 243--267.
-\url{https://doi.org/10.1146/annurev-psych-010416-044046}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hedge2018reliability}{}}%
-Hedge, C., Powell, G., \& Sumner, P.
-(2018).
-The reliability paradox: {Why} robust cognitive tasks do not produce reliable individual differences.
-\emph{Behavior Research Methods}, \emph{50}(3), 1166--1186.
-\url{https://doi.org/10.3758/s13428-017-0935-1}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infant}{}}%
-Hernik, M., \& Broesch, T.
-(2019).
-Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}.
-\emph{Developmental Science}, \emph{22}(4), e12779.
-\url{https://doi.org/10.1111/desc.12779}
-
-\leavevmode\vadjust pre{\hypertarget{ref-herrmann2010structure}{}}%
-Herrmann, E., Hernández-Lloreda, M.
-V., Call, J., Hare, B., \& Tomasello, M.
-(2010).
-The {Structure} of {Individual Differences} in the {Cognitive Abilities} of {Children} and {Chimpanzees}.
-\emph{Psychological Science}, \emph{21}(1), 102--110.
-\url{https://doi.org/10.1177/0956797609356511}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2000good}{}}%
-Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A.
-(2000).
-Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}.
-\emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490.
-\url{https://doi.org/10.1111/1469-7610.00633}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2015individual}{}}%
-Hughes, C., \& Devine, R.
-T.
-(2015).
-Individual {Differences} in {Theory} of {Mind From Preschool} to {Adolescence}: {Achievements} and {Directions}.
-\emph{Child Development Perspectives}, \emph{9}(3), 149--153.
-\url{https://doi.org/10.1111/cdep.12124}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2007executive}{}}%
-Hughes, C., \& Ensor, R.
-(2007).
-Executive function and theory of mind: {Predictive} relations from ages 2 to 4.
-\emph{Developmental Psychology}, \emph{43}(6), 1447--1459.
-\url{https://doi.org/10.1037/0012-1649.43.6.1447}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2011individual}{}}%
-Hughes, C., Ensor, R., \& Marks, A.
-(2011).
-Individual differences in false belief understanding are stable from 3 to 6 years of age and predict children's mental state talk with school friends.
-\emph{Journal of Experimental Child Psychology}, \emph{108}(1), 96--112.
-\url{https://doi.org/10.1016/j.jecp.2010.07.012}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hughes2004links}{}}%
-Hughes, C., \& Leekam, S.
-(2004).
-What are the {Links Between Theory} of {Mind} and {Social Relations}?
-{Review}, {Reflections} and {New Directions} for {Studies} of {Typical} and {Atypical Development}.
-\emph{Social Development}, \emph{13}(4), 590--619.
-\url{https://doi.org/10.1111/j.1467-9507.2004.00285.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-imuta2016theory}{}}%
-Imuta, K., Henry, J.
-D., Slaughter, V., Selcuk, B., \& Ruffman, T.
-(2016).
-Theory of mind and prosocial behavior in childhood: {A} meta-analytic review.
-\emph{Developmental Psychology}, \emph{52}(8), 1192--1205.
-\url{https://doi.org/10.1037/dev0000140}
-
 \leavevmode\vadjust pre{\hypertarget{ref-itakura1998use}{}}%
@@
 \url{https://doi.org/10.1037/0735-7036.112.2.119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
-Kidd, E., Donnelly, S., \& Christiansen, M.
-H.
-(2018).
-Individual {Differences} in {Language Acquisition} and {Processing}.
-\emph{Trends in Cognitive Sciences}, \emph{22}(2), 154--169.
-\url{https://doi.org/10.1016/j.tics.2017.11.006}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lecce2014promoting}{}}%
-Lecce, S., Bianco, F., Devine, R.
-T., Hughes, C., \& Banerjee, R.
-(2014).
-Promoting theory of mind during middle childhood: {A} training program.
-\emph{Journal of Experimental Child Psychology}, \emph{126}, 52--67.
-\url{https://doi.org/10.1016/j.jecp.2014.03.002}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-macdonald2013eye}{}}%
-Macdonald, R.
-G., \& Tatler, B.
-W.
-(2013).
-Do as eye say: {Gaze} cueing and language in a real-world social interaction.
-\emph{Journal of Vision}, \emph{13}(4), 6--6.
-\url{https://doi.org/10.1167/13.4.6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mahy2017testing}{}}%
-Mahy, C.
-E.
-V., Bernstein, D.
-M., Gerrard, L.
-D., \& Atance, C.
-M.
-(2017).
-Testing the validity of a continuous false belief task in 3- to 7-year-old children.
-\emph{Journal of Experimental Child Psychology}, \emph{160}, 50--66.
-\url{https://doi.org/10.1016/j.jecp.2017.03.010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayer2015weird}{}}%
-Mayer, A., \& Träuble, B.
-(2015).
-The weird world of cross-cultural false-belief research: {A} true- and false-belief study among samoan children based on commands.
-\emph{Journal of Cognition and Development}, \emph{16}(4), 650--665.
-\url{https://doi.org/10.1080/15248372.2014.926273}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mayes1996testretest}{}}%
-Mayes, L.
-C., Klin, A., Tercyak, K.
-P., Cicchetti, D.
-V., \& Cohen, D.
-J.
-(1996).
-Test-{Retest Reliability} for {False-Belief Tasks}.
-\emph{Journal of Child Psychology and Psychiatry}, \emph{37}(3), 313--319.
-\url{https://doi.org/10.1111/j.1469-7610.1996.tb01408.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
-McEwen, F., Happé, F., Bolton, P., Rijsdijk, F., Ronald, A., Dworzynski, K., \& Plomin, R.
-(2007).
-Origins of individual differences in imitation: Links with language, pretend play, and socially insightful behavior in two-year-old twins.
-\emph{Child Development}, \emph{78}(2), 474--492.
-\url{https://doi.org/10.1111/j.1467-8624.2007.01010.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-milligan2007language}{}}%
-Milligan, K., Astington, J.
-W., \& Dack, L.
-A.
-(2007).
-Language and {Theory} of {Mind}: {Meta-Analysis} of the {Relation Between Language Ability} and {False-belief Understanding}.
-\emph{Child Development}, \emph{78}(2), 622--646.
-\url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-molleman2019unleashing}{}}%
-Molleman, L., Kurvers, R.
-H.
-J.
-M., \& van den Bos, W.
-(2019).
-Unleashing the {BEAST}: A brief measure of human social information use.
-\emph{Evolution and Human Behavior}, \emph{40}(5), 492--499.
-\url{https://doi.org/10.1016/j.evolhumbehav.2019.06.005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
-Moore, C. (2008). The {Development} of {Gaze Following}. \emph{Child Development Perspectives}, \emph{2}(2), 66--70. \url{https://doi.org/10.1111/j.1750-8606.2008.00052.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mundy2007individual}{}}%
-Mundy, P., Block, J., Delgado, C., Pomares, Y., Van Hecke, A.
-V., \& Parlade, M.
-V.
-(2007).
-Individual differences and the development of joint attention in infancy.
-\emph{Child Development}, \emph{78}(3), 938--954.
-\url{https://doi.org/10.1111/j.1467-8624.2007.01042.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-okumura2017individual}{}}%
-Okumura, Y., Kanakogi, Y., Kobayashi, T., \& Itakura, S.
-(2017).
-Individual differences in object-processing explain the relationship between early gaze-following and later language development.
-\emph{Cognition}, \emph{166}, 418--424.
-\url{https://doi.org/10.1016/j.cognition.2017.06.005}
+\leavevmode\vadjust pre{\hypertarget{ref-moll200412}{}}%
+Moll, H., \& Tomasello, M.
+(2004).
+12- and 18-month-old infants follow gaze to spaces behind barriers.
+\emph{Developmental Science}, \emph{7}(1), F1--F9.
+\url{https://doi.org/10.1111/j.1467-7687.2004.00315.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore1997role}{}}%
+Moore, C., Angelopoulos, M., \& Bennett, P.
+(1997).
+The role of movement in the development of joint visual attention.
+\emph{Infant Behavior and Development}, \emph{20}(1), 83--92.
+\url{https://doi.org/10.1016/S0163-6383(97)90063-1}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pavarini2013parental}{}}%
-Pavarini, G., de Hollanda Souza, D., \& Hawk, C.
-K.
-(2013).
-Parental {Practices} and {Theory} of {Mind Development}.
-\emph{Journal of Child and Family Studies}, \emph{22}(6), 844--853.
-\url{https://doi.org/10.1007/s10826-012-9643-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
-Perner, J., Ruffman, T., \& Leekam, S.
-R.
-(1994).
-Theory of {Mind Is Contagious}: {You Catch It} from {Your Sibs}.
-\emph{Child Development}, \emph{65}(4), 1228--1238.
-\url{https://doi.org/10.2307/1131316}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
-Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2012mind}{}}%
-Peterson, Wellman, H.
-M., \& Slaughter, V.
-(2012).
-The {Mind Behind} the {Message}: {Advancing Theory-of-Mind Scales} for {Typically Developing Children}, and {Those With Deafness}, {Autism}, or {Asperger Syndrome}: {\textbf{The Mind Behind}}{ \textbf{the} }{\textbf{Message}}.
-\emph{Child Development}, \emph{83}(2), 469--485.
-\url{https://doi.org/10.1111/j.1467-8624.2011.01728.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-poulin-dubois2023discontinuity}{}}%
-Poulin-Dubois, D., Goldman, E.
-J., Meltzer, A., \& Psaradellis, E.
-(2023).
-Discontinuity from implicit to explicit theory of mind from infancy to preschool age.
-\emph{Cognitive Development}, \emph{65}, 101273.
-\url{https://doi.org/10.1016/j.cogdev.2022.101273}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pronk2021methods}{}}%
-Pronk, T., Molenaar, D., Wiers, R.
-W., \& Murre, J.
-(2021).
-Methods to split cognitive task data for estimating split-half reliability: {A} comprehensive review and systematic assessment.
-\emph{Psychonomic Bulletin \& Review}.
-\url{https://doi.org/10.3758/s13423-021-01948-3}
+\leavevmode\vadjust pre{\hypertarget{ref-povinelli1997exploitation}{}}%
+Povinelli, D.
+J., Reaux, J.
+E., Bierschwale, D.
+T., Allain, A.
+D., \& Simon, B.
+B.
+(1997).
+Exploitation of pointing as a referential gesture in young children, but not adolescent chimpanzees.
+\emph{Cognitive Development}, \emph{12}(4), 423--461.
+\url{https://doi.org/10.1016/S0885-2014(97)90017-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-prein2022tango}{}}%
+Prein, J.
+C., Bohn, M., Kalinke, S., \& Haun, D.
+B.
+M.
+(2022).
+\emph{{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/vghw8}
 
@@
 R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
-Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, 1--13. \url{https://doi.org/10.1038/s44159-022-00037-z}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-repacholi2003introduction}{}}%
-Repacholi, V. S. \&. B. (2003). Introduction {Individual Differences} in {Theory} of {Mind}: {What Are We Investigating}? In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rizzo2018theory}{}}%
-Rizzo, M.
-T., \& Killen, M.
-(2018).
-Theory of mind is related to children's resource allocations in gender stereotypic contexts.
-\emph{Developmental Psychology}, \emph{54}(3), 510.
-\url{https://doi.org/10.1037/dev0000439}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rouder2019psychometrics}{}}%
-Rouder, J.
-N., \& Haaf, J.
-M.
-(2019).
-A psychometrics of individual differences in experimental tasks.
-\emph{Psychonomic Bulletin \& Review}, \emph{26}(2), 452--467.
-\url{https://doi.org/10.3758/s13423-018-1558-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-samuel2018egocentric}{}}%
-Samuel, S., Legg, E.
-W., Lurz, R., \& Clayton, N.
-S.
-(2018a).
-Egocentric bias across mental and non-mental representations in the {Sandbox Task}.
-\emph{Quarterly Journal of Experimental Psychology}, \emph{71}(11), 2395--2410.
-\url{https://doi.org/10.1177/1747021817742367}
-
-\leavevmode\vadjust pre{\hypertarget{ref-samuel2018unreliability}{}}%
-Samuel, S., Legg, E.
-W., Lurz, R., \& Clayton, N.
-S.
-(2018b).
-The unreliability of egocentric bias across self\textendash other and memory\textendash belief distinctions in the {Sandbox Task}.
-\emph{Royal Society Open Science}, \emph{5}(11), 181355.
-\url{https://doi.org/10.1098/rsos.181355}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schaafsma2015deconstructing}{}}%
-Schaafsma, S.
-M., Pfaff, D.
-W., Spunt, R.
-P., \& Adolphs, R.
-(2015).
-Deconstructing and reconstructing theory of mind.
-\emph{Trends in Cognitive Sciences}, \emph{19}(2), 65--72.
-\url{https://doi.org/10.1016/j.tics.2014.11.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-shepherd2010following}{}}%
-Shepherd, S. (2010). Following {Gaze}: {Gaze-Following Behavior} as a {Window} into {Social Cognition}. \emph{Frontiers in Integrative Neuroscience}, \emph{4}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-slaughter2015theorya}{}}%
-Slaughter, V. (2015). Theory of {Mind} in {Infants} and {Young Children}: {A Review}. \emph{Australian Psychologist}, \emph{50}(3), 169--172. \url{https://doi.org/10.1111/ap.12080}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sodian2023reply}{}}%
-Sodian, B.
-(2023).
-Reply to {Poulin-Dubois} et al.
-(2023): {Replication} problems concerning both implicit and explicit false belief reasoning greatly reduced the chance of finding longitudinal correlations.
-\emph{Cognitive Development}, \emph{65}, 101294.
-\url{https://doi.org/10.1016/j.cogdev.2022.101294}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
-Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A.
-(2016).
-Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}.
-\emph{Child Development}, \emph{87}(4), 1221--1232.
-\url{https://doi.org/10.1111/cdev.12533}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sommerville2013measuring}{}}%
-Sommerville, J.
-A., Bernstein, D.
-M., \& Meltzoff, A.
-N.
-(2013).
-Measuring {Beliefs} in {Centimeters}: {Private Knowledge Biases Preschoolers}' and {Adults}' {Representation} of {Others}' {Beliefs}.
-\emph{Child Development}, \emph{84}(6), 1846--1854.
-\url{https://doi.org/10.1111/cdev.12110}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003constructing}{}}%
-Tomasello, M. (2003). \emph{Constructing a language: {A} usage-based theory of language acquisition} (pp. viii, 388). {Cambridge, MA, US}: {Harvard University Press}.
+\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
+Scaife, M., \& Bruner, J. S. (1975). The capacity for joint visual attention in the infant. \emph{Nature}, \emph{253}(5489), 265--266. \url{https://doi.org/10.1038/253265a0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-silverstein2021infants}{}}%
+Silverstein, P., Feng, J., Westermann, G., Parise, E., \& Twomey, K.
+E.
+(2021).
+Infants {Learn} to {Follow Gaze} in {Stages}: {Evidence Confirming} a {Robotic Prediction}.
+\emph{Open Mind}, \emph{5}, 174--188.
+\url{https://doi.org/10.1162/opmi_a_00049}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-underwood1975individual}{}}%
-Underwood, B. J. (1975). Individual differences as a crucible in theory construction. \emph{American Psychologist}, \emph{30}(2), 128--134. \url{https://doi.org/10.1037/h0076759}
-
-\leavevmode\vadjust pre{\hypertarget{ref-walker2005gender}{}}%
-Walker, S.
-(2005).
-Gender {Differences} in the {Relationship Between Young Children}'s {Peer-Related Social Competence} and {Individual Differences} in {Theory} of {Mind}.
-\emph{The Journal of Genetic Psychology}, \emph{166}(3), 297--312.
-\url{https://doi.org/10.3200/GNTP.166.3.297-312}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2012theory}{}}%
-Wellman, H.
-M.
-(2012).
-Theory of mind: {Better} methods, clearer findings, more development.
-\emph{European Journal of Developmental Psychology}, \emph{9}(3), 313--330.
-\url{https://doi.org/10.1080/17405629.2012.680297}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysis}{}}%
-Wellman, H.
-M., Cross, D., \& Watson, J.
-(2001).
-Meta-analysis of theory-of-mind development: {The} truth about false belief.
-\emph{Child Development}, \emph{72}, 655--684.
-\url{https://doi.org/10.1111/1467-8624.00304}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
-Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wimmer1983beliefs}{}}%
-Wimmer, H., \& Perner, J.
-(1983).
-Beliefs about beliefs: {Representation} and constraining function of wrong beliefs in young children's understanding of deception.
-\emph{Cognition}.
-\url{https://doi.org/10.1016/0010-0277(83)90004-5}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhang2021worse}{}}%
-Zhang, Z., Yu, H., Long, M., \& Li, H.
-(2021).
-Worse {Theory} of {Mind} in {Only-Children Compared} to {Children With Siblings} and {Its Intervention}.
-\emph{Frontiers in Psychology}, \emph{12}, 5073.
-\url{https://doi.org/10.3389/fpsyg.2021.754168}
+\leavevmode\vadjust pre{\hypertarget{ref-zhang2019role}{}}%
+Zhang, X., Zhang, Z., Zhang, Z., Tang, Y., \& Liu, W.
+(2019).
+The role of the motion cue in the dynamic gaze-cueing effect: {A} study of the lateralized {ERPs}.
+\emph{Neuropsychologia}, \emph{124}, 151--160.
+\url{https://doi.org/10.1016/j.neuropsychologia.2018.12.016}
 
@@
 
+\newpage
+
 \end{document}

### 2023-06-09 stats/gazemodel.Rmd
add gazemodel data adults; write magnet sections

@@
 ```{r load_data}
-gaze_data <- readRDS("../data/tango-model.rds")
+gaze_data_kids <- readRDS("../data/tango-model-kids.rds")
+gaze_data_adults <- readRDS("../data/tango-model-adults.rds") %>% mutate(age_group = 18)
+gaze_data <- full_join(gaze_data_kids, gaze_data_adults)
 ```
@@
 ```{r sample}
-gazemodel_sample <- gaze_data %>% 
+gazemodel_sample_kids <- gaze_data_kids %>% 
   group_by(age_group) %>%
@@
 
-gazemodel_sample
+gazemodel_sample_kids
+
+gazemodel_sample_adults <- gaze_data_adults %>% 
+  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
+  summarise(
+    n_total = n_distinct(subj_id), 
+    age_mean = mean(age, na.rm = T) %>% round(2),
+    age_sd = sd(age, na.rm = T) %>% round(2),
+    age_min = min(age, na.rm = T),
+    age_max = max(age, na.rm = T),
+    n_females = ceiling(sum(female/15)),
+  ) %>% 
+  mutate(age_group = 18)
+
+gazemodel_sample <- gazemodel_sample_kids %>% full_join(gazemodel_sample_adults)
 
@@
 ```{r plot}
-dev_plot <- gaze_data %>% 
+dev_plot <- gaze_data_kids %>% 
   group_by(subj_id, age, age_group) %>%
@@
   scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
-  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d"), breaks = c("3", "4", "5"), labels = c("3-year-olds", "4-year-olds", "5-year-olds")) +
+  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "darkgrey"), breaks = c("3", "4", "5", "18"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")) +
     labs(x = "Target position (binned)", y = "Average imprecision in target widths", col = "Age in years")
@@
 
-# ggsave("../figures/gazefunnel.png", width = 6, height = 4, scale = 1.2)
-# saveRDS(gazefunnel, "../saves/gazefunnel.rds")
+ggsave("../figures/gazefunnel.png", width = 6, height = 4, scale = 1.2)
+saveRDS(gazefunnel, "../saves/gazefunnel.rds")
 ```

### 2023-06-09 supplements/supplements.Rmd
add gazemodel data adults; write magnet sections

@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
-    email         : "julia_prein@eva.mpg.de"
-
   - name          : "Manuel Bohn"
-    affiliation   : "1"
+    affiliation   : "1,2"
   - name          : "Luke Maurits"
@@
     institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
+  - id            : "2"
+    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"  
 floatsintext      : yes
@@
 ```
+
+# Components of gaze understanding
+## Theory of mind battery
+
+|     |     |     |     |
+| --- | --- | --- | --- |
+| **Task name** | **Author** | **Description** | **Material used** |
+| Diverse Beliefs | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Wellman et al., 1996 | Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it.
+“Here’s Linda.
+Linda wants to find her cat.
+Her cat might be hiding in the bushes or it might be hiding in the garage.
+Where do you think the cat is?
+In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage.
+She thinks her cat is in the garage.” (or vice versa) Then the child is asked the *target* question: “So where will Linda look for her cat?
+in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question.
+| Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) |
+| Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
+“Here’s a drawer.
+What do you think is inside the drawer?” (The child can give any answer she/he likes or indicate that she/he does not know).
+Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer.
+Now here comes Polly.
+So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”.
+| Toy figure of another girl, Plastic box with drawer, Toy dog |
+| Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
+‘‘Here’s a band-aid box.
+What do you think is inside the band-aid box?’’ Next, the band-aid box is opened: ‘‘Let’s see … it’s really a pig inside!’’ The band-aid box is closed: ‘‘Okay, what is in the band-aid box?’’ Then a toy figure of a boy is produced: ‘‘Peter has never ever seen inside this band-aid box.
+Now here comes Peter.
+So, what does Peter think is in the box?
+Band-Aids or a pig?
+(the *target* question) ‘‘Did Peter see inside this box?’’ (the *memory* question).
+To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ | Toy figure of a boy, Band-aid box , Toy pig |
+| Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
+‘‘Here’s Scott.
+Scott wants to find his mittens.
+His mittens might be in his backpack or they might be in the closet.
+Really, Scott’s mittens are in his backpack.
+But Scott thinks his mittens are in the closet.’’ ‘‘So, where will Scott look for his mittens?
+In his backpack or in the closet?’’ (the *target* question) ‘‘Where are Scott’s mittens really?
+In his backpack or in the closet?’’ (the _reality_ question).
+To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
+| Perspective-Taking Level 2 | Flavell et al., 1981 | Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child’s side and right side up (or upside down) from the experimenter’s.
+The child’s task is to indicate in which of these two orientations it appeared to the experimenter (“standing on its feet” or “lying on its back”).
+| Picture of a turtle |
+| Perspective-Taking Level 2 | Flavell et al., 1981 | Children are shown a horizontally placed picture of a worm lying between a red blanket and a blue blanket.
+The child was then asked if the worm appeared to the experimenter, seated opposite, to be lying on the red blanket or on the blue blanket.
+| Picture of a worm between two blankets |
 

### 2023-06-12 paper/manuscript.Rmd
add williams test, continue magnet results

@@
 library("kableExtra")
+library("brms")
 
@@
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in `R: performance ~ age + datacollection + (symmetricPosition | subjID) + (1 | targetPosition)`).
-Here, `targetPosition` refers to the exact bin/box of the target, while `symmetricPosition` refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed), in `R: imprecision ~ age_centered`).
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
-For the box version, the model predicted correct responses (0/1) using a `Bernoulli` distribution with a logit link function.
+Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
 We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
@@
 
--   model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
--   entwicklungsperspektive basierend auf model
--   dann prozess-ebene = magnet
+Task design, data collection, and sample sizes were pre-registered: https://osf.io/r3bhn.
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.
+2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+Data were collected between May and August 2021.
 
@@
 
-The sample included the `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` three- to five-year-old children and `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group == 18])` adults from our Lifespan study.
-For age distributions, see Participant section of the Lifespan Study.
+The sample included `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children consisting of
+`r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls),
+`r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls),
+`r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls), and
+`r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
 
-out of convenience, we only used ... since developmental chnage was minimial in adutls we used ...
+Data of children was collected in kindergartens located in Leipzig, Germany.
+The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
+Adults were recruited over *Prolific*  [@palan2018prolific].
+
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.
 
 ## Procedure
+As in the previous study, participants completed the continuous version of the TANGO [@prein2022tango].
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
 
@@
 Testing took place in kindergartens in Leipzig, Germany.
-The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r sum(magnet_sample$age_sd)`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
+The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
 
@@
 By design, both the gaze understanding task as well as the non-social vector estimation task involve vector estimation.
-On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate significantly.
-For these two tasks, we calculated the mean level of imprecision for each subject.
-We correlated these two scores using *Pearson's* correlation coefficients.
+On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate with each other.
+For each of these two tasks, we calculated the mean level of imprecision for each subject.
+We then correlated these two scores using *Pearson's* correlation coefficients.
 
-Regarding the relationship between the two vector estimation tasks and the ToM measures, we can imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expect that gaze understanding and ToM measures are more strongly correlated than non-social vector estimation and ToM measures.
-(B) If gaze understanding relies purely on task-specific processes, then the correlation between gaze understanding and ToM measures will be comparable to the correlation between non-social vector estimation and the ToM measures.
-For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficient.
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
+(B) If gaze understanding relies purely on task-specific processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficients.
 
-Furthermore, to estimate which components contribute to gaze understanding, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in\`R: tango_mean \~ age_centered + magnet_scaled + perspective_scaled\`).
+We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function `cocor.dep.groups.overlap` (designed for two dependent overlapping correlations) from the package `cocor` [@diedenhofen2015cocor].
+
+Furthermore, to estimate which components contribute to gaze understanding, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
 The outcome variable was modeled by a lognormal distribution.
-With this analysis, we wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value.
+With this analysis, we wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
 
@@
 
-As expected, we found that gaze understanding as a social vector estimation task correlated with the non-social vector estimation task.
+```{r magnet_results}
+magnet_williamsttest_tom <- readRDS("../saves/williams_tom.rds")
+magnet_williamsttest_perspective <- readRDS("../saves/williams_perspective.rds")
+magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
+magnet_model <- readRDS("../saves/magnet_winningmodel.rds")
+```
+
+As expected, we found that gaze understanding as a social vector estimation task correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`].
 Importantly, however, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
 
-Our model comparison corroborated this: evidently, gaze understanding was best predicted by non-social vector estimation and perspective-taking.
-This shows that the gaze understanding task recruits social-cognitive abilities beyond vector estimation.
+Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking showed a correlation of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+According to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
+
+Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]).
+
+Taken together, this shows that the gaze understanding task recruited social-cognitive abilities beyond vector estimation.
+Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
 

### 2023-06-12 stats/magnet.Rmd
add williams test, continue magnet results

@@
 library(apaTables) # as name says
+library(cocor) # compare correlations
+library(magrittr) # extract list elements
 
@@
 # apa table function only supports pearson corr so far
-magnet_data %>% select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% apa.cor.table(filename = "../saves/magnet_corrtable.doc", table.number=1)
+# magnet_data %>% select(tango_mean, magnet_mean, tom_aggregate, perspective_aggregate) %>% apa.cor.table(filename = "../saves/magnet_corrtable.doc", table.number=1)
+
+cor_matrix
+
+write.csv(cor_matrix, "../saves/magnet_cormatrix.csv", quote = F, row.names = F)
+saveRDS(cor_matrix, "../saves/magnet_cormatrix.rds")
 ```
@@
 saveRDS(model_results, "../saves/magnet_modelresults.rds")
+
+write.csv(mmagnet_perspective, "../saves/magnet_winningmodel.csv", quote = F, row.names = F)
+saveRDS(mmagnet_perspective, "../saves/magnet_winningmodel.rds")
 ```
@@
 ```
+
+```{r williamstest}
+williams_tom <- cocor.dep.groups.overlap(
+                         r.jk = cor_matrix$r[cor_matrix$Correlation == "Tango x ToM"], 
+                         r.jh = cor_matrix$r[cor_matrix$Correlation == "Magnet x ToM"], 
+                         r.kh = cor_matrix$r[cor_matrix$Correlation == "Tango x Magnet"], 
+                         n = nrow(magnet_data), 
+                         alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0, 
+                         return.htest = T) %>% 
+                       extract2("williams1959")
+
+saveRDS(williams_tom, "../saves/williams_tom.rds")
+
+williams_perspective <- cocor.dep.groups.overlap(
+                         r.jk = cor_matrix$r[cor_matrix$Correlation == "Tango x Perspective-taking"], 
+                         r.jh = cor_matrix$r[cor_matrix$Correlation == "Magnet x Perspective-taking"], 
+                         r.kh = cor_matrix$r[cor_matrix$Correlation == "Tango x Magnet"], 
+                         n = nrow(magnet_data), 
+                         alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0, 
+                         return.htest = T) %>% 
+                       extract2("williams1959")
+
+saveRDS(williams_perspective, "../saves/williams_perspective.rds")
+```

### 2023-06-15 paper/manuscript.Rmd
update magnet data (remove safety copies), add suppl. human vs animal stimuli analysis

@@
 
-The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r lifespan_sample$n_total[lifespan_sample$age_group == "3"]` 3-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "3"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "3"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "3"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "3"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "3"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "4"]` 4-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "4"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "4"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "4"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "4"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "4"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "5"]` 5-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "5"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "5"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "5"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "5"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "5"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "6"]` 6-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "6"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "6"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "6"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "6"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "6"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "7"]` 7-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "7"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "7"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "7"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "7"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "7"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "8"]` 8-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "8"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "8"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "8"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "8"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "8"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "9"]` 9-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "9"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "9"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "9"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "9"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "9"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "10"]` 10-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "10"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "10"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "10"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "10"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "10"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "11"]` 11-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "11"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "11"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "11"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "11"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "11"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "12"]` 12-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "12"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "12"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "12"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "12"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "12"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "13"]` 13-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "13"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "13"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "13"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "13"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "13"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "14"]` 14-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "14"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "14"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "14"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "14"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "14"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "15"]` 15-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "15"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "15"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "15"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "15"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "15"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "16"]` 16-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "16"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "16"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "16"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "16"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "16"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "17"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "17"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "17"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "17"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "17"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "17"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "18"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "18"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "18"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "18"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "18"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "18"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "19"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "19"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "19"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "19"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "19"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "19"]` girls).
-
+The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants.
 Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
@@
 Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision.
-The sample included `r lifespan_sample$n_total[lifespan_sample$age_group == "20"]` 20- to 29-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "20"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "20"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "20"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "20"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "20"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "30"]` 30- to 39-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "30"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "30"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "30"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "30"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "30"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "40"]` 40- to 49-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "40"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "40"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "40"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "40"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "40"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "50"]` 50- to 59-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "50"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "50"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "50"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "50"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "50"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "60"]` 60- to 69-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "60"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "60"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "60"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "60"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "60"]` female), and `r lifespan_sample$n_total[lifespan_sample$age_group == "70"]` 70- to 79-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "70"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "70"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "70"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "70"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "70"]` female).
+For further information on age and gender of participants, see Table 1.
 
@@
 
-As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. Children were tested on a tablet.
+Children were tested on a tablet. As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. 
+To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance.
+This further highlighted the contrast to the non-social vector estimation task.
+We had already created these stimuli for another project focusing on cross-cultural similarities in gaze understanding (https://osf.io/tdsvc).
+[^1]
+
+[^1]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
+human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
+animal).
+See Supplements for further detail.
 

### 2023-06-15 stats/supplementary_analyses.Rmd
update magnet data (remove safety copies), add suppl. human vs animal stimuli analysis

---
title: "Supplementary analysis"
author: "Julia Prein"
date: "06/13/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(janitor)
library(brms) # modeling
library(cmdstanr) # modeling
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
tango_humans <- readRDS("../data/magnet-tango-data.rds") %>% 
  mutate(target_position = as.factor(target_position), stimuli = "humans")

tango_animals <- readRDS("../data/tango-lifespan.rds") %>%
  filter(age >= min(tango_humans$age) & age <= max(tango_humans$age)) %>% 
  mutate(stimuli = "animals")

combined_data <- full_join(tango_humans, tango_animals) %>% 
  remove_empty(which = "cols") %>% 
  mutate(
    age_centered = age - min(age)
  )
```

```{r exploratory_plots}
combined_data %>% 
  ggplot(., aes(x = agent, y = click_dist_balloons)) +
  geom_count()
```

```{r models, message=FALSE, warning=FALSE}
mdata <- combined_data %>% 
  mutate(
    # scaled (centered around mean, SD = 1, i.e., z-transformed)
    age_scaled = scale(age), 
    symmetric_position = scale(symmetric_position),
    trial_nr = trial_nr - min(trial_nr), 
    click = abs(click_dist_from_target_center_x), 
  ) %>% 
  select(subj_id, age, age_scaled, stimuli, agent, symmetric_position, trial_nr, click) %>% 
  filter(click > 0)

mstimuli <- brm(click ~ age_scaled + stimuli + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

mstimuli

pp_check(mstimuli)

magent <- brm(click ~ age_scaled + agent + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
                    data = mdata,
                    family = lognormal(),
                    warmup = 2000, 
                    iter   = 6000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))

magent

pp_check(magent)

saveRDS(mstimuli, "../saves/supplements_magnet_mstimuli.rds")
saveRDS(magent, "../saves/supplements_magnet_magent.rds")
```

### 2023-06-23 paper/manuscript.Rmd
start working on modeling section

@@
 
-Task design, data collection, and sample sizes were pre-registered: https://osf.io/r3bhn.
+In a previous study, we have shown that the inter-individual variation in gaze understanding is reliable (@prein2022tango).
+Now, we asked ourselves what varies between participants on a process-level and how this changes with age.
+To answer this question, we aimed to formalize the process of gaze understanding in a computational cognitive model.
+The model seeks to explain how participants solve the TANGO task.
+
+Computational modeling frameworks allow researcher to establish mechanistic explanations of psychological phenomena and form testable predictions [@grahek2021anatomy].
+As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all underlying assumptions [@simmering2010dialogue].
+In addition, models can be used to simulate and predict behavior as it would be expected in novel experimental manipulations.
+This can then in turn be compared to empirically observed behavior and can, for example, demonstrate assumptions of the model to be false.
+
+The model assumes that participants estimate the agent's eye center and observe the current location of the pupil center.
+These two point estimates are then used to calculate a vector that points towards the attentional focus of the agent.
+Our model assumes that participants sample from a distribution around the true gaze vector.
+Individual differences could now be explained as more narrow or wider distribution around the true gaze vector (i.e., amount of deviation).
+This could represent participants' level of uncertainty in estimating the agent's attentional focus: the wider the distribution around the true gaze vector, the less precise participants estimate the focus of attention.
+This is the key parameter in our model: this so-called inferential component describes how accurately the participant infers the attentional focus based upon the state of the agent's pupil.
+
+However, participants who are very imprecise in locating the attentional focus of the agent could be less likely to make use of the eye information in the first place.
+To accomodate this, we created an alternative model that estimates the probability that a participant engages in random guessing.
+
+With this approach, we can formalize whether (A) a participant makes use of the available gaze information at all, and (B) how accurate they are, if they do pay attention to the agent's eyes.
+We expect a dual developmental process.
+The older children get, the more likely they are to use the gaze cues and the more precise they get in doing so.
+
+The geometry of the estimated gaze vector and the sampling of a distribution around this vector lead to interesting, testable group-level predictions.
+As the pupil location varies, a fixed amount of uncertainty about the eye angle corresponds to a varying amount of uncertainty in the estimated focus of attention (i.e., the target location).
+This could be thought of as a "headlight distribution": when the agent's eye gaze is directed centrally to the ground in front of them, the distribution from which participants sample is comparatively more narrow then when the agent's eye gaze is directed to the side.
+A similar phenomenon can be observed when you direct a torch light straight onto the ground or when you direct it at a further distance away from you.
+It leads the model to predict that our trials vary in difficulty: participants' clicks should be more imprecise, the further out the target x coordinate is.
+
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/r3bhn>.
 The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
@@
 
-The sample included `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children consisting of
-`r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls),
-`r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls),
-`r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls), and
-`r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
+The sample included `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children consisting of `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls), and `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
 
@@
 Adults were recruited over *Prolific* [@palan2018prolific].
-
 Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.
@@
 ## Procedure
+
 As in the previous study, participants completed the continuous version of the TANGO [@prein2022tango].
 Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
 
@@
 
+Our cognitive model attempts to explain the behavior of participants as being generated by one of two possible approaches.
+At each trial, a weighted coin toss determines whether the participant solves the task by \"guessing\" (sampling a clicking coordination from a uniform distribution over all possible coordinates) or by applying a gaze following model described below.
+Each participant has their own \"guessing probability\", determining the mixture of strategies they use.
+These per-participant parameters are modeled as having a Beta distribution over the population of participants.
+
+Our proposed gaze understanding model is a simplification of an originally three-component model, which consisted of: (1) a perceptual component, whereby the participant produces a noisy observation of the angle of each of the agent's eyes, (2) an inferential component, whereby the participant produces an estimate of the coordinate the agent is looking at based on the above noisy observations of eye angles and a model of how agents direct their eyes relative to where they are looking, and (3) a motor component, whereby the participant samples a location to click at from a distribution centered around the above estimate of where the agent is looking.
+Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components and so the model was simplified to include only the inferential component
+
+In the inferential component, the participant assumes that the agent\'s attention is focused on a single point coordinate and that the agent\'s left and right eyes are positioned by sampling (independently for each eye) eye angles from Normal distributions centered on the unique angle such that a line subtended from the center of the agent\'s eye through the center of its pupil will meet the attentional focal point (i.e.
+the modal behavior is to direct both eyes directly toward the focal point).
+The standard deviation of these distributions (equal for each eye) is a parameter that varies per participant, with higher values increasing the expected imprecision.
+When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant\'s assumptions about how wide an area of the agent\'s visual field their attention occupies.
+
+Because of the geometry of the situation (where a fixed amount of uncertainty about the agent\'s eye angle corresponds to a varying amount of uncertainty in the underlying point of attention as the eye angle varies), and because the participant integrates information from two eyes, the resulting posterior distribution (which the participant\'s mouse click is modeled as a sample from) does not belong to a standard parametric family, but can be easily numerically approximated as part of the inference process.
+
+We will compare this model against two models which represent alternatives about how participants' responses are generated.
+The \"random guessing\" model simply assumes that participants ignore the agent's gaze and randomly click on the screen (cf.
+coin toss, sampling a coordination from a uniform distribution over all possible coordinates).
+The \"motor noise\" model assumes that participants have no uncertainty about where the agent is looking but that their responses (clicks on the screen) come with a small amount of random noise (cf.
+motor component of our originally proposed model).
+We will then directly compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
+The models make different predictions about how participants\' clicks will be distributed for different locations of the target.
+We will visualise and evaluate these differences using correlations between the model predictions and the data.
+
 ## Results
+
+A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
+Our computational model can explain what varies between precise and imprecise individuals.
+There are two sources of errors: (1) do you actually use the eye gaze information?
+and (2) how accurate are you at estimating the focus point when you do pay attention to the agent's eyes?
+This way, we can track developmental changes in gaze understanding in a more fine-tuned way.
+
+In addition, our model was able to recover "signature patterns" in the data.
+Both the model predictions and the actual raw data show that precision levels drop as the agent's gaze moves further away from the center.
+Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.
 
@@
 Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
-In this study, we sought to inquire whether there are any other cognitive processes outside vector-following that constitute gaze understanding.
+In this study, we sought to experimentally isolate the physical vector estimation component.
+In addition, we inquired whether there are any other cognitive processes outside the vector estimation that constitute gaze understanding.
 We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
 
-First, we aimed at isolating the vector-following part of the gaze understanding task.
-For this, we designed a new non-social vector estimation task that shared all crucial design features of the understanding task.
-Additionally, we administered a ToM task battery, comprising 4 tasks from the ToM scale by Wellman and Liu (2004) and two additional perspective-taking tasks.
+First, we aimed to isolate the vector estimation component of the gaze understanding task.
+We designed a new non-social vector estimation task that shared all crucial design features of the gaze understanding task.
+Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (@wellman2004scaling) and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
 
 Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
-This way, we can disentangle which components comprise gaze understanding.
-In this way, we can find out what contribution each component makes to explain gaze understanding.
+This way, we can disentangle what components comprise gaze understanding.
 
@@
 The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
+Information on individual socio-economic status was not formally recorded.
+Children in our sample live in an industrialized, urban Central-European city with approximately 600,000 inhabitants.
+Households often consist of nuclear families with few household members.
+The majority of families in our data base come from mainly mid to high socio-economic backgrounds with high levels of parental education.
 
@@
 An experimenter guided the child through the study.
-Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects design.
+Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects study design.
 All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task.
-Several reasons motivated the decision.
-First, we decided for a fixed order to be able to compare participant's performance straight-forwardly with each other.
-Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task, to tasks with personal interaction, back to a tablet task.
-Third, we showed the non-social vector estimation task before the gaze understanding task, so that participants would not be biased to interpret the presented stimuli as "eye- / "agent-like".
+Several reasons motivated this decision.
+First, we decided on a fixed order to be able to compare participants' performance straight-forwardly with each other.
+Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
+Third, we showed the non-social vector estimation task before the gaze understanding task so that participants would not be biased to interpret the presented stimuli as "eye- /"agent-like".
 
@@
 Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task.
-This task was also presented as a webapp and made use of the concept of magnetism.
+This task was also presented as a webapp on a tablet and made use of the concept of magnetism.
 The setup looked as follows.
-On the upper part of the screen, there was a tube with a gearwheel, located in a circular window.
-On the floor, there laid a magnet.
+On the upper part of the screen, there was a tube with a gearwheel located in a circular window.
+On the floor, there lay a magnet.
 The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
-The gearwheel moved in a way that its center aligned with the center of the magnet.
+The gearwheel moved in a way that its center aligned with the center of the magnet, while staying inside the circular window.
 Participants were then asked to locate the magnet.
@@
 As in the TANGO, there were three different trial types depending on the visual access to the true magnet location.
-In the touch training, participants had full visual access to the magnet's location (i.e., no wooden wall).
-In familiarization trials, participants had partial visual access, since the wooden wall was moved in front of the target after the magnet's location was already visible.
-In test trials, participants have no visual access to the magnet location, because the wall covers the magnet from the beginning of the trial.
+In full visual access trials, the magnet's location was presented without impediment (i.e., no wooden wall).
+In partial visual access trials, the wooden wall was moved in front of the target after the magnet's location had already been visible.
+In test trials, participants had no visual access to the magnet's location because the wall covered the magnet from the beginning of the trial.
 
-Children received 19 trials with one touch training, two familiarization trials, and 16 test trials each.
+Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
 The first trial of each type comprised a voice-over description of the presented events.
-We conducted our analysis with 15 test trials, excluding the touch, familiarization, and voice-over trials.
+We conducted our analysis with 15 test trials (excluding the voice-over trial).
 The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click.
@@
 We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
-Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga], with the aim of increasing the task battery's difficulty.
-See Supplements for further detail.
-The dependent variable was the aggregate score of all solved ToM tasks.
+Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga].
+We added the perspective-taking tasks (1) with the aim of increasing the task battery's difficulty, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
+The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
 In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
@@
 
-Children were tested on a tablet. As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. 
-To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance.
-This further highlighted the contrast to the non-social vector estimation task.
-We had already created these stimuli for another project focusing on cross-cultural similarities in gaze understanding (https://osf.io/tdsvc).
-[^1]
+As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango].
+To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
+This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^1]
 
-[^1]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
-human agents.
-Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
-animal).
+[^1]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
+    Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal).
     See Supplements for further detail.
@@
 
-Furthermore, to estimate which components contribute to gaze understanding, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
 The outcome variable was modeled by a lognormal distribution.
-With this analysis, we wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
 
@@
 
-Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking showed a correlation of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
 According to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
@@
 Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]).
+See Supplements for further detail of the model comparison.
 
@@
 
-(ref:figlab4) **Components of gaze understanding**
+(ref:figlab4) **Components of gaze understanding.** (A) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+Dots show the correlation coefficients, while error bars represent 95% CIs.
+(B) Influence of perspective-taking and physical vector estimation on gaze understanding.
+The graph show the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
 
@@
 
+By carefully isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
+This is in line with our computational cognitive framework that assumes vector calculations on a process-level.
+However, physical vector estimation alone did not suffice to explain gaze understanding.
+In addition, perspective-taking proved to be a relevant social-cognitive ability.
+
 In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2022tango].
 Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-
-It seems noteworthy to point out that lower correlations between ToM skills and gaze understanding could be grounded in the design features of the applied ToM tasks.
-The tasks we used to measure ToM skills were not designed to capture individual differences: they rely on an aggregate score of dichotomous measures.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of dichotomous measures.
 These sum scores can only capture limited variance, which may obscure potential correlations.
 However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
+It seems noteworthy to point out that lower correlations between ToM abilities and gaze understanding could be grounded in the design features of the applied ToM tasks.
+We already stated this concern in the Pre-registration (<https://osf.io/xsqkt>).
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.

### 2023-06-23 paper/manuscript.tex
start working on modeling section

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-The remote child and teenager sample consisted of 471 children, including 19 3-year-olds (mean = 3.62 years, SD = 0.31, range = 3.04 - 3.99, 7 girls), 17 4-year-olds (mean = 4.45 years, SD = 0.30, range = 4.05 - 4.91, 9 girls), 22 5-year-olds (mean = 5.56 years, SD = 0.31, range = 5.08 - 5.99, 13 girls), 24 6-year-olds (mean = 6.50 years, SD = 0.28, range = 6.10 - 6.99, 16 girls), 39 7-year-olds (mean = 7.48 years, SD = 0.25, range = 7.04 - 7.95, 20 girls), 41 8-year-olds (mean = 8.46 years, SD = 0.27, range = 8.03 - 8.98, 20 girls), 56 9-year-olds (mean = 9.46 years, SD = 0.28, range = 9.01 - 9.96, 29 girls), 35 10-year-olds (mean = 10.49 years, SD = 0.28, range = 10.01 - 11, 22 girls), 54 11-year-olds (mean = 11.43 years, SD = 0.28, range = 11.01 - 11.96, 26 girls), 43 12-year-olds (mean = 12.41 years, SD = 0.30, range = 12.01 - 12.99, 19 girls), 42 13-year-olds (mean = 13.50 years, SD = 0.27, range = 13.09 - 13.99, 19 girls), 20 14-year-olds (mean = 14.37 years, SD = 0.23, range = 14.05 - 14.98, 14 girls), 21 15-year-olds (mean = 15.56 years, SD = 0.30, range = 15.05 - 15.98, 11 girls), 19 16-year-olds (mean = 16.51 years, SD = 0.24, range = 16.17 - 16.97, 10 girls), 19 17-year-olds (mean = 17.53 years, SD = 0.28, range = 17.01 - 17.95, 10 girls), 2 17-year-olds (mean = 18 years, SD = 0, range = 18 - 18, 0 girls),
-5 17-year-olds (mean = 19 years, SD = 0, range = 19 - 19, 4 girls).
-
+The remote child and teenager sample consisted of 471 participants.
 Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
@@
 Participants consisted of 240 English-speaking adults that reported to have normal or corrected-to-normal vision.
-The sample included 40 20- to 29-year-olds (mean = 23.02 years, SD = 2.77, range = 20 - 29, 25 female),
-40 30- to 39-year-olds (mean = 34.42 years, SD = 3, range = 30 - 39, 21 female),
-40 40- to 49-year-olds (mean = 44.17 years, SD = 2.92, range = 40 - 49, 24 female),
-40 50- to 59-year-olds (mean = 54.38 years, SD = 3.04, range = 50 - 59, 21 female),
-40 60- to 69-year-olds (mean = 63.73 years, SD = 2.56, range = 60 - 69, 21 female), and
-40 70- to 79-year-olds (mean = 72.75 years, SD = 2.44, range = 70 - 79, 20 female).
+For further information on age and gender of participants, see Table 1.
 
@@
 
-We used the TANGO task (Prein, Bohn, Kalinke, \& Haun, 2022).
+We used the continuous version of the TANGO (Prein, Bohn, Kalinke, \& Haun, 2022).
 The task was presented as an interactive web application (see Figure \ref{fig:fig1}; live demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
-The TANGO showed satisfactory internal consistency and retest reliability {[}with reliability estimates \emph{Pearson's r} ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; Prein et al.
+The TANGO showed satisfactory internal consistency and retest reliability {[}with reliability estimates \emph{Pearson's r} ranging from .7 to .8 for the continuous task version; Prein et al.
 (2022){]}.
@@
 Each trial presented an agent standing in a window, watching a balloon (\emph{i.e.}, target) falling to the ground.
-Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
+The target then fell behind a hedge (continuous task version).
 The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
-The target flight was covered so that participants could not see where the target landed.
+In test trials, the target flight was covered so that participants could not see where the target landed.
 Participants' task was to locate the target by tracking the agent's gaze.
-They could respond by clicking or touching on the screen.
+They could respond by touching on the screen.
 
@@
 
-The outcome measure depended on the task version.
-In the continuous \emph{hedge version}, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the discrete \emph{box version}, we calculated the proportion of correct responses.
-
-The randomization of the final target location also depended on the task version.
-In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
-In the box version, the target randomly landed in one of the boxes.
-We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
-Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
+The outcome measure was imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
+Target coordinates were randomly generated during runtime.
+Each target bin, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
 
@@
 
-\caption{\textbf{Setup of the TANGO}.
-(A) Infrastructure for online testing.
-(i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens, or research labs.
-(ii) The task is presented as a website that works across devices.
-(iii) The scripts for the website and the recorded data are stored on secure local servers.
-(B) Hedge version (continuous) of the gaze understanding task.
-(i) The agent stands in a window with the target in front of them.
-(ii) A hedge grows and covers the target.
-(iii) The target falls to a random location on the ground.
+\caption{\textbf{Setup of the TANGO and Magnet tasks}.
+(A) TANGO: Gaze understanding task.
+The agent stands in a window with the target in front of them.
+A hedge grows and covers the target.
+The target falls to a random location on the ground.
 The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task.
-Number of boxes (min.
-1; max.
-8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
+(B) Magnet task: non-social vector estimation.}\label{fig:fig1}
 \end{figure}
@@
 
-In the remote sample for children from three to five years old, the family's presentation device determined the task version.
-Whenever a touchscreen was available, the continuous task version was presented.
-For families using a computer without touchscreen, the discrete task version was shown.
-Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.
-
-The number of teenagers in our internal database for recruiting families substantially decreased by age.
-To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
-Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.
-
-The remote adult sample was equally distributed across the two task versions.
-
 \hypertarget{analysis}{%
 \subsection{Analysis}\label{analysis}}
-
-\begin{itemize}
-\tightlist
-\item
-  TODO: non-linear model for development
-\end{itemize}
 
@@
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
-Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
+To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed), in \texttt{R:\ imprecision\ \textasciitilde{}\ age\_centered}).
 
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
-For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
+Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
 We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
@@
 
-\begin{itemize}
-\tightlist
-\item
-  model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
-\item
-  entwicklungsperspektive basierend auf model
-\item
-  dann prozess-ebene = magnet
-\end{itemize}
+In a previous study, we have shown that the inter-individual variation in gaze understanding is reliable (Prein et al. (2022)).
+Now, we asked ourselves what varies between participants on a process-level and how this changes with age.
+To answer this question, we aimed to formalize the process of gaze understanding in a computational cognitive model.
+The model seeks to explain how participants solve the TANGO task.
+
+Computational modeling frameworks allow researcher to establish mechanistic explanations of psychological phenomena and form testable predictions (Grahek, Schaller, \& Tackett, 2021).
+As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all underlying assumptions (Simmering, Triesch, Deák, \& Spencer, 2010).
+In addition, models can be used to simulate and predict behavior as it would be expected in novel experimental manipulations.
+This can then in turn be compared to empirically observed behavior and can, for example, demonstrate assumptions of the model to be false.
+
+The model assumes that participants estimate the agent's eye center and observe the current location of the pupil center.
+These two point estimates are then used to calculate a vector that points towards the attentional focus of the agent.
+Our model assumes that participants sample from a distribution around the true gaze vector.
+Individual differences could now be explained as more narrow or wider distribution around the true gaze vector (i.e., amount of deviation).
+This could represent participants' level of uncertainty in estimating the agent's attentional focus: the wider the distribution around the true gaze vector, the less precise participants estimate the focus of attention.
+This is the key parameter in our model: this so-called inferential component describes how accurately the participant infers the attentional focus based upon the state of the agent's pupil.
+
+However, participants who are very imprecise in locating the attentional focus of the agent could be less likely to make use of the eye information in the first place.
+To accomodate this, we created an alternative model that estimates the probability that a participant engages in random guessing.
+
+With this approach, we can formalize whether (A) a participant makes use of the available gaze information at all, and (B) how accurate they are, if they do pay attention to the agent's eyes.
+We expect a dual developmental process.
+The older children get, the more likely they are to use the gaze cues and the more precise they get in doing so.
+
+The geometry of the estimated gaze vector and the sampling of a distribution around this vector lead to interesting, testable group-level predictions.
+As the pupil location varies, a fixed amount of uncertainty about the eye angle corresponds to a varying amount of uncertainty in the estimated focus of attention (i.e., the target location).
+This could be thought of as a ``headlight distribution'': when the agent's eye gaze is directed centrally to the ground in front of them, the distribution from which participants sample is comparatively more narrow then when the agent's eye gaze is directed to the side.
+A similar phenomenon can be observed when you direct a torch light straight onto the ground or when you direct it at a further distance away from you.
+It leads the model to predict that our trials vary in difficulty: participants' clicks should be more imprecise, the further out the target x coordinate is.
+
+Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/r3bhn}.
+The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
+No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+Data were collected between May and August 2021.
 
@@
 
-The sample included the 58 three- to five-year-old children and 240 adults from our Lifespan study. For age distributions, see Participant section of the Lifespan Study.
+The sample included 60 children consisting of 20 three-year-olds (mean age = 3.47 years, SD = 0.34, range = 3.07 - 3.97, 11 girls), 20 four-year-olds (mean age = 4.61 years, SD = 0.26, range = 4.09 - 4.98, 10 girls), 20 five-year-olds (mean age = 5.66 years, SD = 0.24, range = 5.01 - 5.96, 12 girls), and 50 adults from our Lifespan study (mean age = 31.92 years, SD = 12.15, range = 18 - 63, 36 female).
 
-\hypertarget{non-social-vector-following}{%
-\section{Non-social vector following}\label{non-social-vector-following}}
+Data of children was collected in kindergartens located in Leipzig, Germany.
+The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
+Adults were recruited over \emph{Prolific} (Palan \& Schitter, 2018).
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
+As in the previous study, participants completed the continuous version of the TANGO (Prein et al., 2022).
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
+
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
+
+Our cognitive model attempts to explain the behavior of participants as being generated by one of two possible approaches.
+At each trial, a weighted coin toss determines whether the participant solves the task by "guessing" (sampling a clicking coordination from a uniform distribution over all possible coordinates) or by applying a gaze following model described below.
+Each participant has their own "guessing probability", determining the mixture of strategies they use.
+These per-participant parameters are modeled as having a Beta distribution over the population of participants.
+
+Our proposed gaze understanding model is a simplification of an originally three-component model, which consisted of: (1) a perceptual component, whereby the participant produces a noisy observation of the angle of each of the agent's eyes, (2) an inferential component, whereby the participant produces an estimate of the coordinate the agent is looking at based on the above noisy observations of eye angles and a model of how agents direct their eyes relative to where they are looking, and (3) a motor component, whereby the participant samples a location to click at from a distribution centered around the above estimate of where the agent is looking.
+Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components and so the model was simplified to include only the inferential component
+
+In the inferential component, the participant assumes that the agent\textquotesingle s attention is focused on a single point coordinate and that the agent\textquotesingle s left and right eyes are positioned by sampling (independently for each eye) eye angles from Normal distributions centered on the unique angle such that a line subtended from the center of the agent\textquotesingle s eye through the center of its pupil will meet the attentional focal point (i.e.~the modal behavior is to direct both eyes directly toward the focal point).
+The standard deviation of these distributions (equal for each eye) is a parameter that varies per participant, with higher values increasing the expected imprecision.
+When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant\textquotesingle s assumptions about how wide an area of the agent\textquotesingle s visual field their attention occupies.
+
+Because of the geometry of the situation (where a fixed amount of uncertainty about the agent\textquotesingle s eye angle corresponds to a varying amount of uncertainty in the underlying point of attention as the eye angle varies), and because the participant integrates information from two eyes, the resulting posterior distribution (which the participant\textquotesingle s mouse click is modeled as a sample from) does not belong to a standard parametric family, but can be easily numerically approximated as part of the inference process.
+
+We will compare this model against two models which represent alternatives about how participants' responses are generated.
+The "random guessing" model simply assumes that participants ignore the agent's gaze and randomly click on the screen (cf.~coin toss, sampling a coordination from a uniform distribution over all possible coordinates).
+The "motor noise" model assumes that participants have no uncertainty about where the agent is looking but that their responses (clicks on the screen) come with a small amount of random noise (cf.~motor component of our originally proposed model).
+We will then directly compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
+The models make different predictions about how participants\textquotesingle{} clicks will be distributed for different locations of the target.
+We will visualise and evaluate these differences using correlations between the model predictions and the data.
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
+Our computational model can explain what varies between precise and imprecise individuals.
+There are two sources of errors: (1) do you actually use the eye gaze information?
+and (2) how accurate are you at estimating the focus point when you do pay attention to the agent's eyes?
+This way, we can track developmental changes in gaze understanding in a more fine-tuned way.
+
+In addition, our model was able to recover ``signature patterns'' in the data.
+Both the model predictions and the actual raw data show that precision levels drop as the agent's gaze moves further away from the center.
+Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gazefunnel_combined}
+
+}
+
+\caption{\textbf{Gaze funnel}}\label{fig:fig3}
+\end{figure}
+
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
+
+\hypertarget{components-of-gaze-understanding}{%
+\section{Components of gaze understanding}\label{components-of-gaze-understanding}}
+
+Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
+In this study, we sought to experimentally isolate the physical vector estimation component.
+In addition, we inquired whether there are any other cognitive processes outside the vector estimation that constitute gaze understanding.
+We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
+
+First, we aimed to isolate the vector estimation component of the gaze understanding task.
+We designed a new non-social vector estimation task that shared all crucial design features of the gaze understanding task.
+Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (Wellman and Liu (2004)) and two additional perspective-taking tasks (Flavell, Everett, Croft, \& Flavell, 1981; Flavell, Flavell, Green, \& Wilcox, 1981).
+
+Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
+This way, we can disentangle what components comprise gaze understanding.
 
 Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/xsqkt}.
-
 The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
@@
 
-The sample consisted of 102 children (mean age = 4.54 years, SD = 0.31, range = 3.99 - 5.03, 54 girls),
+Testing took place in kindergartens in Leipzig, Germany.
+The sample consisted of 102 children (mean age = 4.54 years, SD = 0.31, range = 3.99 - 5.03, 54 girls).
+Information on individual socio-economic status was not formally recorded.
+Children in our sample live in an industrialized, urban Central-European city with approximately 600,000 inhabitants.
+Households often consist of nuclear families with few household members.
+The majority of families in our data base come from mainly mid to high socio-economic backgrounds with high levels of parental education.
 
-\begin{itemize}
-\item
-  gut, dass unser maß ind diff messen kann, das nutzen wir jetzt
-\item
-  zsmhang mit vector following, aber nicht redundant
-\item
-  perspective-taking auch, aber auch nicht relevant, nicht theory of mind score
-\item
-  diskutieren dass die maße auch nict ind diff maße sind
-\item
-  model vergleich: welche komponente stecken in gafo drin?,
-  welchen beitrag liefern die um score zu erklären?
-  welche wichtiger, tom oder nur perspective taking
-\item
-  magnet versuch das vector following zu isolieren.
-  ist da noch was anderes außerhalb vector-following?
-\item
-  aggregierte messungen immer besser, nur indikatoren für konstrukt
-\end{itemize}
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
+
+Children were tested in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects study design.
+All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task.
+Several reasons motivated this decision.
+First, we decided on a fixed order to be able to compare participants' performance straight-forwardly with each other.
+Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
+Third, we showed the non-social vector estimation task before the gaze understanding task so that participants would not be biased to interpret the presented stimuli as ``eye- /''agent-like''.
+
+\hypertarget{non-social-vector-estimation}{%
+\subsubsection{Non-social vector estimation}\label{non-social-vector-estimation}}
+
+Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task.
+This task was also presented as a webapp on a tablet and made use of the concept of magnetism.
+The setup looked as follows.
+On the upper part of the screen, there was a tube with a gearwheel located in a circular window.
+On the floor, there lay a magnet.
+The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
+The gearwheel moved in a way that its center aligned with the center of the magnet, while staying inside the circular window.
+Participants were then asked to locate the magnet.
+Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
+When no information about the magnet location was accessible, participants were expected to use the gearwheel inside the window as a non-social cue to locate the magnet.
+
+As in the TANGO, there were three different trial types depending on the visual access to the true magnet location.
+In full visual access trials, the magnet's location was presented without impediment (i.e., no wooden wall).
+In partial visual access trials, the wooden wall was moved in front of the target after the magnet's location had already been visible.
+In test trials, participants had no visual access to the magnet's location because the wall covered the magnet from the beginning of the trial.
+
+Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+We conducted our analysis with 15 test trials (excluding the voice-over trial).
+The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click.
+Magnet coordinates were generated as follows.
+The full width of the screen was divided into ten bins.
+Each bin occurred equally often, while the same bin could occur in two consecutive trials.
+Exact coordinates within each bin were randomly generated.
+
+\hypertarget{theory-of-mind-task-battery}{%
+\subsubsection{Theory of Mind task battery}\label{theory-of-mind-task-battery}}
+
+We administered four tasks from the Wellman and Liu (2004) Theory of Mind scale.
+We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the ``cold, cognitive'' (as compared to the ``emotional'') aspects of social cognition.
+Instead, we added two perspective-taking level-2 tasks (Flavell, Everett, et al., 1981; Flavell, Flavell, et al., 1981).
+We added the perspective-taking tasks (1) with the aim of increasing the task battery's difficulty, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
+The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
+In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
+
+\hypertarget{gaze-understanding}{%
+\subsubsection{Gaze understanding}\label{gaze-understanding}}
+
+As in the two previously reported studies, we presented children with the continuous version of the TANGO (Prein et al., 2022).
+To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (\url{https://osf.io/tdsvc})).
+This further highlighted the contrast (i.e., social vs.~non-social context) to the non-social vector estimation task.\footnote{In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.~human agents.
+  Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.~animal).
+  See Supplements for further detail.}
+
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
+
+By design, both the gaze understanding task as well as the non-social vector estimation task involve vector estimation.
+On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate with each other.
+For each of these two tasks, we calculated the mean level of imprecision for each subject.
+We then correlated these two scores using \emph{Pearson's} correlation coefficients.
+
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
+(B) If gaze understanding relies purely on task-specific processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used \emph{Spearman's} rank correlation coefficients.
+
+We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function \texttt{cocor.dep.groups.overlap} (designed for two dependent overlapping correlations) from the package \texttt{cocor} (Diedenhofen \& Musch, 2015).
+
+Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
+We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
+The outcome variable was modeled by a lognormal distribution.
+
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
+
+As expected, we found that gaze understanding as a social vector estimation task correlated with the non-social vector estimation task, \emph{r} = 0.38, 95\%CI {[}0.20, 0.53{]}.
+Importantly, however, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
+
+Gaze understanding and perspective-taking showed a \emph{Spearman} correlation coefficient of \(\rho\) = -0.29, 95\%CI {[}-0.46, -0.10{]}, while non-social vector estimation and perspective-taking did not correlate, \(\rho\) = -0.09, 95\%CI {[}-0.28, 0.10{]}.
+According to the Williams' test, these two correlations did not differ significantly from each other, \emph{t}(99) = -1.86, \emph{p} = 0.07.
+
+Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation (\(\beta\) = 0.14, 95\% CrI {[}0.06; 0.21{]}) and perspective-taking (\(\beta\) = -0.10; 95\% CrI {[}-0.17, -0.03{]}), even when controlling for age (\(\beta\) = -0.14, 95\% CrI {[}-0.38, 0.10{]}).
+See Supplements for further detail of the model comparison.
+
+Taken together, this shows that the gaze understanding task recruited social-cognitive abilities beyond vector estimation.
+Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/magnet_arrangedplot}
+
+}
+
+\caption{\textbf{Components of gaze understanding.} (A) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+Dots show the correlation coefficients, while error bars represent 95\% CIs.
+(B) Influence of perspective-taking and physical vector estimation on gaze understanding.
+The graph show the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80\% CrI and thinner black lines 95\% CrI.}\label{fig:fig4}
+\end{figure}
+
+\hypertarget{discussion-2}{%
+\subsection{Discussion}\label{discussion-2}}
+
+By carefully isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
+This is in line with our computational cognitive framework that assumes vector calculations on a process-level.
+However, physical vector estimation alone did not suffice to explain gaze understanding.
+In addition, perspective-taking proved to be a relevant social-cognitive ability.
+
+In previous work, we could establish that the TANGO is suited as an individual differences measure (Prein et al., 2022).
+Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of dichotomous measures.
+These sum scores can only capture limited variance, which may obscure potential correlations.
+However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
+It seems noteworthy to point out that lower correlations between ToM abilities and gaze understanding could be grounded in the design features of the applied ToM tasks.
+We already stated this concern in the Pre-registration (\url{https://osf.io/xsqkt}).
+The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
+
+\hypertarget{general-discussion}{%
+\section{General discussion}\label{general-discussion}}
 
@@
 \section{Limitations}\label{limitations}}
-
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
-Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1). \url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-diedenhofen2015cocor}{}}%
+Diedenhofen, B., \& Musch, J.
+(2015).
+Cocor: {A Comprehensive Solution} for the {Statistical Comparison} of {Correlations}.
+\emph{PLoS ONE}, \emph{10}(4), e0121945.
+\url{https://doi.org/10.1371/journal.pone.0121945}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981younga}{}}%
+Flavell, J.
+H., Everett, B.
+A., Croft, K., \& Flavell, E.
+R.
+(1981).
+Young children's knowledge about visual perception: {Further} evidence for the {Level} 1\textendash{{Level}} 2 distinction.
+\emph{Developmental Psychology}, \emph{17}, 99--103.
+\url{https://doi.org/10.1037/0012-1649.17.1.99}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981development}{}}%
+Flavell, J.
+H., Flavell, E.
+R., Green, F.
+L., \& Wilcox, S.
+A.
+(1981).
+The {Development} of {Three Spatial Perspective-Taking Rules}.
+\emph{Child Development}, \emph{52}(1), 356--358.
+\url{https://doi.org/10.2307/1129250}
+
 \leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
@@
 \url{https://doi.org/10.1037/0012-1649.40.2.177}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grahek2021anatomy}{}}%
+Grahek, I., Schaller, M., \& Tackett, J.
+L.
+(2021).
+Anatomy of a {Psychological Theory}: {Integrating Construct-Validation} and {Computational-Modeling Methods} to {Advance Theorizing}.
+\emph{Perspectives on Psychological Science}, \emph{16}(4), 803--815.
+\url{https://doi.org/10.1177/1745691620966794}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-simmering2010dialogue}{}}%
+Simmering, V.
+R., Triesch, J., Deák, G.
+O., \& Spencer, J.
+P.
+(2010).
+A {Dialogue} on the {Role} of {Computational Modeling} in {Developmental Science}.
+\emph{Child Development Perspectives}, \emph{4}(2), 152--158.
+\url{https://doi.org/10.1111/j.1750-8606.2010.00134.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
@@
 \url{https://doi.org/10.1016/j.jhevol.2006.10.001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
+Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
 

### 2023-06-23 supplements/supplements.Rmd
start working on modeling section

@@
 
+## Model comparison
+
+```{r magnet_modelcomparison}
+magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
+  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
+  mutate_if(is.numeric, round, 2)
+
+knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
+
 # References

### 2023-06-30 paper/manuscript.Rmd
save interim for computational model description

@@
 
-  - name          : "Julia Prein"
+  - name          : "Julia Christin Prein"
     affiliation   : "1"
@@
       - Investigation
-      - Formal Analysis
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-
-  - name          : "Manuel Bohn"
-    affiliation   : "1,2"
-    role          :
-      - Conceptualization
       - Formal Analysis
@@
   - name          : "Daniel B. M. Haun"
-    affiliation   : "1"
+    affiliation   : "1,*"
     role          :
       - Supervision
+      - Writing - Review & Editing
+
+  - name          : "Manuel Bohn"
+    affiliation   : "1,2,*"
+    role          :
+      - Conceptualization
+      - Formal Analysis
+      - Writing - Original Draft Preparation
       - Writing - Review & Editing
@@
     institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+  - id            : "*"
+    institution   : "Shared senior authorship" 
 authornote: |
+highlights: |
+  Abstract max 250 words
+
 abstract: |
-  Abstract
+  Abstract max 250 words
 
-keywords          : "social cognition, individual differences, gaze cues, cognitive modeling"
-wordcount         : "xxx"
+keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
+wordcount         : "xxx max 8000"
 bibliography      : ["../../references.bib"]
@@
 linenumbers       : yes
-mask              : no
+mask              : yes 
 draft             : no
@@
 ```
+
+# Variation in gaze understanding across the life span: A process-level perspective
+
+**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1^, & Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
+
+**Affiliations:** ^1^ Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+^2^ Institute of Psychology, Leuphana University Lüneburg, Germany.
+^\*^ shared senior authorship
+
+**ORCiD**: *Julia Christin Prein* <https://orcid.org/0000-0002-3154-6167>
+
+**Conflicts of interest:** The authors declare that they have no conflict of interest.
+
+**Data availability statement:** The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
+The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
+All experiments were pre-registered (<https://osf.io/zjhsc/>).
+
+**Acknowledgements:** We thank Jana Jurkat for her help with data collection and participant recruitment.
+We would also like to thank Steven Kalinke for his technical programming support.
+
+**Funding:** This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
+We thank all the children, caregivers, and adults who participated in the study.
+
+**Ethical statement:** The studies were approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.Informed consent was obtained from all individual participants or their legal guardians.
+
+\newpage
+
+# Research highlights
+
+-   up to four bulleted points outlining the key contributions to research the paper makes.
+-   The Research Highlights should be placed before the abstract.
+-   Each research highlight should not be longer than 25 words.
 
@@
 
+Children came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
+They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income \~ 1,600€ as of 2021).
+Most were raised monolingually in a nuclear two-generational family setting.
+Information on demographics and socioeconomic status was not formally recorded on a participant level.
+The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+Data was collected between May 2021 and April 2023.
+
 We collected data from a remote child, teenager and adult sample.
@@
 
-In a previous study, we have shown that the inter-individual variation in gaze understanding is reliable (@prein2022tango).
-Now, we asked ourselves what varies between participants on a process-level and how this changes with age.
-To answer this question, we aimed to formalize the process of gaze understanding in a computational cognitive model.
-The model seeks to explain how participants solve the TANGO task.
+Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
+The TANGO has previously been proven reliable for capturing inter-individual differences in gaze understanding [@prein2022tango].
+The variation between participants is thus likely genuine and not due to random noise.
+Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
+Therefore, we formalized the process of gaze understanding in a computational cognitive model.
+Computational modeling frameworks allow researchers to establish mechanistic explanations of psychological phenomena [@grahek2021anatomy].
+As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all their underlying assumptions [@simmering2010dialogue].
+In addition, models can be used to simulate behavior and form testable predictions.
+The expected patterns can then, in turn, be compared to the empirically observed behavior.
 
-Computational modeling frameworks allow researcher to establish mechanistic explanations of psychological phenomena and form testable predictions [@grahek2021anatomy].
-As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all underlying assumptions [@simmering2010dialogue].
-In addition, models can be used to simulate and predict behavior as it would be expected in novel experimental manipulations.
-This can then in turn be compared to empirically observed behavior and can, for example, demonstrate assumptions of the model to be false.
+With our model, we seek to explain how participants solved the TANGO.
+Our modeling framework consists of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+We gauge which model can best explain our data by conducting a model comparison.
 
-The model assumes that participants estimate the agent's eye center and observe the current location of the pupil center.
-These two point estimates are then used to calculate a vector that points towards the attentional focus of the agent.
-Our model assumes that participants sample from a distribution around the true gaze vector.
-Individual differences could now be explained as more narrow or wider distribution around the true gaze vector (i.e., amount of deviation).
-This could represent participants' level of uncertainty in estimating the agent's attentional focus: the wider the distribution around the true gaze vector, the less precise participants estimate the focus of attention.
-This is the key parameter in our model: this so-called inferential component describes how accurately the participant infers the attentional focus based upon the state of the agent's pupil.
+\-\-- explanation based on online experiment logic:
 
-However, participants who are very imprecise in locating the attentional focus of the agent could be less likely to make use of the eye information in the first place.
-To accomodate this, we created an alternative model that estimates the probability that a participant engages in random guessing.
+The gaze model mirrors the logic of the TANGO programming code.
+In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
+We then calculate a line between these two points: this is our gaze vector.
+Now, we also know the eyeball radius and, hence, the eyeball boundary.
+We then calculate the point of intersection at which the gaze vector meets the eyeball boundary.
+Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
+This way, the agent "looks at" the target.
 
-With this approach, we can formalize whether (A) a participant makes use of the available gaze information at all, and (B) how accurate they are, if they do pay attention to the agent's eyes.
-We expect a dual developmental process.
-The older children get, the more likely they are to use the gaze cues and the more precise they get in doing so.
+In the computational gaze model, we assume that participants need to go through these steps in reversed order.
+The only information that they have readily available is the boundary of the eyeball and the final location of the agent's pupil (i.e., the intersection point).
+Now, we assume that participants estimate the center point of the agent's eyeball and then, estimate a line from the center point to the intersection point: this will serve as the gaze vector.
+Participants are then thought to extend this gaze vector until it reaches the ground.
+They apply this procedure to both eyes and integrate the information.
+This way, they can estimate the final target location.
 
-The geometry of the estimated gaze vector and the sampling of a distribution around this vector lead to interesting, testable group-level predictions.
-As the pupil location varies, a fixed amount of uncertainty about the eye angle corresponds to a varying amount of uncertainty in the estimated focus of attention (i.e., the target location).
-This could be thought of as a "headlight distribution": when the agent's eye gaze is directed centrally to the ground in front of them, the distribution from which participants sample is comparatively more narrow then when the agent's eye gaze is directed to the side.
-A similar phenomenon can be observed when you direct a torch light straight onto the ground or when you direct it at a further distance away from you.
-It leads the model to predict that our trials vary in difficulty: participants' clicks should be more imprecise, the further out the target x coordinate is.
+\-\-- explanation based on pre-reg:
+
+The gaze model assumes that the agent focuses their attention on a single point coordinate and that the agent's left and right eyes are positioned by sampling (independently for each eye) gaze vectors from Normal distributions centered on the unique vector that extends from the center of the agent's eye through the center of its pupil to finally meet the attentional focal point (i.e., the modal behavior is to direct both eyes directly toward the focal point).
+The standard deviation of these distributions (equal for each eye) is estimated for each individual participant, with higher values increasing the expected imprecision.
+When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant's assumptions about how wide an area of the agent's visual field their attention occupies.
+
+\-\-- alternative explanation:
+
+The gaze model assumes participants use the agent's gaze as a cue to locate the target.
+Participants are assumed to observe the current location of the pupil and estimate the agent's eye center.
+These two point estimates are sufficient to calculate a vector that points toward the attentional focus of the agent.
+Extending this gaze vector to the ground points to the target's location.
+Participants are thought to sample from a normal distribution around the true gaze vector.
+Individuals would differ in how wide their distribution around the true gaze vector is.
+The wider the distribution around the true gaze vector, the more uncertain participants are in estimating the agent's focus of attention.
+The so-called inferential component in our model describes this distribution width and represents how accurately the participant infers the target location based on the agent's pupil location.
+
+The geometry of sampling from a distribution around the gaze vector leads to an interesting, testable group-level prediction.
+As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
+We describe this as a "headlight distribution": when the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them (Imagine a similar phenomenon: pointing a torch light to the ground.
+When one directs the light straight onto the ground, the light beam is clearly defined and smaller than when one points the torch light further away from oneself).
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.
+If our data matches the pattern of this model prediction, this speaks for the gaze model.
+
+However, participants who are overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
+To accommodate this, we designed two models that represent alternatives about how participants solve the TANGO, ignoring the agent's gaze.
+One alternative model estimates how likely a participant engages in random guessing.
+This acts like a coin toss, as sampling from a uniform distribution over all possible coordinates.
+The other alternative model explores the possibility of a center bias: it estimates how likely a participant shows a bias toward the center of the screen.
+Partipants' clicks could be drawn toward the center since the agent and the starting point of the balloon are located here.
+
+With our modeling framework, we can formalize whether a participant (A) uses the available gaze information at all and (B) how accurately they are in using this gaze information.
+Regarding developmental change, we hypothesize that a dual process could explain the development of gaze understanding: The older children are, the more likely they are to use gaze as a cue, and the more precise they become at it.
 
@@
 
-Our cognitive model attempts to explain the behavior of participants as being generated by one of two possible approaches.
-At each trial, a weighted coin toss determines whether the participant solves the task by \"guessing\" (sampling a clicking coordination from a uniform distribution over all possible coordinates) or by applying a gaze following model described below.
-Each participant has their own \"guessing probability\", determining the mixture of strategies they use.
-These per-participant parameters are modeled as having a Beta distribution over the population of participants.
-
-Our proposed gaze understanding model is a simplification of an originally three-component model, which consisted of: (1) a perceptual component, whereby the participant produces a noisy observation of the angle of each of the agent's eyes, (2) an inferential component, whereby the participant produces an estimate of the coordinate the agent is looking at based on the above noisy observations of eye angles and a model of how agents direct their eyes relative to where they are looking, and (3) a motor component, whereby the participant samples a location to click at from a distribution centered around the above estimate of where the agent is looking.
-Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components and so the model was simplified to include only the inferential component
-
-In the inferential component, the participant assumes that the agent\'s attention is focused on a single point coordinate and that the agent\'s left and right eyes are positioned by sampling (independently for each eye) eye angles from Normal distributions centered on the unique angle such that a line subtended from the center of the agent\'s eye through the center of its pupil will meet the attentional focal point (i.e.
-the modal behavior is to direct both eyes directly toward the focal point).
-The standard deviation of these distributions (equal for each eye) is a parameter that varies per participant, with higher values increasing the expected imprecision.
-When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant\'s assumptions about how wide an area of the agent\'s visual field their attention occupies.
-
-Because of the geometry of the situation (where a fixed amount of uncertainty about the agent\'s eye angle corresponds to a varying amount of uncertainty in the underlying point of attention as the eye angle varies), and because the participant integrates information from two eyes, the resulting posterior distribution (which the participant\'s mouse click is modeled as a sample from) does not belong to a standard parametric family, but can be easily numerically approximated as part of the inference process.
-
-We will compare this model against two models which represent alternatives about how participants' responses are generated.
-The \"random guessing\" model simply assumes that participants ignore the agent's gaze and randomly click on the screen (cf.
-coin toss, sampling a coordination from a uniform distribution over all possible coordinates).
-The \"motor noise\" model assumes that participants have no uncertainty about where the agent is looking but that their responses (clicks on the screen) come with a small amount of random noise (cf.
-motor component of our originally proposed model).
-We will then directly compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
-The models make different predictions about how participants\' clicks will be distributed for different locations of the target.
-We will visualise and evaluate these differences using correlations between the model predictions and the data.
+We compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
+The models make different predictions about how participants' clicks will be distributed for different target locations.
+We visualize and evaluate these differences using correlations between the model predictions and the data.
 
 ## Results
+
+(ref:figlab3) **Gaze funnel**
+
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gazefunnel_combined.png")
+```
+
+## Discussion
 
@@
 In addition, our model was able to recover "signature patterns" in the data.
-Both the model predictions and the actual raw data show that precision levels drop as the agent's gaze moves further away from the center.
+Both the model predictions and the observed data show that precision levels drop as the agent's gaze moves further away from the center.
 Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.
 
-(ref:figlab3) **Gaze funnel**
-
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/gazefunnel_combined.png")
-```
-
-## Discussion
+A limitation of our model is that we cannot disentangle how much of the participant's uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
+Initially, our proposed gaze model consisted of three components: (1) A perceptual component, whereby the participant produces a noisy observation of the agent's eye angle, (2) an inferential component, whereby the participant estimates the agent's point of attention based on the above perceptual component, and (3) a motor component, whereby the participant samples a click location from a distribution centered around the above estimate of the agent's attentional focus.
+Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components, so we simplified the gaze model to include only the inferential component.
 
@@
 
-## Open practices statement
-
-The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
-All experiments were pre-registered (<https://osf.io/zjhsc/>).
-
-## Funding
-
-This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers, and adults who participated in the study.
-We thank Jana Jurkat for her help with data collection.
-
-## Conflicts of interest
-
-The authors declare that they have no conflict of interest.
-
-## Consent to participate
-
-Informed consent was obtained from all individual participants included in the study or their legal guardians.
-
-## Authors' contributions
-
-The authors made the following contributions: \### TODO
+... can be found on the title page.
 
@@
 ```
-\newpage

### 2023-07-07 paper/manuscript.Rmd
update lifespan analysis

@@
 
-**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1^, & Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
+**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1^, Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
 
@@
 
--   development & individual differences in gaze understanding
--   verweis methods paper reliable differences kinder & adults.
--   kontinuerliche, systematische variation, wodrin? =\> model
+We aimed at assessing the developmental trajectory of gaze understanding across the lifespan.
+First, we were interested in how this ability changes with age: Is the ability to understand gaze fully developed once emerged in infancy and stays stable across the lifetime?
+Or do we fine-tune our already existing ability in early adulthood?
+Do we then potentially even notice an age decay later in adulthood?
+Second, we were interested in individual differences across the age groups.
+Does the variation between individuals decrease, the older they get?
+Do all adults reach the same level of precision in gaze understanding?
+
+Due to the sheer number of participants, we restricted this analysis to a remote sample.
+Pre-registrations can be found here: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
+The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+No.
+2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+Data was collected between May 2021 and April 2023.
 
@@
 
-Children came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
+We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age.
+
+The child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants.
+We recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
 They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income \~ 1,600€ as of 2021).
@@
 Information on demographics and socioeconomic status was not formally recorded on a participant level.
-The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-Data was collected between May 2021 and April 2023.
-
-We collected data from a remote child, teenager and adult sample.
-For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
-
-The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants.
-Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
 
@@
 Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision.
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
 For further information on age and gender of participants, see Table 1.
-
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
 
@@
 Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
-The target then fell behind a hedge (continuous task version).
-The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
+The target fell behind a hedge, while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
 In test trials, the target flight was covered so that participants could not see where the target landed.
-Participants' task was to locate the target by tracking the agent's gaze.
+Participant were tasked to locate the target by tracking the agent's gaze.
 They could respond by touching on the screen.
@@
 
+Adults completed the online study unsupervised.
+
 ## Analysis
 
-All test trials without voice-over description were included in our analyses.
 We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
@@
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed), in `R: imprecision ~ age_centered`).
+To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, cubic.
+In addition, we applied spline-based smooths splines [@burkner2017brms] and examined nonlinearity.
 
+The models predict the imprecision in each trial by age and include random effects for participant and symmetric target position: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
 Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
-We inspected the posterior distribution (mean and 95% Confidence Interval (CI)) for the age and data collection estimates.
+We inspect the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compare models using LOO and WAIC scores and model weights.
 
@@
 
+We found a clear non-linear development in gaze understanding across the lifespan.
+Early in childhood, children quickly enhance their level of proficiency.
+Performance peaks around early adulthood.
+There is a minor decay in elderly adulthood.
+Our Gaussian Process model indicated non-linearity: XXX. 
+The Bayesian changepoint analysis revealed two major shifts in gaze understanding during the lifespan.
+
 ## Discussion
@@
 A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
-
 Another point to keep in mind is that we used subtle eye movements as cues.
@@
 Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
+The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
 
-The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
+Regarding the sample of elderly adults, there is most likely a sampling bias present.
+Elderly which know how to participate in *Prolific* studies certainly might show greater cognitive fitness compared to their offline counterparts.
+
+Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
+We could circumvent these issues by applying the exact same task for the entire life span.
 
@@
 Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
-Therefore, we formalized the process of gaze understanding in a computational cognitive model.
+We formalized the process of gaze understanding in a computational cognitive model.
 Computational modeling frameworks allow researchers to establish mechanistic explanations of psychological phenomena [@grahek2021anatomy].
@@
 
-\-\-- explanation based on online experiment logic:
-
-The gaze model mirrors the logic of the TANGO programming code.
+The gaze model assumes participants use the agent's gaze as a cue to locate the target.
+This model mirrors the logic of the TANGO programming code.
 In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
 We then calculate a line between these two points: this is our gaze vector.
-Now, we also know the eyeball radius and, hence, the eyeball boundary.
-We then calculate the point of intersection at which the gaze vector meets the eyeball boundary.
+Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
 Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
-This way, the agent "looks at" the target.
+This way, the agent is animated to "look at" the target.
 
-In the computational gaze model, we assume that participants need to go through these steps in reversed order.
-The only information that they have readily available is the boundary of the eyeball and the final location of the agent's pupil (i.e., the intersection point).
-Now, we assume that participants estimate the center point of the agent's eyeball and then, estimate a line from the center point to the intersection point: this will serve as the gaze vector.
-Participants are then thought to extend this gaze vector until it reaches the ground.
-They apply this procedure to both eyes and integrate the information.
-This way, they can estimate the final target location.
+In the gaze model, we assume participants go through these steps in reverse order.
+Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
+Connecting these two point estimates as a line yields the true gaze vector: the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+Participants are assumed to sample gaze vectors from a Normal distribution centered around this true gaze vector.
+They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
 
-\-\-- explanation based on pre-reg:
-
-The gaze model assumes that the agent focuses their attention on a single point coordinate and that the agent's left and right eyes are positioned by sampling (independently for each eye) gaze vectors from Normal distributions centered on the unique vector that extends from the center of the agent's eye through the center of its pupil to finally meet the attentional focal point (i.e., the modal behavior is to direct both eyes directly toward the focal point).
-The standard deviation of these distributions (equal for each eye) is estimated for each individual participant, with higher values increasing the expected imprecision.
-When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant's assumptions about how wide an area of the agent's visual field their attention occupies.
-
-\-\-- alternative explanation:
-
-The gaze model assumes participants use the agent's gaze as a cue to locate the target.
-Participants are assumed to observe the current location of the pupil and estimate the agent's eye center.
-These two point estimates are sufficient to calculate a vector that points toward the attentional focus of the agent.
-Extending this gaze vector to the ground points to the target's location.
-Participants are thought to sample from a normal distribution around the true gaze vector.
-Individuals would differ in how wide their distribution around the true gaze vector is.
-The wider the distribution around the true gaze vector, the more uncertain participants are in estimating the agent's focus of attention.
-The so-called inferential component in our model describes this distribution width and represents how accurately the participant infers the target location based on the agent's pupil location.
+Individuals differ in how wide their distribution around the true gaze vector is.
+The model's inferential component estimates the standard deviation of these distributions for each individual participant.
+With higher standard deviations, participants are expected to show increasing imprecision in estimating the target location.
 
@@
 As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
-We describe this as a "headlight distribution": when the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them (Imagine a similar phenomenon: pointing a torch light to the ground.
-When one directs the light straight onto the ground, the light beam is clearly defined and smaller than when one points the torch light further away from oneself).
+We describe this as a "headlight distribution": when the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
+For illustrative purposes, imagine a similar phenomenon: pointing a torch light to the ground.
+When one directs the torch light straight onto the ground, the light beam is clearly defined and smaller than when one points the torch light further away from oneself.
 Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.
@@
 However, participants who are overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
-To accommodate this, we designed two models that represent alternatives about how participants solve the TANGO, ignoring the agent's gaze.
+To accommodate this, we designed two models that represent alternatives about how participants solve the TANGO when ignoring the agent's gaze.
 One alternative model estimates how likely a participant engages in random guessing.
-This acts like a coin toss, as sampling from a uniform distribution over all possible coordinates.
-The other alternative model explores the possibility of a center bias: it estimates how likely a participant shows a bias toward the center of the screen.
-Partipants' clicks could be drawn toward the center since the agent and the starting point of the balloon are located here.
+This behaves like a coin toss, sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
+The other alternative model estimates how likely a participant shows a center bias.
+This is implemented as sampling from a Normal distribution with the center of the screen as the mean and one target width as the standard deviation.
+Partipants' clicks could be drawn toward the center since the agent and the starting point of the balloon are located there.
 
-With our modeling framework, we can formalize whether a participant (A) uses the available gaze information at all and (B) how accurately they are in using this gaze information.
-Regarding developmental change, we hypothesize that a dual process could explain the development of gaze understanding: The older children are, the more likely they are to use gaze as a cue, and the more precise they become at it.
+With our modeling framework, we can formalize whether a participant (A) uses the available gaze information at all and (B) how accurately they are in using this gaze information to locate the target.
+Regarding developmental change, we hypothesize that a dual process could explain the development of gaze understanding: The older children are, the more likely they are to use gaze as a cue, and the more precise they become at using it to locate the target.
 
@@
 
-The sample included `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children consisting of `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls), and `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
-
+The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
 Data of children was collected in kindergartens located in Leipzig, Germany.
 The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
+
+In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
 Adults were recruited over *Prolific* [@palan2018prolific].
-Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that had completed the study.
 
@@
 
-As in the previous study, participants completed the continuous version of the TANGO [@prein2022tango].
+We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2022tango].
 Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
@@
 Both the model predictions and the observed data show that precision levels drop as the agent's gaze moves further away from the center.
-Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same mechanism to solve the task.
 
-A limitation of our model is that we cannot disentangle how much of the participant's uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
-Initially, our proposed gaze model consisted of three components: (1) A perceptual component, whereby the participant produces a noisy observation of the agent's eye angle, (2) an inferential component, whereby the participant estimates the agent's point of attention based on the above perceptual component, and (3) a motor component, whereby the participant samples a click location from a distribution centered around the above estimate of the agent's attentional focus.
+A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
+Initially, our proposed gaze model consisted of three components: (1) a perceptual component, whereby the participant produces a noisy observation of the agent's eye angle, (2) an inferential component, whereby the participant estimates the agent's point of attention based on the above perceptual component, and (3) a motor component, whereby the participant samples a click location from a distribution centered around the above estimate of the agent's attentional focus.
 Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components, so we simplified the gaze model to include only the inferential component.

### 2023-07-07 stats/gaussianprocess.Rmd
update lifespan analysis

---
title: "Gaussian process"
author: "Julia Prein"
date: "2023-07-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

```{r load_data}
lifespan_data <- readRDS("../data/tango-lifespan.rds")

mdata <- lifespan_data %>% 
  mutate(
    symmetric_position = abs(960 - target_center_x),
    symmetric_position = scale(symmetric_position) %>% round(2),
    trial_nr = trial_nr - min(trial_nr), 
    imprecision = click_dist_balloons + 0.005,
  ) %>% 
  select(subj_id, age, age_centered, symmetric_position, trial_nr, click_dist_balloons, imprecision)
```

```{r model_triallevel}
mgp_triallevel <- brm(imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE) + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id),
                    data = mdata,
                    family = lognormal(),
                    warmup = 5000, 
                    iter   = 20000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr")

mgp_triallevel <- mgp_triallevel %>% add_criterion(c("loo","waic"))

write.csv(mgp_triallevel, "../saves/mgp_triallevel.csv", quote = F, row.names = F)
saveRDS(mgp_triallevel, "../saves/mgp_triallevel.rds")
```

```{r plot_triallevel}
mgp_triallevel

pp_check(mgp_triallevel)

conditional_effects(mgp_triallevel, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)
```

```{r model_aggregated}
mdata_aggregated <- mdata %>% 
  group_by(subj_id, age, age_centered) %>% 
  summarize(mean_imprecision = mean(click_dist_balloons, na.rm = TRUE))

mgp_aggregated <- brm(mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
                    data = mdata,
                    family = lognormal(),
                    warmup = 5000, 
                    iter   = 20000, 
                    chains = 4, 
                    cores  = 4, 
                    threads = threading(8), 
                    control = list(adapt_delta = 0.95), 
                    backend = "cmdstanr")

mgp_aggregated <- mgp_aggregated %>% add_criterion(c("loo","waic"))

write.csv(mgp_aggregated, "../saves/mgp_aggregated.csv", quote = F, row.names = F)
saveRDS(mgp_aggregated, "../saves/mgp_aggregated.rds")
```

```{r plot_aggregated}
mgp_aggregated

pp_check(mgp_aggregated)

conditional_effects(mgp_aggregated, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)
```

### 2023-07-07 stats/lifespan.Rmd
update lifespan analysis

@@
 saveRDS(mgaussianprocess, "../saves/lifespan_mgaussianprocess.rds")
-
-## spline model
-# https://discourse.mc-stan.org/t/smooth-spline-modeling-with-brm/6364/2
-msplines <- brm(mean_dist ~ s(age_centered),
-                    data = mdata,
-                    family = lognormal(),
-                    warmup = 2000,
-                    iter   = 6000,
-                    chains = 4,
-                    cores  = 4,
-                    threads = threading(8),
-                    control = list(adapt_delta = 0.95),
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
-
-msplines
-
-pp_check(msplines)
-
-conditional_effects(msplines, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-write.csv(msplines, "../saves/lifespan_msplines.csv", quote = F, row.names = F)
-saveRDS(msplines, "../saves/lifespan_msplines.rds")
-
-## playing around with parameters
-msplines2 <- brm(mean_dist ~ s(age_centered, k = 2),
-                    data = mdata,
-                    family = lognormal(),
-                    warmup = 2000,
-                    iter   = 6000,
-                    chains = 4,
-                    cores  = 4,
-                    threads = threading(8),
-                    control = list(adapt_delta = 0.95),
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
-
-conditional_effects(msplines2, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-write.csv(msplines2, "../saves/lifespan_msplines2.csv", quote = F, row.names = F)
-saveRDS(msplines2, "../saves/lifespan_msplines2.rds")
-
-# 3
-msplines3 <- brm(mean_dist ~ s(age_centered, k = 3),
-                    data = mdata,
-                    family = lognormal(),
-                    warmup = 2000,
-                    iter   = 6000,
-                    chains = 4,
-                    cores  = 4,
-                    threads = threading(8),
-                    control = list(adapt_delta = 0.95),
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
-
-conditional_effects(msplines3, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-write.csv(msplines3, "../saves/lifespan_msplines3.csv", quote = F, row.names = F)
-saveRDS(msplines3, "../saves/lifespan_msplines3.rds")
-
-# 4
-msplines4 <- brm(mean_dist ~ s(age_centered, k = 4),
-                    data = mdata,
-                    family = lognormal(),
-                    warmup = 2000,
-                    iter   = 6000,
-                    chains = 4,
-                    cores  = 4,
-                    threads = threading(8),
-                    control = list(adapt_delta = 0.95),
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
-
-conditional_effects(msplines4, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-write.csv(msplines4, "../saves/lifespan_msplines4.csv", quote = F, row.names = F)
-saveRDS(msplines4, "../saves/lifespan_msplines4.rds")
-
-# 5
-msplines5 <- brm(mean_dist ~ s(age_centered, k = 5),
-                    data = mdata,
-                    family = lognormal(),
-                    warmup = 2000,
-                    iter   = 6000,
-                    chains = 4,
-                    cores  = 4,
-                    threads = threading(8),
-                    control = list(adapt_delta = 0.95),
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
-
-conditional_effects(msplines5, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-write.csv(msplines5, "../saves/lifespan_msplines5.csv", quote = F, row.names = F)
-saveRDS(msplines5, "../saves/lifespan_msplines5.rds")
 ```
@@
 # mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
-# msplines <- readRDS("../saves/lifespan_msplines.rds")
 
-mcomparison <- loo_compare(mlinear, mquadratic, mcubic, mgaussianprocess, msplines, msplines2, msplines3, msplines4, msplines5, criterion = "waic") %>% 
+mcomparison <- loo_compare(mlinear, mquadratic, mcubic, mgaussianprocess, criterion = "waic") %>% 
   as_tibble(rownames = "model") %>%
-  left_join(as_tibble(model_weights(mlinear, mquadratic, mcubic, mgaussianprocess, msplines, msplines2, msplines3, msplines4, msplines5, weights = "waic"), rownames = "model")) %>% 
+  left_join(as_tibble(model_weights(mlinear, mquadratic, mcubic, mgaussianprocess, weights = "waic"), rownames = "model")) %>% 
   rename(modelweight = value)
@@
 ```{r draws_winning_model}
-msplines <- readRDS("../saves/lifespan_msplines.rds")
+# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
 
 mdraws <- mdata %>%
-  add_predicted_draws(msplines) %>% 
+  add_predicted_draws(mgaussianprocess) %>% 
   ungroup() %>% 
@@
 
-# prediction_plot
-
 # saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
 ggsave("../figures/lifespan_modelplot.png", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+```{r playground}
+# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+
+# model checks: 
+# density plot overlay of the original response values (the thick black line) with 10 draws from the posterior distribution of the model
+pp_check(mgaussianprocess)
+
+# empirical cumulative distribution function of the observations and random draws from the model posterior:
+pp_check(mgaussianprocess, type = "ecdf_overlay")
+
+# plots distribution of estimates & chains converging
+plot(mgaussianprocess)
+
+# model plotting
+spline_plot_data <- fitted(mgaussianprocess) %>% 
+  data.frame() %>% 
+  bind_cols(mdata)
+
+spline_plot_data %>% 
+  ggplot(aes(x = age, y = mean_dist, ymin = Q2.5, ymax = Q97.5)) + 
+  geom_hline(yintercept = fixef(mgaussianprocess)[1, 1], linetype = 2) +
+  geom_point(color = "steelblue") +
+  geom_ribbon(alpha = 2/3) +
+  labs(x = "Age",
+       y = "Imprecision") +
+  theme_classic()
+
+# predictions & actual raw data underneath
+conditional_effects(mgaussianprocess, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T)
+
+# get intercepts
+posterior_summary(mgaussianprocess)
 ```
@@
   geom_smooth(method = lm, formula = y ~ splines::bs(x, 5), se = F, aes(colour = "E")) +
+  geom_smooth(method = gam, formula = y ~ s(x), se = F, aes(colour = "F")) +
   scale_fill_brewer(palette = "Greys") + 
@@
   scale_color_manual(name = "Smooth method", 
-                     breaks = c("A", "B", "C", "D", "E"),
-                     values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"),
-                     labels = c("linear", "quadratic", "cubic", "loess", "splines (k=5)")) +
+                     breaks = c("A", "B", "C", "D", "E", "F"),
+                     values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D", "orange"),
+                     labels = c("linear", "quadratic", "cubic", "loess", "splines (k=5)", "splines (default)")) +
   labs(x = "Age in years", y = "Mean click distance in target widths")

### 2023-07-10 stats/gaussianprocess.Rmd
update gaussian process models

@@
 mgp_aggregated <- brm(mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
-                    data = mdata,
+                    data = mdata_aggregated,
                     family = lognormal(),
@@
 ```
+
+```{r compare_models}
+nd_triallevel <- mdata %>% 
+  select(-c(imprecision, click_dist_balloons)) %>% 
+  mutate(symmetric_position = 0, trial_nr = 0)
+
+pred_triallevel <- fitted(mgp_triallevel, newdata = nd_triallevel, re_formula = NA) %>% as_tibble() %>% bind_cols(nd_triallevel)
+
+# same for aggregate
+
+nd_aggregated <- mdata_aggregated %>% 
+  select(-c(mean_imprecision))
+
+pred_aggregated <- fitted(mgp_aggregated, newdata = nd_aggregated, re_formula = NA) %>% as_tibble() %>% bind_cols(nd_aggregated)
+
+pred_combined <-full_join(pred_aggregated %>% mutate(model = "subject level"), pred_triallevel %>% mutate(model = "trial level"))
+
+# plot
+
+ggplot() +
+
+  geom_smooth(
+    data = pred_combined, 
+    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = model, col = model), 
+    stat = "identity", size = 0.5, alpha = 0.15
+  ) 
+```
+
+```{r aggregated_plot}
+ggplot() +
+
+  geom_jitter(
+    data = mdata_aggregated, 
+    aes(x = age, y = mean_imprecision), 
+    col = "darkgrey", alpha = 0.75
+  ) +
+
+  geom_smooth(
+    data = pred_aggregated, 
+    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
+    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
+  ) +
+
+  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width")
+```

### 2023-07-10 stats/lifespan.Rmd
clean up, add Bayesian changepoint (Rbeast)

@@
 library(cmdstanr) # modeling
+library(Rbeast) # Bayesian change point analysis
 check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
@@
   group_by(subj_id, age, age_centered) %>% 
-  summarize(mean_dist = mean(click_dist_balloons, na.rm = TRUE))
+  summarize(mean_imprecision = mean(click_dist_balloons, na.rm = TRUE))
 ```
@@
 
+# MODEL COMPARISON FOR DEVELOPMENTAL TRAJECTORY
+
 ```{r models, message=FALSE, warning=FALSE}
 # linear age
-mlinear <- brm(mean_dist ~ age_centered,
+mlinear <- brm(mean_imprecision ~ age_centered,
                     data = mdata,
@@
 ## quadratic age
-mquadratic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2),
+mquadratic <- brm(mean_imprecision ~ 1 + age_centered + I(age_centered^2),
                     data = mdata,
@@
 ## cubic age
-mcubic <- brm(mean_dist ~ 1 + age_centered + I(age_centered^2) + I(age_centered^3),
+mcubic <- brm(mean_imprecision ~ 1 + age_centered + I(age_centered^2) + I(age_centered^3),
                     data = mdata,
@@
 ## gaussian process model
-mgaussianprocess <- brm(mean_dist ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
+mgaussianprocess <- brm(mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE),
                     data = mdata,
                     family = lognormal(),
-                    warmup = 2000, 
-                    iter   = 6000, 
+                    warmup = 5000, 
+                    iter   = 20000, 
                     chains = 4, 
@@
                     control = list(adapt_delta = 0.95), 
-                    backend = "cmdstanr") %>% add_criterion(c("loo","waic"))
+                    backend = "cmdstanr")
 
-mgaussianprocess
+mgaussianprocess <- mgaussianprocess %>% add_criterion(c("loo","waic"))
 
@@
 
-```{r lifespan_modelcomparison}
+```{r modelcomparison}
 # mlinear <- readRDS("../saves/lifespan_mlinear.rds")
@@
 
-```{r draws_winning_model}
+```{r draws_winningmodel}
 # mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
 
-mdraws <- mdata %>%
-  add_predicted_draws(mgaussianprocess) %>% 
-  ungroup() %>% 
-  select(-c(.row, .chain, .iteration)) %>%
-  rename(draw = .draw, predicted_value = .prediction)
+# mdraws <- mdata %>%
+#   add_predicted_draws(mgaussianprocess) %>% 
+#   ungroup() %>% 
+#   select(-c(.row, .chain, .iteration)) %>%
+#   rename(draw = .draw, predicted_value = .prediction)
+# 
+# write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
+# saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
 
-write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
-saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
+nd <- mdata %>% 
+  select(-c(mean_imprecision))
+
+pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(nd) 
 ```
 
-```{r prediction_plot_winning_model}
-### this sections takes a while to run
+# CHANGE POINT ANALYSIS
 
-# mdraws <- readRDS("../saves/lifespan_mdraws.rds")
+```{r changepoints}
+x <- mdata %>% arrange(age) %>% pull(age)
+y <- mdata %>% arrange(age) %>% pull(mean_imprecision)
 
-mdraws %>%
-  ggplot(aes(x = age)) +
-  stat_lineribbon(aes(y = predicted_value), .width = c(.95), colour = "#006c66", fill = "lightgrey") +
-  geom_jitter(aes(y = mean_dist), colour = "darkgrey", size = 1.5, alpha = 0.8) +
-  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) +
-  scale_y_continuous(limits = c(0,4)) +
-  labs(x = "Age in years", y = "Mean click distance in target widths")
+## irregular time intervals
+ibeast <- beast.irreg(y = y, time = x, season = "none", 
+            torder.minmax = c(0, 0), # for constant
+            tcp.minmax = c(0, 5), # we assume 3, allow some room for exploration
+            tseg.min = 10, 
+            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            ci = TRUE)
 
-# saveRDS(prediction_plot, file = "../saves/lifespan_modelplot.rds")
-ggsave("../figures/lifespan_modelplot.png", width = 8, height = 5, scale = 1, bg = "white")
+print(ibeast)
+plot(ibeast)
+
+ibeast$trend$cp
 ```
 
-```{r playground}
-# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+# PLOT
 
-# model checks: 
-# density plot overlay of the original response values (the thick black line) with 10 draws from the posterior distribution of the model
-pp_check(mgaussianprocess)
+```{r plot}
+ggplot() +
 
-# empirical cumulative distribution function of the observations and random draws from the model posterior:
-pp_check(mgaussianprocess, type = "ecdf_overlay")
+  geom_jitter(
+    data = mdata, 
+    aes(x = age, y = mean_imprecision), 
+    col = "darkgrey", alpha = 0.75
+  ) +
 
-# plots distribution of estimates & chains converging
-plot(mgaussianprocess)
+  geom_smooth(
+    data = pred, 
+    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
+    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
+  ) +
 
-# model plotting
-spline_plot_data <- fitted(mgaussianprocess) %>% 
-  data.frame() %>% 
-  bind_cols(mdata)
+  # TODO: add lines where changepoints
+  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
 
-spline_plot_data %>% 
-  ggplot(aes(x = age, y = mean_dist, ymin = Q2.5, ymax = Q97.5)) + 
-  geom_hline(yintercept = fixef(mgaussianprocess)[1, 1], linetype = 2) +
-  geom_point(color = "steelblue") +
-  geom_ribbon(alpha = 2/3) +
-  labs(x = "Age",
-       y = "Imprecision") +
-  theme_classic()
-
-# predictions & actual raw data underneath
-conditional_effects(mgaussianprocess, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
-
-# get intercepts
-posterior_summary(mgaussianprocess)
+  labs(x = "Age in years", y = "Average imprecision in target width")
 ```
-
-```{r smooths}
-lifespan_smooths <- mdata %>%
-  ggplot(aes(x = age, y = mean_dist)) +  
-  geom_jitter(colour = "grey", size = 1.5, alpha = 0.8) + 
-  geom_smooth(method = lm, se = F, aes(colour = "A")) +
-  geom_smooth(method = lm, formula = y ~ poly(x, 2), se = F, aes(colour = "B")) +
-  geom_smooth(method = lm, formula = y ~ poly(x, 3), se = F, aes(colour = "C")) +
-  geom_smooth(method = loess, se = F, aes(colour = "D")) +
-  geom_smooth(method = lm, formula = y ~ splines::bs(x, 5), se = F, aes(colour = "E")) +
-  geom_smooth(method = gam, formula = y ~ s(x), se = F, aes(colour = "F")) +
-  scale_fill_brewer(palette = "Greys") + 
-  scale_x_continuous(limits = c(0,80), breaks = seq(0, 80, 5)) + 
-  scale_y_continuous(limits = c(0,4)) + 
-  scale_color_manual(name = "Smooth method", 
-                     breaks = c("A", "B", "C", "D", "E", "F"),
-                     values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D", "orange"),
-                     labels = c("linear", "quadratic", "cubic", "loess", "splines (k=5)", "splines (default)")) +
-  labs(x = "Age in years", y = "Mean click distance in target widths")
-
-lifespan_smooths
-
-saveRDS(lifespan_smooths, file = "../saves/lifespan_smooths.rds")
-ggsave("../figures/lifespan_smooths.png", width = 10, height = 6, scale = 0.7, bg = "white")
-```

### 2023-07-10 stats/lifespan.Rmd
let analysis run, plot gp & cps together

@@
 saveRDS(lifespan_sample, "../saves/lifespan_sample.rds")
-```
-
-```{r plot}
-lifespan_plot <- lifespan_data %>% 
-  group_by(subj_id, age, age_group) %>%
-  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = age, y = mean)) +
-  geom_point(color = "darkgrey", alpha = 0.5) +
-  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
-  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
-  labs(x = "Age in years", y = "Average imprecision in target widths")
-
-lifespan_plot
-
-ggsave("../figures/lifespan_plot.png", width = 8, height = 4, scale = 1.2)
-saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
 ```
@@
 conditional_effects(mcubic, ndraws = 200, spaghetti = TRUE) %>% 
-  plot(points = T)
+  plot(points = T, yaxp = c(0,4,1))
 
@@
 
-# mdraws <- mdata %>%
-#   add_predicted_draws(mgaussianprocess) %>% 
-#   ungroup() %>% 
-#   select(-c(.row, .chain, .iteration)) %>%
-#   rename(draw = .draw, predicted_value = .prediction)
-# 
-# write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
-# saveRDS(mdraws, "../saves/lifespan_mdraws.rds")
-
 nd <- mdata %>% 
@@
 pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(nd)
+
+write.csv(pred, "../saves/lifespan_mgpdraws.csv", quote = F, row.names = F)
+saveRDS(pred, "../saves/lifespan_mgpdraws.rds")
 ```
@@
 
+# how many changepoints?
+ibeast$trend$ncp_median
+
+# location of changepoints
 ibeast$trend$cp
+
+# pull out all relevant change points
+cps <- tibble(
+          cp = ibeast$trend$cp[1:ibeast$trend$ncp_median], 
+          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,1], 
+          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,2]
+       )
+
+saveRDS(ibeast, "../saves/lifespan_ibeast.rds")
+
+write.csv(cps, "../saves/lifespan_ibeast_cps.csv", quote = F, row.names = F)
+saveRDS(cps, "../saves/lifespan_ibeast_cps.rds")
 ```
@@
 
-  # TODO: add lines where changepoints
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
+  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
+  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +
+
   scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
@@
   labs(x = "Age in years", y = "Average imprecision in target width")
+
+# ZOOM IN
+ggplot() +
+
+  geom_jitter(
+    data = mdata, 
+    aes(x = age, y = mean_imprecision), 
+    col = "darkgrey", alpha = 0.75
+  ) +
+
+  geom_smooth(
+    data = pred, 
+    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
+    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
+  ) +
+
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
+
+  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) + 
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
+
+  coord_cartesian(xlim = c(3, 10), ) +
+
+  labs(x = "Age in years", y = "Average imprecision in target width")
 ```

### 2023-07-12 paper/manuscript.Rmd
update lifespan analysis, move around cogn model

@@
 wordcount         : "xxx max 8000"
-bibliography      : ["../../references.bib"]
 floatsintext      : yes
@@
 output            : papaja::apa6_word
-header-includes:
+header-includes   :
   - \usepackage{setspace}
   - \captionsetup[figure]{font={stretch=1}}
-editor_options: 
+editor_options    : 
   markdown: 
     wrap: sentence
+bibliography      : "../../references.bib"
 ---
@@
 
-# Lifespan
+# Study 1: Gaze understanding across the lifespan
 
@@
 
-We used the continuous version of the TANGO [@prein2022tango].
+We used the continuous version of the TANGO [@prein2023tango].
 The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; @prein2022tango].
+The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; @prein2023tango].
 
@@
 To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, cubic.
-In addition, we applied spline-based smooths splines [@burkner2017brms] and examined nonlinearity.
+In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
+The models predicted imprecision by age (continuous).
+[^1] Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, aggregated across trials, and modeled by a `lognormal` distribution.
+We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using LOO and WAIC scores and model weights.
 
-The models predict the imprecision in each trial by age and include random effects for participant and symmetric target position: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
-Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a `lognormal` distribution.
-We inspect the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compare models using LOO and WAIC scores and model weights.
+[^1]: Originally, our models implemented the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
+    However, the Gaussian Process model was computationally heavy.
+    To circumvent issues of convergence and for practicability, we simplified the model structure to include only age as an effect.
+    In the Supplements, you can find a comparison between the original and the here reported model structures.
+    Essentially, the model predictions did not differ notably.
+
+To further assess developmental change, we performed a Bayesian change-point analysis, using the package `RBeast` [@zhao2019detecting].
+The function `beast.irreg` handled the irregular nature of our series, which did not have the same number of data points for each year in age.
+We were interested in finding the most prominent, most likely change-points in our data, assuming a constant mean (i.e., a flat line) within each segment.
+Additionally, we wanted to avoid "overreactions" to individual outlying data points.
+Therefore, we restricted our search to a maximum number of five change-points and a minimum length of 9.1245 data points between change-points (corresponding to the product of mean age difference between consecutive points \* mean number of data points within 3 years \* 3).
+We inspected the probability of number of change-points and the locations of these change-points (mean and 95% CrI).
+See Supplements for change-point analyses with differently set parameters.
 
@@
 
+[TODO] report model comparison
+
 We found a clear non-linear development in gaze understanding across the lifespan.
-Early in childhood, children quickly enhance their level of proficiency.
-Performance peaks around early adulthood.
-There is a minor decay in elderly adulthood.
+Early in childhood, children quickly enhanced their level of proficiency.
+Performance peaked around early adulthood.
+There was a minor decay in elderly adulthood.
 Our Gaussian Process model indicated non-linearity: XXX.
-The Bayesian changepoint analysis revealed two major shifts in gaze understanding during the lifespan.
+The Bayesian change-point analysis revealed four major shifts in gaze understanding during the lifespan: We see a very rapid initial improvement in early childhood (3 change-points in rapid succession), followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
 
@@
 Three-year-olds were surprisingly inaccurate in their responses.
-One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze following.
-Contrasting our results with previous findings on infant gaze following, this explanation is unlikely.
+One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze-following.
+Contrasting our results with previous findings on infant gaze-following, this explanation is unlikely.
 A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
@@
 
-# Computational cognitive model
+# Study 2: Computational cognitive model
 
 Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
-The TANGO has previously been proven reliable for capturing inter-individual differences in gaze understanding [@prein2022tango].
+The TANGO has previously been proven reliable for capturing inter-individual differences in gaze understanding [@prein2023tango].
 The variation between participants is thus likely genuine and not due to random noise.
 Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
-We formalized the process of gaze understanding in a computational cognitive model.
+We present a theory of gaze understanding that explains how children use all available information to make inferences about the agent's gaze and its attentional focus, which leads them to correctly identify the target position.
+We formalize this inference process in a computational cognitive model.
+
 Computational modeling frameworks allow researchers to establish mechanistic explanations of psychological phenomena [@grahek2021anatomy].
@@
 
-With our model, we seek to explain how participants solved the TANGO.
-Our modeling framework consists of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+We seek to explain how participants solved the TANGO.
+Our gaze model assumes that participants use available gaze information to infer the target location.
+We quantify how well our model explains the gaze understanding process by comparing it to two alternative models that make different assumptions of which information children use and where they consequently click to locate the target.
+Therefore, our modeling framework consists of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
 We gauge which model can best explain our data by conducting a model comparison.
-
-The gaze model assumes participants use the agent's gaze as a cue to locate the target.
-This model mirrors the logic of the TANGO programming code.
-In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
-We then calculate a line between these two points: this is our gaze vector.
-Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
-Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
-This way, the agent is animated to "look at" the target.
-
-In the gaze model, we assume participants go through these steps in reverse order.
-Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
-Connecting these two point estimates as a line yields the true gaze vector: the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-Participants are assumed to sample gaze vectors from a Normal distribution centered around this true gaze vector.
-They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
-
-Individuals differ in how wide their distribution around the true gaze vector is.
-The model's inferential component estimates the standard deviation of these distributions for each individual participant.
-With higher standard deviations, participants are expected to show increasing imprecision in estimating the target location.
-
-The geometry of sampling from a distribution around the gaze vector leads to an interesting, testable group-level prediction.
-As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
-We describe this as a "headlight distribution": when the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
-For illustrative purposes, imagine a similar phenomenon: pointing a torch light to the ground.
-When one directs the torch light straight onto the ground, the light beam is clearly defined and smaller than when one points the torch light further away from oneself.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.
-If our data matches the pattern of this model prediction, this speaks for the gaze model.
-
-However, participants who are overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
-To accommodate this, we designed two models that represent alternatives about how participants solve the TANGO when ignoring the agent's gaze.
-One alternative model estimates how likely a participant engages in random guessing.
-This behaves like a coin toss, sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
-The other alternative model estimates how likely a participant shows a center bias.
-This is implemented as sampling from a Normal distribution with the center of the screen as the mean and one target width as the standard deviation.
-Partipants' clicks could be drawn toward the center since the agent and the starting point of the balloon are located there.
 
@@
 
-We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2022tango].
+We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2023tango].
 Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
@@
 
-We compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
-The models make different predictions about how participants' clicks will be distributed for different target locations.
+Our goal was to describe the inferential process by which participants locate the target.
+We compared three computational cognitive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+All cognitive models and model comparisons were implemented in WebPPL [@goodman2014design].
+
+The gaze model assumes participants use the agent's gaze as a cue to locate the target.[^2]
+Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
+Connecting these two point estimates as a line yields a gaze vector: the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+This inferential process involves some uncertainty about the true center of the eyeball.
+Participants are assumed to sample gaze vectors from a Normal distribution centered around the true gaze vector.
+They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
+
+[^2]: This model mirrors the logic of the TANGO programming code.
+    In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
+    We then calculate a line between these two points: this is our gaze vector.
+    Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
+    Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
+    This way, the agent is animated to "look at" the target.
+    In the gaze model, we assume participants go through these steps in reverse order.
+
+Now, individuals can differ in how wide their distribution around the true gaze vector is.
+The model's inferential component, α, estimates the standard deviation of the distribution for each individual participant.
+With higher standard deviations (i.e., increased α), participants are expected to show decreasing precision in estimating the target location.
+The model assumes that the sensitivity to the available gaze information changes with age.
+
+The geometry of sampling from a distribution around the gaze vector leads to an interesting, testable group-level prediction.
+As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
+When the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
+For illustrative purposes, imagine a similar phenomenon: pointing a torch light to the ground.
+When one directs the torchlight straight onto the ground, the light beam is clearly defined and smaller than when one points the torchlight further away from oneself.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.
+If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding, with testable model predictions.
+
+To gauge the plausibility of our gaze model, we implemented two models that represent alternatives about how participants solve the TANGO.
+Participants who are overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
+The alternative models, therefore, do not assume that participants make use of the gaze cue.
+The first alternative model estimates how likely a participant engages in random guessing.
+This behaves like a coin toss, sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
+The second alternative model estimates how likely a participant shows a center bias: Participants' clicks could be drawn toward the screen center since the agent and the starting point of the balloon are located there.
+This bias is implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
+
+Our three proposed models make different predictions about how participants' clicks will be distributed for different target locations.
 We visualize and evaluate these differences using correlations between the model predictions and the data.
+Furthermore, we evaluated these probabilistic models based on the marginal likelihood of the data under each model.
+The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor.
+This factor quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
+It can be used to estimate how much more likely the data under one model are compared to the other.
+Bayes Factors implicitly consider model complexity (i.e., Bayesian Occam's razor): models with more parameters often have a broader prior distribution over parameters, which might weaken potential gains in predictive accuracy.
+Details on models, including code to run the models, information about priors for parameter estimation, and Markov chain Monte Carlo settings, can be found in the associated online repository.
 
 ## Results
+
+When we compared the gaze model to the two competitor models, we found little support for the two alternatives.
+Comparing the models using marginal likelihood of the data under each model, the data were XXX [TODO] more likely under the gaze model compared to the random clicking or center bias model.
+
+For the gaze model, we found a high similarity between the model predictions and the observed data across the entire age range.
+The developmental trajectory that we observed in the data closely resembled the predictions of the model.
+The model explained XXX% [TODO] of the variance in the data.
 
@@
 
+Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan.
+To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
+Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
+We assume that children become increasingly sensitive to gaze cues but that the inference process remains the same.
+By conducting model comparisons, we could rule out that participants' responses can be explained by random guessing or a center bias.
+
 A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
@@
 
-In addition, our model was able to recover "signature patterns" in the data.
-Both the model predictions and the observed data show that precision levels drop as the agent's gaze moves further away from the center.
-Future research could use this signature in the data as evidence of whether diverse communities employ the same mechanism to solve the task.
+In addition, we observed differences in performance depending on where the agent looks.
+The observed data showed that precision levels dropped as the agent's gaze moved further away from the center.
+Our gaze model predictions recovered this "signature pattern" in the data.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
 
@@
 
-# Components of gaze understanding
+# Study 3: Components of gaze understanding
 
@@
 
-As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango].
+As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2023tango].
 To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^1]
+This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^3]
 
-[^1]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
+[^3]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
     Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal).
@@
 
-In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2022tango].
+In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2023tango].
 Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.

### 2023-07-12 stats/lifespan.Rmd
update lifespan analysis, move around cogn model

@@
                     family = lognormal(),
-                    warmup = 2000, 
-                    iter   = 6000, 
+                    warmup = 5000, 
+                    iter   = 20000, 
                     chains = 4, 

### 2023-07-12 stats/supplements_changepoint_parameters.Rmd
update lifespan analysis, move around cogn model

---
title: "Change point analysis"
author: "Julia Prein"
date: "03/21/2023"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

options(scipen = 999)
theme_set(theme_classic())

# Seed for random number generation
set.seed(42)
```

### Data preparation

```{r load_data}
lifespan_data <- readRDS("../data/tango-lifespan.rds")
```

```{r prepare_modeldata}
mdata <- lifespan_data %>% 
  group_by(subj_id, age, age_centered) %>% 
  summarize(mean_imprecision = mean(click_dist_balloons, na.rm = TRUE))

x <- mdata %>% arrange(age) %>% pull(age)
y <- mdata %>% arrange(age) %>% pull(mean_imprecision)
```

### BEASTs

```{r run_beasts, echo=T, message=FALSE, warning=FALSE, results=FALSE}
b1 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0), 
            tcp.minmax = c(0, 5),
            tseg.min = 10, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b2 <- beast.irreg(y = y, time = x, season = "none", 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b3 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b4 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 10), 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b5 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 10), 
            tseg.min = 50, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b6 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 10), 
            tseg.min = 100, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b7 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 3), 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b8 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 20), 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b9 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 100), 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

b10 <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0),
            tcp.minmax = c(0, 100), 
            tseg.min = 100, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)
```

```{r fct_printbeasts}
showBeast <- function(beast) {

  print(beast)
  plot(beast)
  print("...continuing to next beast")
}
```

```{r actually_printbeasts}
beasts <- list(b1, b2, b3, b4, b5, b6, b7, b8, b9, b10)

counter = 1

for (i in beasts) {
  print("")
  print("This is the BEAST...")
  print(counter)
  print("")

  showBeast(i)
  counter = counter + 1 
}
```

### Searching for reasonable minimum nr between change points

```{r}
mdata <- mdata %>% 
  ungroup() %>% 
  arrange(age) %>% 
  mutate(
    age_diff = lead(age) - age, 
    age_years = floor(age), 
    three_year_bins = case_match(age_years %% 3, 
                                 0 ~ age_years,
                                 1 ~ age_years-1,
                                 2 ~ age_years-2),
  ) %>% 
  select(-age_years)

mean_age_diff <- mean(mdata$age_diff, na.rm = T) %>% round(2)

mean_n_per_3y <- mdata %>% 
  group_by(three_year_bins) %>% 
  summarize(n_per_bin = n()) %>% 
  summarize(mean_n_per_3y = mean(n_per_bin) %>% round(2)) %>% 
  pull(mean_n_per_3y)

mean_age_diff * mean_n_per_3y * 3

3/mean_age_diff
```

```{r final_beast, message=FALSE, warning=FALSE}
bfinal <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0), 
            tcp.minmax = c(0, 5),
            tseg.min = mean_age_diff * mean_n_per_3y * 3, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)
```

```{r final_beast}
showBeast(bfinal)

# pull out all relevant change points
cps <- tibble(
          cp = bfinal$trend$cp[1:bfinal$trend$ncp_median], 
          lowerCrI = bfinal$trend$cpCI[1:bfinal$trend$ncp_median,1], 
          upperCrI = bfinal$trend$cpCI[1:bfinal$trend$ncp_median,2]
       )
```

### 2023-07-19 stats/lifespan.Rmd
adjust lifespan plot (blue spaghetti)

@@
 saveRDS(lifespan_sample, "../saves/lifespan_sample.rds")
+```
+
+```{r variation}
+lifespan_data %>% 
+  group_by(age_group) %>%
+  summarise(
+    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_min = min(click_dist_balloons, na.rm = T),
+    imprecision_max = max(click_dist_balloons, na.rm = T),
+  )
 ```
@@
 
-pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(nd)
+pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% 
+  as_tibble() %>% 
+  bind_cols(nd)
+
+pred <- pred %>% clean_names()
 
@@
 # PLOT
+```{r plot}
+# mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+# cps <- readRDS("../saves/lifespan_ibeast_cps.rds")
 
-```{r plot}
-ggplot() +
+# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
+mdata %>%
+  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
 
-  geom_jitter(
-    data = mdata, 
-    aes(x = age, y = mean_imprecision), 
-    col = "darkgrey", alpha = 0.75
-  ) +
+  ggplot(aes(x = age, y = mean_imprecision)) +
 
-  geom_smooth(
-    data = pred, 
-    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
-    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
-  ) +
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
 
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
-  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
-  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +
+  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
+
+  geom_smooth(data = pred, aes(x = age, y = estimate), stat = "identity", col = "black", size = 0.75) +
+
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
 
@@
 
+  # ## to zoom in
+  # coord_cartesian(xlim = c(3, 10)) +
+  # scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 1)) +
+
   labs(x = "Age in years", y = "Average imprecision in target width")
 
-# ZOOM IN
-ggplot() +
-
-  geom_jitter(
-    data = mdata, 
-    aes(x = age, y = mean_imprecision), 
-    col = "darkgrey", alpha = 0.75
-  ) +
-
-  geom_smooth(
-    data = pred, 
-    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
-    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
-  ) +
-
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
-
-  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) + 
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
-
-  coord_cartesian(xlim = c(3, 10), ) +
-
-  labs(x = "Age in years", y = "Average imprecision in target width")
+# ggsave("../figures/lifespan.png", width = 7, height = 4)
+# ggsave("../figures/lifespan.pdf", width = 7, height = 4)
 ```

### 2023-07-19 stats/lifespan.Rmd
run lifespan analysis on server

@@
 library(Rbeast) # Bayesian change point analysis
+library(janitor) # clean_names
+
 check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
@@
 pp_check(mlinear)
+
+conditional_effects(mlinear, ndraws = 200, spaghetti = TRUE) %>% 
+  plot(points = T, yaxp = c(0,4,1))
 
@@
 # https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
-mdata %>%
+lifespan_plot <- mdata %>%
   add_epred_draws(mgaussianprocess, ndraws = 100) %>%
@@
 
+lifespan_plot
+
+saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
+
 # ggsave("../figures/lifespan.png", width = 7, height = 4)

### 2023-08-02 paper/manuscript.Rmd
edit manuscript figures and corresponding saves

@@
 bibliography      : "../../references.bib"
+bibliography: references.bib
 ---
@@
 library("brms")
+library("janitor")
 
@@
 
-**Acknowledgements:** We thank Jana Jurkat for her help with data collection and participant recruitment.
-We would also like to thank Steven Kalinke for his technical programming support.
+**Acknowledgements:** We thank Jana Jurkat for her help with data collection and participant recruitment. We would also like to thank Steven Kalinke for his technical programming support.
 
 **Funding:** This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship.
 We thank all the children, caregivers, and adults who participated in the study.
@@
 While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
-One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.However, many cognitive abilities develop with age [e.g., working memory, @gathercole2004structure].
+One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
+However, many cognitive abilities develop with age [e.g., working memory, @gathercole2004structure].
 Similarly, visual processing appears to improve with age.
@@
 
-We aimed at assessing the developmental trajectory of gaze understanding across the lifespan.
+We aimed to assess the developmental trajectory of gaze understanding across the lifespan.
 First, we were interested in how this ability changes with age: Is the ability to understand gaze fully developed once emerged in infancy and stays stable across the lifetime?
@@
 lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
-
-lifespan_table <- lifespan_sample %>% 
-  mutate(
-    n = str_glue_data(., "{n_total} ({n_females} female)"), 
-    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
-  ) %>% 
-  rename(
-    `Age group` = age_group,
-    `Age SD` = age_sd, 
-    `Age mean` = age_mean
-  ) %>% 
-  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
-
-apa_table(lifespan_table)
 ```
@@
 
-We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age.
+We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age (see Supplements for further details).
 
@@
 Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
-The target fell behind a hedge, while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
+The target fell behind a hedge while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
 In test trials, the target flight was covered so that participants could not see where the target landed.
-Participant were tasked to locate the target by tracking the agent's gaze.
+Participants were tasked to locate the target by tracking the agent's gaze.
 They could respond by touching on the screen.
@@
 
-The outcome measure was imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
-Target coordinates were randomly generated during runtime.
-Each target bin, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
-
-(ref:figlab1) **Setup of the TANGO and Magnet tasks**.
-(A) TANGO: Gaze understanding task.
-The agent stands in a window with the target in front of them.
-A hedge grows and covers the target.
-The target falls to a random location on the ground.
-The agent's eyes track the movement of the target.
-(B) Magnet task: non-social vector estimation.
-
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/procedure.png")
-```
+The outcome measure was imprecision, defined as the absolute difference between the target (i.e., balloon) center and the x coordinate of the participant's click.
+The full screen width was divided into ten bins.
+Within each bin, exact target coordinates were randomly generated during runtime.
+Each target bin, as well as all agents and target colors, occurred equally often and did not appear in more than two consecutive trials.
 
@@
 Children and teenagers received a personalized link to the study website.
-Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
-Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.
-
+Caregivers were asked to provide technical support whenever needed, while explicitly being reminded not to help their children in responding.
+Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
 Adults completed the online study unsupervised.
@@
 
-To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, cubic.
+To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, or cubic.
 In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
-The models predicted imprecision by age (continuous).
-[^1] Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, aggregated across trials, and modeled by a `lognormal` distribution.
-We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using LOO and WAIC scores and model weights.
+The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights [@vehtari2017practicala].
 
-[^1]: Originally, our models implemented the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
+[^1]: Originally, our models were fitted on a trial-by-trial basis and implemented the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
 However, the Gaussian Process model was computationally heavy.
-    To circumvent issues of convergence and for practicability, we simplified the model structure to include only age as an effect.
+To circumvent issues of convergence and for practicability, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
 In the Supplements, you can find a comparison between the original and the here reported model structures.
@@
 
-To further assess developmental change, we performed a Bayesian change-point analysis, using the package `RBeast` [@zhao2019detecting].
+Confirming that the developmental change was non-linear, we performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
 The function `beast.irreg` handled the irregular nature of our series, which did not have the same number of data points for each year in age.
-We were interested in finding the most prominent, most likely change-points in our data, assuming a constant mean (i.e., a flat line) within each segment.
-Additionally, we wanted to avoid "overreactions" to individual outlying data points.
-Therefore, we restricted our search to a maximum number of five change-points and a minimum length of 9.1245 data points between change-points (corresponding to the product of mean age difference between consecutive points \* mean number of data points within 3 years \* 3).
-We inspected the probability of number of change-points and the locations of these change-points (mean and 95% CrI).
-See Supplements for change-point analyses with differently set parameters.
+We were interested in finding the most prominent, most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
+To avoid "overreactions" to individual outlying data points, we constrained the model to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade).
+We inspected the probability of number of change points and the locations of these change points (mean and 95% CrI).[^2]
+
+[^2]: In a supplementary analysis, we varied the parameters of our changepoint analysis.
+We modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When we allowed more explorative room (i.e., greater nr of change points, smaller minimum nr of data points between change points, higher polynomial order), the models became more sensitive and added more fine-grained change points.
+The exact location of the change points varied slightly.
+However, the overall interpretation stayed the same, fitting our initial visual inspection.
+While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
+There was a minor change in that elderly adults became slightly more imprecise again.
+See Supplements for further detail.
 
@@
 
-(ref:figlab2) **Differentiation in gaze understanding**.
+(ref:figlab1) **Differentiation in gaze understanding**.
+Developmental trajectory in gaze understanding across the lifespan.
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
 The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+Grey dots show the mean performance for each subject averaged across trials.
+Blue lines show 100 draws from the expectation of the posterior predictive distribution (i.e, conditional expectation) of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
+Vertical, black, dashed lines show the location of the most prominent change points.
 
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics(c("../figures/lifespan_plot.png"))
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics(c("../figures/lifespan_all.png"))
 ```
 
-[TODO] report model comparison
+```{r lifespan_results, include=FALSE}
+lifespan_variation <- readRDS("../saves/lifespan_variation_all.rds")
+lifespan_mcomparison <- readRDS("../saves/lifespan_mcomparison.rds") %>% mutate_if(is.numeric, round, 2)
+lifespan_mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+lifespan_beast <- readRDS("../saves/lifespan_ibeast.rds")
+lifespan_cps <- readRDS("../saves/lifespan_ibeast_cps.rds") %>% round(2)
 
-We found a clear non-linear development in gaze understanding across the lifespan.
-Early in childhood, children quickly enhanced their level of proficiency.
-Performance peaked around early adulthood.
-There was a minor decay in elderly adulthood.
-Our Gaussian Process model indicated non-linearity: XXX.
-The Bayesian change-point analysis revealed four major shifts in gaze understanding during the lifespan: We see a very rapid initial improvement in early childhood (3 change-points in rapid succession), followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
+lifespan_gp <- summary(lifespan_mgaussianprocess)$gp %>% 
+  rownames_to_column("param") %>% 
+  clean_names()
+```
+
+High levels of variation pointed to individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
+For example, there were some children that were more accurate than the average adult.
+
+In our model comparison, we found clear evidence for a non-linear development in gaze understanding across the lifespan.
+Compared against a linear, quadratic, and cubic model, the Gaussian Process model showed the best model fit, demonstrated by the greatest model weight and smallest WAIC values.
+For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) and visual inspection indicated nonlinearity (see Figure \@ref(fig:fig2)).
+
+Going one step further, we investigated the most prominent change points in the data.
+The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp %>% round(1)` (with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp %>% round(1) + 1] * 100 %>% round(2)`% probability) major shifts in gaze understanding during the lifespan.
+The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); followed by `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); followed by `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); and finally at `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]).
+In other words: we found a very rapid initial improvement in early childhood (three change points in rapid succession), followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
 
@@
 
-Three-year-olds were surprisingly inaccurate in their responses.
-One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze-following.
-Contrasting our results with previous findings on infant gaze-following, this explanation is unlikely.
-A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
-Another point to keep in mind is that we used subtle eye movements as cues.
-Many existing studies let the agents move eye and head in parallel, therefore establishing a confound with greater (head) movement.
-Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
-The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
+We investigated the shape of change in gaze understanding across the lifespan.
+By applying the exact same task for the entire life span, we could directly compare gaze understanding in all ages.
+Therefore, we circumvented methodological challenges that often arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
 
-Regarding the sample of elderly adults, there is most likely a sampling bias present.
-Elderly which know how to participate in *Prolific* studies certainly might show greater cognitive fitness compared to their offline counterparts.
+We found a non-linear developmental trajectory in gaze understanding: Early in childhood, children quickly enhanced their level of proficiency.
+Performance peaked (i.e., imprecision was lowest) around early adulthood, while there was a minor decay in later adulthood.
+This is consistent with the view that we fine-tune our existing gaze understanding ability after the first emergence in early childhood.
+Furthermore, we observed individual differences in all age groups.
+While variation was highest in the three- and four-year-olds, it remained relatively stable across the lifespan.
 
-Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
-We could circumvent these issues by applying the exact same task for the entire life span.
+Previous studies found that children start to follow gaze in the second half of their first year of life [@moll200412].
+In our sample, three-year-olds were still rather imprecise in their gaze understanding ability.
+How can we explain this divergence?
+First of all, we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel [@behne2005oneyearolds; @povinelli1997exploitation], therefore establishing a confound with greater (head) movement.
+Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation [@carpenter1998social].
+Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and then (3) make use of this cue to guide their own behavior (i.e., touching the screen at the cued location).
+We measured an active location choice instead of an attention orientation.
+It is conceivable that three-year-olds followed the agent's gaze but were still learning to translate this understanding into precise, active behavior.
+
+Regarding the sample of elderly adults, we expect a sampling bias to be present [@bethlehem2010selection; @gosling2004should; @remillard2014systematic].
+First, certainly not all older people have working a high-speed Internet connection or are knowledgeable and trained in its use.
+Second, it takes a certain amount of independence and motivation to participate in *Prolific* studies.
+The elderly who know how to participate in *Prolific* studies certainly might show greater cognitive fitness and flexibility compared to their offline counterparts.
+Therefore, a representative sample might show a greater age decline in gaze understanding compared to our reported sample.
+In addition, it is noteworthy that older people might be more likely to suffer from visual impairments.
+Even though we filtered participants to only include normal- to correct-to-normal vision, we cannot guarantee that our participants showed no symptoms of reduced vision.
 
@@
 Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
-The TANGO has previously been proven reliable for capturing inter-individual differences in gaze understanding [@prein2023tango].
+The TANGO has previously been shown to be reliably capture inter-individual differences in gaze understanding [@prein2023tango].
 The variation between participants is thus likely genuine and not due to random noise.
 Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
-We present a theory of gaze understanding that explains how children use all available information to make inferences about the agent's gaze and its attentional focus, which leads them to correctly identify the target position.
+We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's gaze and its attentional focus, which leads them to identify the target position.
 We formalize this inference process in a computational cognitive model.
@@
 
-We seek to explain how participants solved the TANGO.
-Our gaze model assumes that participants use available gaze information to infer the target location.
-We quantify how well our model explains the gaze understanding process by comparing it to two alternative models that make different assumptions of which information children use and where they consequently click to locate the target.
-Therefore, our modeling framework consists of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
-We gauge which model can best explain our data by conducting a model comparison.
-
-With our modeling framework, we can formalize whether a participant (A) uses the available gaze information at all and (B) how accurately they are in using this gaze information to locate the target.
-Regarding developmental change, we hypothesize that a dual process could explain the development of gaze understanding: The older children are, the more likely they are to use gaze as a cue, and the more precise they become at using it to locate the target.
+We seek to explain how participants solved the TANGO. Our gaze model assumes that participants use available gaze information to infer the target location.
 
@@
 
-## Analysis
+## Computational model
 
-Our goal was to describe the inferential process by which participants locate the target.
-We compared three computational cognitive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
-All cognitive models and model comparisons were implemented in WebPPL [@goodman2014design].
-
-The gaze model assumes participants use the agent's gaze as a cue to locate the target.[^2]
-Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
+The gaze model assumes participants use the agent's gaze as a cue to locate the target.[^3] Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
 Connecting these two point estimates as a line yields a gaze vector: the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-This inferential process involves some uncertainty about the true center of the eyeball.
 Participants are assumed to sample gaze vectors from a Normal distribution centered around the true gaze vector.
 They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
+This inferential process involves some uncertainty about the true gaze vector.
 
-[^2]: This model mirrors the logic of the TANGO programming code.
+[^3]: This model mirrors the logic of the TANGO programming code.
 In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
@@
 When one directs the torchlight straight onto the ground, the light beam is clearly defined and smaller than when one points the torchlight further away from oneself.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.
-If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
 Therefore, our gaze model provides a quantitative theory of gaze understanding, with testable model predictions.
 
+[^4]: In our screen-based study, this effect should decrease again towards the most outward sides.
+Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
+In these cases, the uncertainty about the true gaze vector is - practically - only on the inner side (facing the center) of the screen.
+The natural border of the screen limits where participants can respond.
+In another adult sample with more trials, we could recover this pattern.
+For further elaboration, see Supplements.
+
+## Analysis
+
+Our goal was to describe the inferential process of gaze understanding.
+We quantified how well our model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information children use and where they consequently click to locate the target.
+Our modeling framework consisted of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+We gauged which model can best explain our data by conducting model comparisons.
+All cognitive models and model comparisons were implemented in WebPPL [@goodman2014design].
+
 To gauge the plausibility of our gaze model, we implemented two models that represent alternatives about how participants solve the TANGO.
-Participants who are overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
-The alternative models, therefore, do not assume that participants make use of the gaze cue.
-The first alternative model estimates how likely a participant engages in random guessing.
-This behaves like a coin toss, sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
-The second alternative model estimates how likely a participant shows a center bias: Participants' clicks could be drawn toward the screen center since the agent and the starting point of the balloon are located there.
-This bias is implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
+Participants who were overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
+The alternative models, therefore, do not assume that participants made use of the gaze cue.
+The first alternative model assumed participants were randomly guessing.
+This was implemented as sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
+The second alternative model assumed the participants were biased towards the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
+This bias was implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
 
-Our three proposed models make different predictions about how participants' clicks will be distributed for different target locations.
-We visualize and evaluate these differences using correlations between the model predictions and the data.
+Our three proposed models made different predictions about how participants' clicks would be distributed for different target locations.
+We visualized and evaluated these differences using correlations between the model predictions and the data.
 Furthermore, we evaluated these probabilistic models based on the marginal likelihood of the data under each model.
@@
 
+[TODO: add more infos on priors & parameters]
+
 ## Results
+
+We found clear support for our gaze model, both in children as well as adults.
 
@@
 For the gaze model, we found a high similarity between the model predictions and the observed data across the entire age range.
-The developmental trajectory that we observed in the data closely resembled the predictions of the model.
+The developmental trajectory that we observed in the data closely resembled the predictions of the model: the correlation between the data and the model predictions was XXX [TODO].
 The model explained XXX% [TODO] of the variance in the data.
 
-(ref:figlab3) **Gaze funnel**
+[TODO: report prior]
 
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/gazefunnel_combined.png")
+(ref:figlab2) **Gaze model**
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gazemodel_plot.png")
 ```
@@
 Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
-We assume that children become increasingly sensitive to gaze cues but that the inference process remains the same.
+We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
 By conducting model comparisons, we could rule out that participants' responses can be explained by random guessing or a center bias.
-
-A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
-Our computational model can explain what varies between precise and imprecise individuals.
-There are two sources of errors: (1) do you actually use the eye gaze information?
-and (2) how accurate are you at estimating the focus point when you do pay attention to the agent's eyes?
-This way, we can track developmental changes in gaze understanding in a more fine-tuned way.
 
@@
 A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
-Initially, our proposed gaze model consisted of three components: (1) a perceptual component, whereby the participant produces a noisy observation of the agent's eye angle, (2) an inferential component, whereby the participant estimates the agent's point of attention based on the above perceptual component, and (3) a motor component, whereby the participant samples a click location from a distribution centered around the above estimate of the agent's attentional focus.
-Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components, so we simplified the gaze model to include only the inferential component.
+
+A critical feature of our model is that it assumes gaze understanding to rely on vector estimations.
+In other words, subjects are modeled to calculate gaze vectors based on the location of an agent's pupil.
+This way, they can infer the agent's attentional focus.
+Even though this vector estimation component is a rather physical, geometrical calculation, it still happens in a social context.
+In the first place, one must interpret the agent's eyes as a relevant social stimulus.
+Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
 
@@
 
-Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
-In this study, we sought to experimentally isolate the physical vector estimation component.
-In addition, we inquired whether there are any other cognitive processes outside the vector estimation that constitute gaze understanding.
-We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
+## Perspective-taking:
 
-First, we aimed to isolate the vector estimation component of the gaze understanding task.
-We designed a new non-social vector estimation task that shared all crucial design features of the gaze understanding task.
-Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (@wellman2004scaling) and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
+[@erle2017grounded]
 
-Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
-This way, we can disentangle what components comprise gaze understanding.
+-   differentiation between visuospatial perspective-taking and psychological (i.e., cognitive and affective) perspective-taking
 
-Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.
-The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
-No.
-2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
-Data were collected between February and March 2023.
+-   unclear boundaries between ToM & perspective-taking, many correlational studies, not so many causation "terminological confusion"
+
+-   persepctive-taking: stepping into somebody else's shoes. recognizing the other's thoughts, feelings, mental states (=\> ToM!!)
+
+    -
+
+        1)  attesting mental states to another social agent
+
+    -
+
+        2)  other's states can be ≠ to own
+
+    -
+
+        3)  put aside egocentric bias
+
+-   little is known about underlying psychological mechanisms of perspective-taking
+
+-   visuospatial perspective taking: mentally transforming yourself and your body into the physical location of another agent.
+judging differences between one's own egocentric point of view an that of another person
+
+    -   level 1: visibility of objects from certain view point. can operate independently from another's frame of reference
+
+    -   level 2: imagine how world looks like for another person "climbing into the skin of another person".
+literally rotating body schema (embodied) "transposing body schema into the target's position"
+
+-   clinical populations show deficit in empathy & visuospatial perspective-taking
+
+-   idea that psychological & visuospatial perspective-taking share common simulation-based mechanism
+
+-   studies show that: "Taking another's perspective led participants to adopt the thoughts of the target person more strongly (Experiments 1--3) and increased the perceived similarity of that person to the self (Experiment 4) and participants' liking of that person (Experiment 5).
+These effects were independent of task difficulty (Experiment 2), and only present during trials where an embodied transformation happened (i.e., at high angular disparities; Experiment 3)." "not only affects social-cognitive outcomes, but also empathic perspective-taking" =\> "shared mechanism of all kinds of perspective-taking"
+
+-   non-social perspective-taking task: display empty chair. spatial perspective-taking. lead to "diametrically different results"
+
+[@birch2017perspectives]
+
+-   "Specifically, we contend that these processes (a) are partially innate, (b) develop over time and can be honed through experience, and (c) lie on a continuum with some individuals being better than others."
+
+-   Apperly & Buuterfill 2009: System 1 process social information relatively quickly & effortlessly, clear limitations, inflexible.
+System 2 explicit reasoning, involves language, inhibitory control, working memory, cognitive flexibility, reasoning, planning etc.
+
+-   chapter assumes partial innateness, develop over time, can be honed through experience, lie on a continuum with some individuals being "Better" than others
+
+-   children use gaze as indicators of others' mental states from an early age
+
+-   individual differences:
+
+    -   children differ in onset of milestones, degree to which they can and do use ToM in daily life. vary in frequency / propensity (connected to motivation?) and accuracy
+
+    -   ind diff to "illustrate important function ToM serves in navigating the social world". for which processes involved, contribution of other skills & environmental scaffolding
+
+-   curse of knowledge: U shaped curve. hindsight bias & tom correlated, but not inhibitory control as mediator
+
+We previously presented a computational cognitive model of gaze understanding.
+Our model relies on the perhaps unexpected assumption that vector estimation is a crucial component of gaze understanding.
+In model comparisons, we found overwhelming support for this model in children and adults.
+Now, we wanted to test this assumption experimentally.
+We were interested in the degree to which vector estimation is a part of gaze understanding.
+Additionally, we investigated whether there is more to gaze understanding than the physical vector estimation component.
+To answer this question, we assessed the relationship between gaze understanding and other social-cognitive abilities.
+
+First, we aimed to experimentally isolate the vector estimation component of the TANGO.
+We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
+Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (\@wellman2004scaling) and two additional perspective-taking tasks [\@flavell1981development; \@flavell1981younga].
+
+We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+This way, we aimed to disentangle what components comprise gaze understanding.
+
+[TODO: welche sozialen prozesse überlappen hier. das hilft dann auch dabei zu sagen warum wir nicht unbedingt erwarten, dass alle ToM komponenten einen einfluss haben.]
+
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>. Data were collected between February and March 2023.
 
@@
 Information on individual socio-economic status was not formally recorded.
-Children in our sample live in an industrialized, urban Central-European city with approximately 600,000 inhabitants.
-Households often consist of nuclear families with few household members.
-The majority of families in our data base come from mainly mid to high socio-economic backgrounds with high levels of parental education.
 
@@
 Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects study design.
-All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) gaze understanding task.
+All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) TANGO.
 Several reasons motivated this decision.
@@
 Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
-Third, we showed the non-social vector estimation task before the gaze understanding task so that participants would not be biased to interpret the presented stimuli as "eye- /"agent-like".
+Third, we showed the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the presented stimuli as "eye- /"agent-like".
 
@@
 
-Modeling the setup and structure of the previously applied gaze understanding task, we designed a non-social vector estimation task.
-This task was also presented as a webapp on a tablet and made use of the concept of magnetism.
+Modeling the setup and structure of the previously applied TANGO, we designed a non-social vector estimation task.
+This task was also presented as a web application on a tablet and made use of the concept of magnetism.
 The setup looked as follows.
 On the upper part of the screen, there was a tube with a gearwheel located in a circular window.
-On the floor, there lay a magnet.
+On the floor, there was a magnet.
 The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
@@
 Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga].
-We added the perspective-taking tasks (1) with the aim of increasing the task battery's difficulty, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
+We added the perspective-taking tasks (1) with the aim of increasing the variablility we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
 The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
-In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
+Additionally, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
 
@@
 As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2023tango].
-To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^3]
+To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
+This further highlighted the contrast (i.e., social vs.
+non-social context) to the non-social vector estimation task.[^5]
 
-[^3]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
-    Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal).
+[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
+human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
+animal).
 See Supplements for further detail.
@@
 
-By design, both the gaze understanding task as well as the non-social vector estimation task involve vector estimation.
+By design, both the TANGO as well as the non-social vector estimation task involve vector estimation.
 On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate with each other.
@@
 
-Taken together, this shows that the gaze understanding task recruited social-cognitive abilities beyond vector estimation.
+Taken together, this shows that the TANGO recruited social-cognitive abilities beyond vector estimation.
 Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
 
-(ref:figlab4) **Components of gaze understanding.** (A) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+(ref:figlab3) **Components of gaze understanding.** (A) Study procedures.
+Top: TANGO (i.e., social vector estimation; gaze understanding).
+Bottom: Magnet (i.e., non-social vector estimation).
+Left: Screenshots of familiarization phase.
+Right: Screenshots of test phase.
+(B) Magnet task: non-social vector estimation.(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
 Dots show the correlation coefficients, while error bars represent 95% CIs.
-(B) Influence of perspective-taking and physical vector estimation on gaze understanding.
+(C) Influence of perspective-taking and physical vector estimation on gaze understanding.
 The graph show the posterior distributions for the respective predictor.
@@
 
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/magnet_arrangedplot.png")
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/magnet_plot.png")
 ```
@@
 
+[TODO: das klingt als ob perspective taking ein prozess wäre, ist es aber nicht - versuch mal zu überlegen was hier die gemeinsamkeiten sein könnten und das zu beschreiben.]
+
 In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2023tango].
@@
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
+
+[TODO: die "wahren" Korrealtionen (die zwischen den latenten konstrukten) eigentloch stärker sind weil hier ja auch measurement error drin steckt.
+das kann man berechnen wenn man die reliabilität jeweils kennt.
+Die haben wir hier halt nciht für tango (außer vll split half??)]
 

### 2023-08-02 stats/gazemodel.Rmd
edit manuscript figures and corresponding saves

@@
 library(tidyboot) # for bootstrap CIs
+library(coda) # HPDinterval
+library(ggpubr) # stat_cor
+library(ggdist) # stat_pointinterval
+library(matrixStats) # logSumExp
+library(ggridges) # for geom_density_ridges
+library(ggthemes) # themes for plotting
+library(cowplot) # ggdraw, draw_image, plot_grid
 
@@
 
+```{r functions}
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+```
+
 ```{r load_data}
-gaze_data_kids <- readRDS("../data/tango-model-kids.rds")
-gaze_data_adults <- readRDS("../data/tango-model-adults.rds") %>% mutate(age_group = 18)
-gaze_data <- full_join(gaze_data_kids, gaze_data_adults)
+tango_kids <- readRDS("../data/tango-model-kids.rds")
+tango_adults <- readRDS("../data/tango-model-adults.rds") %>% mutate(age_group = 18)
+tango <- full_join(tango_kids, tango_adults)
+
+# careful, this takes a while... 
+model_kids <- readRDS("../data/gazemodel_kids.rds")
+model_kids_dev_prior <- readRDS("../data/gazemodel_kids_dev_prior.rds")
 ```
@@
 ```{r sample}
-gazemodel_sample_kids <- gaze_data_kids %>% 
+gazemodel_sample_kids <- tango_kids %>% 
   group_by(age_group) %>%
@@
 
-gazemodel_sample_adults <- gaze_data_adults %>% 
+gazemodel_sample_adults <- tango_adults %>% 
   mutate(female = ifelse(gender == "f", 1, 0)) %>% 
@@
 
-```{r plot}
-dev_plot <- gaze_data_kids %>% 
-  group_by(subj_id, age, age_group) %>%
-  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
-  ggplot(., aes(x = age, y = mean)) +
-  geom_point(color = "darkgrey", alpha = 0.5) +
-  geom_smooth(method = "lm", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
-  scale_x_continuous(limits = c(3, 5), breaks = seq(3, 5, 0.5)) +
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
-  labs(x = "Age in years", y = "Average imprecision in target widths")
-
-dev_plot
-
-# ggsave("../figures/dev_plot.png", width = 8, height = 4, scale = 1.2)
-```
-
-```{r gazefunnel}
-target_position_imprecision <- gaze_data %>%
+```{r data_gazefunnel}
+target_position_imprecision <- tango %>%
   group_by(age_group, target_position) %>%
@@
 
-target_position_imprecision_ind <- gaze_data %>%
+target_position_imprecision_ind <- tango %>%
   group_by(subj_id, age_group, target_position) %>%
@@
 
-ggsave("../figures/gazefunnel.png", width = 6, height = 4, scale = 1.2)
-saveRDS(gazefunnel, "../saves/gazefunnel.rds")
+# saveRDS(gazefunnel, "../saves/gazemodel_funnel.rds")
+# ggsave("../figures/gazemodel_funnel.png", width = 6, height = 4, scale = 1.2)
 ```
+
+# CHILDREN
+
+## Inference
+
+```{r dev_traj_inf}
+inf_map_devp <- model_kids_dev_prior %>%
+  filter(scope == "global", 
+         parameter == "inference", 
+         type != "sigma") %>%
+  group_by(type) %>%
+  summarise(mode = estimate_mode(value)) %>%
+  pivot_wider(names_from = "type", values_from = "mode") %>%
+  expand_grid(age = seq(0, 3, 0.1)) %>%
+  mutate(sd = exp(intercept + slope * age))
+
+inf_samp_devp <- model_kids_dev_prior%>%
+  filter(scope == "global", 
+         parameter == "inference", 
+         type != "sigma") %>%
+  pivot_wider(names_from = "type", values_from = "value") %>%
+  sample_n(1000) %>%
+  expand_grid(age = seq(0, 3, 0.1)) %>%
+  mutate(sd = exp(intercept + slope * age))
+
+id_devp <- model_kids_dev_prior%>%
+  filter(scope == "id", 
+         type == "sd") %>%
+  group_by(id) %>%
+  summarise(mode = estimate_mode(value),
+            lci = hdi_lower(value), 
+            uci = hdi_upper(value)) %>%
+  left_join(tango_kids %>% 
+              select(subj_id, age, age_group) %>% 
+              rename(id = subj_id) %>% 
+              distinct(id, .keep_all = T)) %>%
+  ungroup()
+
+dev_plot <- ggplot() +
+  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
+  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
+  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
+  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
+  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
+  coord_cartesian(ylim = c(0, 3)) +
+  labs(x = "Age", y = "Inference parameter")
+
+dev_plot
+saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")
+
+# ggsave("../figures/gazemodel_dev.png", width = 8, height = 5, scale = 1, bg = "white")
+# ggsave("../figures/gazemodel_dev.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+## Inference parameters individuals
+
+```{r id_inf}
+# prepare data
+id_inf <- model_kids_dev_prior %>%
+  filter(scope == "id", parameter == "inference") %>% 
+  group_by(id) %>% 
+  mutate(mean = mean(value, na.rm = T))
+
+idinf_plot <- id_inf %>% 
+  slice_sample(n = 2000) %>% # for faster debugging
+  full_join((tango_kids %>% select(subj_id, age, age_group)), by = join_by(id == subj_id)) %>% 
+  ggplot(aes(x = value, y = reorder(id, mean), fill = age)) +
+  geom_density_ridges(bandwidth = .05, rel_min_height = .01, size = .25, scale = 3, alpha = .5) + 
+  scale_fill_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
+  scale_x_continuous(breaks = seq(0, 7, 0.5)) +
+  coord_cartesian(xlim = c(0, 7)) +
+  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) + 
+  labs(x = "Inference parameter", y = "Participants (ordered by mean)", fill = "Age")
+
+idinf_plot
+saveRDS(idinf_plot, "../saves/supplements_gazemodel_idinf_plot.rds")
+
+ggsave("../figures/supplements_gazemodel_indinference.png", width = 5, height = 5)
+ggsave("../figures/supplements_gazemodel_indinference.pdf", width = 5, height = 5)
+```
+
+```{r faceted_inf, message=FALSE, warning=FALSE}
+faceted_inf <- model_kids_dev_prior %>%
+  filter(scope == "id", parameter == "inference") %>%
+  mutate(id = vctrs::vec_group_id(id)) %>% 
+  ggplot() + 
+  geom_density(aes(x = value, fill = factor(chain)), alpha = .5) +
+  stat_pointinterval(aes(x = value)) +
+  facet_wrap(~ id, nrow = 6, scales = "free") +
+  scale_fill_viridis_d() +
+  scale_x_continuous(limits = c(0, 3)) + 
+  scale_y_continuous(limits = function(x){c(0, max(0.1, x))}) +
+  labs(x = "Inference parameter value", y = "", fill = "Model chains") +
+  theme_minimal()
+
+faceted_inf
+saveRDS(faceted_inf, "../saves/supplements_gazemodel_facetedinference.rds")
+
+ggsave("../figures/supplements_gazemodel_facetedinference.png", width = 10, height = 6, scale = 1.4, bg = "white")
+ggsave("../figures/supplements_gazemodel_facetedinference.pdf", width = 10, height = 6, scale = 1.4, bg = "white")
+```
+
+## Recover U pattern
+
+```{r get_click_prior}
+get_click_prior <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX, priorInt, priorSlope, age){
+
+  if(eyeCenterLX > pupilLX) {
+    tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+  } else {
+    tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+  }
+
+  #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
+
+  if(eyeCenterRX > pupilRX) {
+    tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+  } else {
+    tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+  }
+
+  #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
+
+  bRDist = c()
+
+  bLDist = c()
+
+  for (x in 1:1920){
+
+  if(eyeCenterLX > x) {
+    betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+  } else {
+    betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+  }
+    betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
+
+  if(eyeCenterRX > x) {
+    betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+  } else {
+    betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+  }
+    betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
+
+    #betaDist = betaLDist + betaRDist
+
+    #bDist[x] <- exp(betaDist)
+    bRDist[x] <- betaRDist
+
+    bLDist[x] <- betaLDist
+
+  }
+
+  xRDist = exp(bRDist-logSumExp(bRDist))
+
+  xLDist = exp(bLDist-logSumExp(bLDist))
+
+  priorSD = priorInt + priorSlope * age
+
+  xDist = (xRDist * xLDist) * dnorm(seq(1:1920), mean = 960, sd = priorSD)
+
+  dist = xDist / sum(xDist)
+
+  click = sample(1:1920, prob = xDist, size = 1)-1
+
+  return(click)
+}
+```
+
+```{r u_pattern}
+ind_sd <- model_kids_dev_prior %>%
+  filter(scope == "id", type == "sd") %>%
+  group_by(id) %>%
+  summarise(sdTol = estimate_mode(value)) %>%
+  left_join(tango_kids %>% rename(id = subj_id,
+                          eyeCenterLY = eye_center_left_y,
+                          eyeCenterLX = eye_center_left_x, 
+                          eyeCenterRY = eye_center_right_y,
+                          eyeCenterRX = eye_center_right_x,
+                          pupilLX = pupil_final_left_x,
+                          pupilRX = pupil_final_right_x,
+                          targetCenterX = target_center_x,
+                          targetCenterY = target_center_y) %>%
+              mutate(clickDist = abs(click_dist_from_target_center_x)) %>%
+              select(id, age, age_group, trial_nr, eyeCenterLX, eyeCenterLY, eyeCenterRX, eyeCenterRY, pupilLX, pupilRX, targetCenterY, targetCenterX, clickDist))
+
+ind_sd_long <- ind_sd %>% slice(rep(1:n(), each = 100))
+
+priorMode <- model_kids_dev_prior %>%
+  filter(scope == "global", 
+         parameter == "priorSd", 
+         type != "sigma") %>%
+  group_by(type) %>%
+  summarise(mode = estimate_mode(value))
+
+# careful, this runs a while...
+gen_model_clicks <- ind_sd_long %>%
+  rowwise() %>%
+  mutate(modelClick = get_click_prior(
+          sdTol = sdTol,
+          eyeCenterLY = eyeCenterLY,
+          eyeCenterLX = eyeCenterLX, 
+          eyeCenterRY = eyeCenterRY,
+          eyeCenterRX = eyeCenterRX,
+          targetCenterX = targetCenterX,
+          pupilLX = pupilLX,
+          pupilRX = pupilRX,
+          targetCenterY = targetCenterY,
+          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
+          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
+          age = age
+          ))
+
+recover_plotdata <- gen_model_clicks %>%
+  mutate(
+    modelClickDist = abs(modelClick - targetCenterX),
+    targetBin = cut(targetCenterX, 
+                    breaks=seq(from = 0, to = 1920, by =192),
+                    labels=as.character(1:10))
+  ) %>%
+  group_by(age_group, targetBin) %>%
+  summarise(
+    data_mean = mean(clickDist), 
+    model_mean = mean(modelClickDist)
+  )
+
+saveRDS(recover_plotdata, "../saves/gazemodel_recoverU_plotdata.rds")
+# recover_plotdata <- readRDS("../saves/gazemodel_recoverU_plotdata.rds")
+
+u_plot <- recover_plotdata %>%
+  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
+  mutate(
+    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
+    imprecision = imprecision / 160,
+  ) %>% 
+  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
+  geom_point(alpha = 0.8) +
+  facet_grid(~ age_group) +
+  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 0.5)) +
+  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model estimate")) +
+  labs(x = "Target position", y = "Imprecision in target width", color = "Source") + 
+  theme_few() +
+  theme(
+    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
+    legend.background = element_rect(color = "darkgrey", size = 0.1), 
+    legend.text = element_text(size = 8),
+    strip.text = element_text(face = "bold", size = 12)
+  )
+
+u_plot
+saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
+ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
+ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+```{r imprecision_bin_plot}
+imprecision_bin_plot <- recover_plotdata %>% 
+  mutate(
+    model_mean = model_mean / 160, 
+    data_mean = data_mean / 160,
+  ) %>% 
+  ggplot(., aes(x = model_mean, y = data_mean)) +
+  geom_point(aes(col = targetBin)) +
+  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_abline(intercept = 0, slope = 1, linetype = 3) +
+  scale_color_brewer(palette="BrBG") +
+  labs(x = "Model estimated imprecision", y = "Data mean imprecision", color = "Target bin") + 
+  scale_x_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1)) + 
+  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1))
+
+saveRDS(imprecision_bin_plot, "../saves/gazemodel_imprecision_bin_plot.rds")
+ggsave("../figures/gazemodel_imprecision_bin_plot.png", width = 8, height = 5, scale = 1, bg = "white")
+ggsave("../figures/gazemodel_imprecision_bin_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+## Data recovery
+
+```{r model_vs_data}
+comparison_model_data_devp <- model_kids_dev_prior %>%
+  filter(scope == "id", type == "sd") %>%
+  group_by(id) %>%
+  summarise(model_mode = estimate_mode(value)) %>%
+  left_join(
+    tango_kids %>% 
+      group_by(subj_id, age, age_group) %>%
+      summarise(data_mean = mean(click_dist_balloons)) %>%
+      rename(id = subj_id)
+  )
+
+model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
+  geom_point(aes(col = age)) +
+  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
+  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
+  labs(x = "Model estimated mode", y = "Data imprecision mean", color = "Age") + 
+  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))
+
+model_vs_data_plot
+saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
+ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
+ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+# Plot
+
+```{r arrange_plot}
+setup_png <- ggdraw() + draw_image("../figures/gazemodel_setup.png")
+ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_Ulogic.png")
+
+gazemodel_plot <- ggarrange(
+  setup_png,
+  dev_plot, 
+  NULL, 
+  model_vs_data_plot,
+
+  ulogic_png, 
+  u_plot, 
+  NULL, 
+  imprecision_bin_plot,
+
+  ncol = 4, 
+  nrow = 2, 
+  widths = c(9, 12, 1, 11), 
+  labels = c("A", "B", "", "C", "D", "E", "", "F")
+)
+
+gazemodel_plot
+saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
+ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
+ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
+```

### 2023-08-02 stats/lifespan.Rmd
edit manuscript figures and corresponding saves

--- 2023-07-12 stats/lifespan.Rmd
@@
 library(Rbeast) # Bayesian change point analysis
+library(janitor) # clean_names
+library(ggpubr) # ggarrange
+
 check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)
@@
 
+```{r variation}
+lifespan_variation_all <- lifespan_data %>% 
+  summarise(
+    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_min = min(click_dist_balloons, na.rm = T),
+    imprecision_max = max(click_dist_balloons, na.rm = T),
+  )
+
+lifespan_variation_agegroups <- lifespan_data %>% 
+  group_by(age_group) %>%
+  summarise(
+    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
+    imprecision_min = min(click_dist_balloons, na.rm = T),
+    imprecision_max = max(click_dist_balloons, na.rm = T),
+  )
+
+lifespan_variation_all
+write.csv(lifespan_variation_all, "../saves/lifespan_variation_all.csv", quote = F, row.names = F)
+saveRDS(lifespan_variation_all, "../saves/lifespan_variation_all.rds")
+
+lifespan_variation_agegroups
+write.csv(lifespan_variation_agegroups, "../saves/lifespan_variation_agegroups.csv", quote = F, row.names = F)
+saveRDS(lifespan_variation_agegroups, "../saves/lifespan_variation_agegroups.rds")
+```
+
 # MODEL COMPARISON FOR DEVELOPMENTAL TRAJECTORY
@@
             torder.minmax = c(0, 0), # for constant
-            tcp.minmax = c(0, 5), # we assume 3, allow some room for exploration
-            tseg.min = 10, 
+            # tcp.minmax = c(0, 5), # let the beast decide on its own how many changepoints
+            tseg.min = 10, # half of nr data points for decade in adult sample
             mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
@@
 ```{r plot}
-ggplot() +
+mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
+cps <- readRDS("../saves/lifespan_ibeast_cps.rds")
 
-  geom_jitter(
-    data = mdata, 
-    aes(x = age, y = mean_imprecision), 
-    col = "darkgrey", alpha = 0.75
-  ) +
+# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
+lifespan_plot <- mdata %>%
+  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
+  ggplot(aes(x = age, y = mean_imprecision)) +
 
-  geom_smooth(
-    data = pred, 
-    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
-    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
-  ) +
+  # raw data points
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
 
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
-  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
-  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +
+  # model predictions spaghetti lines
+  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
+  # mean model prediction
+  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", fill = "black") +
+
+  # change points from beast
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
 
@@
   scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
-
   labs(x = "Age in years", y = "Average imprecision in target width")
 
-# ZOOM IN
-ggplot() +
+lifespan_plot
 
-  geom_jitter(
-    data = mdata, 
-    aes(x = age, y = mean_imprecision), 
-    col = "darkgrey", alpha = 0.75
-  ) +
+saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
 
-  geom_smooth(
-    data = pred, 
-    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
-    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
-  ) +
+ggsave("../figures/lifespan_all.png", width = 7, height = 4)
+ggsave("../figures/lifespan_all.pdf", width = 7, height = 4)
+```
 
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
+```{r zoomed_plot}
+# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
+lifespan_plot_zoom <- mdata %>%
+  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
+  ggplot(aes(x = age, y = mean_imprecision)) +
 
+  # raw data points
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
+
+  # model predictions spaghetti lines
+  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
+  # mean model prediction
+  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", fill = "black") +
+
+  # change points from beast
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
+
+  coord_cartesian(xlim = c(3, 10)) +
   scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) +
+
+  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
+  labs(x = "Age in years", y = "Average imprecision in target width")
+
+lifespan_plot_zoom
+
+saveRDS(lifespan_plot_zoom, "../saves/lifespan_plot_zoom.rds")
+
+# ggsave("../figures/lifespan_zoom.png", width = 7, height = 4)
+# ggsave("../figures/lifespan_zoom.pdf", width = 7, height = 4)
+```
+
+```{r arrange_plot}
+arranged <- ggarrange(
+  lifespan_plot, 
+  lifespan_plot_zoom, 
+  widths = c(2, 1.5), 
+  labels = c("A", "B")
+)
+
+arranged
+
+ggsave("../figures/lifespan_plot.png", width = 10, height = 3, scale = 1.2)
+ggsave("../figures/lifespan_plot.pdf", width = 10, height = 3, scale = 1.2)
+```
+
+```{r try_ggbreak}
+library(ggbreak)
+
+lifespan_cut <- mdata %>%
+  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
+  ggplot(aes(x = age, y = mean_imprecision)) +
+
+  # raw data points
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
+
+  scale_x_cut(breaks = c(18), scales = "free", space = 0.001) +
+
+  # model predictions spaghetti lines
+  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
+  # mean model prediction
+  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +
+
+  # change points from beast
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
+
+  scale_x_continuous(limits = c(3, 80), breaks = c(3:17, 20, 30, 40, 50, 60, 70, 80)) +
   scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
 
-  coord_cartesian(xlim = c(3, 10), ) +
+  labs(x = "Age", y = "Mean imprecision", xdist = "", ydist = "")
 
-  labs(x = "Age in years", y = "Average imprecision in target width")
+lifespan_cut
 ```
+
+```{r try_ggh4x}
+library(ggh4x)
+
+mdata %>%
+  mutate(my_facet = age > 20.00) %>% 
+  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
+
+  ggplot(aes(x = age, y = mean_imprecision)) +
+
+    # raw data points
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
+
+    # model predictions spaghetti lines
+  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
+  # mean model prediction
+  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +
+
+  # for gap in x axis
+  facet_grid(~ my_facet, scales = "free_x") +
+  theme(strip.text.x = element_blank()) +
+
+  ggh4x::facetted_pos_scales(x = list(
+    my_facet == FALSE ~ scale_x_continuous(limits = c(3, 20), breaks = seq(3, 19, 1)),
+    my_facet == TRUE ~ scale_x_continuous(limits = c(20, 80), breaks = seq(20, 80, 10))
+)) +
+
+  geom_vline(data = data.frame(xint=cps$cp[1:4], my_facet = FALSE), aes(xintercept = xint), linetype = "dotted") +
+  geom_vline(data = data.frame(xint=cps$cp[5:6], my_facet = TRUE), aes(xintercept = xint), linetype = "dotted") +
+
+  labs(x = "Age in years", y = "Average imprecision in target width") +
+
+  # get rid of space between facets
+  theme(panel.spacing = unit(0.1, "lines"))
+```

### 2023-08-02 stats/magnet.Rmd
edit manuscript figures and corresponding saves

@@
 library(magrittr) # extract list elements
+library(cowplot) # ggdraw, draw_image, plot_grid
 
@@
   ggplot(., aes(x=Correlation, y=r, ymin=lower, ymax=upper)) +
-  geom_pointrange(color = "#005555", size = 0.8, linewidth = 1) +
+  geom_pointrange(color = "black", size = 0.8, linewidth = 1) +
   scale_y_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25)) +
@@
 ```{r modelplot}
+magnet_draws <- readRDS("../saves/magnet_draws.rds")
+
 modelplot <- magnet_draws %>% 
@@
   ggplot(., aes(x = estimate, y = predictor, fill = includes_zero)) +
- tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "#006c66", slab_alpha = 0.5) +
-    labs(x = "Posterior estimate when predicting TANGO mean", y = "") +
+ tidybayes::stat_halfeye(.width = c(.95, .8), scale = 1, slab_color = "darkgrey", slab_alpha = 0.9) +
+    labs(x = "Posterior estimate TANGO mean", y = "") +
   guides(fill = "none")+
   geom_vline(xintercept = 0, linetype = "dashed") +
-  scale_fill_manual(values = c("#006c66", "#EBECEC")) +
+  scale_fill_manual(values = c("darkgrey", "#EBECEC")) +
   coord_cartesian(expand = TRUE, xlim = c(-0.6, 0.4), ylim = c(1.5, 3.5)) +
@@
 # ggsave("../figures/modelplot.png", width = 10, height = 6, scale = 0.7, bg = "white")
-```
-
-```{r arrange_plot}
-arrangedplot <- ggarrange(
-  cor_ci, 
-  modelplot, 
-  ncol = 2, 
-  labels = c("A", "B")
-)
-
-saveRDS(arrangedplot, file = "../saves/magnet_arrangedplot.rds")
-ggsave("../figures/magnet_arrangedplot.png", width = 6, height = 2, scale = 1.75, bg = "white")
 ```
@@
 
-saveRDS(williams_tom, "../saves/williams_tom.rds")
+saveRDS(williams_tom, "../saves/magnet_williams_tom.rds")
 
@@
 
-saveRDS(williams_perspective, "../saves/williams_perspective.rds")
+saveRDS(williams_perspective, "../saves/magnet_williams_perspective.rds")
 ```
+
+```{r arrange_plot}
+procedure_png <- ggdraw() + draw_image("../figures/procedure.png")
+cor_ci <- readRDS(file = "../saves/magnet_cor_ci.rds")
+modelplot <- readRDS(file = "../saves/magnet_modelplot.rds")
+
+magnet_plot <- ggarrange(NULL, 
+          procedure_png, 
+          cor_ci, 
+          modelplot, 
+          NULL, 
+          ncol = 5, 
+          labels = c("A", "", "B", "C", ""),
+          widths = c(1, 16, 18, 13, 1.5)
+          )
+
+saveRDS(magnet_plot, file = "../saves/magnet_plot.rds")
+ggsave("../figures/magnet_plot.png", width = 10, height = 2, scale = 1.4, bg = "white")
+ggsave("../figures/magnet_plot.pdf", width = 10, height = 2, scale = 1.4, bg = "white")
+
+# alternative positioning: procedure on top, cor left below, model right below
+# ggarrange(procedure_png, 
+#           NULL, 
+#           
+#           ggarrange(
+#             cor_ci, 
+#             modelplot, 
+#             NULL, 
+#             ncol = 3, 
+#             labels = c("B", "C", ""), 
+#             widths = c(12, 10, 2)
+#           ), 
+#           
+#           nrow = 3,
+#           heights = c(11, 1, 9), 
+#           labels = c("A", ""), 
+#           align = "h"
+#           )
+# 
+# # saveRDS(magnet_plot, file = "../saves/magnet_plot.rds")
+# ggsave("../figures/magnet_plot2.png", width = 8, height = 5, scale = 1.2, bg = "white")
+```

### 2023-08-02 stats/supplements_gaussianprocess.Rmd
edit manuscript figures and corresponding saves

--- 2023-07-10 stats/gaussianprocess.Rmd
@@
 
-write.csv(mgp_triallevel, "../saves/mgp_triallevel.csv", quote = F, row.names = F)
-saveRDS(mgp_triallevel, "../saves/mgp_triallevel.rds")
+write.csv(mgp_triallevel, "../saves/lifespan_mgp_triallevel.csv", quote = F, row.names = F)
+saveRDS(mgp_triallevel, "../saves/lifespan_mgp_triallevel.rds")
 ```
@@
 
-write.csv(mgp_aggregated, "../saves/mgp_aggregated.csv", quote = F, row.names = F)
-saveRDS(mgp_aggregated, "../saves/mgp_aggregated.rds")
+write.csv(mgp_aggregated, "../saves/lifespan_mgp_aggregated.csv", quote = F, row.names = F)
+saveRDS(mgp_aggregated, "../saves/lifespan_mgp_aggregated.rds")
 ```

### 2023-08-02 supplements/supplements.Rmd
edit manuscript figures and corresponding saves

@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Lifespan
+## Participants
+```{r lifespan_sample, include = T, out.width = "100%"}
+lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
+
+lifespan_table <- lifespan_sample %>% 
+  mutate(
+    n = str_glue_data(., "{n_total} ({n_females} female)"), 
+    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
+  ) %>% 
+  rename(
+    `Age group` = age_group,
+    `Age SD` = age_sd, 
+    `Age mean` = age_mean
+  ) %>% 
+  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
+
+apa_table(lifespan_table)
+```
+
+# Computational cognitive model 
+## Imprecision by target position
+
+(ref:figlab1) **Gaze funnel for adult sample with higher trial number**.
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/gazefunnel_adults.pdf")
 ```

### 2023-08-10 paper/manuscript.Rmd
adjust gaze model parts

@@
 bibliography      : "../../references.bib"
-bibliography: references.bib
 ---
@@
 
-**Acknowledgements:** We thank Jana Jurkat for her help with data collection and participant recruitment. We would also like to thank Steven Kalinke for his technical programming support.
+**Acknowledgements:** We thank Jana Jurkat for her help with data collection and participant recruitment.
+We would also like to thank Steven Kalinke for his technical programming support.
 
@@
 In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
-The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1]
+The unit of imprecision was counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
 We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights [@vehtari2017practicala].
@@
 
-(ref:figlab1) **Differentiation in gaze understanding**.
-Developmental trajectory in gaze understanding across the lifespan.
+(ref:figlab1) **Developmental trajectory of gaze understanding across the lifespan**.
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
@@
 
-We seek to explain how participants solved the TANGO. Our gaze model assumes that participants use available gaze information to infer the target location.
+We seek to explain how participants solved the TANGO.
+Our gaze model assumes that participants use available gaze information to infer the target location.
 
@@
 
-The gaze model assumes participants use the agent's gaze as a cue to locate the target.[^3] Participants are assumed to observe the current location of the pupil and estimate the center of the agent's eyeball.
-Connecting these two point estimates as a line yields a gaze vector: the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-Participants are assumed to sample gaze vectors from a Normal distribution centered around the true gaze vector.
-They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
-This inferential process involves some uncertainty about the true gaze vector.
+Our model quantifies a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+It is formally defined as:
+
+\begin{equation}
+    P(\mathbf{\theta} | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \mathbf{\theta})P(\mathbf{\theta})
+\end{equation}
+
+where $\mathbf{\theta}$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
+The pupil angle is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the pupil.[^3]
 
@@
 
-Now, individuals can differ in how wide their distribution around the true gaze vector is.
-The model's inferential component, α, estimates the standard deviation of the distribution for each individual participant.
-With higher standard deviations (i.e., increased α), participants are expected to show decreasing precision in estimating the target location.
-The model assumes that the sensitivity to the available gaze information changes with age.
+Based on our verbal task instructions, we assume that participants (1) expect the agent's looks to be directed at the target, and (2) to click on the coordinate they estimate the agent to look at. 
+Consequently, we do not assume that participant's clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at). 
+However, the true eye angles ($\alpha_l$ and $\alpha_r$) cannot be directly observed.
+These have to be estimated based on the position of the pupils within the eyes, resulting in approximate values ($\hat{\alpha_l}$ and $\hat{\alpha_r}$).
+We presume this estimation to be a noisy process.
+Thus, the development of the cognitive ability to follow gaze corresponds to a reduction in the magnitude of the noise in the estimates (i.e., an increased certainty about the eye angles).
 
-The geometry of sampling from a distribution around the gaze vector leads to an interesting, testable group-level prediction.
-As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
-When the agent directs their gaze toward the very left or right side, the distribution around the gaze vector from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
-For illustrative purposes, imagine a similar phenomenon: pointing a torch light to the ground.
-When one directs the torchlight straight onto the ground, the light beam is clearly defined and smaller than when one points the torchlight further away from oneself.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Any clicked value of $x_c$ implies a "matched pair" of the estimated pupil angles $\hat{\alpha_l}$ and $\hat{\alpha_r}$, with the property that lines extended along those two angles meet at the precise location of the target.
+As a consequence, we can rewrite the likelihood function of the model above:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assume to be skewed towards the screen center: 
+We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
+We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data.
+
+The main inferential task for the participant lies in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
+For this, we assume that the pair of estimated angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance $\sigma_v$ centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+Broadly summarizing: Participants are assumed to observe the pupil locations and estimate the center of the agent's eyes.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point. 
+Taking the angle between this vector and a line pointing vertically to the ground yields the pupil angle. 
+Participants are assumed to sample from Normal distributions centered around the true pupil angle.
+They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
+
+As $\sigma_v$ determines the level of accuracy with which the participant estimates the pupil angles, it is the component that defines $\mathbf{\theta}$.
+When $\sigma_v$ is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.
+When $\sigma_v$ is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
+We expect $\sigma_v$ to vary between individuals. Consequently, individuals differ in the level of precision with which they can locate the target based on observing the agent's eyes.
+
+The shape of the $P(x_c | \alpha_l, \alpha_r, \theta)$ distribution leads to an interesting, testable group-level prediction. 
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
+When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
+For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
+When one points the light cone directly at the surface, the light beam is concentrated in a clearly defined, small, symmetric area. 
+When one points the light cone further away from oneself (shining at an angle), the light from one half of the cone must travel further to reach the surface than the light from the other half, resulting in an asymmetric light pattern.
+As the angle increases, the light is spread over a wider area, and the surface is illuminated less evenly. 
+Consequently, for the same $\sigma_v$, the further out a target coordinate lies, the wider and less symmetric the distribution.
+This increases both the variance and the bias in a participant's estimate of the agent's attentional focus, resulting in decreased performance in the task.
+As $\sigma_v$ decreases and the cone narrows, the extent to which performance varies at different angles decreases.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4]
+If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
 Therefore, our gaze model provides a quantitative theory of gaze understanding, with testable model predictions.
@@
     Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
-In these cases, the uncertainty about the true gaze vector is - practically - only on the inner side (facing the center) of the screen.
-The natural border of the screen limits where participants can respond.
+    In these cases, the uncertainty about the true gaze vector faces - practically - only the inner side (facing the center) of the screen, since the natural border of the screen limits where participants can click.
     In another adult sample with more trials, we could recover this pattern.
@@
 Our goal was to describe the inferential process of gaze understanding.
-We quantified how well our model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information children use and where they consequently click to locate the target.
+We quantified how well our gaze model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information participants use and where they consequently click to locate the target.
 Our modeling framework consisted of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
 We gauged which model can best explain our data by conducting model comparisons.
-All cognitive models and model comparisons were implemented in WebPPL [@goodman2014design].
+All cognitive models were implemented in WebPPL [@goodman2014design].
 
@@
 This was implemented as sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
-The second alternative model assumed the participants were biased towards the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
-This bias was implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
+The second alternative model assumed the participants always want to click at the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
+This was implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
 
@@
 ## Results
+```{r gazemodel_corrs}
+gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
+```
 
@@
 
-For the gaze model, we found a high similarity between the model predictions and the observed data across the entire age range.
-The developmental trajectory that we observed in the data closely resembled the predictions of the model: the correlation between the data and the model predictions was XXX [TODO].
-The model explained XXX% [TODO] of the variance in the data.
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
+The developmental trajectory of the estimated gaze model parameter also correlated highly with the observed data: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`].
 
@@
 
-(ref:figlab2) **Gaze model**
+(ref:figlab2) **Gaze model** (A) Visualization of the gaze model.
+\alpha is defined as the pupil angle, i.e., the angle between a line connecting the eye center to the pupil and a line extended vertically downward from the pupil.
+$\sigma_v$ is the variance around the Normal distribution centered on the true pupil angle.
+This component is expected to vary between participants.
+(B) Developmental trajectory of the estimated model parameter.
+Grey dots show individual level parameter values.
+The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
+(C) Correlation between estimated mode of the model parameter and data mean per individual, color-coded by age.
+The grey regression line with 95% CI shows smooth conditional mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
+(D) Geometrical features of the gaze model.
+As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
+Top: Agent gazes centrally to the ground.
+Bottom: Agent gazes toward the side.
+The distribution around the gaze vector from which participants sample is wider compared to when the agent gazes centrally.
+The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward.
+(E) Pattern recovery.
+Imprecision in target width for each target bin by age group.
+Model predictions in blue; data in grey.
+(F) Correlation between the observed data and the predictions of the three models by target position (across age and individuals).
 
@@
 
--   persepctive-taking: stepping into somebody else's shoes. recognizing the other's thoughts, feelings, mental states (=\> ToM!!)
+-   persepctive-taking: stepping into somebody else's shoes.
+    recognizing the other's thoughts, feelings, mental states (=\> ToM!!)
 
@@
 
-    -   level 1: visibility of objects from certain view point. can operate independently from another's frame of reference
+    -   level 1: visibility of objects from certain view point.
+        can operate independently from another's frame of reference
 
@@
 
--   non-social perspective-taking task: display empty chair. spatial perspective-taking. lead to "diametrically different results"
+-   non-social perspective-taking task: display empty chair.
+    spatial perspective-taking.
+    lead to "diametrically different results"
 
@@
 
-    -   children differ in onset of milestones, degree to which they can and do use ToM in daily life. vary in frequency / propensity (connected to motivation?) and accuracy
+    -   children differ in onset of milestones, degree to which they can and do use ToM in daily life.
+        vary in frequency / propensity (connected to motivation?) and accuracy
 
-    -   ind diff to "illustrate important function ToM serves in navigating the social world". for which processes involved, contribution of other skills & environmental scaffolding
+    -   ind diff to "illustrate important function ToM serves in navigating the social world".
+        for which processes involved, contribution of other skills & environmental scaffolding
 
--   curse of knowledge: U shaped curve. hindsight bias & tom correlated, but not inhibitory control as mediator
+-   curse of knowledge: U shaped curve.
+    hindsight bias & tom correlated, but not inhibitory control as mediator
 
@@
 
-[TODO: welche sozialen prozesse überlappen hier. das hilft dann auch dabei zu sagen warum wir nicht unbedingt erwarten, dass alle ToM komponenten einen einfluss haben.]
+[TODO: welche sozialen prozesse überlappen hier.
+das hilft dann auch dabei zu sagen warum wir nicht unbedingt erwarten, dass alle ToM komponenten einen einfluss haben.]
 
-Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>. Data were collected between February and March 2023.
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.
+Data were collected between February and March 2023.
 
@@
 To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs.
-non-social context) to the non-social vector estimation task.[^5]
+This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^5]
 
-[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
-human agents.
-Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
-animal).
+[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
+    Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal).
     See Supplements for further detail.
@@
 ```{r magnet_results}
-magnet_williamsttest_tom <- readRDS("../saves/williams_tom.rds")
-magnet_williamsttest_perspective <- readRDS("../saves/williams_perspective.rds")
+magnet_williamsttest_tom <- readRDS("../saves/magnet_williams_tom.rds")
+magnet_williamsttest_perspective <- readRDS("../saves/magnet_williams_perspective.rds")
 magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
@@
 (ref:figlab3) **Components of gaze understanding.** (A) Study procedures.
-Top: TANGO (i.e., social vector estimation; gaze understanding).
+Top: TANGO (i.e., gaze understanding; social vector estimation).
 Bottom: Magnet (i.e., non-social vector estimation).
-Left: Screenshots of familiarization phase.
-Right: Screenshots of test phase.
-(B) Magnet task: non-social vector estimation.(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+Left hand side show screenshots of familiarization phase; right hand side show screenshots of the test phase.
+(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
 Dots show the correlation coefficients, while error bars represent 95% CIs.
-(C) Influence of perspective-taking and physical vector estimation on gaze understanding.
-The graph show the posterior distributions for the respective predictor.
+(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
+The graph shows the posterior distributions for the respective predictor.
 Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.

### 2023-08-10 stats/gazemodel.Rmd
adjust gaze model parts

@@
 library(cowplot) # ggdraw, draw_image, plot_grid
+library(psych) #corr.test
 
@@
 
-```{r dev_traj_inf}
+```{r plot2B}
+# (plot 2A is model logic, png)
+# developmental trajectory model inference parameter
 inf_map_devp <- model_kids_dev_prior %>%
@@
   coord_cartesian(ylim = c(0, 3)) +
-  labs(x = "Age", y = "Inference parameter")
+  labs(x = "Age", y = "Model parameter")
 
@@
 # ggsave("../figures/gazemodel_dev.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+## Correlation model vs data individual level / age
+
+```{r plot2C}
+comparison_model_data_devp <- model_kids_dev_prior %>%
+  filter(scope == "id", type == "sd") %>%
+  group_by(id) %>%
+  summarise(model_mode = estimate_mode(value)) %>%
+  left_join(
+    tango_kids %>% 
+      group_by(subj_id, age, age_group) %>%
+      summarise(data_mean = mean(click_dist_balloons)) %>%
+      rename(id = subj_id)
+  )
+
+model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
+  geom_point(aes(col = age)) +
+  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
+  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
+  labs(x = "Model parameter", y = "Data imprecision", color = "Age") + 
+  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
+  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))
+
+model_vs_data_plot
+saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
+# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
+# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
 ```
@@
 
-```{r u_pattern}
+```{r plot2E}
+# (plot 2D is model geometry logic, png)
+# u pattern recovery
 ind_sd <- model_kids_dev_prior %>%
@@
 
-priorMode <- model_kids_dev_prior %>%
-  filter(scope == "global", 
-         parameter == "priorSd", 
-         type != "sigma") %>%
-  group_by(type) %>%
-  summarise(mode = estimate_mode(value))
+# saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
 
-# careful, this runs a while...
-gen_model_clicks <- ind_sd_long %>%
-  rowwise() %>%
-  mutate(modelClick = get_click_prior(
-          sdTol = sdTol,
-          eyeCenterLY = eyeCenterLY,
-          eyeCenterLX = eyeCenterLX, 
-          eyeCenterRY = eyeCenterRY,
-          eyeCenterRX = eyeCenterRX,
-          targetCenterX = targetCenterX,
-          pupilLX = pupilLX,
-          pupilRX = pupilRX,
-          targetCenterY = targetCenterY,
-          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
-          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
-          age = age
-          ))
+# priorMode <- model_kids_dev_prior %>%
+#   filter(scope == "global",
+#          parameter == "priorSd",
+#          type != "sigma") %>%
+#   group_by(type) %>%
+#   summarise(mode = estimate_mode(value))
+#
 
-recover_plotdata <- gen_model_clicks %>%
-  mutate(
-    modelClickDist = abs(modelClick - targetCenterX),
-    targetBin = cut(targetCenterX, 
-                    breaks=seq(from = 0, to = 1920, by =192),
-                    labels=as.character(1:10))
-  ) %>%
-  group_by(age_group, targetBin) %>%
-  summarise(
-    data_mean = mean(clickDist), 
-    model_mean = mean(modelClickDist)
-  )
+# # careful, this runs a while... (ca. 30-45 min for me)
 
-saveRDS(recover_plotdata, "../saves/gazemodel_recoverU_plotdata.rds")
-# recover_plotdata <- readRDS("../saves/gazemodel_recoverU_plotdata.rds")
+# gen_model_clicks <- ind_sd_long %>%
+#   rowwise() %>%
+#   mutate(modelClick = get_click_prior(
+#           sdTol = sdTol,
+#           eyeCenterLY = eyeCenterLY,
+#           eyeCenterLX = eyeCenterLX, 
+#           eyeCenterRY = eyeCenterRY,
+#           eyeCenterRX = eyeCenterRX,
+#           targetCenterX = targetCenterX,
+#           pupilLX = pupilLX,
+#           pupilRX = pupilRX,
+#           targetCenterY = targetCenterY,
+#           priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
+#           priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
+#           age = age
+#           ))
+# 
+# modelpred_gaze <- gen_model_clicks %>%
+#   mutate(
+#     modelClickDist = abs(modelClick - targetCenterX),
+#     targetBin = cut(targetCenterX, 
+#                     breaks = seq(from = 0, to = 1920, by = 192),
+#                     labels = as.character(1:10))
+#   ) %>%
+#   group_by(age_group, targetBin) %>%
+#   summarise(
+#     data_mean = mean(clickDist) / 160, 
+#     model_mean = mean(modelClickDist) / 160,
+#   )
 
-u_plot <- recover_plotdata %>%
+# saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
+modelpred_gaze <- readRDS("../saves/gazemodel_modelpred_gaze.rds")
+
+u_plot <- modelpred_gaze %>%
   pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
@@
     age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
-    imprecision = imprecision / 160,
   ) %>% 
@@
   facet_grid(~ age_group) +
-  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 0.5)) +
-  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model estimate")) +
-  labs(x = "Target position", y = "Imprecision in target width", color = "Source") + 
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
+  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
+  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
+  theme_few() +
+  theme(
+    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
+    strip.text = element_text(face = "bold", size = 12), 
+    legend.title = element_text(size = 6),
+    legend.text = element_text(size = 6), 
+    legend.box.background = element_rect(), 
+    legend.key.height = unit(0, "cm"),
+    legend.key.width = unit(-1.5, "cm"),
+    plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
+  )
+
+u_plot
+saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
+# ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
+# ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+
+```{r modelpred_gaze_plot}
+# correlation model predicted imprecision vs data imprecision across target positions
+modelpred_gaze_plot <- modelpred_gaze %>% 
+  ggplot(., aes(x = model_mean, y = data_mean)) +
+  geom_point(aes(col = targetBin)) +
+  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_abline(intercept = 0, slope = 1, linetype = 3) +
+  scale_color_brewer(palette="BrBG") +
+  labs(x = "Gaze model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
+  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))
+
+modelpred_gaze_plot
+saveRDS(modelpred_gaze_plot, "../saves/gazemodel_modelpred_gaze_plot.rds")
+# ggsave("../figures/gazemodel_modelpred_gaze_plot.png", width = 8, height = 5, scale = 1, bg = "white")
+# ggsave("../figures/gazemodel_modelpred_gaze_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+```
+# Alternative models click generation
+
+## Center bias model
+
+```{r get_click_center}
+get_click_center <- function(){
+
+  xDist = dnorm(seq(1:1920), mean = 960, sd = 160)
+
+  click = sample(1:1920, prob = xDist, size = 1)-1
+
+  return(click)
+}
+```
+
+```{r center_model}
+gen_model_clicks_center <- ind_sd_long %>%
+  rowwise()%>%
+  mutate(modelClick = get_click_center())
+
+modelpred_center <- gen_model_clicks_center %>%
+  mutate(
+    modelClickDist = abs(modelClick - targetCenterX),
+    targetBin = cut(targetCenterX, 
+                    breaks = seq(from = 0, to = 1920, by = 192),
+                    labels = as.character(1:10))) %>%
+  group_by(age_group, targetBin) %>%
+  summarise(
+    data_mean = mean(clickDist) / 160, 
+    model_mean = mean(modelClickDist) / 160, 
+  )
+
+saveRDS(modelpred_center, file = "../saves/gazemodel_modelpred_center.rds")
+
+# facetted U plot
+modelpred_center %>%
+  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
+  mutate(
+    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
+  ) %>% 
+  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
+  geom_point(alpha = 0.8) +
+  facet_grid(~ age_group) +
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
+  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
+  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
   theme_few() +
@@
 
-u_plot
-saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
-ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
-ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+# corr plot
+modelpred_center_plot <- modelpred_center %>% 
+  ggplot(., aes(x = model_mean, y = data_mean)) +
+  geom_point(aes(col = targetBin), size = 0.8) +
+  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_abline(intercept = 0, slope = 1, linetype = 3) +
+  scale_color_brewer(palette="BrBG") +
+  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
+  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))
+
+modelpred_center_plot
+saveRDS(modelpred_center_plot, "../saves/gazemodel_modelpred_center_plot.rds")
+# ggsave("../figures/gazemodel_modelpred_center_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
+# ggsave("../figures/gazemodel_modelpred_center_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
 ```
 
-```{r imprecision_bin_plot}
-imprecision_bin_plot <- recover_plotdata %>% 
+## Random clicks model
+
+```{r get_click_random}
+get_click_random <- function(){
+
+  xDist = dunif(seq(1:1920), min = 1, max = 1920)
+
+  click = sample(1:1920, prob = xDist, size = 1)-1
+
+  return(click)
+}
+```
+
+```{r random_model}
+gen_model_clicks_random <- ind_sd_long %>%
+  rowwise() %>%
+  mutate(modelClick = get_click_random())
+
+modelpred_random <- gen_model_clicks_random %>%
   mutate(
-    model_mean = model_mean / 160, 
-    data_mean = data_mean / 160,
+    modelClickDist = abs(modelClick - targetCenterX),
+    targetBin = cut(targetCenterX, 
+                    breaks = seq(from = 0, to = 1920, by = 192),
+                    labels=as.character(1:10))
   ) %>%
+  group_by(age_group, targetBin) %>%
+  summarise(
+    data_mean = mean(clickDist) / 160, 
+    model_mean = mean(modelClickDist) / 160
+  )
+
+saveRDS(modelpred_random, file = "../saves/gazemodel_modelpred_random.rds")
+
+# facetted U plot
+modelpred_random %>%
+  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
+  mutate(
+    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
+  ) %>% 
+  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
+  geom_point(alpha = 0.8) +
+  facet_grid(~ age_group) +
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5.5, 0.5)) +
+  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model prediction")) +
+  labs(x = "Target bin", y = "Imprecision", color = "Source") + 
+  theme_few() +
+  theme(
+    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
+    legend.background = element_rect(color = "darkgrey", size = 0.1), 
+    legend.text = element_text(size = 8),
+    strip.text = element_text(face = "bold", size = 12)
+  )
+
+# corr plot
+modelpred_random_plot <- modelpred_random %>% 
   ggplot(., aes(x = model_mean, y = data_mean)) +
-  geom_point(aes(col = targetBin)) +
-  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  geom_point(aes(col = targetBin), size = 0.8) +
+  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
   geom_abline(intercept = 0, slope = 1, linetype = 3) +
   scale_color_brewer(palette="BrBG") +
-  labs(x = "Model estimated imprecision", y = "Data mean imprecision", color = "Target bin") + 
-  scale_x_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1)) + 
-  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1))
+  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
+  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
+  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))
 
-saveRDS(imprecision_bin_plot, "../saves/gazemodel_imprecision_bin_plot.rds")
-ggsave("../figures/gazemodel_imprecision_bin_plot.png", width = 8, height = 5, scale = 1, bg = "white")
-ggsave("../figures/gazemodel_imprecision_bin_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
+modelpred_random_plot
+saveRDS(modelpred_random_plot, "../saves/gazemodel_modelpred_random_plot.rds")
+# ggsave("../figures/gazemodel_modelpred_random_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
+# ggsave("../figures/gazemodel_modelpred_random_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
 ```
 
-## Data recovery
+## Combine plots of predictions from 3 models
 
-```{r model_vs_data}
-comparison_model_data_devp <- model_kids_dev_prior %>%
-  filter(scope == "id", type == "sd") %>%
-  group_by(id) %>%
-  summarise(model_mode = estimate_mode(value)) %>%
-  left_join(
-    tango_kids %>% 
-      group_by(subj_id, age, age_group) %>%
-      summarise(data_mean = mean(click_dist_balloons)) %>%
-      rename(id = subj_id)
+```{r plot2F}
+modelpred_gaze_plot <- readRDS("../saves/gazemodel_modelpred_gaze_plot.rds")
+modelpred_center_plot <- readRDS("../saves/gazemodel_modelpred_center_plot.rds")
+modelpred_random_plot <- readRDS("../saves/gazemodel_modelpred_random_plot.rds")
+
+corr_model_pred_plot <- ggarrange(
+
+  modelpred_gaze_plot + 
+    theme(legend.position = c(0.85, 0.2), 
+          legend.title = element_text(size = 6),
+          legend.text = element_text(size = 6), 
+          legend.box.background = element_rect(), 
+          legend.key.height = unit(0, "cm"),
+          legend.key.width = unit(-1.5, "cm"),
+          plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
+         ),
+
+  ggarrange(
+    modelpred_center_plot + 
+      labs(x = "Center bias model", y = "") +
+      theme(legend.position = "none", 
+            axis.text = element_text(size = 6), 
+            axis.title = element_text(size = 8), 
+            plot.subtitle = element_text(size = 8), 
+            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")),
+
+    modelpred_random_plot + 
+      labs(x = "Random guessing model", y = "") +
+      theme(legend.position = "none", 
+            axis.text = element_text(size = 6), 
+            axis.title = element_text(size = 8), 
+            plot.subtitle = element_text(size = 8), 
+            plot.margin = margin(0.2, 0.2, 0.2, 0, "cm")), 
+    nrow = 2
+  ),
+
+  ncol = 2, 
+  widths = c(1.5, 1), 
+  align = "v"
   )
 
-model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
-  geom_point(aes(col = age)) +
-  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
-  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
-  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
-  labs(x = "Model estimated mode", y = "Data imprecision mean", color = "Age") + 
-  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))
-
-model_vs_data_plot
-saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
-ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
-ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
+corr_model_pred_plot
+saveRDS(corr_model_pred_plot, file = "../saves/gazemodel_corr_model_pred_plot.rds")
 ```
@@
 ```{r arrange_plot}
-setup_png <- ggdraw() + draw_image("../figures/gazemodel_setup.png")
-ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_Ulogic.png")
+setup_png <- ggdraw() + draw_image("../figures/gazemodel_logic_alpha.png", scale = 0.82)
+ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_geometry_lines.png", scale = 0.95)
+
+dev_plot <- readRDS(file = "../saves/gazemodel_dev_plot.rds")
+model_vs_data_plot <- readRDS(file = "../saves/gazemodel_model_vs_data.rds")
+u_plot <- readRDS("../saves/gazemodel_u_plot.rds")
+corr_model_pred_plot <- readRDS("../saves/gazemodel_corr_model_pred_plot.rds")
 
@@
   NULL, 
-  imprecision_bin_plot,
+  corr_model_pred_plot,
 
@@
   nrow = 2, 
-  widths = c(9, 12, 1, 11), 
+  widths = c(9, 11, 1, 11), 
   labels = c("A", "B", "", "C", "D", "E", "", "F")
@@
 ```
+
+```{r results_table}
+# create tibble for reading out stats results in rmd manuscript
+corr_gazemodel_param <- comparison_model_data_devp %>% select(model_mode, data_mean) %>% corr.test(method = "pearson")
+
+corr_gazemodel_pred <- modelpred_gaze %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
+corr_centermodel_pred <- modelpred_center %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
+corr_randommodel_pred <- modelpred_random %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
+
+corrs <- rbind(corr_gazemodel_param$ci, corr_gazemodel_pred$ci, corr_centermodel_pred$ci, corr_randommodel_pred$ci) %>% 
+  rownames_to_column(var = "corr") %>% 
+  mutate(
+    corr = recode(
+            corr,
+            `mdl_m-dt_mn` = "gazemodel_param", 
+            `mdl_m-dt_mn1` = "gazemodel_pred", 
+            `mdl_m-dt_mn2` = "centermodel_pred", 
+            `mdl_m-dt_mn3` = "randommodel_pred", 
+           )
+  ) %>% 
+  mutate(across(where(is.numeric), round, 2))
+
+corrs
+saveRDS(corrs, file = "../saves/gazemodel_correlations.rds")
+```
+
+# Model comparison BayesFactor
+## TODO GET DATA FROM SERVER
+```{r read_data_mcomparison}
+# devp_model_comp <- rbindlist(
+#   list(
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain7.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike)),
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain8.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike)),
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain9.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike)),
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain10.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike)),
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain11.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike)),
+#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain12.csv")%>%
+#   group_by(chain, iteration, model)%>%
+#   summarise(like = sum(loglike))
+#     ), use.names=TRUE)
+```
+
+```{r modelcomparison}
+devp_model_comp %>%
+  group_by(model,chain) %>%
+  summarise(margllh = logSumExp(like)) %>%
+  pivot_wider(names_from = model, values_from = margllh)
+
+devp_model_comp %>%
+  group_by(model) %>%
+  summarise(margllh = logSumExp(like)) %>%
+  pivot_wider(names_from = model, values_from = margllh) %>%
+  summarise(bf_inf_center = inf - center, 
+            bf_inf_guess = inf - guess)
+
+devp_model_comp%>%
+  ggplot(aes(x = like))+
+  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
+  scale_fill_colorblind()+
+  xlim(-8000, -5000)+
+  theme_bw()
+```
+
+# Headlight distribution for plots
+
+```{r get_dist}
+# get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){
+# 
+#   if(eyeCenterLX > pupilLX) {
+#     tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+#   } else {
+#     tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+#   }
+#   
+#   #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
+#   
+#   if(eyeCenterRX > pupilRX) {
+#     tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+#   } else {
+#     tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+#   }
+#   
+#   #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
+# 
+#   bRDist = c()
+#   
+#   bLDist = c()
+#   
+#   for (x in 1:1920){
+#     
+#   if(eyeCenterLX > x) {
+#     betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+#   } else {
+#     betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+#   }
+#     betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
+#     
+#   if(eyeCenterRX > x) {
+#     betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+#   } else {
+#     betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+#   }
+#     betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
+#     
+#     #betaDist = betaLDist + betaRDist
+#     
+#     #bDist[x] <- exp(betaDist)
+#     bRDist[x] <- betaRDist
+#     
+#     bLDist[x] <- betaLDist
+#     
+#   }
+#   
+#   xRDist = exp(bRDist-logSumExp(bRDist))
+#   
+#   xLDist = exp(bLDist-logSumExp(bLDist))
+#   
+#   xDist = xRDist * xLDist
+#   
+#   dist = xDist / sum(xDist)
+#   
+#   # click = sample(1:1920, prob = xDist, size = 1)-1
+#   
+#   return(dist)
+# }
+```
+
+```{r headlight_dist}
+# headlight_df <- data.frame(
+#   coord = 1:1920,
+#   sdTol = "0.175"
+# )
+# 
+# for (i in c(960,1736)){
+#   
+#   probdist <-  get_dist(
+#     sdTol = 0.175,
+#     targetCenterX = i,
+#     eyeCenterLY = 937.8,
+#     eyeCenterLX = 872.12,
+#     eyeCenterRY = 937.8,
+#     eyeCenterRX = 1045.89,
+#     targetCenterY = 127.5,
+#     pupilLX = i-1,
+#     pupilRX = i-1)
+#   
+#     colname = as.character(i)
+#     
+#     headlight_df[, colname] <- probdist
+#   
+#   }
+# 
+# headlight_df %>%
+#   pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
+#   filter(target_coordinate == "960") %>%
+#   ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
+#   geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
+#   ylim(0, 0.006) +
+#   scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
+#   guides(fill = F) + 
+#   # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
+#   # labs(x = "Coordinate", y = "Probability") +
+#   # scale_fill_colorblind(name = "Inference SD") +
+#   theme_few() + 
+#   theme(
+#     panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
+#     panel.grid.minor = element_blank(), 
+#     panel.grid.major = element_blank(),
+#     plot.background = element_rect(fill = "transparent",colour = NA)
+# )
+# 
+# ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")
+# 
+# ##  Standard normal dist
+# dnorm_one_sd <- function(x){
+#   norm_one_sd <- dnorm(x)
+#   # Have NA values outside interval x in [-1, 1]:
+#   norm_one_sd[x <= -1 | x >= 1] <- NA
+#   return(norm_one_sd)
+# }
+# 
+# ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
+#   stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) + 
+#   stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
+#   # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
+#   theme_void()
+# 
+# ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
+```

### 2023-08-10 stats/supplements_changepoint_parameters.Rmd
adjust gaze model parts

@@
 ```{r run_beasts, echo=T, message=FALSE, warning=FALSE, results=FALSE}
+# this is the one we report in our paper: 
+b0 <- beast.irreg(y = y, time = x, season = "none", 
+            torder.minmax = c(0, 0), 
+            tseg.min = 10, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
+            ci = TRUE)
+
 b1 <- beast.irreg(y = y, time = x, season = "none", 
@@
             tseg.min = 10, 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
 b2 <- beast.irreg(y = y, time = x, season = "none", 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             torder.minmax = c(0, 0),
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tcp.minmax = c(0, 10), 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tseg.min = 50, 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tseg.min = 100, 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tcp.minmax = c(0, 3), 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tcp.minmax = c(0, 20), 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
             tcp.minmax = c(0, 100), 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42,
             ci = TRUE)
@@
             tseg.min = 100, 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
+            ci = TRUE)
+
+b11 <- beast.irreg(y = y, time = x, season = "none", 
+            torder.minmax = c(0, 0),
+            tcp.minmax = c(0, 72), # as max nr, since 719 datapoints, 10 tseg.min
+            tseg.min = 10, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
             ci = TRUE)
@@
 ```{r actually_printbeasts}
-beasts <- list(b1, b2, b3, b4, b5, b6, b7, b8, b9, b10)
+beasts <- list(b0, b1, b2, b3, b4, b5, b6, b7, b8, b9, b10, b11)
 
-counter = 1
+counter = 0
 
@@
 
-### Searching for reasonable minimum nr between change points
+### To judge nr of data points between change points
 
@@
 
-mean_age_diff * mean_n_per_3y * 3
+mean_age_diff
+# [1] 0.11 corresponds to mean age difference between consecutive points on the x-axis
 
-3/mean_age_diff
+mean_n_per_3y
+# [1] 27.65 data points correspond to 3 years of development
 ```
 
-```{r final_beast, message=FALSE, warning=FALSE}
-bfinal <- beast.irreg(y = y, time = x, season = "none", 
-            torder.minmax = c(0, 0), 
-            tcp.minmax = c(0, 5),
-            tseg.min = mean_age_diff * mean_n_per_3y * 3, 
-            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
-            ci = TRUE)
+```{r}
+b11
+
+plot(b11)
+
+str(b11)
+
+# Y: a vector of length N; the estimated trend component.It is the Bayesian model averaging of all the individual sampled trend.
+b11$trend$Y
+
+plot(b11, vars = c('t', 'y'))
+
+plot(b11$time, b11$trend$Y, type = 'l') # #directly plot output: the fitted trend
+
+plot(b11$time, b11$trend$cpOccPr) # #directly plot output: trend chgpt occurrence prob
 ```
 
-```{r final_beast}
-showBeast(bfinal)
+```{r}
+est <- tibble(age = x, data = y, model = b11$trend$Y)
+cps <- b11$trend$cp[1:b11$trend$ncp_median]
 
-# pull out all relevant change points
-cps <- tibble(
-          cp = bfinal$trend$cp[1:bfinal$trend$ncp_median], 
-          lowerCrI = bfinal$trend$cpCI[1:bfinal$trend$ncp_median,1], 
-          upperCrI = bfinal$trend$cpCI[1:bfinal$trend$ncp_median,2]
-       )
+ggplot(data = est, aes(data, model)) + 
+  geom_point() +
+  geom_smooth(method = "lm") + 
+  stat_cor() +
+  scale_x_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5)) +
+  scale_y_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5))
+
+n_distinct(est$model)
+
+est %>% 
+  pivot_longer(cols = c(data, model), names_to = "source") %>% 
+  ggplot(aes(x = age, y = value, color = as.factor(source))) + 
+  geom_point(alpha = 0.5) +
+  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
+  scale_color_manual(values = c("darkblue", "orange")) +
+  scale_x_continuous(limits = c(3, 80), breaks = seq(0, 80, 5)) +
+  scale_y_continuous(limits = c(0, 2.5), breaks = seq(0, 2.5, 0.5)) + 
+  labs(x = "Age", y = "Mean imprecision", color = "Source")
+
+est %>% 
+  pivot_longer(cols = c(data, model), names_to = "source") %>% 
+  filter(source == "model", age >= 20) %>%
+  ggplot(aes(x = age, y = value)) + 
+  geom_point() +
+  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
+  scale_x_continuous(limits = c(20, 80), breaks = seq(0, 80, 5)) +
+  scale_y_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, 0.5)) +
+  labs(x = "Age", y = "Mean imprecision")
 ```

### 2023-08-24 stats/gazemodel.Rmd
adjust analysis and plots

@@
 # careful, this takes a while... 
-model_kids <- readRDS("../data/gazemodel_kids.rds")
-model_kids_dev_prior <- readRDS("../data/gazemodel_kids_dev_prior.rds")
+model_kids <- readRDS("../data/gazemodel-kids.rds")
+model_kids_dev_prior <- readRDS("../data/gazemodel-kids-dev-prior.rds")
 ```
@@
 
-inf_samp_devp <- model_kids_dev_prior%>%
+inf_samp_devp <- model_kids_dev_prior %>%
   filter(scope == "global", 
@@
 
-id_devp <- model_kids_dev_prior%>%
+id_devp <- model_kids_dev_prior %>%
   filter(scope == "id", 
@@
   geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
-  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
+  geom_line(data = inf_map_devp, aes(x = age + 3, y = sd), col = "black", linewidth = 1.25) +
   scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
@@
   coord_cartesian(ylim = c(0, 3)) +
-  labs(x = "Age", y = "Model parameter")
+  labs(x = "Age in years", y = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")))
 
-dev_plot
 saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")
@@
   scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
-  labs(x = "Model parameter", y = "Data imprecision", color = "Age") + 
+  labs(x = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")), y = "Mean data imprecision", color = "Age") + 
   scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
@@
 saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
+
 # ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
@@
   scale_color_brewer(palette="BrBG") +
-  labs(x = "Gaze model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
+  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
   scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
@@
 saveRDS(modelpred_center, file = "../saves/gazemodel_modelpred_center.rds")
+modelpred_center <- readRDS(file = "../saves/gazemodel_modelpred_center.rds")
 
@@
   scale_color_brewer(palette="BrBG") +
-  labs(x = "Model predicted imprecision", y = "Data imprecision", color = "Target bin") + 
+  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
   scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
@@
 saveRDS(modelpred_random, file = "../saves/gazemodel_modelpred_random.rds")
+modelpred_random <- readRDS(file = "../saves/gazemodel_modelpred_random.rds")
 
@@
     modelpred_center_plot + 
-      labs(x = "Center bias model", y = "") +
+      labs(title = "Center bias model", x = "", y = "") +
       theme(legend.position = "none", 
             axis.text = element_text(size = 6), 
-            axis.title = element_text(size = 8), 
+            plot.title = element_text(size = 8), 
             plot.subtitle = element_text(size = 8), 
@@
     modelpred_random_plot + 
-      labs(x = "Random guessing model", y = "") +
+      labs(title = "Random guessing model", x = "", y = "") +
       theme(legend.position = "none", 
             axis.text = element_text(size = 6), 
-            axis.title = element_text(size = 8), 
+            plot.title = element_text(size = 8), 
             plot.subtitle = element_text(size = 8), 
@@
   nrow = 2, 
-  widths = c(9, 11, 1, 11), 
+  widths = c(9, 11, 1, 12), 
   labels = c("A", "B", "", "C", "D", "E", "", "F")
@@
 ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
-ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
+ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white", device = cairo_pdf) 
+# add cairo_pdf to enable greek symbols in pdf saving
 ```
@@
 # Model comparison BayesFactor
-## TODO GET DATA FROM SERVER
+
 ```{r read_data_mcomparison}
-# devp_model_comp <- rbindlist(
-#   list(
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain7.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike)),
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain8.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike)),
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain9.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike)),
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain10.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike)),
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain11.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike)),
-#        fread("../models/output/child_gaze_model_dev_prior_hedge_model_comparison_chain12.csv")%>%
-#   group_by(chain, iteration, model)%>%
-#   summarise(like = sum(loglike))
-#     ), use.names=TRUE)
+modelcomparison_kids_bf <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
+modelcomparison_kids_samples <- readRDS("../data/gazemodel-kids-comparison-samples.rds")
 ```
-
-```{r modelcomparison}
-devp_model_comp %>%
-  group_by(model,chain) %>%
-  summarise(margllh = logSumExp(like)) %>%
-  pivot_wider(names_from = model, values_from = margllh)
-
-devp_model_comp %>%
+```{r mcomparison}
+# same as reading in modelcomparison_kids_bf
+modelcomparison_kids_samples %>%
   group_by(model) %>%
@@
             bf_inf_guess = inf - guess)
-
-devp_model_comp%>%
-  ggplot(aes(x = like))+
-  geom_histogram(alpha = .5, aes(fill = model), col = "black")+
-  scale_fill_colorblind()+
-  xlim(-8000, -5000)+
-  theme_bw()
 ```

### 2023-08-24 stats/lifespan.Rmd
adjust analysis and plots

@@
 library(ggpubr) # ggarrange
+library(ggmagnify) # for plot inset
 
@@
   # raw data points
-  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
+  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey", size = 0.75) +
 
@@
   # change points from beast
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
+  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.5) +
 
-  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) +
+  # scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) +
   scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
@@
 lifespan_plot
-
-saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
-
-ggsave("../figures/lifespan_all.png", width = 7, height = 4)
-ggsave("../figures/lifespan_all.pdf", width = 7, height = 4)
 ```
 
-```{r zoomed_plot}
-# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
-lifespan_plot_zoom <- mdata %>%
-  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
-  ggplot(aes(x = age, y = mean_imprecision)) +
+```{r magnify}
+lifespan_combined <- lifespan_plot +
+  scale_x_continuous(breaks = seq(0, 10, 1)) +
+  coord_cartesian(clip = "off") + 
+  theme(plot.margin = margin(t = 40, r = 60, l = 10, b = 10)) +
 
-  # raw data points
-  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
+  # xmin, xmax, ymin, ymax
+  geom_magnify(aes(from = age < 10), to = c(55, 90, 2.5, 4.5), axes = "xy", linewidth = 0.5, proj.linetype = 3, proj = "single") +
 
-  # model predictions spaghetti lines
-  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
-  # mean model prediction
-  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", fill = "black") +
+  scale_x_continuous(breaks = seq(0, 80, 5))
 
-  # change points from beast
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
+lifespan_combined
 
-  coord_cartesian(xlim = c(3, 10)) +
-  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) +
-
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
-  labs(x = "Age in years", y = "Average imprecision in target width")
-
-lifespan_plot_zoom
-
-saveRDS(lifespan_plot_zoom, "../saves/lifespan_plot_zoom.rds")
-
-# ggsave("../figures/lifespan_zoom.png", width = 7, height = 4)
-# ggsave("../figures/lifespan_zoom.pdf", width = 7, height = 4)
+saveRDS(lifespan_combined, "../saves/lifespan_plot.rds")
+ggsave("../figures/lifespan_plot.png", width = 7, height = 4)
+ggsave("../figures/lifespan_plot.pdf", width = 7, height = 4)
 ```
-
-```{r arrange_plot}
-arranged <- ggarrange(
-  lifespan_plot, 
-  lifespan_plot_zoom, 
-  widths = c(2, 1.5), 
-  labels = c("A", "B")
-)
-
-arranged
-
-ggsave("../figures/lifespan_plot.png", width = 10, height = 3, scale = 1.2)
-ggsave("../figures/lifespan_plot.pdf", width = 10, height = 3, scale = 1.2)
-```
-
-```{r try_ggbreak}
-library(ggbreak)
-
-lifespan_cut <- mdata %>%
-  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
-  ggplot(aes(x = age, y = mean_imprecision)) +
-
-  # raw data points
-  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
-
-  scale_x_cut(breaks = c(18), scales = "free", space = 0.001) +
-
-  # model predictions spaghetti lines
-  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
-  # mean model prediction
-  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +
-
-  # change points from beast
-  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +
-
-  scale_x_continuous(limits = c(3, 80), breaks = c(3:17, 20, 30, 40, 50, 60, 70, 80)) +
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
-
-  labs(x = "Age", y = "Mean imprecision", xdist = "", ydist = "")
-
-lifespan_cut
-```
-
-```{r try_ggh4x}
-library(ggh4x)
-
-mdata %>%
-  mutate(my_facet = age > 20.00) %>% 
-  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
-
-  ggplot(aes(x = age, y = mean_imprecision)) +
-
-    # raw data points
-  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +
-
-    # model predictions spaghetti lines
-  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
-  # mean model prediction
-  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +
-
-  # for gap in x axis
-  facet_grid(~ my_facet, scales = "free_x") +
-  theme(strip.text.x = element_blank()) +
-
-  ggh4x::facetted_pos_scales(x = list(
-    my_facet == FALSE ~ scale_x_continuous(limits = c(3, 20), breaks = seq(3, 19, 1)),
-    my_facet == TRUE ~ scale_x_continuous(limits = c(20, 80), breaks = seq(20, 80, 10))
-)) +
-
-  geom_vline(data = data.frame(xint=cps$cp[1:4], my_facet = FALSE), aes(xintercept = xint), linetype = "dotted") +
-  geom_vline(data = data.frame(xint=cps$cp[5:6], my_facet = TRUE), aes(xintercept = xint), linetype = "dotted") +
-
-  labs(x = "Age in years", y = "Average imprecision in target width") +
-
-  # get rid of space between facets
-  theme(panel.spacing = unit(0.1, "lines"))
-```

### 2023-08-24 stats/magnet.Rmd
adjust analysis and plots

@@
   labs(x = "Magnet mean", y = "Tango mean")
+
+magnet_data %>% 
+  group_by(subj_id) %>% 
+  mutate(tom_other = sum(desires, knowledge, content, explicit)) %>% 
+  ggplot(., aes(x = tom_other, y = perspective_aggregate)) + 
+  geom_smooth(method = "lm", size = 1, alpha = 0.25, col = "darkgrey") +
+  geom_jitter(color = "#005555", width = 0.05, height = 0.05) +
+  stat_cor(method = "pearson", label.x = 0, label.y = 1.1, aes(label = paste(..r.label..)), size = 5, r.accuracy = 0.01, cor.coef.name = "r") + 
+  scale_x_continuous(limits = c(0, 4), breaks = seq(0, 4, 1)) +
+  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, 1)) +
+  labs(x = "ToM excl. perspective-taking", y = "Perspective-taking")
 ```

### 2023-08-24 stats/supplements_changepoint_parameters.Rmd
adjust analysis and plots

@@
 
-```{r}
-b11
+```{r luke}
+library(tidyverse)
+library(Rbeast) # Bayesian change point analysis
+set.seed(42)
 
-plot(b11)
+lifespan_data <- readRDS("../data/tango-lifespan.rds")
 
-str(b11)
+mdata <- lifespan_data %>% 
+  group_by(subj_id, age, age_centered) %>% 
+  summarize(mean_imprecision = mean(click_dist_balloons, na.rm = TRUE))
+
+x <- mdata %>% arrange(age) %>% pull(age)
+y <- mdata %>% arrange(age) %>% pull(mean_imprecision)
+
+ibeast <- beast.irreg(y = y, time = x, season = "none", 
+            torder.minmax = c(0, 0),
+            tcp.minmax = c(0, 72), # as max nr, since 719 datapoints, 10 tseg.min
+            tseg.min = 10, 
+            mcmc.chains = 4, mcmc.burnin = 1000,  mcmc.samples = 10000, mcmc.seed = 42, 
+            ci = TRUE)
 
 # Y: a vector of length N; the estimated trend component.It is the Bayesian model averaging of all the individual sampled trend.
-b11$trend$Y
+ibeast$trend$Y
 
-plot(b11, vars = c('t', 'y'))
+# plotting with Rbeast plot function
+plot(ibeast)
 
-plot(b11$time, b11$trend$Y, type = 'l') # #directly plot output: the fitted trend
+plot(ibeast, vars = c('t', 'y')) # plot time vs predicted values
+plot(ibeast$time, ibeast$trend$Y, type = 'l') # directly plot output: the fitted trend line
+plot(ibeast$time, ibeast$trend$cpOccPr) # directly plot output: trend chgpt occurrence prob
 
-plot(b11$time, b11$trend$cpOccPr) # #directly plot output: trend chgpt occurrence prob
-```
+# create imprecision as observed in data and as predicted by cp analysis
+est <- tibble(age = x, data = y, model = ibeast$trend$Y)
+cps <- ibeast$trend$cp[1:ibeast$trend$ncp_median]
 
-```{r}
-est <- tibble(age = x, data = y, model = b11$trend$Y)
-cps <- b11$trend$cp[1:b11$trend$ncp_median]
-
-ggplot(data = est, aes(data, model)) + 
-  geom_point() +
-  geom_smooth(method = "lm") + 
-  stat_cor() +
-  scale_x_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5)) +
-  scale_y_continuous(limits = c(0, 3), breaks = seq(0, 3, 0.5))
-
+# check how many distinct fitted values
+# => here question: 
+# I'd assume that we need as many distinct
 n_distinct(est$model)
 
+# plot raw data and fitted values from cp analysis
 est %>% 
@@
   labs(x = "Age", y = "Mean imprecision", color = "Source")
-
-est %>% 
-  pivot_longer(cols = c(data, model), names_to = "source") %>% 
-  filter(source == "model", age >= 20) %>%
-  ggplot(aes(x = age, y = value)) + 
-  geom_point() +
-  geom_vline(xintercept = cps, linetype = "dashed", alpha = 0.9, size = 0.75) +
-  scale_x_continuous(limits = c(20, 80), breaks = seq(0, 80, 5)) +
-  scale_y_continuous(limits = c(0.5, 1), breaks = seq(0.5, 1, 0.5)) +
-  labs(x = "Age", y = "Mean imprecision")
 ```

### 2023-09-01 paper/manuscript.Rmd
major edits in intro & discussion

@@
 abstract: |
-  Abstract max 250 words
-
+  Observing eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
+While the emergence of gaze following in infancy has been thoroughly studied, we know little about the developmental trajectory throughout childhood and adolescence.
+The present study examines gaze understanding across the lifespan.
+We formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way.
+The key parameter in our model is an inferential component, which describes how accurately a participant infers a target location based on the agent's gaze.
+We test a fundamental assumption of our gaze model by studying vector estimation in a non-social setting.
+Lastly, we explore the relationship between other social-cognitive abilities and gaze understanding.
+We found a steep learning curve in gaze understanding during the preschool years.
+In these years, children become more precise in locating the attentional focus of an agent.
+Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+Our gaze model estimates reliable individual parameter values and recovers signature patterns in the data.
+Furthermore, we found that gaze understanding is associated with non-social vector estimation and perspective-taking but not with other Theory of Mind tasks.
+This work illustrates how the combination of reliable tasks and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
 keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
@@
 We would also like to thank Steven Kalinke for his technical programming support.
+We thank all the children, caregivers, and adults who participated in the study.
 
@@
 Manuel Bohn was supported by a Jacobs Foundation Research Fellowship.
-We thank all the children, caregivers, and adults who participated in the study.
 
-**Ethical statement:** The studies were approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.Informed consent was obtained from all individual participants or their legal guardians.
+**Ethical statement:** The studies were approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+Informed consent was obtained from all individual participants or their legal guardians.
 
@@
 
-# Research highlights
+# Research highlights (to be placed before the abstract)
 
--   up to four bulleted points outlining the key contributions to research the paper makes.
--   The Research Highlights should be placed before the abstract.
--   Each research highlight should not be longer than 25 words.
+-	Gaze understanding develops beyond infancy. Young adults reach the highest precision levels in localizing an attentional focus, while older adults perform slightly less precisely. 
+-	We present a computational model as a mechanistic description of gaze understanding. The model explains individual differences and recovers signature patterns in the data.
+-	Our model assumes that gaze understanding relies on vector estimation. To test this assumption experimentally, we designed a non-social vector estimation task. 
+-	We found an association between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
 
 # Introduction
+How do humans learn about their environment and navigate through their social surroundings?
+A promising approach to extract information from the environment is through following the gaze of others.
+Recognizing the attentional focus of other agents also helps in building common ground and is vital for communicative interactions and shared activities [@tomasello2007reliance].
 
--   why do we care about developmental trajectory? ref to stat learning paper
--   variation
+Existing studies operationalize gaze following as the ability to follow another agent’s line of sight.
+As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
+The traditional, often-used paradigm to study gaze following looks as follows [e.g., @gredeback2010development]: The experimenter sits in front of the infant, with one object to their left and one to the right.
+The experimenter looks directly at the infant before shifting her head and eyes to one of the two objects.
+Infants’ looking times or dichotomous object choices are then recorded.
+Analyses traditionally focus on the average age at which children reach an above-chance performance (i.e., looking at the gaze-cued target object).
+According to this research, infants as young as six months can attune their gaze to that of another agent  [@dentremont1997demonstration].
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects].
 
-## Why do we need gaze understanding?
+At first glance, the debate about infants’ gaze-following abilities seems to be settled.
+On further view, however, some methodological choices in the experimental paradigms as well as the scope of infants’ abilities seem to offer room for further exploration.
+We see the following challenges: (1) Studies focus on infancy, leaving aside further potential developments in childhood and adolescence; (2) Gaze cues are often accompanied by a head movement in the same direction, which makes it hard to isolate the signaling power of the eyes; (3) Often, infants’ looking times are taken as a benchmark for passing a task, while it is uncertain how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Behavior is grouped into passing/failing or a comparison against chance, ignoring the accuracy of children; (6) Analyses focus on group-level averages, overlooking variation in the sample.
 
-How do humans learn about their environment and navigate through their social surroundings?
-One possibility to extract information from the environment is through following others' focus of attention.
-Building a common ground is considered especially important in communicative interactions and shared activities [@tomasello2007reliance].
-
-## How does gaze following emerge?
-
-Existing studies operationalize gaze following as the ability to follow another agent's line of sight.
-As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
-Infants as young as six months can attune their gaze to that of another agent [@dentremont1997demonstration].
-At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412].
-
-While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
+Adding to the first point, while the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
 One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
@@
 Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
+We believe that the development of gaze understanding is, most likely, not complete merely because infants can differentiate between two objects, one which has been gazed at.
+In daily life, we often face more nuanced, fine-grained gaze cues and must differentiate between a virtually unlimited number of potential targets.
 
-## The scope of infants' gaze following ability
-
-Though these studies suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions of the other agent.
-Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.
-Butterworth & Jarrett's ecological and geometric mechanism, @butterworth1991minds].
-Therefore, it is crucial to study children's intentional understanding of gaze.
-
-@moore1997role showed that 9-month-olds followed an agent's gaze more, when it was accompanied by a dynamic head turn in comparison to a static head turn.
-
-In a hiding game with two search locations, @povinelli1997exploitation found that three-year-olds used gaze as a cue to locate the reward, while two-year-olds performed at chance level.
-
-In a similar object choice paradigm with two containers, @behne2005oneyearolds investigated whether infants understand the communicative intent behind pointing and gaze cues.
-In contrast to @povinelli1997exploitation, they found that already 14-month-olds used the agent's cues to select an object.
-In conditions with absent-minded 'cues', infants performed around chance.
-This could be interpreted as infants recognizing the nature of this joint activity: namely, that the adult's behavior was beneficial and relevant for their object choice.
-
-### Head vs eye direction
-
-It is important to note that in many existing gaze conditions, the experimenter shifted their eyes and head in synchrony (e.g., [@povinelli1997exploitation, @behne2005oneyearolds]).
+Let us now turn to the point that often the experimenter shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds].
 Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
-
 A handful of studies approached this potential confound by separately manipulating head and eye movement.
 @brooks2002importance implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
-
+@moore1997role showed that 9-month-olds followed an agent’s gaze more when it was accompanied by a dynamic head turn in comparison to a static head turn.
 Investigating the 'cooperative eye hypothesis', @tomasello2007reliance implemented six conditions, in which an experimenter oriented towards the ceiling with their eyes only, head only (eyes closed), both head and eyes, or neither.
 They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
+Results of @corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
+This underlines how important the movement of the head is when interpreting the gaze of others and that the scope of infants' gaze understanding might be less comprehensive than previously assumed.
 
-Importantly, the subjects were not presented with an object choice but their attention orientation was measured.
+Next, let us consider the classical response measure of collecting looking times.
+Though previous studies using the above-mentioned methods suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the content of the other agent’s gaze.
+Infants could simply attune their orientation or be attracted by others’ gaze without processing what exactly the other is seeing [cf.
+Butterworth & Jarrett's ecological and geometric mechanism, @butterworth1991minds].
+Arguably, this is not sufficient to claim an understanding of visual perspectives, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
+358].
+To fulfill this criterion, @moll2006level used an active behavioral choice as a response measure and tested infants' understanding of the intentions behind gaze.
+Infants interactively searched for the target object, which was either occluded or visually accessible.
+They found that 24-month-olds adaptively handed over the target object, while 18-month-olds still struggled to complete this task.
+In a hiding game with two search locations, @povinelli1997exploitation found that two-year-olds performed at chance level when using gaze as a cue to locate the reward, while three-year-olds passed the task.
+However, in a similar object choice paradigm with two containers, @behne2005oneyearolds investigated whether infants understand the communicative intent behind pointing and gaze cues.
+In contrast to @povinelli1997exploitation, they found that already 14-month-olds used the agent’s cues to select an object.
+In conditions with absent-minded ‘cues’, infants performed around chance.
+The specific scope of children’s gaze understanding and whether correct looking translates into meaningful active behavior deserve further investigation.
 
--   [@raviv2018developmental]
-
--   [@astor2022gaze]
-
--   [@colombo2001development]
-
--   [@scaife1975capacity]
-
--   [@itakura1998use]
-
--   [@carpenter1998social] "Several other studies have attempted to determine more precisely the cue that infants are using when they follow the gaze direction of others, that is, whether they use adults' head or eye orientation.
-In tasks comparing infants' responses when the experimenters turned their head and eyes together to targets with their responses when the experimenters directed their eyes to the targets but their head remained facing forward, Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) all found that only infants age 12 months and older responded correctly when eyes and head were oriented in the same direction and that infants at all ages (i.e., through 19 months) performed poorly when eye and head direction diverged" (p.10-11) object choice.
-
--   [@silverstein2021infants] for vertical plane
-
--   [@zhang2019role]
-
--   [@frischen2007gaze]
-
--   [@lee1998children]
-
--   [@coelho2006searching]
+Finally, presenting two objects, focusing on group-level analysis, and passing versus failing a task drastically limit the level of detail with which we can gauge children’s gaze understanding.
+Undoubtedly, children can vary in the onset of their social-cognitive abilities: these skills develop over time, with experience, and on a continuum.
+@birch2017perspectives argued that individuals can differ in their frequency (or propensity) and accuracy of applying social cognition in their daily lives.
+Measuring individual differences in this domain is especially important to understand the underlying processes and to disentangle the impact of environmental influences (scaffolding) and other cognitive abilities [@birch2017perspectives].
 
@@
 
-### Developmental trajectory, measuring & modeling individual differences
+With our study, we aim to deepen our knowledge about the development and mechanisms behind gaze understanding.
+We study the differentiation of this social-cognitive ability by using a study design with subtle gaze cues without head rotation.
+While we expect the younger children to be able to follow gaze, we aim at assessing the differentiation of their social-cognitive ability.
+Our goal was *not* to establish the youngest age at which children understand gaze cues.
+Rather, we wanted to examine *how* that ability changes with age.
+In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent’s gaze.
+While language demands are low, participants have to actively respond and, therefore, make use of the presented gaze cue.
+By measuring a continuous, active behavior, we can capture meaningful variation between individuals.
+We strive to embrace and explain diversity in gaze understanding and use individual differences to inform what happens on a process level.
 
-In this study, we were interested in the developmental trajectory of gaze understanding.
-While we expect the younger children to be able to follow gaze, we aimed at assessing the differentiation of their social-cognitive ability.
-Our goal was *not* to establish the youngest age at which children understand gaze cues.
-Rather, we wanted to examine how that ability changes with age.
-
-In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent's gaze.
-While language demands were kept low, the participants had to actively respond and, therefore, make use of the presented gaze cue.
-
-A unique contribution of this study is the richness of the data set.
-Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
-We could circumvent these issues by applying the exact same task for the entire life span.
+The present paper is structured in the following way.
+In Study 1, we explore gaze understanding across the lifespan.
+We assess the developmental trajectory and individual differences in this fundamental social-cognitive ability in a sample of 3- to 80-year-olds.
+In Study 2, we propose a computational cognitive model of gaze understanding.
+This model helps us to explain where individuals vary and which mechanisms participants use to locate an agent’s attentional focus.
+In Study 3, we revisit a fundamental assumption of our computational gaze model by experimentally isolating the vector estimation component of gaze understanding.
+Furthermore, we investigate the relationship between gaze understanding and other (social-) cognitive processes.
 
@@
 
-<https://osf.io/6yjz3>
-
 ```{r lifespan_sample, include = T, out.width = "100%"}
@@
 We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age (see Supplements for further details).
-
 The child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants.
@@
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
-They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income \~ 1,600€ as of 2021).
+They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income ~ 1,600€ as of 2021).
 Most were raised monolingually in a nuclear two-generational family setting.
@@
 *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision.
+Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults who reported to have normal or corrected-to-normal vision.
 For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
-For further information on age and gender of participants, see Table 1.
 
@@
 We used the continuous version of the TANGO [@prein2023tango].
-The task was presented as an interactive web application (see Figure \@ref(fig:fig1); live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability [with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; @prein2023tango].
+The task was presented as an interactive web application (live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
+The TANGO showed satisfactory internal consistency and retest reliability (with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; [@prein2023tango]).
 
@@
 In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
-The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1]
-The unit of imprecision was counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target widths, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
 We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights [@vehtari2017practicala].
@@
 However, the Gaussian Process model was computationally heavy.
-    To circumvent issues of convergence and for practicability, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
-    In the Supplements, you can find a comparison between the original and the here reported model structures.
-    Essentially, the model predictions did not differ notably.
+To circumvent issues of convergence, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+See Supplements for a comparison between the original and the here-reported model structures.
+The model predictions did not differ notably.
 
@@
 Grey dots show the mean performance for each subject averaged across trials.
-Blue lines show 100 draws from the expectation of the posterior predictive distribution (i.e, conditional expectation) of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
-Vertical, black, dashed lines show the location of the most prominent change points.
+Blue lines show 100 draws from the expectation of the posterior predictive distribution (i.e., conditional expectation) of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
+Vertical, black, dashed lines show the locations of the most prominent changes according to our Bayesian change point analysis.
 
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics(c("../figures/lifespan_all.png"))
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics(c("../figures/lifespan_plot.png"))
 ```
@@
 High levels of variation pointed to individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
-For example, there were some children that were more accurate than the average adult.
+For example, there were some children who were more accurate than the average adult.
 
 In our model comparison, we found clear evidence for a non-linear development in gaze understanding across the lifespan.
-Compared against a linear, quadratic, and cubic model, the Gaussian Process model showed the best model fit, demonstrated by the greatest model weight and smallest WAIC values.
-For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) and visual inspection indicated nonlinearity (see Figure \@ref(fig:fig2)).
+Compared against linear, quadratic, and cubic models, the Gaussian Process model showed the best model fit, demonstrated by the greatest model weight and smallest WAIC values.
+For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) and visual inspection indicated nonlinearity (see Figure \@ref(fig:fig1)).
 
 Going one step further, we investigated the most prominent change points in the data.
-The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp %>% round(1)` (with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp %>% round(1) + 1] * 100 %>% round(2)`% probability) major shifts in gaze understanding during the lifespan.
-The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); followed by `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); followed by `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); and finally at `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]).
-In other words: we found a very rapid initial improvement in early childhood (three change points in rapid succession), followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
+The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` (with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability) major shifts in gaze understanding during the lifespan.
+The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[5]` years (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]); `r lifespan_cps$upperCrI[5]`]); and finally, at `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
+In other words: we found a very rapid initial improvement in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
 
@@
 We investigated the shape of change in gaze understanding across the lifespan.
-By applying the exact same task for the entire life span, we could directly compare gaze understanding in all ages.
+By applying the exact same task for the entire age range, we could directly compare gaze understanding in all ages.
 Therefore, we circumvented methodological challenges that often arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
@@
 First of all, we used subtle eye movements as cues.
-Many existing studies let the agents move eye and head in parallel [@behne2005oneyearolds; @povinelli1997exploitation], therefore establishing a confound with greater (head) movement.
+Many existing studies let the agents move eye and head in parallel [@behne2005oneyearolds; @povinelli1997exploitation], therefore establishing a confound with more salient head movement.
 Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation [@carpenter1998social].
@@
 Regarding the sample of elderly adults, we expect a sampling bias to be present [@bethlehem2010selection; @gosling2004should; @remillard2014systematic].
-First, certainly not all older people have working a high-speed Internet connection or are knowledgeable and trained in its use.
+First, certainly not all older people have a working high-speed Internet connection or are knowledgeable and trained in its use.
 Second, it takes a certain amount of independence and motivation to participate in *Prolific* studies.
-The elderly who know how to participate in *Prolific* studies certainly might show greater cognitive fitness and flexibility compared to their offline counterparts.
+The elderly who know how to participate in *Prolific* studies might show greater cognitive fitness and flexibility compared to their offline counterparts.
 Therefore, a representative sample might show a greater age decline in gaze understanding compared to our reported sample.
@@
 Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
-The TANGO has previously been shown to be reliably capture inter-individual differences in gaze understanding [@prein2023tango].
+The TANGO has previously been shown to reliably capture inter-individual differences in gaze understanding [@prein2023tango].
 The variation between participants is thus likely genuine and not due to random noise.
@@
 We seek to explain how participants solved the TANGO.
-Our gaze model assumes that participants use available gaze information to infer the target location.
+We designed a computational cognitive model that replicates a schematic representation of how participants make inferences in the task's context (i.e., model of the task and not the data).
+The fundamental assumption of this gaze model is that participants use all available gaze information to infer the target location.
 
@@
 Adults were recruited over *Prolific* [@palan2018prolific].
-Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that had completed the study.
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
 
@@
 \begin{equation}
-    P(\mathbf{\theta} | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \mathbf{\theta})P(\mathbf{\theta})
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
 \end{equation}
 
-where $\mathbf{\theta}$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
-The pupil angle is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the pupil.[^3]
+where $\theta$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
+The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see \@ref(fig:fig2)A).[^3]
 
@@
 In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
-    We then calculate a line between these two points: this is our gaze vector.
+We then calculate a line between these two points: this is our gaze vector (acting in the functionally same way as a pupil angle).
 Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
@@
 Based on our verbal task instructions, we assume that participants (1) expect the agent's looks to be directed at the target, and (2) to click on the coordinate they estimate the agent to look at.
-Consequently, we do not assume that participant's clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at). 
+Consequently, we do not assume that participants' clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at).
 However, the true eye angles ($\alpha_l$ and $\alpha_r$) cannot be directly observed.
@@
 We presume this estimation to be a noisy process.
-Thus, the development of the cognitive ability to follow gaze corresponds to a reduction in the magnitude of the noise in the estimates (i.e., an increased certainty about the eye angles).
+Thus, the development of the cognitive ability to follow gaze corresponds to a reduction in the magnitude of the noise in the estimates (i.e., an increased certainty about the pupil angles).
 
@@
 
-The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assume to be skewed towards the screen center: 
-We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
+The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assume to be skewed towards the screen center: We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
 We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data.
 
+We estimated $P(x_c)$ as a deviation from a hyper parameter: $P(x_c)_i \sim \mathcal{N}(960,\sigma^{P(x_c)_j})$.
+Please note that µ = 960 specifies the center of the screen.
+To allow developmental effects in this center bias, we defined $P(x_c)_j$ via a linear regression as a function of the participant's age ($age_i$): $P(x_c)_j = \beta_0^{P(x_c)} + age_i \cdot \beta_1^{P(x_c)}$.
+Therefore, the participant-specific value for $P(x_c)$ was constrained by the performance in the TANGO and the participant's age.
+
 The main inferential task for the participant lies in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
-For this, we assume that the pair of estimated angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance $\sigma_v$ centered on the true pupil angles:
+For this, we assume that the pair of estimated pupil angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance $\sigma_v$ centered on the true pupil angles:
 
@@
 
-Broadly summarizing: Participants are assumed to observe the pupil locations and estimate the center of the agent's eyes.
+Broadly summarizing: Participants are assumed to observe the pupil locations and the center of the agent's eyes.
 Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
@@
 
-As $\sigma_v$ determines the level of accuracy with which the participant estimates the pupil angles, it is the component that defines $\mathbf{\theta}$.
-When $\sigma_v$ is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.
-When $\sigma_v$ is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
-We expect $\sigma_v$ to vary between individuals. Consequently, individuals differ in the level of precision with which they can locate the target based on observing the agent's eyes.
+As $\sigma_v$ determines the level of accuracy with which the participant estimates the pupil angles, it is the component that defines $\theta$.
+When $\sigma_v$ is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.\ When $\sigma_v$ is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
+We expect $\sigma_v$ to vary between individuals.
+Consequently, individuals differ in the level of precision with which they can locate the target based on observing the agent's eyes.
 
@@
 As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
-When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
+When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them (see \@ref(fig:fig2)D).
 For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
@@
 Consequently, for the same $\sigma_v$, the further out a target coordinate lies, the wider and less symmetric the distribution.
-This increases both the variance and the bias in a participant's estimate of the agent's attentional focus, resulting in decreased performance in the task.
+This increases both the variance and the bias in a participant's estimate of the agent's attentional focus, resulting in a decreased performance in the task.
 As $\sigma_v$ decreases and the cone narrows, the extent to which performance varies at different angles decreases.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4]
-If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
-Therefore, our gaze model provides a quantitative theory of gaze understanding, with testable model predictions.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding with testable model predictions.
 
@@
 Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
-    In these cases, the uncertainty about the true gaze vector faces - practically - only the inner side (facing the center) of the screen, since the natural border of the screen limits where participants can click.
+In these cases, the uncertainty about the pupil angle faces practically only the inner side (facing the center) of the screen, since the natural border of the screen limits where participants can click.
 In another adult sample with more trials, we could recover this pattern.
@@
 The first alternative model assumed participants were randomly guessing.
-This was implemented as sampling from a uniform distribution over all possible coordinates (i.e., 0 - 1920).
-The second alternative model assumed the participants always want to click at the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
-This was implemented as sampling from a Normal distribution, with the center of the screen as the mean and one target width as the standard deviation.
+This was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
+The second alternative model assumed the participants always wanted to click at the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
+This was implemented as sampling from a Normal distribution, $\mathcal{N}(960, 160^2)$, with the the center of the screen as the mean, and one target width as the standard deviation.
 
@@
 We visualized and evaluated these differences using correlations between the model predictions and the data.
+For this, we converted the models' posterior distributions for each participant into a single value by taking the mode (and 95% highest density interval--HDI).
 Furthermore, we evaluated these probabilistic models based on the marginal likelihood of the data under each model.
@@
 
-[TODO: add more infos on priors & parameters]
+## [TODO: add more infos on priors & parameters]
 
 ## Results
-```{r gazemodel_corrs}
+
+```{r gazemodel_results}
+gazemodel_comparison_bf <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
 gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
@@
 We found clear support for our gaze model, both in children as well as adults.
-
-When we compared the gaze model to the two competitor models, we found little support for the two alternatives.
-Comparing the models using marginal likelihood of the data under each model, the data were XXX [TODO] more likely under the gaze model compared to the random clicking or center bias model.
-
+The Bayes Factors we computed via the marginal likelihood of the data strongly favored our gaze model compared to the center bias model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_center`) and the random guessing model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_guess`).
 When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
 The developmental trajectory of the estimated gaze model parameter also correlated highly with the observed data: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`].
-
-[TODO: report prior]
+The age effects in Study 2 largely replicated those of Study 1.
 
 (ref:figlab2) **Gaze model** (A) Visualization of the gaze model.
-\alpha is defined as the pupil angle, i.e., the angle between a line connecting the eye center to the pupil and a line extended vertically downward from the pupil.
-$\sigma_v$ is the variance around the Normal distribution centered on the true pupil angle.
-This component is expected to vary between participants.
+Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+Taking the angle between this vector and a line pointing vertically to the ground (black dashed line) yields the pupil angle ($\alpha$).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle ($\alpha$).
+The variance around the Normal distribution ($\sigma_v$) is centered on the true pupil angle and expected to vary between participants.
 (B) Developmental trajectory of the estimated model parameter.
@@
 (D) Geometrical features of the gaze model.
-As the pupil location varies, a fixed amount of uncertainty around the gaze vector corresponds to a varying degree of uncertainty in the estimated target location.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
 Top: Agent gazes centrally to the ground.
 Bottom: Agent gazes toward the side.
-The distribution around the gaze vector from which participants sample is wider compared to when the agent gazes centrally.
+The distribution around the pupil angle from which participants sample is wider compared to when the agent gazes centrally.
 The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward.
@@
 
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
 knitr::include_graphics("../figures/gazemodel_plot.png")
@@
 
-Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan.
-To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
+Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
 Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
@@
 
+Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of @michelon2006two: in their Level 1 perspective-taking visibility task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
+Additionally, targets closer to the midline were more easily traced than ones further away from the agent.
+The authors concluded that visual acuity is generally higher for locations on the vertical axis than for those on diagonal axes (cf.
+"oblique effect"; [@appelle1972perception; @heeley1997oblique; @mikellidou2015oblique]).
+Not only is our finding of increased imprecision for greater pupil angles (i.e., trials in which the target lands further out) consistent with this finding, but our gaze model poses a viable explanation for this effect.
+
 A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
 
-A critical feature of our model is that it assumes gaze understanding to rely on vector estimations.
-In other words, subjects are modeled to calculate gaze vectors based on the location of an agent's pupil.
-This way, they can infer the agent's attentional focus.
+A critical feature of our model is that it assumes gaze understanding to rely on vector estimation.
+In other words, subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
 Even though this vector estimation component is a rather physical, geometrical calculation, it still happens in a social context.
@@
 # Study 3: Components of gaze understanding
-
-## Perspective-taking:
-
-[@erle2017grounded]
-
--   differentiation between visuospatial perspective-taking and psychological (i.e., cognitive and affective) perspective-taking
-
--   unclear boundaries between ToM & perspective-taking, many correlational studies, not so many causation "terminological confusion"
-
--   persepctive-taking: stepping into somebody else's shoes.
-    recognizing the other's thoughts, feelings, mental states (=\> ToM!!)
-
-    -
-
-        1)  attesting mental states to another social agent
-
-    -
-
-        2)  other's states can be ≠ to own
-
-    -
-
-        3)  put aside egocentric bias
-
--   little is known about underlying psychological mechanisms of perspective-taking
-
--   visuospatial perspective taking: mentally transforming yourself and your body into the physical location of another agent.
-    judging differences between one's own egocentric point of view an that of another person
-
-    -   level 1: visibility of objects from certain view point.
-        can operate independently from another's frame of reference
-
-    -   level 2: imagine how world looks like for another person "climbing into the skin of another person".
-        literally rotating body schema (embodied) "transposing body schema into the target's position"
-
--   clinical populations show deficit in empathy & visuospatial perspective-taking
-
--   idea that psychological & visuospatial perspective-taking share common simulation-based mechanism
-
--   studies show that: "Taking another's perspective led participants to adopt the thoughts of the target person more strongly (Experiments 1--3) and increased the perceived similarity of that person to the self (Experiment 4) and participants' liking of that person (Experiment 5).
-These effects were independent of task difficulty (Experiment 2), and only present during trials where an embodied transformation happened (i.e., at high angular disparities; Experiment 3)." "not only affects social-cognitive outcomes, but also empathic perspective-taking" =\> "shared mechanism of all kinds of perspective-taking"
-
--   non-social perspective-taking task: display empty chair.
-    spatial perspective-taking.
-    lead to "diametrically different results"
-
-[@birch2017perspectives]
-
--   "Specifically, we contend that these processes (a) are partially innate, (b) develop over time and can be honed through experience, and (c) lie on a continuum with some individuals being better than others."
-
--   Apperly & Buuterfill 2009: System 1 process social information relatively quickly & effortlessly, clear limitations, inflexible.
-    System 2 explicit reasoning, involves language, inhibitory control, working memory, cognitive flexibility, reasoning, planning etc.
-
--   chapter assumes partial innateness, develop over time, can be honed through experience, lie on a continuum with some individuals being "Better" than others
-
--   children use gaze as indicators of others' mental states from an early age
-
--   individual differences:
-
-    -   children differ in onset of milestones, degree to which they can and do use ToM in daily life.
-        vary in frequency / propensity (connected to motivation?) and accuracy
-
-    -   ind diff to "illustrate important function ToM serves in navigating the social world".
-        for which processes involved, contribution of other skills & environmental scaffolding
-
--   curse of knowledge: U shaped curve.
-    hindsight bias & tom correlated, but not inhibitory control as mediator
 
@@
 To answer this question, we assessed the relationship between gaze understanding and other social-cognitive abilities.
+We reasoned that gaze understanding is integral to social interaction, which is most likely learned in the social world.
+The positive link between TANGO and family-level variables like number of siblings [@prein2023tango] underlines this.
+Therefore, it seems reasonable to expect correlations between gaze understanding and other social-cognitive abilities.
 
@@
 We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
-Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (\@wellman2004scaling) and two additional perspective-taking tasks [\@flavell1981development; \@flavell1981younga].
+Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling] and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
 
-We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
+We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
 This way, we aimed to disentangle what components comprise gaze understanding.
 
-[TODO: welche sozialen prozesse überlappen hier.
-das hilft dann auch dabei zu sagen warum wir nicht unbedingt erwarten, dass alle ToM komponenten einen einfluss haben.]
-
-Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>.
-Data were collected between February and March 2023.
+Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>. Data were collected between February and March 2023.
 
@@
 
-### Theory of Mind task battery
+### ToM task battery
 
-We administered four tasks from the @wellman2004scaling Theory of Mind scale.
+We administered four tasks from the @wellman2004scaling ToM scale.
 We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
@@
 To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs. non-social context) to the non-social vector estimation task.[^5]
+This further highlighted the contrast (i.e., social vs.
+non-social context) to the non-social vector estimation task.[^5]
 
-[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents.
-    Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal).
+[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
+human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
+animal).
 See Supplements for further detail.
@@
 
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
 knitr::include_graphics("../figures/magnet_plot.png")
@@
 However, physical vector estimation alone did not suffice to explain gaze understanding.
-In addition, perspective-taking proved to be a relevant social-cognitive ability.
+In addition, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
 
-[TODO: das klingt als ob perspective taking ein prozess wäre, ist es aber nicht - versuch mal zu überlegen was hier die gemeinsamkeiten sein könnten und das zu beschreiben.]
+Both the TANGO and the two applied perspective-taking tasks can be seen as instances of *visuospatial perspective-taking.* According to @surtees2013similarities, perspective-taking tasks involve three components: (1) a Self (i.e., the perspective-taker), (2) the Other (i.e., a target perspective that gets judged), and (3) an Object (which is taken into perspective).
+One can roughly categorize them into two groups.
+
+Level 1 perspective-taking, also termed visual accessibility judgment, is concerned with the visibility of objects from a particular viewpoint.
+In these tasks, participants judge whether an object is located before or behind an agent and if this agent can see it [@surtees2013similarities].
+Usually, participants can solve these tasks independently from another's agent frame of reference and do not need to apply mental rotation (not matching the "mentalizing criterion"; [@quesque2020theoryofmind]).
+
+Level 2 perspective-taking, however, does rely on a mental transformation of oneself into the space of another agent.
+In these tasks, participants judge how (visually or conceptually) the world looks like for another person or whether an object is to their right or left.
+This presumably entails a simulative transformation of one's own body schema [@erle2017grounded].
+Additionally, participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
+
+In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
+The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale.
+The two perspective-taking tasks we administered within the ToM scale fall into the second category.
+
+What drives the connection between the TANGO and the two other perspective-taking tasks?
+Both tasks tap into the ability to judge what another person sees.
+In the TANGO, participants must assume that another agent perceives and looks at the target in order to locate it.
+The here-used perspective-taking tasks add a layer by asking how one's perspective differs from another person's and how exactly the other person sees an object.
+In an intriguing series of experiments, @michelon2006two assessed the different processes that participants used to master Level 1 (visibility of objects) and Level 2 (object's location relative to another agent) perspective-taking tasks.
+Their results suggest that participants rely on line-of-sight tracing in the former case and perspective transformation in the latter case.
+According to [@michelon2006two], **line-of-sight tracing** presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
+Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
+
+Perspective transformation presumably adds complexity and consists of: "(1) locate the avatar in an egocentric space, (2) perform a perspective transformation so that one's imagined position matches the position of the avatar, (3) locate the target object in the transformed spatial representation of the scene, and (4) read off the coordinates of the object" [@michelon2006two].
+Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
+Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
+
+Why doesn't gaze understanding correlate with the other ToM tasks?
+While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
+As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be mutually incompatible, false, or involve fine-grained aspectual information.
+
+@surtees2013similarities further differentiate between visual and perspective-taking.
+While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
+Spatial perspective-taking can work without mental states and can, therefore, be applied to non-agentive objects with a front [@surtees2013similarities].
+Interestingly, computing a line of sight does not demand the presence of another agent [@michelon2006two].
+This could explain how our participants solved the non-social vector estimation task.
 
@@
 Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of dichotomous measures.
-These sum scores can only capture limited variance, which may obscure potential correlations.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous trials.
+These sum scores contan measurement errors and can only capture limited variance, which may obscure potential correlations.
 However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
@@
 We already stated this concern in the Pre-registration (<https://osf.io/xsqkt>).
+
+If the reliability of a certain task is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation; @trafimow2016attenuation].
+Adjusting for the measurement error would most likely increase the underlying correlation.
+While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task (for example, see [prein2023tango]), we do not have reliability estimates of the ToM measures.
+Therefore, applying said approaches is unfortunately not feasible to compare correlations between all our applied measures.
+This, in turn, underlines the importance of the psychometric properties of a task and the reporting of such.
+
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
-
-[TODO: die "wahren" Korrealtionen (die zwischen den latenten konstrukten) eigentloch stärker sind weil hier ja auch measurement error drin steckt.
-das kann man berechnen wenn man die reliabilität jeweils kennt.
-Die haben wir hier halt nciht für tango (außer vll split half??)]
 
@@
 
+In this paper, we have illuminated the developmental trajectory of gaze understanding and the cognitive processes behind it.
+Study 1 focussed on how gaze understanding changes with age.
+We found that individual differences exist throughout the lifespan.
+There is a steep learning curve in the preschool years in which children become more and more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reach their peak performance.
+Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+In Study 2, we proposed a computational cognitive model that describes gaze understanding at a process level.
+Our gaze model estimates reliable individual parameter values and could recover signature patterns in the data.
+It outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+Study 3 made use of the case that the TANGO is a reliable individual differences measure to further investigate potential components of gaze understanding.
+One fundamental assumption of our computational cognitive model is that gaze understanding relies on a vector estimation process.
+We experimentally isolated this component by carefully designing a non-social, physical vector estimation task.
+Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
+We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
+In addition, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
+
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy continue to develop throughout childhood.
+While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
+By studying gaze understanding on a continuum, we could move beyond the pure existence of gaze understanding and assess how precisely children locate an attentional focus.
+Our applied measure allowed us to capture fine-grained individual differences throughout the lifespan.
+In previous work, we have shown that these individual differences are meaningful variations (e.g., connected to theoretically related constructs, high split half and retest reliability; [@prein2023tango]).
+Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
+
+Preschool children increase their precision level to locate an agent's attentional focus, which then stays comparably stable across adulthood.
+Older adults decrease slightly in their precision levels.
+This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
+A crucial benefit of this study is that we could use the same experimental paradigm in all age groups.
+This considerably lifts methodological challenges when comparing performance in a given social-cognitive task across ages.
+
+In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
+Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
+We find strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig2)F).
+Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig2)E).
+The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
+The model proposes that development in gaze understanding equals an improvement in estimating the agent's pupil angles.
+
+In Study 3, we tested a modeling assumption by adopting a non-social vector estimation task.
+As suggested by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
+This ability might be helpful in several social-cognitive tasks, for example, action prediction and intention understanding.
+Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
+
+Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the real 3D world.
+The processes of understanding gaze in daily life likely rely on the same principles proposed in this paper.
+We presented the first evidence that this might be the case.
+In Study 3, we administered a Level 2 perspective-taking task in which participants needed to adapt to another person's frame of reference in a real-world interaction.
+The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.
+real-life interaction).
+
+Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+However, we can use other signals to disentangle where others are looking; for example, a body or head orientation or our common ground.
+A previously shared interaction history might restrict the options we consider potential targets.
+This might be represented in a model as a non-uniform distribution over the visual scenery.
+
+While we described the development and mechanisms behind gaze understanding, we still need to explore further the driving forces behind this development.
+As we have previously seen [@prein2023tango], precision in gaze understanding is linked to receptive vocabulary and chances for social interaction (e.g., number of siblings and age when entering childcare).
+Humans likely learn to follow gaze in social interactions.
+Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
+A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding.
+In addition, a next logical step for studying individual developments in gaze understanding would be a longitudinal data collection.
+
+In sum, this paper deepens our insight into the fundamental social-cognitive ability to understand gaze.
+In addition, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
+
 # Limitations
+
+Regarding Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
+However, it is important to note that a critical feature of the target object differs between the two tasks: in the TANGO, the target (= balloon) moves from the center of the screen to its final position in a self-propelled, continuous way.
+In the non-social vector estimation task, the target (=magnet) does not move but stays stationary on the ground.
+Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
+Second, the starting positions differ: the magnet never floats in the center of the screen.
+Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
+
+It is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
+Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
 

### 2023-09-18 paper/manuscript.Rmd
complete first draft

@@
 While the emergence of gaze following in infancy has been thoroughly studied, we know little about the developmental trajectory throughout childhood and adolescence.
-The present study examines gaze understanding across the lifespan.
-We formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way.
-The key parameter in our model is an inferential component, which describes how accurately a participant infers a target location based on the agent's gaze.
-We test a fundamental assumption of our gaze model by studying vector estimation in a non-social setting.
+In Study 1, we examine gaze understanding across the lifespan.
+In Study 2, we formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way.
+The key parameter in our model is an inferential component, which describes how accurately a participant infers a target location based on an agent's gaze.
+In Study 3, we test a fundamental assumption of our gaze model by studying vector estimation in a non-social setting.
 Lastly, we explore the relationship between other social-cognitive abilities and gaze understanding.
-We found a steep learning curve in gaze understanding during the preschool years.
-In these years, children become more precise in locating the attentional focus of an agent.
-Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+Our results suggest a steep learning curve in gaze understanding during the preschool years.
+Children become more precise in locating the attentional focus of an agent, while precision levels then stay comparably stable throughout adulthood.
 Our gaze model estimates reliable individual parameter values and recovers signature patterns in the data.
@@
 
-At first glance, the debate about infants’ gaze-following abilities seems to be settled.
+At first glance, the debate about children’s gaze following abilities seems to be settled.
 On further view, however, some methodological choices in the experimental paradigms as well as the scope of infants’ abilities seem to offer room for further exploration.
 We see the following challenges: (1) Studies focus on infancy, leaving aside further potential developments in childhood and adolescence; (2) Gaze cues are often accompanied by a head movement in the same direction, which makes it hard to isolate the signaling power of the eyes; (3) Often, infants’ looking times are taken as a benchmark for passing a task, while it is uncertain how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Behavior is grouped into passing/failing or a comparison against chance, ignoring the accuracy of children; (6) Analyses focus on group-level averages, overlooking variation in the sample.
+In the following paragraphs, we will turn to each of these arguments.
 
-Adding to the first point, while the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
+While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
 One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
@@
 Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
-We believe that the development of gaze understanding is, most likely, not complete merely because infants can differentiate between two objects, one which has been gazed at.
-In daily life, we often face more nuanced, fine-grained gaze cues and must differentiate between a virtually unlimited number of potential targets.
+The development of gaze understanding is, most likely, not complete merely because infants can differentiate between two objects, of which one has been gazed at.
 
-Let us now turn to the point that often the experimenter shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds].
+In traditional gaze following studies, the experimenter often shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds].
 Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
@@
 Results of @corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
-This underlines how important the movement of the head is when interpreting the gaze of others and that the scope of infants' gaze understanding might be less comprehensive than previously assumed.
+This underlines how important it is to differentiate between studying head and/or eye movement.
+By isolating eye movement alone, we can get a clearer understanding of infants' gaze understanding.
+This also makes it easier to understand the processes behind gaze understanding.
 
@@
 In conditions with absent-minded ‘cues’, infants performed around chance.
-The specific scope of children’s gaze understanding and whether correct looking translates into meaningful active behavior deserve further investigation.
+The specific scope of children’s gaze understanding and whether looking toward the cued location translates into meaningful active behavior deserve further investigation.
 
 Finally, presenting two objects, focusing on group-level analysis, and passing versus failing a task drastically limit the level of detail with which we can gauge children’s gaze understanding.
+In daily life, we must differentiate between a virtually unlimited number of potential targets and often face more nuanced, fine-grained gaze cues.
 Undoubtedly, children can vary in the onset of their social-cognitive abilities: these skills develop over time, with experience, and on a continuum.
@@
 In Study 3, we revisit a fundamental assumption of our computational gaze model by experimentally isolating the vector estimation component of gaze understanding.
-Furthermore, we investigate the relationship between gaze understanding and other (social-) cognitive processes.
+Furthermore, we investigate the relationship between gaze understanding and other social-cognitive processes.
 
@@
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
-They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income ~ 1,600€ as of 2021).
+They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income approx.
+1,600€ as of 2021).
 Most were raised monolingually in a nuclear two-generational family setting.
@@
 We quantified how well our gaze model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information participants use and where they consequently click to locate the target.
-Our modeling framework consisted of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+Our modeling framework consisted of three models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
 We gauged which model can best explain our data by conducting model comparisons.
@@
 When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
+As can be seen in Figure \@ref(fig:fig2)E, the gaze model could recover the U-shaped pattern that we observed our our data.
 The developmental trajectory of the estimated gaze model parameter also correlated highly with the observed data: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`].
@@
 
-Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
+Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan.
+To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
 Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
@@
 A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
+However, the children participating in our study seemed rather determined in where they wanted to click and to not have issues with aiming or motor control.
+Therefore, imprecise clicking should not be a great concern.
 
@@
 Even though this vector estimation component is a rather physical, geometrical calculation, it still happens in a social context.
-In the first place, one must interpret the agent's eyes as a relevant social stimulus.
+For example, one must interpret the agent's eyes as a relevant social stimulus.
 Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
@@
 In model comparisons, we found overwhelming support for this model in children and adults.
-Now, we wanted to test this assumption experimentally.
+Now, we wanted to further explore this assumption experimentally.
 We were interested in the degree to which vector estimation is a part of gaze understanding.
@@
 We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
-Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling] and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
+Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling], and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
 
@@
 Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
-Third, we showed the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the presented stimuli as "eye- /"agent-like".
+Third, we showed the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the presented stimuli as "eye- /agent-like".
 
@@
 We added the perspective-taking tasks (1) with the aim of increasing the variablility we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
-The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
-Additionally, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
 
@@
 
+For the ToM battery, the dependent variable was the aggregate score of all solved tasks (see Supplements for further detail).
 Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
@@
 Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+The outcome variable was modeled by a lognormal distribution.
 We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
-The outcome variable was modeled by a lognormal distribution.
+As pre-registered, we hypothesized that perspective-taking seemed most closely theoretically related to gaze understanding as in both cases the participant is asked to judge another person's point of view.
 
@@
 Both the TANGO and the two applied perspective-taking tasks can be seen as instances of *visuospatial perspective-taking.* According to @surtees2013similarities, perspective-taking tasks involve three components: (1) a Self (i.e., the perspective-taker), (2) the Other (i.e., a target perspective that gets judged), and (3) an Object (which is taken into perspective).
-One can roughly categorize them into two groups.
-
+Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
 Level 1 perspective-taking, also termed visual accessibility judgment, is concerned with the visibility of objects from a particular viewpoint.
@@
 Usually, participants can solve these tasks independently from another's agent frame of reference and do not need to apply mental rotation (not matching the "mentalizing criterion"; [@quesque2020theoryofmind]).
-
 Level 2 perspective-taking, however, does rely on a mental transformation of oneself into the space of another agent.
@@
 Additionally, participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
-
 In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
@@
 
-What drives the connection between the TANGO and the two other perspective-taking tasks?
+What could drive the connection between the TANGO and the two other perspective-taking tasks?
 Both tasks tap into the ability to judge what another person sees.
 In the TANGO, participants must assume that another agent perceives and looks at the target in order to locate it.
-The here-used perspective-taking tasks add a layer by asking how one's perspective differs from another person's and how exactly the other person sees an object.
+The here-applied Level 2 perspective-taking tasks add a layer by asking how one's perspective differs from another person's and how exactly the other person sees an object.
 In an intriguing series of experiments, @michelon2006two assessed the different processes that participants used to master Level 1 (visibility of objects) and Level 2 (object's location relative to another agent) perspective-taking tasks.
 Their results suggest that participants rely on line-of-sight tracing in the former case and perspective transformation in the latter case.
-According to [@michelon2006two], **line-of-sight tracing** presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
+According to [@michelon2006two], line-of-sight tracing presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
 Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
-
 Perspective transformation presumably adds complexity and consists of: "(1) locate the avatar in an egocentric space, (2) perform a perspective transformation so that one's imagined position matches the position of the avatar, (3) locate the target object in the transformed spatial representation of the scene, and (4) read off the coordinates of the object" [@michelon2006two].
@@
 
-Why doesn't gaze understanding correlate with the other ToM tasks?
-While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
-As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
-However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be mutually incompatible, false, or involve fine-grained aspectual information.
-
-@surtees2013similarities further differentiate between visual and perspective-taking.
+@surtees2013similarities further differentiate between visual and spatial perspective-taking.
 While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
@@
 
+Interestingly, we did not find a correlation between gaze understanding and the other ToM tasks.
+Why not?
+While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
+As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be mutually incompatible, false, or involve fine-grained aspectual information.
+
 In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2023tango].
@@
 Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous trials.
-These sum scores contan measurement errors and can only capture limited variance, which may obscure potential correlations.
+These sum scores contain measurement errors and can only capture limited variance, which may obscure potential correlations.
 However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
@@
 Adjusting for the measurement error would most likely increase the underlying correlation.
-While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task (for example, see [prein2023tango]), we do not have reliability estimates of the ToM measures.
+While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task (for example, see [@prein2023tango]), we do not have reliability estimates of the ToM measures.
 Therefore, applying said approaches is unfortunately not feasible to compare correlations between all our applied measures.
 This, in turn, underlines the importance of the psychometric properties of a task and the reporting of such.
-
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
@@
 
-The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy continue to develop throughout childhood.
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
 While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
@@
 Our applied measure allowed us to capture fine-grained individual differences throughout the lifespan.
-In previous work, we have shown that these individual differences are meaningful variations (e.g., connected to theoretically related constructs, high split half and retest reliability; [@prein2023tango]).
+In previous work, we have shown that these individual differences are meaningful variations (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
 Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
 
-Preschool children increase their precision level to locate an agent's attentional focus, which then stays comparably stable across adulthood.
-Older adults decrease slightly in their precision levels.
+Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
+Older adults decreased slightly in their precision levels.
 This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
@@
 We presented the first evidence that this might be the case.
-In Study 3, we administered a Level 2 perspective-taking task in which participants needed to adapt to another person's frame of reference in a real-world interaction.
+In Study 3, we administered a Level 2 perspective-taking task in which participants needed to adapt to another person's frame of reference in a real-world social interaction.
 The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.
@@
 
-Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+Moving away from the traditional testing setup with two objects allowed us to simulate our daily environment more closely.
+Clearly, our real-life environment is visually still more cluttered and diverse than the one presented in our tablet task.
 However, we can use other signals to disentangle where others are looking; for example, a body or head orientation or our common ground.
@@
 
-While we described the development and mechanisms behind gaze understanding, we still need to explore further the driving forces behind this development.
-As we have previously seen [@prein2023tango], precision in gaze understanding is linked to receptive vocabulary and chances for social interaction (e.g., number of siblings and age when entering childcare).
+Compared to previous gaze following studies, we applied an active response measure.
+By asking our participants to locate a target, we created a motivation and reason to follow gaze as it might be the case in real-life social interactions.
+This behavioral outcome seems well suited to study children's understanding about the intention behind gaze.
+What is more, we could show that children's ability to follow gaze toward a cued location translated into meaningful active behavior.
+
+While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
+As we have previously seen [@prein2023tango], precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
 Humans likely learn to follow gaze in social interactions.
@@
 
-In sum, this paper deepens our insight into the fundamental social-cognitive ability to understand gaze.
+In sum, this paper deepens our insights into the fundamental social-cognitive ability to understand gaze.
 In addition, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
@@
 # Limitations
+
+It is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
+Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
+
+Furthermore, the testing setup might have influences different age groups differentially.
+It is conceivable that younger children and teenagers are more trained in using a tablet.
+Potentially, the older adults in our sample were not as trained in its use.
+As mentioned in Study 1, recruiting older participants online might also select a particular subgroup of this age range.
+Seventy-year-olds who have working WIFI connections, know how to use a computer and are registered on Prolific might not be representative for their age group.
+We can imagine that results from a more diverse, in-person data collection might show differently.
+
+Our computational cognitive model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
+The model assumes no motor imprecision in this estimation.
+Clearly, it could be the case that younger children located the agent's focus at one particular point but clicked somewhere slightly off.
+This would blur the model's estimation of the inferential component.
+However, watching the children aim at the screen during data collection, we believe that inaccurate aiming was seldom the case.
 
@@
 
-It is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
-Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
+# Conclusion
 
-# Conclusion
+In three studies, we have illuminated the development and the mechanisms of gaze understanding in further detail.
+In Study 1, we saw that children's precision in localizing the attentional focus of an agent improves into the teenage years.
+Adults' level of precision stays comparatively stable, even though older participants perform slighty more imprecise.
+In addition, we found individual differences throughout the sample.
+Not all adults performed equally precise in our task.
+In Study 2, we presented a computational cognitive model of gaze understanding.
+An inferential component estimates a participant's ability to locate the attentional focus of another agent based on calculating pupil angles.
+The model can explain individual differences between participants and recovers signature patterns of our data.
+In Study 3, we explore a crucial assumption of our model: that understanding gaze relies on vector estimation.
+We designed a non-social, physical vector estimation task that closely matched the design of the gaze understanding task.
+Furthermore, we applied traditional ToM measures.
+We found that gaze understanding correlates with vector estimation, supporting our modeling assumption.
+Gaze understanding and perspective-taking also relate to one another, while the other ToM tasks did not correlate with gaze understanding.
+This proves how important it is to further think about the processes which individuals employ to solve a given task.
+While the context of all ToM measures might be similar in its social nature, the mechanisms to solve gaze understanding and false belief reasoning might vary.
+In summary, we have carefully examined gaze understanding throughout the lifespan and present a testable computational modeling framework to explain variation between individuals.
 

### 2023-09-18 paper/manuscript.tex
complete first draft

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,mask,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, cognitive modeling\newline\indent Word count: xxx}
+\keywords{social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan\newline\indent Word count: xxx max 8000}
 \usepackage{lineno}
@@
   pdftitle={Variation in gaze understanding across the life span: A process-level perspective},
-  pdfauthor={Julia Prein1, Manuel Bohn1,2, Luke Maurits1, Annika Werwach1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
-  pdfkeywords={social cognition, individual differences, gaze cues, cognitive modeling},
+  pdfkeywords={social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan},
   hidelinks,
@@
 \title{Variation in gaze understanding across the life span: A process-level perspective}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
+\author{Julia Christin Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
 \date{}
@@
 The authors made the following contributions.
-Julia Prein: Conceptualization, Methodology, Software, Investigation, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Luke Maurits: Formal Analysis, Writing - Review \& Editing; Annika Werwach: Methodology, Investigation, Writing - Review \& Editing; Daniel B.
+Julia Christin Prein: Conceptualization, Methodology, Software, Investigation, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing; Luke Maurits: Formal Analysis, Writing - Review \& Editing; Annika Werwach: Methodology, Investigation, Writing - Review \& Editing; Daniel B.
 M.
-Haun: Supervision, Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
+Haun: Supervision, Writing - Review \& Editing; Manuel Bohn: Conceptualization, Formal Analysis, Writing - Original Draft Preparation, Writing - Review \& Editing.
+
+Correspondence concerning this article should be addressed to Julia Christin Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
 E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{*} Shared senior authorship}
 
 \abstract{%
-Abstract
+Observing eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
+While the emergence of gaze following in infancy has been thoroughly studied, we know little about the developmental trajectory throughout childhood and adolescence.
+In Study 1, we examine gaze understanding across the lifespan.
+In Study 2, we formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way.
+The key parameter in our model is an inferential component, which describes how accurately a participant infers a target location based on an agent's gaze.
+In Study 3, we test a fundamental assumption of our gaze model by studying vector estimation in a non-social setting.
+Lastly, we explore the relationship between other social-cognitive abilities and gaze understanding.
+Our results suggest a steep learning curve in gaze understanding during the preschool years.
+In these years, children become more precise in locating the attentional focus of an agent.
+Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+Our gaze model estimates reliable individual parameter values and recovers signature patterns in the data.
+Furthermore, we found that gaze understanding is associated with non-social vector estimation and perspective-taking but not with other Theory of Mind tasks.
+This work illustrates how the combination of reliable tasks and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
 }
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\hypertarget{variation-in-gaze-understanding-across-the-life-span-a-process-level-perspective}{%
+\section{Variation in gaze understanding across the life span: A process-level perspective}\label{variation-in-gaze-understanding-across-the-life-span-a-process-level-perspective}}
+
+\textbf{Authors:} Julia Christin Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B.
+M.
+Haun\textsuperscript{1,*}, Manuel Bohn\textsuperscript{1,2,*}
+
+\textbf{Affiliations:} \textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany.
+\textsuperscript{*} shared senior authorship
+
+\textbf{ORCiD}: \emph{Julia Christin Prein} \url{https://orcid.org/0000-0002-3154-6167}
+
+\textbf{Conflicts of interest:} The authors declare that they have no conflict of interest.
+
+\textbf{Data availability statement:} The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
+The data sets generated during and/or analysed during the current study are available in the {[}gazecues-modeling{]} repository (\url{https://github.com/ccp-eva/gazecues-modeling}).
+All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
+
+\textbf{Acknowledgements:} We thank Jana Jurkat for her help with data collection and participant recruitment.
+We would also like to thank Steven Kalinke for his technical programming support.
+We thank all the children, caregivers, and adults who participated in the study.
+
+\textbf{Funding:} This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship.
+
+\textbf{Ethical statement:} The studies were approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+Informed consent was obtained from all individual participants or their legal guardians.
+
+\newpage
+
+\hypertarget{research-highlights-to-be-placed-before-the-abstract}{%
+\section{Research highlights (to be placed before the abstract)}\label{research-highlights-to-be-placed-before-the-abstract}}
 
@@
 \item
-  why do we care about developmental trajectory? ref to stat learning paper
+  Gaze understanding develops beyond infancy. Young adults reach the highest precision levels in localizing an attentional focus, while older adults perform slightly less precisely.
 \item
-  variation
+  We present a computational model as a mechanistic description of gaze understanding. The model explains individual differences and recovers signature patterns in the data.
+\item
+  Our model assumes that gaze understanding relies on vector estimation. To test this assumption experimentally, we designed a non-social vector estimation task.
+\item
+  We found an association between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
 \end{itemize}
 
-\hypertarget{why-do-we-need-gaze-understanding}{%
-\subsection{Why do we need gaze understanding?}\label{why-do-we-need-gaze-understanding}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
 How do humans learn about their environment and navigate through their social surroundings?
-One possibility to extract information from the environment is through following others' focus of attention.
-Building a common ground is considered especially important in communicative interactions and shared activities (Tomasello, Hare, Lehmann, \& Call, 2007).
-
-\hypertarget{how-does-gaze-following-emerge}{%
-\subsection{How does gaze following emerge?}\label{how-does-gaze-following-emerge}}
+A promising approach to extract information from the environment is through following the gaze of others.
+Recognizing the attentional focus of other agents also helps in building common ground and is vital for communicative interactions and shared activities (Tomasello, Hare, Lehmann, \& Call, 2007).
 
@@
 As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
-Infants as young as six months can attune their gaze to that of another agent (D'Entremont, Hains, \& Muir, 1997).
-At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access (Moll \& Tomasello, 2004).
+The traditional, often-used paradigm to study gaze following looks as follows (e.g., Gredebäck, Fikke, \& Melinder, 2010): The experimenter sits in front of the infant, with one object to their left and one to the right.
+The experimenter looks directly at the infant before shifting her head and eyes to one of the two objects.
+Infants' looking times or dichotomous object choices are then recorded.
+Analyses traditionally focus on the average age at which children reach an above-chance performance (i.e., looking at the gaze-cued target object).
+According to this research, infants as young as six months can attune their gaze to that of another agent (D'Entremont, Hains, \& Muir, 1997).
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access (Deák, Flom, \& Pick, 2000; Moll \& Tomasello, 2004).
+
+At first glance, the debate about children's gaze-following abilities seems to be settled.
+
+Some open questions remain, partly because of the methodological choices and the focus of previous research.
+For example, most studies focussed on infancy and focussed on the youngest age, in which children succeed.
+Often, these studies rely on two objects\ldots{}
+
+On further view, however, some methodological choices in the experimental paradigms as well as the scope of infants' abilities seem to offer room for further exploration.
+We see the following challenges: (1) Studies focus on infancy, leaving aside further potential developments in childhood and adolescence; (2) Gaze cues are often accompanied by a head movement in the same direction, which makes it hard to isolate the signaling power of the eyes; (3) Often, infants' looking times are taken as a benchmark for passing a task, while it is uncertain how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Behavior is grouped into passing/failing or a comparison against chance, ignoring the accuracy of children; (6) Analyses focus on group-level averages, overlooking variation in the sample.
+In the following paragraphs, we will turn to each of these arguments.
 
 While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
-One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.However, many cognitive abilities develop with age (e.g., working memory, Gathercole, Pickering, Ambridge, \& Wearing, 2004).
+One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
+However, many cognitive abilities develop with age (e.g., working memory, Gathercole, Pickering, Ambridge, \& Wearing, 2004).
 Similarly, visual processing appears to improve with age.
 Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
-
-\hypertarget{the-scope-of-infants-gaze-following-ability}{%
-\subsection{The scope of infants' gaze following ability}\label{the-scope-of-infants-gaze-following-ability}}
-
-Though these studies suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions of the other agent.
-Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.~Butterworth \& Jarrett's ecological and geometric mechanism, Butterworth and Jarrett (1991){]}.
-Therefore, it is crucial to study children's intentional understanding of gaze.
-
-Moore, Angelopoulos, and Bennett (1997) showed that 9-month-olds followed an agent's gaze more, when it was accompanied by a dynamic head turn in comparison to a static head turn.
-
-In a hiding game with two search locations, Povinelli, Reaux, Bierschwale, Allain, and Simon (1997) found that three-year-olds used gaze as a cue to locate the reward, while two-year-olds performed at chance level.
-
-In a similar object choice paradigm with two containers, Behne, Carpenter, and Tomasello (2005) investigated whether infants understand the communicative intent behind pointing and gaze cues.
-In contrast to Povinelli et al. (1997), they found that already 14-month-olds used the agent's cues to select an object.
-In conditions with absent-minded `cues', infants performed around chance.
-This could be interpreted as infants recognizing the nature of this joint activity: namely, that the adult's behavior was beneficial and relevant for their object choice.
-
-\hypertarget{head-vs-eye-direction}{%
-\subsubsection{Head vs eye direction}\label{head-vs-eye-direction}}
-
-It is important to note that in many existing gaze conditions, the experimenter shifted their eyes and head in synchrony (e.g., Behne et al. (2005)).
+We believe that the development of gaze understanding is, most likely, not complete merely because infants can differentiate between two objects, one which has been gazed at.
+In daily life, we often face more nuanced, fine-grained gaze cues and must differentiate between a virtually unlimited number of potential targets.
+
+In traditional gaze-following studies, the experimenter often shifts their eyes and head in synchrony (e.g., Behne, Carpenter, \& Tomasello, 2005).
 Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
-
 A handful of studies approached this potential confound by separately manipulating head and eye movement.
 Brooks and Meltzoff (2002) implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
-
+Moore, Angelopoulos, and Bennett (1997) showed that 9-month-olds followed an agent's gaze more when it was accompanied by a dynamic head turn in comparison to a static head turn.
 Investigating the `cooperative eye hypothesis', Tomasello et al.
@@
 They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
-
-Importantly, the subjects were not presented with an object choice but their attention orientation was measured.
-
-\begin{itemize}
-\item
-  (Raviv \& Arnon, 2018)
-\item
-  (Astor \& Gredebäck, 2022)
-\item
-  (Colombo, 2001)
-\item
-  (Scaife \& Bruner, 1975)
-\item
-  (Itakura \& Tanaka, 1998)
-\item
-  (Carpenter, Nagell, \& Tomasello, 1998) ``Several other studies have attempted to determine more precisely the cue that infants are using when they follow the gaze direction of others, that is, whether they use adults' head or eye orientation.
-In tasks comparing infants' responses when the experimenters turned their head and eyes together to targets with their responses when the experimenters directed their eyes to the targets but their head remained facing forward, Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) all found that only infants age 12 months and older responded correctly when eyes and head were oriented in the same direction and that infants at all ages (i.e., through 19 months) performed poorly when eye and head direction diverged'' (p.10-11) object choice.
-\item
-  (Silverstein, Feng, Westermann, Parise, \& Twomey, 2021) for vertical plane
-\item
-  (Zhang, Zhang, Zhang, Tang, \& Liu, 2019)
-\item
-  (Frischen, Bayliss, \& Tipper, 2007)
-\item
-  (Lee, Eskritt, Symons, \& Muir, 1998)
-\item
-  (Coelho, George, Conty, Hugueville, \& Tijus, 2006)
-\end{itemize}
+Results of Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
+This underlines how important the movement of the head is when interpreting the gaze of others and that the scope of infants' gaze understanding might be less comprehensive than previously assumed.
+
+Next, let us consider the classical response measure of collecting looking times.
+Though previous studies using the above-mentioned methods suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions or the content of the other agent's gaze.
+Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.~Butterworth \& Jarrett's ecological and geometric mechanism, Butterworth \& Jarrett, 1991).
+Arguably, this is not sufficient to claim an understanding of visual perspectives, because the ``target'' or ``object of representation'' is not necessarily specified (Perner, Brandl, Garnham, \& Peter Lang, 2003, p.
+358).
+To fulfill this criterion, Moll and Tomasello (2006) used an active behavioral choice as a response measure and tested infants' understanding of the intentions behind gaze.
+Infants interactively searched for the target object, which was either occluded or visually accessible.
+They found that 24-month-olds adaptively handed over the target object, while 18-month-olds still struggled to complete this task.
+In a hiding game with two search locations, Povinelli, Reaux, Bierschwale, Allain, and Simon (1997) found that two-year-olds performed at chance level when using gaze as a cue to locate the reward, while three-year-olds passed the task.
+However, in a similar object choice paradigm with two containers, Behne et al.
+(2005) investigated whether infants understand the communicative intent behind pointing and gaze cues.
+In contrast to Povinelli et al.
+(1997), they found that already 14-month-olds used the agent's cues to select an object.
+In conditions with absent-minded `cues', infants performed around chance.
+The specific scope of children's gaze understanding and whether looking toward the cued location translates into meaningful active behavior deserve further investigation.
+
+Finally, presenting two objects, focusing on group-level analysis, and passing versus failing a task drastically limit the level of detail with which we can gauge children's gaze understanding.
+Undoubtedly, children can vary in the onset of their social-cognitive abilities: these skills develop over time, with experience, and on a continuum.
+Birch et al.
+(2017) argued that individuals can differ in their frequency (or propensity) and accuracy of applying social cognition in their daily lives.
+Measuring individual differences in this domain is especially important to understand the underlying processes and to disentangle the impact of environmental influences (scaffolding) and other cognitive abilities (Birch et al., 2017).
 
@@
 
-\hypertarget{developmental-trajectory-measuring-modeling-individual-differences}{%
-\subsubsection{Developmental trajectory, measuring \& modeling individual differences}\label{developmental-trajectory-measuring-modeling-individual-differences}}
-
-In this study, we were interested in the developmental trajectory of gaze understanding.
-While we expect the younger children to be able to follow gaze, we aimed at assessing the differentiation of their social-cognitive ability.
+With our study, we aim to deepen our knowledge about the development and mechanisms behind gaze understanding.
+We study the differentiation of this social-cognitive ability by using a study design with subtle gaze cues without head rotation.
+While we expect the younger children to be able to follow gaze, we aim at assessing the differentiation of their social-cognitive ability.
 Our goal was \emph{not} to establish the youngest age at which children understand gaze cues.
-Rather, we wanted to examine how that ability changes with age.
-
+Rather, we wanted to examine \emph{how} that ability changes with age.
 In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent's gaze.
-While language demands were kept low, the participants had to actively respond and, therefore, make use of the presented gaze cue.
-
-A unique contribution of this study is the richness of the data set.
-Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
-We could circumvent these issues by applying the exact same task for the entire life span.
-
-\hypertarget{lifespan}{%
-\section{Lifespan}\label{lifespan}}
-
-\begin{itemize}
-\tightlist
-\item
-  development \& individual differences in gaze understanding
-\item
-  verweis methods paper reliable differences kinder \& adults.
-\item
-  kontinuerliche, systematische variation, wodrin? =\textgreater{} model
-\end{itemize}
-
-\url{https://osf.io/6yjz3}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:lifespan_sample}}
-
-\begin{tabular}{lllll}
-\toprule
-Age group & \multicolumn{1}{c}{n} & \multicolumn{1}{c}{Age mean} & \multicolumn{1}{c}{Age range} & \multicolumn{1}{c}{Age SD}\\
-\midrule
-3.00 & 19 (7 female) & 3.62 & 3.04 - 3.99 & 0.31\\
-4.00 & 17 (9 female) & 4.45 & 4.05 - 4.91 & 0.30\\
-5.00 & 22 (13 female) & 5.56 & 5.08 - 5.99 & 0.31\\
-6.00 & 24 (16 female) & 6.50 & 6.1 - 6.99 & 0.28\\
-7.00 & 39 (20 female) & 7.48 & 7.04 - 7.95 & 0.25\\
-8.00 & 41 (20 female) & 8.46 & 8.03 - 8.98 & 0.27\\
-9.00 & 56 (29 female) & 9.46 & 9.01 - 9.96 & 0.28\\
-10.00 & 35 (22 female) & 10.49 & 10.01 - 11 & 0.28\\
-11.00 & 54 (26 female) & 11.43 & 11.01 - 11.96 & 0.28\\
-12.00 & 43 (19 female) & 12.41 & 12.01 - 12.99 & 0.30\\
-13.00 & 42 (19 female) & 13.50 & 13.09 - 13.99 & 0.27\\
-14.00 & 20 (14 female) & 14.37 & 14.05 - 14.98 & 0.23\\
-15.00 & 21 (11 female) & 15.56 & 15.05 - 15.98 & 0.30\\
-16.00 & 19 (10 female) & 16.51 & 16.17 - 16.97 & 0.24\\
-17.00 & 19 (10 female) & 17.53 & 17.01 - 17.95 & 0.28\\
-18.00 & 2 (0 female) & 18.00 & 18 - 18 & 0.00\\
-19.00 & 5 (4 female) & 19.00 & 19 - 19 & 0.00\\
-20.00 & 40 (25 female) & 23.02 & 20 - 29 & 2.77\\
-30.00 & 40 (21 female) & 34.42 & 30 - 39 & 3.00\\
-40.00 & 40 (24 female) & 44.17 & 40 - 49 & 2.92\\
-50.00 & 40 (21 female) & 54.38 & 50 - 59 & 3.04\\
-60.00 & 40 (21 female) & 63.73 & 60 - 69 & 2.56\\
-70.00 & 40 (20 female) & 72.75 & 70 - 79 & 2.44\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+While language demands are low, participants have to actively respond and, therefore, make use of the presented gaze cue.
+By measuring a continuous, active behavior, we can capture meaningful variation between individuals.
+We strive to embrace and explain diversity in gaze understanding and use individual differences to inform what happens on a process level.
+
+The present paper is structured in the following way.
+In Study 1, we explore gaze understanding across the lifespan.
+We assess the developmental trajectory and individual differences in this fundamental social-cognitive ability in a sample of 3- to 80-year-olds.
+In Study 2, we propose a computational cognitive model of gaze understanding.
+This model helps us to explain where individuals vary and which mechanisms participants use to locate an agent's attentional focus.
+In Study 3, we revisit a fundamental assumption of our computational gaze model by experimentally isolating the vector estimation component of gaze understanding.
+Furthermore, we investigate the relationship between gaze understanding and other social-cognitive processes.
+
+\hypertarget{study-1-gaze-understanding-across-the-lifespan}{%
+\section{Study 1: Gaze understanding across the lifespan}\label{study-1-gaze-understanding-across-the-lifespan}}
+
+We aimed to assess the developmental trajectory of gaze understanding across the lifespan.
+First, we were interested in how this ability changes with age: Is the ability to understand gaze fully developed once emerged in infancy and stays stable across the lifetime?
+Or do we fine-tune our already existing ability in early adulthood?
+Do we then potentially even notice an age decay later in adulthood?
+Second, we were interested in individual differences across the age groups.
+Does the variation between individuals decrease, the older they get?
+Do all adults reach the same level of precision in gaze understanding?
+
+Due to the sheer number of participants, we restricted this analysis to a remote sample.
+Pre-registrations can be found here: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/6yjz3} (adult sample).
+The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
+The research adheres to the legal requirements of psychological research with children in Germany.
+Data was collected between May 2021 and April 2023.
 
@@
 
-We collected data from a remote child, teenager and adult sample.
-For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
-
-The remote child and teenager sample consisted of 471 participants.
-Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age (see Supplements for further details).
+The child and teenager sample consisted of 471 participants.
+We recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
+They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income approx.
+1,600€ as of 2021).
+Most were raised monolingually in a nuclear two-generational family setting.
+Information on demographics and socioeconomic status was not formally recorded on a participant level.
 
@@
 \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of 240 English-speaking adults that reported to have normal or corrected-to-normal vision.
-For further information on age and gender of participants, see Table 1.
-
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
+Participants consisted of 240 English-speaking adults who reported to have normal or corrected-to-normal vision.
+For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
 
@@
 
-We used the continuous version of the TANGO (Prein, Bohn, Kalinke, \& Haun, 2022).
-The task was presented as an interactive web application (see Figure \ref{fig:fig1}; live demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
-The TANGO showed satisfactory internal consistency and retest reliability {[}with reliability estimates \emph{Pearson's r} ranging from .7 to .8 for the continuous task version; Prein et al.
-(2022){]}.
+We used the continuous version of the TANGO (Prein, Kalinke, Haun, \& Bohn, 2023).
+The task was presented as an interactive web application (live demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
+The TANGO showed satisfactory internal consistency and retest reliability (with reliability estimates \emph{Pearson's r} ranging from .7 to .8 for the continuous task version; (Prein et al., 2023)).
 
 Each trial presented an agent standing in a window, watching a balloon (\emph{i.e.}, target) falling to the ground.
-The target then fell behind a hedge (continuous task version).
-The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
+The target fell behind a hedge while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
 In test trials, the target flight was covered so that participants could not see where the target landed.
-Participants' task was to locate the target by tracking the agent's gaze.
+Participants were tasked to locate the target by tracking the agent's gaze.
 They could respond by touching on the screen.
@@
 
-The outcome measure was imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
-Target coordinates were randomly generated during runtime.
-Each target bin, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/procedure}
-
-}
-
-\caption{\textbf{Setup of the TANGO and Magnet tasks}.
-(A) TANGO: Gaze understanding task.
-The agent stands in a window with the target in front of them.
-A hedge grows and covers the target.
-The target falls to a random location on the ground.
-The agent's eyes track the movement of the target.
-(B) Magnet task: non-social vector estimation.}\label{fig:fig1}
-\end{figure}
+The outcome measure was imprecision, defined as the absolute difference between the target (i.e., balloon) center and the x coordinate of the participant's click.
+The full screen width was divided into ten bins.
+Within each bin, exact target coordinates were randomly generated during runtime.
+Each target bin, as well as all agents and target colors, occurred equally often and did not appear in more than two consecutive trials.
 
@@
 Children and teenagers received a personalized link to the study website.
-Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
-Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.
+Caregivers were asked to provide technical support whenever needed, while explicitly being reminded not to help their children in responding.
+Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
+Adults completed the online study unsupervised.
 
@@
 
-All test trials without voice-over description were included in our analyses.
-We ran all analyses in R version 4.3.0 (2023-04-21) (R Core Team, 2022).
+We ran all analyses in R version 4.3.1 (2023-06-16) (R Core Team, 2022).
 Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
 
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed), in \texttt{R:\ imprecision\ \textasciitilde{}\ age\_centered}).
-
-Imprecision was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
-We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
+To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, or cubic.
+In addition, we applied a Gaussian Process model (Bürkner, 2017) and examined nonlinearity.
+The models predicted imprecision by age (continuous), aggregated across trials and modeled as a \texttt{lognormal} distribution.\footnote{Originally, our models were fitted on a trial-by-trial basis and implemented the following structure: \texttt{performance\ tilde\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}.
+However, the Gaussian Process model was computationally heavy.
+To circumvent issues of convergence, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+See Supplements for a comparison between the original and the here-reported model structures.
+The model predictions did not differ notably.} The unit of imprecision was counted in target widths, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+We inspected the posterior distributions (mean and 95\% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights (Vehtari, Gelman, \& Gabry, 2017).
+
+Confirming that the developmental change was non-linear, we performed a Bayesian change point analysis, using the package \texttt{RBeast} (Zhao et al., 2019).
+The function \texttt{beast.irreg} handled the irregular nature of our series, which did not have the same number of data points for each year in age.
+We were interested in finding the most prominent, most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
+To avoid ``overreactions'' to individual outlying data points, we constrained the model to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade).
+We inspected the probability of number of change points and the locations of these change points (mean and 95\% CrI).\footnote{In a supplementary analysis, we varied the parameters of our changepoint analysis.
+We modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When we allowed more explorative room (i.e., greater nr of change points, smaller minimum nr of data points between change points, higher polynomial order), the models became more sensitive and added more fine-grained change points.
+The exact location of the change points varied slightly.
+However, the overall interpretation stayed the same, fitting our initial visual inspection.
+While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
+There was a minor change in that elderly adults became slightly more imprecise again.
+See Supplements for further detail.}
 
@@
 
-\caption{\textbf{Differentiation in gaze understanding}.
+\caption{\textbf{Developmental trajectory of gaze understanding across the lifespan}.
 Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.}\label{fig:fig2}
+The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+Grey dots show the mean performance for each subject averaged across trials.
+Blue lines show 100 draws from the expectation of the posterior predictive distribution (i.e., conditional expectation) of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
+Vertical, black, dashed lines show the locations of the most prominent changes according to our Bayesian change point analysis.}\label{fig:fig1}
 \end{figure}
+
+High levels of variation pointed to individual differences in all age groups (overall imprecision mean = 0.81, sd = 0.82, range = {[}0 - 10.73{]}).
+For example, there were some children who were more accurate than the average adult.
+
+In our model comparison, we found clear evidence for a non-linear development in gaze understanding across the lifespan.
+Compared against linear, quadratic, and cubic models, the Gaussian Process model showed the best model fit, demonstrated by the greatest model weight and smallest WAIC values.
+For the imprecision in gaze understanding, the standard deviation (\emph{b} = 1.52, 95\% CrI {[}0.25; 5.19{]}) and visual inspection indicated nonlinearity (see Figure \ref{fig:fig1}).
+
+Going one step further, we investigated the most prominent change points in the data.
+The Bayesian change point analysis revealed 6 (with 23.49\% probability) major shifts in gaze understanding during the lifespan.
+The change points occurred at the following ages: 4.23 years (95\% CrI {[}4.13; 4.33{]}); 5.71 years (95\% CrI {[}5.38; 5.90{]}); 9.94 years (95\% CrI {[}8.66; 12.55{]}); 44.01 years (95\% CrI {[}40.37; 6.98 years (95\% CrI {[}6.64; 8.04{]}); 44.43{]}); and finally, at 35.97 years (95\% CrI {[}27.30; 39.69{]}).
+In other words: we found a very rapid initial improvement in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
 
@@
 
-Three-year-olds were surprisingly inaccurate in their responses.
-One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze following.
-Contrasting our results with previous findings on infant gaze following, this explanation is unlikely.
-A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
-
-Another point to keep in mind is that we used subtle eye movements as cues.
-Many existing studies let the agents move eye and head in parallel, therefore establishing a confound with greater (head) movement.
-Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
-
-The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
-
-\hypertarget{computational-cognitive-model}{%
-\section{Computational cognitive model}\label{computational-cognitive-model}}
-
-In a previous study, we have shown that the inter-individual variation in gaze understanding is reliable (Prein et al. (2022)).
-Now, we asked ourselves what varies between participants on a process-level and how this changes with age.
-To answer this question, we aimed to formalize the process of gaze understanding in a computational cognitive model.
-The model seeks to explain how participants solve the TANGO task.
-
-Computational modeling frameworks allow researcher to establish mechanistic explanations of psychological phenomena and form testable predictions (Grahek, Schaller, \& Tackett, 2021).
-As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all underlying assumptions (Simmering, Triesch, Deák, \& Spencer, 2010).
-In addition, models can be used to simulate and predict behavior as it would be expected in novel experimental manipulations.
-This can then in turn be compared to empirically observed behavior and can, for example, demonstrate assumptions of the model to be false.
-
-The model assumes that participants estimate the agent's eye center and observe the current location of the pupil center.
-These two point estimates are then used to calculate a vector that points towards the attentional focus of the agent.
-Our model assumes that participants sample from a distribution around the true gaze vector.
-Individual differences could now be explained as more narrow or wider distribution around the true gaze vector (i.e., amount of deviation).
-This could represent participants' level of uncertainty in estimating the agent's attentional focus: the wider the distribution around the true gaze vector, the less precise participants estimate the focus of attention.
-This is the key parameter in our model: this so-called inferential component describes how accurately the participant infers the attentional focus based upon the state of the agent's pupil.
-
-However, participants who are very imprecise in locating the attentional focus of the agent could be less likely to make use of the eye information in the first place.
-To accomodate this, we created an alternative model that estimates the probability that a participant engages in random guessing.
-
-With this approach, we can formalize whether (A) a participant makes use of the available gaze information at all, and (B) how accurate they are, if they do pay attention to the agent's eyes.
-We expect a dual developmental process.
-The older children get, the more likely they are to use the gaze cues and the more precise they get in doing so.
-
-The geometry of the estimated gaze vector and the sampling of a distribution around this vector lead to interesting, testable group-level predictions.
-As the pupil location varies, a fixed amount of uncertainty about the eye angle corresponds to a varying amount of uncertainty in the estimated focus of attention (i.e., the target location).
-This could be thought of as a ``headlight distribution'': when the agent's eye gaze is directed centrally to the ground in front of them, the distribution from which participants sample is comparatively more narrow then when the agent's eye gaze is directed to the side.
-A similar phenomenon can be observed when you direct a torch light straight onto the ground or when you direct it at a further distance away from you.
-It leads the model to predict that our trials vary in difficulty: participants' clicks should be more imprecise, the further out the target x coordinate is.
+We investigated the shape of change in gaze understanding across the lifespan.
+By applying the exact same task for the entire age range, we could directly compare gaze understanding in all ages.
+Therefore, we circumvented methodological challenges that often arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
+
+We found a non-linear developmental trajectory in gaze understanding: Early in childhood, children quickly enhanced their level of proficiency.
+Performance peaked (i.e., imprecision was lowest) around early adulthood, while there was a minor decay in later adulthood.
+This is consistent with the view that we fine-tune our existing gaze understanding ability after the first emergence in early childhood.
+Furthermore, we observed individual differences in all age groups.
+While variation was highest in the three- and four-year-olds, it remained relatively stable across the lifespan.
+
+Previous studies found that children start to follow gaze in the second half of their first year of life (Moll \& Tomasello, 2004).
+In our sample, three-year-olds were still rather imprecise in their gaze understanding ability.
+How can we explain this divergence?
+First of all, we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel (Behne et al., 2005; Povinelli et al., 1997), therefore establishing a confound with more salient head movement.
+Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation (Carpenter, Nagell, \& Tomasello, 1998).
+Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and then (3) make use of this cue to guide their own behavior (i.e., touching the screen at the cued location).
+We measured an active location choice instead of an attention orientation.
+It is conceivable that three-year-olds followed the agent's gaze but were still learning to translate this understanding into precise, active behavior.
+
+Regarding the sample of elderly adults, we expect a sampling bias to be present (Bethlehem, 2010; Gosling, Vazire, Srivastava, \& John, 2004; Remillard, Mazor, Cutrona, Gurwitz, \& Tjia, 2014).
+First, certainly not all older people have a working high-speed Internet connection or are knowledgeable and trained in its use.
+Second, it takes a certain amount of independence and motivation to participate in \emph{Prolific} studies.
+The elderly who know how to participate in \emph{Prolific} studies might show greater cognitive fitness and flexibility compared to their offline counterparts.
+Therefore, a representative sample might show a greater age decline in gaze understanding compared to our reported sample.
+In addition, it is noteworthy that older people might be more likely to suffer from visual impairments.
+Even though we filtered participants to only include normal- to correct-to-normal vision, we cannot guarantee that our participants showed no symptoms of reduced vision.
+
+\hypertarget{study-2-computational-cognitive-model}{%
+\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
+
+Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
+The TANGO has previously been shown to reliably capture inter-individual differences in gaze understanding (Prein et al., 2023).
+The variation between participants is thus likely genuine and not due to random noise.
+Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
+We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's gaze and its attentional focus, which leads them to identify the target position.
+We formalize this inference process in a computational cognitive model.
+
+Computational modeling frameworks allow researchers to establish mechanistic explanations of psychological phenomena (Grahek, Schaller, \& Tackett, 2021).
+As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all their underlying assumptions (Simmering, Triesch, Deák, \& Spencer, 2010).
+In addition, models can be used to simulate behavior and form testable predictions.
+The expected patterns can then, in turn, be compared to the empirically observed behavior.
+
+We seek to explain how participants solved the TANGO.
+We designed a computational cognitive model that replicates a schematic representation of how participants make inferences in the task's context (i.e., model of the task and not the data).
+The fundamental assumption of this gaze model is that participants use all available gaze information to infer the target location.
 
@@
 
-The sample included 60 children consisting of 20 three-year-olds (mean age = 3.47 years, SD = 0.34, range = 3.07 - 3.97, 11 girls), 20 four-year-olds (mean age = 4.61 years, SD = 0.26, range = 4.09 - 4.98, 10 girls), 20 five-year-olds (mean age = 5.66 years, SD = 0.24, range = 5.01 - 5.96, 12 girls), and 50 adults from our Lifespan study (mean age = 31.92 years, SD = 12.15, range = 18 - 63, 36 female).
-
+The sample consisted of 60 children, including 20 three-year-olds (mean age = 3.47 years, SD = 0.34, range = 3.07 - 3.97, 11 girls), 20 four-year-olds (mean age = 4.61 years, SD = 0.26, range = 4.09 - 4.98, 10 girls), 20 five-year-olds (mean age = 5.66 years, SD = 0.24, range = 5.01 - 5.96, 12 girls).
 Data of children was collected in kindergartens located in Leipzig, Germany.
 The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
+
+In addition, we included 50 adults from our Lifespan study (mean age = 31.92 years, SD = 12.15, range = 18 - 63, 36 female).
 Adults were recruited over \emph{Prolific} (Palan \& Schitter, 2018).
-Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults that completed the study.
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
 
@@
 
-As in the previous study, participants completed the continuous version of the TANGO (Prein et al., 2022).
+We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO (Prein et al., 2023).
 Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
@@
 
+\hypertarget{computational-model}{%
+\subsection{Computational model}\label{computational-model}}
+
+Our model quantifies a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+It is formally defined as:
+
+\begin{equation}
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
+\end{equation}
+
+where \(\theta\) is an individual's cognitive ability to locate the focus of the agent's attention, \(x_c\) is the coordinate the participant clicked, and \(\alpha_l\) and \(\alpha_r\) are the pupil angles for the left and right eye, respectively.
+The pupil angle \(\alpha\) is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see \ref{fig:fig2}A).\footnote{This model mirrors the logic of the TANGO programming code.
+In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
+We then calculate a line between these two points: this is our gaze vector (acting in the functionally same way as a pupil angle).
+Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
+Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
+This way, the agent is animated to ``look at'' the target.
+In the gaze model, we assume participants go through these steps in reverse order.}
+
+Based on our verbal task instructions, we assume that participants (1) expect the agent's looks to be directed at the target, and (2) to click on the coordinate they estimate the agent to look at.
+Consequently, we do not assume that participants' clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at).
+However, the true eye angles (\(\alpha_l\) and \(\alpha_r\)) cannot be directly observed.
+These have to be estimated based on the position of the pupils within the eyes, resulting in approximate values (\(\hat{\alpha_l}\) and \(\hat{\alpha_r}\)).
+We presume this estimation to be a noisy process.
+Thus, the development of the cognitive ability to follow gaze corresponds to a reduction in the magnitude of the noise in the estimates (i.e., an increased certainty about the pupil angles).
+
+Any clicked value of \(x_c\) implies a ``matched pair'' of the estimated pupil angles \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\), with the property that lines extended along those two angles meet at the precise location of the target.
+As a consequence, we can rewrite the likelihood function of the model above:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+The second term of the right-hand side equation above, \(P(x_c)\), is a prior over potential target locations, which we assume to be skewed towards the screen center: We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
+We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data.
+
+We estimated \(P(x_c)\) as a deviation from a hyper parameter: \(P(x_c)_i \sim \mathcal{N}(960,\sigma^{P(x_c)_j})\).
+Please note that µ = 960 specifies the center of the screen.
+To allow developmental effects in this center bias, we defined \(P(x_c)_j\) via a linear regression as a function of the participant's age (\(age_i\)): \(P(x_c)_j = \beta_0^{P(x_c)} + age_i \cdot \beta_1^{P(x_c)}\).
+Therefore, the participant-specific value for \(P(x_c)\) was constrained by the performance in the TANGO and the participant's age.
+
+The main inferential task for the participant lies in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, \(P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)\).
+For this, we assume that the pair of estimated pupil angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance \(\sigma_v\) centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+Broadly summarizing: Participants are assumed to observe the pupil locations and the center of the agent's eyes.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+Taking the angle between this vector and a line pointing vertically to the ground yields the pupil angle.
+Participants are assumed to sample from Normal distributions centered around the true pupil angle.
+They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
+
+As \(\sigma_v\) determines the level of accuracy with which the participant estimates the pupil angles, it is the component that defines \(\theta\).
+When \(\sigma_v\) is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.~When \(\sigma_v\) is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
+We expect \(\sigma_v\) to vary between individuals.
+Consequently, individuals differ in the level of precision with which they can locate the target based on observing the agent's eyes.
+
+The shape of the \(P(x_c | \alpha_l, \alpha_r, \theta)\) distribution leads to an interesting, testable group-level prediction.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
+When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them (see \ref{fig:fig2}D).
+For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
+When one points the light cone directly at the surface, the light beam is concentrated in a clearly defined, small, symmetric area.
+When one points the light cone further away from oneself (shining at an angle), the light from one half of the cone must travel further to reach the surface than the light from the other half, resulting in an asymmetric light pattern.
+As the angle increases, the light is spread over a wider area, and the surface is illuminated less evenly.
+Consequently, for the same \(\sigma_v\), the further out a target coordinate lies, the wider and less symmetric the distribution.
+This increases both the variance and the bias in a participant's estimate of the agent's attentional focus, resulting in a decreased performance in the task.
+As \(\sigma_v\) decreases and the cone narrows, the extent to which performance varies at different angles decreases.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.\footnote{In our screen-based study, this effect should decrease again towards the most outward sides.
+Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
+In these cases, the uncertainty about the pupil angle faces practically only the inner side (facing the center) of the screen, since the natural border of the screen limits where participants can click.
+In another adult sample with more trials, we could recover this pattern.
+For further elaboration, see Supplements.} If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding with testable model predictions.
+
 \hypertarget{analysis-1}{%
@@
 
-Our cognitive model attempts to explain the behavior of participants as being generated by one of two possible approaches.
-At each trial, a weighted coin toss determines whether the participant solves the task by "guessing" (sampling a clicking coordination from a uniform distribution over all possible coordinates) or by applying a gaze following model described below.
-Each participant has their own "guessing probability", determining the mixture of strategies they use.
-These per-participant parameters are modeled as having a Beta distribution over the population of participants.
-
-Our proposed gaze understanding model is a simplification of an originally three-component model, which consisted of: (1) a perceptual component, whereby the participant produces a noisy observation of the angle of each of the agent's eyes, (2) an inferential component, whereby the participant produces an estimate of the coordinate the agent is looking at based on the above noisy observations of eye angles and a model of how agents direct their eyes relative to where they are looking, and (3) a motor component, whereby the participant samples a location to click at from a distribution centered around the above estimate of where the agent is looking.
-Simulation studies suggested it was difficult to disentangle the independent noise terms from these three components and so the model was simplified to include only the inferential component
-
-In the inferential component, the participant assumes that the agent\textquotesingle s attention is focused on a single point coordinate and that the agent\textquotesingle s left and right eyes are positioned by sampling (independently for each eye) eye angles from Normal distributions centered on the unique angle such that a line subtended from the center of the agent\textquotesingle s eye through the center of its pupil will meet the attentional focal point (i.e.~the modal behavior is to direct both eyes directly toward the focal point).
-The standard deviation of these distributions (equal for each eye) is a parameter that varies per participant, with higher values increasing the expected imprecision.
-When interpreted strictly as a model of inferring attentional focus, this standard deviation corresponds to the participant\textquotesingle s assumptions about how wide an area of the agent\textquotesingle s visual field their attention occupies.
-
-Because of the geometry of the situation (where a fixed amount of uncertainty about the agent\textquotesingle s eye angle corresponds to a varying amount of uncertainty in the underlying point of attention as the eye angle varies), and because the participant integrates information from two eyes, the resulting posterior distribution (which the participant\textquotesingle s mouse click is modeled as a sample from) does not belong to a standard parametric family, but can be easily numerically approximated as part of the inference process.
-
-We will compare this model against two models which represent alternatives about how participants' responses are generated.
-The "random guessing" model simply assumes that participants ignore the agent's gaze and randomly click on the screen (cf.~coin toss, sampling a coordination from a uniform distribution over all possible coordinates).
-The "motor noise" model assumes that participants have no uncertainty about where the agent is looking but that their responses (clicks on the screen) come with a small amount of random noise (cf.~motor component of our originally proposed model).
-We will then directly compare the three models via BayesFactors computed based on the marginal log-likelihood of the data under each model.
-The models make different predictions about how participants\textquotesingle{} clicks will be distributed for different locations of the target.
-We will visualise and evaluate these differences using correlations between the model predictions and the data.
+Our goal was to describe the inferential process of gaze understanding.
+We quantified how well our gaze model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information participants use and where they consequently click to locate the target.
+Our modeling framework consisted of three mutually exclusive models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
+We gauged which model can best explain our data by conducting model comparisons.
+All cognitive models were implemented in WebPPL (Goodman \& Stuhlmüller, 2014).
+
+To gauge the plausibility of our gaze model, we implemented two models that represent alternatives about how participants solve the TANGO.
+Participants who were overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
+The alternative models, therefore, do not assume that participants made use of the gaze cue.
+The first alternative model assumed participants were randomly guessing.
+This was implemented as sampling from a uniform distribution over all possible coordinates, \(\mathcal{U}(0, 1920)\).
+The second alternative model assumed the participants always wanted to click at the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
+This was implemented as sampling from a Normal distribution, \(\mathcal{N}(960, 160^2)\), with the the center of the screen as the mean, and one target width as the standard deviation.
+
+Our three proposed models made different predictions about how participants' clicks would be distributed for different target locations.
+We visualized and evaluated these differences using correlations between the model predictions and the data.
+For this, we converted the models' posterior distributions for each participant into a single value by taking the mode (and 95\% highest density interval--HDI).
+Furthermore, we evaluated these probabilistic models based on the marginal likelihood of the data under each model.
+The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor.
+This factor quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
+It can be used to estimate how much more likely the data under one model are compared to the other.
+Bayes Factors implicitly consider model complexity (i.e., Bayesian Occam's razor): models with more parameters often have a broader prior distribution over parameters, which might weaken potential gains in predictive accuracy.
+Details on models, including code to run the models, information about priors for parameter estimation, and Markov chain Monte Carlo settings, can be found in the associated online repository.
+
+\hypertarget{todo-add-more-infos-on-priors-parameters}{%
+\subsection{{[}TODO: add more infos on priors \& parameters{]}}\label{todo-add-more-infos-on-priors-parameters}}
 
@@
 
-A big advantage of using a computational modeling framework is that it can disentangle where people's errors come from.
-Our computational model can explain what varies between precise and imprecise individuals.
-There are two sources of errors: (1) do you actually use the eye gaze information?
-and (2) how accurate are you at estimating the focus point when you do pay attention to the agent's eyes?
-This way, we can track developmental changes in gaze understanding in a more fine-tuned way.
-
-In addition, our model was able to recover ``signature patterns'' in the data.
-Both the model predictions and the actual raw data show that precision levels drop as the agent's gaze moves further away from the center.
-Future research could use this signature in the data as evidence whether diverse communities employ the same mechanism to solve the task.
+We found clear support for our gaze model, both in children as well as adults.
+The Bayes Factors we computed via the marginal likelihood of the data strongly favored our gaze model compared to the center bias model (\(logBF_{10}\) = 1,015.33) and the random guessing model (\(logBF_{10}\) = 388.98).
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: \emph{r} = 0.95, 95\%CI {[}0.90, 0.98{]}, while the correlations with the alternative models were substantially smaller (center bias model: \emph{r} = 0.77, 95\%CI {[}0.57, 0.89{]}; random guessing model: \emph{r} = 0.78, 95\%CI {[}0.58, 0.89{]}).
+The developmental trajectory of the estimated gaze model parameter also correlated highly with the observed data: \emph{r} = 0.95, 95\%CI {[}0.92, 0.97{]}.
+The age effects in Study 2 largely replicated those of Study 1.
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/gazefunnel_combined}
+{\centering \includegraphics[width=1\linewidth]{../figures/gazemodel_plot}
 
@@
 
-\caption{\textbf{Gaze funnel}}\label{fig:fig3}
+\caption{\textbf{Gaze model} (A) Visualization of the gaze model.
+Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+Taking the angle between this vector and a line pointing vertically to the ground (black dashed line) yields the pupil angle (\(\alpha\)).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle (\(\alpha\)).
+The variance around the Normal distribution (\(\sigma_v\)) is centered on the true pupil angle and expected to vary between participants.
+(B) Developmental trajectory of the estimated model parameter.
+Grey dots show individual level parameter values.
+The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
+(C) Correlation between estimated mode of the model parameter and data mean per individual, color-coded by age.
+The grey regression line with 95\% CI shows smooth conditional mean based on a linear model, with \emph{Pearson}'s correlation coefficient \emph{r}.
+(D) Geometrical features of the gaze model.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
+Top: Agent gazes centrally to the ground.
+Bottom: Agent gazes toward the side.
+The distribution around the pupil angle from which participants sample is wider compared to when the agent gazes centrally.
+The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward.
+(E) Pattern recovery.
+Imprecision in target width for each target bin by age group.
+Model predictions in blue; data in grey.
+(F) Correlation between the observed data and the predictions of the three models by target position (across age and individuals).}\label{fig:fig2}
 \end{figure}
@@
 
-\hypertarget{components-of-gaze-understanding}{%
-\section{Components of gaze understanding}\label{components-of-gaze-understanding}}
-
-Our computational cognitive model assumes that the ability to engage in vector estimation is a crucial component of mastering gaze understanding.
-In this study, we sought to experimentally isolate the physical vector estimation component.
-In addition, we inquired whether there are any other cognitive processes outside the vector estimation that constitute gaze understanding.
+Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
+Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
+We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
+By conducting model comparisons, we could rule out that participants' responses can be explained by random guessing or a center bias.
+
+In addition, we observed differences in performance depending on where the agent looks.
+The observed data showed that precision levels dropped as the agent's gaze moved further away from the center.
+Our gaze model predictions recovered this ``signature pattern'' in the data.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
+
+Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of Michelon and Zacks (2006): in their Level 1 perspective-taking visibility task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
+Additionally, targets closer to the midline were more easily traced than ones further away from the agent.
+The authors concluded that visual acuity is generally higher for locations on the vertical axis than for those on diagonal axes (cf.~``oblique effect''; (Appelle, 1972; Heeley, Buchanan-Smith, Cromwell, \& Wright, 1997; Mikellidou, Cicchini, Thompson, \& Burr, 2015)).
+Not only is our finding of increased imprecision for greater pupil angles (i.e., trials in which the target lands further out) consistent with this finding, but our gaze model poses a viable explanation for this effect.
+
+A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
+
+A critical feature of our model is that it assumes gaze understanding to rely on vector estimation.
+In other words, subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
+Even though this vector estimation component is a rather physical, geometrical calculation, it still happens in a social context.
+In the first place, one must interpret the agent's eyes as a relevant social stimulus.
+Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
+
+\hypertarget{study-3-components-of-gaze-understanding}{%
+\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
+
+We previously presented a computational cognitive model of gaze understanding.
+Our model relies on the perhaps unexpected assumption that vector estimation is a crucial component of gaze understanding.
+In model comparisons, we found overwhelming support for this model in children and adults.
+Now, we wanted to test this assumption experimentally.
+We were interested in the degree to which vector estimation is a part of gaze understanding.
+Additionally, we investigated whether there is more to gaze understanding than the physical vector estimation component.
+To answer this question, we assessed the relationship between gaze understanding and other social-cognitive abilities.
+We reasoned that gaze understanding is integral to social interaction, which is most likely learned in the social world.
+The positive link between TANGO and family-level variables like number of siblings (Prein et al., 2023) underlines this.
+Therefore, it seems reasonable to expect correlations between gaze understanding and other social-cognitive abilities.
+
+First, we aimed to experimentally isolate the vector estimation component of the TANGO.
+We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
+Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu (Wellman \& Liu, 2004) and two additional perspective-taking tasks (Flavell, Everett, Croft, \& Flavell, 1981; Flavell, Flavell, Green, \& Wilcox, 1981).
+
 We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
-
-First, we aimed to isolate the vector estimation component of the gaze understanding task.
-We designed a new non-social vector estimation task that shared all crucial design features of the gaze understanding task.
-Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu (Wellman and Liu (2004)) and two additional perspective-taking tasks (Flavell, Everett, Croft, \& Flavell, 1981; Flavell, Flavell, Green, \& Wilcox, 1981).
-
-Our reasoning was that the gaze understanding task shares task demands with the non-social vector estimation task, while it shares its social context with the ToM tasks.
-This way, we can disentangle what components comprise gaze understanding.
-
-Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/xsqkt}.
-The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
-No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
-Data were collected between February and March 2023.
+We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+This way, we aimed to disentangle what components comprise gaze understanding.
+
+Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/xsqkt}. Data were collected between February and March 2023.
 
@@
 Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
-Third, we showed the non-social vector estimation task before the gaze understanding task so that participants would not be biased to interpret the presented stimuli as ``eye- /''agent-like''.
+Third, we showed the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the presented stimuli as ``eye- /''agent-like''.
 
@@
 
-\hypertarget{theory-of-mind-task-battery}{%
-\subsubsection{Theory of Mind task battery}\label{theory-of-mind-task-battery}}
-
-We administered four tasks from the Wellman and Liu (2004) Theory of Mind scale.
+\hypertarget{tom-task-battery}{%
+\subsubsection{ToM task battery}\label{tom-task-battery}}
+
+We administered four tasks from the Wellman and Liu (2004) ToM scale.
 We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the ``cold, cognitive'' (as compared to the ``emotional'') aspects of social cognition.
 Instead, we added two perspective-taking level-2 tasks (Flavell, Everett, et al., 1981; Flavell, Flavell, et al., 1981).
-We added the perspective-taking tasks (1) with the aim of increasing the task battery's difficulty, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
+We added the perspective-taking tasks (1) with the aim of increasing the variablility we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
 The dependent variable was the aggregate score of all solved ToM tasks (see Supplements for further detail).
-In an exploratory analysis, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
+Additionally, we investigated if gaze understanding was more strongly associated with the two perspective-taking tasks compared to the other ToM tasks, as perspective-taking seems most closely theoretically related to gaze understanding (i.e., in both cases the participant is asked to judge another person's point of view).
 
@@
 
-As in the two previously reported studies, we presented children with the continuous version of the TANGO (Prein et al., 2022).
-To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (\url{https://osf.io/tdsvc})).
+As in the two previously reported studies, we presented children with the continuous version of the TANGO (Prein et al., 2023).
+To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (\url{https://osf.io/tdsvc})).
 This further highlighted the contrast (i.e., social vs.~non-social context) to the non-social vector estimation task.\footnote{In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.~human agents.
@@
 
-Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
+Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in \texttt{R:\ tango\_mean\ tilde\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
 We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
@@
 
-Taken together, this shows that the gaze understanding task recruited social-cognitive abilities beyond vector estimation.
+Taken together, this shows that the TANGO recruited social-cognitive abilities beyond vector estimation.
 Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/magnet_arrangedplot}
+{\centering \includegraphics[width=1\linewidth]{../figures/magnet_plot}
 
@@
 
-\caption{\textbf{Components of gaze understanding.} (A) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+\caption{\textbf{Components of gaze understanding.} (A) Study procedures.
+Top: TANGO (i.e., gaze understanding; social vector estimation).
+Bottom: Magnet (i.e., non-social vector estimation).
+Left hand side show screenshots of familiarization phase; right hand side show screenshots of the test phase.
+(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
 Dots show the correlation coefficients, while error bars represent 95\% CIs.
-(B) Influence of perspective-taking and physical vector estimation on gaze understanding.
-The graph show the posterior distributions for the respective predictor.
-Black dots represent means, thicker black lines 80\% CrI and thinner black lines 95\% CrI.}\label{fig:fig4}
+(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
+The graph shows the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80\% CrI and thinner black lines 95\% CrI.}\label{fig:fig3}
 \end{figure}
@@
 However, physical vector estimation alone did not suffice to explain gaze understanding.
-In addition, perspective-taking proved to be a relevant social-cognitive ability.
-
-In previous work, we could establish that the TANGO is suited as an individual differences measure (Prein et al., 2022).
+In addition, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
+
+Both the TANGO and the two applied perspective-taking tasks can be seen as instances of \emph{visuospatial perspective-taking.} According to Surtees, Apperly, and Samson (2013), perspective-taking tasks involve three components: (1) a Self (i.e., the perspective-taker), (2) the Other (i.e., a target perspective that gets judged), and (3) an Object (which is taken into perspective).
+One can roughly categorize them into two groups.
+
+Level 1 perspective-taking, also termed visual accessibility judgment, is concerned with the visibility of objects from a particular viewpoint.
+In these tasks, participants judge whether an object is located before or behind an agent and if this agent can see it (Surtees et al., 2013).
+Usually, participants can solve these tasks independently from another's agent frame of reference and do not need to apply mental rotation (not matching the ``mentalizing criterion''; (Quesque \& Rossetti, 2020)).
+
+Level 2 perspective-taking, however, does rely on a mental transformation of oneself into the space of another agent.
+In these tasks, participants judge how (visually or conceptually) the world looks like for another person or whether an object is to their right or left.
+This presumably entails a simulative transformation of one's own body schema (Erle \& Topolinski, 2017).
+Additionally, participants must understand that different viewpoints lead to different perspectives (Flavell, Everett, et al., 1981): two agents can see the same object ``in different, incompatible, fine-grained ways'' (Rakoczy, 2022).
+
+In short, Level 1 perspective-taking addresses \emph{what} an agent can see, while Level 2 perspective-taking addresses \emph{how or where} they see it (Moll \& Tomasello, 2006).
+The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale.
+The two perspective-taking tasks we administered within the ToM scale fall into the second category.
+
+What drives the connection between the TANGO and the two other perspective-taking tasks?
+Both tasks tap into the ability to judge what another person sees.
+In the TANGO, participants must assume that another agent perceives and looks at the target in order to locate it.
+The here-used perspective-taking tasks add a layer by asking how one's perspective differs from another person's and how exactly the other person sees an object.
+In an intriguing series of experiments, Michelon and Zacks (2006) assessed the different processes that participants used to master Level 1 (visibility of objects) and Level 2 (object's location relative to another agent) perspective-taking tasks.
+Their results suggest that participants rely on line-of-sight tracing in the former case and perspective transformation in the latter case.
+According to (Michelon \& Zacks, 2006), \textbf{line-of-sight tracing} presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
+Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
+
+Perspective transformation presumably adds complexity and consists of: ``(1) locate the avatar in an egocentric space, (2) perform a perspective transformation so that one's imagined position matches the position of the avatar, (3) locate the target object in the transformed spatial representation of the scene, and (4) read off the coordinates of the object'' (Michelon \& Zacks, 2006).
+Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
+Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
+
+Why doesn't gaze understanding correlate with the other ToM tasks?
+While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
+As Rakoczy (2022) reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be mutually incompatible, false, or involve fine-grained aspectual information.
+
+Surtees et al.
+(2013) further differentiate between visual and perspective-taking.
+While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
+Spatial perspective-taking can work without mental states and can, therefore, be applied to non-agentive objects with a front (Surtees et al., 2013).
+Interestingly, computing a line of sight does not demand the presence of another agent (Michelon \& Zacks, 2006).
+This could explain how our participants solved the non-social vector estimation task.
+
+In previous work, we could establish that the TANGO is suited as an individual differences measure (Prein et al., 2023).
 Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of dichotomous measures.
-These sum scores can only capture limited variance, which may obscure potential correlations.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous trials.
+These sum scores contan measurement errors and can only capture limited variance, which may obscure potential correlations.
 However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
@@
 We already stated this concern in the Pre-registration (\url{https://osf.io/xsqkt}).
+
+If the reliability of a certain task is known, one can estimate the ``true'' correlation between the latent constructs by applying an attenuation formula or structural equation models (Metsämuuronen, 2022; Trafimow, 2016, 2016).
+Adjusting for the measurement error would most likely increase the underlying correlation.
+While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task (for example, see {[}prein2023tango{]}), we do not have reliability estimates of the ToM measures.
+Therefore, applying said approaches is unfortunately not feasible to compare correlations between all our applied measures.
+This, in turn, underlines the importance of the psychometric properties of a task and the reporting of such.
+
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
@@
 
+In this paper, we have illuminated the developmental trajectory of gaze understanding and the cognitive processes behind it.
+Study 1 focussed on how gaze understanding changes with age.
+We found that individual differences exist throughout the lifespan.
+There is a steep learning curve in the preschool years in which children become more and more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reach their peak performance.
+Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+In Study 2, we proposed a computational cognitive model that describes gaze understanding at a process level.
+Our gaze model estimates reliable individual parameter values and could recover signature patterns in the data.
+It outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+Study 3 made use of the case that the TANGO is a reliable individual differences measure to further investigate potential components of gaze understanding.
+One fundamental assumption of our computational cognitive model is that gaze understanding relies on a vector estimation process.
+We experimentally isolated this component by carefully designing a non-social, physical vector estimation task.
+Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
+We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
+In addition, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
+
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
+While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
+By studying gaze understanding on a continuum, we could move beyond the pure existence of gaze understanding and assess how precisely children locate an attentional focus.
+Our applied measure allowed us to capture fine-grained individual differences throughout the lifespan.
+In previous work, we have shown that these individual differences are meaningful variations (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; (Prein et al., 2023)).
+Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
+
+Preschool children increase their precision level to locate an agent's attentional focus, which then stays comparably stable across adulthood.
+Older adults decrease slightly in their precision levels.
+This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
+A crucial benefit of this study is that we could use the same experimental paradigm in all age groups.
+This considerably lifts methodological challenges when comparing performance in a given social-cognitive task across ages.
+
+In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
+Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \ref{fig:fig2}A).
+We find strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \ref{fig:fig2}F).
+Notably, the model recovers signature patterns in the data (see Figure \ref{fig:fig2}E).
+The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
+The model proposes that development in gaze understanding equals an improvement in estimating the agent's pupil angles.
+
+In Study 3, we tested a modeling assumption by adopting a non-social vector estimation task.
+As suggested by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
+This ability might be helpful in several social-cognitive tasks, for example, action prediction and intention understanding.
+Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
+
+Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the real 3D world.
+The processes of understanding gaze in daily life likely rely on the same principles proposed in this paper.
+We presented the first evidence that this might be the case.
+In Study 3, we administered a Level 2 perspective-taking task in which participants needed to adapt to another person's frame of reference in a real-world social interaction.
+The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.~real-life interaction).
+
+Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+However, we can use other signals to disentangle where others are looking; for example, a body or head orientation or our common ground.
+A previously shared interaction history might restrict the options we consider potential targets.
+This might be represented in a model as a non-uniform distribution over the visual scenery.
+
+While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
+As we have previously seen (Prein et al., 2023), precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
+Humans likely learn to follow gaze in social interactions.
+Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
+A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding.
+In addition, a next logical step for studying individual developments in gaze understanding would be a longitudinal data collection.
+
+In sum, this paper deepens our insight into the fundamental social-cognitive ability to understand gaze.
+In addition, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
+
 \hypertarget{limitations}{%
@@
 
+It is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
+Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
+Furthermore, the testing setup might have influences different age groups differentially.
+It is conceivable that younger children and teenagers are more trained in using a tablet.
+Potentially, the older adults in our sample were not as trained in its use.
+As mentioned in Study 1, recruiting older participants online might also select a particular subgroup of this age range.
+Seventy-year-olds who have working WIFI connections, know how to use a computer and are registered on Prolific might not be representative for their age group.
+We can imagine that results from a more diverse, in-person data collection might show differently.
+
+Our computational cognitive model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
+The model assumes no motor imprecision in this estimation.
+Clearly, it could be the case that younger children located the agent's focus at one particular point but clicked somewhere slightly off.
+This would blur the model's estimation of the inferential component.
+However, watching the children aim at the screen during data collection, we believe that inaccurate aiming was seldom the case.
+
+Regarding Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
+However, it is important to note that a critical feature of the target object differs between the two tasks: in the TANGO, the target (= balloon) moves from the center of the screen to its final position in a self-propelled, continuous way.
+In the non-social vector estimation task, the target (=magnet) does not move but stays stationary on the ground.
+Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
+Second, the starting positions differ: the magnet never floats in the center of the screen.
+Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
+
 \hypertarget{conclusion}{%
@@
 
+In three studies, we have illuminated the development and the mechanisms of gaze understanding in further detail.
+In Study 1, we saw that children's precision in localizing the attentional focus of an agent improves into the teenage years.
+Adults' level of precision stays comparatively stable, even though older participants perform slighty more imprecise.
+In addition, we found individual differences throughout the sample.
+Not all adults performed equally precise in our task.
+In Study 2, we presented a computational cognitive model of gaze understanding.
+An inferential component estimates a participant's ability to locate the attentional focus of another agent.
+The model can explain individual differences between participants and recovers signature patterns of our data.
+In Study 3, we explore a crucial assumption of our model: that understanding gaze relies on vector estimation.
+We designed a non-social, physical vector estimation task that closely matched the design of the gaze understanding task.
+Furthermore, we applied traditional ToM measures.
+We found that gaze understanding correlates with vector estimation, supporting our modeling assumption.
+Gaze understanding and perspective-taking also relate to one another, while the other ToM tasks did not correlate with gaze understanding.
+This proves how important it is to further think about the processes which individuals employ to solve a given task.
+While the context of all ToM measures might be similar in its social nature, the mechanisms to solve gaze understanding and false belief reasoning might vary.
+In summary, we have carefully examined gaze understanding throughout the lifespan and present a testable computational modeling framework to explain variation between individuals.
+
 \newpage
@@
 
-\hypertarget{open-practices-statement}{%
-\subsection{Open practices statement}\label{open-practices-statement}}
-
-The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
-The data sets generated during and/or analysed during the current study are available in the {[}gazecues-modeling{]} repository (\url{https://github.com/ccp-eva/gazecues-modeling}).
-All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
-
-\hypertarget{funding}{%
-\subsection{Funding}\label{funding}}
-
-This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers, and adults who participated in the study.
-We thank Jana Jurkat for her help with data collection.
-
-\hypertarget{conflicts-of-interest}{%
-\subsection{Conflicts of interest}\label{conflicts-of-interest}}
-
-The authors declare that they have no conflict of interest.
-
-\hypertarget{consent-to-participate}{%
-\subsection{Consent to participate}\label{consent-to-participate}}
-
-Informed consent was obtained from all individual participants included in the study or their legal guardians.
-
-\hypertarget{authors-contributions}{%
-\subsection{Authors' contributions}\label{authors-contributions}}
-
-The authors made the following contributions: \#\#\# TODO
+\ldots{} can be found on the title page.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-astor2022gaze}{}}%
-Astor, K., \& Gredebäck, G.
-(2022).
-Gaze following in infancy: {Five} big questions that the field should answer.
-In \emph{Advances in {Child Development} and {Behavior}} (p.
-S0065240722000192).
-{Elsevier}.
-\url{https://doi.org/10.1016/bs.acdb.2022.04.003}
+\leavevmode\vadjust pre{\hypertarget{ref-appelle1972perception}{}}%
+Appelle, S.
+(1972).
+Perception and discrimination as a function of stimulus orientation: {The} "oblique effect" in man and animals.
+\emph{Psychological Bulletin}, \emph{78}(4), 266--278.
+\url{https://doi.org/10.1037/h0033117}
 
@@
 \url{https://doi.org/10.1111/j.1467-7687.2005.00440.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bethlehem2010selection}{}}%
+Bethlehem, J. (2010). Selection {Bias} in {Web Surveys}. \emph{International Statistical Review}, \emph{78}(2), 161--188. \url{https://doi.org/10.1111/j.1751-5823.2010.00112.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-birch2017perspectives}{}}%
+Birch, S.
+A.
+J., Li, V., Haddock, T., Ghrear, S.
+E., Brosseau-Liard, P., Baimel, A., \& Whyte, M.
+(2017).
+Perspectives on {Perspective Taking}.
+In \emph{Advances in {Child Development} and {Behavior}} (Vol.
+52, pp.
+185--226).
+{Elsevier}.
+\url{https://doi.org/10.1016/bs.acdb.2016.10.005}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-coelho2006searching}{}}%
-Coelho, E., George, N., Conty, L., Hugueville, L., \& Tijus, C.
-(2006).
-Searching for asymmetries in the detection of gaze contact versus averted gaze under different head views: A behavioural study.
-\emph{Spatial Vision}, \emph{19}(6), 529--545.
-\url{https://doi.org/10.1163/156856806779194026}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colombo2001development}{}}%
-Colombo, J. (2001). The development of visual attention in infancy. \emph{Annual Review of Psychology}, \emph{52}, 337--367. \url{https://doi.org/10.1146/annurev.psych.52.1.337}
+\leavevmode\vadjust pre{\hypertarget{ref-corkum1995development}{}}%
+Corkum, V., \& Moore, C.
+(1995).
+Development of joint visual attention in infants.
+In \emph{Joint attention: {Its} origins and role in development} (pp.
+61--83).
+{Hillsdale, NJ, US}: {Lawrence Erlbaum Associates, Inc}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-deak2000effects}{}}%
+Deák, G.
+O., Flom, R.
+A., \& Pick, A.
+D.
+(2000).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/10902702}{Effects of gesture and target on 12- and 18-month-olds' joint visual attention to objects in front of or behind them}.
+\emph{Developmental Psychology}, \emph{36}(4), 511--523.
+
 \leavevmode\vadjust pre{\hypertarget{ref-diedenhofen2015cocor}{}}%
@@
 \url{https://doi.org/10.1371/journal.pone.0121945}
+
+\leavevmode\vadjust pre{\hypertarget{ref-erle2017grounded}{}}%
+Erle, T.
+M., \& Topolinski, S.
+(2017).
+The grounded nature of psychological perspective-taking.
+\emph{Journal of Personality and Social Psychology}, \emph{112}(5), 683--695.
+\url{https://doi.org/10.1037/pspa0000081}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
-Frischen, A., Bayliss, A.
-P., \& Tipper, S.
-P.
-(2007).
-Gaze cueing of attention: {Visual} attention, social cognition, and individual differences.
-\emph{Psychological Bulletin}, \emph{133}(4), 694--724.
-\url{https://doi.org/10.1037/0033-2909.133.4.694}
-
 \leavevmode\vadjust pre{\hypertarget{ref-gathercole2004structure}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-goodman2014design}{}}%
+Goodman, N. D., \& Stuhlmüller, A. (2014). \emph{The {Design} and {Implementation} of {Probabilistic Programming Languages}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gosling2004should}{}}%
+Gosling, S.
+D., Vazire, S., Srivastava, S., \& John, O.
+P.
+(2004).
+Should {We Trust Web-Based Studies}?
+{A Comparative Analysis} of {Six Preconceptions About Internet Questionnaires}.
+\emph{American Psychologist}, \emph{59}(2), 93--104.
+\url{https://doi.org/10.1037/0003-066X.59.2.93}
+
 \leavevmode\vadjust pre{\hypertarget{ref-grahek2021anatomy}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-itakura1998use}{}}%
-Itakura, S., \& Tanaka, M.
-(1998).
-Use of experimenter-given cues during object-choice tasks by chimpanzees ({Pan} troglodytes), an orangutan ({Pongo} pygmaeus), and human infants ({Homo} sapiens).
-\emph{Journal of Comparative Psychology}, \emph{112}(2), 119--126.
-\url{https://doi.org/10.1037/0735-7036.112.2.119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lee1998children}{}}%
-Lee, K., Eskritt, M., Symons, L.
-A., \& Muir, D.
-(1998).
-Children's use of triadic eye gaze information for "mind reading".
-\emph{Developmental Psychology}, \emph{34}(3), 525--539.
-\url{https://doi.org/10.1037//0012-1649.34.3.525}
+\leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
+Gredebäck, G., Fikke, L., \& Melinder, A.
+(2010).
+The development of joint visual attention: A longitudinal study of gaze following during interactions with mothers and strangers.
+\emph{Developmental Science}, \emph{13}(6), 839--848.
+\url{https://doi.org/10.1111/j.1467-7687.2009.00945.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-heeley1997oblique}{}}%
+Heeley, D.
+W., Buchanan-Smith, H.
+M., Cromwell, J.
+A., \& Wright, J.
+S.
+(1997).
+The oblique effect in orientation acuity.
+\emph{Vision Research}, \emph{37}(2), 235--242.
+\url{https://doi.org/10.1016/S0042-6989(96)00097-1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lempers1979young}{}}%
+Lempers, J.
+D.
+(1979).
+Young {Children}'s {Production} and {Comprehension} of {Nonverbal Deictic Behaviors}.
+\emph{The Journal of Genetic Psychology}, \emph{135}(1), 93--102.
+\url{https://doi.org/10.1080/00221325.1979.10533420}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lempers1977development}{}}%
+Lempers, J.
+D., Flavell, E.
+R., \& Flavell, J.
+H.
+(1977).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/849832}{The development in very young children of tacit knowledge concerning visual perception}.
+\emph{Genetic Psychology Monographs}, \emph{95}(1), 3--53.
+
+\leavevmode\vadjust pre{\hypertarget{ref-metsamuuronen2022attenuationcorrected}{}}%
+Metsämuuronen, J. (2022). Attenuation-{Corrected Estimators} of {Reliability}. \emph{Applied Psychological Measurement}, \emph{46}(8), 720--737. \url{https://doi.org/10.1177/01466216221108131}
+
+\leavevmode\vadjust pre{\hypertarget{ref-michelon2006two}{}}%
+Michelon, P., \& Zacks, J. M. (2006). Two kinds of visual perspective taking. \emph{Perception \& Psychophysics}, \emph{68}(2), 327--337. \url{https://doi.org/10.3758/BF03193680}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mikellidou2015oblique}{}}%
+Mikellidou, K., Cicchini, G.
+M., Thompson, P.
+G., \& Burr, D.
+C.
+(2015).
+The oblique effect is both allocentric and egocentric.
+\emph{Journal of Vision}, \emph{15}(8), 24.
+\url{https://doi.org/10.1167/15.8.24}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-moll2006level}{}}%
+Moll, H., \& Tomasello, M.
+(2006).
+Level 1 perspective-taking at 24 months of age.
+\emph{British Journal of Developmental Psychology}, \emph{24}(3), 603--613.
+\url{https://doi.org/10.1348/026151005X55370}
+
 \leavevmode\vadjust pre{\hypertarget{ref-moore1997role}{}}%
@@
 \url{https://doi.org/10.1016/j.jbef.2017.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-perner2003perspective}{}}%
+Perner, J., Brandl, J.
+L., Garnham, A., \& Peter Lang.
+(2003).
+What is a {Perspective Problem}?
+{Developmental Issues} in {Belief Ascription} and {Dual Identity}.
+\emph{Facta Philosophica}, \emph{5}(2), 355--378.
+\url{https://doi.org/10.5840/factaphil20035220}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-prein2022tango}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
 Prein, J.
-C., Bohn, M., Kalinke, S., \& Haun, D.
+C., Kalinke, S., Haun, D.
 B.
-M.
-(2022).
-\emph{{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}.
-{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/vghw8}
+M., \& Bohn, M.
+(2023).
+{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-023-02159-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-quesque2020theoryofmind}{}}%
+Quesque, F., \& Rossetti, Y.
+(2020).
+What {Do Theory-of-Mind Tasks Actually Measure}?
+{Theory} and {Practice}.
+\emph{Perspectives on Psychological Science}, \emph{15}(2), 384--396.
+\url{https://doi.org/10.1177/1745691619896607}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-raviv2018developmental}{}}%
-Raviv, L., \& Arnon, I.
-(2018).
-The developmental trajectory of children's auditory and visual statistical learning abilities: Modality-based differences in the effect of age.
-\emph{Developmental Science}, \emph{21}(4), e12593.
-\url{https://doi.org/10.1111/desc.12593}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
-Scaife, M., \& Bruner, J. S. (1975). The capacity for joint visual attention in the infant. \emph{Nature}, \emph{253}(5489), 265--266. \url{https://doi.org/10.1038/253265a0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-silverstein2021infants}{}}%
-Silverstein, P., Feng, J., Westermann, G., Parise, E., \& Twomey, K.
-E.
-(2021).
-Infants {Learn} to {Follow Gaze} in {Stages}: {Evidence Confirming} a {Robotic Prediction}.
-\emph{Open Mind}, \emph{5}, 174--188.
-\url{https://doi.org/10.1162/opmi_a_00049}
+\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
+Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, \emph{1}(4), 223--235. \url{https://doi.org/10.1038/s44159-022-00037-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-remillard2014systematic}{}}%
+Remillard, M.
+L., Mazor, K.
+M., Cutrona, S.
+L., Gurwitz, J.
+H., \& Tjia, J.
+(2014).
+Systematic {Review} of the {Use} of {Online Questionnaires} of {Older Adults}.
+\emph{Journal of the American Geriatrics Society}, \emph{62}(4), 696--705.
+\url{https://doi.org/10.1111/jgs.12747}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-surtees2013similarities}{}}%
+Surtees, A., Apperly, I., \& Samson, D.
+(2013).
+Similarities and differences in visual and spatial perspective-taking processes.
+\emph{Cognition}, \emph{129}(2), 426--438.
+\url{https://doi.org/10.1016/j.cognition.2013.06.008}
+
 \leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-trafimow2016attenuation}{}}%
+Trafimow, D. (2016). The attenuation of correlation coefficients: A statistical literacy issue. \emph{Teaching Statistics}, \emph{38}(1), 25--28. \url{https://doi.org/10.1111/test.12087}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vehtari2017practicala}{}}%
+Vehtari, A., Gelman, A., \& Gabry, J.
+(2017).
+Practical {Bayesian} model evaluation using leave-one-out cross-validation and {WAIC}.
+\emph{Statistics and Computing}, \emph{27}(5), 1413--1432.
+\url{https://doi.org/10.1007/s11222-016-9696-4}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zhang2019role}{}}%
-Zhang, X., Zhang, Z., Zhang, Z., Tang, Y., \& Liu, W.
+\leavevmode\vadjust pre{\hypertarget{ref-zhao2019detecting}{}}%
+Zhao, K., Wulder, M.
+A., Hu, T., Bright, R., Wu, Q., Qin, H., \ldots{} Brown, M.
 (2019).
-The role of the motion cue in the dynamic gaze-cueing effect: {A} study of the lateralized {ERPs}.
-\emph{Neuropsychologia}, \emph{124}, 151--160.
-\url{https://doi.org/10.1016/j.neuropsychologia.2018.12.016}
+Detecting change-point, trend, and seasonality in satellite time series data to track abrupt changes and nonlinear dynamics: {A Bayesian} ensemble algorithm.
+\emph{Remote Sensing of Environment}, \emph{232}, 111181.
+\url{https://doi.org/10.1016/j.rse.2019.04.034}
 
@@
 
-\newpage
-
 \end{document}

### 2023-09-24 paper/manuscript.Rmd
incorporate Manuel's feedback

@@
   Observing eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
-While the emergence of gaze following in infancy has been thoroughly studied, we know little about the developmental trajectory throughout childhood and adolescence.
-In Study 1, we examine gaze understanding across the lifespan.
-In Study 2, we formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way.
-The key parameter in our model is an inferential component, which describes how accurately a participant infers a target location based on an agent's gaze.
-In Study 3, we test a fundamental assumption of our gaze model by studying vector estimation in a non-social setting.
-Lastly, we explore the relationship between other social-cognitive abilities and gaze understanding.
-Our results suggest a steep learning curve in gaze understanding during the preschool years.
-Children become more precise in locating the attentional focus of an agent, while precision levels then stay comparably stable throughout adulthood.
-Our gaze model estimates reliable individual parameter values and recovers signature patterns in the data.
-Furthermore, we found that gaze understanding is associated with non-social vector estimation and perspective-taking but not with other Theory of Mind tasks.
-This work illustrates how the combination of reliable tasks and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
+While the emergence of gaze following - on a group level - has been thoroughly studied, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
+In Study 1, we examine gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds from a mid-sized German city).
+We found a steep learning curve during preschool years, in which children become more precise in locating the attentional focus of an agent.
+Precision levels then stay comparably stable throughout adulthood with a minor decline toward old age.
+In Study 2, we formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way (*N* = 60 3- to 5-year-olds, 50 adults).
+According to our model, participants estimate pupil angles with varying levels of precision based on observing the pupil location within the agent's eyes.
+In Study 3, we test two implications of our gaze model, namely that gaze understanding should be related to perspective-taking abilities and vector estimation in non-social settings (*N* = 102 4- to 5-year-olds).
+We found that gaze understanding is associated with both of these abilities but not with other Theory of Mind tasks.
+This work illustrates how the combination of reliable measurement instruments and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
 keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
@@
 
--	Gaze understanding develops beyond infancy. Young adults reach the highest precision levels in localizing an attentional focus, while older adults perform slightly less precisely. 
+-	Gaze understanding develops beyond infancy. Highest precision levels in localizing attentional foci are reached in young adulthood with a slight decrease towards old age. 
 -	We present a computational model as a mechanistic description of gaze understanding. The model explains individual differences and recovers signature patterns in the data.
 -	Our model assumes that gaze understanding relies on vector estimation. To test this assumption experimentally, we designed a non-social vector estimation task. 
--	We found an association between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
+-	We found substantial correlations between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
 
 # Introduction
-How do humans learn about their environment and navigate through their social surroundings?
+How do humans learn about their environment and navigate their social surroundings?
 A promising approach to extract information from the environment is through following the gaze of others.
-Recognizing the attentional focus of other agents also helps in building common ground and is vital for communicative interactions and shared activities [@tomasello2007reliance].
+Another's eye gaze can guide us to "informational hotspots" [@meltzoff2010social, p.1] and proves helpful when learning about external objects or surroundings.
+Additionally, eye gaze can be used to identify internal states such as intentions or emotions [@corkum1998origins; @pfeiffer2013gaze], and is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@senju2008gaze; @moore2008development; @tomasello2007reliance; @meltzoff2010social; @bohn2019pervasive; @okumura2017individual; @byers-heinlein2021development; @delbianco2019developmental; @brooks2005development; @emery2000eyes; @stephenson2021gaze].
 
 Existing studies operationalize gaze following as the ability to follow another agent’s line of sight.
-As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
-The traditional, often-used paradigm to study gaze following looks as follows [e.g., @gredeback2010development]: The experimenter sits in front of the infant, with one object to their left and one to the right.
-The experimenter looks directly at the infant before shifting her head and eyes to one of the two objects.
-Infants’ looking times or dichotomous object choices are then recorded.
-Analyses traditionally focus on the average age at which children reach an above-chance performance (i.e., looking at the gaze-cued target object).
-According to this research, infants as young as six months can attune their gaze to that of another agent  [@dentremont1997demonstration].
-At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects].
+As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy [for review, see @delbianco2019developmental].
+The traditional, often-used paradigm to study gaze following looks as follows [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawaphysiological]: The experimenter sits in front of the infant, with one object to their left and one to the right.
+The experimenter looks directly at the infant before shifting their head and eyes to one of the two objects.
+Infants’ looking times to the potential targets or choices of objects are recorded as dependent variables.
+Analyses traditionally focus on the average age at which children - as a group - reach an above-chance performance (i.e., looking at the gaze-cued target object).
+Research in this tradition finds that infants as young as six months can follow their gaze to that of another agent  [@dentremont1997demonstration].
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects; @butterworth1991minds; @corkum1995development].
 
-At first glance, the debate about children’s gaze following abilities seems to be settled.
+At first glance, the debate about children’s gaze following abilities seems to be settled: at 12 months of age, children are already competent gaze followers.
 On further view, however, some methodological choices in the experimental paradigms as well as the scope of infants’ abilities seem to offer room for further exploration.
-We see the following challenges: (1) Studies focus on infancy, leaving aside further potential developments in childhood and adolescence; (2) Gaze cues are often accompanied by a head movement in the same direction, which makes it hard to isolate the signaling power of the eyes; (3) Often, infants’ looking times are taken as a benchmark for passing a task, while it is uncertain how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Behavior is grouped into passing/failing or a comparison against chance, ignoring the accuracy of children; (6) Analyses focus on group-level averages, overlooking variation in the sample.
-In the following paragraphs, we will turn to each of these arguments.
+We see the following challenges: (1) Studies focus on infancy, leaving aside further development in childhood, adolescence and adulthood; (2) Gaze cues are often accompanied by head movements in the same direction [see @delbianco2019developmental], which makes it hard to isolate the referential information extracted from the eyes; (3) Infants’ looking times are usually used as the dependent variable and it is unclear if and how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Analyses focus on group-level averages, and we overlook variation in the sample because we cannot measure it with dichotomous outcome variables.
+In the following paragraphs, we will turn to each of these arguments and point out gaps in our understanding of the development of gaze following.
 
-While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
-One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
-However, many cognitive abilities develop with age [e.g., working memory, @gathercole2004structure].
+First, while the emergence of gaze following has been well established, less is known about the developmental trajectory beyond infancy.
+One possibility is that the ability to follow gaze does not improve further once it emerges.
+Yet, most - if not all - cognitive abilities develop throughout childhood [e.g., working memory, @gathercole2004structure].
 Similarly, visual processing appears to improve with age.
-Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
-The development of gaze understanding is, most likely, not complete merely because infants can differentiate between two objects, of which one has been gazed at.
+First longitudinal evidence points to a development in the infant's individual joint attention accuracy and latency [@gredeback2010development].
+It seems likely that children fine-tune the performance of the already existing skills - presumably while using them in social interactions.
+To capture further development in gaze understanding, we therefore conduct our study across the lifespan.
 
-In traditional gaze following studies, the experimenter often shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds].
-Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
+Second, we see in traditional gaze following studies that the experimenter often shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds; @okumura2017individual] so that children's gaze following could be interpreted as following face direction alone.
 A handful of studies approached this potential confound by separately manipulating head and eye movement.
-@brooks2002importance implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
-@moore1997role showed that 9-month-olds followed an agent’s gaze more when it was accompanied by a dynamic head turn in comparison to a static head turn.
-Investigating the 'cooperative eye hypothesis', @tomasello2007reliance implemented six conditions, in which an experimenter oriented towards the ceiling with their eyes only, head only (eyes closed), both head and eyes, or neither.
-They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
+@michel2021effects found that gaze following in four-month-olds was likely driven by another's head instead of their eye movement.
+@brooks2002importance implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes [see also @moore1997role].
 Results of @corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
-This underlines how important it is to differentiate between studying head and/or eye movement.
-By isolating eye movement alone, we can get a clearer understanding of infants' gaze understanding.
-This also makes it easier to understand the processes behind gaze understanding.
+From farther distance, body or face orientation can act as more salient cues to determine another's area of attention.
+However, eye direction can indicate a more precise location of focus [@emery2000eyes], and allows us to anticipate likely future actions [@zohary2022gaze; @friesen2011gaze].
+Clearly, it is important to differentiate between head and gaze following.
+In this study, we focus on subtle gaze cues and isolate eye movement alone.
 
-Next, let us consider the classical response measure of collecting looking times.
-Though previous studies using the above-mentioned methods suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the content of the other agent’s gaze.
-Infants could simply attune their orientation or be attracted by others’ gaze without processing what exactly the other is seeing [cf.
+Third, let us consider the classical response measure of collecting looking times.
+Though previous studies suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the focus of the agent.
+Infants could simply align their orientation without processing what exactly the other is seeing [cf.
 Butterworth & Jarrett's ecological and geometric mechanism, @butterworth1991minds].
-Arguably, this is not sufficient to claim an understanding of visual perspectives, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
+In fact, one might ask if such an alignment reflects understanding of visual perspectives at all, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
 358].
-To fulfill this criterion, @moll2006level used an active behavioral choice as a response measure and tested infants' understanding of the intentions behind gaze.
-Infants interactively searched for the target object, which was either occluded or visually accessible.
-They found that 24-month-olds adaptively handed over the target object, while 18-month-olds still struggled to complete this task.
-In a hiding game with two search locations, @povinelli1997exploitation found that two-year-olds performed at chance level when using gaze as a cue to locate the reward, while three-year-olds passed the task.
-However, in a similar object choice paradigm with two containers, @behne2005oneyearolds investigated whether infants understand the communicative intent behind pointing and gaze cues.
-In contrast to @povinelli1997exploitation, they found that already 14-month-olds used the agent’s cues to select an object.
-In conditions with absent-minded ‘cues’, infants performed around chance.
-The specific scope of children’s gaze understanding and whether looking toward the cued location translates into meaningful active behavior deserve further investigation.
+To fulfill this criterion, @moll2006level used an active behavioral choice as a response measure.
+Participants had to search for the target object, which was either visually accessible or behind a barrier.
+24-month-olds succeeded in the task, while 18-month-olds did not.
+In an object choice study with two containers, @behne2005oneyearolds found that already 14-month-olds used an experimenter's gaze; however, this was again confounded with a congruent face movement [cf.
+@povinelli1997exploitation].
+In this paper, we assess how subtle gaze cues guide participants' behavior in actively locating a target.
 
-Finally, presenting two objects, focusing on group-level analysis, and passing versus failing a task drastically limit the level of detail with which we can gauge children’s gaze understanding.
-In daily life, we must differentiate between a virtually unlimited number of potential targets and often face more nuanced, fine-grained gaze cues.
-Undoubtedly, children can vary in the onset of their social-cognitive abilities: these skills develop over time, with experience, and on a continuum.
-@birch2017perspectives argued that individuals can differ in their frequency (or propensity) and accuracy of applying social cognition in their daily lives.
-Measuring individual differences in this domain is especially important to understand the underlying processes and to disentangle the impact of environmental influences (scaffolding) and other cognitive abilities [@birch2017perspectives].
+Finally, presenting two objects and focusing on group-level analyses masks individual differences between children in their gaze following abilities.
+Measuring individual differences in basic aspects of social cognition is especially important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
+In this study, we measure participants' gaze understanding continuously by using a task which is designed to capture individual-level variation [@prein2023tango].
 
-## Aim of the current project
+## The current study
 
-With our study, we aim to deepen our knowledge about the development and mechanisms behind gaze understanding.
-We study the differentiation of this social-cognitive ability by using a study design with subtle gaze cues without head rotation.
-While we expect the younger children to be able to follow gaze, we aim at assessing the differentiation of their social-cognitive ability.
-Our goal was *not* to establish the youngest age at which children understand gaze cues.
-Rather, we wanted to examine *how* that ability changes with age.
-In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent’s gaze.
-While language demands are low, participants have to actively respond and, therefore, make use of the presented gaze cue.
-By measuring a continuous, active behavior, we can capture meaningful variation between individuals.
-We strive to embrace and explain diversity in gaze understanding and use individual differences to inform what happens on a process level.
-
-The present paper is structured in the following way.
-In Study 1, we explore gaze understanding across the lifespan.
-We assess the developmental trajectory and individual differences in this fundamental social-cognitive ability in a sample of 3- to 80-year-olds.
-In Study 2, we propose a computational cognitive model of gaze understanding.
-This model helps us to explain where individuals vary and which mechanisms participants use to locate an agent’s attentional focus.
-In Study 3, we revisit a fundamental assumption of our computational gaze model by experimentally isolating the vector estimation component of gaze understanding.
-Furthermore, we investigate the relationship between gaze understanding and other social-cognitive processes.
+The present study has two main goals: first, we study the development of gaze understanding beyond infancy on a group level (Study 1).
+Our goal was not to establish the youngest age at which children understand gaze cues.
+Rather, we wanted to examine how this ability changes with age.
+Even though we find expected developmental patterns - rapid improvement in early childhood; some decline toward old age - we observed substantial variation between individuals at all ages.
+Our second goal is to provide a substantive process-level theory of gaze understanding (and individual differences therein) in the form of a computational model.
+We formalize gaze understanding as a form of vector estimation and show that our model explains empirical data (Study 2).
+Furthermore, we test two empirical predictions that follow from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
 
@@
 We aimed to assess the developmental trajectory of gaze understanding across the lifespan.
-First, we were interested in how this ability changes with age: Is the ability to understand gaze fully developed once emerged in infancy and stays stable across the lifetime?
-Or do we fine-tune our already existing ability in early adulthood?
-Do we then potentially even notice an age decay later in adulthood?
-Second, we were interested in individual differences across the age groups.
-Does the variation between individuals decrease, the older they get?
-Do all adults reach the same level of precision in gaze understanding?
-
-Due to the sheer number of participants, we restricted this analysis to a remote sample.
-Pre-registrations can be found here: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
+The study was pre-registered at: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
 The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
@@
 
-We collected data from a remote child, teenager and adult sample, reaching from 3 to 80 years of age (see Supplements for further details).
-The child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants.
-We recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+We collected data online from participants between 3 to 80 years of age (see Supplements for further details).
+The child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants and were recruited via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
@@
 The task was presented as an interactive web application (live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability (with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; [@prein2023tango]).
+The TANGO showed satisfactory internal consistency and retest reliability for both children and adults (with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; [@prein2023tango]).
 
-Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground.
+Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground (see Figure \@ref(fig:fig4)A; however, please note that Study 1 presented animal agents).
 The target fell behind a hedge while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
@@
 Participants were tasked to locate the target by tracking the agent's gaze.
-They could respond by touching on the screen.
+They could respond by touching or clicking the screen.
 
@@
 In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
-The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target widths, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in widths, i.e., a participant with an imprecision of 1 clicked on average one balloon width to the left or right of the true target center.
 We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights [@vehtari2017practicala].
@@
 However, the Gaussian Process model was computationally heavy.
-To circumvent issues of convergence, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+Thus, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
 See Supplements for a comparison between the original and the here-reported model structures.
@@
 
-Confirming that the developmental change was non-linear, we performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
+After finding that the developmental change was best described by the Gaussian process model, we performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
 The function `beast.irreg` handled the irregular nature of our series, which did not have the same number of data points for each year in age.
@@
 lifespan_beast <- readRDS("../saves/lifespan_ibeast.rds")
-lifespan_cps <- readRDS("../saves/lifespan_ibeast_cps.rds") %>% round(2)
+lifespan_cps <- readRDS("../saves/lifespan_ibeast_cps.rds") %>% round(2) %>% arrange(cp)
 
@@
 
-High levels of variation pointed to individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
-For example, there were some children who were more accurate than the average adult.
+High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
+For example, there were some children who were more accurate than the average adult (see Figure \@ref(fig:fig1)).
 
@@
 The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` (with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability) major shifts in gaze understanding during the lifespan.
-The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[5]` years (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]); `r lifespan_cps$upperCrI[5]`]); and finally, at `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
-In other words: we found a very rapid initial improvement in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward the eldest in our sample.
+The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]);
+`r lifespan_cps$cp[5]` years (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`]);
+and finally, at `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
+In other words: we found a very rapid initial improvement in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision towards old age.
 
@@
 We investigated the shape of change in gaze understanding across the lifespan.
-By applying the exact same task for the entire age range, we could directly compare gaze understanding in all ages.
-Therefore, we circumvented methodological challenges that often arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
-
+One of the major strengths of our study was that we used the same task for all age groups.
+This allowed us to quantitatively compare performance across ages and directly model performance in relation to age.
 We found a non-linear developmental trajectory in gaze understanding: Early in childhood, children quickly enhanced their level of proficiency.
@@
 
-Previous studies found that children start to follow gaze in the second half of their first year of life [@moll200412].
+Previous studies found that children start to follow gaze in the second half of their first year of life [e.g., @moll200412].
 In our sample, three-year-olds were still rather imprecise in their gaze understanding ability.
@@
 Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation [@carpenter1998social].
+@silverstein2021infants used a similar manipulation of subtle gaze cues without head rotation.
+Interestingly, they found that infants (6- to 18-month-olds) were around or just above chance for gaze following.
+The authors argue that this might be because infants fixate on another's face most of the time, while eye movement alone might not be strong enough to guide their attention.
 Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and then (3) make use of this cue to guide their own behavior (i.e., touching the screen at the cued location).
@@
 It is conceivable that three-year-olds followed the agent's gaze but were still learning to translate this understanding into precise, active behavior.
+@moll2013primacy also argue that social forms of perspective-taking evolve prior to visual perspective-taking, which only emerges within the third year of life.
+Children might not be interested in a differential, spatial representation of the surrounding objects: "What is of primary importance to children is to share the world of those around them.
+Precisely how this shared world presents itself from one specific vantage point is secondary and does not become thematic in the very early stages" (p.
+6).
+Taken together, this might explain why some of our younger participants located the agent's gaze rather imprecisely.
 
@@
 The variation between participants is thus likely genuine and not due to random noise.
-Now, we aim to understand what explains the developmental change and the variation across participants on a process level.
-We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's gaze and its attentional focus, which leads them to identify the target position.
+Now, we aim to understand developmental change and variation across participants on a process level.
+We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's line of sight and its attentional focus, which leads them to identify the target position.
 We formalize this inference process in a computational cognitive model.
@@
 The expected patterns can then, in turn, be compared to the empirically observed behavior.
+@moore2008development have already argued for systematic, empirical approaches in combination with formal modeling to arrive at a deeper understanding of gaze following.
 
-We seek to explain how participants solved the TANGO.
+Here, we seek to explain how participants solved the TANGO.
 We designed a computational cognitive model that replicates a schematic representation of how participants make inferences in the task's context (i.e., model of the task and not the data).
-The fundamental assumption of this gaze model is that participants use all available gaze information to infer the target location.
+The fundamental assumption of this gaze model is that participants use the available gaze information to infer the target location.
 
 Task design, data collection, and sample sizes were pre-registered: <https://osf.io/r3bhn>.
-The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
-No.
-2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
+The study design and procedure obtained ethical clearance in the same way as Study 1.
 Data were collected between May and August 2021.
 
-```{r gazemodel_sample}
-gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
+## Computational model
+
+(ref:figlab2) **Gaze model** (A) Visualization of the gaze model.
+Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+Taking the angle between this vector and a line pointing vertically to the ground (black dashed line) yields the pupil angle ($\alpha$).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle ($\alpha$).
+The variance around the Normal distribution ($\sigma_v$) is centered on the true pupil angle and expected to vary between participants.
+(B & C) Geometrical features of the gaze model.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
+The distribution around the pupil angle from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
+The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward (C).
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/gazemodel.png")
 ```
-
-## Participants
-
-The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
-Data of children was collected in kindergartens located in Leipzig, Germany.
-The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
-
-In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
-Adults were recruited over *Prolific* [@palan2018prolific].
-Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
-
-## Procedure
-
-We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2023tango].
-Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
-Adults participated online.
-
-## Computational model
 
@@
 where $\theta$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
-The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see \@ref(fig:fig2)A).[^3]
+The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \@ref(fig:fig2)A).[^3]
 
@@
 Consequently, we do not assume that participants' clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at).
-However, the true eye angles ($\alpha_l$ and $\alpha_r$) cannot be directly observed.
-These have to be estimated based on the position of the pupils within the eyes, resulting in approximate values ($\hat{\alpha_l}$ and $\hat{\alpha_r}$).
+
+The true eye angles ($\alpha_l$ and $\alpha_r$) cannot be directly observed and have to be estimated based on the position of the pupils within the eyes, resulting in approximate values ($\hat{\alpha_l}$ and $\hat{\alpha_r}$).
 We presume this estimation to be a noisy process.
-Thus, the development of the cognitive ability to follow gaze corresponds to a reduction in the magnitude of the noise in the estimates (i.e., an increased certainty about the pupil angles).
+Thus, we conceptualize the development of the cognitive ability to follow gaze as a reduction of noise in the estimates (i.e., an increased certainty about the pupil angles).
 
@@
 The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assume to be skewed towards the screen center: We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
-We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data.
+We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
 
-We estimated $P(x_c)$ as a deviation from a hyper parameter: $P(x_c)_i \sim \mathcal{N}(960,\sigma^{P(x_c)_j})$.
-Please note that µ = 960 specifies the center of the screen.
-To allow developmental effects in this center bias, we defined $P(x_c)_j$ via a linear regression as a function of the participant's age ($age_i$): $P(x_c)_j = \beta_0^{P(x_c)} + age_i \cdot \beta_1^{P(x_c)}$.
+The width of this distribution is defined by $\sigma^p$.
+We assumed that the center bias changes with age and we therefore estimated $\sigma^p$ via a linear regression as a function of the participant's age ($age_i$): $\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}$.
 Therefore, the participant-specific value for $P(x_c)$ was constrained by the performance in the TANGO and the participant's age.
@@
 The main inferential task for the participant lies in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
-For this, we assume that the pair of estimated pupil angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance $\sigma_v$ centered on the true pupil angles:
+For this, we assume that the pair of estimated pupil angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
 
@@
 
-The shape of the $P(x_c | \alpha_l, \alpha_r, \theta)$ distribution leads to an interesting, testable group-level prediction.
-As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
-When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them (see \@ref(fig:fig2)D).
+The shape of the $P(x_c | \alpha_l, \alpha_r, \theta)$ distribution leads to a testable group-level prediction.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location (see Figure \@ref(fig:fig2)B & C).
+When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
 For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
@@
 As $\sigma_v$ decreases and the cone narrows, the extent to which performance varies at different angles decreases.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
-Therefore, our gaze model provides a quantitative theory of gaze understanding with testable model predictions.
+Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding with testable predictions.
+In the following, we test these predictions in children and adults.
 
@@
 
+## Participants
+
+```{r gazemodel_sample}
+gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
+```
+
+The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
+Data of children was collected in kindergartens located in Leipzig, Germany.
+The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
+
+In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
+Adults were recruited over *Prolific* [@palan2018prolific].
+Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
+
+## Procedure
+
+We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2023tango].
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
+
 ## Analysis
@@
 Our goal was to describe the inferential process of gaze understanding.
-We quantified how well our gaze model explained the gaze understanding process by comparing it to two alternative models that make different assumptions of which information participants use and where they consequently click to locate the target.
-Our modeling framework consisted of three models: (1) a gaze model, (2) a random guessing model, and (3) a center bias model.
-We gauged which model can best explain our data by conducting model comparisons.
+We quantified how well our gaze model explained the gaze understanding process in two ways.
+First, we used correlations to quantify how well the gaze model is able to recover the data.
+For this, we aggregated the model predictions and the data for each target bin and age group (3-, 4-, 5-years-olds), and computed the coorrelation between predictions and the data.
+Second, we compared the predictions of our gaze model to two - very simple - alternative models that assume that participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
+The random guessing model assumed that participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
+The center bias model assumed that participants always click at the screen center and was implemented as sampling from a Normal distribution with the the center of the screen as the mean, and one balloon width as the standard deviation, $\mathcal{N}(960, 160^2)$.
+Note that the center bias model also predicts that imprecision should be higher for targets further out on the screen, resulting also in a U-shaped pattern.
+However, the shape of this pattern is different from that of the gaze model [TODO: in what way?!].
 All cognitive models were implemented in WebPPL [@goodman2014design].
 
-To gauge the plausibility of our gaze model, we implemented two models that represent alternatives about how participants solve the TANGO.
-Participants who were overall very imprecise in locating the target might be less likely to use the agent's gaze as a cue at all.
-The alternative models, therefore, do not assume that participants made use of the gaze cue.
-The first alternative model assumed participants were randomly guessing.
-This was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
-The second alternative model assumed the participants always wanted to click at the screen center: Participants could be drawn toward the screen center since the agent and the starting point of the balloon were located there.
-This was implemented as sampling from a Normal distribution, $\mathcal{N}(960, 160^2)$, with the the center of the screen as the mean, and one target width as the standard deviation.
-
-Our three proposed models made different predictions about how participants' clicks would be distributed for different target locations.
-We visualized and evaluated these differences using correlations between the model predictions and the data.
-For this, we converted the models' posterior distributions for each participant into a single value by taking the mode (and 95% highest density interval--HDI).
-Furthermore, we evaluated these probabilistic models based on the marginal likelihood of the data under each model.
+We compared models via the marginal likelihood of the data under each model.
 The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor.
@@
 It can be used to estimate how much more likely the data under one model are compared to the other.
-Bayes Factors implicitly consider model complexity (i.e., Bayesian Occam's razor): models with more parameters often have a broader prior distribution over parameters, which might weaken potential gains in predictive accuracy.
+Bayes Factors implicitly consider model complexity (i.e., Bayesian Occam's razor): models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
 Details on models, including code to run the models, information about priors for parameter estimation, and Markov chain Monte Carlo settings, can be found in the associated online repository.
-
-## [TODO: add more infos on priors & parameters]
 
@@
 We found clear support for our gaze model, both in children as well as adults.
-The Bayes Factors we computed via the marginal likelihood of the data strongly favored our gaze model compared to the center bias model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_center`) and the random guessing model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_guess`).
-When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
-As can be seen in Figure \@ref(fig:fig2)E, the gaze model could recover the U-shaped pattern that we observed our our data.
-The developmental trajectory of the estimated gaze model parameter also correlated highly with the observed data: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`].
+When correlating the observed data across all target posions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
+The model comparison strongly favored our gaze model over the center bias model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_center`) and the random guessing model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_guess`).
+As can be seen in Figure \@ref(fig:fig3)C, the gaze model predicts a U-shaped pattern which we also observed in our data.
+A strong correlation between the data mean and the gaze model estimate ($\sigma_v$), *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`],  showed that the data mean is suitable to quantify individual differences.
 The age effects in Study 2 largely replicated those of Study 1.
+When comparing performance of the three- to five-year-olds in Study 1 and 2, we see a rapid improvement in gaze understanding in early childhood (see Figure \@ref(fig:fig1) inset and \@ref(fig:fig3)A).
 
-(ref:figlab2) **Gaze model** (A) Visualization of the gaze model.
-Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
-Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-Taking the angle between this vector and a line pointing vertically to the ground (black dashed line) yields the pupil angle ($\alpha$).
-Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle ($\alpha$).
-The variance around the Normal distribution ($\sigma_v$) is centered on the true pupil angle and expected to vary between participants.
-(B) Developmental trajectory of the estimated model parameter.
+(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
 Grey dots show individual level parameter values.
 The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
-(C) Correlation between estimated mode of the model parameter and data mean per individual, color-coded by age.
+(B) Correlation between estimated mode of the model parameter and data mean per individual, color-coded by age.
 The grey regression line with 95% CI shows smooth conditional mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
-(D) Geometrical features of the gaze model.
-As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
-Top: Agent gazes centrally to the ground.
-Bottom: Agent gazes toward the side.
-The distribution around the pupil angle from which participants sample is wider compared to when the agent gazes centrally.
-The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward.
-(E) Pattern recovery.
+(C) Pattern recovery.
 Imprecision in target width for each target bin by age group.
 Model predictions in blue; data in grey.
-(F) Correlation between the observed data and the predictions of the three models by target position (across age and individuals).
+(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals).
 
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
 knitr::include_graphics("../figures/gazemodel_plot.png")
@@
 To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
-Participants are modeled to observe all available gaze information, integrate it from both the agent's eyes, and consequently arrive at the attentional focus of the agent: the target location.
+
+We modeled gaze understanding as a process in which participants estimate pupil angles based on the pupil location within the eye.
+By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent: the target location.
+Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
 We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
-By conducting model comparisons, we could rule out that participants' responses can be explained by random guessing or a center bias.
+By conducting model comparisons, we ruled out simpler explanations of the data.
 
@@
 A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
-However, the children participating in our study seemed rather determined in where they wanted to click and to not have issues with aiming or motor control.
+However, the children participating in our study seemed rather determined in where they wanted to click and to not have issues with aiming or motor control (see precision in training trials).
 Therefore, imprecise clicking should not be a great concern.
@@
 Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
+In the next study, we test this prediction.
 
@@
 
-We previously presented a computational cognitive model of gaze understanding.
-Our model relies on the perhaps unexpected assumption that vector estimation is a crucial component of gaze understanding.
-In model comparisons, we found overwhelming support for this model in children and adults.
-Now, we wanted to further explore this assumption experimentally.
-We were interested in the degree to which vector estimation is a part of gaze understanding.
+Study 3 examined the degree to which vector estimation is a part of gaze understanding.
 Additionally, we investigated whether there is more to gaze understanding than the physical vector estimation component.
 To answer this question, we assessed the relationship between gaze understanding and other social-cognitive abilities.
-We reasoned that gaze understanding is integral to social interaction, which is most likely learned in the social world.
-The positive link between TANGO and family-level variables like number of siblings [@prein2023tango] underlines this.
-Therefore, it seems reasonable to expect correlations between gaze understanding and other social-cognitive abilities.
+We reasoned that gaze understanding is integral to social interaction.
+The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underlines this.
+Therefore, it seems reasonable to expect correlations between gaze understanding and other measures of social-cognitive abilities.
 
@@
 Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling], and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
-
 We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
 We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze understanding.
+Our reasoning was that similar underlying mechanisms might be needed to solve these tasks, since they ask participants to take into account another person's point of view.
 This way, we aimed to disentangle what components comprise gaze understanding.
@@
 
+Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
+Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
+In the experimental design process, we decided against using an arrow (or, similarly, a stick or shooting star): we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
+In both cases, the starting point of the vector needs to be estimated by the participant.
+In the case of an arrow, we would have drastically reduced the level of uncertainty and the participants would not have needed to estimate the vector anymore, since the arrow already fully displays all information (with the arrow end as the starting point and arrow tip as the "gaze" direction).
+Furthermore, we wanted to avoid any referential or iconic stimuli.
+
 Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
@@
 Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga].
-We added the perspective-taking tasks (1) with the aim of increasing the variablility we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding.
+We added the perspective-taking tasks (1) with the aim of increasing the variability we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding; both relying on another's person frame of reference.
 
@@
 By design, both the TANGO as well as the non-social vector estimation task involve vector estimation.
-On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks correlate with each other.
+On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks would correlate with each other.
 For each of these two tasks, we calculated the mean level of imprecision for each subject.
@@
 
-As expected, we found that gaze understanding as a social vector estimation task correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`].
-Importantly, however, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
+As expected, we found that gaze understanding as a social vector estimation task substantially correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
+Importantly, however, and despite the designed overlap in task demands, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
 
-Gaze understanding and perspective-taking showed a *Spearman* correlation coefficient of $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`], while non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
-According to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
+Gaze understanding and perspective-taking correlated substantially, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
+Please note that the negative correlation can be explained by our outcome measure of imprecision in the TANGO (i.e., the more imprecise gaze understanding, the less perspective-taking).
+Non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+However, according to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
 
-Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]).
+Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]) (see Figure \@ref(fig:fig4)C).
 See Supplements for further detail of the model comparison.
 
-Taken together, this shows that the TANGO recruited social-cognitive abilities beyond vector estimation.
-Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
-
-(ref:figlab3) **Components of gaze understanding.** (A) Study procedures.
+(ref:figlab4) **Components of gaze understanding.** (A) Study procedures.
 Top: TANGO (i.e., gaze understanding; social vector estimation).
@@
 
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
 knitr::include_graphics("../figures/magnet_plot.png")
@@
 ## Discussion
+
+Taken together, the results suggest shows that the TANGO recruited social-cognitive abilities beyond vector estimation.
+Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
 
@@
 Their results suggest that participants rely on line-of-sight tracing in the former case and perspective transformation in the latter case.
-According to [@michelon2006two], line-of-sight tracing presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
+According to @michelon2006two, line-of-sight tracing presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
 Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
@@
 
-Interestingly, we did not find a correlation between gaze understanding and the other ToM tasks.
-Why not?
+Interestingly, we found weaker correlations between gaze understanding and the other ToM tasks.
 While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
@@
 
-In previous work, we could establish that the TANGO is suited as an individual differences measure [@prein2023tango].
+In previous work, we established that the TANGO is suited as an individual differences measure [@prein2023tango].
 Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous trials.
-These sum scores contain measurement errors and can only capture limited variance, which may obscure potential correlations.
-However, since these tasks are the gold standard in the social-cognitive literature and continuous measures with satisfying psychometric properties are, to the best of our knowledge, still scarce, we nonetheless relied on them in this study.
-It seems noteworthy to point out that lower correlations between ToM abilities and gaze understanding could be grounded in the design features of the applied ToM tasks.
-We already stated this concern in the Pre-registration (<https://osf.io/xsqkt>).
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous items.
+The resulting sum scores are of limited use when it comes to quantifying genuine differences between individuals.
+However, since these tasks are the gold standard in the social-cognitive literature [@rakoczy2022foundations; @poulin-dubois2023discontinuity; @wellman2018theory; @byom2013theory; @bialecka-pikul2021early], and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce [e.g., @beaudoin2020systematic; @mayes1996testretest], we nonetheless relied on them in this study.
+Thus, lower correlations between ToM abilities and gaze understanding could reflect poor measurement on the side of ToM tasks rather than a genuine absence of association.
+We would like to point out that we already stated this concern in our pre-registration (<https://osf.io/xsqkt>).
 
-If the reliability of a certain task is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation; @trafimow2016attenuation].
-Adjusting for the measurement error would most likely increase the underlying correlation.
-While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task (for example, see [@prein2023tango]), we do not have reliability estimates of the ToM measures.
+If the reliability of a certain task is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation].
+Adjusting for the measurement error would increase the so-called true correlation.
+While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task [e.g., see @prein2023tango], we do not have reliability estimates of the ToM measures.
 Therefore, applying said approaches is unfortunately not feasible to compare correlations between all our applied measures.
-This, in turn, underlines the importance of the psychometric properties of a task and the reporting of such.
+This, in turn, underlines the importance of assessing the psychometric properties of a task and the reporting of such.
 The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
@@
 
-In this paper, we have illuminated the developmental trajectory of gaze understanding and the cognitive processes behind it.
-Study 1 focussed on how gaze understanding changes with age.
-We found that individual differences exist throughout the lifespan.
+In a series of three studies, we shed light on the developmental trajectory of gaze understanding across the lifespan and the cognitive processes behind it.
+Study 1 focused on how gaze understanding changes with age.
 There is a steep learning curve in the preschool years in which children become more and more precise in locating the attentional focus of an agent.
@@
 Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
 In Study 2, we proposed a computational cognitive model that describes gaze understanding at a process level.
-Our gaze model estimates reliable individual parameter values and could recover signature patterns in the data.
-It outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate a pupil angle.
+To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
+Individual differences can be represented as varying levels of uncertainty around these pupil angles.
+Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
 Study 3 made use of the case that the TANGO is a reliable individual differences measure to further investigate potential components of gaze understanding.
 One fundamental assumption of our computational cognitive model is that gaze understanding relies on a vector estimation process.
-We experimentally isolated this component by carefully designing a non-social, physical vector estimation task.
+We experimentally isolated this component by designing a non-social, physical vector estimation task.
 Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
@@
 Our applied measure allowed us to capture fine-grained individual differences throughout the lifespan.
-In previous work, we have shown that these individual differences are meaningful variations (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
+In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
 Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
@@
 Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
-We find strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig2)F).
-Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig2)E).
+We find strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D).
+Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
 The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
-The model proposes that development in gaze understanding equals an improvement in estimating the agent's pupil angles.
+The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
 
-In Study 3, we tested a modeling assumption by adopting a non-social vector estimation task.
-As suggested by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
-This ability might be helpful in several social-cognitive tasks, for example, action prediction and intention understanding.
+In Study 3, we tested the relation between gaze understanding and non-social vector estimation.
+As implied by the structure of our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
+This ability might be helpful in several social-cognitive tasks, for example, action prediction [@friesen2011gaze], and intention understanding.
 Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
@@
 Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the real 3D world.
-The processes of understanding gaze in daily life likely rely on the same principles proposed in this paper.
+The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
 We presented the first evidence that this might be the case.
@@
 
-Moving away from the traditional testing setup with two objects allowed us to simulate our daily environment more closely.
 Clearly, our real-life environment is visually still more cluttered and diverse than the one presented in our tablet task.
-However, we can use other signals to disentangle where others are looking; for example, a body or head orientation or our common ground.
+However, in contrast to our task, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground [@bohn2018common; @moll2013primacy; @osborne-crowley2020social].
 A previously shared interaction history might restrict the options we consider potential targets.
-This might be represented in a model as a non-uniform distribution over the visual scenery.
+From a modeling perspective, this might be represented as a non-uniform distribution over locations in the visual scenery.
 
@@
 As we have previously seen [@prein2023tango], precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
-Humans likely learn to follow gaze in social interactions.
+Humans likely learn to follow gaze in social interactions [@triesch2006gaze].
 Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
-A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding.
-In addition, a next logical step for studying individual developments in gaze understanding would be a longitudinal data collection.
-
-In sum, this paper deepens our insights into the fundamental social-cognitive ability to understand gaze.
-In addition, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
+A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding [@hernik2019infanta].
+In addition, a next logical step for studying individual developments in gaze understanding would be longitudinal data collection.
 
@@
 Seventy-year-olds who have working WIFI connections, know how to use a computer and are registered on Prolific might not be representative for their age group.
-We can imagine that results from a more diverse, in-person data collection might show differently.
+We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories towards old age.
 
@@
 The model assumes no motor imprecision in this estimation.
-Clearly, it could be the case that younger children located the agent's focus at one particular point but clicked somewhere slightly off.
+Clearly, it could be the case that younger children located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
 This would blur the model's estimation of the inferential component.
-However, watching the children aim at the screen during data collection, we believe that inaccurate aiming was seldom the case.
+An argument that speaks againt motor control issues is children's performance in the training trials.
+In the first trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels [also see Supplements of @prein2023tango].
+Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem therefore very unlikely.
 
 Regarding Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
-However, it is important to note that a critical feature of the target object differs between the two tasks: in the TANGO, the target (= balloon) moves from the center of the screen to its final position in a self-propelled, continuous way.
-In the non-social vector estimation task, the target (=magnet) does not move but stays stationary on the ground.
+However, it is important to note that a critical feature of the target object differed between the two tasks: in the TANGO, the target (= balloon) moved from the center of the screen to its final position in a self-propelled, continuous way.
+In the non-social vector estimation task, the target (=magnet) did not move but stayed stationary on the ground.
 Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
-Second, the starting positions differ: the magnet never floats in the center of the screen.
+Second, the starting positions differ: the magnet never appears in the center of the screen.
 Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
+Additionally, in the TANGO, two eyes are presented and information of the two (matching) cues need to be integrated to infer the target's location.
+In the non-social vector estimation task, only one circular window with a gearwheel inside is presented as a directional cue and there is no need to integrate two different information sources.
+Future research could further investigate how factors like self-propelled movement, agency (of the cued target), spatial layout, and number of information sources influence the mechanisms of gaze understanding.
 
@@
 In three studies, we have illuminated the development and the mechanisms of gaze understanding in further detail.
-In Study 1, we saw that children's precision in localizing the attentional focus of an agent improves into the teenage years.
-Adults' level of precision stays comparatively stable, even though older participants perform slighty more imprecise.
-In addition, we found individual differences throughout the sample.
-Not all adults performed equally precise in our task.
-In Study 2, we presented a computational cognitive model of gaze understanding.
-An inferential component estimates a participant's ability to locate the attentional focus of another agent based on calculating pupil angles.
-The model can explain individual differences between participants and recovers signature patterns of our data.
-In Study 3, we explore a crucial assumption of our model: that understanding gaze relies on vector estimation.
-We designed a non-social, physical vector estimation task that closely matched the design of the gaze understanding task.
-Furthermore, we applied traditional ToM measures.
-We found that gaze understanding correlates with vector estimation, supporting our modeling assumption.
-Gaze understanding and perspective-taking also relate to one another, while the other ToM tasks did not correlate with gaze understanding.
-This proves how important it is to further think about the processes which individuals employ to solve a given task.
-While the context of all ToM measures might be similar in its social nature, the mechanisms to solve gaze understanding and false belief reasoning might vary.
-In summary, we have carefully examined gaze understanding throughout the lifespan and present a testable computational modeling framework to explain variation between individuals.
+In Study 1, we found gaze understanding to rapidly improve in early childhood, and minimally decline again toward old age.
+Additionally, we found individual differences throughout the lifespan.
+In Study 2, we presented a computational cognitive model of gaze understanding, which can explain the variation between individuals.
+The model's inferential component estimates the participant's ability to estimate pupil angles based on the pupil location within the eyes.
+In Study 3, we found that gaze understanding correlates with non-social vector estimation, supporting a fundamental assumption of our gaze model.
+Gaze understanding and perspective-taking also relate to one another, while other ToM tasks did not correlate.
+While all ToM measures take place in a social context, the underlying mechanisms to solve each task might vary.
+Paying attention to the variation between individuals - instead of averaging over them - helps us to understand the processes behind our social-cognitive abilities.
+In sum, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
 

### 2023-09-24 stats/gazemodel.Rmd
incorporate Manuel's feedback

@@
 ```{r arrange_plot}
-setup_png <- ggdraw() + draw_image("../figures/gazemodel_logic_alpha.png", scale = 0.82)
-ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_geometry_lines.png", scale = 0.95)
-
 dev_plot <- readRDS(file = "../saves/gazemodel_dev_plot.rds")
@@
 gazemodel_plot <- ggarrange(
-  setup_png,
   dev_plot, 
@@
 
-  ulogic_png, 
   u_plot, 
@@
 
-  ncol = 4, 
+  ncol = 3, 
   nrow = 2, 
-  widths = c(9, 11, 1, 12), 
-  labels = c("A", "B", "", "C", "D", "E", "", "F")
+  widths = c(11, 1, 12), 
+  labels = c("A", "", "B", "C", "", "D")
 )
@@
 saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
-ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
-ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white", device = cairo_pdf) 
+ggsave("../figures/gazemodel_plot.png", width = 8, height = 5, scale = 1.3, bg = "white")
+ggsave("../figures/gazemodel_plot.pdf", width = 8, height = 5, scale = 1.3, bg = "white", device = cairo_pdf) 
 # add cairo_pdf to enable greek symbols in pdf saving

### 2023-10-04 paper/manuscript.Rmd
ready for first round of co-author feedback

@@
 While the emergence of gaze following - on a group level - has been thoroughly studied, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
-In Study 1, we examine gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds from a mid-sized German city).
+In Study 1, we examined gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds; children from a mid-sized German city; international remotely tested adults).
 We found a steep learning curve during preschool years, in which children become more precise in locating the attentional focus of an agent.
-Precision levels then stay comparably stable throughout adulthood with a minor decline toward old age.
-In Study 2, we formalize the process of gaze understanding in a computational cognitive model that allows us to conceptualize individual differences in a psychologically meaningful way (*N* = 60 3- to 5-year-olds, 50 adults).
+Precision levels then stayed comparably stable throughout adulthood with a minor decline toward old age.
+In Study 2, we formalized the process of gaze understanding in a computational cognitive model that allowed us to conceptualize individual differences in a psychologically meaningful way (*N* = 60 3- to 5-year-olds, 50 adults).
 According to our model, participants estimate pupil angles with varying levels of precision based on observing the pupil location within the agent's eyes.
-In Study 3, we test two implications of our gaze model, namely that gaze understanding should be related to perspective-taking abilities and vector estimation in non-social settings (*N* = 102 4- to 5-year-olds).
-We found that gaze understanding is associated with both of these abilities but not with other Theory of Mind tasks.
+In Study 3, we tested two implications of our gaze model, namely that gaze understanding should be related to perspective-taking abilities and vector estimation in non-social settings (*N* = 102 4- to 5-year-olds).
+We found that gaze understanding is associated with both of these abilities but less so with other Theory of Mind tasks.
 This work illustrates how the combination of reliable measurement instruments and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
@@
 We see the following challenges: (1) Studies focus on infancy, leaving aside further development in childhood, adolescence and adulthood; (2) Gaze cues are often accompanied by head movements in the same direction [see @delbianco2019developmental], which makes it hard to isolate the referential information extracted from the eyes; (3) Infants’ looking times are usually used as the dependent variable and it is unclear if and how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Analyses focus on group-level averages, and we overlook variation in the sample because we cannot measure it with dichotomous outcome variables.
-In the following paragraphs, we will turn to each of these arguments and point out gaps in our understanding of the development of gaze following.
+In the following paragraphs, we will turn to each of these arguments and note how we addressed them consequently in our study.
 
@@
 It seems likely that children fine-tune the performance of the already existing skills - presumably while using them in social interactions.
-To capture further development in gaze understanding, we therefore conduct our study across the lifespan.
+To capture further development in gaze understanding, we therefore conducted our Study 1 across the lifespan.
 
@@
 Clearly, it is important to differentiate between head and gaze following.
-In this study, we focus on subtle gaze cues and isolate eye movement alone.
+In our three studies, we focused on subtle gaze cues and isolated eye movement alone.
 
 Third, let us consider the classical response measure of collecting looking times.
-Though previous studies suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the focus of the agent.
+Though previous studies suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the focus of the agent [cf.
+@aslin2007look].
 Infants could simply align their orientation without processing what exactly the other is seeing [cf.
@@
 @povinelli1997exploitation].
-In this paper, we assess how subtle gaze cues guide participants' behavior in actively locating a target.
+In this paper, we assessed how subtle gaze cues guided participants' behavior in actively locating a target.
 
@@
 Measuring individual differences in basic aspects of social cognition is especially important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
-In this study, we measure participants' gaze understanding continuously by using a task which is designed to capture individual-level variation [@prein2023tango].
+In our studies, we measured participants' gaze understanding continuously by using a task which has been designed to capture individual-level variation [@prein2023tango].
 
@@
 
-The present study has two main goals: first, we study the development of gaze understanding beyond infancy on a group level (Study 1).
-Our goal was not to establish the youngest age at which children understand gaze cues.
-Rather, we wanted to examine how this ability changes with age.
-Even though we find expected developmental patterns - rapid improvement in early childhood; some decline toward old age - we observed substantial variation between individuals at all ages.
-Our second goal is to provide a substantive process-level theory of gaze understanding (and individual differences therein) in the form of a computational model.
-We formalize gaze understanding as a form of vector estimation and show that our model explains empirical data (Study 2).
-Furthermore, we test two empirical predictions that follow from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
+The present study had two main goals: first, we studied the development of gaze understanding beyond infancy on a group level (Study 1).
+Instead of capturing the youngest age at which children can follow gaze, we wanted to examine how this ability changes with age.
+Even though we found expected developmental patterns - rapid improvement in early childhood; some decline toward old age - we observed substantial variation between individuals at all ages.
+Our second goal was to provide a substantive process-level theory of gaze understanding (and individual differences therein) in the form of a computational model.
+We formalized gaze understanding as a form of vector estimation and showed that our model explained empirical data (Study 2).
+Furthermore, we tested two empirical predictions that followed from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
 
@@
 2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
+The research adhered to the legal requirements of psychological research with children in Germany.
 Data was collected between May 2021 and April 2023.
@@
 
+## Procedure
+
+Children and teenagers received a personalized link to the study website.
+Caregivers were asked to provide technical support whenever needed, while explicitly being reminded not to help their children in responding.
+Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
+Adults completed the online study unsupervised.
+
 Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground (see Figure \@ref(fig:fig4)A; however, please note that Study 1 presented animal agents).
@@
 
-## Procedure
-
-Children and teenagers received a personalized link to the study website.
-Caregivers were asked to provide technical support whenever needed, while explicitly being reminded not to help their children in responding.
-Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
-Adults completed the online study unsupervised.
-
 ## Analysis
@@
 The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in widths, i.e., a participant with an imprecision of 1 clicked on average one balloon width to the left or right of the true target center.
-We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models using leave-one-out cross-validation (LOO), the widely applicable information criterion (WAIC), and model weights [@vehtari2017practicala].
+We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models via model weights and the difference in expected log pointwise predictive density (ELPD) estimated using leave-one-out cross-validation (LOO) [@vehtari2017practicala].
 
@@
 
-In our model comparison, we found clear evidence for a non-linear development in gaze understanding across the lifespan.
-Compared against linear, quadratic, and cubic models, the Gaussian Process model showed the best model fit, demonstrated by the greatest model weight and smallest WAIC values.
+In our model comparison, we found substantial evidence for a non-linear development in gaze understanding across the lifespan.
+The Gaussian process model was clearly preferred over the cubic, quadratic and linear models due to the highest predictive accuracy according to the LOO ELPD estimates (with negative ELPD differences and more than twice the estimated standard error): elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); and elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model.
+Morover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`).
 For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) and visual inspection indicated nonlinearity (see Figure \@ref(fig:fig1)).
@@
 The TANGO has previously been shown to reliably capture inter-individual differences in gaze understanding [@prein2023tango].
-The variation between participants is thus likely genuine and not due to random noise.
-Now, we aim to understand developmental change and variation across participants on a process level.
+The variation between participants was thus likely genuine and not due to random noise.
+Now, we aimed to understand developmental change and variation across participants on a process level.
 We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's line of sight and its attentional focus, which leads them to identify the target position.
-We formalize this inference process in a computational cognitive model.
+We formalized this inference process in a computational cognitive model.
 
@@
 The expected patterns can then, in turn, be compared to the empirically observed behavior.
-@moore2008development have already argued for systematic, empirical approaches in combination with formal modeling to arrive at a deeper understanding of gaze following.
+@moore2008development has already argued for systematic, empirical approaches in combination with formal modeling to arrive at a deeper understanding of gaze following.
 
@@
 
-Our model quantifies a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+Our model quantified a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
 It is formally defined as:
@@
 In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
-We then calculate a line between these two points: this is our gaze vector (acting in the functionally same way as a pupil angle).
-Now, knowing the eyeball radius, we calculate the point of intersection at which the gaze vector meets the eyeball boundary.
-Finally, the agent's pupil moves from the center of the eyeball along the gaze vector to the intersection point.
-This way, the agent is animated to "look at" the target.
-In the gaze model, we assume participants go through these steps in reverse order.
+We then calculated a line between these two points: this was our gaze vector (acting in the functionally same way as a pupil angle).
+Now, knowing the eyeball radius, we calculated the point of intersection at which the gaze vector met the eyeball boundary.
+Finally, the agent's pupil moved from the center of the eyeball along the gaze vector to the intersection point.
+This way, the agent was animated to "look at" the target.
+In the gaze model, we assumed participants go through these steps in reverse order.
 
-Based on our verbal task instructions, we assume that participants (1) expect the agent's looks to be directed at the target, and (2) to click on the coordinate they estimate the agent to look at.
-Consequently, we do not assume that participants' clicks are noisy in any way but that they click on the screen location where they genuinely think the target is (and that the agent is looking at).
+Based on our verbal task instructions, we assumed that participants (1) expected the agent's looks to be directed at the target, and (2) to click on the coordinate they estimated the agent to look at.
+Consequently, we did not assume that participants' clicks were noisy in any way but that they clicked on the screen location where they genuinely thought the target was (and that the agent was looking at).
 
 The true eye angles ($\alpha_l$ and $\alpha_r$) cannot be directly observed and have to be estimated based on the position of the pupils within the eyes, resulting in approximate values ($\hat{\alpha_l}$ and $\hat{\alpha_r}$).
-We presume this estimation to be a noisy process.
-Thus, we conceptualize the development of the cognitive ability to follow gaze as a reduction of noise in the estimates (i.e., an increased certainty about the pupil angles).
+We presumed this estimation to be a noisy process.
+Thus, we conceptualized the development of the cognitive ability to follow gaze as a reduction of noise in the estimates (i.e., an increased certainty about the pupil angles).
 
-Any clicked value of $x_c$ implies a "matched pair" of the estimated pupil angles $\hat{\alpha_l}$ and $\hat{\alpha_r}$, with the property that lines extended along those two angles meet at the precise location of the target.
+Any clicked value of $x_c$ implied a "matched pair" of the estimated pupil angles $\hat{\alpha_l}$ and $\hat{\alpha_r}$, with the property that lines extended along those two angles met at the precise location of the target.
 As a consequence, we can rewrite the likelihood function of the model above:
@@
 
-The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assume to be skewed towards the screen center: We anticipate that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent is located centrally on the screen.
-We estimate the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
+The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assumed to be skewed towards the screen center: We anticipated that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent was located centrally on the screen.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
 
 The width of this distribution is defined by $\sigma^p$.
-We assumed that the center bias changes with age and we therefore estimated $\sigma^p$ via a linear regression as a function of the participant's age ($age_i$): $\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}$.
-Therefore, the participant-specific value for $P(x_c)$ was constrained by the performance in the TANGO and the participant's age.
+For children, we assumed that the center bias changed with age and we therefore estimated $\sigma^p$ via a linear regression as a function of the child's age ($age_i$): $\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}$.
+Therefore, the participant-specific distribution for $P(x_c)$ was constrained by the performance in the TANGO and the child's age.
+For the adults, $\sigma^p$ was not age-specific.
 
-The main inferential task for the participant lies in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
-For this, we assume that the pair of estimated pupil angles are sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
+The main inferential task for the participant lied in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
+For this, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
 
@@
 
-Broadly summarizing: Participants are assumed to observe the pupil locations and the center of the agent's eyes.
+Broadly summarizing: Participants were assumed to observe the pupil locations and the center of the agent's eyes.
 Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
 Taking the angle between this vector and a line pointing vertically to the ground yields the pupil angle.
-Participants are assumed to sample from Normal distributions centered around the true pupil angle.
-They are assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
+Participants were assumed to sample from Normal distributions centered around the true pupil angle.
+They were assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
 
-As $\sigma_v$ determines the level of accuracy with which the participant estimates the pupil angles, it is the component that defines $\theta$.
+As $\sigma_v$ determined the level of accuracy with which the participant estimated the pupil angles, it is the component that defines $\theta$.
 When $\sigma_v$ is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.\ When $\sigma_v$ is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
-We expect $\sigma_v$ to vary between individuals.
-Consequently, individuals differ in the level of precision with which they can locate the target based on observing the agent's eyes.
+We expected $\sigma_v$ to vary between individuals.
+Consequently, individuals differed in the level of precision with which they can locate the target based on observing the agent's eyes.
 
@@
 As $\sigma_v$ decreases and the cone narrows, the extent to which performance varies at different angles decreases.
-Therefore, our gaze model predicts that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.[^4] If our data matches the pattern of this model prediction, this can act as evidence for the gaze model.
+Therefore, our gaze model predicted that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.[^4] If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
 Therefore, our gaze model provides a quantitative theory of gaze understanding with testable predictions.
-In the following, we test these predictions in children and adults.
+In the following, we tested these predictions in children and adults.
 
@@
 Our goal was to describe the inferential process of gaze understanding.
+Our analysis focused on the child sample.
 We quantified how well our gaze model explained the gaze understanding process in two ways.
 First, we used correlations to quantify how well the gaze model is able to recover the data.
-For this, we aggregated the model predictions and the data for each target bin and age group (3-, 4-, 5-years-olds), and computed the coorrelation between predictions and the data.
+For this, we aggregated the model predictions and the data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed the coorrelation between predictions and the data.
 Second, we compared the predictions of our gaze model to two - very simple - alternative models that assume that participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
 The random guessing model assumed that participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
-The center bias model assumed that participants always click at the screen center and was implemented as sampling from a Normal distribution with the the center of the screen as the mean, and one balloon width as the standard deviation, $\mathcal{N}(960, 160^2)$.
-Note that the center bias model also predicts that imprecision should be higher for targets further out on the screen, resulting also in a U-shaped pattern.
-However, the shape of this pattern is different from that of the gaze model [TODO: in what way?!].
+The center bias model assumed that participants always click at the screen center and was implemented as sampling from a Normal distribution with the the center of the screen as the mean, and one balloon width as the variance, $\mathcal{N}(960, 160)$.
+Note that the center bias model also predicted that imprecision should be higher for targets further out on the screen.
+However, compared to the gaze model, the center bias model predicted a very steep effect towards the sides, resulting in a V-shaped pattern (i.e., imprecision as the distance between the target location and the screen center).
 All cognitive models were implemented in WebPPL [@goodman2014design].
@@
 ```{r gazemodel_results}
-gazemodel_comparison_bf <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
+gazemodel_comparison_kids <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
+gazemodel_comparison_adults <- readRDS("../data/gazemodel-adults-comparison-bf.rds")
 gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
+gazemodel_prior <- readRDS("../saves/gazemodel_prior.rds")
 ```
 
-We found clear support for our gaze model, both in children as well as adults.
-When correlating the observed data across all target posions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred"]`]).
-The model comparison strongly favored our gaze model over the center bias model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_center`) and the random guessing model ($logBF_{10}$ = `r gazemodel_comparison_bf$bf_inf_guess`).
-As can be seen in Figure \@ref(fig:fig3)C, the gaze model predicts a U-shaped pattern which we also observed in our data.
-A strong correlation between the data mean and the gaze model estimate ($\sigma_v$), *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param"]`],  showed that the data mean is suitable to quantify individual differences.
 The age effects in Study 2 largely replicated those of Study 1.
 When comparing performance of the three- to five-year-olds in Study 1 and 2, we see a rapid improvement in gaze understanding in early childhood (see Figure \@ref(fig:fig1) inset and \@ref(fig:fig3)A).
+The gaze model's prior over potential target locations assumed that participants would be skewed to click towards the screen center.
+For the children, we estimated the width of the prior's distribution based on the participants' age.
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
+The slope of the prior indicated that older children were only marginally less drawn towards the screen center (i.e., marginally wider distribution) compared to the younger children.
+
+We found very clear support for our gaze model, both in children as well as adults.
+A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
+As can be seen in Figure \@ref(fig:fig3)C, the gaze model predicted a U-shaped pattern which we also observed in our data.
+The model comparison strongly favored our gaze model over the center bias model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_center`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_center`) and the random guessing model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_guess`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_guess`).
+For the child sample, we went one step further into the analysis.
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
 
@@
 The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
-(B) Correlation between estimated mode of the model parameter and data mean per individual, color-coded by age.
-The grey regression line with 95% CI shows smooth conditional mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
+The large black point with 95% HDI presents the mean of the model parameter for the adult sample.
+We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
+(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
+In the child sample, color denotes the age in years.
+Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*.
 (C) Pattern recovery.
@@
 Model predictions in blue; data in grey.
-(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals).
+(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals; only for the child sample).
 
@@
 Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
-In the next study, we test this prediction.
+In the next study, we tested this prediction.
 
@@
 The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underlines this.
-Therefore, it seems reasonable to expect correlations between gaze understanding and other measures of social-cognitive abilities.
+Therefore, it seemed reasonable to expect correlations between gaze understanding and other measures of social-cognitive abilities.
 
@@
 
-We administered four tasks from the @wellman2004scaling ToM scale.
+We administered four tasks from the @wellman2004scaling ToM scale (see Supplements for further detail).
 We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
@@
 
-By design, both the TANGO as well as the non-social vector estimation task involve vector estimation.
+By design, both the TANGO as well as the non-social vector estimation task involved vector estimation.
 On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks would correlate with each other.
@@
 
-For the ToM battery, the dependent variable was the aggregate score of all solved tasks (see Supplements for further detail).
-Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruits a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
-(B) If gaze understanding relies purely on task-specific processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the ToM battery, the dependent variable was the aggregate score of all solved tasks.
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruited a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
+(B) If gaze understanding relied purely on task-specific processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
 For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficients.
@@
 Study 1 focused on how gaze understanding changes with age.
-There is a steep learning curve in the preschool years in which children become more and more precise in locating the attentional focus of an agent.
-During teenage years and early adulthood, participants reach their peak performance.
-Precision levels then stay comparably stable, with a minor decay toward older adulthood.
+We found a steep learning curve in the preschool years in which children became more and more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reached their peak performance.
+Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
 Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
-In Study 2, we proposed a computational cognitive model that describes gaze understanding at a process level.
-We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate a pupil angle.
+In Study 2, we proposed a computational cognitive model that described gaze understanding at a process level.
+We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate pupil angles.
 To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
@@
 Study 3 made use of the case that the TANGO is a reliable individual differences measure to further investigate potential components of gaze understanding.
-One fundamental assumption of our computational cognitive model is that gaze understanding relies on a vector estimation process.
+One fundamental assumption of our computational cognitive model was that gaze understanding relies on a vector estimation process.
 We experimentally isolated this component by designing a non-social, physical vector estimation task.
@@
 Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
-We find strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D).
+We found strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D).
 Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
@@
 The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
+Impressively, we found evidence that the same model performed well for a child as well as an adult sample.
 
@@
 
-Compared to previous gaze following studies, we applied an active response measure.
-By asking our participants to locate a target, we created a motivation and reason to follow gaze as it might be the case in real-life social interactions.
-This behavioral outcome seems well suited to study children's understanding about the intention behind gaze.
-What is more, we could show that children's ability to follow gaze toward a cued location translated into meaningful active behavior.
-
 While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
@@
 Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
-A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding [@hernik2019infanta].
+A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding.
 In addition, a next logical step for studying individual developments in gaze understanding would be longitudinal data collection.
@@
 
-It is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
+In this project, we have focused on studying variation between individuals and across age groups.
+However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta].
+Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals [@nielsen2017persistent].
+There is first evidence that cultural variation in face-to-face interactions does not influence infants' gaze following abilities [@hernik2019infanta].
+However, we cannot generalize our here-reported developmental trajectory to different socio-environmental and cultural settings, and assume that our presented process model of gaze understanding holds universally true.
+Analysing cross-cultural variation and, for example, checking for predicted "signature patterns" in the data, will inform our modeling work and theory building in further detail [@amir2020crosscultural].
+
+Moreover, is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
 Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
@@
 In three studies, we have illuminated the development and the mechanisms of gaze understanding in further detail.
-In Study 1, we found gaze understanding to rapidly improve in early childhood, and minimally decline again toward old age.
-Additionally, we found individual differences throughout the lifespan.
-In Study 2, we presented a computational cognitive model of gaze understanding, which can explain the variation between individuals.
-The model's inferential component estimates the participant's ability to estimate pupil angles based on the pupil location within the eyes.
-In Study 3, we found that gaze understanding correlates with non-social vector estimation, supporting a fundamental assumption of our gaze model.
-Gaze understanding and perspective-taking also relate to one another, while other ToM tasks did not correlate.
-While all ToM measures take place in a social context, the underlying mechanisms to solve each task might vary.
-Paying attention to the variation between individuals - instead of averaging over them - helps us to understand the processes behind our social-cognitive abilities.
-In sum, the present research shows how new social cognition measures and detailed statistical models can lead to exciting research questions, which we can, in turn, experimentally test.
+We have shown that gaze understanding continues to develop beyond infancy, and that individuals differ in their precision levels to localize the attentional focus of an agent.
+Our proposed process-level theory proved helpful to model the mechanisms of gaze understanding and the source of individual differences.
+The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
 

### 2023-10-04 stats/gazemodel.Rmd
ready for first round of co-author feedback

@@
 model_kids_dev_prior <- readRDS("../data/gazemodel-kids-dev-prior.rds")
+
+model_adults_ind <- readRDS("../data/gazemodel-adults-ind.rds") %>% 
+  rename("mode" = sdTol) %>% 
+  mutate(
+    age_group = 18, 
+    age = 18,
+    id = str_replace_all(id, "gafo_prolific_modelvalidation_vp", "gp1-")
+  )
+
+model_adults_bins <- readRDS("../data/gazemodel-adults-bins.rds") %>% 
+  mutate(
+    age_group = 18, 
+    # transform into target width units
+    data_mean = data_mean / 160, 
+    model_mean = model_mean / 160,
+  )
 ```
@@
 
-# CHILDREN
+# Inference
 
-## Inference
-
-```{r plot2B}
-# (plot 2A is model logic, png)
+```{r plot3A}
 # developmental trajectory model inference parameter
@@
 
+model_adults_sd <- model_adults_ind %>% 
+  summarize(
+    mean_mode = mean(mode), 
+    lci = hdi_lower(mode), 
+    uci = hdi_upper(mode)
+  )
+
 dev_plot <- ggplot() +
+
+  # children
   geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
@@
   geom_line(data = inf_map_devp, aes(x = age + 3, y = sd), col = "black", linewidth = 1.25) +
-  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
+
+  # adults 
+  geom_jitter(data = model_adults_ind, aes(x = 6.5, y = mode), alpha = 0.5, color = "darkgrey",  width = .1) + 
+  geom_pointrange(data = model_adults_sd %>% head(1), aes(x = 6.5, y = mean_mode, ymin = lci, ymax = uci), size = 0.5) +
+
+  scale_x_continuous(limits = c(3, 6.7), breaks = seq(3, 6.5, 0.5), labels = c("3.0", "3.5", "4.0", "4.5", "5.0", "5.5", "6.0", "Adults")) + 
   scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
@@
 
-```{r plot2C}
+```{r plot3B}
 comparison_model_data_devp <- model_kids_dev_prior %>%
@@
 
-model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
+comparison_model_data_adults <- tango_adults %>% 
+  group_by(subj_id) %>% 
+  summarize(
+    data_mean = mean(click_dist_balloons)
+  ) %>% 
+  left_join(model_adults_ind %>% select(-lci, -uci) %>% rename("model_mode" = mode, "subj_id" = id))
+
+comparison_model_data <- full_join(comparison_model_data_devp, comparison_model_data_adults) %>% 
+  mutate(sample = ifelse(age < 18, "children", "adults"))
+
+model_vs_data_plot <- ggplot(comparison_model_data, aes(x = model_mode, y = data_mean, group = sample)) +
   geom_point(aes(col = age)) +
-  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
+  stat_cor(data = comparison_model_data %>% filter(sample == "children"), aes(label = paste(..r.label..)), method = "pearson", size = 4, r.accuracy = 0.01, cor.coef.name = "r", label.x = 0, label.y = 4.5) +
+
+  stat_cor(data = comparison_model_data %>% filter(sample == "adults"), aes(label = paste(..r.label..)), method = "pearson", size = 4, r.accuracy = 0.01, cor.coef.name = "r", label.x = 0, label.y = 2.25) +
+
   geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
+
+  labs(x = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")), y = "Mean data imprecision", color = "Age") +
+
+  scale_x_continuous(limits = c(0, NA), n.breaks = 7) +
+  scale_y_continuous(limits = c(0, NA), n.breaks = 5) +
   scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
-  labs(x = expression(paste("Mode model parameter (", italic("\U03C3"[v]), ")")), y = "Mean data imprecision", color = "Age") + 
-  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
-  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))
+  theme_few() +
+  theme(
+    legend.position = c(0.37, 0.3),
+    strip.text = element_text(face = "bold", size = 10), 
+    legend.title = element_text(size = 8),
+    legend.text = element_text(size = 8), 
+    legend.box.background = element_rect(), 
+    legend.key.height = unit(0.5, "cm"),
+  ) +
+  facet_wrap(~ factor(sample, levels = c("children", "adults"), labels = c("Child sample", "Adult sample")), scales = "free")
 
 model_vs_data_plot
+
 saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
@@
 
-## Inference parameters individuals
+# Inference parameters individuals
 
@@
 
-## Recover U pattern
+# Recover U pattern
 
@@
 
-```{r plot2E}
-# (plot 2D is model geometry logic, png)
+```{r plot3C}
 # u pattern recovery
@@
 # saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
+# ind_sd_long <- readRDS("../saves/gazemodel_ind_sd_long.rds")
 
-# priorMode <- model_kids_dev_prior %>%
-#   filter(scope == "global",
-#          parameter == "priorSd",
-#          type != "sigma") %>%
-#   group_by(type) %>%
-#   summarise(mode = estimate_mode(value))
-#
+priorMode <- model_kids_dev_prior %>%
+  filter(scope == "global",
+         parameter == "priorSd",
+         type != "sigma") %>%
+  group_by(type) %>%
+  summarise(
+    mode = estimate_mode(value), 
+    lci = hdi_lower(value), 
+    uci = hdi_upper(value))
+
+saveRDS(priorMode, file = "../saves/gazemodel_prior.rds")
 
@@
 
-u_plot <- modelpred_gaze %>%
+u_data <- full_join(modelpred_gaze, model_adults_bins)
+saveRDS(u_data, "../saves/gazemodel_u_data.rds")
+
+u_plot <- u_data %>%
   pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
   mutate(
-    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
+    age_group = factor(age_group, levels = c(3, 4, 5, 18), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "Adults")), 
   ) %>% 
@@
   theme(
-    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
-    strip.text = element_text(face = "bold", size = 12), 
-    legend.title = element_text(size = 6),
-    legend.text = element_text(size = 6), 
+    legend.position = c(0.881, 0.7), # c(0,0) bottom left, c(1,1) top-right
+    strip.text = element_text(face = "bold", size = 10), 
+    legend.title = element_text(size = 8),
+    legend.text = element_text(size = 8), 
     legend.box.background = element_rect(), 
-    legend.key.height = unit(0, "cm"),
-    legend.key.width = unit(-1.5, "cm"),
+    legend.key.height = unit(0.4, "cm"),
+    legend.key.width = unit(-1.2, "cm"),
     plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
@@
 ```
+
 # Alternative models click generation
@@
 
-```{r plot2F}
+```{r plot3D}
 modelpred_gaze_plot <- readRDS("../saves/gazemodel_modelpred_gaze_plot.rds")
@@
   modelpred_gaze_plot + 
-    theme(legend.position = c(0.85, 0.2), 
-          legend.title = element_text(size = 6),
-          legend.text = element_text(size = 6), 
+    theme(legend.position = c(0.85, 0.3), 
+          legend.title = element_text(size = 8),
+          legend.text = element_text(size = 8), 
           legend.box.background = element_rect(), 
-          legend.key.height = unit(0, "cm"),
+          legend.key.height = unit(0.3, "cm"),
           legend.key.width = unit(-1.5, "cm"),
-          plot.margin = margin(0.2, 0, 0.1, 0.2, "cm") # t r b l
+          plot.margin = margin(0.2, -2, 0.1, 0.2, "cm") # t r b l
          ),
@@
   nrow = 2, 
-  widths = c(11, 1, 12), 
+  widths = c(13, 1, 12), 
   labels = c("A", "", "B", "C", "", "D")
@@
 saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
-ggsave("../figures/gazemodel_plot.png", width = 8, height = 5, scale = 1.3, bg = "white")
-ggsave("../figures/gazemodel_plot.pdf", width = 8, height = 5, scale = 1.3, bg = "white", device = cairo_pdf) 
+ggsave("../figures/gazemodel_plot.png", width = 8, height = 5, scale = 1.5, bg = "white")
+ggsave("../figures/gazemodel_plot.pdf", width = 8, height = 5, scale = 1.4, bg = "white", device = cairo_pdf)
 # add cairo_pdf to enable greek symbols in pdf saving
@@
 # create tibble for reading out stats results in rmd manuscript
-corr_gazemodel_param <- comparison_model_data_devp %>% select(model_mode, data_mean) %>% corr.test(method = "pearson")
+corr_gazemodel_param_children <- comparison_model_data_devp %>% select(model_mode, data_mean) %>% corr.test(method = "pearson")
 
+corr_gazemodel_param_adults <- comparison_model_data_adults %>% select(model_mode, data_mean) %>% corr.test(method = "pearson")
+
+# this is children only 
 corr_gazemodel_pred <- modelpred_gaze %>% ungroup() %>% select(model_mean, data_mean) %>% corr.test(method = "pearson")
@@
 
-corrs <- rbind(corr_gazemodel_param$ci, corr_gazemodel_pred$ci, corr_centermodel_pred$ci, corr_randommodel_pred$ci) %>% 
+corrs <- rbind(corr_gazemodel_param_children$ci, corr_gazemodel_param_adults$ci, corr_gazemodel_pred$ci, corr_centermodel_pred$ci, corr_randommodel_pred$ci) %>% 
   rownames_to_column(var = "corr") %>% 
@@
             corr,
-            `mdl_m-dt_mn` = "gazemodel_param", 
-            `mdl_m-dt_mn1` = "gazemodel_pred", 
-            `mdl_m-dt_mn2` = "centermodel_pred", 
-            `mdl_m-dt_mn3` = "randommodel_pred", 
+            `mdl_m-dt_mn` = "gazemodel_param_kids", 
+            `mdl_m-dt_mn1` = "gazemodel_param_adults", 
+            `mdl_m-dt_mn2` = "gazemodel_pred_kids", 
+            `mdl_m-dt_mn3` = "centermodel_pred_kids", 
+            `mdl_m-dt_mn4` = "randommodel_pred_kids", 
            )
@@
 ```
+
 ```{r mcomparison}

### 2023-10-04 stats/supplements_gaussianprocess.Rmd
ready for first round of co-author feedback

--- 2023-07-10 stats/gaussianprocess.Rmd
@@
 
-write.csv(mgp_triallevel, "../saves/mgp_triallevel.csv", quote = F, row.names = F)
-saveRDS(mgp_triallevel, "../saves/mgp_triallevel.rds")
+write.csv(mgp_triallevel, "../saves/lifespan_mgp_triallevel.csv", quote = F, row.names = F)
+saveRDS(mgp_triallevel, "../saves/lifespan_mgp_triallevel.rds")
+mgp_triallevel <- readRDS("../saves/lifespan_mgp_triallevel.rds")
 ```
@@
 
-write.csv(mgp_aggregated, "../saves/mgp_aggregated.csv", quote = F, row.names = F)
-saveRDS(mgp_aggregated, "../saves/mgp_aggregated.rds")
+write.csv(mgp_aggregated, "../saves/lifespan_mgp_aggregated.csv", quote = F, row.names = F)
+saveRDS(mgp_aggregated, "../saves/lifespan_mgp_aggregated.rds")
+mgp_aggregated <- readRDS("../saves/lifespan_mgp_aggregated.rds")
 ```
@@
 ggplot() +
+  geom_jitter(
+    data = mdata, 
+    aes(x = age, y = imprecision), 
+    col = "darkgrey", alpha = 0.1
+  ) +
 
@@
     aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5, group = model, col = model), 
-    stat = "identity", size = 0.5, alpha = 0.15
-  ) 
-```
-
-```{r aggregated_plot}
-ggplot() +
-
-  geom_jitter(
-    data = mdata_aggregated, 
-    aes(x = age, y = mean_imprecision), 
-    col = "darkgrey", alpha = 0.75
+    stat = "identity", size = 0.75, alpha = 0.15
   ) +
 
-  geom_smooth(
-    data = pred_aggregated, 
-    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
-    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
-  ) +
+  scale_color_colorblind() + 
+  scale_x_continuous(breaks = seq(0, 80, 5)) +
+  coord_cartesian(ylim = c(0, 4)) +
+  labs(x = "Age in years", y = "Imprecision in target width", col = "Model structure")
 
-  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
-  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +
-
-  labs(x = "Age in years", y = "Average imprecision in target width")
+ggsave("../figures/supplements_lifespan_modelstructure.png", width = 7, height = 5, scale = 1, bg = "white")
+ggsave("../figures/supplements_lifespan_modelstructure.pdf", width = 7, height = 5, scale = 1, bg = "white")
 ```

### 2023-10-04 supplements/supplements.Rmd
ready for first round of co-author feedback

--- 2023-06-23 supplements/supplements.Rmd
@@
     affiliation   : "1"
-  - name          : "Manuel Bohn"
-    affiliation   : "1,2"
   - name          : "Luke Maurits"
@@
   - name          : "Daniel B. M. Haun"
-    affiliation   : "1"
+    affiliation   : "1,*"
+  - name          : "Manuel Bohn"
+    affiliation   : "1,2,*"
 affiliation:
@@
     institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+  - id            : "*"
+    institution   : "shared last authorship"  
 floatsintext      : yes
@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 header-includes:
   - \usepackage{setspace}
+  - \usepackage{float}
   - \captionsetup[figure]{font={stretch=1}}
@@
 
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(fig.pos = 'H')
+```
+
 ```{r setup, include = FALSE}
@@
 library("kableExtra")
+library("brms")
 theme_set(theme_classic())
@@
 
-# Components of gaze understanding
-## Theory of mind battery
+# Study 1: Lifespan
+## Participants
+```{r lifespan_sample, include = T, out.width = "100%"}
+lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
+
+lifespan_table <- lifespan_sample %>% 
+  mutate(
+    n = str_glue_data(., "{n_total} ({n_females} female)"), 
+    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
+  ) %>% 
+  rename(
+    `Age group` = age_group,
+    `Age SD` = age_sd, 
+    `Age mean` = age_mean
+  ) %>% 
+  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
+
+knitr::kable(lifespan_table, format = "latex", booktabs = TRUE) %>% 
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
+
+## Analysis
+### Model structures
+In the paper, we reported the following model structures: linear model: `mean_imprecision ~ age_centered`; quadratic model in `R: mean_imprecision ~ 1 + age_centered + I(age_centered^2)`; cubic model: `mean_imprecision ~ 1 + age_centered + I(age_centered^2) + I(age_centered^3);` Gaussian process model: `mean_imprecision ~ gp(age_centered, k=50, c=5/4, scale=TRUE)`.
+Note the additional parameters in the Gaussian process model.
+With the default settings, the underlying Gaussian process maths would get solved exactly.
+By providing the arguments `k` and `c`, we use an approximation process.
+The higher the value of k, the better the approximation: we have used `k=50` for faster processing speed and better diagnostics.
+`brms` suggests 5/4 as a value for `c`.
+Adding `scale=TRUE` is supposed to improve sampling speed and convergence.
+
+Originally, we fitted the models on a trial-by-trial basis with the following structure in `R: performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
+However, the Gaussian Process model was computationally heavy.
+Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+We then visually compared the model predictions of the original and the simplified models with each other.
+As you can see in Figure \@ref(fig:fig1), results of the two models did not differ notably.
+
+(ref:figlab1) **Comparison between models on a trial- or subject-level**.
+Grey dots show data of each trial.
+Solid lines show the mean predicted developmental trajectory for both models.
+Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).
+```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
+knitr::include_graphics("../figures/supplements_lifespan_modelstructure.pdf")
+```
+
+### Changepoint analysis
+In our Bayesian changepoint analysis, we restricted the model to a constant mean (i.e., a flat line with zero degree polynomial) within each segment, and to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade) to avoid "overreactions" to individual outlying data points.
+In a supplementary analysis, we assessed how different parameter settings effected of our changepoint analysis.
+We changed the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When the model had more explorative room, for example, by a greater number of change points, smaller minimum number of data points between change points, higher polynomial order, the model outputs showed more fine-grained change points.
+The exact location of the change points varied slightly.
+Overall, the interpretation stayed the same as the one we reported in the paper.
+While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
+There was a minor change in that elderly adults became slightly more imprecise again.
+If you are interested into the details, please have a look at the file `supplements_changepoint_parameters.html`, which you can find in the GitHub repository in the `stats` folder.
+
+# Study 2: Computational cognitive model 
+## Analysis
+### Gaze model prediction
+Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides).
+Since the task is presented on a screen, there is a natural border towards one side.
+Imagine the target lands to the very right side.
+Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now.
+Therefore, the predicted U-shaped pattern should decrease again towards the screen borders.
+For previous reliability analyses [@prein2023tango], we had increased the trial number for an adult sample (N = 70; each 30 trials).
+Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \@ref(fig:fig2)).
+
+(ref:figlab2) **Gaze funnel for adult sample with higher trial number**.
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/gazefunnel_adults.pdf")
+```
+
+## Inference parameter estimates per individual
+As can be seen in Figure \@ref(fig:fig3) and Figure \@ref(fig:fig4), the gaze model estimated the inference parameter for each individual.
+Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty.
+In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.
+
+(ref:figlab3) **Gaze model estimates faceted by individual**.
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/supplements_gazemodel_facetedinference.pdf")
+```
+
+(ref:figlab4) **Gaze model estimates ordered by descending inference parameter value**.
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/supplements_gazemodel_indinference.pdf")
+```
+
+\newpage
+
+# Study 3: Components of gaze understanding
+## Procedure Theory of mind battery
 
@@
 
-\newpage
+## Analysis
+### Animal vs. human faces
 
-## Model comparison
+```{r animal_human}
+mstimuli <- readRDS("../saves/supplements_magnet_mstimuli.rds")
+```
+
+In Study 1 and Study 2, we presented the TANGO [@prein2023tango] with animal characters.
+For Study 3, we exchanged the animals with human faces, modelled in appearance after the local population.
+We decided to do so in order to enhance the social context of this task and to make it more comparable to the Theory of Mind task battery (where there is live interaction with the experimenter).
+To ensure the change from animal to human faces did not notably change children's responses, we conducted an exploratory analysis.
+We conducted a GLMM analysis with the following model structure in `R: click ~ age_scaled + stimuli + symmetric_position + trial_nr + (1 + symmetric_position + trial_nr | subj_id)`; where `stimuli` denoted either human or animal faces.
+The estimate for the fixed effect of `stimuli` was small and the 95% CrI included zero: $\beta$ = `r fixef(mstimuli)["stimulihumans", "Estimate"]`; 95% CrI [`r fixef(mstimuli)["stimulihumans", "Q2.5"]`; `r fixef(mstimuli)["stimulihumans", "Q97.5"]`]).
+Therefore, we concluded that the animal vs.
+human version of the TANGO did not differ substantially.
+
+### Model comparisons
+To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery).
+For example, the model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results below.
 

### 2023-10-04 supplements/supplements.tex
ready for first round of co-author feedback

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \usepackage{setspace}
+\usepackage{float}
 \captionsetup[figure]{font={stretch=1}}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
-  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
+  pdftitle={Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'},
+  pdfauthor={Julia Prein1, Luke Maurits1, Annika Werwach1, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
   pdflang={en-EN},
@@
 
-\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
+\title{Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'}
+\author{Julia Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
 \date{}
@@
 
-\authornote{
-
-Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany.
-E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{*} shared last authorship}
 
@@
 
-\hypertarget{effects-of-trial-type-and-trial-number}{%
-\section{Effects of trial type and trial number}\label{effects-of-trial-type-and-trial-number}}
+\hypertarget{study-1-lifespan}{%
+\section{Study 1: Lifespan}\label{study-1-lifespan}}
 
-Children showed nearly perfect precision in the first training trial.
-As visual access to the target location decreased in the succeeding training trials, imprecision levels increased.
-Within test trials, children's imprecision levels did not vary as a function of trial number.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-\begin{figure}
+\begin{table}[H]
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}{rlrlr}
+\toprule
+Age group & n & Age mean & Age range & Age SD\\
+\midrule
+3 & 19 (7 female) & 3.62 & 3.04 - 3.99 & 0.31\\
+4 & 17 (9 female) & 4.45 & 4.05 - 4.91 & 0.30\\
+5 & 22 (13 female) & 5.56 & 5.08 - 5.99 & 0.31\\
+6 & 24 (16 female) & 6.50 & 6.1 - 6.99 & 0.28\\
+7 & 39 (20 female) & 7.48 & 7.04 - 7.95 & 0.25\\
+\addlinespace
+8 & 41 (20 female) & 8.46 & 8.03 - 8.98 & 0.27\\
+9 & 56 (29 female) & 9.46 & 9.01 - 9.96 & 0.28\\
+10 & 35 (22 female) & 10.49 & 10.01 - 11 & 0.28\\
+11 & 54 (26 female) & 11.43 & 11.01 - 11.96 & 0.28\\
+12 & 43 (19 female) & 12.41 & 12.01 - 12.99 & 0.30\\
+\addlinespace
+13 & 42 (19 female) & 13.50 & 13.09 - 13.99 & 0.27\\
+14 & 20 (14 female) & 14.37 & 14.05 - 14.98 & 0.23\\
+15 & 21 (11 female) & 15.56 & 15.05 - 15.98 & 0.30\\
+16 & 19 (10 female) & 16.51 & 16.17 - 16.97 & 0.24\\
+17 & 19 (10 female) & 17.53 & 17.01 - 17.95 & 0.28\\
+\addlinespace
+18 & 2 (0 female) & 18.00 & 18 - 18 & 0.00\\
+19 & 5 (4 female) & 19.00 & 19 - 19 & 0.00\\
+20 & 40 (25 female) & 23.02 & 20 - 29 & 2.77\\
+30 & 40 (21 female) & 34.42 & 30 - 39 & 3.00\\
+40 & 40 (24 female) & 44.17 & 40 - 49 & 2.92\\
+\addlinespace
+50 & 40 (21 female) & 54.38 & 50 - 59 & 3.04\\
+60 & 40 (21 female) & 63.73 & 60 - 69 & 2.56\\
+70 & 40 (20 female) & 72.75 & 70 - 79 & 2.44\\
+\bottomrule
+\end{tabular}}
+\end{table}
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_trainingtrials}
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+\hypertarget{model-structures}{%
+\subsubsection{Model structures}\label{model-structures}}
+
+In the paper, we reported the following model structures: linear model: \texttt{mean\_imprecision\ \textasciitilde{}\ age\_centered}; quadratic model in \texttt{R:\ mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)}; cubic model: \texttt{mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)\ +\ I(age\_centered\^{}3);} Gaussian process model: \texttt{mean\_imprecision\ \textasciitilde{}\ gp(age\_centered,\ k=50,\ c=5/4,\ scale=TRUE)}.
+Note the additional parameters in the Gaussian process model.
+With the default settings, the underlying Gaussian process maths would get solved exactly.
+By providing the arguments \texttt{k} and \texttt{c}, we use an approximation process.
+The higher the value of k, the better the approximation: we have used \texttt{k=50} for faster processing speed and better diagnostics.
+\texttt{brms} suggests 5/4 as a value for \texttt{c}.
+Adding \texttt{scale=TRUE} is supposed to improve sampling speed and convergence.
+
+Originally, we fitted the models on a trial-by-trial basis with the following structure in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}.
+However, the Gaussian Process model was computationally heavy.
+Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+We then visually compared the model predictions of the original and the simplified models with each other.
+As you can see in Figure \ref{fig:fig1}, results of the two models did not differ notably.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../figures/supplements_lifespan_modelstructure}
 
@@
 
-\caption{\textbf{Imprecision by trial type, split by study version and sample}.
-The x axis represents the trial type.
-The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
-Small dots show the imprecision for each subject in each trial.
-Boxplots (boxes represent first to third quartiles of data; vertical lines indicate the median; horizontal black lines display the range) and a half violin plot show the data distribution.}\label{fig:fig1}
+\caption{\textbf{Comparison between models on a trial- or subject-level}.
+Grey dots show data of each trial.
+Solid lines show the mean predicted developmental trajectory for both models.
+Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).}\label{fig:fig1}
 \end{figure}
 
-\begin{figure}
+\hypertarget{changepoint-analysis}{%
+\subsubsection{Changepoint analysis}\label{changepoint-analysis}}
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_acrosstrials}
+In our Bayesian changepoint analysis, we restricted the model to a constant mean (i.e., a flat line with zero degree polynomial) within each segment, and to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade) to avoid ``overreactions'' to individual outlying data points.
+In a supplementary analysis, we assessed how different parameter settings effected of our changepoint analysis.
+We changed the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When the model had more explorative room, for example, by a greater number of change points, smaller minimum number of data points between change points, higher polynomial order, the model outputs showed more fine-grained change points.
+The exact location of the change points varied slightly.
+Overall, the interpretation stayed the same as the one we reported in the paper.
+While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
+There was a minor change in that elderly adults became slightly more imprecise again.
+If you are interested into the details, please have a look at the file \texttt{supplements\_changepoint\_parameters.html}, which you can find in the GitHub repository in the \texttt{stats} folder.
+
+\hypertarget{study-2-computational-cognitive-model}{%
+\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
+
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
+
+\hypertarget{gaze-model-prediction}{%
+\subsubsection{Gaze model prediction}\label{gaze-model-prediction}}
+
+Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides).
+Since the task is presented on a screen, there is a natural border towards one side.
+Imagine the target lands to the very right side.
+Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now.
+Therefore, the predicted U-shaped pattern should decrease again towards the screen borders.
+For previous reliability analyses (Prein, Kalinke, Haun, \& Bohn, 2023), we had increased the trial number for an adult sample (N = 70; each 30 trials).
+Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \ref{fig:fig2}).
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gazefunnel_adults}
 
@@
 
-\caption{\textbf{Imprecision across test trials, split by study version and sample}.
-The x axis represents trial number.
-The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click.
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center.
-The black dashed regression lines show smooth conditional means based on linear models.
-Small colored dots show the imprecision for each subject in each trial.
-Colored lines connect the trials of each individual.}\label{fig:fig2}
+\caption{\textbf{Gaze funnel for adult sample with higher trial number}.}\label{fig:fig2}
+\end{figure}
+
+\hypertarget{inference-parameter-estimates-per-individual}{%
+\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}}
+
+As can be seen in Figure \ref{fig:fig3} and Figure \ref{fig:fig4}, the gaze model estimated the inference parameter for each individual.
+Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty.
+In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_facetedinference}
+
+}
+
+\caption{\textbf{Gaze model estimates faceted by individual}.}\label{fig:fig3}
+\end{figure}
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_indinference}
+
+}
+
+\caption{\textbf{Gaze model estimates ordered by descending inference parameter value}.}\label{fig:fig4}
 \end{figure}
@@
 
-\hypertarget{webcam-coding-of-the-child-sample}{%
-\section{Webcam coding of the child sample}\label{webcam-coding-of-the-child-sample}}
+\hypertarget{study-3-components-of-gaze-understanding}{%
+\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
 
-\begin{figure}
+\hypertarget{procedure-theory-of-mind-battery}{%
+\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}}
 
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_webcamcoding}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
+\toprule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+\textbf{Task name} & \textbf{Author} & \textbf{Description} & \textbf{Material used} \\
+Diverse Beliefs & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Wellman et al., 1996 & Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it.
+``Here's Linda.
+Linda wants to find her cat.
+Her cat might be hiding in the bushes or it might be hiding in the garage.
+Where do you think the cat is?
+In the bushes or the garage?'' This is the \emph{own-belief} question., If the child chooses the bushes: ``Well, that's a good idea, but Linda thinks her cat is in the garage.
+She thinks her cat is in the garage.'' (or vice versa) Then the child is asked the \emph{target} question: ``So where will Linda look for her cat?
+in the bushes or in the garage?'', To be correct, the child must answer the target question opposite from his/her answer to the \emph{own-belief} question.
+& Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
+Knowledge Access & Wellman \& Liu, 2004 → Pratt \& Bryant (1990), Pillow (1989) & Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
+``Here's a drawer.
+What do you think is inside the drawer?'' (The child can give any answer she/he likes or indicate that she/he does not know).
+Next, the drawer is opened and the child is shown the content of the drawer: ``Let's see\ldots it's really a dog inside!'' Close the drawer: ``Okay, what is in the drawer?'', Then a toy figure of a girl is produced: ``Polly has never ever seen inside this drawer.
+Now here comes Polly.
+So, does Polly know what is inside the drawer?'' (\emph{target} question) ``Did Polly see inside this drawer?'' (\emph{memory} question'', To be correct, the child must answer the target question ``no'' and answer the memory control question ``no''.
+& Toy figure of another girl, Plastic box with drawer, Toy dog \\
+Contents False Belief & Wellman \& Liu, 2004 → Perner, Leekam, \& Wimmer, 1987; see also Wellman et al., 2001 & The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
+``Here's a band-aid box.
+What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: ``Peter has never ever seen inside this band-aid box.
+Now here comes Peter.
+So, what does Peter think is in the box?
+Band-Aids or a pig?
+(the \emph{target} question) `\,`Did Peter see inside this box?'' (the \emph{memory} question).
+To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & Toy figure of a boy, Band-aid box , Toy pig \\
+Explicit False Belief & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Siegal \& Beattie, 1991 & Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
+``Here's Scott.
+Scott wants to find his mittens.
+His mittens might be in his backpack or they might be in the closet.
+Really, Scott's mittens are in his backpack.
+But Scott thinks his mittens are in the closet.'' ``So, where will Scott look for his mittens?
+In his backpack or in the closet?'' (the \emph{target} question) ``Where are Scott's mittens really?
+In his backpack or in the closet?'' (the \emph{reality} question).
+To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\
+Perspective-Taking Level 2 & Flavell et al., 1981 & Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child's side and right side up (or upside down) from the experimenter's.
+The child's task is to indicate in which of these two orientations it appeared to the experimenter (``standing on its feet'' or ``lying on its back'').
+& Picture of a turtle \\
+Perspective-Taking Level 2 & Flavell et al., 1981 & Children are shown a horizontally placed picture of a worm lying between a red blanket and a blue blanket.
+The child was then asked if the worm appeared to the experimenter, seated opposite, to be lying on the red blanket or on the blue blanket.
+& Picture of a worm between two blankets \\
+\end{longtable}
 
-}
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
 
-\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}.
-Factors of parental interference and their influence on the probability of responding correctly.
-The graph shows the estimated density curves of a model's predictor coefficient.
-Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison.
-(A) Analysis on a trial-by-trial level.
-(B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig3}
-\end{figure}
+\hypertarget{animal-vs.-human-faces}{%
+\subsubsection{Animal vs.~human faces}\label{animal-vs.-human-faces}}
 
-Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
-This difference was especially prominent in younger participants in the box version of the task.
-It is conceivable that caregivers were especially prone to influence the behavior of younger children.
-In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
-In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
-Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
-We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
-A trial was defined as the time between two eye blinking sounds.
-We transcribed all utterances by parents and children and counted the words uttered by each.
-We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
-In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
-We conducted a model comparison to estimate the effects of parental interference.
-Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.
+In Study 1 and Study 2, we presented the TANGO (Prein et al., 2023) with animal characters.
+For Study 3, we exchanged the animals with human faces, modelled in appearance after the local population.
+We decided to do so in order to enhance the social context of this task and to make it more comparable to the Theory of Mind task battery (where there is live interaction with the experimenter).
+To ensure the change from animal to human faces did not notably change children's responses, we conducted an exploratory analysis.
+We conducted a GLMM analysis with the following model structure in \texttt{R:\ click\ \textasciitilde{}\ age\_scaled\ +\ stimuli\ +\ symmetric\_position\ +\ trial\_nr\ +\ (1\ +\ symmetric\_position\ +\ trial\_nr\ \textbar{}\ subj\_id)}; where \texttt{stimuli} denoted either human or animal faces.
+The estimate for the fixed effect of \texttt{stimuli} was small and the 95\% CrI included zero: \(\beta\) = 0.16; 95\% CrI {[}-0.06; 0.37{]}).
+Therefore, we concluded that the animal vs.~human version of the TANGO did not differ substantially.
 
-We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
-Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
-Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
-We compared models using WAIC (widely applicable information criterion) scores and weights.
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
-Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
-On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
-In all cases, however, ELPD difference scores were smaller than their standard errors.
-Similarly, 95\% CI of the model estimates included zero and were rather wide.
-Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.
+\hypertarget{model-comparisons}{%
+\subsubsection{Model comparisons}\label{model-comparisons}}
+
+To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery).
+For example, the model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
+The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results below.
 
@@
 \toprule
-Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
+Model & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
 \midrule
-By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
-By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
-By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
-By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
-By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
+Magnet mean (scaled) + Perspective-taking aggregate (scaled) & 200.83 & 16.16 & 0.92 & 0.00 & 0.00\\
+Magnet mean (scaled) & 206.51 & 16.92 & 0.05 & -2.84 & 2.64\\
+Magnet mean (scaled) + ToM aggregate (scaled) & 208.51 & 16.79 & 0.02 & -3.84 & 2.38\\
+Perspective-taking aggregate (scaled) & 212.21 & 15.42 & 0.00 & -5.69 & 2.48\\
+Null model with Age (scaled) & 218.72 & 15.96 & 0.00 & -8.95 & 3.35\\
 \addlinespace
-By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
-By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
-By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
-By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
-By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
-\addlinespace
-By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
-By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
+ToM aggregate (scaled) & 220.52 & 15.83 & 0.00 & -9.85 & 3.09\\
 \bottomrule
@@
 \end{table}
-
-\newpage
-
-\hypertarget{reliability-by-age-group}{%
-\section{Reliability by age group}\label{reliability-by-age-group}}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_reli_byagegroup}
-
-}
-
-\caption{\textbf{Reliability split by age group}.
-(A) Internal consistency (odd-even split) in hedge child sample by age group.
-(B) Test-retest reliability in hedge child sample by age group.
-(C) Internal consistency (odd-even split) in box child sample by age group.
-(D) Test-retest reliability in box child sample by age group.
-For the hedge version, performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
-For the box version, performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target.
-Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}.
-Dots show the performance for each subject.
-The color of data points denotes age group.}\label{fig:fig4}
-\end{figure}
-
-\newpage
-
-\hypertarget{validity}{%
-\section{Validity}\label{validity}}
-
-\hypertarget{social-environmental-factors}{%
-\subsection{Social-environmental factors}\label{social-environmental-factors}}
-
-\hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
-
-We included all children where families filled out a short demographic questionnaire.
-This subsample consisted of 109 children, including 30 3-year-olds (mean = 41.80 months, SD = 3.44, range = 36 - 47),
-36 4-year-olds (mean = 54.19 months, SD = 3.08, range = 48 - 59), and
-43 5-year-olds (mean = 66.28 months, SD = 3.62, range = 60 - 71).
-
-\hypertarget{analysis}{%
-\subsubsection{Analysis}\label{analysis}}
-
-To estimate social environmental influences on gaze understanding, we fitted GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (scaled), data collection mode (reference category: remote unsupervised) and study version (reference category: box version): \texttt{cor\_tango\ \textbar{}\ trials(n\_tango)\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion}).
-In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
-For the target position, we categorized two adjacent bins as one imaginary box.
-To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
-Across the two study versions, we could consequently model the number of participant's correct responses using a \texttt{Binomial} distribution.
-For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
-In addition, we calculated three index scores.
-First, we calculated a sibling variety score according to Peterson (2000).
-Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005).
-Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare.
-We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
-As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
-WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
-
-\hypertarget{results}{%
-\subsubsection{Results}\label{results}}
-
-\begin{table}[H]
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrrr}
-\toprule
-Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
-\midrule
-Age of childcare entry & 571.62 & 28.13 & 0.73 & 0.00 & 0.00\\
-Null model & 575.96 & 30.44 & 0.08 & -2.17 & 4.53\\
-\# Children in household aged 0-18 & 577.60 & 29.63 & 0.04 & -2.99 & 4.74\\
-Peer exposure index & 577.74 & 30.19 & 0.03 & -3.06 & 4.68\\
-\# Children in household aged 1-12 & 578.07 & 29.93 & 0.03 & -3.22 & 4.70\\
-\addlinespace
-Sibling variety score (Cassidy et al., 2005) & 578.13 & 29.87 & 0.03 & -3.25 & 4.67\\
-Sibling variety score (Peterson, 2000) & 578.29 & 29.87 & 0.03 & -3.33 & 4.66\\
-\# Household members & 578.80 & 30.40 & 0.02 & -3.59 & 4.53\\
-Average hours spent in childcare per day & 579.36 & 30.74 & 0.02 & -3.87 & 4.60\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights).
-The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero.
-Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding.
-The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue.
-The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.
-Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).
-
-\begin{table}[H]
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrrrrrr}
-\toprule
-  & n & mean & sd & min & max & skew & kurtosis & se\\
-\midrule
-Age of childcare entry in months & 109 & 14.96 & 5.54 & 1.0 & 40 & 1.72 & 5.65 & 0.53\\
-Average hours spent in childcare per day & 109 & 7.50 & 0.92 & 3.5 & 9 & -0.67 & 1.92 & 0.09\\
-\# Household members & 109 & 3.72 & 0.92 & 2.0 & 7 & 0.30 & 0.49 & 0.09\\
-\# Children in household aged 0-18 & 109 & 0.83 & 0.79 & 0.0 & 4 & 0.87 & 1.09 & 0.08\\
-\# Children in household aged 1-12 & 109 & 0.69 & 0.74 & 0.0 & 4 & 1.23 & 2.67 & 0.07\\
-\addlinespace
-Sibling variety score (Peterson, 2000) & 109 & 0.60 & 0.56 & 0.0 & 2 & 0.23 & -0.87 & 0.05\\
-Sibling variety score (Cassidy et al., 2005) & 109 & 0.63 & 0.54 & 0.0 & 2 & 0.18 & -0.70 & 0.05\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\hypertarget{receptive-vocabulary}{%
-\subsection{Receptive vocabulary}\label{receptive-vocabulary}}
-
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-Our sample consisted of 117 children, including 11 3-year-olds (mean = 45.05 months, SD = 1.58, range = 43 - 47,
-26 4-year-olds (mean = 53.17 months, SD = 3.01, range = 48 - 57),
-32 5-year-olds (mean = 65.80 months, SD = 3.23, range = 61 - 71),\\
-36 6-year-olds (mean = 78.36 months, SD = 3.26, range = 72 - 84), and 12 7-year-olds (mean = 88.11 months, SD = 1.96, range = 84 - 91).
-
-\hypertarget{materials}{%
-\subsubsection{Materials}\label{materials}}
-
-We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022).
-Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).
-
-Each trial presented four pictures: one target word alongside three distractors (1 phonological, 1 semantic, 1 unrelated distractor).
-A verbal prompt asked children to select one of the pictures (prompt: ``Zeige mir {[}target word{]}''; engl.: ``Show me {[}target word{]}'').
-The positioning of the target word and the three distractor types was counterbalanced across the four display positions (upper/lower and left/right corners).
-Children responded by clicking on one of the four pictures.
-The outcome measure consisted of the proportion of correct responses.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/orev_procedure}
-
-}
-
-\caption{Setup of the oREV.
-On each trial, participants heard a word and were asked to select the corresponding picture.
-Verbal prompts could be replayed by pressing the loudspeaker button.}\label{fig:fig5}
-\end{figure}
-
-\hypertarget{procedure}{%
-\subsubsection{Procedure}\label{procedure}}
-
-Families received a personalized study link and completed the study at any location or time they wanted.
-Caregivers were asked to only provide technical support but no further help.
-Webcam recordings were done whenever consented and technically possible.
-We analyzed data of 20 trials per child.
-Children received the trials in two different orders.
-Performance across the two study orders did not differ.
-Hence, we decided to combine the data.
-
-\hypertarget{analysis-1}{%
-\subsubsection{Analysis}\label{analysis-1}}
-
-To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: \texttt{cor\_clt\ \textbar{}\ trials(n\_clt)\ \textasciitilde{}\ age\_centered\ +\ mean\_gaze\_centered}).
-We modelled the number of participant's correct responses using a \texttt{Binomial} distribution.
-
-\hypertarget{results-1}{%
-\subsubsection{Results}\label{results-1}}
-
-\begin{table}[H]
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}{lrrrrr}
-\toprule
-Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
-\midrule
-Age (scaled), TANGO score (scaled) & 570.14 & 26.37 & 0.97 & 0.00 & 0.00\\
-Age (scaled) & 577.22 & 27.11 & 0.03 & -3.54 & 4.15\\
-Null model & 635.80 & 28.71 & 0.00 & -32.83 & 10.61\\
-\bottomrule
-\end{tabular}}
-\end{table}
-
-\newpage
-
-\hypertarget{additional-information-for-the-adult-sample}{%
-\section{Additional information for the adult sample}\label{additional-information-for-the-adult-sample}}
-
-\begin{longtable}{llr}
-\toprule
-Current Country of Residence & studytype & n\\
-\midrule
-\endfirsthead
-\multicolumn{3}{@{}l}{\textit{(continued)}}\\
-\toprule
-Current Country of Residence & studytype & n\\
-\midrule
-\endhead
-
-\endfoot
-\bottomrule
-\endlastfoot
-United Kingdom & vali & 47\\
-South Africa & vali & 8\\
-Portugal & vali & 6\\
-Poland & vali & 5\\
-Ireland & vali & 5\\
-\addlinespace
-Italy & vali & 4\\
-Spain & vali & 4\\
-Netherlands & vali & 4\\
-Canada & vali & 2\\
-Australia & vali & 2\\
-\addlinespace
-France & vali & 2\\
-Austria & vali & 2\\
-Norway & vali & 1\\
-DATA EXPIRED & vali & 1\\
-Finland & vali & 1\\
-\addlinespace
-Greece & vali & 1\\
-Germany & vali & 1\\
-United States & vali & 1\\
-Mexico & vali & 1\\
-South Africa & reli & 48\\
-\addlinespace
-United Kingdom & reli & 19\\
-United States & reli & 14\\
-Portugal & reli & 10\\
-Italy & reli & 7\\
-Canada & reli & 6\\
-\addlinespace
-Spain & reli & 5\\
-Ireland & reli & 5\\
-Poland & reli & 4\\
-Greece & reli & 4\\
-Netherlands & reli & 3\\
-\addlinespace
-CONSENT REVOKED & reli & 3\\
-Germany & reli & 3\\
-Australia & reli & 2\\
-France & reli & 2\\
-Czech Republic & reli & 2\\
-\addlinespace
-Hungary & reli & 2\\
-Chile & reli & 1\\
-Iceland & reli & 1\\
-New Zealand & reli & 1\\*
-\end{longtable}
-
-\hypertarget{recruitment}{%
-\subsection{Recruitment}\label{recruitment}}
-
-We recruited participants using the online participant recruitment service \emph{Prolific} from the University of Oxford.
-\emph{Prolific}'s subject pool consists of a mostly European and US-american sample although subjects from all over the world are included.
-The recruitment platform realises ethical payment of participants, which requires researchers to pay participants a fixed minimum wage of £5.00 (around US\$6.50 or €6.00) per hour.
-We decided to pay all participants the same fixed fee which was in relation to the estimated average time taken to complete the task.
-\emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig.
-Therefore, study data was saved only on our internal servers, while \emph{Prolific} provided demographic information of the participants.
-Participants' \emph{Prolific} ID was forwarded to our study website using URL parameters.
-This way, we could match participant demographic data to our study data.
-The same technique was used to confirm study completion: we redirected participants from our study website back to the \emph{Prolific} website using URL parameters.
-We used \emph{Prolific}'s inbuilt prescreening filter to include only participants who were fluent in English and could therefore properly understand our written and oral study instructions.
-
-\hypertarget{study-1---validation-hedge-version}{%
-\subsection{Study 1 - Validation hedge version}\label{study-1---validation-hedge-version}}
-
-The aim of Study 1 was to validate the hedge version of our gaze understanding task.
-The pre-registration can be found here: \url{https://osf.io/r3bhn}.
-We recruited participants online by advertising the study on \emph{Prolific}.
-
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in May 2021.
-Participants were compensated with £1.25 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-On average, participants took 05:56min to complete the study.
-Participants were required to complete the study on a tablet or desktop.
-Participation on mobile devices was disabled since the display would be too small and would harm click precision.
-It was indicated that the study required audio sound.
-
-We stored \emph{Prolific}'s internal demographic information, while not asking for additional personal information.
-
-\hypertarget{study-2---validation-box-version}{%
-\subsection{Study 2 - Validation box version}\label{study-2---validation-box-version}}
-
-As in study 1, we recruited participants on \emph{Prolific}, and employed the same methodology.
-However, this time we focussed on validating the box version of the task in an adult sample.
-Participants were presented with eight boxes in which the target could land.
-50 adults participated in the study.
-One additional subject returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Data collection took place in June 2021.
-Participants were compensated with £1.00 for completing the study.
-We estimated an average completion time of 6 minutes, resulting in an estimated hourly rate of £10.00.
-On average, participants took 04:43min to complete the study.
-
-\hypertarget{study-3---reliability-hedge-version}{%
-\subsection{Study 3 - Reliability hedge version}\label{study-3---reliability-hedge-version}}
-
-In study 3 and 4, we assessed the test-retest reliability of our gaze understanding task in an adult sample.
-The pre-registration can be found here: \url{https://osf.io/nu62m}.
-We tested the same participants twice with a delay of two weeks.
-The testing conditions were as specified in Study 1 and 2.
-However, the target locations as well as the succession of animals and target colors was randomized once.
-Each participant then received the same fixed randomized order of target location, animal, and target color.
-Participants received 30 test trials without voice-over description, so that each of the ten bins occurred exactly three times.
-
-In addition to the aforementioned prescreening settings, we used a whitelist.
-\emph{Prolific} has a so-called \emph{custom allowlist prescreening filter} where one can enter the \emph{Prolific} IDs of participants who completed a previous study.
-Only these subjects are then invited to participate in a study.
-This way, repeated measurements can be implemented, collecting data from the same subjects at different points in time.
-
-In a first round, 60 participants took part on the first testday.
-Additional two subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-The maximum time is calculated by \emph{Prolific}, based on the estimated average completion time.
-For this study, the maximum time amounted to 41 minutes.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-On average, participants took 07:11min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-On average, participants took 06:36min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional seven subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-Two additional participants timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-On average, participants took 06:51min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 29 subjects finished testday 2.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-On average, participants took 06:26min to complete the second part of the study.
-
-\hypertarget{study-4---reliability-box-version}{%
-\subsection{Study 4 - Reliability box version}\label{study-4---reliability-box-version}}
-
-As in study 3, we recruited participants on \emph{Prolific}, and employed the same methodology.
-However, this time participants were presented with the box version of the task.
-Participants received 32 test trials without voice-over description, so that each of the eight boxes occurred exactly four times.
-As in study 2, we employed eight boxes in which the target could land.
-
-In a first round, 60 participants took part on the first testday.
-Additional five subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-For the first testday, participants were compensated with £1.25.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £8.33.
-On average, participants took 07:33min to complete the first part.
-
-Of the 60 participants that completed testday 1, 41 subjects finished testday 2.
-Participants were compensated with £1.50 for completing the second part of the study.
-We estimated an average completion time of 9 minutes, resulting in an estimated hourly rate of £10.
-On average, participants took 07:50min to complete the second part of the study.
-
-Since we aimed for a minimum sample size of 60 subjects participating on both testdays, we reran the first testday with additional 50 participants.
-Additional eight subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.25 for completing the first part of the study (estimated average completion time 9 minutes, estimated hourly rate of £8.33).
-On average, participants took 07:37min to complete the first part.
-
-Of the additional 50 participants that completed testday 1, 28 subjects finished testday 2.
-Additional three subjects returned their submission, i.e., decided to leave the study early or withdrew their submission after study completion.
-One additional participant timed out, i.e., did not finish the survey within the allowed maximum time.
-Again, participants were compensated with £1.50 for completing the second part of the study (estimated average completion time 9 minutes, estimated hourly rate of £10).
-On average, participants took 06:30min to complete the second part of the study.
-
-\newpage
-
-\hypertarget{instructions-and-voice-over-descriptions}{%
-\section{Instructions and voice-over descriptions}\label{instructions-and-voice-over-descriptions}}
-
-This is the content of our audio recordings that were played as instructions and during voice-over trials.
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
-\toprule()
-\endhead
-\textbf{Timeline} & \textbf{German} & \textbf{English} & \textbf{Filename} \\
-\textbf{welcome} & Hallo!
-Schön, dass du da bist.
-Wir spielen jetzt das Ballon-Spiel!
-Siehst du die Tiere auf dem Bild da?
-Wir möchten gleich zusammen mit den Tieren mit einem Ballon spielen.
-Was genau passiert, erklären wir dir jetzt ganz in Ruhe.
-& Hello!
-Great that you're here.
-We'll now play a balloon game.
-Can you see the animals in the picture over there?
-We want to play together with the animals using the balloon.
-We'll now talk you through exactly what will happen.
-& welcome.mp3 \\
-\textbf{touch} & Schau mal, da steht ein Tier im Fenster.
-Und siehst du den Ballon da?
-Der Ballon fällt immer runter und landet auf dem Boden.
-Und du musst ihn dann finden.
-Das Tier hilft Dir und schaut immer den Ballon an.
-& Look, an animal is standing in the window.
-And can you see the balloon over there?
-The balloon always falls down and lands on the ground.
-And you have to find it!
-The animal helps you and always looks at the balloon.
-& touch-1.mp3 \\
-& Wo ist der Ballon? Drück auf den Ballon! & Where is the balloon? Click on the balloon! & prompt-touch-long.mp3 \\
-\textbf{fam - HEDGE} & Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er hinter eine Hecke.
-Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-& Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon will fall down again.
-This time, it will fall behind a hedge.
-And you have to find it!
-The animal helps you and looks at the balloon.
-& fam-hedge-1.mp3 \\
-& Wo ist der Ballon? Drücke auf die Hecke - wo der Ballon ist. & Where is the balloon? On the hedge, click where the balloon is. & prompt-hedge-long.mp3 \\
-\textbf{fam - BOX} & Klasse, das war super!
-Jetzt spielen wir weiter.
-Siehst du wieder das Tier und den Ballon da?
-Der Ballon fällt wieder runter.
-Diesmal fällt er in eine Kiste.
-Du musst ihn wieder finden.
-Das Tier hilft dir und schaut immer den Ballon an.
-& Perfect, that was great!
-Now, we'll continue playing.
-Can you see the animal and the balloon again?
-The balloon falls down again.
-This time, it falls into a box.
-And you have to find it!
-The animal helps you and looks at the balloon.
-& fam-box-1.mp3 \\
-& Wo ist der Ballon? Drücke auf die Kiste mit dem Ballon. & Where is the balloon? Click on the box with the balloon. & prompt-box-long.mp3 \\
-\textbf{test - HEDGE} & Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Hecke.
-Die Hecke wächst jetzt hoch.
-& Nice, good job!
-Now, we'll continue playing.
-There is the balloon, the animal and the hedge.
-The hedge is growing a bit now.
-& test-hedge-1.mp3 \\
-& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon auf den Boden und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-& The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls to the ground and you have to find it.
-Remember - the animal always looks at the balloon!
-& test-hedge-2.mp3 \\
-& Dann schrumpft die Hecke. Drücke auf die Hecke - wo der Ballon ist. & Now, the hedge is shrinking. On the hedge, click where the balloon is. & test-hedge-3.mp3 \\
-\textbf{test - BOX} & Klasse , das hast du toll gemacht!
-Nun spielen wir weiter.
-Da sind wieder der Ballon, das Tier und die Kisten.
-Jetzt wächst eine Hecke hoch.
-& Nice, good job!
-Now, we'll continue playing.
-There is the balloon and the animal.
-Now, a hedge is growing.
-& test-box-1.mp3 \\
-& Der Ballon ist nun hinter der Hecke.~Du kannst das nicht sehen - das Tier aber!
-Jetzt fällt der Ballon in eine Kiste und du musst ihn wieder finden.
-Denk dran - das Tier schaut immer den Ballon an.
-& The balloon is behind the hedge now.
-You can't see it - but the animal can!
-The balloon falls into a box and you have to find it.
-Remember - the animal always looks at the balloon!
-& test-box-2.mp3 \\
-& Dann schrumpft die Hecke. Drücke auf die Kiste mit dem Ballon. & Now, the hedge is shrinking. Click on the box with the balloon. & test-box-3.mp3 \\
-\textbf{goodbye} & Geschafft!
-Die Tiere sind schon ganz glücklich vom Spielen!
-Vielen Dank für deine Hilfe!
-Bis zum nächsten Mal und liebe Grüße vom Schwein, Affen und Schaf & The animals are super happy after playing.
-Thanks a lot for your help!
-See you soon and goodbye from the pig, monkey and sheep & goodbye.mp3 \\
-\textbf{general prompt} & Wo ist der Ballon? & Where is the balloon? & prompt-general.mp3 \\
-\textbf{touch - no response} & Drück auf den Ballon! & Click on the balloon! & prompt-touch.mp3 \\
-\textbf{hedge - no response} & Drücke auf die Hecke - wo der Ballon ist! & On the hedge, click where the balloon is! & prompt-hedge.mp3 \\
-\textbf{box - no response} & Drücke auf die Kiste mit dem Ballon! & Click on the box with the balloon! & prompt-box.mp3 \\
-\textbf{landing sound of balloon} & - & - & balloon-lands.mp3 \\
-\textbf{sound of blinking eyes} & - & - & blink.mp3 \\
-\textbf{sound for target click} & - & - & positive-feedback.mp3 \\
-\bottomrule()
-\end{longtable}
-
-\newpage
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bohn2022orev}{}}%
-Bohn, M., Prein, J., Delikaya, B., Haun, D. B. M., \& Gagarina, N. (2022). \emph{{oREV}: An {Item Response Theory} based open receptive vocabulary task for 3 to 8-year-old children}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cassidy2005theory}{}}%
-Cassidy, K.
-W., Fineberg, D.
-S., Brown, K., \& Perkins, A.
-(2005).
-Theory of {Mind May Be Contagious}, but {You Don}'t {Catch It} from {Your Twin}.
-\emph{Child Development}, \emph{76}(1), 97--106.
-Retrieved from \url{https://www.jstor.org/stable/3696711}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcelreath2020statistical}{}}%
-McElreath, R. (2020). \emph{Statistical rethinking: {A Bayesian Course} with {Examples} in {R} and {Stan}} (Second). {Chapman and Hall/CRC}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2000kindred}{}}%
-Peterson. (2000). Kindred spirits: {Influences} of siblings' perspectives on theory of mind. \emph{Cognitive Development}, \emph{15}(4), 435--455. \url{https://doi.org/10.1016/S0885-2014(01)00040-5}
+\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
+Prein, J.
+C., Kalinke, S., Haun, D.
+B.
+M., \& Bohn, M.
+(2023).
+{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-023-02159-5}
 

### 2023-10-23 paper/manuscript.Rmd
shortened to 8000 words

@@
   - name          : "Annika Werwach"
-    affiliation   : "1"
+    affiliation   : "3,4"
     role          :
@@
     institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+  - id            : "3"
+    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
+  - id            : "4"
+    institution   : "Max Planck School of Cognition, Leipzig, Germany"
   - id            : "*"
     institution   : "Shared senior authorship"
-authornote: |
-highlights: |
-  Abstract max 250 words
 
 abstract: |
-  Observing eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
-While the emergence of gaze following - on a group level - has been thoroughly studied, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
+  Following eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
+While the emergence of gaze-following has been thoroughly studied on a group level, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
 In Study 1, we examined gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds; children from a mid-sized German city; international remotely tested adults).
@@
 keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
-wordcount         : "xxx max 8000"
+wordcount         : "7909"
 floatsintext      : yes
@@
 
-**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1^, Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
+**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1,3,4^, Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
 
@@
 ^2^ Institute of Psychology, Leuphana University Lüneburg, Germany.
+^3^ Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany.
+^4^ Max Planck School of Cognition, Leipzig, Germany.
 ^\*^ shared senior authorship
@@
 **Data availability statement:** The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analysed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
+The data sets generated during and/or analyzed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
 All experiments were pre-registered (<https://osf.io/zjhsc/>).
@@
 
-**Ethical statement:** The studies were approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+**Ethical statement:**  The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+No.
+2021_45).
 Informed consent was obtained from all individual participants or their legal guardians.
+The research adhered to the legal requirements of psychological research with children in Germany.
 
@@
 # Introduction
-How do humans learn about their environment and navigate their social surroundings?
-A promising approach to extract information from the environment is through following the gaze of others.
-Another's eye gaze can guide us to "informational hotspots" [@meltzoff2010social, p.1] and proves helpful when learning about external objects or surroundings.
-Additionally, eye gaze can be used to identify internal states such as intentions or emotions [@corkum1998origins; @pfeiffer2013gaze], and is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@senju2008gaze; @moore2008development; @tomasello2007reliance; @meltzoff2010social; @bohn2019pervasive; @okumura2017individual; @byers-heinlein2021development; @delbianco2019developmental; @brooks2005development; @emery2000eyes; @stephenson2021gaze].
-
-Existing studies operationalize gaze following as the ability to follow another agent’s line of sight.
-As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy [for review, see @delbianco2019developmental].
-The traditional, often-used paradigm to study gaze following looks as follows [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawaphysiological]: The experimenter sits in front of the infant, with one object to their left and one to the right.
-The experimenter looks directly at the infant before shifting their head and eyes to one of the two objects.
-Infants’ looking times to the potential targets or choices of objects are recorded as dependent variables.
-Analyses traditionally focus on the average age at which children - as a group - reach an above-chance performance (i.e., looking at the gaze-cued target object).
-Research in this tradition finds that infants as young as six months can follow their gaze to that of another agent  [@dentremont1997demonstration].
+Following the gaze of others is valuable to extract information from the environment.
+It guides us to "informational hotspots" [@meltzoff2010social, p.1] and can be used to identify internal states such as intentions or emotions [@corkum1998origins; @pfeiffer2013gaze].
+As one of the most fundamental social-cognitive abilities, gaze-following is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@emery2000eyes; @rakoczy2022foundations; @frith2012mechanisms; @tomasello2003makes; @bohn2019pervasive; @moore2008development; @hessels2020how], and has been extensively studied in infancy [for review, see @delbianco2019developmental].
+In the most commonly used paradigm [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawaphysiological], the experimenter looks directly at the infant before shifting their head and eyes to one of the two objects.
+Infants’ looking times to the target or the proportion of choosing the target over the distractor are measured.
+Analyses traditionally focus on the average age at which children as a group reach an above-chance performance.
+Research in this tradition finds that infants as young as six months can follow gaze to that of another agent [@dentremont1997demonstration].
 At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects; @butterworth1991minds; @corkum1995development].
 
-At first glance, the debate about children’s gaze following abilities seems to be settled: at 12 months of age, children are already competent gaze followers.
-On further view, however, some methodological choices in the experimental paradigms as well as the scope of infants’ abilities seem to offer room for further exploration.
-We see the following challenges: (1) Studies focus on infancy, leaving aside further development in childhood, adolescence and adulthood; (2) Gaze cues are often accompanied by head movements in the same direction [see @delbianco2019developmental], which makes it hard to isolate the referential information extracted from the eyes; (3) Infants’ looking times are usually used as the dependent variable and it is unclear if and how this would translate into active behavior; (4) Presenting two objects drastically limits the complexity of the visual input, especially when compared to our daily, visually cluttered environment; (5) Analyses focus on group-level averages, and we overlook variation in the sample because we cannot measure it with dichotomous outcome variables.
-In the following paragraphs, we will turn to each of these arguments and note how we addressed them consequently in our study.
+While the emergence of gaze-following has been well established, less is known about its developmental trajectory beyond infancy.
+One possibility is that the ability to follow gaze does not improve once it emerges.
+Yet, most, if not all, cognitive abilities continue to develop throughout childhood [e.g., @gathercole2004structure; @gredeback2010development].
+It seems likely that children fine-tune their gaze understanding as they get older - presumably while using them in social interactions.
+To capture development in gaze understanding beyond infancy, we conducted our Study 1 across the lifespan.
 
-First, while the emergence of gaze following has been well established, less is known about the developmental trajectory beyond infancy.
-One possibility is that the ability to follow gaze does not improve further once it emerges.
-Yet, most - if not all - cognitive abilities develop throughout childhood [e.g., working memory, @gathercole2004structure].
-Similarly, visual processing appears to improve with age.
-First longitudinal evidence points to a development in the infant's individual joint attention accuracy and latency [@gredeback2010development].
-It seems likely that children fine-tune the performance of the already existing skills - presumably while using them in social interactions.
-To capture further development in gaze understanding, we therefore conducted our Study 1 across the lifespan.
+Up until today, only a handful of gaze-following studies differentiate between manipulating head and eye movement.
+@michel2021effects found that gaze-following in four-month-olds was likely driven by other's head- instead of eye movements.
+@corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
+From farther distance, body or face orientation can act as more salient cues to determine another's area of attention.
+However, eye direction indicates a more precise location of focus [@emery2000eyes], and allows to anticipate likely future actions [@zohary2022gaze; @friesen2011gaze].
+In our three studies, we therefore focused on subtle gaze cues and isolated eye movement alone.
 
-Second, we see in traditional gaze following studies that the experimenter often shifts their eyes and head in synchrony [e.g., @behne2005oneyearolds; @okumura2017individual] so that children's gaze following could be interpreted as following face direction alone.
-A handful of studies approached this potential confound by separately manipulating head and eye movement.
-@michel2021effects found that gaze following in four-month-olds was likely driven by another's head instead of their eye movement.
-@brooks2002importance implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes [see also @moore1997role].
-Results of @corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
-From farther distance, body or face orientation can act as more salient cues to determine another's area of attention.
-However, eye direction can indicate a more precise location of focus [@emery2000eyes], and allows us to anticipate likely future actions [@zohary2022gaze; @friesen2011gaze].
-Clearly, it is important to differentiate between head and gaze following.
-In our three studies, we focused on subtle gaze cues and isolated eye movement alone.
-
-Third, let us consider the classical response measure of collecting looking times.
-Though previous studies suggest that young infants can align their visual attention to another’s line of sight, it does not necessarily include understanding the intentions or the focus of the agent [cf.
-@aslin2007look].
-Infants could simply align their orientation without processing what exactly the other is seeing [cf.
-Butterworth & Jarrett's ecological and geometric mechanism, @butterworth1991minds].
-In fact, one might ask if such an alignment reflects understanding of visual perspectives at all, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
+Though previous studies suggest that young infants can align their visual attention to another’s line of sight, this does not necessarily indicate understanding the intentions of the agent [@aslin2007look].
+Infants could simply align their orientation without processing what exactly the other is seeing [@butterworth1991minds].
+In fact, one might question if such an alignment reflects an understanding of visual perspectives at all, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
 358].
-To fulfill this criterion, @moll2006level used an active behavioral choice as a response measure.
-Participants had to search for the target object, which was either visually accessible or behind a barrier.
+To fulfill this criterion, @moll2006level applied an active behavioral choice, in which participants searched for a visually accessible or inaccessible target object.
 24-month-olds succeeded in the task, while 18-month-olds did not.
@@
 @povinelli1997exploitation].
-In this paper, we assessed how subtle gaze cues guided participants' behavior in actively locating a target.
+In our three studies, we assessed how subtle gaze cues guided participants' behavior in actively locating a target.
 
-Finally, presenting two objects and focusing on group-level analyses masks individual differences between children in their gaze following abilities.
+Finally, group-level analyses of gaze-following abilities may mask individual differences between children.
 Measuring individual differences in basic aspects of social cognition is especially important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
-In our studies, we measured participants' gaze understanding continuously by using a task which has been designed to capture individual-level variation [@prein2023tango].
+In our studies, we measured gaze understanding continuously by using a task which is designed to capture individual-level variation [@prein2023tango].
 
-## The current study
-
-The present study had two main goals: first, we studied the development of gaze understanding beyond infancy on a group level (Study 1).
-Instead of capturing the youngest age at which children can follow gaze, we wanted to examine how this ability changes with age.
-Even though we found expected developmental patterns - rapid improvement in early childhood; some decline toward old age - we observed substantial variation between individuals at all ages.
-Our second goal was to provide a substantive process-level theory of gaze understanding (and individual differences therein) in the form of a computational model.
-We formalized gaze understanding as a form of vector estimation and showed that our model explained empirical data (Study 2).
-Furthermore, we tested two empirical predictions that followed from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
+The present study had two main goals: first, we studied the development of gaze understanding beyond infancy (Study 1).
+Instead of capturing the youngest age at which children follow gaze, we examined how this ability changes with age.
+Our second goal was to provide a process-level theory of gaze understanding (and individual differences therein) as a computational cognitive model.
+We formalized gaze understanding as a form of vector estimation and tested whether our model explained empirical data (Study 2).
+Finally, we examined two empirical predictions that followed from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
 
@@
 
-We aimed to assess the developmental trajectory of gaze understanding across the lifespan.
 The study was pre-registered at: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
@@
 No.
-2021_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adhered to the legal requirements of psychological research with children in Germany.
+2021_45).
 Data was collected between May 2021 and April 2023.
@@
 
-We collected data online from participants between 3 to 80 years of age (see Supplements for further details).
-The child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants and were recruited via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
+We collected data online from 3- to 80- year-olds (see Supplements for further details).
+The child sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants and was recruited via an internal database of families in Leipzig, Germany, who volunteered to participate in child development studies.
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
@@
 Adults were recruited via *Prolific* [@palan2018prolific].
-*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
+*Prolific* is an online participant recruitment tool from the University of Oxford with predominantly European and US-American subjects.
 Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults who reported to have normal or corrected-to-normal vision.
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour).
+For completing the study, subjects were paid above the fixed minimum wage (~£10.00/hour).
 
@@
 We used the continuous version of the TANGO [@prein2023tango].
-The task was presented as an interactive web application (live demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability for both children and adults (with reliability estimates *Pearson's r* ranging from .7 to .8 for the continuous task version; [@prein2023tango]).
+The task was presented as a web application (demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
+The TANGO showed satisfactory internal consistency and retest reliability for children and adults (reliability estimates *Pearson's r* from .7 to .8; [@prein2023tango]).
 
@@
 Children and teenagers received a personalized link to the study website.
-Caregivers were asked to provide technical support whenever needed, while explicitly being reminded not to help their children in responding.
+Caregivers were asked to provide technical support, while explicitly being reminded not to help in responding.
 Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
@@
 
-Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground (see Figure \@ref(fig:fig4)A; however, please note that Study 1 presented animal agents).
-The target fell behind a hedge while the agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
-In test trials, the target flight was covered so that participants could not see where the target landed.
-Participants were tasked to locate the target by tracking the agent's gaze.
-They could respond by touching or clicking the screen.
+Each trial presented an agent standing in a window, watching a balloon (*i.e.*, target) falling to the ground (see Figure \@ref(fig:fig4)A; however, Study 1 presented animal agents).
+The target fell behind a hedge while the agent's gaze followed the target's trajectory.
+In test trials, a hedge covered the target's position.
+Participants were asked to touch or click where they estimated the target to be based on the agent's gaze.
+Four familiarization trials ensured participants understood the task and felt comfortable with the response format.
+Then, 15 test trials followed.
+Completing 19 trials took 5-10 minutes.
 
-Four familiarization trials ensured that participants understood the task and felt comfortable with the response format.
-Then, 15 test trials followed.
-Completing the 19 trials took approximately 5-10 minutes.
-
-The outcome measure was imprecision, defined as the absolute difference between the target (i.e., balloon) center and the x coordinate of the participant's click.
-The full screen width was divided into ten bins.
-Within each bin, exact target coordinates were randomly generated during runtime.
-Each target bin, as well as all agents and target colors, occurred equally often and did not appear in more than two consecutive trials.
+We measured imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
+The screen width was divided into ten bins.
+Within each bin, exact target coordinates were randomly generated.
+Each target bin, agent, and target color occurred equally often and did not appear in more than two consecutive trials.
 
@@
 We ran all analyses in `r R.version$version.string` [@rcoreteam2022language].
-Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors using the function `brm` from the package `brms` [@burkner2017brms; @burkner2018advanced].
 
-To estimate the effect of age on gaze understanding, we fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship as linear, quadratic, or cubic.
-In addition, we applied a Gaussian Process model [@burkner2017brms] and examined nonlinearity.
-The models predicted imprecision by age (continuous), aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in widths, i.e., a participant with an imprecision of 1 clicked on average one balloon width to the left or right of the true target center.
+We fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship between age and performance as linear, quadratic, or cubic.
+In addition, we fit a Gaussian Process model [@burkner2017brms], which assumes a smooth relationship but avoids enforcing a particular shape.
+Per individuum, imprecision was aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target widths, i.e., an imprecision of 1 meant clicking one balloon width to the left or right of the true target center.
 We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models via model weights and the difference in expected log pointwise predictive density (ELPD) estimated using leave-one-out cross-validation (LOO) [@vehtari2017practicala].
 
-[^1]: Originally, our models were fitted on a trial-by-trial basis and implemented the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
+[^1]: Originally, we fit our models on a trial-by-trial basis with the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
 However, the Gaussian Process model was computationally heavy.
@@
 
-After finding that the developmental change was best described by the Gaussian process model, we performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
-The function `beast.irreg` handled the irregular nature of our series, which did not have the same number of data points for each year in age.
-We were interested in finding the most prominent, most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
-To avoid "overreactions" to individual outlying data points, we constrained the model to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade).
-We inspected the probability of number of change points and the locations of these change points (mean and 95% CrI).[^2]
+To obtain a concise but principled characterization of the developmental trajectory, we additionally performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
+We sought the most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
+To avoid "overreactions" to outlying data points, we constrained the model to have minimally 10 data points between consecutive change points (= half of the data points collected per adult decade).
+We inspected the posterior probability of different numbers of change points and the locations of these change points (mean and 95% CrI).[^2]
 
-[^2]: In a supplementary analysis, we varied the parameters of our changepoint analysis.
-We modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
-When we allowed more explorative room (i.e., greater nr of change points, smaller minimum nr of data points between change points, higher polynomial order), the models became more sensitive and added more fine-grained change points.
+[^2]: In a supplementary analysis, we varied the parameters of our change point analysis and modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When we allowed more explorative room, the models became more sensitive and added more fine-grained change points.
 The exact location of the change points varied slightly.
-However, the overall interpretation stayed the same, fitting our initial visual inspection.
-While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
-There was a minor change in that elderly adults became slightly more imprecise again.
+However, the overall interpretation stayed the same, fitting our initial visual inspection: while early childhood was characterized by much change, adults showed a relatively stable level of imprecision, with a minor decay toward elderly adulthood.
 See Supplements for further detail.
@@
 (ref:figlab1) **Developmental trajectory of gaze understanding across the lifespan**.
-Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
-Grey dots show the mean performance for each subject averaged across trials.
-Blue lines show 100 draws from the expectation of the posterior predictive distribution (i.e., conditional expectation) of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
+Grey dots show the mean level of imprecision (ie., absolute distance between the target's center and the participant's click) for each subject averaged across trials.
+The unit of imprecision is counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+Blue lines show 100 draws from the expectation of the posterior predictive distribution of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
 Vertical, black, dashed lines show the locations of the most prominent changes according to our Bayesian change point analysis.
@@
 High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
-For example, there were some children who were more accurate than the average adult (see Figure \@ref(fig:fig1)).
+We found substantial evidence for a non-linear development in gaze understanding across the lifespan.
+The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model.
+Moreover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`).
+For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.
 
-In our model comparison, we found substantial evidence for a non-linear development in gaze understanding across the lifespan.
-The Gaussian process model was clearly preferred over the cubic, quadratic and linear models due to the highest predictive accuracy according to the LOO ELPD estimates (with negative ELPD differences and more than twice the estimated standard error): elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); and elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model.
-Morover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`).
-For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) and visual inspection indicated nonlinearity (see Figure \@ref(fig:fig1)).
-
-Going one step further, we investigated the most prominent change points in the data.
-The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` (with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability) major shifts in gaze understanding during the lifespan.
-The change points occurred at the following ages: `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]);
-`r lifespan_cps$cp[5]` years (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`]);
-and finally, at `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
-In other words: we found a very rapid initial improvement in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision towards old age.
+The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` major shifts in gaze understanding during the lifespan (MAP estimate with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability).
+The change points occurred at `r lifespan_cps$cp[1]` (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[4]` (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]); `r lifespan_cps$cp[5]` (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`]); and `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
+In short: we found a rapid initial improvement in gaze understanding in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward old age.
 
@@
 
-We investigated the shape of change in gaze understanding across the lifespan.
-One of the major strengths of our study was that we used the same task for all age groups.
-This allowed us to quantitatively compare performance across ages and directly model performance in relation to age.
-We found a non-linear developmental trajectory in gaze understanding: Early in childhood, children quickly enhanced their level of proficiency.
-Performance peaked (i.e., imprecision was lowest) around early adulthood, while there was a minor decay in later adulthood.
-This is consistent with the view that we fine-tune our existing gaze understanding ability after the first emergence in early childhood.
-Furthermore, we observed individual differences in all age groups.
+We investigated the shape of change in gaze understanding across the lifespan and found a non-linear developmental trajectory, in which young children quickly enhanced their level of proficiency.
+Performance peaked around early adulthood, while there was a minor decay in later adulthood.
+This is consistent with the view that humans fine-tune their existing gaze understanding ability after the first emergence in infancy.
+Furthermore, we observed substantial individual differences in all age groups.
 While variation was highest in the three- and four-year-olds, it remained relatively stable across the lifespan.
@@
 Previous studies found that children start to follow gaze in the second half of their first year of life [e.g., @moll200412].
-In our sample, three-year-olds were still rather imprecise in their gaze understanding ability.
+In our sample, three-year-olds were still rather imprecise in their gaze understanding ability (average imprecision was approx.
+two target widths).
 How can we explain this divergence?
-First of all, we used subtle eye movements as cues.
-Many existing studies let the agents move eye and head in parallel [@behne2005oneyearolds; @povinelli1997exploitation], therefore establishing a confound with more salient head movement.
+First, we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel [@behne2005oneyearolds; @povinelli1997exploitation], establishing a confound with the more salient head movement.
 Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation [@carpenter1998social].
-@silverstein2021infants used a similar manipulation of subtle gaze cues without head rotation.
-Interestingly, they found that infants (6- to 18-month-olds) were around or just above chance for gaze following.
-The authors argue that this might be because infants fixate on another's face most of the time, while eye movement alone might not be strong enough to guide their attention.
-Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and then (3) make use of this cue to guide their own behavior (i.e., touching the screen at the cued location).
-We measured an active location choice instead of an attention orientation.
-It is conceivable that three-year-olds followed the agent's gaze but were still learning to translate this understanding into precise, active behavior.
-@moll2013primacy also argue that social forms of perspective-taking evolve prior to visual perspective-taking, which only emerges within the third year of life.
-Children might not be interested in a differential, spatial representation of the surrounding objects: "What is of primary importance to children is to share the world of those around them.
-Precisely how this shared world presents itself from one specific vantage point is secondary and does not become thematic in the very early stages" (p.
-6).
-Taken together, this might explain why some of our younger participants located the agent's gaze rather imprecisely.
+@silverstein2021infants used a similar manipulation of gaze cues without head rotation and found that 6- to 18-month-olds were around or just above chance for gaze-following.
+The authors argue that infants might fixate on another's face most of the time, while eye movement alone might not be strong enough to guide their attention.
+Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and (3) use the cue to guide their own behavior.
+It is conceivable that three-year-olds followed the agent's gaze but did not translate this into precise, active behavior.
+@moll2013primacy argue that social forms of perspective-taking evolve prior to visual perspective-taking, which only emerges within the third year of life.
+Young children might simply not be interested in a differential, spatial representation of the surrounding objects.
+Taken together, this might explain why our younger participants located the agent's gaze rather imprecisely.
 
-Regarding the sample of elderly adults, we expect a sampling bias to be present [@bethlehem2010selection; @gosling2004should; @remillard2014systematic].
-First, certainly not all older people have a working high-speed Internet connection or are knowledgeable and trained in its use.
-Second, it takes a certain amount of independence and motivation to participate in *Prolific* studies.
-The elderly who know how to participate in *Prolific* studies might show greater cognitive fitness and flexibility compared to their offline counterparts.
-Therefore, a representative sample might show a greater age decline in gaze understanding compared to our reported sample.
-In addition, it is noteworthy that older people might be more likely to suffer from visual impairments.
+Regarding our sample of elderly adults, we expect a sampling bias [@bethlehem2010selection; @gosling2004should; @remillard2014systematic].
+First, certainly not all older people have a high-speed internet connection or are knowledgeable in its use.
+Second, it takes motivation to participate in *Prolific* studies.
+The elderly adults participating in *Prolific* studies might show greater cognitive flexibility compared to their offline counterparts.
+Therefore, a representative sample may show a greater age decline in gaze understanding compared to our reported sample.
+In addition, older people might be more likely to suffer from visual impairments.
 Even though we filtered participants to only include normal- to correct-to-normal vision, we cannot guarantee that our participants showed no symptoms of reduced vision.
@@
 The variation between participants was thus likely genuine and not due to random noise.
-Now, we aimed to understand developmental change and variation across participants on a process level.
-We present a theory of gaze understanding that explains how children process the available information (i.e., the agent's eyes) to make inferences about the agent's line of sight and its attentional focus, which leads them to identify the target position.
-We formalized this inference process in a computational cognitive model.
+In Study 2, we aimed to understand the developmental change and individual differences on a process level.
+We present a theory of gaze understanding that explains how participants process the available gaze information to identify the agent's focus.
+We formalized this inference process in a computational cognitive model that replicates a schematic representation of how participants make inferences in the task’s context (i.e., model of the task and not the data).
 
-Computational modeling frameworks allow researchers to establish mechanistic explanations of psychological phenomena [@grahek2021anatomy].
-As formal, mathematical accounts of the psychological process in question, they force researchers to accurately and comprehensively state all their underlying assumptions [@simmering2010dialogue].
-In addition, models can be used to simulate behavior and form testable predictions.
-The expected patterns can then, in turn, be compared to the empirically observed behavior.
-@moore2008development has already argued for systematic, empirical approaches in combination with formal modeling to arrive at a deeper understanding of gaze following.
-
-Here, we seek to explain how participants solved the TANGO.
-We designed a computational cognitive model that replicates a schematic representation of how participants make inferences in the task's context (i.e., model of the task and not the data).
-The fundamental assumption of this gaze model is that participants use the available gaze information to infer the target location.
-
-Task design, data collection, and sample sizes were pre-registered: <https://osf.io/r3bhn>.
-The study design and procedure obtained ethical clearance in the same way as Study 1.
-Data were collected between May and August 2021.
+The study design and procedure obtained ethical clearance in the same way as Study 1 and was pre-registered: <https://osf.io/r3bhn>. Data were collected between May and August 2021.
 
@@
 
-(ref:figlab2) **Gaze model** (A) Visualization of the gaze model.
+A formal definition of our computational cognitive model can be found in the Appendix.
+Broadly summarizing, our gaze model assumes participants to click at a certain point where two estimated gaze vectors meet.
+Each of these gaze vectors implies an estimated pupil angle for each eye that results from connecting the center of the agent’s eyeball and the center of the pupil (see Figure \@ref(fig:fig2)A).
+These angles are sampled from a product of two independent Normal distributions with equal variance, which are centered around the true pupil angles.
+Development of gaze understanding corresponds to a decrease in variance of the Normal distributions and, therefore, a more precise localization of the attentional focus of the agent.
+
+The geometry of our model leads to a testable group-level prediction: the model predicted that TANGO trials vary in difficulty (see Figure \@ref(fig:fig2)B and C): participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.
+If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding.
+In the following, we tested these predictions in children and adults.
+
+(ref:figlab2) **Gaze model** (A) Visualization of the gaze model (simplified, for one eye).
 Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
 Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-Taking the angle between this vector and a line pointing vertically to the ground (black dashed line) yields the pupil angle ($\alpha$).
-Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle ($\alpha$).
-The variance around the Normal distribution ($\sigma_v$) is centered on the true pupil angle and expected to vary between participants.
+The angle between this vector and a line pointing vertically to the ground (black dashed line) is the pupil angle ($\alpha$).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle.
+The variance of the Normal distribution ($\sigma_v$) is expected to vary between participants.
 (B & C) Geometrical features of the gaze model.
-As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location.
-The distribution around the pupil angle from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
+As the pupil angle varies, a fixed amount of uncertainty in the angle corresponds to a varying degree of uncertainty in the estimated target location.
+The distribution around the target location from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
 The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward (C).
@@
 
-Our model quantified a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+## Participants
+
+```{r gazemodel_sample}
+gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
+```
+
+The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
+Children were recruited via an internal database, where each parent previously consented to child development studies, and data was collected in kindergartens in Leipzig, Germany.
+
+In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from Study 1 (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
+Since developmental change was minimal in our adult sample (see Study 1) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
+
+## Procedure
+
+We applied the same procedure as in Study 1.
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
+
+## Analysis
+
+We quantified how well our gaze model explained the gaze understanding process in two ways.
+First, we aggregated the model predictions and data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed correlation to quantify how well the model was able to recover the data.
+Second, we compared the predictions of our gaze model to two simple alternative models that assume participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
+The random guessing model assumed participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
+The center bias model assumed participants always clicked near the screen center and was implemented as sampling from a Normal distribution with the screen center as the mean, and one balloon width as the variance, $\mathcal{N}(960, 160)$.
+Note that the center bias model also predicted imprecision should be higher for targets further out on the screen.
+However, compared to the gaze model, it predicted a steep effect towards the sides, resulting in a V-shaped pattern (imprecision as the distance between the target location and the screen center).
+All cognitive models were implemented in WebPPL [@goodman2014design].
+
+We compared models via the marginal likelihood of the data under each model.
+The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor, which quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
+It can be used to estimate how much more likely the data under one model are compared to the other.
+Bayes Factors implicitly consider model complexity: models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
+
+## Results
+
+```{r gazemodel_results}
+gazemodel_comparison_kids <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
+gazemodel_comparison_adults <- readRDS("../data/gazemodel-adults-comparison-bf.rds")
+gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
+gazemodel_prior <- readRDS("../saves/gazemodel_prior.rds")
+```
+
+We found very clear support for our gaze model, both in children as well as adults.
+A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
+The gaze model predicted a U-shaped pattern which we also observed in our data (see Figure \@ref(fig:fig3)C).
+The model comparison strongly favored our gaze model over the center bias model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_center`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_center`) and the random guessing model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_guess`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_guess`).
+For the child sample, we went one step further into the analysis.
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
+The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
+For children, we estimated the width of the prior's distribution based on the participants' age.
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
+The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
+
+(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
+Grey dots show individual level parameter values.
+The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
+The large black point with 95% HDI shows the mean of the model parameter for the adult sample.
+We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
+(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
+In the child sample, color denotes age in years.
+Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*.
+(C) Pattern recovery.
+Imprecision in target width for each target bin by age group.
+Model predictions in blue; data in grey.
+(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals; only for the child sample).
+
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gazemodel_plot.png")
+```
+
+## Discussion
+
+We presented a formal cognitive model of gaze understanding to describe how gaze understanding develops with age and varies between individuals.
+We modeled gaze understanding as a process in which participants estimate pupil angles based on the pupil location within the eye.
+By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent.
+Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
+We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
+By conducting model comparisons, we ruled out simpler explanations of the data.
+
+In addition, we observed differences in performance depending on gaze location: participant data showed that precision levels dropped as the agent's gaze moved further away from the center.
+Our gaze model predictions recovered this "signature pattern" in the data.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
+
+Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of @michelon2006two: in their Level 1 perspective-taking task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
+Targets closer to the midline were more easily traced than ones further away from the agent.
+The authors concluded that visual acuity is generally higher for locations on the vertical than the diagonal axis ("oblique effect"; [@appelle1972perception; @heeley1997oblique; @mikellidou2015oblique]).
+Not only is the increased imprecision for TANGO trials in which the target lands further out consistent with this finding, but our gaze model poses a viable explanation for this effect.
+
+A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., experiencing motor issues, adding random noise to the click).
+However, we believe imprecise clicking to be of minor concern, since the children in our sample seemed determined in where they clicked and to not have issues with aiming or motor control (see precision in training trials).
+
+A critical feature of our model is that it assumes gaze understanding to rely on vector estimation: subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
+Even though this vector estimation component is a geometrical calculation, one must first interpret the agent's eyes as a relevant social stimulus.
+Therefore, our model describes gaze understanding as a particular form of vector estimation in a social context.
+
+# Study 3: Components of gaze understanding
+
+Study 3 examined the components of gaze understanding and whether it can be fully reduced to physical vector estimation.
+The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underline how gaze understanding is integral to social interaction.
+Therefore, we expected associations between gaze understanding and other measures of social-cognitive abilities.
+
+First, we experimentally isolated the vector estimation component of the TANGO.
+We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
+Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling] and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
+We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze understanding.
+Our reasoning was that similar underlying mechanisms might be needed to solve these tasks since they require participants to take into account another person's point of view.
+
+Data collection was pre-registered (<https://osf.io/xsqkt>) and took place in Leipzig, Germany, between February and March 2023.
+
+## Participants
+
+```{r magnet_sample}
+magnet_sample <- readRDS("../saves/magnet_sample.rds")
+```
+
+The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
+Information on individual socio-economic status was not formally recorded.
+
+## Procedure
+
+Children were tested in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+For maximum control of extraneous participant variables, we employed a within-subjects study design.
+Participants performed the tasks in this order: (1) non-social vector estimation task, (2) ToM task battery, (3) TANGO.
+We decided on a fixed order to compare participants' performance straight-forwardly with each other.
+To increase engagement and decrease fatigue or fuzziness, we switched between tablet tasks and tasks with personal interaction.
+We presented the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the stimuli as "agent-like".
+
+### Non-social vector estimation
+
+Modeling the structure of the TANGO, we designed a non-social vector estimation task.
+This task was presented on a tablet and used the concept of magnetism.
+On the upper part of the screen, there was a tube with a circular window, containing a gearwheel.
+On the floor, there was a magnet.
+The magnet got switched on (with a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
+The gearwheel moved so that its center aligned with the magnet center while staying inside the circular window.
+Participants were then asked to locate the magnet.
+Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
+Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
+Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
+We deliberately decided against displaying an arrow: we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
+In both cases, the starting point of the vector needs to be estimated by the participant.
+With an arrow, we would have drastically reduced the level of uncertainty, since the arrow already displays all information (arrow tip as the "gaze" direction).
+Furthermore, we wanted to avoid referential or iconic stimuli.
+
+Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+We conducted our analysis with 15 test trials (excluding the voice-over trial).
+The outcome variable was imprecision, defined as the absolute distance between the magnet's x coordinate and the x coordinate of the participant's click.
+Magnet coordinates were randomized: The full width of the screen was divided into ten bins; each bin occurred equally often, while the same bin could occur in two consecutive trials; and exact coordinates within each bin were randomly generated.
+
+### ToM task battery
+
+We administered four tasks from the @wellman2004scaling ToM scale (see Supplements for further detail).
+We excluded three tasks: the Diverse Desires task to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (vs.
+"emotional") aspects of social cognition.
+We added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga] with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding, both relying on another's person egocentric frame of reference.
+
+### Gaze understanding
+
+As in Study 1 and 2, we presented children with the TANGO [@prein2023tango].
+To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
+This further highlighted the contrast (i.e., social vs.
+non-social context) to the physical vector estimation task.[^5]
+
+[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
+human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice.
+See Supplements for further detail.
+
+## Analysis
+
+By design, the TANGO and the non-social vector estimation task involved vector estimation.
+Based on our computational model, we expected children's performance in both tasks to correlate with each other.
+For each task, we calculated the mean level of imprecision for each subject and correlated them using *Pearson's* correlation coefficient.
+
+For the ToM battery, we aggregated the score of all solved tasks.
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruited a social-cognitive ability beyond geometric vector estimation, we expected that ToM measures would correlate more strongly with the gaze understanding task than with the non-social vector estimation task.
+(B) If gaze understanding relied purely on task-specific geometric processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficients.
+
+We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function `cocor.dep.groups.overlap` (designed for two dependent overlapping correlations) from the package `cocor` [@diedenhofen2015cocor].
+
+To estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+The outcome variable was modeled by a lognormal distribution.
+We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
+We hypothesized that perspective-taking seemed most closely theoretically related to gaze understanding as in both cases the participant was asked to judge another person's point of view.
+
+## Results
+
+```{r magnet_results}
+magnet_williamsttest_tom <- readRDS("../saves/magnet_williams_tom.rds")
+magnet_williamsttest_perspective <- readRDS("../saves/magnet_williams_perspective.rds")
+magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
+magnet_model <- readRDS("../saves/magnet_winningmodel.rds")
+```
+
+Gaze understanding substantially correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
+Despite the designed overlap in task demands, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
+
+ToM abilities did not correlate with gaze understanding ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x ToM"]`]) or non-social vector estimation ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x ToM"]`]), and the correlations did not differ from each other, Williams' test *t*(`r magnet_williamsttest_tom$parameter`) = `r round(magnet_williamsttest_tom$statistic, 2)`, *p* = `r round(magnet_williamsttest_tom$p.value, 2)`.
+
+Interestingly, gaze understanding and perspective-taking correlated with each other, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
+Please note that the negative correlation can be explained by the measure of imprecision in the TANGO (i.e., the more imprecise gaze understanding, the less perspective-taking).
+Non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+However, according to the Williams' test, the two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
+
+Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]) (see Figure \@ref(fig:fig4)C and Supplements for the model comparison).
+
+(ref:figlab4) **Components of gaze understanding.** (A) Study procedures.
+Top: TANGO (i.e., gaze understanding; social vector estimation).
+Bottom: Magnet (i.e., non-social vector estimation).
+The left-hand side shows screenshots of the familiarization phase; right-hand side shows screenshots of the test phase.
+(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+Dots show the correlation coefficients, error bars represent 95% CIs.
+(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
+The graph shows the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80% CrI, and thinner black lines 95% CrI.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/magnet_plot.png")
+```
+
+## Discussion
+
+Our gaze model assumed vector calculations on a process level.
+By isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
+However, physical vector estimation alone did not suffice to explain variation in gaze understanding.
+Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
+The overall ToM aggregate score did not add explanatory power.
+
+The TANGO and the two perspective-taking tasks can be seen as instances of visuospatial perspective-taking.
+Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
+Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint (Surtees et al., 2013), and can usually be solved independently from another’s agent frame of reference and without mental rotation [not matching the “mentalizing criterion”; @quesque2020theoryofmind].
+In contrast, Level 2 perspective-taking tasks ask participants to judge how (visually or conceptually) the world looks for another person.
+Solving these tasks presumably relies on a simulation of mentally transforming one's own body schema into the space of another agent [@erle2017grounded].
+Participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
+In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
+The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale - while the perspective-taking tasks within our ToM scale fall into the second category.
+
+In the TANGO, participants locate the target by assuming that another agent perceives and looks at the it.
+The here-applied Level 2 perspective-taking tasks add another layer by asking how one's perspective differs from another's and how exactly the other person sees an object.
+@michelon2006two assessed the different processes that participants used to master Level 1 and Level 2 perspective-taking tasks and concluded that participants rely on line-of-sight tracing in the former and perspective transformation in the latter case.
+Line-of-sight tracing consists of locating the avatar and the target, and drawing a line between them.
+Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
+Level 2 perspective-taking requires an additional step in which participants "perform a perspective transformation so that one's imagined position matches the position of the avatar" [@michelon2006two].
+Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
+Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
+
+@surtees2013similarities further differentiated between visual and spatial perspective-taking.
+While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
+Spatial perspective-taking does not necessitate mental states since computing a line of sight does not demand the presence of another agent [@michelon2006two] and can, therefore, be applied to non-agentive objects with a front [@surtees2013similarities].
+This could explain how our participants solved the non-social vector estimation task.
+
+Interestingly, we found weaker correlations between gaze understanding and the other ToM tasks.
+While the ToM tasks and the TANGO shared the social context, the cognitive processes needed to solve each task might vary.
+As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be false or involve aspectual information.
+
+In previous work, we established that the TANGO is suited to capture meaningful variability across individuals [@prein2023tango], which is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: the aggregate score of few dichotomous items is of limited use when it comes to quantifying genuine differences between individuals.
+However, since these tasks are the gold standard in the social-cognitive literature [@rakoczy2022foundations; @poulin-dubois2023discontinuity; @wellman2018theory; @byom2013theory; @bialecka-pikul2021early], and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce [e.g., @beaudoin2020systematic; @mayes1996testretest], we nonetheless relied on them in this study.
+Thus, lower correlations between ToM abilities and gaze understanding may reflect poor measurement characteristics on the side of ToM tasks rather than a genuine absence of association.
+We would like to point out that we already stated this concern in our pre-registration (<https://osf.io/xsqkt>).
+
+If the reliability of the tasks at hand is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation].
+Adjusting for the measurement error would increase the so-called true correlation.
+While we can estimate the split-half reliability for the TANGO and the non-social vector estimation task [@prein2023tango], we do not have reliability estimates of the ToM measures and cannot apply said approaches.
+This, in turn, underlines the importance of reporting the psychometric properties of a task.
+The development of new measures to capture individual differences in social-cognitive abilities seems essential to move this research further.
+
+# General discussion
+
+In three studies, we shed light on the cognitive process underlying gaze understanding and its developmental trajectory across the lifespan.
+Study 1 focused on how gaze understanding changes with age.
+We found a steep learning curve in the preschool years in which children became more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reached their peak performance.
+Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
+Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
+In Study 2, we proposed a computational cognitive model that described gaze understanding at a process level.
+We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate pupil angles.
+To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
+Individuals vary in their levels of uncertainty around these pupil angles.
+Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+Knowing the TANGO to be a reliable individual differences measure, we investigated potential components of gaze understanding in Study 3.
+A fundamental assumption of our computational model was that gaze understanding relies on a vector estimation process.
+We experimentally isolated this component by designing a non-social vector estimation task.
+Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
+We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
+Additionally, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
+
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
+While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
+By studying gaze understanding on a continuum, we assessed not just *whether*, but *how precisely* children locate others’ attentional focus.
+In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
+Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
+
+Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
+Older adults decreased slightly in their precision levels.
+This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
+
+In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
+Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
+The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
+The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
+We found strong evidence for the proposed gaze model when comparing it against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D), both for children and adults.
+Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
+
+In Study 3, we tested the relation between gaze understanding and non-social vector estimation.
+As implied by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
+This ability might be helpful in several social-cognitive tasks, for example, action prediction [@friesen2011gaze], and intention understanding.
+Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
+
+Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the 3D world.
+The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
+We presented the first evidence that this might be the case.
+In Study 3, we administered Level 2 perspective-taking tasks in which participants needed to adapt another person's frame of reference in a real-world social interaction.
+The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.
+real-life interaction).
+Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+Here, however, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground [@bohn2018common; @moll2013primacy; @osborne-crowley2020social].
+A previously shared interaction history might restrict the options we consider potential targets.
+From a modeling perspective, this might be represented as a non-uniform distribution over locations in the visual scenery.
+
+While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
+As seen in @prein2023tango, precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
+Humans likely learn to follow gaze in social interactions [@triesch2006gaze].
+Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
+
+# Limitations
+
+In this paper, we have focused on studying variation across ages and individuals.
+However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta].
+Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals [@nielsen2017persistent].
+First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze-following abilities [@hernik2019infanta].
+While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze understanding holds true across communities.
+Analyzing cross-cultural variation and checking for predicted "signature patterns" in the data will inform our modeling work and theory building in further detail [@amir2020crosscultural].
+
+Moreover, our reported developmental trajectory in gaze understanding relied on a cross-sectional study.
+Longitudinal studies are needed to de-confound it from cohort effects and interpret the correlations between gaze understanding and other social-cognitive abilities.
+
+We applied the same experimental paradigm for children, teenagers and adults alike.
+While this enables a direct comparison in performance across ages, it remains unclear whether the same method measures the same underlying psychological process in humans of different ages [@petersen2023reexamining].
+As we find strong evidence for our computational gaze model in children and adults, we are optimistic that our task is valid throughout the lifespan.
+Furthermore, the testing setup might have influenced different age groups differentially.
+Children and teenagers are likely more trained in using a tablet than the older adults in our sample.
+Recruiting older participants online might also select a particular subgroup of this age range.
+Seventy-year-olds who have working WIFI connections, know how to use a computer, and are registered on *Prolific* might not be representative of their age group.
+We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories toward old age.
+
+Our computational model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
+The model assumes no motor imprecision in this estimation.
+However, younger children could have located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
+This would blur the model's estimation of the inferential component.
+However, in the first training trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels [cf.
+@prein2023tango].
+Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem unlikely.
+
+In Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
+However, a critical feature of the target object differed between the two tasks: in the TANGO, the target (= balloon) moved from the center of the screen to its final position in a self-propelled, continuous way.
+In the non-social vector estimation task, the target (= magnet) stayed stationary on the ground.
+Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
+Second, the starting positions differ: the magnet never appears in the center of the screen.
+Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
+Additionally, in the TANGO, two eyes are presented and information of the two (matching) cues needs to be integrated to infer the target's location.
+In the non-social vector estimation task, only one circular window with a gearwheel inside is presented as a directional cue, and there is no need to integrate two different information sources.
+Future research should investigate how factors like self-propelled movement, sense of agency, spatial layout, and number of information sources influence the mechanisms of gaze understanding.
+
+# Conclusion
+
+In three studies, we have illuminated the development and the mechanisms of gaze understanding.
+We have shown that gaze understanding continues to develop beyond infancy, and that individuals differ in their precision levels to localize the attentional focus of an agent.
+Our proposed process-level theory successfully modeled the mechanisms of gaze understanding and the source of individual differences.
+The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
+
+\newpage
+
+# References
+
+```{=tex}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
+```{=tex}
+\endgroup
+```
+
+\newpage
+
+# Appendix
+
+Our computational model in Study 2 quantified a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
 It is formally defined as:
@@
 where $\theta$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
-The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \@ref(fig:fig2)A).[^3]
+The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \@ref(fig:fig2)A).
 
-[^3]: This model mirrors the logic of the TANGO programming code.
-In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates).
-We then calculated a line between these two points: this was our gaze vector (acting in the functionally same way as a pupil angle).
-Now, knowing the eyeball radius, we calculated the point of intersection at which the gaze vector met the eyeball boundary.
+This model mirrors the logic of the TANGO programming code.
+In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates), and then calculated a line between these two points: this was our gaze vector (acting in the functionally same way as a pupil angle).
+Knowing the eyeball radius, we calculated the point of intersection at which the gaze vector met the eyeball boundary.
 Finally, the agent's pupil moved from the center of the eyeball along the gaze vector to the intersection point.
@@
 
-The second term of the right-hand side equation above, $P(x_c)$, is a prior over potential target locations, which we assumed to be skewed towards the screen center: We anticipated that participants have an a priori expectation that the target will land close to the middle, partly because the target was last visible in the screen center before disappearing behind the hedge, and because the agent was located centrally on the screen.
-We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the center of the screen) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
+$P(x_c)$ is a prior over potential target locations, which we assumed to be skewed towards the screen center: We anticipated that participants have an a priori expectation that the target will land close to the middle, because the target was last visible in the screen center before disappearing behind the hedge and because the agent was located centrally on the screen.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: $P(x_c) \sim \mathcal{N}(960, \sigma^p)$.
 
 The width of this distribution is defined by $\sigma^p$.
-For children, we assumed that the center bias changed with age and we therefore estimated $\sigma^p$ via a linear regression as a function of the child's age ($age_i$): $\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}$.
+For children, we assumed that the center bias changed with age and estimated $\sigma^p$ via a linear regression as a function of the child's age ($age_i$): $\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}$.
 Therefore, the participant-specific distribution for $P(x_c)$ was constrained by the performance in the TANGO and the child's age.
@@
 
-The main inferential task for the participant lied in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
+The main inferential task for the participant lay in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, $P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)$.
 For this, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, $\sigma_v$, centered on the true pupil angles:
@@
 
-Broadly summarizing: Participants were assumed to observe the pupil locations and the center of the agent's eyes.
-Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-Taking the angle between this vector and a line pointing vertically to the ground yields the pupil angle.
-Participants were assumed to sample from Normal distributions centered around the true pupil angle.
-They were assumed to do this independently for the left and right eye and then integrate the information to estimate the target's location.
-
-As $\sigma_v$ determined the level of accuracy with which the participant estimated the pupil angles, it is the component that defines $\theta$.
+As $\sigma_v$ determined the level of accuracy with which participants estimated the pupil angles, it is the component of the model that defines $\theta$.
 When $\sigma_v$ is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.\ When $\sigma_v$ is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
@@
 As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location (see Figure \@ref(fig:fig2)B & C).
-When the agent directs their gaze toward the very left or right side, the distribution around the pupil angle from which participants sample is comparatively wider than when the agent gazes centrally to the ground in front of them.
+When the agent directs their gaze toward the very left or right side, the distribution around the target location from which participants sample is comparatively wider than when the agent gazes centrally to the ground.
 For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
@@
 As $\sigma_v$ decreases and the cone narrows, the extent to which performance varies at different angles decreases.
-Therefore, our gaze model predicted that our trials vary in difficulty: participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.[^4] If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
-Therefore, our gaze model provides a quantitative theory of gaze understanding with testable predictions.
-In the following, we tested these predictions in children and adults.
 
-[^4]: In our screen-based study, this effect should decrease again towards the most outward sides.
+In our screen-based study, this effect should decrease again towards the most outward sides.
 Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
@@
 For further elaboration, see Supplements.
-
-## Participants
-
-```{r gazemodel_sample}
-gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
-```
-
-The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
-Data of children was collected in kindergartens located in Leipzig, Germany.
-The children within each kindergarten were recruited via an internal database, where each parent priorly consented to child development studies.
-
-In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from our Lifespan study (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
-Adults were recruited over *Prolific* [@palan2018prolific].
-Since developmental change was minimal in our adult sample (see Lifespan study) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
-
-## Procedure
-
-We applied exactly the same procedure as in the first study, employing the continuous version of the TANGO [@prein2023tango].
-Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
-Adults participated online.
-
-## Analysis
-
-Our goal was to describe the inferential process of gaze understanding.
-Our analysis focused on the child sample.
-We quantified how well our gaze model explained the gaze understanding process in two ways.
-First, we used correlations to quantify how well the gaze model is able to recover the data.
-For this, we aggregated the model predictions and the data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed the coorrelation between predictions and the data.
-Second, we compared the predictions of our gaze model to two - very simple - alternative models that assume that participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
-The random guessing model assumed that participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
-The center bias model assumed that participants always click at the screen center and was implemented as sampling from a Normal distribution with the the center of the screen as the mean, and one balloon width as the variance, $\mathcal{N}(960, 160)$.
-Note that the center bias model also predicted that imprecision should be higher for targets further out on the screen.
-However, compared to the gaze model, the center bias model predicted a very steep effect towards the sides, resulting in a V-shaped pattern (i.e., imprecision as the distance between the target location and the screen center).
-All cognitive models were implemented in WebPPL [@goodman2014design].
-
-We compared models via the marginal likelihood of the data under each model.
-The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor.
-This factor quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
-It can be used to estimate how much more likely the data under one model are compared to the other.
-Bayes Factors implicitly consider model complexity (i.e., Bayesian Occam's razor): models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
-Details on models, including code to run the models, information about priors for parameter estimation, and Markov chain Monte Carlo settings, can be found in the associated online repository.
-
-## Results
-
-```{r gazemodel_results}
-gazemodel_comparison_kids <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
-gazemodel_comparison_adults <- readRDS("../data/gazemodel-adults-comparison-bf.rds")
-gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
-gazemodel_prior <- readRDS("../saves/gazemodel_prior.rds")
-```
-
-The age effects in Study 2 largely replicated those of Study 1.
-When comparing performance of the three- to five-year-olds in Study 1 and 2, we see a rapid improvement in gaze understanding in early childhood (see Figure \@ref(fig:fig1) inset and \@ref(fig:fig3)A).
-The gaze model's prior over potential target locations assumed that participants would be skewed to click towards the screen center.
-For the children, we estimated the width of the prior's distribution based on the participants' age.
-Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
-The slope of the prior indicated that older children were only marginally less drawn towards the screen center (i.e., marginally wider distribution) compared to the younger children.
-
-We found very clear support for our gaze model, both in children as well as adults.
-A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
-As can be seen in Figure \@ref(fig:fig3)C, the gaze model predicted a U-shaped pattern which we also observed in our data.
-The model comparison strongly favored our gaze model over the center bias model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_center`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_center`) and the random guessing model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_guess`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_guess`).
-For the child sample, we went one step further into the analysis.
-When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were substantially smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
-
-(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
-Grey dots show individual level parameter values.
-The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
-The large black point with 95% HDI presents the mean of the model parameter for the adult sample.
-We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
-(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
-In the child sample, color denotes the age in years.
-Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*.
-(C) Pattern recovery.
-Imprecision in target width for each target bin by age group.
-Model predictions in blue; data in grey.
-(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals; only for the child sample).
-
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/gazemodel_plot.png")
-```
-
-## Discussion
-
-Our findings from Study 1 showed individual differences and a developmental change in gaze understanding across the lifespan.
-To answer what develops with age and how participants differ from one another, we presented a formal cognitive model of gaze understanding.
-
-We modeled gaze understanding as a process in which participants estimate pupil angles based on the pupil location within the eye.
-By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent: the target location.
-Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
-We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
-By conducting model comparisons, we ruled out simpler explanations of the data.
-
-In addition, we observed differences in performance depending on where the agent looks.
-The observed data showed that precision levels dropped as the agent's gaze moved further away from the center.
-Our gaze model predictions recovered this "signature pattern" in the data.
-Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
-
-Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of @michelon2006two: in their Level 1 perspective-taking visibility task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
-Additionally, targets closer to the midline were more easily traced than ones further away from the agent.
-The authors concluded that visual acuity is generally higher for locations on the vertical axis than for those on diagonal axes (cf.
-"oblique effect"; [@appelle1972perception; @heeley1997oblique; @mikellidou2015oblique]).
-Not only is our finding of increased imprecision for greater pupil angles (i.e., trials in which the target lands further out) consistent with this finding, but our gaze model poses a viable explanation for this effect.
-
-A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., wanting to click somewhere but experiencing motor issues at aiming, adding random noise to the click).
-However, the children participating in our study seemed rather determined in where they wanted to click and to not have issues with aiming or motor control (see precision in training trials).
-Therefore, imprecise clicking should not be a great concern.
-
-A critical feature of our model is that it assumes gaze understanding to rely on vector estimation.
-In other words, subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
-Even though this vector estimation component is a rather physical, geometrical calculation, it still happens in a social context.
-For example, one must interpret the agent's eyes as a relevant social stimulus.
-Therefore, our computational model describes gaze understanding as a particular form of vector estimation in a social context.
-In the next study, we tested this prediction.
-
-# Study 3: Components of gaze understanding
-
-Study 3 examined the degree to which vector estimation is a part of gaze understanding.
-Additionally, we investigated whether there is more to gaze understanding than the physical vector estimation component.
-To answer this question, we assessed the relationship between gaze understanding and other social-cognitive abilities.
-We reasoned that gaze understanding is integral to social interaction.
-The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underlines this.
-Therefore, it seemed reasonable to expect correlations between gaze understanding and other measures of social-cognitive abilities.
-
-First, we aimed to experimentally isolate the vector estimation component of the TANGO.
-We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
-Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling], and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
-We aimed to assess whether there are exclusively task-specific processes at hand or whether gaze understanding recruits a general social-cognitive ability that is shared among other social-cognitive tasks.
-We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
-As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze understanding.
-Our reasoning was that similar underlying mechanisms might be needed to solve these tasks, since they ask participants to take into account another person's point of view.
-This way, we aimed to disentangle what components comprise gaze understanding.
-
-Task design, data collection, and sample sizes were pre-registered: <https://osf.io/xsqkt>. Data were collected between February and March 2023.
-
-## Participants
-
-```{r magnet_sample}
-magnet_sample <- readRDS("../saves/magnet_sample.rds")
-```
-
-Testing took place in kindergartens in Leipzig, Germany.
-The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
-Information on individual socio-economic status was not formally recorded.
-
-## Procedure
-
-Children were tested in a quiet room in their kindergarten.
-An experimenter guided the child through the study.
-Since our research questions related to individual differences and we wanted maximum control of extraneous participant variables, we employed a within-subjects study design.
-All participants performed the following tasks in a fixed order: (1) non-social vector estimation task, (2) ToM task battery, (3) TANGO.
-Several reasons motivated this decision.
-First, we decided on a fixed order to be able to compare participants' performance straight-forwardly with each other.
-Second, to increase participant engagement and decrease fatigue or fuzziness, we switched from a tablet task to tasks with personal interaction back to a tablet task.
-Third, we showed the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the presented stimuli as "eye- /agent-like".
-
-### Non-social vector estimation
-
-Modeling the setup and structure of the previously applied TANGO, we designed a non-social vector estimation task.
-This task was also presented as a web application on a tablet and made use of the concept of magnetism.
-The setup looked as follows.
-On the upper part of the screen, there was a tube with a gearwheel located in a circular window.
-On the floor, there was a magnet.
-The magnet then got switched on (making a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
-The gearwheel moved in a way that its center aligned with the center of the magnet, while staying inside the circular window.
-Participants were then asked to locate the magnet.
-Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
-When no information about the magnet location was accessible, participants were expected to use the gearwheel inside the window as a non-social cue to locate the magnet.
-
-As in the TANGO, there were three different trial types depending on the visual access to the true magnet location.
-In full visual access trials, the magnet's location was presented without impediment (i.e., no wooden wall).
-In partial visual access trials, the wooden wall was moved in front of the target after the magnet's location had already been visible.
-In test trials, participants had no visual access to the magnet's location because the wall covered the magnet from the beginning of the trial.
-
-Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
-Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
-In the experimental design process, we decided against using an arrow (or, similarly, a stick or shooting star): we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
-In both cases, the starting point of the vector needs to be estimated by the participant.
-In the case of an arrow, we would have drastically reduced the level of uncertainty and the participants would not have needed to estimate the vector anymore, since the arrow already fully displays all information (with the arrow end as the starting point and arrow tip as the "gaze" direction).
-Furthermore, we wanted to avoid any referential or iconic stimuli.
-
-Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
-The first trial of each type comprised a voice-over description of the presented events.
-We conducted our analysis with 15 test trials (excluding the voice-over trial).
-The outcome variable was imprecision, defined as the absolute difference between the magnet's x coordinate and the x coordinate of the participant's click.
-Magnet coordinates were generated as follows.
-The full width of the screen was divided into ten bins.
-Each bin occurred equally often, while the same bin could occur in two consecutive trials.
-Exact coordinates within each bin were randomly generated.
-
-### ToM task battery
-
-We administered four tasks from the @wellman2004scaling ToM scale (see Supplements for further detail).
-We excluded three tasks: the Diverse Desires task in order to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (as compared to the "emotional") aspects of social cognition.
-Instead, we added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga].
-We added the perspective-taking tasks (1) with the aim of increasing the variability we can capture between individuals, and (2) since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding; both relying on another's person frame of reference.
-
-### Gaze understanding
-
-As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2023tango].
-To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs.
-non-social context) to the non-social vector estimation task.[^5]
-
-[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
-human agents.
-Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs.
-animal).
-See Supplements for further detail.
-
-## Analysis
-
-By design, both the TANGO as well as the non-social vector estimation task involved vector estimation.
-On the basis of the results from our computational cognitive model, we expected that children's performance in both tasks would correlate with each other.
-For each of these two tasks, we calculated the mean level of imprecision for each subject.
-We then correlated these two scores using *Pearson's* correlation coefficients.
-
-For the ToM battery, the dependent variable was the aggregate score of all solved tasks.
-Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruited a general social-cognitive ability beyond vector estimation, we expected that gaze understanding and ToM measures would correlate more strongly with each other than non-social vector estimation and ToM measures.
-(B) If gaze understanding relied purely on task-specific processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
-For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficients.
-
-We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function `cocor.dep.groups.overlap` (designed for two dependent overlapping correlations) from the package `cocor` [@diedenhofen2015cocor].
-
-Furthermore, to estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
-The outcome variable was modeled by a lognormal distribution.
-We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
-As pre-registered, we hypothesized that perspective-taking seemed most closely theoretically related to gaze understanding as in both cases the participant is asked to judge another person's point of view.
-
-## Results
-
-```{r magnet_results}
-magnet_williamsttest_tom <- readRDS("../saves/magnet_williams_tom.rds")
-magnet_williamsttest_perspective <- readRDS("../saves/magnet_williams_perspective.rds")
-magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
-magnet_model <- readRDS("../saves/magnet_winningmodel.rds")
-```
-
-As expected, we found that gaze understanding as a social vector estimation task substantially correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
-Importantly, however, and despite the designed overlap in task demands, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
-
-Gaze understanding and perspective-taking correlated substantially, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
-Please note that the negative correlation can be explained by our outcome measure of imprecision in the TANGO (i.e., the more imprecise gaze understanding, the less perspective-taking).
-Non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
-However, according to the Williams' test, these two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
-
-Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]) (see Figure \@ref(fig:fig4)C).
-See Supplements for further detail of the model comparison.
-
-(ref:figlab4) **Components of gaze understanding.** (A) Study procedures.
-Top: TANGO (i.e., gaze understanding; social vector estimation).
-Bottom: Magnet (i.e., non-social vector estimation).
-Left hand side show screenshots of familiarization phase; right hand side show screenshots of the test phase.
-(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
-Dots show the correlation coefficients, while error bars represent 95% CIs.
-(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
-The graph shows the posterior distributions for the respective predictor.
-Black dots represent means, thicker black lines 80% CrI and thinner black lines 95% CrI.
-
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/magnet_plot.png")
-```
-
-## Discussion
-
-Taken together, the results suggest shows that the TANGO recruited social-cognitive abilities beyond vector estimation.
-Evidently, it shared some of its variance with other level 2 perspective-taking tasks, while the overall ToM aggregate score did not add explanatory power.
-
-By carefully isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
-This is in line with our computational cognitive framework that assumes vector calculations on a process-level.
-However, physical vector estimation alone did not suffice to explain gaze understanding.
-In addition, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
-
-Both the TANGO and the two applied perspective-taking tasks can be seen as instances of *visuospatial perspective-taking.* According to @surtees2013similarities, perspective-taking tasks involve three components: (1) a Self (i.e., the perspective-taker), (2) the Other (i.e., a target perspective that gets judged), and (3) an Object (which is taken into perspective).
-Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
-Level 1 perspective-taking, also termed visual accessibility judgment, is concerned with the visibility of objects from a particular viewpoint.
-In these tasks, participants judge whether an object is located before or behind an agent and if this agent can see it [@surtees2013similarities].
-Usually, participants can solve these tasks independently from another's agent frame of reference and do not need to apply mental rotation (not matching the "mentalizing criterion"; [@quesque2020theoryofmind]).
-Level 2 perspective-taking, however, does rely on a mental transformation of oneself into the space of another agent.
-In these tasks, participants judge how (visually or conceptually) the world looks like for another person or whether an object is to their right or left.
-This presumably entails a simulative transformation of one's own body schema [@erle2017grounded].
-Additionally, participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
-In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
-The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale.
-The two perspective-taking tasks we administered within the ToM scale fall into the second category.
-
-What could drive the connection between the TANGO and the two other perspective-taking tasks?
-Both tasks tap into the ability to judge what another person sees.
-In the TANGO, participants must assume that another agent perceives and looks at the target in order to locate it.
-The here-applied Level 2 perspective-taking tasks add a layer by asking how one's perspective differs from another person's and how exactly the other person sees an object.
-In an intriguing series of experiments, @michelon2006two assessed the different processes that participants used to master Level 1 (visibility of objects) and Level 2 (object's location relative to another agent) perspective-taking tasks.
-Their results suggest that participants rely on line-of-sight tracing in the former case and perspective transformation in the latter case.
-According to @michelon2006two, line-of-sight tracing presumably consists of (1) locating the avatar, (2) locating the target, and (3) drawing a line from the agent to the target.
-Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
-Perspective transformation presumably adds complexity and consists of: "(1) locate the avatar in an egocentric space, (2) perform a perspective transformation so that one's imagined position matches the position of the avatar, (3) locate the target object in the transformed spatial representation of the scene, and (4) read off the coordinates of the object" [@michelon2006two].
-Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
-Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
-
-@surtees2013similarities further differentiate between visual and spatial perspective-taking.
-While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
-Spatial perspective-taking can work without mental states and can, therefore, be applied to non-agentive objects with a front [@surtees2013similarities].
-Interestingly, computing a line of sight does not demand the presence of another agent [@michelon2006two].
-This could explain how our participants solved the non-social vector estimation task.
-
-Interestingly, we found weaker correlations between gaze understanding and the other ToM tasks.
-While ToM tasks and the TANGO share the social context, the cognitive processes needed to solve each task might vary.
-As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
-However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be mutually incompatible, false, or involve fine-grained aspectual information.
-
-In previous work, we established that the TANGO is suited as an individual differences measure [@prein2023tango].
-Capturing meaningful variability in performance is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: they relied on an aggregate score of few dichotomous items.
-The resulting sum scores are of limited use when it comes to quantifying genuine differences between individuals.
-However, since these tasks are the gold standard in the social-cognitive literature [@rakoczy2022foundations; @poulin-dubois2023discontinuity; @wellman2018theory; @byom2013theory; @bialecka-pikul2021early], and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce [e.g., @beaudoin2020systematic; @mayes1996testretest], we nonetheless relied on them in this study.
-Thus, lower correlations between ToM abilities and gaze understanding could reflect poor measurement on the side of ToM tasks rather than a genuine absence of association.
-We would like to point out that we already stated this concern in our pre-registration (<https://osf.io/xsqkt>).
-
-If the reliability of a certain task is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation].
-Adjusting for the measurement error would increase the so-called true correlation.
-While we can estimate the split-half reliability (stratified by target position) for the TANGO and the non-social vector estimation task [e.g., see @prein2023tango], we do not have reliability estimates of the ToM measures.
-Therefore, applying said approaches is unfortunately not feasible to compare correlations between all our applied measures.
-This, in turn, underlines the importance of assessing the psychometric properties of a task and the reporting of such.
-The development of new measures to capture individual differences in social-cognitive abilities like false-belief understanding seems desirable and essential to move this line of research further.
-
-# General discussion
-
-In a series of three studies, we shed light on the developmental trajectory of gaze understanding across the lifespan and the cognitive processes behind it.
-Study 1 focused on how gaze understanding changes with age.
-We found a steep learning curve in the preschool years in which children became more and more precise in locating the attentional focus of an agent.
-During teenage years and early adulthood, participants reached their peak performance.
-Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
-Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
-In Study 2, we proposed a computational cognitive model that described gaze understanding at a process level.
-We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate pupil angles.
-To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
-Individual differences can be represented as varying levels of uncertainty around these pupil angles.
-Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
-Study 3 made use of the case that the TANGO is a reliable individual differences measure to further investigate potential components of gaze understanding.
-One fundamental assumption of our computational cognitive model was that gaze understanding relies on a vector estimation process.
-We experimentally isolated this component by designing a non-social, physical vector estimation task.
-Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
-We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
-In addition, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
-
-The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
-While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
-By studying gaze understanding on a continuum, we could move beyond the pure existence of gaze understanding and assess how precisely children locate an attentional focus.
-Our applied measure allowed us to capture fine-grained individual differences throughout the lifespan.
-In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
-Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
-
-Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
-Older adults decreased slightly in their precision levels.
-This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
-A crucial benefit of this study is that we could use the same experimental paradigm in all age groups.
-This considerably lifts methodological challenges when comparing performance in a given social-cognitive task across ages.
-
-In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
-Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
-We found strong evidence for the proposed gaze model when compared against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D).
-Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
-The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
-The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
-Impressively, we found evidence that the same model performed well for a child as well as an adult sample.
-
-In Study 3, we tested the relation between gaze understanding and non-social vector estimation.
-As implied by the structure of our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
-This ability might be helpful in several social-cognitive tasks, for example, action prediction [@friesen2011gaze], and intention understanding.
-Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
-
-Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the real 3D world.
-The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
-We presented the first evidence that this might be the case.
-In Study 3, we administered a Level 2 perspective-taking task in which participants needed to adapt to another person's frame of reference in a real-world social interaction.
-The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.
-real-life interaction).
-
-Clearly, our real-life environment is visually still more cluttered and diverse than the one presented in our tablet task.
-However, in contrast to our task, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground [@bohn2018common; @moll2013primacy; @osborne-crowley2020social].
-A previously shared interaction history might restrict the options we consider potential targets.
-From a modeling perspective, this might be represented as a non-uniform distribution over locations in the visual scenery.
-
-While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
-As we have previously seen [@prein2023tango], precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
-Humans likely learn to follow gaze in social interactions [@triesch2006gaze].
-Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
-A promising field for future research would be to study the influence of cultural and environmental factors on gaze understanding.
-In addition, a next logical step for studying individual developments in gaze understanding would be longitudinal data collection.
-
-# Limitations
-
-In this project, we have focused on studying variation between individuals and across age groups.
-However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta].
-Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals [@nielsen2017persistent].
-There is first evidence that cultural variation in face-to-face interactions does not influence infants' gaze following abilities [@hernik2019infanta].
-However, we cannot generalize our here-reported developmental trajectory to different socio-environmental and cultural settings, and assume that our presented process model of gaze understanding holds universally true.
-Analysing cross-cultural variation and, for example, checking for predicted "signature patterns" in the data, will inform our modeling work and theory building in further detail [@amir2020crosscultural].
-
-Moreover, is important to note that our estimation of the developmental trajectory in gaze understanding relies on a cross-sectional study.
-Longitudinal studies are needed to gain more confidence in the here-described developmental trajectory and to interpret the correlations between gaze understanding and other social-cognitive abilities.
-
-Furthermore, the testing setup might have influences different age groups differentially.
-It is conceivable that younger children and teenagers are more trained in using a tablet.
-Potentially, the older adults in our sample were not as trained in its use.
-As mentioned in Study 1, recruiting older participants online might also select a particular subgroup of this age range.
-Seventy-year-olds who have working WIFI connections, know how to use a computer and are registered on Prolific might not be representative for their age group.
-We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories towards old age.
-
-Our computational cognitive model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
-The model assumes no motor imprecision in this estimation.
-Clearly, it could be the case that younger children located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
-This would blur the model's estimation of the inferential component.
-An argument that speaks againt motor control issues is children's performance in the training trials.
-In the first trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels [also see Supplements of @prein2023tango].
-Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem therefore very unlikely.
-
-Regarding Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
-However, it is important to note that a critical feature of the target object differed between the two tasks: in the TANGO, the target (= balloon) moved from the center of the screen to its final position in a self-propelled, continuous way.
-In the non-social vector estimation task, the target (=magnet) did not move but stayed stationary on the ground.
-Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
-Second, the starting positions differ: the magnet never appears in the center of the screen.
-Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
-Additionally, in the TANGO, two eyes are presented and information of the two (matching) cues need to be integrated to infer the target's location.
-In the non-social vector estimation task, only one circular window with a gearwheel inside is presented as a directional cue and there is no need to integrate two different information sources.
-Future research could further investigate how factors like self-propelled movement, agency (of the cued target), spatial layout, and number of information sources influence the mechanisms of gaze understanding.
-
-# Conclusion
-
-In three studies, we have illuminated the development and the mechanisms of gaze understanding in further detail.
-We have shown that gaze understanding continues to develop beyond infancy, and that individuals differ in their precision levels to localize the attentional focus of an agent.
-Our proposed process-level theory proved helpful to model the mechanisms of gaze understanding and the source of individual differences.
-The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
-
-\newpage
-
-# Declarations
-
-... can be found on the title page.
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-```{=tex}
-\endgroup
-```

### 2023-10-23 stats/lifespan.Rmd
shortened to 8000 words

@@
 # how many changepoints?
-ibeast$trend$ncp_median
+ibeast$trend$ncp_mode
 
@@
 cps <- tibble(
-          cp = ibeast$trend$cp[1:ibeast$trend$ncp_median], 
-          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,1], 
-          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,2]
+          cp = ibeast$trend$cp[1:ibeast$trend$ncp_mode], 
+          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_mode,1], 
+          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_mode,2]
        )

### 2023-10-23 stats/supplements_changepoint_parameters.Rmd
shortened to 8000 words

@@
 est <- tibble(age = x, data = y, model = ibeast$trend$Y)
-cps <- ibeast$trend$cp[1:ibeast$trend$ncp_median]
+cps <- ibeast$trend$cp[1:ibeast$trend$ncp_mode]
 

### 2023-10-24 paper/manuscript.Rmd
ready for first submission & pre-print

@@
     institution   : "Shared senior authorship" 
-
 abstract: |
@@
 In Study 1, we examined gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds; children from a mid-sized German city; international remotely tested adults).
-We found a steep learning curve during preschool years, in which children become more precise in locating the attentional focus of an agent.
+We found a steep learning curve during preschool years, in which children became more precise in locating the attentional focus of an agent.
 Precision levels then stayed comparably stable throughout adulthood with a minor decline toward old age.
@@
 According to our model, participants estimate pupil angles with varying levels of precision based on observing the pupil location within the agent's eyes.
-In Study 3, we tested two implications of our gaze model, namely that gaze understanding should be related to perspective-taking abilities and vector estimation in non-social settings (*N* = 102 4- to 5-year-olds).
+In Study 3, we tested two implications of our gaze model, namely that gaze understanding could be related to vector estimation in non-social settings and perspective-taking abilities (*N* = 102 4- to 5-year-olds).
 We found that gaze understanding is associated with both of these abilities but less so with other Theory of Mind tasks.
@@
 keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
-wordcount         : "7909"
+wordcount         : "7914"
 floatsintext      : yes
@@
 However, physical vector estimation alone did not suffice to explain variation in gaze understanding.
-Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
+Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO [cf.
+@astor2022gaze].
 The overall ToM aggregate score did not add explanatory power.
@@
 Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
-Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint (Surtees et al., 2013), and can usually be solved independently from another’s agent frame of reference and without mental rotation [not matching the “mentalizing criterion”; @quesque2020theoryofmind].
+Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint [@surtees2013similarities], and can usually be solved independently from another’s agent frame of reference and without mental rotation [not matching the “mentalizing criterion”; @quesque2020theoryofmind].
 In contrast, Level 2 perspective-taking tasks ask participants to judge how (visually or conceptually) the world looks for another person.
@@
 Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals [@nielsen2017persistent].
-First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze-following abilities [@hernik2019infanta].
+First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts [@hernik2019infanta].
 While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze understanding holds true across communities.

### 2024-03-27 paper/manuscript.Rmd
prepare revision

@@
 ---
-title: "Variation in gaze understanding across the life span: A process-level perspective"
-shorttitle: "modeling variation in gaze understanding"
+title: "Variation in gaze following across the life span: A process-level perspective"
+shorttitle: "modeling variation in gaze following"
 author:
@@
   - name          : "Julia Christin Prein"
-    affiliation   : "1"
+    affiliation   : "1,2"
     corresponding : yes    # Define only one corresponding author
@@
   Following eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
-While the emergence of gaze-following has been thoroughly studied on a group level, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
-In Study 1, we examined gaze understanding across the lifespan (*N* = 471 3- to 80-years-olds; children from a mid-sized German city; international remotely tested adults).
-We found a steep learning curve during preschool years, in which children became more precise in locating the attentional focus of an agent.
+While the emergence of gaze following has been thoroughly studied on a group level, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
+In Study 1, we examined gaze following across the lifespan (*N* = 471 3- to 80-year-olds; children from a mid-sized German city; international remotely tested adults).
+We found a steep performance improvement during preschool years, in which children became more precise in locating the attentional focus of an agent.
 Precision levels then stayed comparably stable throughout adulthood with a minor decline toward old age.
-In Study 2, we formalized the process of gaze understanding in a computational cognitive model that allowed us to conceptualize individual differences in a psychologically meaningful way (*N* = 60 3- to 5-year-olds, 50 adults).
+In Study 2, we formalized the process of gaze following in a computational cognitive model that allowed us to conceptualize individual differences in a psychologically meaningful way (*N* = 60 3- to 5-year-olds, 50 adults).
 According to our model, participants estimate pupil angles with varying levels of precision based on observing the pupil location within the agent's eyes.
-In Study 3, we tested two implications of our gaze model, namely that gaze understanding could be related to vector estimation in non-social settings and perspective-taking abilities (*N* = 102 4- to 5-year-olds).
-We found that gaze understanding is associated with both of these abilities but less so with other Theory of Mind tasks.
+In Study 3, we empirically tested how gaze following relates to vector following in non-social settings and perspective-taking abilities (*N* = 102 4- to 5-year-olds).
+We found that gaze following is associated with both of these abilities but less so with other Theory of Mind tasks.
 This work illustrates how the combination of reliable measurement instruments and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
-keywords          : "social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan"
-wordcount         : "7914"
+keywords          : "social-cognitive development, theory of mind, gaze following, individual differences, cognitive modeling, lifespan"
+wordcount         : "X"
 floatsintext      : yes
@@
 draft             : no
-documentclass     : "apa6"
 classoption       : "man"
-output            : papaja::apa6_word
-header-includes   :
+
+header-includes:
   - \usepackage{setspace}
   - \captionsetup[figure]{font={stretch=1}}
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            : papaja::apa6_word
+
 editor_options    : 
@@
 
-# Variation in gaze understanding across the life span: A process-level perspective
+# Variation in gaze following across the life span: A process-level perspective
 
@@
 
-**Data availability statement:** The web application (<https://ccp-odc.eva.mpg.de/tango-demo/>) described here is open source (<https://github.com/ccp-eva/tango-demo>).
-The data sets generated during and/or analyzed during the current study are available in the [gazecues-modeling] repository (<https://github.com/ccp-eva/gazecues-modeling>).
-All experiments were pre-registered (<https://osf.io/zjhsc/>).
+**Data availability statement:** The gaze following task (<https://ccp-odc.eva.mpg.de/tango-demo/>) is open source (<https://github.com/ccp-eva/tango-demo>).
+The data sets generated during and/or analyzed during the current study are available in the following repository (<https://github.com/ccp-eva/gazecues-modeling>).
+All experiments and analyses were pre-registered prior to data collection (<https://osf.io/zjhsc/>).
 
@@
 **Funding:** This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-Manuel Bohn was supported by a Jacobs Foundation Research Fellowship.
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship (grant no.
+2022-1484-00).
 
@@
 
--	Gaze understanding develops beyond infancy. Highest precision levels in localizing attentional foci are reached in young adulthood with a slight decrease towards old age. 
--	We present a computational model as a mechanistic description of gaze understanding. The model explains individual differences and recovers signature patterns in the data.
--	Our model assumes that gaze understanding relies on vector estimation. To test this assumption experimentally, we designed a non-social vector estimation task. 
--	We found substantial correlations between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
+-	Gaze following develops beyond infancy. Highest precision levels in localizing attentional foci are reached in young adulthood with a slight decrease towards old age. 
+-	We present a computational model that describes gaze following as a process of estimating pupil angles and the corresponding gaze vectors. 
+- The model explains individual differences and recovers signature patterns in the data. To estimate the relation between gaze- and vector following, we designed a non-social vector following task. 
+-	We found substantial correlations between gaze following and vector following, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
 
 # Introduction
-Following the gaze of others is valuable to extract information from the environment.
+Following the gaze of others is valuable for extracting information from the environment.
 It guides us to "informational hotspots" [@meltzoff2010social, p.1] and can be used to identify internal states such as intentions or emotions [@corkum1998origins; @pfeiffer2013gaze].
 As one of the most fundamental social-cognitive abilities, gaze-following is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@emery2000eyes; @rakoczy2022foundations; @frith2012mechanisms; @tomasello2003makes; @bohn2019pervasive; @moore2008development; @hessels2020how], and has been extensively studied in infancy [for review, see @delbianco2019developmental].
-In the most commonly used paradigm [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawaphysiological], the experimenter looks directly at the infant before shifting their head and eyes to one of the two objects.
+In the most commonly used paradigm [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawa2022physiological], the experimenter looks directly at the infant before shifting their head and eyes to one of two objects.
 Infants’ looking times to the target or the proportion of choosing the target over the distractor are measured.
-Analyses traditionally focus on the average age at which children as a group reach an above-chance performance.
-Research in this tradition finds that infants as young as six months can follow gaze to that of another agent [@dentremont1997demonstration].
+Research in this tradition finds that infants as young as three to four months can follow the gaze of another agent [@delbianco2019developmental; @dentremont2000perceptual; @dentremont1997demonstration; @astor2021gaze].
+
+Previous research has shown a refinement of gaze-following abilities in a child's first and second year of life [e.g., @astor2021gaze; @butterworth1991minds; @brooks2002importance].
 At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects; @butterworth1991minds; @corkum1995development].
+However, we do not know much about the developmental progression beyond these qualitative milestones.
+One possibility is that the ability to follow gaze does not improve beyond infancy.
+Yet, most, if not all, cognitive abilities continue to develop throughout childhood [e.g., @gathercole2004structure; @gredeback2010development].
+It seems likely that children fine-tune their gaze following as they get older - presumably while using them in social interactions.
+To capture the development in gaze following beyond infancy, Study 1 was included participants from preschool to old age.
 
-While the emergence of gaze-following has been well established, less is known about its developmental trajectory beyond infancy.
-One possibility is that the ability to follow gaze does not improve once it emerges.
-Yet, most, if not all, cognitive abilities continue to develop throughout childhood [e.g., @gathercole2004structure; @gredeback2010development].
-It seems likely that children fine-tune their gaze understanding as they get older - presumably while using them in social interactions.
-To capture development in gaze understanding beyond infancy, we conducted our Study 1 across the lifespan.
-
-Up until today, only a handful of gaze-following studies differentiate between manipulating head and eye movement.
-@michel2021effects found that gaze-following in four-month-olds was likely driven by other's head- instead of eye movements.
+Up until today, only a handful of gaze following studies differentiate between manipulating head and eye movement.
+@michel2021effects found that gaze following in four-month-olds was likely driven by other's head- instead of eye movements.
 @corkum1995development, @lempers1979young, and @lempers1977development suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
 From farther distance, body or face orientation can act as more salient cues to determine another's area of attention.
-However, eye direction indicates a more precise location of focus [@emery2000eyes], and allows to anticipate likely future actions [@zohary2022gaze; @friesen2011gaze].
-In our three studies, we therefore focused on subtle gaze cues and isolated eye movement alone.
+However, eye direction indicates a more precise location of focus [@emery2000eyes; @stiefelhagen2002head; however, see @loomis2008psychophysics for peripheral vision], and allows to anticipate likely future actions [@zohary2022gaze; @friesen2011gaze].
+The three studies included in this work, therefore, focused on subtle gaze cues and isolated eye movement alone.
 
-Though previous studies suggest that young infants can align their visual attention to another’s line of sight, this does not necessarily indicate understanding the intentions of the agent [@aslin2007look].
+Group-level analyses of gaze-following abilities (e.g., average age at which children as a group reach an above-chance performance) may mask individual differences between children.
+Measuring individual differences in basic aspects of social cognition is important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
+Across the three studies, we measured gaze following continuously by using a task that is designed to capture individual-level variation [@prein2023tango]: the TANGO avoids floor and ceiling effects in children and adults and is thus particularly suited to examine how gaze following changes with age.
+
+A promising approach to interpreting individual differences in cognitive abilities is computational cognitive modeling.
+Existing computational models have described gaze following via reinforcement learning [@ishikawa2020learning], as a consequence of goal interference and mapping self-experience onto other agents [@friesen2011gaze] or an interplay of object distances/saliencies and head poses [@lau2004learning; @jasso2006using; @recasens2015they].
+As such, these models focus on the motivation behind gaze following or on situations in which the context (e.g., head orientation, surrounding objects) offers cues to the gaze direction.
+Our goal, however, was to formulate a theory that models how people estimate gaze direction based on the eyes alone (i.e., “literal” gaze following) when no target objects are present [^1] and the other’s head is frontally oriented.
+
+[^1]: As @jasso2006using put it: “There is a general agreement that tests of gaze following in the absence of targets are more stringent than with targets, because that eliminates the possibility that infants are simply following the target’s saliency” (p.
+2).
+
+To our knowledge, there are three views that focus on the eyes alone that conceptualize gaze as (1) a beam, (2) a cone, or (3) a line (alternatively called a vector, ray, or line-of-sight).
+@guterstam2019implicit proposed the idea of gaze as a force-carrying beam.
+This theory, however, focuses on how people's implicit assumptions about the physical properties of an object changes when someone looks at it.
+The idea of gaze as a cone is mostly concerned with the question of how people determine whether someone else looks at them [@horstmann2021examining; @gamer2007you].
+The conception most relevant to the present study sees eye gaze as a line: @yaniv1990heuristics proposed that children extrapolate an imaginary trajectory between the agent and the object to identify the focus of attention (similar to “geometrical” gaze following; [@butterworth1991minds]).
+Anecdotal evidence was already reported by @walker1977perspective, who observed two children pointing their fingers into the air, drawing a line between an agent and an object, and saying, “He sees that” (p.
+354).
+@michelon2006two found that response time in Level 1 visual perspective-taking tasks depends on the distance between the agent and the object (i.e., the length of the line-of-sight).
+Some researchers additionally highlight iris eccentricity, that is, the ratio of the visible sclera on each side of the pupil [@anstis1969perception; @todorovic2006geometrical; @symons2004you].
+@todorovic2006geometrical defined gaze direction as “the vector positioned along the visual axis, pointing from the fovea of the looker through the center of the pupil to the gazed-at spot” (p.
+3550).
+@symons2004you furthermore reasoned that “the perceiver must use the asymmetrical configuration of the dark-white contrast of another individual’s eyes, and trace along two invisible sight-lines to their convergent point, that is, the third part of the triad (e.g., an object or a person)” (p.
+452).
+Based on their finding that adults’ gaze direction sensitivity decreases when only one eye is shown, @symons2004you conclude that information from both eyes must be integrated.
+
+While the previously mentioned conceptualizations focus on the direction of eye gaze, they (A) cannot explain how people differ in their abilities to precisely estimate gaze direction, and (B) are not clearly expressed as formal, mathematical models with explicit assumptions and testable predictions.
+In the words of [@gamer2007you]: “Given the social relevance of determining gaze direction, the psychophysics of gaze is underdeveloped” (p.
+705).
+
+Here, we propose a cognitive model of gaze following, which builds upon the notion of eye gaze as line-of-sight tracing and extends this by explicitly modeling individual differences.
+Our gaze model assumes participants infer the locus of someone’s attention to be where two estimated gaze vectors meet.
+Each of these gaze vectors results from connecting the center of the agent’s eyeball and the center of the pupil.
+Because the center of the eyeball is not directly observable, vector estimation happens with a degree of uncertainty.
+Development of gaze following corresponds to a decrease in uncertainty.
+Individual differences correspond to systematic differences in uncertainty.
+
+By focusing on individual differences, we can further address the relationship between gaze following and other cognitive abilities.
+A longstanding question has been whether gaze following is related to Theory of Mind (ToM) [e.g., @brooks2015connecting].
+@moll2011perspectivetaking have suggested that joint attention (including gaze following) might be seen as “Level 0 perspective-taking”, which provides the foundation for later-emerging, more complex perspective-taking abilities.
+On the other hand, an alignment of infants’ visual attention to another’s gaze does not necessarily indicate understanding the intentions of the agent [@aslin2007look].
 Infants could simply align their orientation without processing what exactly the other is seeing [@butterworth1991minds].
-In fact, one might question if such an alignment reflects an understanding of visual perspectives at all, because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
+In fact, one might question if such an alignment reflects an understanding of visual perspectives at all because the “target” or “object of representation” is not necessarily specified [@perner2003perspective, p.
 358].
-To fulfill this criterion, @moll2006level applied an active behavioral choice, in which participants searched for a visually accessible or inaccessible target object.
-24-month-olds succeeded in the task, while 18-month-olds did not.
-In an object choice study with two containers, @behne2005oneyearolds found that already 14-month-olds used an experimenter's gaze; however, this was again confounded with a congruent face movement [cf.
-@povinelli1997exploitation].
-In our three studies, we assessed how subtle gaze cues guided participants' behavior in actively locating a target.
+Consequently, @astor2022gaze have listed the relationship between gaze following and perspective-taking as one of their five big open questions in gaze following research.
+Therefore, in Study 3, we assessed how gaze following relates to ToM abilities, especially visual perspective-taking.
 
-Finally, group-level analyses of gaze-following abilities may mask individual differences between children.
-Measuring individual differences in basic aspects of social cognition is especially important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
-In our studies, we measured gaze understanding continuously by using a task which is designed to capture individual-level variation [@prein2023tango].
+Taken together, the present study had three main goals: first, we studied the development of gaze following beyond infancy (Study 1).
+Instead of capturing the youngest age at which children follow gaze, we examined how this ability changes with age.
+Our second goal was to provide a process-level theory of gaze following – and, most importantly, individual differences therein.
+We proposed a computational cognitive model, which formalized gaze following as a form of vector following, and tested whether our model explained empirical data (Study 2).
+Third, we examined which (social-)cognitive components comprise gaze following (Study 3).
+Based on our model, we predicted that gaze following should be related to non-social vector following.
+Additionally, we assessed the link between gaze following and ToM measures, with a particular focus on visual perspective-taking.
 
-The present study had two main goals: first, we studied the development of gaze understanding beyond infancy (Study 1).
-Instead of capturing the youngest age at which children follow gaze, we examined how this ability changes with age.
-Our second goal was to provide a process-level theory of gaze understanding (and individual differences therein) as a computational cognitive model.
-We formalized gaze understanding as a form of vector estimation and tested whether our model explained empirical data (Study 2).
-Finally, we examined two empirical predictions that followed from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
+# Study 1: Gaze following across the lifespan
 
-# Study 1: Gaze understanding across the lifespan
-
-The study was pre-registered at: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
-The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+The study was pre-registered prior data collection: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
+The study obtained ethical clearance by the MPG Ethics commission in Munich, Germany, falling under an umbrella ethics application (Appl.
 No.
@@
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
-They lived in an industrialized, urban Central-European context in a mid-size German city (∼600,000 inhabitants; median individual monthly net income approx.
+They lived in an industrialized, urban Central-European context in a mid-size German city (approx.
+600,000 inhabitants; median individual monthly net income approx.
 1,600€ as of 2021).
@@
 The task was presented as a web application (demo [https://ccp-odc.eva.mpg.de/tango-demo/](https://ccp-odc.eva.mpg.de/tango-demo/.); source code <https://github.com/ccp-eva/tango-demo>).
-The TANGO showed satisfactory internal consistency and retest reliability for children and adults (reliability estimates *Pearson's r* from .7 to .8; [@prein2023tango]).
+The TANGO showed satisfactory internal consistency and retest reliability (*Pearson's r* from .7 to .8; @prein2023tango) and no floor or ceiling effects for children and adults.
 
@@
 In addition, we fit a Gaussian Process model [@burkner2017brms], which assumes a smooth relationship but avoids enforcing a particular shape.
-Per individuum, imprecision was aggregated across trials and modeled as a `lognormal` distribution.[^1] The unit of imprecision was counted in target widths, i.e., an imprecision of 1 meant clicking one balloon width to the left or right of the true target center.
+Per individual, imprecision was aggregated across trials and modeled as a `lognormal` distribution.[^2] The unit of imprecision was counted in target widths, i.e., an imprecision of 1 meant clicking one balloon width to the left or right of the true target center.
 We inspected the posterior distributions (mean and 95% Credible Interval (CrI)) for the age estimates and compared models via model weights and the difference in expected log pointwise predictive density (ELPD) estimated using leave-one-out cross-validation (LOO) [@vehtari2017practicala].
 
-[^1]: Originally, we fit our models on a trial-by-trial basis with the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
+[^2]: Originally, we fit our models on a trial-by-trial basis with the following structure: `performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`.
 However, the Gaussian Process model was computationally heavy.
@@
 To obtain a concise but principled characterization of the developmental trajectory, we additionally performed a Bayesian change point analysis, using the package `RBeast` [@zhao2019detecting].
-We sought the most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
+We sought the most likely change points in our data, assuming a constant mean (i.e., a flat line, zero-degree polynomial) within each segment.
 To avoid "overreactions" to outlying data points, we constrained the model to have minimally 10 data points between consecutive change points (= half of the data points collected per adult decade).
-We inspected the posterior probability of different numbers of change points and the locations of these change points (mean and 95% CrI).[^2]
+We inspected the posterior probability of different numbers of change points and the locations of these change points (mean and 95% CrI).[^3]
 
-[^2]: In a supplementary analysis, we varied the parameters of our change point analysis and modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+[^3]: In a supplementary analysis, we varied the parameters of our change point analysis and modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
 When we allowed more explorative room, the models became more sensitive and added more fine-grained change points.
@@
 
-(ref:figlab1) **Developmental trajectory of gaze understanding across the lifespan**.
+(ref:figlab1) **Developmental trajectory of gaze following across the lifespan**.
 Grey dots show the mean level of imprecision (ie., absolute distance between the target's center and the participant's click) for each subject averaged across trials.
@@
 High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
-We found substantial evidence for a non-linear development in gaze understanding across the lifespan.
+We found substantial evidence for a non-linear development in gaze following across the lifespan.
 The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model.
 Moreover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`).
-For the imprecision in gaze understanding, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.
+For the imprecision in gaze following, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.
 
-The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` major shifts in gaze understanding during the lifespan (MAP estimate with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability).
+The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` major shifts in gaze following during the lifespan (MAP estimate with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability).
 The change points occurred at `r lifespan_cps$cp[1]` (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[4]` (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]); `r lifespan_cps$cp[5]` (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`]); and `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
-In short: we found a rapid initial improvement in gaze understanding in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward old age.
+In short: we found a rapid initial improvement in gaze following in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward old age.
 
@@
 
-We investigated the shape of change in gaze understanding across the lifespan and found a non-linear developmental trajectory, in which young children quickly enhanced their level of proficiency.
+We investigated the shape of change in gaze following across the lifespan and found a non-linear developmental trajectory, in which young children quickly enhanced their level of proficiency.
 Performance peaked around early adulthood, while there was a minor decay in later adulthood.
-This is consistent with the view that humans fine-tune their existing gaze understanding ability after the first emergence in infancy.
+These results support the idea that humans fine-tune their existing gaze following ability after the first emergence in infancy.
 Furthermore, we observed substantial individual differences in all age groups.
@@
 
-Previous studies found that children start to follow gaze in the second half of their first year of life [e.g., @moll200412].
-In our sample, three-year-olds were still rather imprecise in their gaze understanding ability (average imprecision was approx.
+Previous studies found that already four-month-olds demonstrate basic gaze-following abilities [@delbianco2019developmental].
+In our sample, three-year-olds were still rather imprecise in their gaze following ability (average imprecision was approx.
 two target widths).
@@
 First, certainly not all older people have a high-speed internet connection or are knowledgeable in its use.
-Second, it takes motivation to participate in *Prolific* studies.
-The elderly adults participating in *Prolific* studies might show greater cognitive flexibility compared to their offline counterparts.
-Therefore, a representative sample may show a greater age decline in gaze understanding compared to our reported sample.
+Second, the elderly adults participating in *Prolific* studies might show greater cognitive flexibility compared to their offline counterparts.
+Therefore, a representative sample may show a greater age decline in gaze following compared to our reported sample.
 In addition, older people might be more likely to suffer from visual impairments.
@@
 
-Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
-The TANGO has previously been shown to reliably capture inter-individual differences in gaze understanding [@prein2023tango].
+Our lifespan study showed that gaze following develops throughout childhood, and variation between individuals appears in all age groups.
+The TANGO has previously been shown to reliably capture inter-individual differences in gaze following [@prein2023tango].
 The variation between participants was thus likely genuine and not due to random noise.
 In Study 2, we aimed to understand the developmental change and individual differences on a process level.
-We present a theory of gaze understanding that explains how participants process the available gaze information to identify the agent's focus.
+We present a theory of gaze following that explains how participants process the available gaze information and trace a line-of-sight to identify the agent's focus.
 We formalized this inference process in a computational cognitive model that replicates a schematic representation of how participants make inferences in the task’s context (i.e., model of the task and not the data).
 
-The study design and procedure obtained ethical clearance in the same way as Study 1 and was pre-registered: <https://osf.io/r3bhn>. Data were collected between May and August 2021.
+The study design and procedure obtained ethical clearance in the same way as Study 1.
+The study and the model were pre-registered prior to data collection: <https://osf.io/r3bhn>.
+Data were collected between May and August 2021.
 
@@
 
-A formal definition of our computational cognitive model can be found in the Appendix.
-Broadly summarizing, our gaze model assumes participants to click at a certain point where two estimated gaze vectors meet.
-Each of these gaze vectors implies an estimated pupil angle for each eye that results from connecting the center of the agent’s eyeball and the center of the pupil (see Figure \@ref(fig:fig2)A).
-These angles are sampled from a product of two independent Normal distributions with equal variance, which are centered around the true pupil angles.
-Development of gaze understanding corresponds to a decrease in variance of the Normal distributions and, therefore, a more precise localization of the attentional focus of the agent.
-
-The geometry of our model leads to a testable group-level prediction: the model predicted that TANGO trials vary in difficulty (see Figure \@ref(fig:fig2)B and C): participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.
-If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
-Therefore, our gaze model provides a quantitative theory of gaze understanding.
-In the following, we tested these predictions in children and adults.
-
-(ref:figlab2) **Gaze model** (A) Visualization of the gaze model (simplified, for one eye).
-Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
-Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
-The angle between this vector and a line pointing vertically to the ground (black dashed line) is the pupil angle ($\alpha$).
-Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle.
-The variance of the Normal distribution ($\sigma_v$) is expected to vary between participants.
-(B & C) Geometrical features of the gaze model.
-As the pupil angle varies, a fixed amount of uncertainty in the angle corresponds to a varying degree of uncertainty in the estimated target location.
-The distribution around the target location from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
-The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward (C).
-
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics("../figures/gazemodel.png")
-```
-
-## Participants
-
-```{r gazemodel_sample}
-gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
-```
-
-The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
-Children were recruited via an internal database, where each parent previously consented to child development studies, and data was collected in kindergartens in Leipzig, Germany.
-
-In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from Study 1 (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
-Since developmental change was minimal in our adult sample (see Study 1) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
-
-## Procedure
-
-We applied the same procedure as in Study 1.
-Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
-Adults participated online.
-
-## Analysis
-
-We quantified how well our gaze model explained the gaze understanding process in two ways.
-First, we aggregated the model predictions and data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed correlation to quantify how well the model was able to recover the data.
-Second, we compared the predictions of our gaze model to two simple alternative models that assume participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
-The random guessing model assumed participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
-The center bias model assumed participants always clicked near the screen center and was implemented as sampling from a Normal distribution with the screen center as the mean, and one balloon width as the variance, $\mathcal{N}(960, 160)$.
-Note that the center bias model also predicted imprecision should be higher for targets further out on the screen.
-However, compared to the gaze model, it predicted a steep effect towards the sides, resulting in a V-shaped pattern (imprecision as the distance between the target location and the screen center).
-All cognitive models were implemented in WebPPL [@goodman2014design].
-
-We compared models via the marginal likelihood of the data under each model.
-The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor, which quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
-It can be used to estimate how much more likely the data under one model are compared to the other.
-Bayes Factors implicitly consider model complexity: models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
-
-## Results
-
-```{r gazemodel_results}
-gazemodel_comparison_kids <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
-gazemodel_comparison_adults <- readRDS("../data/gazemodel-adults-comparison-bf.rds")
-gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
-gazemodel_prior <- readRDS("../saves/gazemodel_prior.rds")
-```
-
-We found very clear support for our gaze model, both in children as well as adults.
-A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
-The gaze model predicted a U-shaped pattern which we also observed in our data (see Figure \@ref(fig:fig3)C).
-The model comparison strongly favored our gaze model over the center bias model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_center`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_center`) and the random guessing model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_guess`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_guess`).
-For the child sample, we went one step further into the analysis.
-When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
-The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
-For children, we estimated the width of the prior's distribution based on the participants' age.
-Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
-The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
-
-(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
-Grey dots show individual level parameter values.
-The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
-The large black point with 95% HDI shows the mean of the model parameter for the adult sample.
-We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
-(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
-In the child sample, color denotes age in years.
-Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*.
-(C) Pattern recovery.
-Imprecision in target width for each target bin by age group.
-Model predictions in blue; data in grey.
-(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals; only for the child sample).
-
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/gazemodel_plot.png")
-```
-
-## Discussion
-
-We presented a formal cognitive model of gaze understanding to describe how gaze understanding develops with age and varies between individuals.
-We modeled gaze understanding as a process in which participants estimate pupil angles based on the pupil location within the eye.
-By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent.
-Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
-We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
-By conducting model comparisons, we ruled out simpler explanations of the data.
-
-In addition, we observed differences in performance depending on gaze location: participant data showed that precision levels dropped as the agent's gaze moved further away from the center.
-Our gaze model predictions recovered this "signature pattern" in the data.
-Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
-
-Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of @michelon2006two: in their Level 1 perspective-taking task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
-Targets closer to the midline were more easily traced than ones further away from the agent.
-The authors concluded that visual acuity is generally higher for locations on the vertical than the diagonal axis ("oblique effect"; [@appelle1972perception; @heeley1997oblique; @mikellidou2015oblique]).
-Not only is the increased imprecision for TANGO trials in which the target lands further out consistent with this finding, but our gaze model poses a viable explanation for this effect.
-
-A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., experiencing motor issues, adding random noise to the click).
-However, we believe imprecise clicking to be of minor concern, since the children in our sample seemed determined in where they clicked and to not have issues with aiming or motor control (see precision in training trials).
-
-A critical feature of our model is that it assumes gaze understanding to rely on vector estimation: subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
-Even though this vector estimation component is a geometrical calculation, one must first interpret the agent's eyes as a relevant social stimulus.
-Therefore, our model describes gaze understanding as a particular form of vector estimation in a social context.
-
-# Study 3: Components of gaze understanding
-
-Study 3 examined the components of gaze understanding and whether it can be fully reduced to physical vector estimation.
-The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underline how gaze understanding is integral to social interaction.
-Therefore, we expected associations between gaze understanding and other measures of social-cognitive abilities.
-
-First, we experimentally isolated the vector estimation component of the TANGO.
-We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
-Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling] and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
-We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
-As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze understanding.
-Our reasoning was that similar underlying mechanisms might be needed to solve these tasks since they require participants to take into account another person's point of view.
-
-Data collection was pre-registered (<https://osf.io/xsqkt>) and took place in Leipzig, Germany, between February and March 2023.
-
-## Participants
-
-```{r magnet_sample}
-magnet_sample <- readRDS("../saves/magnet_sample.rds")
-```
-
-The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
-Information on individual socio-economic status was not formally recorded.
-
-## Procedure
-
-Children were tested in a quiet room in their kindergarten.
-An experimenter guided the child through the study.
-For maximum control of extraneous participant variables, we employed a within-subjects study design.
-Participants performed the tasks in this order: (1) non-social vector estimation task, (2) ToM task battery, (3) TANGO.
-We decided on a fixed order to compare participants' performance straight-forwardly with each other.
-To increase engagement and decrease fatigue or fuzziness, we switched between tablet tasks and tasks with personal interaction.
-We presented the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the stimuli as "agent-like".
-
-### Non-social vector estimation
-
-Modeling the structure of the TANGO, we designed a non-social vector estimation task.
-This task was presented on a tablet and used the concept of magnetism.
-On the upper part of the screen, there was a tube with a circular window, containing a gearwheel.
-On the floor, there was a magnet.
-The magnet got switched on (with a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
-The gearwheel moved so that its center aligned with the magnet center while staying inside the circular window.
-Participants were then asked to locate the magnet.
-Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
-Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
-Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
-We deliberately decided against displaying an arrow: we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
-In both cases, the starting point of the vector needs to be estimated by the participant.
-With an arrow, we would have drastically reduced the level of uncertainty, since the arrow already displays all information (arrow tip as the "gaze" direction).
-Furthermore, we wanted to avoid referential or iconic stimuli.
-
-Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
-The first trial of each type comprised a voice-over description of the presented events.
-We conducted our analysis with 15 test trials (excluding the voice-over trial).
-The outcome variable was imprecision, defined as the absolute distance between the magnet's x coordinate and the x coordinate of the participant's click.
-Magnet coordinates were randomized: The full width of the screen was divided into ten bins; each bin occurred equally often, while the same bin could occur in two consecutive trials; and exact coordinates within each bin were randomly generated.
-
-### ToM task battery
-
-We administered four tasks from the @wellman2004scaling ToM scale (see Supplements for further detail).
-We excluded three tasks: the Diverse Desires task to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (vs.
-"emotional") aspects of social cognition.
-We added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga] with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding, both relying on another's person egocentric frame of reference.
-
-### Gaze understanding
-
-As in Study 1 and 2, we presented children with the TANGO [@prein2023tango].
-To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (<https://osf.io/tdsvc>)).
-This further highlighted the contrast (i.e., social vs.
-non-social context) to the physical vector estimation task.[^5]
-
-[^5]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
-human agents.
-Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice.
-See Supplements for further detail.
-
-## Analysis
-
-By design, the TANGO and the non-social vector estimation task involved vector estimation.
-Based on our computational model, we expected children's performance in both tasks to correlate with each other.
-For each task, we calculated the mean level of imprecision for each subject and correlated them using *Pearson's* correlation coefficient.
-
-For the ToM battery, we aggregated the score of all solved tasks.
-Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruited a social-cognitive ability beyond geometric vector estimation, we expected that ToM measures would correlate more strongly with the gaze understanding task than with the non-social vector estimation task.
-(B) If gaze understanding relied purely on task-specific geometric processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
-For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used *Spearman's* rank correlation coefficients.
-
-We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function `cocor.dep.groups.overlap` (designed for two dependent overlapping correlations) from the package `cocor` [@diedenhofen2015cocor].
-
-To estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
-The outcome variable was modeled by a lognormal distribution.
-We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
-We hypothesized that perspective-taking seemed most closely theoretically related to gaze understanding as in both cases the participant was asked to judge another person's point of view.
-
-## Results
-
-```{r magnet_results}
-magnet_williamsttest_tom <- readRDS("../saves/magnet_williams_tom.rds")
-magnet_williamsttest_perspective <- readRDS("../saves/magnet_williams_perspective.rds")
-magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
-magnet_model <- readRDS("../saves/magnet_winningmodel.rds")
-```
-
-Gaze understanding substantially correlated with the non-social vector estimation task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
-Despite the designed overlap in task demands, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
-
-ToM abilities did not correlate with gaze understanding ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x ToM"]`]) or non-social vector estimation ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x ToM"]`]), and the correlations did not differ from each other, Williams' test *t*(`r magnet_williamsttest_tom$parameter`) = `r round(magnet_williamsttest_tom$statistic, 2)`, *p* = `r round(magnet_williamsttest_tom$p.value, 2)`.
-
-Interestingly, gaze understanding and perspective-taking correlated with each other, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
-Please note that the negative correlation can be explained by the measure of imprecision in the TANGO (i.e., the more imprecise gaze understanding, the less perspective-taking).
-Non-social vector estimation and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
-However, according to the Williams' test, the two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
-
-Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]) (see Figure \@ref(fig:fig4)C and Supplements for the model comparison).
-
-(ref:figlab4) **Components of gaze understanding.** (A) Study procedures.
-Top: TANGO (i.e., gaze understanding; social vector estimation).
-Bottom: Magnet (i.e., non-social vector estimation).
-The left-hand side shows screenshots of the familiarization phase; right-hand side shows screenshots of the test phase.
-(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
-Dots show the correlation coefficients, error bars represent 95% CIs.
-(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
-The graph shows the posterior distributions for the respective predictor.
-Black dots represent means, thicker black lines 80% CrI, and thinner black lines 95% CrI.
-
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/magnet_plot.png")
-```
-
-## Discussion
-
-Our gaze model assumed vector calculations on a process level.
-By isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
-However, physical vector estimation alone did not suffice to explain variation in gaze understanding.
-Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO [cf.
-@astor2022gaze].
-The overall ToM aggregate score did not add explanatory power.
-
-The TANGO and the two perspective-taking tasks can be seen as instances of visuospatial perspective-taking.
-Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
-Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint [@surtees2013similarities], and can usually be solved independently from another’s agent frame of reference and without mental rotation [not matching the “mentalizing criterion”; @quesque2020theoryofmind].
-In contrast, Level 2 perspective-taking tasks ask participants to judge how (visually or conceptually) the world looks for another person.
-Solving these tasks presumably relies on a simulation of mentally transforming one's own body schema into the space of another agent [@erle2017grounded].
-Participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
-In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
-The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale - while the perspective-taking tasks within our ToM scale fall into the second category.
-
-In the TANGO, participants locate the target by assuming that another agent perceives and looks at the it.
-The here-applied Level 2 perspective-taking tasks add another layer by asking how one's perspective differs from another's and how exactly the other person sees an object.
-@michelon2006two assessed the different processes that participants used to master Level 1 and Level 2 perspective-taking tasks and concluded that participants rely on line-of-sight tracing in the former and perspective transformation in the latter case.
-Line-of-sight tracing consists of locating the avatar and the target, and drawing a line between them.
-Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
-Level 2 perspective-taking requires an additional step in which participants "perform a perspective transformation so that one's imagined position matches the position of the avatar" [@michelon2006two].
-Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
-Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
-
-@surtees2013similarities further differentiated between visual and spatial perspective-taking.
-While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
-Spatial perspective-taking does not necessitate mental states since computing a line of sight does not demand the presence of another agent [@michelon2006two] and can, therefore, be applied to non-agentive objects with a front [@surtees2013similarities].
-This could explain how our participants solved the non-social vector estimation task.
-
-Interestingly, we found weaker correlations between gaze understanding and the other ToM tasks.
-While the ToM tasks and the TANGO shared the social context, the cognitive processes needed to solve each task might vary.
-As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
-However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be false or involve aspectual information.
-
-In previous work, we established that the TANGO is suited to capture meaningful variability across individuals [@prein2023tango], which is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
-Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: the aggregate score of few dichotomous items is of limited use when it comes to quantifying genuine differences between individuals.
-However, since these tasks are the gold standard in the social-cognitive literature [@rakoczy2022foundations; @poulin-dubois2023discontinuity; @wellman2018theory; @byom2013theory; @bialecka-pikul2021early], and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce [e.g., @beaudoin2020systematic; @mayes1996testretest], we nonetheless relied on them in this study.
-Thus, lower correlations between ToM abilities and gaze understanding may reflect poor measurement characteristics on the side of ToM tasks rather than a genuine absence of association.
-We would like to point out that we already stated this concern in our pre-registration (<https://osf.io/xsqkt>).
-
-If the reliability of the tasks at hand is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation].
-Adjusting for the measurement error would increase the so-called true correlation.
-While we can estimate the split-half reliability for the TANGO and the non-social vector estimation task [@prein2023tango], we do not have reliability estimates of the ToM measures and cannot apply said approaches.
-This, in turn, underlines the importance of reporting the psychometric properties of a task.
-The development of new measures to capture individual differences in social-cognitive abilities seems essential to move this research further.
-
-# General discussion
-
-In three studies, we shed light on the cognitive process underlying gaze understanding and its developmental trajectory across the lifespan.
-Study 1 focused on how gaze understanding changes with age.
-We found a steep learning curve in the preschool years in which children became more precise in locating the attentional focus of an agent.
-During teenage years and early adulthood, participants reached their peak performance.
-Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
-Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
-In Study 2, we proposed a computational cognitive model that described gaze understanding at a process level.
-We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate pupil angles.
-To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
-Individuals vary in their levels of uncertainty around these pupil angles.
-Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
-Knowing the TANGO to be a reliable individual differences measure, we investigated potential components of gaze understanding in Study 3.
-A fundamental assumption of our computational model was that gaze understanding relies on a vector estimation process.
-We experimentally isolated this component by designing a non-social vector estimation task.
-Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
-We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
-Additionally, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
-
-The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
-While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
-By studying gaze understanding on a continuum, we assessed not just *whether*, but *how precisely* children locate others’ attentional focus.
-In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
-Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
-
-Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
-Older adults decreased slightly in their precision levels.
-This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
-
-In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
-Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \@ref(fig:fig2)A).
-The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
-The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
-We found strong evidence for the proposed gaze model when comparing it against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D), both for children and adults.
-Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
-
-In Study 3, we tested the relation between gaze understanding and non-social vector estimation.
-As implied by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
-This ability might be helpful in several social-cognitive tasks, for example, action prediction [@friesen2011gaze], and intention understanding.
-Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
-
-Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the 3D world.
-The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
-We presented the first evidence that this might be the case.
-In Study 3, we administered Level 2 perspective-taking tasks in which participants needed to adapt another person's frame of reference in a real-world social interaction.
-The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.
-real-life interaction).
-Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
-Here, however, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground [@bohn2018common; @moll2013primacy; @osborne-crowley2020social].
-A previously shared interaction history might restrict the options we consider potential targets.
-From a modeling perspective, this might be represented as a non-uniform distribution over locations in the visual scenery.
-
-While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
-As seen in @prein2023tango, precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
-Humans likely learn to follow gaze in social interactions [@triesch2006gaze].
-Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
-
-# Limitations
-
-In this paper, we have focused on studying variation across ages and individuals.
-However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta].
-Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals [@nielsen2017persistent].
-First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts [@hernik2019infanta].
-While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze understanding holds true across communities.
-Analyzing cross-cultural variation and checking for predicted "signature patterns" in the data will inform our modeling work and theory building in further detail [@amir2020crosscultural].
-
-Moreover, our reported developmental trajectory in gaze understanding relied on a cross-sectional study.
-Longitudinal studies are needed to de-confound it from cohort effects and interpret the correlations between gaze understanding and other social-cognitive abilities.
-
-We applied the same experimental paradigm for children, teenagers and adults alike.
-While this enables a direct comparison in performance across ages, it remains unclear whether the same method measures the same underlying psychological process in humans of different ages [@petersen2023reexamining].
-As we find strong evidence for our computational gaze model in children and adults, we are optimistic that our task is valid throughout the lifespan.
-Furthermore, the testing setup might have influenced different age groups differentially.
-Children and teenagers are likely more trained in using a tablet than the older adults in our sample.
-Recruiting older participants online might also select a particular subgroup of this age range.
-Seventy-year-olds who have working WIFI connections, know how to use a computer, and are registered on *Prolific* might not be representative of their age group.
-We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories toward old age.
-
-Our computational model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
-The model assumes no motor imprecision in this estimation.
-However, younger children could have located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
-This would blur the model's estimation of the inferential component.
-However, in the first training trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels [cf.
-@prein2023tango].
-Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem unlikely.
-
-In Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
-However, a critical feature of the target object differed between the two tasks: in the TANGO, the target (= balloon) moved from the center of the screen to its final position in a self-propelled, continuous way.
-In the non-social vector estimation task, the target (= magnet) stayed stationary on the ground.
-Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
-Second, the starting positions differ: the magnet never appears in the center of the screen.
-Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
-Additionally, in the TANGO, two eyes are presented and information of the two (matching) cues needs to be integrated to infer the target's location.
-In the non-social vector estimation task, only one circular window with a gearwheel inside is presented as a directional cue, and there is no need to integrate two different information sources.
-Future research should investigate how factors like self-propelled movement, sense of agency, spatial layout, and number of information sources influence the mechanisms of gaze understanding.
-
-# Conclusion
-
-In three studies, we have illuminated the development and the mechanisms of gaze understanding.
-We have shown that gaze understanding continues to develop beyond infancy, and that individuals differ in their precision levels to localize the attentional focus of an agent.
-Our proposed process-level theory successfully modeled the mechanisms of gaze understanding and the source of individual differences.
-The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-```{=tex}
-\endgroup
-```
-
-\newpage
-
-# Appendix
-
-Our computational model in Study 2 quantified a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+Our model quantifies a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
 It is formally defined as:
@@
 where $\theta$ is an individual's cognitive ability to locate the focus of the agent's attention, $x_c$ is the coordinate the participant clicked, and $\alpha_l$ and $\alpha_r$ are the pupil angles for the left and right eye, respectively.
-The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \@ref(fig:fig2)A).
+The pupil angle $\alpha$ is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \@ref(fig:fig2)A)[^4].
+Please note that in our case, the center of the pupil is simultaneously the center of the iris (see @anstis2018role for the influence of moving irises, pupils, and corneal reflexes).
 
-This model mirrors the logic of the TANGO programming code.
+[^4]: This model mirrors the logic of the TANGO programming code.
 In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates), and then calculated a line between these two points: this was our gaze vector (acting in the functionally same way as a pupil angle).
@@
 
-In our screen-based study, this effect should decrease again towards the most outward sides.
+Our gaze model consequently predicted that TANGO trials vary in difficulty (see Figure \@ref(fig:fig2)B and C): participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern[^5].
+If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze following.
+In the following, we tested these predictions in children and adults.
+
+[^5]: In our screen-based study, this effect should decrease again towards the most outward sides.
 Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
@@
 For further elaboration, see Supplements.
+
+(ref:figlab2) **Gaze model** (A) Visualization of the gaze model (simplified, for one eye).
+Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point (line-of-sight).
+The angle between this vector and a line pointing vertically to the ground (black dashed line) is the pupil angle ($\alpha$).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle.
+The variance of the Normal distribution ($\sigma_v$) is expected to vary between participants.
+(B & C) Geometrical features of the gaze model.
+As the pupil angle varies, a fixed amount of uncertainty in the angle corresponds to a varying degree of uncertainty in the estimated target location.
+The distribution around the target location from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
+The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward (C).
+
+```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
+knitr::include_graphics("../figures/gazemodel.png")
+```
+
+## Participants
+
+```{r gazemodel_sample}
+gazemodel_sample <- readRDS("../saves/gazemodel_sample.rds")
+```
+
+The sample consisted of `r sum(gazemodel_sample$n_total[gazemodel_sample$age_group < 6])` children, including `r gazemodel_sample$n_total[gazemodel_sample$age_group == 3]` three-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 3]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 3]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 3]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 3]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 3]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 4]` four-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 4]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 4]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 4]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 4]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 4]` girls), `r gazemodel_sample$n_total[gazemodel_sample$age_group == 5]` five-year-olds (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 5]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 5]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 5]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 5]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 5]` girls).
+Children were recruited via an internal database, where each parent previously consented to child development studies, and data was collected in kindergartens in Leipzig, Germany.
+
+In addition, we included `r gazemodel_sample$n_total[gazemodel_sample$age_group == 18]` adults from Study 1 (mean age = `r gazemodel_sample$age_mean[gazemodel_sample$age_group == 18]` years, SD = `r gazemodel_sample$age_sd[gazemodel_sample$age_group == 18]`, range = `r gazemodel_sample$age_min[gazemodel_sample$age_group == 18]` - `r gazemodel_sample$age_max[gazemodel_sample$age_group == 18]`, `r gazemodel_sample$n_females[gazemodel_sample$age_group == 18]` female).
+Since developmental change was minimal in our adult sample (see Study 1) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
+
+## Procedure
+
+We applied the same procedure as in Study 1.
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
+
+## Analysis
+
+We quantified how well our gaze model explained the gaze following process in two ways.
+First, we aggregated the model predictions and data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed correlation to quantify how well the model was able to recover the data.
+Second, we compared the predictions of our gaze model to two simple alternative models that assume participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
+The random guessing model assumed participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, $\mathcal{U}(0, 1920)$.
+The center bias model assumed participants always clicked near the screen center and was implemented as sampling from a Normal distribution with the screen center as the mean, and one balloon width as the variance, $\mathcal{N}(960, 160)$.
+Note that the center bias model also predicted imprecision should be higher for targets further out on the screen.
+However, compared to the gaze model, it predicted a steep effect towards the sides, resulting in a V-shaped pattern (imprecision as the distance between the target location and the screen center).
+All cognitive models were implemented in WebPPL [@goodman2014design].[^6]
+
+[^6]: In an exploratory analysis, we simulated data for two more alternatives: a line-of-sight tracing model that assumed no inferential noise in the participants' gaze-following ability, and a model building up on the line-of-sight tracing with added motor noise.
+Please note that these did not predict a U-shape pattern, since all target locations would be influenced by the motor noise equally.
+For further details, see Supplements.
+
+We compared models via the marginal likelihood of the data under each model.
+The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor, which quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
+It can be used to estimate how much more likely the data under one model are compared to the other.
+Bayes Factors implicitly consider model complexity: models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
+
+## Results
+
+```{r gazemodel_results}
+gazemodel_comparison_kids <- readRDS("../data/gazemodel-kids-comparison-bf.rds")
+gazemodel_comparison_adults <- readRDS("../data/gazemodel-adults-comparison-bf.rds")
+gazemodel_corrs <- readRDS("../saves/gazemodel_correlations.rds")
+gazemodel_prior <- readRDS("../saves/gazemodel_prior.rds")
+```
+
+We found very clear support for our gaze model, both in children as well as adults.
+A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
+The gaze model predicted a U-shaped pattern which we also observed in our data (see Figure \@ref(fig:fig3)C).
+The model comparison strongly favored our gaze model over the center bias model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_center`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_center`) and the random guessing model (child sample $logBF_{10}$ = `r gazemodel_comparison_kids$bf_inf_guess`; adult sample $logBF_{10}$ = `r gazemodel_comparison_adults$bf_inf_guess`).
+For the child sample, we went one step further into the analysis.
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
+The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
+For children, we estimated the width of the prior's distribution based on the participants' age.
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
+The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
+
+(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
+Grey dots show individual level parameter values.
+The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
+The large black point with 95% HDI shows the mean of the model parameter for the adult sample.
+We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
+(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
+In the child sample, color denotes age in years.
+Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*.
+(C) Pattern recovery.
+Imprecision in target width for each target bin by age group.
+Model predictions in blue; data in grey.
+(D) Correlation between the observed data and the predictions of the three models by target position and age group (across individuals; only for the child sample).
+
+```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
+knitr::include_graphics("../figures/gazemodel_plot.png")
+```
+
+## Discussion
+
+We presented a formal cognitive model of gaze following to describe how gaze following develops with age and varies between individuals.
+We modeled gaze following as a process in which participants estimate pupil angles based on the pupil location within the eye.
+By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent.
+Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
+We assume the basic process of gaze following to be the same across the lifespan, though individuals become increasingly precise with age.
+While we did not include an infancy sample, we believe the process of gaze following should operate similarly — if not other cues such as the object saliencies or head directions are followed instead.
+By conducting model comparisons, we ruled out simpler explanations of the data.
+
+In addition, we observed differences in performance depending on gaze location: participant data showed that precision levels dropped as the agent's gaze moved further away from the center.
+Our gaze model predictions recovered this "signature pattern" in the data.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
+
+Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of @michelon2006two: in their Level 1 perspective-taking task, an increased distance between the agent and the target decreased performance in adults (i.e., reaction times).
+Targets closer to the midline were more easily traced than ones further away from the agent.
+The authors concluded that visual acuity is generally higher for locations on the vertical than the diagonal axis ("oblique effect"; [@appelle1972perception; @heeley1997oblique; @mikellidou2015oblique]).
+Similarly, @symons2004you have found that adults' acuity for gaze direction depends on the target location.
+Not only is the increased imprecision for TANGO trials in which the target lands further out consistent with this finding, but our gaze model poses a viable explanation for this effect.
+
+A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., experiencing motor issues, adding random noise to the click).
+However, we believe imprecise clicking to be of minor concern, since the children in our sample seemed determined in where they clicked and to not have issues with aiming or motor control (see precision in training trials in Supplements).
+
+A critical feature of our model is that it assumes gaze following to rely on vector following: subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
+Even though this vector following component is a geometrical calculation, one must first interpret the agent's eyes as a relevant social stimulus.
+Therefore, our model describes gaze following as a particular form of vector following in a social context.
+
+# Study 3: Components of gaze following
+
+Study 3 examined the components of gaze following and whether it can be fully reduced to physical vector following.
+The positive link between TANGO and social-environmental factors like age of childcare entry [@prein2023tango] underline how social interaction is integral to gaze following.
+Nevertheless, it is unclear how gaze following relates to other forms of perspective-taking [@astor2022gaze].
+Therefore, we investigated associations between gaze following and other measures of social-cognitive abilities.
+
+First, we experimentally isolated the vector following component of the TANGO.
+We designed a new non-social vector following task that shared all crucial design features of the TANGO.
+Second, we assessed children's social-cognitive abilities by administering a ToM task battery, comprising four tasks from the ToM scale by Wellman and Liu [@wellman2004scaling] and two additional perspective-taking tasks [@flavell1981development; @flavell1981younga].
+We reasoned that the TANGO shares task demands with the non-social vector following task while it shares its social context with the ToM tasks.
+We could therefore imagine both an absence or presence of relationship betweenn gaze following and ToM.
+As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze following.
+Our reasoning was that similar underlying mechanisms might be needed to solve these tasks since they require participants to take into account another person's point of view.
+
+The study design and procedure obtained ethical clearance in the same way as Study 1.
+The study was pre-registered prior to data collection: (<https://osf.io/xsqkt>).
+Data collection took place in Leipzig, Germany, between February and March 2023.
+
+## Participants
+
+```{r magnet_sample}
+magnet_sample <- readRDS("../saves/magnet_sample.rds")
+```
+
+The sample consisted of `r magnet_sample$n_total` children (mean age = `r magnet_sample$age_mean` years, SD = `r magnet_sample$age_sd`, range = `r magnet_sample$age_min` - `r magnet_sample$age_max`, `r magnet_sample$n_females` girls).
+Information on individual socio-economic status was not formally recorded.
+
+## Procedure
+
+Children were tested in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+For maximum control of extraneous participant variables, we employed a within-subjects study design.
+Participants performed the tasks in this order: (1) non-social vector following task, (2) ToM task battery, (3) TANGO.
+We decided on a fixed order to compare participants' performance straight-forwardly with each other.
+To increase engagement and decrease fatigue or fuzziness, we switched between tablet tasks and tasks with personal interaction.
+We presented the non-social vector following task before the TANGO so that participants would not be biased to interpret the stimuli as "agent-like".
+
+### Non-social vector following
+
+Modeling the structure of the TANGO, we designed a non-social vector following task.
+This task was presented on a tablet and used the concept of magnetism.
+On the upper part of the screen, there was a tube with a circular window, containing a gearwheel.
+On the floor, there was a magnet.
+The magnet got switched on (with a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
+The gearwheel moved so that its center aligned with the magnet center while staying inside the circular window.
+Participants were then asked to locate the magnet.
+Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
+Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
+Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
+We deliberately decided against displaying an arrow: we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
+In both cases, the starting point of the vector needs to be estimated by the participant.
+With an arrow, we would have drastically reduced the level of uncertainty, since the arrow already displays all information (arrow tip as the "gaze" direction).
+Furthermore, we wanted to avoid referential or iconic stimuli.
+
+Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+We conducted our analysis with 15 test trials (excluding the voice-over trial).
+The outcome variable was imprecision, defined as the absolute distance between the magnet's x coordinate and the x coordinate of the participant's click.
+Magnet coordinates were randomized: The full width of the screen was divided into ten bins; each bin occurred equally often, while the same bin could occur in two consecutive trials; and exact coordinates within each bin were randomly generated.
+
+### ToM task battery
+
+We administered four tasks from the @wellman2004scaling ToM scale (see Supplements for further detail).
+We excluded three tasks: the Diverse Desires task to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the "cold, cognitive" (vs.
+"emotional") aspects of social cognition.
+We added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga; where children were asked whether a turtle appeared to be on its back or feet / a worm lay on a red or blue blanket from the experimenter's point of view] with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze following, both relying on another's person egocentric frame of reference.
+
+### Gaze following
+
+As in Study 1 and 2, we presented children with the TANGO [@prein2023tango].
+To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze following (<https://osf.io/tdsvc>)).
+This further highlighted the contrast (i.e., social vs.
+non-social context) to the non-social vector following task.[^7]
+
+[^7]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.
+human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice.
+See Supplements for further detail.
+
+## Analysis
+
+By design, the TANGO and the non-social vector following task involved vector following.
+Based on our computational model, we expected children's performance in both tasks to correlate with each other.
+For each task, we calculated the mean level of imprecision for each subject and correlated them using *Pearson's* correlation coefficient.
+
+For the ToM battery, we aggregated the score of all solved tasks.
+Please note that the ToM score acted as an umbrella term and included the two perspective-taking tasks.
+Regarding the relationship between the two vector following tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze following recruited a social-cognitive ability beyond geometric vector following, we expected that ToM measures would correlate more strongly with the gaze following task than with the non-social vector following task.
+(B) If gaze following relied purely on task-specific geometric processes, then the correlation between gaze following and ToM measures would be comparable to the correlation between non-social vector following and the ToM measures.
+For the association between the aggregate ToM scores and the gaze following / non-social vector following tasks, we used *Spearman's* rank correlation coefficients.
+
+We compared the correlation between gaze following and ToM measures and the correlation between non-social vector following and ToM measures by using the Williams' test from the function `cocor.dep.groups.overlap` (designed for two dependent overlapping correlations) from the package `cocor` [@diedenhofen2015cocor].
+
+To estimate which components best explain the gaze following score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze following by age, imprecision in non-social vector following, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
+The outcome variable was modeled by a lognormal distribution.
+We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze following score.
+We hypothesized that perspective-taking seemed most closely theoretically related to gaze following as in both cases the participant was asked to judge another person's point of view.
+
+## Results
+
+```{r magnet_results}
+magnet_williamsttest_tom <- readRDS("../saves/magnet_williams_tom.rds")
+magnet_williamsttest_perspective <- readRDS("../saves/magnet_williams_perspective.rds")
+magnet_cormatrix <- readRDS("../saves/magnet_cormatrix.rds")
+magnet_model <- readRDS("../saves/magnet_winningmodel.rds")
+magnet_descriptives <- readRDS("../saves/magnet_descriptives.rds")
+```
+
+Children performed similarly well in the social and non-social vector following tasks (gaze following mean = `r magnet_descriptives["tango_mean",]$mean`, sd = `r magnet_descriptives["tango_mean",]$sd`, range = [`r magnet_descriptives["tango_mean",]$min` — `r magnet_descriptives["tango_mean",]$max`]; vector following mean = `r magnet_descriptives["magnet_mean",]$mean`, sd = `r magnet_descriptives["magnet_mean",]$sd`, range = [`r magnet_descriptives["magnet_mean",]$min` — `r magnet_descriptives["magnet_mean",]$max`]).
+The mean aggregate ToM score was `r magnet_descriptives["tom_aggregate",]$mean` (sd = `r magnet_descriptives["tom_aggregate",]$sd`, range = [`r magnet_descriptives["tom_aggregate",]$min` — `r magnet_descriptives["tom_aggregate",]$max`]), while the mean aggregate perspective-taking score was `r magnet_descriptives["perspective_aggregate",]$mean` (sd = `r magnet_descriptives["perspective_aggregate",]$sd`, range = [`r magnet_descriptives["perspective_aggregate",]$min` — `r magnet_descriptives["perspective_aggregate",]$max`]).
+
+Gaze following substantially correlated with the non-social vector following task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
+While the tasks highly overlap in task demands, their measures shared some, but not all of their variance.
+
+ToM abilities did not correlate with gaze following ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x ToM"]`]) or non-social vector following ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x ToM"]`]), and the correlations did not differ from each other, Williams' test *t*(`r magnet_williamsttest_tom$parameter`) = `r round(magnet_williamsttest_tom$statistic, 2)`, *p* = `r round(magnet_williamsttest_tom$p.value, 2)`.
+
+Interestingly, gaze following and perspective-taking correlated with each other, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
+Please note that the TANGO quantifies imprecision in gaze following.
+Therefore, a negative correlation suggests that imprecision in gaze following corresponds to less perspective-taking.
+Non-social vector following and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+However, according to the Williams' test, the two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
+
+Our model comparison revealed that gaze following was best predicted by a model including non-social vector following ($\beta$ = `r fixef(magnet_model)["magnet_scaled", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["magnet_scaled", "Q2.5"]`; `r fixef(magnet_model)["magnet_scaled", "Q97.5"]`]) and perspective-taking ($\beta$ = `r fixef(magnet_model)["perspective_scaled", "Estimate"]`; 95% CrI [`r fixef(magnet_model)["perspective_scaled", "Q2.5"]`, `r fixef(magnet_model)["perspective_scaled", "Q97.5"]`]), even when controlling for age ($\beta$ = `r fixef(magnet_model)["age_centered", "Estimate"]`, 95% CrI [`r fixef(magnet_model)["age_centered", "Q2.5"]`, `r fixef(magnet_model)["age_centered", "Q97.5"]`]) (see Figure \@ref(fig:fig4)C and Supplements for the model comparison).
+
+(ref:figlab4) **Components of gaze following.** (A) Study procedures.
+Top: TANGO (i.e., gaze following; social vector following).
+Bottom: Magnet (i.e., non-social vector following).
+The left-hand side shows screenshots of the familiarization phase; right-hand side shows screenshots of the test phase.
+For illustrative purposes, transluscent targets are shown in the test phase.
+Participants cannot see them.
+(B) Correlations between gaze following, non-social vector following, ToM, and perspective-taking.
+Dots show the correlation coefficients, error bars represent 95% CIs.
+Please note that the ToM score acts as an umbrella term and also includes two perspective-taking tasks.
+(C) Influence of age, perspective-taking and non-social vector following on gaze following.
+The graph shows the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80% CrI, and thinner black lines 95% CrI.
+
+```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
+knitr::include_graphics("../figures/magnet_plot.png")
+```
+
+## Discussion
+
+Our gaze model assumed vector calculations on a process level.
+By isolating non-social vector following experimentally, we could show that gaze following does indeed, to a certain degree, rely on this component.
+However, non-social vector following alone did not suffice to explain variation in gaze following.
+Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO.
+The overall ToM aggregate score did not add explanatory power.
+
+The TANGO and the two perspective-taking tasks can be seen as instances of visuospatial perspective-taking.
+Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
+Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint [@surtees2013similarities], and can usually be solved independently from another’s agent frame of reference and without mental rotation [not matching the “mentalizing criterion”; @quesque2020theoryofmind].
+In contrast, Level 2 perspective-taking tasks ask participants to judge how (visually or conceptually) the world looks for another person.
+Solving these tasks presumably relies on a simulation of mentally transforming one's own body schema into the space of another agent [@erle2017grounded].
+Participants must understand that different viewpoints lead to different perspectives [@flavell1981younga]: two agents can see the same object "in different, incompatible, fine-grained ways" [@rakoczy2022foundations].
+In short, Level 1 perspective-taking addresses *what* an agent can see, while Level 2 perspective-taking addresses *how or where* they see it [@moll2006level].
+The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale - while the perspective-taking tasks presented within the ToM scale fall into the second category.
+
+In the TANGO, participants locate the target by assuming that another agent perceives and looks at the it.
+The here-applied Level 2 perspective-taking tasks add another layer by asking how one's perspective differs from another's and how exactly the other person sees an object.
+@michelon2006two assessed the different processes that participants used to master Level 1 and Level 2 perspective-taking tasks and concluded that participants rely on line-of-sight tracing in the former and perspective transformation in the latter case.
+Line-of-sight tracing consists of locating the avatar and the target, and drawing a line between them.
+Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
+Level 2 perspective-taking requires an additional step in which participants "perform a perspective transformation so that one's imagined position matches the position of the avatar" [@michelon2006two].
+Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt a new reference frame and there is no potential conflict between one's own and the other person's reference frame.
+Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
+
+@surtees2013similarities further differentiated between visual and spatial perspective-taking.
+While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
+Spatial perspective-taking does not necessitate mental states since computing a line of sight does not demand the presence of another agent [@michelon2006two] and can, therefore, be applied to non-agentive objects with a front [@surtees2013similarities].
+This could explain how our participants solved the non-social vector following task.
+
+Interestingly, we found weaker correlations between gaze following and the other ToM tasks.
+Similarly, in a longitudinal study, @brooks2015connecting found no direct association between gaze following at 10.5 months and explicit ToM at 4.5 years.
+While the ToM tasks and the TANGO shared the social context, the cognitive processes needed to solve each task might vary.
+As @rakoczy2022foundations reflected, perception-goal psychology (which includes gaze following) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be false or involve aspectual information.
+
+In previous work, we established that the TANGO is suited to capture meaningful variability across individuals [@prein2023tango], which is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: the aggregate score of few dichotomous items is of limited use when it comes to quantifying genuine differences between individuals.
+However, since these tasks are the gold standard in the social-cognitive literature [@rakoczy2022foundations; @poulin-dubois2023discontinuity; @wellman2018theory; @byom2013theory; @bialecka-pikul2021early], and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce [e.g., @beaudoin2020systematic; @mayes1996testretest], we nonetheless relied on them in this study.
+Thus, lower correlations between ToM abilities and gaze following may reflect poor measurement characteristics on the side of ToM tasks rather than a genuine absence of association.
+We would like to point out that we already stated this concern in our pre-registration (<https://osf.io/xsqkt>).
+
+If the reliability of the tasks at hand is known, one can estimate the "true" correlation between the latent constructs by applying an attenuation formula or structural equation models [@metsamuuronen2022attenuationcorrected; @trafimow2016attenuation].
+Adjusting for the measurement error would increase the so-called true correlation.
+While we can estimate the split-half reliability for the TANGO [@prein2023tango] and the non-social vector following task, we do not have reliability estimates of the ToM measures and cannot apply said approaches.
+This, in turn, underlines the importance of reporting the psychometric properties of a task.
+The development of new measures to capture individual differences in social-cognitive abilities seems essential to move this research further.
+
+# General discussion
+
+In three studies, we shed light on the cognitive process underlying gaze following and its developmental trajectory across the lifespan.
+Study 1 focused on how gaze following changes with age.
+We found a steep performance improvement in the preschool years in which children became more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reached their peak performance.
+Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
+Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
+In Study 2, we proposed a computational cognitive model that described gaze following at a process level.
+We modeled gaze following as a process in which participants use the pupil location within the eyes to estimate pupil angles.
+To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
+Individuals vary in their levels of uncertainty around these pupil angles.
+Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+Knowing the TANGO to be a reliable individual differences measure, we investigated potential components of gaze following in Study 3.
+A fundamental assumption of our computational model was that gaze following relies on a vector following process.
+We experimentally isolated this component by designing a non-social vector following task.
+Furthermore, we assessed the relationship between gaze following and traditional ToM tasks.
+We found that gaze following does, indeed, share a substantial part of its variance with the non-social counterpart of vector following.
+Additionally, perspective-taking correlated with gaze following, whereas the other ToM measures (focusing on diverse desires, knowledge access, and false beliefs) did not.
+
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
+While previous research established that four-month-olds can follow gaze toward one out of two objects, this is not the end point of development.
+By studying gaze following on a continuum, we assessed not just *whether*, but *how precisely* children locate others’ attentional focus.
+In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; [@prein2023tango]).
+Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
+
+Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
+Older adults decreased slightly in their precision levels.
+This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
+
+In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze following.
+Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; line-of-sight; see Figure \@ref(fig:fig2)A).
+The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
+The model proposes that development in gaze following equals a reduction in noise when estimating the agent's pupil angles.
+We found strong evidence for the proposed gaze model when comparing it against two alternative models and correlating its predictions with the observed data (see Figure \@ref(fig:fig3)D), both for children and adults.
+Notably, the model recovers signature patterns in the data (see Figure \@ref(fig:fig3)C).
+
+In Study 3, we tested the relation between gaze following and non-social vector following.
+As implied by our gaze model, we found that gaze following relates to the ability to estimate vectors in space.
+Already @butterworth1991minds have argued that, as the scene of actions, space is the commonality between different minds.
+The spatial vector following ability might be helpful in several social-cognitive tasks, for example, action prediction [@friesen2011gaze], and intention understanding.
+Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector following abilities.
+
+Gaze as displayed in the TANGO versus as in real-life social interactions differs with regard to which information is available.
+In the TANGO, the agent’s eyes are big and round, with uniform colors, white sclera, fully visible iris and pupils, and continuous eye movement.
+Eye gaze in natural social interactions often provides less information and is more ambiguous.
+Even though the TANGO and our gaze model are designed within a 2D world, we believe the mechanisms can be extrapolated into the 3D world.
+The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
+In Study 3, we presented the first evidence that this might be the case.
+We administered Level 2 perspective-taking tasks in which participants needed to adapt another person's frame of reference in a real-world social interaction.
+The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup or stimulus features.
+Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+Here, however, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground [@bohn2018common; @moll2013primacy; @osborne-crowley2020social].
+From a modeling perspective, a shared interaction history or diverse desires might be represented as non-uniform prior distributions over locations in the visual scenery.
+This way, our gaze model could be expanded to include more complex processes like mental state reasoning.
+
+Theories of gaze following differ in whether they illustrate why children pay attention to gaze in the first place versus how they identify the exact location of gaze.
+While we described  the process behind children’s increasing precision in gaze following, we still need to further explore the driving forces behind this development.
+Existing theories broadly vary in how much importance they place on (A) experience and social environment, and (B) social awareness vs.
+domain-general learning mechanisms (see categorization by @astor2022gaze).
+For example, it has been hypothesized that infants might be equipped with an innate gaze module and special neural mechanisms to detect eyes [@baron-cohen1995mindblindness; @batki2000there]; that children identify contingencies in social interactions and, in these, get reinforced to follow gaze [@triesch2006gaze; @corkum1998origins; @silverstein2021infants]; or that children are intrinsically socially motivated and simulate their own experiences to understand others [@tomasello1999social; @meltzoff2007me; @astor2020social; @friesen2011gaze; @ishikawa2020learning].
+As seen in @prein2023tango, precision in gaze following is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
+Which exact kind of interactions are most helpful to improve precision in gaze following remains unknown.
+
+# Limitations
+
+In this paper, we have focused on studying variation across ages and individuals.
+However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds [@henrich2010weirdesta].
+Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communication [@nielsen2017persistent].
+First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts [@hernik2019infanta].
+While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze following holds true across communities.
+Analyzing cross-cultural variation and checking for predicted "signature patterns" in the data will inform our modeling work and theory building in further detail [@amir2020crosscultural].
+
+In Study 1, we recruited older participants online which might have selected a particular subgroup of this age range.
+Seventy-year-olds who have working WIFI connections, know how to use a computer, and are registered on *Prolific* might not be representative of their age group.
+We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories toward old age.
+
+Our computational model of gaze following estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
+The model assumes no motor imprecision in this estimation.
+However, younger children could have located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
+This would blur the model's estimation of the inferential component.
+However, in the first training trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels [cf.
+@prein2023tango].
+Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem unlikely.
+
+In Study 3, we matched the non-social vector following task as closely as possible to the TANGO.
+However, the starting positions differ: the magnet never appeared in the center of the screen.
+The starting point of the balloon might be especially important when interpreting the U-shaped pattern in Study 2.
+Furthermore, in the TANGO, two eyes are presented and information of the two (matching) cues needs to be integrated to infer the target's location.
+In the non-social vector following task, only one circular window with a gearwheel inside is presented as a directional cue, and there is no need to integrate two different information sources.
+In addition, we want to mention that the gaze presented in the TANGO might be more prominent compared to real-life social interactions (e.g., perfectly round and visible sclera; see discussion above).
+Future research should investigate how factors like self-propelled movement, spatial layout, and number of information sources influence the mechanisms of gaze following.
+
+# Conclusion
+
+In three studies, we have illuminated the lifelong development of precisely estimating another's gaze direction, and the psychophysical process behind this.
+We have shown that gaze following continues to develop beyond infancy, and that individuals differ in their precision levels to localize the gaze direction of an agent.
+Our proposed process-level theory of gaze following modeled individual differences in precision as varying levels of uncertainty in the estimated gaze vectors.
+Consequently, we found that imprecision in gaze following relates to non-social vector following, as proposed by the model.
+Additionally, gaze following was linked to visual perspective-taking but no other aspects of ToM.
+The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
+
+\newpage
+
+# References
+
+```{=tex}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
+```{=tex}
+\endgroup
+```

### 2024-03-27 paper/manuscript.tex
prepare revision

--- 2023-06-09 paper/manuscript.tex
@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man,mask,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 {}{\PatchFailed}
-\keywords{social cognition, individual differences, gaze cues, cognitive modeling\newline\indent Word count: xxx}
+\keywords{social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan\newline\indent Word count: 7914}
 \usepackage{lineno}
@@
 \captionsetup[figure]{font={stretch=1}}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 \ifLuaTeX
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
   pdftitle={Variation in gaze understanding across the life span: A process-level perspective},
-  pdfauthor={Julia Prein1, Manuel Bohn1,2, Luke Maurits1, Annika Werwach1, \& Daniel B. M. Haun1},
   pdflang={en-EN},
-  pdfkeywords={social cognition, individual differences, gaze cues, cognitive modeling},
+  pdfkeywords={social-cognitive development, theory of mind, gaze cues, individual differences, cognitive modeling, lifespan},
   hidelinks,
@@
 \title{Variation in gaze understanding across the life span: A process-level perspective}
-\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
+\author{Julia Christin Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{3,4}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{3} Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany\\\textsuperscript{4} Max Planck School of Cognition, Leipzig, Germany\\\textsuperscript{*} Shared senior authorship}
 
 \abstract{%
-Abstract
+Following eye gaze is fundamental for many social-cognitive abilities, for example, when judging what another agent can or cannot know.
+While the emergence of gaze-following has been thoroughly studied on a group level, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
+In Study 1, we examined gaze understanding across the lifespan (\emph{N} = 471 3- to 80-years-olds; children from a mid-sized German city; international remotely tested adults).
+We found a steep performance improvement during preschool years, in which children became more precise in locating the attentional focus of an agent.
+Precision levels then stayed comparably stable throughout adulthood with a minor decline toward old age.
+In Study 2, we formalized the process of gaze understanding in a computational cognitive model that allowed us to conceptualize individual differences in a psychologically meaningful way (\emph{N} = 60 3- to 5-year-olds, 50 adults).
+According to our model, participants estimate pupil angles with varying levels of precision based on observing the pupil location within the agent's eyes.
+In Study 3, we tested two implications of our gaze model, namely that gaze understanding could be related to vector estimation in non-social settings and perspective-taking abilities (\emph{N} = 102 4- to 5-year-olds).
+We found that gaze understanding is associated with both of these abilities but less so with other Theory of Mind tasks.
+This work illustrates how the combination of reliable measurement instruments and formal theoretical models allows us to explore the in(ter)dependence of core social-cognitive processes in greater detail.
 }
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\hypertarget{variation-in-gaze-understanding-across-the-life-span-a-process-level-perspective}{%
+\section{Variation in gaze understanding across the life span: A process-level perspective}\label{variation-in-gaze-understanding-across-the-life-span-a-process-level-perspective}}
+
+\textbf{Authors:} Julia Christin Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1,3,4}, Daniel B.
+M.
+Haun\textsuperscript{1,*}, Manuel Bohn\textsuperscript{1,2,*}
+
+\textbf{Affiliations:} \textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.
+\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany.
+\textsuperscript{3} Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany.
+\textsuperscript{4} Max Planck School of Cognition, Leipzig, Germany.
+\textsuperscript{*} shared senior authorship
+
+\textbf{ORCiD}: \emph{Julia Christin Prein} \url{https://orcid.org/0000-0002-3154-6167}
+
+\textbf{Conflicts of interest:} The authors declare that they have no conflict of interest.
+
+\textbf{Data availability statement:} The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
+The data sets generated during and/or analyzed during the current study are available in the {[}gazecues-modeling{]} repository (\url{https://github.com/ccp-eva/gazecues-modeling}).
+All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
+
+\textbf{Acknowledgements:} We thank Jana Jurkat for her help with data collection and participant recruitment.
+We would also like to thank Steven Kalinke for his technical programming support.
+We thank all the children, caregivers, and adults who participated in the study.
+
+\textbf{Funding:} This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
+Manuel Bohn was supported by a Jacobs Foundation Research Fellowship.
+
+\textbf{Ethical statement:} The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+No.~2021\_45).
+Informed consent was obtained from all individual participants or their legal guardians.
+The research adhered to the legal requirements of psychological research with children in Germany.
+
+\newpage
+
+\hypertarget{research-highlights-to-be-placed-before-the-abstract}{%
+\section{Research highlights (to be placed before the abstract)}\label{research-highlights-to-be-placed-before-the-abstract}}
 
@@
 \item
-  why do we care about developmental trajectory? ref to stat learning paper
+  Gaze understanding develops beyond infancy. Highest precision levels in localizing attentional foci are reached in young adulthood with a slight decrease towards old age.
 \item
-  variation
+  We present a computational model as a mechanistic description of gaze understanding. The model explains individual differences and recovers signature patterns in the data.
+\item
+  Our model assumes that gaze understanding relies on vector estimation. To test this assumption experimentally, we designed a non-social vector estimation task.
+\item
+  We found substantial correlations between gaze understanding and vector estimation, as well as Level 2 perspective-taking. Other Theory of Mind tasks did not correlate.
 \end{itemize}
 
-\hypertarget{why-do-we-need-gaze-understanding}{%
-\subsection{Why do we need gaze understanding?}\label{why-do-we-need-gaze-understanding}}
-
-How do humans learn about their environment and navigate through their social surroundings?
-One possibility to extract information from the environment is through following others' focus of attention.
-Building a common ground is considered especially important in communicative interactions and shared activities (Tomasello, Hare, Lehmann, \& Call, 2007).
-
-\hypertarget{how-does-gaze-following-emerge}{%
-\subsection{How does gaze following emerge?}\label{how-does-gaze-following-emerge}}
-
-Existing studies operationalize gaze following as the ability to follow another agent's line of sight.
-As one of the most fundamental social-cognitive abilities, it has been extensively studied in infancy and early childhood.
-Infants as young as six months can attune their gaze to that of another agent (D'Entremont, Hains, \& Muir, 1997).
-At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access (Moll \& Tomasello, 2004).
-
-While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
-One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.However, many cognitive abilities develop with age (e.g., working memory, Gathercole, Pickering, Ambridge, \& Wearing, 2004).
-Similarly, visual processing appears to improve with age.
-Therefore, children could potentially improve in gaze following, fine-tuning the performance of the already existing skill.
-
-\hypertarget{the-scope-of-infants-gaze-following-ability}{%
-\subsection{The scope of infants' gaze following ability}\label{the-scope-of-infants-gaze-following-ability}}
-
-Though these studies suggest that young infants can align their visual attention to another's line of sight, it does not necessarily include understanding the intentions of the other agent.
-Infants could simply attune their orientation or be attracted by others' gaze without processing what exactly the other is seeing (cf.~Butterworth \& Jarrett's ecological and geometric mechanism, Butterworth and Jarrett (1991){]}.
-Therefore, it is crucial to study children's intentional understanding of gaze.
-
-Moore, Angelopoulos, and Bennett (1997) showed that 9-month-olds followed an agent's gaze more, when it was accompanied by a dynamic head turn in comparison to a static head turn.
-
-In a hiding game with two search locations, Povinelli, Reaux, Bierschwale, Allain, and Simon (1997) found that three-year-olds used gaze as a cue to locate the reward, while two-year-olds performed at chance level.
-
-In a similar object choice paradigm with two containers, Behne, Carpenter, and Tomasello (2005) investigated whether infants understand the communicative intent behind pointing and gaze cues.
-In contrast to Povinelli et al. (1997), they found that already 14-month-olds used the agent's cues to select an object.
-In conditions with absent-minded `cues', infants performed around chance.
-This could be interpreted as infants recognizing the nature of this joint activity: namely, that the adult's behavior was beneficial and relevant for their object choice.
-
-\hypertarget{head-vs-eye-direction}{%
-\subsubsection{Head vs eye direction}\label{head-vs-eye-direction}}
-
-It is important to note that in many existing gaze conditions, the experimenter shifted their eyes and head in synchrony (e.g., Behne et al. (2005)).
-Instead of pointing towards gaze understanding, a critic could claim that the results can be explained by face direction alone.
-
-A handful of studies approached this potential confound by separately manipulating head and eye movement.
-Brooks and Meltzoff (2002) implemented a comparison between eye and head orientation and found that 14-month-olds were sensitive to open versus closed eyes.
-
-Investigating the `cooperative eye hypothesis', Tomasello et al.
-(2007) implemented six conditions, in which an experimenter oriented towards the ceiling with their eyes only, head only (eyes closed), both head and eyes, or neither.
-They found that human infants relied more on the eye movement, while chimpanzees paid more attention to the head movement.
-
-Importantly, the subjects were not presented with an object choice but their attention orientation was measured.
-
-\begin{itemize}
-\item
-  (Raviv \& Arnon, 2018)
-\item
-  (Astor \& Gredebäck, 2022)
-\item
-  (Colombo, 2001)
-\item
-  (Scaife \& Bruner, 1975)
-\item
-  (Itakura \& Tanaka, 1998)
-\item
-  (Carpenter, Nagell, \& Tomasello, 1998) ``Several other studies have attempted to determine more precisely the cue that infants are using when they follow the gaze direction of others, that is, whether they use adults' head or eye orientation.
-In tasks comparing infants' responses when the experimenters turned their head and eyes together to targets with their responses when the experimenters directed their eyes to the targets but their head remained facing forward, Corkum and Moore (1995), Lempers (1979), and Lempers, Flavell, and Flavell (1977) all found that only infants age 12 months and older responded correctly when eyes and head were oriented in the same direction and that infants at all ages (i.e., through 19 months) performed poorly when eye and head direction diverged'' (p.10-11) object choice.
-\item
-  (Silverstein, Feng, Westermann, Parise, \& Twomey, 2021) for vertical plane
-\item
-  (Zhang, Zhang, Zhang, Tang, \& Liu, 2019)
-\item
-  (Frischen, Bayliss, \& Tipper, 2007)
-\item
-  (Lee, Eskritt, Symons, \& Muir, 1998)
-\item
-  (Coelho, George, Conty, Hugueville, \& Tijus, 2006)
-\end{itemize}
-
-\hypertarget{aim-of-the-current-project}{%
-\subsection{Aim of the current project}\label{aim-of-the-current-project}}
-
-\hypertarget{developmental-trajectory-measuring-modeling-individual-differences}{%
-\subsubsection{Developmental trajectory, measuring \& modeling individual differences}\label{developmental-trajectory-measuring-modeling-individual-differences}}
-
-In this study, we were interested in the developmental trajectory of gaze understanding.
-While we expect the younger children to be able to follow gaze, we aimed at assessing the differentiation of their social-cognitive ability.
-Our goal was \emph{not} to establish the youngest age at which children understand gaze cues.
-Rather, we wanted to examine how that ability changes with age.
-
-In our study, we focused on the communicative intents of gaze: we asked children to locate a target by following an agent's gaze.
-While language demands were kept low, the participants had to actively respond and, therefore, make use of the presented gaze cue.
-
-A unique contribution of this study is the richness of the data set.
-Methodological challenges arise when trying to compare data across ages from qualitatively and quantitatively different study tasks.
-We could circumvent these issues by applying the exact same task for the entire life span.
-
-\hypertarget{lifespan}{%
-\section{Lifespan}\label{lifespan}}
-
-\begin{itemize}
-\tightlist
-\item
-  development \& individual differences in gaze understanding
-\item
-  verweis methods paper reliable differences kinder \& adults.
-\item
-  kontinuerliche, systematische variation, wodrin? =\textgreater{} model
-\end{itemize}
-
-\url{https://osf.io/6yjz3}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:lifespan_sample}}
-
-\begin{tabular}{lllll}
-\toprule
-Age group & \multicolumn{1}{c}{n} & \multicolumn{1}{c}{Age mean} & \multicolumn{1}{c}{Age range} & \multicolumn{1}{c}{Age SD}\\
-\midrule
-3.00 & 19 (7 female) & 3.62 & 3.04 - 3.99 & 0.31\\
-4.00 & 17 (9 female) & 4.45 & 4.05 - 4.91 & 0.30\\
-5.00 & 22 (13 female) & 5.56 & 5.08 - 5.99 & 0.31\\
-6.00 & 24 (16 female) & 6.50 & 6.1 - 6.99 & 0.28\\
-7.00 & 39 (20 female) & 7.48 & 7.04 - 7.95 & 0.25\\
-8.00 & 41 (20 female) & 8.46 & 8.03 - 8.98 & 0.27\\
-9.00 & 56 (29 female) & 9.46 & 9.01 - 9.96 & 0.28\\
-10.00 & 35 (22 female) & 10.49 & 10.01 - 11 & 0.28\\
-11.00 & 54 (26 female) & 11.43 & 11.01 - 11.96 & 0.28\\
-12.00 & 43 (19 female) & 12.41 & 12.01 - 12.99 & 0.30\\
-13.00 & 42 (19 female) & 13.50 & 13.09 - 13.99 & 0.27\\
-14.00 & 20 (14 female) & 14.37 & 14.05 - 14.98 & 0.23\\
-15.00 & 21 (11 female) & 15.56 & 15.05 - 15.98 & 0.30\\
-16.00 & 19 (10 female) & 16.51 & 16.17 - 16.97 & 0.24\\
-17.00 & 19 (10 female) & 17.53 & 17.01 - 17.95 & 0.28\\
-18.00 & 2 (0 female) & 18.00 & 18 - 18 & 0.00\\
-19.00 & 5 (4 female) & 19.00 & 19 - 19 & 0.00\\
-20.00 & 40 (25 female) & 23.02 & 20 - 29 & 2.77\\
-30.00 & 40 (21 female) & 34.42 & 30 - 39 & 3.00\\
-40.00 & 40 (24 female) & 44.17 & 40 - 49 & 2.92\\
-50.00 & 40 (21 female) & 54.38 & 50 - 59 & 3.04\\
-60.00 & 40 (21 female) & 63.73 & 60 - 69 & 2.56\\
-70.00 & 40 (20 female) & 72.75 & 70 - 79 & 2.44\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Following the gaze of others is valuable to extract information from the environment.
+It guides us to ``informational hotspots'' (Meltzoff et al., 2010, p.
+1) and can be used to identify internal states such as intentions or emotions (Corkum \& Moore, 1998; Pfeiffer et al., 2013).
+As one of the most fundamental social-cognitive abilities, gaze-following is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning (Bohn \& Frank, 2019; Emery, 2000; Frith \& Frith, 2012; Hessels, 2020; Moore, 2008; Rakoczy, 2022; Tomasello \& Rakoczy, 2003), and has been extensively studied in infancy (for review, see Del Bianco et al., 2019).
+In the most commonly used paradigm (e.g., Astor et al., 2020; Byers-Heinlein et al., 2021; Gredebäck et al., 2010; Ishikawa et al., 2022), the experimenter looks directly at the infant before shifting their head and eyes to one of the two objects.
+Infants' looking times to the target or the proportion of choosing the target over the distractor are measured.
+Analyses traditionally focus on the average age at which children as a group reach an above-chance performance.
+Research in this tradition finds that infants as young as six months can follow gaze to that of another agent (D'Entremont et al., 1997).
+At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access (Butterworth \& Jarrett, 1991; Corkum \& Moore, 1995; Deák et al., 2000; Moll \& Tomasello, 2004).
+
+While the emergence of gaze-following has been well established, less is known about its developmental trajectory beyond infancy.
+One possibility is that the ability to follow gaze does not improve once it emerges.
+Yet, most, if not all, cognitive abilities continue to develop throughout childhood (e.g., Gathercole et al., 2004; Gredebäck et al., 2010).
+It seems likely that children fine-tune their gaze understanding as they get older - presumably while using them in social interactions.
+To capture development in gaze understanding beyond infancy, we conducted our Study 1 across the lifespan.
+
+Up until today, only a handful of gaze-following studies differentiate between manipulating head and eye movement.
+Michel et al.
+(2021) found that gaze-following in four-month-olds was likely driven by other's head- instead of eye movements.
+Corkum and Moore (1995), Lempers (1979), and Lempers et al.
+(1977) suggest that infants, at least until 19 months, struggle when eye and head direction diverge.
+From farther distance, body or face orientation can act as more salient cues to determine another's area of attention.
+However, eye direction indicates a more precise location of focus (Emery, 2000), and allows to anticipate likely future actions (Friesen \& Rao, 2011; Zohary et al., 2022).
+In our three studies, we therefore focused on subtle gaze cues and isolated eye movement alone.
+
+Though previous studies suggest that young infants can align their visual attention to another's line of sight, this does not necessarily indicate understanding the intentions of the agent (Aslin, 2007).
+Infants could simply align their orientation without processing what exactly the other is seeing (Butterworth \& Jarrett, 1991).
+In fact, one might question if such an alignment reflects an understanding of visual perspectives at all, because the ``target'' or ``object of representation'' is not necessarily specified (Perner et al., 2003, p.
+358).
+To fulfill this criterion, Moll and Tomasello (2006) applied an active behavioral choice, in which participants searched for a visually accessible or inaccessible target object.
+24-month-olds succeeded in the task, while 18-month-olds did not.
+In an object choice study with two containers, Behne et al.
+(2005) found that already 14-month-olds used an experimenter's gaze; however, this was again confounded with a congruent face movement (cf.
+Povinelli et al., 1997).
+In our three studies, we assessed how subtle gaze cues guided participants' behavior in actively locating a target.
+
+Finally, group-level analyses of gaze-following abilities may mask individual differences between children.
+Measuring individual differences in basic aspects of social cognition is especially important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities (Birch et al., 2017; Del Bianco et al., 2019).
+In our studies, we measured gaze understanding continuously by using a task which is designed to capture individual-level variation (Prein et al., 2023).
+
+The present study had two main goals: first, we studied the development of gaze understanding beyond infancy (Study 1).
+Instead of capturing the youngest age at which children follow gaze, we examined how this ability changes with age.
+Our second goal was to provide a process-level theory of gaze understanding (and individual differences therein) as a computational cognitive model.
+We formalized gaze understanding as a form of vector estimation and tested whether our model explained empirical data (Study 2).
+Finally, we examined two empirical predictions that followed from the model, namely that gaze understanding is related to non-social vector estimation and visual perspective-taking (Study 3).
+
+\hypertarget{study-1-gaze-understanding-across-the-lifespan}{%
+\section{Study 1: Gaze understanding across the lifespan}\label{study-1-gaze-understanding-across-the-lifespan}}
+
+The study was pre-registered at: \url{https://osf.io/snju6} (child sample) and \url{https://osf.io/6yjz3} (adult sample).
+The study obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under an umbrella ethics application (Appl.
+No.~2021\_45).
+Data was collected between May 2021 and April 2023.
 
@@
 
-We collected data from a remote child, teenager and adult sample.
-For the remote child and teenager sample, we recruited participants via an internal database consisting of families living in Leipzig, Germany, who volunteered to participate in child development studies and indicated an interest in online studies.
-
-The remote child and teenager sample consisted of 471 children, including 19 3-year-olds (mean = 3.62 years, SD = 0.31, range = 3.04 - 3.99, 7 girls), 17 4-year-olds (mean = 4.45 years, SD = 0.30, range = 4.05 - 4.91, 9 girls), 22 5-year-olds (mean = 5.56 years, SD = 0.31, range = 5.08 - 5.99, 13 girls), 24 6-year-olds (mean = 6.50 years, SD = 0.28, range = 6.10 - 6.99, 16 girls), 39 7-year-olds (mean = 7.48 years, SD = 0.25, range = 7.04 - 7.95, 20 girls), 41 8-year-olds (mean = 8.46 years, SD = 0.27, range = 8.03 - 8.98, 20 girls), 56 9-year-olds (mean = 9.46 years, SD = 0.28, range = 9.01 - 9.96, 29 girls), 35 10-year-olds (mean = 10.49 years, SD = 0.28, range = 10.01 - 11, 22 girls), 54 11-year-olds (mean = 11.43 years, SD = 0.28, range = 11.01 - 11.96, 26 girls), 43 12-year-olds (mean = 12.41 years, SD = 0.30, range = 12.01 - 12.99, 19 girls), 42 13-year-olds (mean = 13.50 years, SD = 0.27, range = 13.09 - 13.99, 19 girls), 20 14-year-olds (mean = 14.37 years, SD = 0.23, range = 14.05 - 14.98, 14 girls), 21 15-year-olds (mean = 15.56 years, SD = 0.30, range = 15.05 - 15.98, 11 girls), 19 16-year-olds (mean = 16.51 years, SD = 0.24, range = 16.17 - 16.97, 10 girls), 19 17-year-olds (mean = 17.53 years, SD = 0.28, range = 17.01 - 17.95, 10 girls), 2 17-year-olds (mean = 18 years, SD = 0, range = 18 - 18, 0 girls),
-5 17-year-olds (mean = 19 years, SD = 0, range = 19 - 19, 4 girls).
-
-Children and teenagers in our sample grow up in an industrialized, urban Central-European context.
-Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
+We collected data online from 3- to 80- year-olds (see Supplements for further details).
+The child sample consisted of 471 participants and was recruited via an internal database of families in Leipzig, Germany, who volunteered to participate in child development studies.
+Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
+They lived in an industrialized, urban Central-European context in a mid-size German city (approx.
+600,000 inhabitants; median individual monthly net income approx.
+1,600€ as of 2021).
+Most were raised monolingually in a nuclear two-generational family setting.
+Information on demographics and socioeconomic status was not formally recorded on a participant level.
 
 Adults were recruited via \emph{Prolific} (Palan \& Schitter, 2018).
-\emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
-Participants consisted of 240 English-speaking adults that reported to have normal or corrected-to-normal vision.
-The sample included 40 20- to 29-year-olds (mean = 23.02 years, SD = 2.77, range = 20 - 29, 25 female),
-40 30- to 39-year-olds (mean = 34.42 years, SD = 3, range = 30 - 39, 21 female),
-40 40- to 49-year-olds (mean = 44.17 years, SD = 2.92, range = 40 - 49, 24 female),
-40 50- to 59-year-olds (mean = 54.38 years, SD = 3.04, range = 50 - 59, 21 female),
-40 60- to 69-year-olds (mean = 63.73 years, SD = 2.56, range = 60 - 69, 21 female), and
-40 70- to 79-year-olds (mean = 72.75 years, SD = 2.44, range = 70 - 79, 20 female).
-
-For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).
+\emph{Prolific} is an online participant recruitment tool from the University of Oxford with predominantly European and US-American subjects.
+Participants consisted of 240 English-speaking adults who reported to have normal or corrected-to-normal vision.
+For completing the study, subjects were paid above the fixed minimum wage (\textasciitilde£10.00/hour).
 
@@
 
-We used the TANGO task (Prein, Bohn, Kalinke, \& Haun, 2022).
-The task was presented as an interactive web application (see Figure \ref{fig:fig1}; live demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
-The TANGO showed satisfactory internal consistency and retest reliability {[}with reliability estimates \emph{Pearson's r} ranging from .5 to .8 for the categorical task version and .7 to .8 for the continuous task version; Prein et al.
-(2022){]}.
-
-Each trial presented an agent standing in a window, watching a balloon (\emph{i.e.}, target) falling to the ground.
-Depending on the task version, the target either fell into a box (categorical task version) or behind a hedge (continuous task version).
-The agent's gaze followed the target's trajectory: pupil and iris moved so that their center aligned with the target center.
-The target flight was covered so that participants could not see where the target landed.
-Participants' task was to locate the target by tracking the agent's gaze.
-They could respond by clicking or touching on the screen.
-
-Four familiarization trials ensured that participants understood the task and felt comfortable with the response format.
-Then, 15 test trials followed.
-Completing the 19 trials took approximately 5-10 minutes.
-
-The outcome measure depended on the task version.
-In the continuous \emph{hedge version}, we assessed imprecision defined as the absolute difference between the target center and the x coordinate of the participant's click.
-In the discrete \emph{box version}, we calculated the proportion of correct responses.
-
-The randomization of the final target location also depended on the task version.
-In the hedge version, the screen width was divided into ten bins, while exact coordinates within each bin were randomly generated during runtime.
-In the box version, the target randomly landed in one of the boxes.
-We adjusted the task difficulty according to participants' age: children were presented with five boxes while adults were presented with eight boxes.
-Each bin/box, as well as all agents and target colors, occurred equally often and and did not appear in more than two consecutive trials.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{../figures/procedure}
-
-}
-
-\caption{\textbf{Setup of the TANGO}.
-(A) Infrastructure for online testing.
-(i) Subjects aged 3 -- 99+ can participate.
-Data collection can take place anywhere: online, in kindergartens, or research labs.
-(ii) The task is presented as a website that works across devices.
-(iii) The scripts for the website and the recorded data are stored on secure local servers.
-(B) Hedge version (continuous) of the gaze understanding task.
-(i) The agent stands in a window with the target in front of them.
-(ii) A hedge grows and covers the target.
-(iii) The target falls to a random location on the ground.
-The agent's eyes track the movement of the target.
-(C) Box version (discrete) of the gaze understanding task.
-Number of boxes (min.
-1; max.
-8) as potential hiding locations can be set according to the researcher's need.}\label{fig:fig1}
-\end{figure}
+We used the continuous version of the TANGO (Prein et al., 2023).
+The task was presented as a web application (demo \href{https://ccp-odc.eva.mpg.de/tango-demo/.}{https://ccp-odc.eva.mpg.de/tango-demo/}; source code \url{https://github.com/ccp-eva/tango-demo}).
+The TANGO showed satisfactory internal consistency and retest reliability for children and adults (reliability estimates \emph{Pearson's r} from .7 to .8; (Prein et al., 2023)).
 
@@
 
-In the in-person sample, children were tested on a tablet in a quiet room in their kindergarten.
-An experimenter guided the child through the study.
-Half of the sample completed the continuous task version, while the other half completed the discrete task version.
-
-In the remote sample, children and teenagers received a personalized link to the study website.
-Caregivers were asked to provide technical support whenever needed, while explicitly being reminded to not help their children in responding.
-Webcam videos were recorded whenever consented and technically feasible, in order to monitor whether children and teenagers responded on their own.
-
-In the remote sample for children from three to five years old, the family's presentation device determined the task version.
-Whenever a touchscreen was available, the continuous task version was presented.
-For families using a computer without touchscreen, the discrete task version was shown.
-Here, children were asked to point to the screen while the caregivers should execute the clicking for their children.
-
-The number of teenagers in our internal database for recruiting families substantially decreased by age.
-To avoid small sample sizes, we decided to only employ the continuous task version for our 7- to 17-year-olds.
-Hence, children aged 7 years+ completed the continuous task version, independently from their presentation device.
-
-The remote adult sample was equally distributed across the two task versions.
+Children and teenagers received a personalized link to the study website.
+Caregivers were asked to provide technical support, while explicitly being reminded not to help in responding.
+Webcam videos were recorded whenever consented and technically feasible in order to monitor whether children and teenagers responded on their own.
+Adults completed the online study unsupervised.
+
+Each trial presented an agent standing in a window, watching a balloon (\emph{i.e.}, target) falling to the ground (see Figure \ref{fig:fig4}A; however, Study 1 presented animal agents).
+The target fell behind a hedge while the agent's gaze followed the target's trajectory.
+In test trials, a hedge covered the target's position.
+Participants were asked to touch or click where they estimated the target to be based on the agent's gaze.
+Four familiarization trials ensured participants understood the task and felt comfortable with the response format.
+Then, 15 test trials followed.
+Completing 19 trials took 5-10 minutes.
+
+We measured imprecision, defined as the absolute difference between the target center and the x coordinate of the participant's click.
+The screen width was divided into ten bins.
+Within each bin, exact target coordinates were randomly generated.
+Each target bin, agent, and target color occurred equally often and did not appear in more than two consecutive trials.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  TODO: non-linear model for development
-\end{itemize}
-
-All test trials without voice-over description were included in our analyses.
-We ran all analyses in R version 4.3.0 (2023-04-21) (R Core Team, 2022).
-Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors for all analyses, using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
-
-To estimate the developmental trajectory of gaze understanding and the effect of data collection mode, we fit a GLMM predicting the task performance in each trial by age (in months, z-transformed) and data collection mode (reference category: in-person supervised).
-The model included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants (model notation in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
-Here, \texttt{targetPosition} refers to the exact bin/box of the target, while \texttt{symmetricPosition} refers to the absolute distance from the stimulus center (i.e., smaller value meaning more central target position).
-We expected that trials could differ in their difficulty depending on the target centrality and that these item effects could vary between participants.
-
-For the hedge version, performance was defined as the absolute click distance between the target center and the click X coordinate, scaled according to target widths, and modeled by a \texttt{lognormal} distribution.
-For the box version, the model predicted correct responses (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
-We inspected the posterior distribution (mean and 95\% Confidence Interval (CI)) for the age and data collection estimates.
+We ran all analyses in R version 4.3.2 (2023-10-31) (R Core Team, 2022).
+Regression models were fit as Bayesian generalized linear mixed models (GLMMs) with default priors using the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017, 2018).
+
+We fit GLMMs that make different assumptions about the developmental trajectory, modeling the relationship between age and performance as linear, quadratic, or cubic.
+In addition, we fit a Gaussian Process model (Bürkner, 2017), which assumes a smooth relationship but avoids enforcing a particular shape.
+Per individuum, imprecision was aggregated across trials and modeled as a \texttt{lognormal} distribution.\footnote{Originally, we fit our models on a trial-by-trial basis with the following structure: \texttt{performance\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}.
+However, the Gaussian Process model was computationally heavy.
+Thus, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+See Supplements for a comparison between the original and the here-reported model structures.
+The model predictions did not differ notably.} The unit of imprecision was counted in target widths, i.e., an imprecision of 1 meant clicking one balloon width to the left or right of the true target center.
+We inspected the posterior distributions (mean and 95\% Credible Interval (CrI)) for the age estimates and compared models via model weights and the difference in expected log pointwise predictive density (ELPD) estimated using leave-one-out cross-validation (LOO) (Vehtari et al., 2017).
+
+To obtain a concise but principled characterization of the developmental trajectory, we additionally performed a Bayesian change point analysis, using the package \texttt{RBeast} (Zhao et al., 2019).
+We sought the most likely change points in our data, assuming a constant mean (i.e., a flat line, zero degree polynomial) within each segment.
+To avoid ``overreactions'' to outlying data points, we constrained the model to have minimally 10 data points between consecutive change points (= half of the data points collected per adult decade).
+We inspected the posterior probability of different numbers of change points and the locations of these change points (mean and 95\% CrI).\footnote{In a supplementary analysis, we varied the parameters of our change point analysis and modified the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When we allowed more explorative room, the models became more sensitive and added more fine-grained change points.
+The exact location of the change points varied slightly.
+However, the overall interpretation stayed the same, fitting our initial visual inspection: while early childhood was characterized by much change, adults showed a relatively stable level of imprecision, with a minor decay toward elderly adulthood.
+See Supplements for further detail.}
 
@@
 
-\caption{\textbf{Differentiation in gaze understanding}.
-Performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials).
-The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.}\label{fig:fig2}
+\caption{\textbf{Developmental trajectory of gaze understanding across the lifespan}.
+Grey dots show the mean level of imprecision (ie., absolute distance between the target's center and the participant's click) for each subject averaged across trials.
+The unit of imprecision is counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
+Blue lines show 100 draws from the expectation of the posterior predictive distribution of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
+Vertical, black, dashed lines show the locations of the most prominent changes according to our Bayesian change point analysis.}\label{fig:fig1}
 \end{figure}
+
+High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = 0.81, sd = 0.82, range = {[}0 - 10.73{]}).
+We found substantial evidence for a non-linear development in gaze understanding across the lifespan.
+The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd\_diff between Gaussian process and cubic model = -33.75 (SE = 8.83); elpd\_diff between Gaussian process and quadratic model = -95.07 (SE = 15.19); elpd\_diff between Gaussian process and linear model = -127.17 (SE = 18.18); all in favor of the Gaussian process model.
+Moreover, the Gaussian Process model showed the greatest model weight (approximating 1).
+For the imprecision in gaze understanding, the standard deviation (\emph{b} = 1.52, 95\% CrI {[}0.25; 5.19{]}) indicated nonlinearity.
+
+The Bayesian change point analysis revealed 6 major shifts in gaze understanding during the lifespan (MAP estimate with 23.49\% probability).
+The change points occurred at 4.23 (95\% CrI {[}4.13; 4.33{]}); 5.71 (95\% CrI {[}5.38; 5.90{]}); 6.98 (95\% CrI {[}6.64; 8.04{]}); 9.94 (95\% CrI {[}8.66; 12.55{]}); 35.97 (95\% CrI {[}27.30; 39.69{]}); and 44.01 years (95\% CrI {[}40.37; 44.43{]}).
+In short: we found a rapid initial improvement in gaze understanding in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward old age.
 
@@
 
-Three-year-olds were surprisingly inaccurate in their responses.
-One possible explanation could be that they simply lacked the ability to complete the task, potentially due to issues in gaze following.
-Contrasting our results with previous findings on infant gaze following, this explanation is unlikely.
-A more likely explanation would be that children were able to follow the agent's gaze but struggled to translate this implicit understanding into active behavior.
-
-Another point to keep in mind is that we used subtle eye movements as cues.
-Many existing studies let the agents move eye and head in parallel, therefore establishing a confound with greater (head) movement.
-Relying exclusively on the eye movement might be trickier for children than when presented with a combined eye and head orientation.
-
-The performance of the youngest children seems more consistent with performance demands than with a failure in gaze following.
-
-\hypertarget{computational-cognitive-model}{%
-\section{Computational cognitive model}\label{computational-cognitive-model}}
-
-\begin{itemize}
-\tightlist
-\item
-  model auch für warum ältere Erwachsene schlecht? anders schlecht als kinder?
-\item
-  entwicklungsperspektive basierend auf model
-\item
-  dann prozess-ebene = magnet
-\end{itemize}
+We investigated the shape of change in gaze understanding across the lifespan and found a non-linear developmental trajectory, in which young children quickly enhanced their level of proficiency.
+Performance peaked around early adulthood, while there was a minor decay in later adulthood.
+This is consistent with the view that humans fine-tune their existing gaze understanding ability after the first emergence in infancy.
+Furthermore, we observed substantial individual differences in all age groups.
+While variation was highest in the three- and four-year-olds, it remained relatively stable across the lifespan.
+
+Previous studies found that children start to follow gaze in the second half of their first year of life (e.g., Moll \& Tomasello, 2004).
+In our sample, three-year-olds were still rather imprecise in their gaze understanding ability (average imprecision was approx.
+two target widths).
+How can we explain this divergence?
+First, we used subtle eye movements as cues.
+Many existing studies let the agents move eye and head in parallel (Behne et al., 2005; Povinelli et al., 1997), establishing a confound with the more salient head movement.
+Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation (Carpenter et al., 1998).
+Silverstein et al.
+(2021) used a similar manipulation of gaze cues without head rotation and found that 6- to 18-month-olds were around or just above chance for gaze-following.
+The authors argue that infants might fixate on another's face most of the time, while eye movement alone might not be strong enough to guide their attention.
+Furthermore, our study required participants to (1) precisely follow an agent's gaze, (2) interpret this as a cue, and (3) use the cue to guide their own behavior.
+It is conceivable that three-year-olds followed the agent's gaze but did not translate this into precise, active behavior.
+Moll and Kadipasaoglu (2013) argue that social forms of perspective-taking evolve prior to visual perspective-taking, which only emerges within the third year of life.
+Young children might simply not be interested in a differential, spatial representation of the surrounding objects.
+Taken together, this might explain why our younger participants located the agent's gaze rather imprecisely.
+
+Regarding our sample of elderly adults, we expect a sampling bias (Bethlehem, 2010; Gosling et al., 2004; Remillard et al., 2014).
+First, certainly not all older people have a high-speed internet connection or are knowledgeable in its use.
+Second, it takes motivation to participate in \emph{Prolific} studies.
+The elderly adults participating in \emph{Prolific} studies might show greater cognitive flexibility compared to their offline counterparts.
+Therefore, a representative sample may show a greater age decline in gaze understanding compared to our reported sample.
+In addition, older people might be more likely to suffer from visual impairments.
+Even though we filtered participants to only include normal- to correct-to-normal vision, we cannot guarantee that our participants showed no symptoms of reduced vision.
+
+\hypertarget{study-2-computational-cognitive-model}{%
+\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
+
+Our lifespan study showed that gaze understanding develops throughout childhood, and variation between individuals appears in all age groups.
+The TANGO has previously been shown to reliably capture inter-individual differences in gaze understanding (Prein et al., 2023).
+The variation between participants was thus likely genuine and not due to random noise.
+In Study 2, we aimed to understand the developmental change and individual differences on a process level.
+We present a theory of gaze understanding that explains how participants process the available gaze information to identify the agent's focus.
+We formalized this inference process in a computational cognitive model that replicates a schematic representation of how participants make inferences in the task's context (i.e., model of the task and not the data).
+
+The study design and procedure obtained ethical clearance in the same way as Study 1 and was pre-registered: \url{https://osf.io/r3bhn}. Data were collected between May and August 2021.
+
+\hypertarget{computational-model}{%
+\subsection{Computational model}\label{computational-model}}
+
+A formal definition of our computational cognitive model can be found in the Appendix.
+Broadly summarizing, our gaze model assumes participants to click at a certain point where two estimated gaze vectors meet.
+Each of these gaze vectors implies an estimated pupil angle for each eye that results from connecting the center of the agent's eyeball and the center of the pupil (see Figure \ref{fig:fig2}A).
+These angles are sampled from a product of two independent Normal distributions with equal variance, which are centered around the true pupil angles.
+Development of gaze understanding corresponds to a decrease in variance of the Normal distributions and, therefore, a more precise localization of the attentional focus of the agent.
+
+The geometry of our model leads to a testable group-level prediction: the model predicted that TANGO trials vary in difficulty (see Figure \ref{fig:fig2}B and C): participants should be more imprecise in locating the target the further out it lands, resulting in a U-shaped pattern.
+If our data matched the pattern of this model prediction, this could act as evidence for the gaze model.
+Therefore, our gaze model provides a quantitative theory of gaze understanding.
+In the following, we tested these predictions in children and adults.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gazemodel}
+
+}
+
+\caption{\textbf{Gaze model} (A) Visualization of the gaze model (simplified, for one eye).
+Participants are assumed to observe the pupil location and estimate the center of the agent's eye.
+Connecting these two point estimates as a line yields the unique vector that extends from the center of the agent's eyeball through the center of the pupil to the attentional focal point.
+The angle between this vector and a line pointing vertically to the ground (black dashed line) is the pupil angle (\(\alpha\)).
+Participants are assumed to sample (grey lines) from Normal distributions (blue line) centered around the true pupil angle.
+The variance of the Normal distribution (\(\sigma_v\)) is expected to vary between participants.
+(B \& C) Geometrical features of the gaze model.
+As the pupil angle varies, a fixed amount of uncertainty in the angle corresponds to a varying degree of uncertainty in the estimated target location.
+The distribution around the target location from which participants sample is wider when the agent gazes toward the side than when she gazes centrally.
+The blue line on the ground shows the added level of uncertainty in the estimated target position for the target location further outward (C).}\label{fig:fig2}
+\end{figure}
 
@@
 
-The sample included the 58 three- to five-year-old children and 240 adults from our Lifespan study. For age distributions, see Participant section of the Lifespan Study.
-
-\hypertarget{non-social-vector-following}{%
-\section{Non-social vector following}\label{non-social-vector-following}}
-
-Task design, data collection, and sample sizes were pre-registered: \url{https://osf.io/xsqkt}.
-
-The study design and procedure obtained ethical clearance by the MPG Ethics commission Munich, Germany, falling under a packaged ethics application (Appl.
-No.~2021\_45), and was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology.
-The research adheres to the legal requirements of psychological research with children in Germany.
-Data were collected between February and March 2023.
+The sample consisted of 60 children, including 20 three-year-olds (mean age = 3.47 years, SD = 0.34, range = 3.07 - 3.97, 11 girls), 20 four-year-olds (mean age = 4.61 years, SD = 0.26, range = 4.09 - 4.98, 10 girls), 20 five-year-olds (mean age = 5.66 years, SD = 0.24, range = 5.01 - 5.96, 12 girls).
+Children were recruited via an internal database, where each parent previously consented to child development studies, and data was collected in kindergartens in Leipzig, Germany.
+
+In addition, we included 50 adults from Study 1 (mean age = 31.92 years, SD = 12.15, range = 18 - 63, 36 female).
+Since developmental change was minimal in our adult sample (see Study 1) and the cognitive models were computationally heavy, we decided to only include the first 50 adults who had completed the study.
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
+We applied the same procedure as in Study 1.
+Children were tested in a quiet room in their kindergarten, while an experimenter guided the child through the study on a tablet.
+Adults participated online.
+
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
+
+We quantified how well our gaze model explained the gaze understanding process in two ways.
+First, we aggregated the model predictions and data for each target bin and age group (3-, 4-, 5-years-olds, adults), and computed correlation to quantify how well the model was able to recover the data.
+Second, we compared the predictions of our gaze model to two simple alternative models that assume participants do not rely on the agent's gaze at all: a random guessing model and a center bias model.
+The random guessing model assumed participants randomly clicked on the screen and was implemented as sampling from a uniform distribution over all possible coordinates, \(\mathcal{U}(0, 1920)\).
+The center bias model assumed participants always clicked near the screen center and was implemented as sampling from a Normal distribution with the screen center as the mean, and one balloon width as the variance, \(\mathcal{N}(960, 160)\).
+Note that the center bias model also predicted imprecision should be higher for targets further out on the screen.
+However, compared to the gaze model, it predicted a steep effect towards the sides, resulting in a V-shaped pattern (imprecision as the distance between the target location and the screen center).
+All cognitive models were implemented in WebPPL (Goodman \& Stuhlmüller, 2014).
+
+We compared models via the marginal likelihood of the data under each model.
+The pairwise ratio of marginal likelihoods for two models is also known as the Bayes Factor, which quantifies the quality of a model's predictions by averaging over the possible values of the model's parameters weighted by the prior probabilities of those parameter values.
+It can be used to estimate how much more likely the data under one model are compared to the other.
+Bayes Factors implicitly consider model complexity: models with more parameters often have broader prior distributions over parameters, which might weaken potential gains in predictive accuracy.
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
+
+We found very clear support for our gaze model, both in children as well as adults.
+A strong correlation between the data mean and the gaze model estimate (\(\sigma_v\)) showed that the data mean is suitable to quantify individual differences: child sample \emph{r} = 0.95, 95\%CI {[}0.92, 0.97{]}; adult sample \emph{r} = 0.96, 95\%CI {[}0.93, 0.98{]}).
+The gaze model predicted a U-shaped pattern which we also observed in our data (see Figure \ref{fig:fig3}C).
+The model comparison strongly favored our gaze model over the center bias model (child sample \(logBF_{10}\) = 1,015.33; adult sample \(logBF_{10}\) = 2,575.75) and the random guessing model (child sample \(logBF_{10}\) = 388.98; adult sample \(logBF_{10}\) = 919.03).
+For the child sample, we went one step further into the analysis.
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: \emph{r} = 0.95, 95\%CI {[}0.90, 0.98{]}, while the correlations with the alternative models were smaller (center bias model: \emph{r} = 0.77, 95\%CI {[}0.57, 0.89{]}; random guessing model: \emph{r} = 0.78, 95\%CI {[}0.58, 0.89{]}).
+The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
+For children, we estimated the width of the prior's distribution based on the participants' age.
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = 300.14, 95\%HDI {[}277.19; 321.28{]}; slope = 1.18, 95\%HDI {[}0.00; 18.78{]}).
+The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gazemodel_plot}
+
+}
+
+\caption{\textbf{Gaze model} (A) Developmental trajectory of the estimated model parameter.
+Grey dots show individual level parameter values.
+The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it.
+The large black point with 95\% HDI shows the mean of the model parameter for the adult sample.
+We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting.
+(B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group.
+In the child sample, color denotes age in years.
+Grey regression lines with 95\% CI show smooth conditional means based on linear models, with \emph{Pearson}'s correlation coefficient \emph{r}.
+(C) Pattern recovery.
+Imprecision in target width for each target bin by age group.
+Model predictions in blue; data in grey.
+(D) Correlation between the observed data and the predictions of the three models by target position (across age and individuals; only for the child sample).}\label{fig:fig3}
+\end{figure}
+
+\hypertarget{discussion-1}{%
+\subsection{Discussion}\label{discussion-1}}
+
+We presented a formal cognitive model of gaze understanding to describe how gaze understanding develops with age and varies between individuals.
+We modeled gaze understanding as a process in which participants estimate pupil angles based on the pupil location within the eye.
+By following the resulting gaze vector, they consequently arrive at the attentional focus of the agent.
+Individual differences can be explained as varying levels of imprecision in the pupil angle estimation.
+We assume the basic process of gaze understanding to be the same across the lifespan, though individuals become increasingly precise with age.
+By conducting model comparisons, we ruled out simpler explanations of the data.
+
+In addition, we observed differences in performance depending on gaze location: participant data showed that precision levels dropped as the agent's gaze moved further away from the center.
+Our gaze model predictions recovered this ``signature pattern'' in the data.
+Future research could use this signature in the data as evidence of whether diverse communities employ the same inferential mechanism to solve the task, speaking for a shared cognitive architecture.
+
+Interestingly, the U-shaped pattern in the TANGO task can be conceptually compared to the result patterns of Michelon and Zacks (2006): in their Level 1 perspective-taking task, an increased distance between the agent and the target decreased performance (i.e., reaction times).
+Targets closer to the midline were more easily traced than ones further away from the agent.
+The authors concluded that visual acuity is generally higher for locations on the vertical than the diagonal axis (``oblique effect''; (Appelle, 1972; Heeley et al., 1997; Mikellidou et al., 2015)).
+Not only is the increased imprecision for TANGO trials in which the target lands further out consistent with this finding, but our gaze model poses a viable explanation for this effect.
+
+A limitation of our model is that we cannot disentangle how much of the participants' uncertainty comes from a noisy estimate of the agent's attentional focus and how much is due to imprecise clicking (e.g., experiencing motor issues, adding random noise to the click).
+However, we believe imprecise clicking to be of minor concern, since the children in our sample seemed determined in where they clicked and to not have issues with aiming or motor control (see precision in training trials).
+
+A critical feature of our model is that it assumes gaze understanding to rely on vector estimation: subjects are modeled to calculate pupil angles which serve as gaze vectors to point to the attentional focus point of an agent.
+Even though this vector estimation component is a geometrical calculation, one must first interpret the agent's eyes as a relevant social stimulus.
+Therefore, our model describes gaze understanding as a particular form of vector estimation in a social context.
+
+\hypertarget{study-3-components-of-gaze-understanding}{%
+\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
+
+Study 3 examined the components of gaze understanding and whether it can be fully reduced to physical vector estimation.
+The positive link between TANGO and social-environmental factors like age of childcare entry (Prein et al., 2023) underline how gaze understanding is integral to social interaction.
+Therefore, we expected associations between gaze understanding and other measures of social-cognitive abilities.
+
+First, we experimentally isolated the vector estimation component of the TANGO.
+We designed a new non-social vector estimation task that shared all crucial design features of the TANGO.
+Second, we assessed children's social-cognitive abilities by administering a Theory of Mind (TOM) task battery, comprising four tasks from the ToM scale by Wellman and Liu (Wellman \& Liu, 2004) and two additional perspective-taking tasks (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981).
+We reasoned that the TANGO shares task demands with the non-social vector estimation task while it shares its social context with the ToM tasks.
+As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze understanding.
+Our reasoning was that similar underlying mechanisms might be needed to solve these tasks since they require participants to take into account another person's point of view.
+
+Data collection was pre-registered (\url{https://osf.io/xsqkt}) and took place in Leipzig, Germany, between February and March 2023.
 
@@
 
-The sample consisted of 102 children (mean age = 4.54 years, SD = 0.31, range = 3.99 - 5.03, 54 girls),
-
-\begin{itemize}
-\item
-  gut, dass unser maß ind diff messen kann, das nutzen wir jetzt
-\item
-  zsmhang mit vector following, aber nicht redundant
-\item
-  perspective-taking auch, aber auch nicht relevant, nicht theory of mind score
-\item
-  diskutieren dass die maße auch nict ind diff maße sind
-\item
-  model vergleich: welche komponente stecken in gafo drin?,
-  welchen beitrag liefern die um score zu erklären?
-  welche wichtiger, tom oder nur perspective taking
-\item
-  magnet versuch das vector following zu isolieren.
-  ist da noch was anderes außerhalb vector-following?
-\item
-  aggregierte messungen immer besser, nur indikatoren für konstrukt
-\end{itemize}
+The sample consisted of 102 children (mean age = 4.54 years, SD = 0.31, range = 3.99 - 5.03, 54 girls). Information on individual socio-economic status was not formally recorded.
+
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
+
+Children were tested in a quiet room in their kindergarten.
+An experimenter guided the child through the study.
+For maximum control of extraneous participant variables, we employed a within-subjects study design.
+Participants performed the tasks in this order: (1) non-social vector estimation task, (2) ToM task battery, (3) TANGO.
+We decided on a fixed order to compare participants' performance straight-forwardly with each other.
+To increase engagement and decrease fatigue or fuzziness, we switched between tablet tasks and tasks with personal interaction.
+We presented the non-social vector estimation task before the TANGO so that participants would not be biased to interpret the stimuli as ``agent-like''.
+
+\hypertarget{non-social-vector-estimation}{%
+\subsubsection{Non-social vector estimation}\label{non-social-vector-estimation}}
+
+Modeling the structure of the TANGO, we designed a non-social vector estimation task.
+This task was presented on a tablet and used the concept of magnetism.
+On the upper part of the screen, there was a tube with a circular window, containing a gearwheel.
+On the floor, there was a magnet.
+The magnet got switched on (with a cartoon-like sound), whereupon the gearwheel moved towards the magnet.
+The gearwheel moved so that its center aligned with the magnet center while staying inside the circular window.
+Participants were then asked to locate the magnet.
+Access to the magnet's true location was manipulated by a wooden wall: participants either had full, partial, or no visual access to the true magnet location.
+Compared to the TANGO, the circular window acted functionally similar to the agent's eyeball, while the gearwheel acted similar to the pupil.
+Participants were expected to estimate a vector from the center of the circular window to the gearwheel and extend this as a line toward the ground to locate the magnet.
+We deliberately decided against displaying an arrow: we aimed to keep the mechanistic functions of the TANGO and magnet stimuli as similar as possible.
+In both cases, the starting point of the vector needs to be estimated by the participant.
+With an arrow, we would have drastically reduced the level of uncertainty, since the arrow already displays all information (arrow tip as the ``gaze'' direction).
+Furthermore, we wanted to avoid referential or iconic stimuli.
+
+Children received 19 trials with one full visual access trial, two partial visual access trials, and 16 test trials.
+The first trial of each type comprised a voice-over description of the presented events.
+We conducted our analysis with 15 test trials (excluding the voice-over trial).
+The outcome variable was imprecision, defined as the absolute distance between the magnet's x coordinate and the x coordinate of the participant's click.
+Magnet coordinates were randomized: The full width of the screen was divided into ten bins; each bin occurred equally often, while the same bin could occur in two consecutive trials; and exact coordinates within each bin were randomly generated.
+
+\hypertarget{tom-task-battery}{%
+\subsubsection{ToM task battery}\label{tom-task-battery}}
+
+We administered four tasks from the Wellman and Liu (2004) ToM scale (see Supplements for further detail).
+We excluded three tasks: the Diverse Desires task to avoid ceiling effects; and both tasks involving emotions (Belief Emotion and Real-Apparent Emotion), as we aimed at assessing the ``cold, cognitive'' (vs.~``emotional'') aspects of social cognition.
+We added two perspective-taking level-2 tasks (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981) with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze understanding, both relying on another's person egocentric frame of reference.
+
+\hypertarget{gaze-understanding}{%
+\subsubsection{Gaze understanding}\label{gaze-understanding}}
+
+As in Study 1 and 2, we presented children with the TANGO (Prein et al., 2023).
+To accentuate the social aspect of the TANGO, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance (already created for another project on cross-cultural similarities in gaze understanding (\url{https://osf.io/tdsvc})).
+This further highlighted the contrast (i.e., social vs.~non-social context) to the physical vector estimation task.\footnote{In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs.~human agents.
+Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice.
+See Supplements for further detail.}
+
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
+
+By design, the TANGO and the non-social vector estimation task involved vector estimation.
+Based on our computational model, we expected children's performance in both tasks to correlate with each other.
+For each task, we calculated the mean level of imprecision for each subject and correlated them using \emph{Pearson's} correlation coefficient.
+
+For the ToM battery, we aggregated the score of all solved tasks.
+Regarding the relationship between the two vector estimation tasks and the ToM measures, we could imagine two possible scenarios: (A) If gaze understanding recruited a social-cognitive ability beyond geometric vector estimation, we expected that ToM measures would correlate more strongly with the gaze understanding task than with the non-social vector estimation task.
+(B) If gaze understanding relied purely on task-specific geometric processes, then the correlation between gaze understanding and ToM measures would be comparable to the correlation between non-social vector estimation and the ToM measures.
+For the association between the aggregate ToM scores and the gaze understanding / non-social vector estimation tasks, we used \emph{Spearman's} rank correlation coefficients.
+
+We compared the correlation between gaze understanding and ToM measures and the correlation between non-social vector estimation and ToM measures by using the Williams' test from the function \texttt{cocor.dep.groups.overlap} (designed for two dependent overlapping correlations) from the package \texttt{cocor} (Diedenhofen \& Musch, 2015).
+
+To estimate which components best explain the gaze understanding score, we conducted a model comparison with GLMMs predicting the mean imprecision in gaze understanding by age, imprecision in non-social vector estimation, the ToM aggregate score, or the aggregate of the two perspective-taking tasks (subset of ToM battery; example of model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
+The outcome variable was modeled by a lognormal distribution.
+We wanted to assess whether the ToM aggregate score or the singled-out perspective-taking score added additional explanatory value when predicting the gaze understanding score.
+We hypothesized that perspective-taking seemed most closely theoretically related to gaze understanding as in both cases the participant was asked to judge another person's point of view.
+
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
+
+Gaze understanding substantially correlated with the non-social vector estimation task, \emph{r} = 0.38, 95\%CI {[}0.20, 0.53{]} (see Figure \ref{fig:fig4}B).
+Despite the designed overlap in task demands, the two vector estimation tasks were not redundant: only a part of the variance in gaze understanding could be explained by non-social vector estimation.
+
+ToM abilities did not correlate with gaze understanding (\(\rho\) = -0.12, 95\%CI {[}-0.31, 0.07{]}) or non-social vector estimation (\(\rho\) = -0.12, 95\%CI {[}-0.30, 0.08{]}), and the correlations did not differ from each other, Williams' test \emph{t}(99) = 0, \emph{p} = 1.
+
+Interestingly, gaze understanding and perspective-taking correlated with each other, \(\rho\) = -0.29, 95\%CI {[}-0.46, -0.10{]}.
+Please note that the negative correlation can be explained by the measure of imprecision in the TANGO (i.e., the more imprecise gaze understanding, the less perspective-taking).
+Non-social vector estimation and perspective-taking did not correlate, \(\rho\) = -0.09, 95\%CI {[}-0.28, 0.10{]}.
+However, according to the Williams' test, the two correlations did not differ significantly from each other, \emph{t}(99) = -1.86, \emph{p} = 0.07.
+
+Our model comparison revealed that gaze understanding was best predicted by a model including non-social vector estimation (\(\beta\) = 0.14, 95\% CrI {[}0.06; 0.21{]}) and perspective-taking (\(\beta\) = -0.10; 95\% CrI {[}-0.17, -0.03{]}), even when controlling for age (\(\beta\) = -0.14, 95\% CrI {[}-0.38, 0.10{]}) (see Figure \ref{fig:fig4}C and Supplements for the model comparison).
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{../figures/magnet_plot}
+
+}
+
+\caption{\textbf{Components of gaze understanding.} (A) Study procedures.
+Top: TANGO (i.e., gaze understanding; social vector estimation).
+Bottom: Magnet (i.e., non-social vector estimation).
+The left-hand side shows screenshots of the familiarization phase; right-hand side shows screenshots of the test phase.
+(B) Correlations between gaze understanding, physical vector estimation, ToM, and perspective-taking.
+Dots show the correlation coefficients, error bars represent 95\% CIs.
+(C) Influence of age, perspective-taking and physical vector estimation on gaze understanding.
+The graph shows the posterior distributions for the respective predictor.
+Black dots represent means, thicker black lines 80\% CrI, and thinner black lines 95\% CrI.}\label{fig:fig4}
+\end{figure}
+
+\hypertarget{discussion-2}{%
+\subsection{Discussion}\label{discussion-2}}
+
+Our gaze model assumed vector calculations on a process level.
+By isolating physical vector estimation experimentally, we could show that gaze understanding does indeed, to a certain degree, rely on this component.
+However, physical vector estimation alone did not suffice to explain variation in gaze understanding.
+Additionally, perspective-taking proved to be a relevant social-cognitive ability when predicting the performance in the TANGO (cf.
+Astor \& Gredebäck, 2022).
+The overall ToM aggregate score did not add explanatory power.
+
+The TANGO and the two perspective-taking tasks can be seen as instances of visuospatial perspective-taking.
+Often, researchers distinguish between Level 1 and Level 2 perspective-taking tasks.
+Level 1 perspective-taking is concerned with the visibility of objects from a particular viewpoint (Surtees et al., 2013), and can usually be solved independently from another's agent frame of reference and without mental rotation {[}not matching the ``mentalizing criterion''; Quesque and Rossetti (2020){]}.
+In contrast, Level 2 perspective-taking tasks ask participants to judge how (visually or conceptually) the world looks for another person.
+Solving these tasks presumably relies on a simulation of mentally transforming one's own body schema into the space of another agent (Erle \& Topolinski, 2017).
+Participants must understand that different viewpoints lead to different perspectives (Flavell, Everett, et al., 1981): two agents can see the same object ``in different, incompatible, fine-grained ways'' (Rakoczy, 2022).
+In short, Level 1 perspective-taking addresses \emph{what} an agent can see, while Level 2 perspective-taking addresses \emph{how or where} they see it (Moll \& Tomasello, 2006).
+The TANGO falls into the first category - however, in contrast to existing research, on a continuous scale - while the perspective-taking tasks within our ToM scale fall into the second category.
+
+In the TANGO, participants locate the target by assuming that another agent perceives and looks at the it.
+The here-applied Level 2 perspective-taking tasks add another layer by asking how one's perspective differs from another's and how exactly the other person sees an object.
+Michelon and Zacks (2006) assessed the different processes that participants used to master Level 1 and Level 2 perspective-taking tasks and concluded that participants rely on line-of-sight tracing in the former and perspective transformation in the latter case.
+Line-of-sight tracing consists of locating the avatar and the target, and drawing a line between them.
+Note how our gaze model in Study 2 shares the underlying idea of connecting points in space via a line.
+Level 2 perspective-taking requires an additional step in which participants ``perform a perspective transformation so that one's imagined position matches the position of the avatar'' (Michelon \& Zacks, 2006).
+Therefore, the processes to solve Level 1 perspective-taking tasks might be computationally lighter since there is no need to adapt the other person's reference frame.
+Still, the assumed processes overlap, which could explain the correlation between the TANGO and the administered perspective-taking tasks.
+
+Surtees et al.
+(2013) further differentiated between visual and spatial perspective-taking.
+While the former helps to judge if and how an agent sees an object, the latter involves judging the relative spatial locations of an agent and the object.
+Spatial perspective-taking does not necessitate mental states since computing a line of sight does not demand the presence of another agent (Michelon \& Zacks, 2006) and can, therefore, be applied to non-agentive objects with a front (Surtees et al., 2013).
+This could explain how our participants solved the non-social vector estimation task.
+
+Interestingly, we found weaker correlations between gaze understanding and the other ToM tasks.
+While the ToM tasks and the TANGO shared the social context, the cognitive processes needed to solve each task might vary.
+As Rakoczy (2022) reflected, perception-goal psychology (which includes gaze understanding) comprises understanding that others see different objects or pursue different goals.
+However, this ability does not necessarily entail understanding more complex meta-representational aspects; for example, understanding that mental states can be false or involve aspectual information.
+
+In previous work, we established that the TANGO is suited to capture meaningful variability across individuals (Prein et al., 2023), which is a crucial task feature when we are interested in revealing the relationship between different cognitive abilities.
+Importantly, the tasks we used to measure ToM abilities were not designed to capture individual differences: the aggregate score of few dichotomous items is of limited use when it comes to quantifying genuine differences between individuals.
+However, since these tasks are the gold standard in the social-cognitive literature (Białecka-Pikul et al., 2021; Byom \& Mutlu, 2013; Poulin-Dubois et al., 2023; Rakoczy, 2022; Wellman, 2018), and measures with satisfying psychometric properties are, to the best of our knowledge, still scarce (e.g., Beaudoin et al., 2020; Mayes et al., 1996), we nonetheless relied on them in this study.
+Thus, lower correlations between ToM abilities and gaze understanding may reflect poor measurement characteristics on the side of ToM tasks rather than a genuine absence of association.
+We would like to point out that we already stated this concern in our pre-registration (\url{https://osf.io/xsqkt}).
+
+If the reliability of the tasks at hand is known, one can estimate the ``true'' correlation between the latent constructs by applying an attenuation formula or structural equation models (Metsämuuronen, 2022; Trafimow, 2016).
+Adjusting for the measurement error would increase the so-called true correlation.
+While we can estimate the split-half reliability for the TANGO and the non-social vector estimation task (Prein et al., 2023), we do not have reliability estimates of the ToM measures and cannot apply said approaches.
+This, in turn, underlines the importance of reporting the psychometric properties of a task.
+The development of new measures to capture individual differences in social-cognitive abilities seems essential to move this research further.
+
+\hypertarget{general-discussion}{%
+\section{General discussion}\label{general-discussion}}
+
+In three studies, we shed light on the cognitive process underlying gaze understanding and its developmental trajectory across the lifespan.
+Study 1 focused on how gaze understanding changes with age.
+We found a steep performance improvement in the preschool years in which children became more precise in locating the attentional focus of an agent.
+During teenage years and early adulthood, participants reached their peak performance.
+Precision levels then stayed comparably stable, with a minor decay toward older adulthood.
+Beyond these aggregated developmental patterns, we found that individual differences exist throughout the lifespan.
+In Study 2, we proposed a computational cognitive model that described gaze understanding at a process level.
+We modeled gaze understanding as a process in which participants use the pupil location within the eyes to estimate pupil angles.
+To locate the attentional focus of an agent (and find a target), they extend the resulting gaze vector towards the ground.
+Individuals vary in their levels of uncertainty around these pupil angles.
+Our gaze model outperformed two alternative models, which assumed participants solved the task via a center bias or random guessing.
+Knowing the TANGO to be a reliable individual differences measure, we investigated potential components of gaze understanding in Study 3.
+A fundamental assumption of our computational model was that gaze understanding relies on a vector estimation process.
+We experimentally isolated this component by designing a non-social vector estimation task.
+Furthermore, we assessed the relationship between gaze understanding and traditional ToM tasks.
+We found that gaze understanding does, indeed, share a substantial part of its variance with the non-social counterpart of physical vector estimation.
+Additionally, perspective-taking correlated with gaze understanding, whereas the other ToM measures (focussing on diverse desires, knowledge access, and false beliefs) did not.
+
+The developmental trajectory seen in Study 1 shows how abilities that emerge in infancy can continue to develop throughout childhood.
+While previous research established that one-year-olds can orient their visual attention toward one out of two objects, this is not the end point of development.
+By studying gaze understanding on a continuum, we assessed not just \emph{whether}, but \emph{how precisely} children locate others' attentional focus.
+In previous work, we have shown that these individual differences are meaningful (e.g., connected to theoretically related constructs, and showing high split half and retest reliability; (Prein et al., 2023)).
+Capturing individual variation is crucial when we study development and the improvement in social-cognitive abilities.
+
+Preschool children increased their precision level to locate an agent's attentional focus, which then stayed comparably stable across adulthood.
+Older adults decreased slightly in their precision levels.
+This developmental trajectory of a first emergence with a rapid improvement, followed by a plateau and slight decline toward older age, might be representative of many cognitive processes.
+
+In Study 2, we proposed a theoretical framework to interpret the development and individual differences in gaze understanding.
+Our computational cognitive model assumes that participants estimate a pupil angle (i.e., the angle between a line extending vertically downwards from the pupil center and a line connecting the pupil and eye center; see Figure \ref{fig:fig2}A).
+The model parameter estimates a participant's latent ability to follow gaze and can explain why individuals differ in their precision to locate an agent's attentional focus.
+The model proposes that development in gaze understanding equals a reduction in noise when estimating the agent's pupil angles.
+We found strong evidence for the proposed gaze model when comparing it against two alternative models and correlating its predictions with the observed data (see Figure \ref{fig:fig3}D), both for children and adults.
+Notably, the model recovers signature patterns in the data (see Figure \ref{fig:fig3}C).
+
+In Study 3, we tested the relation between gaze understanding and non-social vector estimation.
+As implied by our gaze model, we found that gaze understanding relates to the ability to estimate vectors in space.
+This ability might be helpful in several social-cognitive tasks, for example, action prediction (Friesen \& Rao, 2011), and intention understanding.
+Predicting which object another agent likely wants to grasp or calculating their movement pathway could rely on similar vector estimation abilities.
+
+Even though our gaze model is designed within a 2D world, we believe the mechanisms can be extrapolated into the 3D world.
+The processes of understanding gaze in daily life likely rely on the same principles as proposed in this paper.
+We presented the first evidence that this might be the case.
+In Study 3, we administered Level 2 perspective-taking tasks in which participants needed to adapt another person's frame of reference in a real-world social interaction.
+The correlation between this task and the TANGO speaks toward a unified mechanism behind these two visual perspective-taking tasks, regardless of the testing setup (i.e., screen-based vs.~real-life interaction).
+Clearly, our real-life environment is visually more cluttered and diverse than the one presented in our tablet task.
+Here, however, additional informational sources are available to infer where others are looking; for example, body or head orientation or common ground (Bohn \& Köymen, 2018; Moll \& Kadipasaoglu, 2013; Osborne-Crowley, 2020).
+A previously shared interaction history might restrict the options we consider potential targets.
+From a modeling perspective, this might be represented as a non-uniform distribution over locations in the visual scenery.
+
+While we described the development and mechanisms behind gaze understanding, we still need to further explore the driving forces behind this development.
+As seen in Prein et al.
+(2023), precision in gaze understanding is linked to receptive vocabulary and opportunities for social interaction (e.g., number of siblings and age when entering childcare).
+Humans likely learn to follow gaze in social interactions (Triesch et al., 2006).
+Which exact kind of interactions are most helpful to improve precision in gaze understanding remains unknown.
 
@@
 
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
+In this paper, we have focused on studying variation across ages and individuals.
+However, our findings rely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) backgrounds (Henrich et al., 2010).
+Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communicative signals (Nielsen et al., 2017).
+First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts (Hernik \& Broesch, 2019).
+While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze understanding holds true across communities.
+Analyzing cross-cultural variation and checking for predicted ``signature patterns'' in the data will inform our modeling work and theory building in further detail (Amir \& McAuliffe, 2020).
+
+Moreover, our reported developmental trajectory in gaze understanding relied on a cross-sectional study.
+Longitudinal studies are needed to de-confound it from cohort effects and interpret the correlations between gaze understanding and other social-cognitive abilities.
+
+We applied the same experimental paradigm for children, teenagers and adults alike.
+While this enables a direct comparison in performance across ages, it remains unclear whether the same method measures the same underlying psychological process in humans of different ages (Petersen, 2023).
+As we find strong evidence for our computational gaze model in children and adults, we are optimistic that our task is valid throughout the lifespan.
+Furthermore, the testing setup might have influenced different age groups differentially.
+Children and teenagers are likely more trained in using a tablet than the older adults in our sample.
+Recruiting older participants online might also select a particular subgroup of this age range.
+Seventy-year-olds who have working WIFI connections, know how to use a computer, and are registered on \emph{Prolific} might not be representative of their age group.
+We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories toward old age.
+
+Our computational model of gaze understanding estimates one person-specific parameter for how accurately participants locate another person's attentional focus.
+The model assumes no motor imprecision in this estimation.
+However, younger children could have located the agent's focus at one particular point but clicked somewhere slightly off for motor control reasons.
+This would blur the model's estimation of the inferential component.
+However, in the first training trial, in which children were simply asked to touch the balloon, we found nearly perfect precision levels (cf.
+Prein et al., 2023).
+Motor issues and inaccurate aiming, resulting in falsely wide estimations in the model's inferential component, seem unlikely.
+
+In Study 3, we matched the non-social vector estimation task as closely as possible to the TANGO.
+However, a critical feature of the target object differed between the two tasks: in the TANGO, the target (= balloon) moved from the center of the screen to its final position in a self-propelled, continuous way.
+In the non-social vector estimation task, the target (= magnet) stayed stationary on the ground.
+Two possible critiques come to mind: first, the self-propelled movement of the balloon could evoke a sense of agency, which would not be the case for the magnet.
+Second, the starting positions differ: the magnet never appears in the center of the screen.
+Keeping the starting point of the balloon in mind might be especially important when interpreting the U-shaped pattern found in Study 2.
+Additionally, in the TANGO, two eyes are presented and information of the two (matching) cues needs to be integrated to infer the target's location.
+In the non-social vector estimation task, only one circular window with a gearwheel inside is presented as a directional cue, and there is no need to integrate two different information sources.
+Future research should investigate how factors like self-propelled movement, sense of agency, spatial layout, and number of information sources influence the mechanisms of gaze understanding.
 
@@
 
-\newpage
-
-\hypertarget{declarations}{%
-\section{Declarations}\label{declarations}}
-
-\hypertarget{open-practices-statement}{%
-\subsection{Open practices statement}\label{open-practices-statement}}
-
-The web application (\url{https://ccp-odc.eva.mpg.de/tango-demo/}) described here is open source (\url{https://github.com/ccp-eva/tango-demo}).
-The data sets generated during and/or analysed during the current study are available in the {[}gazecues-modeling{]} repository (\url{https://github.com/ccp-eva/gazecues-modeling}).
-All experiments were pre-registered (\url{https://osf.io/zjhsc/}).
-
-\hypertarget{funding}{%
-\subsection{Funding}\label{funding}}
-
-This study was funded by the Max Planck Society for the Advancement of Science, a noncommercial, publicly financed scientific organization (no grant number).
-We thank all the children, caregivers, and adults who participated in the study.
-We thank Jana Jurkat for her help with data collection.
-
-\hypertarget{conflicts-of-interest}{%
-\subsection{Conflicts of interest}\label{conflicts-of-interest}}
-
-The authors declare that they have no conflict of interest.
-
-\hypertarget{consent-to-participate}{%
-\subsection{Consent to participate}\label{consent-to-participate}}
-
-Informed consent was obtained from all individual participants included in the study or their legal guardians.
-
-\hypertarget{authors-contributions}{%
-\subsection{Authors' contributions}\label{authors-contributions}}
-
-The authors made the following contributions: \#\#\# TODO
+In three studies, we have illuminated the development and the mechanisms of gaze understanding.
+We have shown that gaze understanding continues to develop beyond infancy, and that individuals differ in their precision levels to localize the attentional focus of an agent.
+Our proposed process-level theory successfully modeled the mechanisms of gaze understanding and the source of individual differences.
+The present research shows how precise and reliable measures and process models jointly inform each other and lead to a more comprehensive understanding of the psychological phenomenon in question.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-amir2020crosscultural}{}}%
+Amir, D., \& McAuliffe, K.
+(2020).
+Cross-cultural, developmental psychology: Integrating approaches and key insights.
+\emph{Evolution and Human Behavior}, \emph{41}(5), 430--444.
+\url{https://doi.org/10.1016/j.evolhumbehav.2020.06.006}
+
+\leavevmode\vadjust pre{\hypertarget{ref-appelle1972perception}{}}%
+Appelle, S.
+(1972).
+Perception and discrimination as a function of stimulus orientation: {The} "oblique effect" in man and animals.
+\emph{Psychological Bulletin}, \emph{78}(4), 266--278.
+\url{https://doi.org/10.1037/h0033117}
+
+\leavevmode\vadjust pre{\hypertarget{ref-aslin2007look}{}}%
+Aslin, R. N. (2007). What's in a look? \emph{Developmental Science}, \emph{10}(1), 48--53. \url{https://doi.org/10.1111/j.1467-7687.2007.00563.x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-astor2022gaze}{}}%
@@
 S0065240722000192).
-{Elsevier}.
+Elsevier.
 \url{https://doi.org/10.1016/bs.acdb.2022.04.003}
+
+\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
+Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., Tharner, A., Cassé, J., \& Gredebäck, G.
+(2020).
+Social and emotional contexts predict the development of gaze following in early infancy.
+\emph{Royal Society Open Science}, \emph{7}(9), 201178.
+\url{https://doi.org/10.1098/rsos.201178}
+
+\leavevmode\vadjust pre{\hypertarget{ref-beaudoin2020systematic}{}}%
+Beaudoin, C., Leblanc, É., Gagner, C., \& Beauchamp, M.
+H.
+(2020).
+Systematic {Review} and {Inventory} of {Theory} of {Mind Measures} for {Young Children}.
+\emph{Frontiers in Psychology}, \emph{10}, 2905.
+\url{https://doi.org/10.3389/fpsyg.2019.02905}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-brooks2002importance}{}}%
-Brooks, R., \& Meltzoff, A.
-N.
-(2002).
-The importance of eyes: {How} infants interpret adult looking behavior.
-\emph{Developmental Psychology}, \emph{38}(6), 958--966.
-\url{https://doi.org/10.1037/0012-1649.38.6.958}
+\leavevmode\vadjust pre{\hypertarget{ref-bethlehem2010selection}{}}%
+Bethlehem, J. (2010). Selection {Bias} in {Web Surveys}. \emph{International Statistical Review}, \emph{78}(2), 161--188. \url{https://doi.org/10.1111/j.1751-5823.2010.00112.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bialecka-pikul2021early}{}}%
+Białecka-Pikul, M., Białek, A., Kosno, M., Stępień-Nycz, M., Blukacz, M., \& Zubek, J.
+(2021).
+Early mindreading scale: {From} joint attention to false-belief understanding.
+\emph{European Journal of Developmental Psychology}, \emph{0}(0), 1--18.
+\url{https://doi.org/10.1080/17405629.2021.1911799}
+
+\leavevmode\vadjust pre{\hypertarget{ref-birch2017perspectives}{}}%
+Birch, S.
+A.
+J., Li, V., Haddock, T., Ghrear, S.
+E., Brosseau-Liard, P., Baimel, A., \& Whyte, M.
+(2017).
+Perspectives on {Perspective Taking}.
+In \emph{Advances in {Child Development} and {Behavior}} (Vol.
+52, pp.
+185--226).
+Elsevier.
+\url{https://doi.org/10.1016/bs.acdb.2016.10.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2019pervasive}{}}%
+Bohn, M., \& Frank, M.
+C.
+(2019).
+The {Pervasive Role} of {Pragmatics} in {Early Language}.
+\emph{Annual Review of Developmental Psychology}, \emph{1}(1), 223--249.
+\url{https://doi.org/10.1146/annurev-devpsych-121318-085037}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bohn2018common}{}}%
+Bohn, M., \& Köymen, B. (2018). Common {Ground} and {Development}. \emph{Child Development Perspectives}, \emph{12}(2), 104--108. \url{https://doi.org/10.1111/cdep.12269}
 
 \leavevmode\vadjust pre{\hypertarget{ref-burkner2017brms}{}}%
-Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1). \url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-byers-heinlein2021development}{}}%
+Byers-Heinlein, K., Tsui, R.
+K.-Y., van Renswoude, D., Black, A.
+K., Barr, R., Brown, A., Colomer, M., Durrant, S., Gampe, A., Gonzalez-Gomez, N., Hay, J.
+F., Hernik, M., Jartó, M., Kovács, Á.
+M., Laoun-Rubenstein, A., Lew-Williams, C., Liszkowski, U., Liu, L., Noble, C., \ldots{} Singh, L.
+(2021).
+The development of gaze following in monolingual and bilingual infants: {A} multi-laboratory study.
+\emph{Infancy}, \emph{26}(1), 4--38.
+\url{https://doi.org/10.1111/infa.12360}
+
+\leavevmode\vadjust pre{\hypertarget{ref-byom2013theory}{}}%
+Byom, L., \& Mutlu, B. (2013). Theory of mind: Mechanisms, methods, and new directions. \emph{Frontiers in Human Neuroscience}, \emph{7}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-carpenter1998social}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-coelho2006searching}{}}%
-Coelho, E., George, N., Conty, L., Hugueville, L., \& Tijus, C.
-(2006).
-Searching for asymmetries in the detection of gaze contact versus averted gaze under different head views: A behavioural study.
-\emph{Spatial Vision}, \emph{19}(6), 529--545.
-\url{https://doi.org/10.1163/156856806779194026}
-
-\leavevmode\vadjust pre{\hypertarget{ref-colombo2001development}{}}%
-Colombo, J. (2001). The development of visual attention in infancy. \emph{Annual Review of Psychology}, \emph{52}, 337--367. \url{https://doi.org/10.1146/annurev.psych.52.1.337}
+\leavevmode\vadjust pre{\hypertarget{ref-corkum1995development}{}}%
+Corkum, V., \& Moore, C. (1995). Development of joint visual attention in infants. In \emph{Joint attention: {Its} origins and role in development} (pp. 61--83). Lawrence Erlbaum Associates, Inc.
+
+\leavevmode\vadjust pre{\hypertarget{ref-corkum1998origins}{}}%
+Corkum, V., \& Moore, C. (1998). The origins of joint visual attention in infants. \emph{Developmental Psychology}, \emph{34}(1), 28--38. \url{https://doi.org/10.1037/0012-1649.34.1.28}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-frischen2007gaze}{}}%
-Frischen, A., Bayliss, A.
-P., \& Tipper, S.
-P.
-(2007).
-Gaze cueing of attention: {Visual} attention, social cognition, and individual differences.
-\emph{Psychological Bulletin}, \emph{133}(4), 694--724.
-\url{https://doi.org/10.1037/0033-2909.133.4.694}
+\leavevmode\vadjust pre{\hypertarget{ref-deak2000effects}{}}%
+Deák, G.
+O., Flom, R.
+A., \& Pick, A.
+D.
+(2000).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/10902702}{Effects of gesture and target on 12- and 18-month-olds' joint visual attention to objects in front of or behind them}.
+\emph{Developmental Psychology}, \emph{36}(4), 511--523.
+
+\leavevmode\vadjust pre{\hypertarget{ref-delbianco2019developmental}{}}%
+Del Bianco, T., Falck-Ytter, T., Thorup, E., \& Gredebäck, G.
+(2019).
+The {Developmental Origins} of {Gaze-Following} in {Human Infants}.
+\emph{Infancy}, \emph{24}(3), 433--454.
+\url{https://doi.org/10.1111/infa.12276}
+
+\leavevmode\vadjust pre{\hypertarget{ref-diedenhofen2015cocor}{}}%
+Diedenhofen, B., \& Musch, J.
+(2015).
+Cocor: {A Comprehensive Solution} for the {Statistical Comparison} of {Correlations}.
+\emph{PLoS ONE}, \emph{10}(4), e0121945.
+\url{https://doi.org/10.1371/journal.pone.0121945}
+
+\leavevmode\vadjust pre{\hypertarget{ref-emery2000eyes}{}}%
+Emery, N.
+J.
+(2000).
+The eyes have it: The neuroethology, function and evolution of social gaze.
+\emph{Neuroscience \& Biobehavioral Reviews}, \emph{24}(6), 581--604.
+\url{https://doi.org/10.1016/S0149-7634(00)00025-7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-erle2017grounded}{}}%
+Erle, T.
+M., \& Topolinski, S.
+(2017).
+The grounded nature of psychological perspective-taking.
+\emph{Journal of Personality and Social Psychology}, \emph{112}(5), 683--695.
+\url{https://doi.org/10.1037/pspa0000081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981younga}{}}%
+Flavell, J.
+H., Everett, B.
+A., Croft, K., \& Flavell, E.
+R.
+(1981).
+Young children's knowledge about visual perception: {Further} evidence for the {Level} 1--{Level} 2 distinction.
+\emph{Developmental Psychology}, \emph{17}, 99--103.
+\url{https://doi.org/10.1037/0012-1649.17.1.99}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981development}{}}%
+Flavell, J.
+H., Flavell, E.
+R., Green, F.
+L., \& Wilcox, S.
+A.
+(1981).
+The {Development} of {Three Spatial Perspective-Taking Rules}.
+\emph{Child Development}, \emph{52}(1), 356--358.
+\url{https://doi.org/10.2307/1129250}
+
+\leavevmode\vadjust pre{\hypertarget{ref-friesen2011gaze}{}}%
+Friesen, A. L., \& Rao, R. P. N. (2011). Gaze {Following} as {Goal Inference}: {A Bayesian Model}. \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}, \emph{33}(33).
+
+\leavevmode\vadjust pre{\hypertarget{ref-frith2012mechanisms}{}}%
+Frith, C. D., \& Frith, U. (2012). Mechanisms of {Social Cognition}. \emph{Annual Review of Psychology}, \emph{63}(1), 287--313. \url{https://doi.org/10.1146/annurev-psych-120710-100449}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-itakura1998use}{}}%
-Itakura, S., \& Tanaka, M.
-(1998).
-Use of experimenter-given cues during object-choice tasks by chimpanzees ({Pan} troglodytes), an orangutan ({Pongo} pygmaeus), and human infants ({Homo} sapiens).
-\emph{Journal of Comparative Psychology}, \emph{112}(2), 119--126.
-\url{https://doi.org/10.1037/0735-7036.112.2.119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lee1998children}{}}%
-Lee, K., Eskritt, M., Symons, L.
-A., \& Muir, D.
-(1998).
-Children's use of triadic eye gaze information for "mind reading".
-\emph{Developmental Psychology}, \emph{34}(3), 525--539.
-\url{https://doi.org/10.1037//0012-1649.34.3.525}
+\leavevmode\vadjust pre{\hypertarget{ref-goodman2014design}{}}%
+Goodman, N. D., \& Stuhlmüller, A. (2014). \emph{The {Design} and {Implementation} of {Probabilistic Programming Languages}}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gosling2004should}{}}%
+Gosling, S.
+D., Vazire, S., Srivastava, S., \& John, O.
+P.
+(2004).
+Should {We Trust Web-Based Studies}?
+{A Comparative Analysis} of {Six Preconceptions About Internet Questionnaires}.
+\emph{American Psychologist}, \emph{59}(2), 93--104.
+\url{https://doi.org/10.1037/0003-066X.59.2.93}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gredeback2010development}{}}%
+Gredebäck, G., Fikke, L., \& Melinder, A.
+(2010).
+The development of joint visual attention: A longitudinal study of gaze following during interactions with mothers and strangers.
+\emph{Developmental Science}, \emph{13}(6), 839--848.
+\url{https://doi.org/10.1111/j.1467-7687.2009.00945.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-heeley1997oblique}{}}%
+Heeley, D.
+W., Buchanan-Smith, H.
+M., Cromwell, J.
+A., \& Wright, J.
+S.
+(1997).
+The oblique effect in orientation acuity.
+\emph{Vision Research}, \emph{37}(2), 235--242.
+\url{https://doi.org/10.1016/S0042-6989(96)00097-1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-henrich2010weirdesta}{}}%
+Henrich, J., Heine, S.
+J., \& Norenzayan, A.
+(2010).
+The weirdest people in the world?
+\emph{The Behavioral and Brain Sciences}, \emph{33}(2-3), 61-83; discussion 83-135.
+\url{https://doi.org/10.1017/S0140525X0999152X}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hernik2019infanta}{}}%
+Hernik, M., \& Broesch, T.
+(2019).
+Infant gaze following depends on communicative signals: {An} eye-tracking study of 5- to 7-month-olds in {Vanuatu}.
+\emph{Developmental Science}, \emph{22}(4), e12779.
+\url{https://doi.org/10.1111/desc.12779}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hessels2020how}{}}%
+Hessels, R.
+S.
+(2020).
+How does gaze to faces support face-to-face interaction?
+{A} review and perspective.
+\emph{Psychonomic Bulletin \& Review}, \emph{27}(5), 856--881.
+\url{https://doi.org/10.3758/s13423-020-01715-w}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ishikawa2022physiological}{}}%
+Ishikawa, M., Senju, A., Kato, M., \& Itakura, S.
+(2022).
+Physiological arousal explains infant gaze following in various social contexts.
+\emph{Royal Society Open Science}, \emph{9}(8), 220592.
+\url{https://doi.org/10.1098/rsos.220592}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lempers1979young}{}}%
+Lempers, J.
+D.
+(1979).
+Young {Children}'s {Production} and {Comprehension} of {Nonverbal Deictic Behaviors}.
+\emph{The Journal of Genetic Psychology}, \emph{135}(1), 93--102.
+\url{https://doi.org/10.1080/00221325.1979.10533420}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lempers1977development}{}}%
+Lempers, J.
+D., Flavell, E.
+R., \& Flavell, J.
+H.
+(1977).
+\href{https://www.ncbi.nlm.nih.gov/pubmed/849832}{The development in very young children of tacit knowledge concerning visual perception}.
+\emph{Genetic Psychology Monographs}, \emph{95}(1), 3--53.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayes1996testretest}{}}%
+Mayes, L.
+C., Klin, A., Tercyak, K.
+P., Cicchetti, D.
+V., \& Cohen, D.
+J.
+(1996).
+Test-{Retest Reliability} for {False-Belief Tasks}.
+\emph{Journal of Child Psychology and Psychiatry}, \emph{37}(3), 313--319.
+\url{https://doi.org/10.1111/j.1469-7610.1996.tb01408.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-meltzoff2010social}{}}%
+Meltzoff, A.
+N., Brooks, R., Shon, A.
+P., \& Rao, R.
+P.
+N.
+(2010).
+{``{Social}''} robots are psychological agents for infants: {A} test of gaze following.
+\emph{Neural Networks}, \emph{23}(8), 966--972.
+\url{https://doi.org/10.1016/j.neunet.2010.09.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-metsamuuronen2022attenuationcorrected}{}}%
+Metsämuuronen, J. (2022). Attenuation-{Corrected Estimators} of {Reliability}. \emph{Applied Psychological Measurement}, \emph{46}(8), 720--737. \url{https://doi.org/10.1177/01466216221108131}
+
+\leavevmode\vadjust pre{\hypertarget{ref-michel2021effects}{}}%
+Michel, C., Kayhan, E., Pauen, S., \& Hoehl, S.
+(2021).
+Effects of {Reinforcement Learning} on {Gaze Following} of {Gaze} and {Head Direction} in {Early Infancy}: {An Interactive Eye-Tracking Study}.
+\emph{Child Development}, \emph{92}(4), e364--e382.
+\url{https://doi.org/10.1111/cdev.13497}
+
+\leavevmode\vadjust pre{\hypertarget{ref-michelon2006two}{}}%
+Michelon, P., \& Zacks, J. M. (2006). Two kinds of visual perspective taking. \emph{Perception \& Psychophysics}, \emph{68}(2), 327--337. \url{https://doi.org/10.3758/BF03193680}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mikellidou2015oblique}{}}%
+Mikellidou, K., Cicchini, G.
+M., Thompson, P.
+G., \& Burr, D.
+C.
+(2015).
+The oblique effect is both allocentric and egocentric.
+\emph{Journal of Vision}, \emph{15}(8), 24.
+\url{https://doi.org/10.1167/15.8.24}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moll2013primacy}{}}%
+Moll, H., \& Kadipasaoglu, D. (2013). The primacy of social over visual perspective-taking. \emph{Frontiers in Human Neuroscience}, \emph{7}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-moore1997role}{}}%
-Moore, C., Angelopoulos, M., \& Bennett, P.
-(1997).
-The role of movement in the development of joint visual attention.
-\emph{Infant Behavior and Development}, \emph{20}(1), 83--92.
-\url{https://doi.org/10.1016/S0163-6383(97)90063-1}
+\leavevmode\vadjust pre{\hypertarget{ref-moll2006level}{}}%
+Moll, H., \& Tomasello, M.
+(2006).
+Level 1 perspective-taking at 24 months of age.
+\emph{British Journal of Developmental Psychology}, \emph{24}(3), 603--613.
+\url{https://doi.org/10.1348/026151005X55370}
+
+\leavevmode\vadjust pre{\hypertarget{ref-moore2008development}{}}%
+Moore, C. (2008). The {Development} of {Gaze Following}. \emph{Child Development Perspectives}, \emph{2}(2), 66--70. \url{https://doi.org/10.1111/j.1750-8606.2008.00052.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nielsen2017persistent}{}}%
+Nielsen, M., Haun, D., Kärtner, J., \& Legare, C.
+H.
+(2017).
+The persistent sampling bias in developmental psychology: {A} call to action.
+\emph{Journal of Experimental Child Psychology}, \emph{162}, 31--38.
+\url{https://doi.org/10.1016/j.jecp.2017.04.017}
+
+\leavevmode\vadjust pre{\hypertarget{ref-osborne-crowley2020social}{}}%
+Osborne-Crowley, K.
+(2020).
+Social {Cognition} in the {Real World}: {Reconnecting} the {Study} of {Social Cognition With Social Reality}.
+\emph{Review of General Psychology}, \emph{24}(2), 144--158.
+\url{https://doi.org/10.1177/1089268020906483}
 
@@
 (2018).
-Prolific.ac\textemdash{{A}} subject pool for online experiments.
+Prolific.ac---{A} subject pool for online experiments.
 \emph{Journal of Behavioral and Experimental Finance}, \emph{17}, 22--27.
 \url{https://doi.org/10.1016/j.jbef.2017.12.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-perner2003perspective}{}}%
+Perner, J., Brandl, J.
+L., Garnham, A., \& Peter Lang.
+(2003).
+What is a {Perspective Problem}?
+{Developmental Issues} in {Belief Ascription} and {Dual Identity}.
+\emph{Facta Philosophica}, \emph{5}(2), 355--378.
+\url{https://doi.org/10.5840/factaphil20035220}
+
+\leavevmode\vadjust pre{\hypertarget{ref-petersen2023reexamining}{}}%
+Petersen, I.
+T.
+(2023).
+\emph{Reexamining {Developmental Continuity} and {Discontinuity} in the 21st {Century}: {Better Aligning Behaviors}, {Functions}, and {Mechanisms}}.
+PsyArXiv.
+\url{https://doi.org/10.31234/osf.io/ghkm6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-pfeiffer2013gaze}{}}%
+Pfeiffer, U.
+J., Vogeley, K., \& Schilbach, L.
+(2013).
+From gaze cueing to dual eye-tracking: {Novel} approaches to investigate the neural correlates of gaze in social interaction.
+\emph{Neuroscience \& Biobehavioral Reviews}, \emph{37}(10, Part 2), 2516--2528.
+\url{https://doi.org/10.1016/j.neubiorev.2013.07.017}
+
+\leavevmode\vadjust pre{\hypertarget{ref-poulin-dubois2023discontinuity}{}}%
+Poulin-Dubois, D., Goldman, E.
+J., Meltzer, A., \& Psaradellis, E.
+(2023).
+Discontinuity from implicit to explicit theory of mind from infancy to preschool age.
+\emph{Cognitive Development}, \emph{65}, 101273.
+\url{https://doi.org/10.1016/j.cogdev.2022.101273}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-prein2022tango}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
 Prein, J.
-C., Bohn, M., Kalinke, S., \& Haun, D.
+C., Kalinke, S., Haun, D.
 B.
-M.
-(2022).
-\emph{{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults}.
-{PsyArXiv}.
-\url{https://doi.org/10.31234/osf.io/vghw8}
+M., \& Bohn, M.
+(2023).
+{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-023-02159-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-quesque2020theoryofmind}{}}%
+Quesque, F., \& Rossetti, Y.
+(2020).
+What {Do Theory-of-Mind Tasks Actually Measure}?
+{Theory} and {Practice}.
+\emph{Perspectives on Psychological Science}, \emph{15}(2), 384--396.
+\url{https://doi.org/10.1177/1745691619896607}
 
 \leavevmode\vadjust pre{\hypertarget{ref-rcoreteam2022language}{}}%
-R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. {Vienna, Austria}: {R Foundation for Statistical Computing}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-raviv2018developmental}{}}%
-Raviv, L., \& Arnon, I.
-(2018).
-The developmental trajectory of children's auditory and visual statistical learning abilities: Modality-based differences in the effect of age.
-\emph{Developmental Science}, \emph{21}(4), e12593.
-\url{https://doi.org/10.1111/desc.12593}
-
-\leavevmode\vadjust pre{\hypertarget{ref-scaife1975capacity}{}}%
-Scaife, M., \& Bruner, J. S. (1975). The capacity for joint visual attention in the infant. \emph{Nature}, \emph{253}(5489), 265--266. \url{https://doi.org/10.1038/253265a0}
+R Core Team. (2022). \emph{R: {A} language and environment for statistical computing} {[}Manual{]}. R Foundation for Statistical Computing.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rakoczy2022foundations}{}}%
+Rakoczy, H. (2022). Foundations of theory of mind and its development in early childhood. \emph{Nature Reviews Psychology}, \emph{1}(4), 223--235. \url{https://doi.org/10.1038/s44159-022-00037-z}
+
+\leavevmode\vadjust pre{\hypertarget{ref-remillard2014systematic}{}}%
+Remillard, M.
+L., Mazor, K.
+M., Cutrona, S.
+L., Gurwitz, J.
+H., \& Tjia, J.
+(2014).
+Systematic {Review} of the {Use} of {Online Questionnaires} of {Older Adults}.
+\emph{Journal of the American Geriatrics Society}, \emph{62}(4), 696--705.
+\url{https://doi.org/10.1111/jgs.12747}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tomasello2007reliance}{}}%
-Tomasello, M., Hare, B., Lehmann, H., \& Call, J.
-(2007).
-Reliance on head versus eyes in the gaze following of great apes and human infants: The cooperative eye hypothesis.
-\emph{Journal of Human Evolution}, \emph{52}(3), 314--320.
-\url{https://doi.org/10.1016/j.jhevol.2006.10.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhang2019role}{}}%
-Zhang, X., Zhang, Z., Zhang, Z., Tang, Y., \& Liu, W.
+\leavevmode\vadjust pre{\hypertarget{ref-surtees2013similarities}{}}%
+Surtees, A., Apperly, I., \& Samson, D.
+(2013).
+Similarities and differences in visual and spatial perspective-taking processes.
+\emph{Cognition}, \emph{129}(2), 426--438.
+\url{https://doi.org/10.1016/j.cognition.2013.06.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasello2003makes}{}}%
+Tomasello, M., \& Rakoczy, H.
+(2003).
+What {Makes Human Cognition Unique}?
+{From Individual} to {Shared} to {Collective Intentionality}.
+\emph{Mind and Language}, \emph{18}(2), 121--147.
+\url{https://doi.org/10.1111/1468-0017.00217}
+
+\leavevmode\vadjust pre{\hypertarget{ref-trafimow2016attenuation}{}}%
+Trafimow, D. (2016). The attenuation of correlation coefficients: A statistical literacy issue. \emph{Teaching Statistics}, \emph{38}(1), 25--28. \url{https://doi.org/10.1111/test.12087}
+
+\leavevmode\vadjust pre{\hypertarget{ref-triesch2006gaze}{}}%
+Triesch, J., Teuscher, C., Deák, G.
+O., \& Carlson, E.
+(2006).
+Gaze following: Why (not) learn it?
+\emph{Developmental Science}, \emph{9}(2), 125--147.
+\url{https://doi.org/10.1111/j.1467-7687.2006.00470.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-vehtari2017practicala}{}}%
+Vehtari, A., Gelman, A., \& Gabry, J.
+(2017).
+Practical {Bayesian} model evaluation using leave-one-out cross-validation and {WAIC}.
+\emph{Statistics and Computing}, \emph{27}(5), 1413--1432.
+\url{https://doi.org/10.1007/s11222-016-9696-4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2018theory}{}}%
+Wellman, H. M. (2018). Theory of mind: {The} state of the art. \emph{European Journal of Developmental Psychology}, \emph{15}(6), 728--755. \url{https://doi.org/10.1080/17405629.2018.1435413}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
+Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhao2019detecting}{}}%
+Zhao, K., Wulder, M.
+A., Hu, T., Bright, R., Wu, Q., Qin, H., Li, Y., Toman, E., Mallick, B., Zhang, X., \& Brown, M.
 (2019).
-The role of the motion cue in the dynamic gaze-cueing effect: {A} study of the lateralized {ERPs}.
-\emph{Neuropsychologia}, \emph{124}, 151--160.
-\url{https://doi.org/10.1016/j.neuropsychologia.2018.12.016}
+Detecting change-point, trend, and seasonality in satellite time series data to track abrupt changes and nonlinear dynamics: {A Bayesian} ensemble algorithm.
+\emph{Remote Sensing of Environment}, \emph{232}, 111181.
+\url{https://doi.org/10.1016/j.rse.2019.04.034}
+
+\leavevmode\vadjust pre{\hypertarget{ref-zohary2022gaze}{}}%
+Zohary, E., Harari, D., Ullman, S., Ben-Zion, I., Doron, R., Attias, S., Porat, Y., Sklar, A.
+Y., \& Mckyton, A.
+(2022).
+Gaze following requires early visual experience.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(20), e2117184119.
+\url{https://doi.org/10.1073/pnas.2117184119}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+Our computational model in Study 2 quantified a participant's cognitive ability to follow gaze by inverting a probabilistic process that generates the participant's clicks from observing the eyes of the agent.
+It is formally defined as:
+
+\begin{equation}
+    P(\theta | x_c, \alpha_l, \alpha_r) \propto P(x_c | \alpha_l, \alpha_r, \theta)P(\theta)
+\end{equation}
+
+where \(\theta\) is an individual's cognitive ability to locate the focus of the agent's attention, \(x_c\) is the coordinate the participant clicked, and \(\alpha_l\) and \(\alpha_r\) are the pupil angles for the left and right eye, respectively.
+The pupil angle \(\alpha\) is defined as the angle between a line connecting the center of the eye to the pupil and a line extended vertically downward from the center of the eye (see Figure \ref{fig:fig2}A).
+
+This model mirrors the logic of the TANGO programming code.
+In the online experiment, we read out the center point coordinates of the target and the agent's eyeball (i.e., the SVG coordinates), and then calculated a line between these two points: this was our gaze vector (acting in the functionally same way as a pupil angle).
+Knowing the eyeball radius, we calculated the point of intersection at which the gaze vector met the eyeball boundary.
+Finally, the agent's pupil moved from the center of the eyeball along the gaze vector to the intersection point.
+This way, the agent was animated to ``look at'' the target.
+In the gaze model, we assumed participants go through these steps in reverse order.
+
+Based on our verbal task instructions, we assumed that participants (1) expected the agent's looks to be directed at the target, and (2) to click on the coordinate they estimated the agent to look at.
+Consequently, we did not assume that participants' clicks were noisy in any way but that they clicked on the screen location where they genuinely thought the target was (and that the agent was looking at).
+
+The true eye angles (\(\alpha_l\) and \(\alpha_r\)) cannot be directly observed and have to be estimated based on the position of the pupils within the eyes, resulting in approximate values (\(\hat{\alpha_l}\) and \(\hat{\alpha_r}\)).
+We presumed this estimation to be a noisy process.
+Thus, we conceptualized the development of the cognitive ability to follow gaze as a reduction of noise in the estimates (i.e., an increased certainty about the pupil angles).
+
+Any clicked value of \(x_c\) implied a ``matched pair'' of the estimated pupil angles \(\hat{\alpha_l}\) and \(\hat{\alpha_r}\), with the property that lines extended along those two angles met at the precise location of the target.
+As a consequence, we can rewrite the likelihood function of the model above:
+
+\begin{equation}
+P(x_c | \alpha_l, \alpha_r, \theta) \propto P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) P(x_c)
+\end{equation}
+
+\(P(x_c)\) is a prior over potential target locations, which we assumed to be skewed towards the screen center: We anticipated that participants have an a priori expectation that the target will land close to the middle, because the target was last visible in the screen center before disappearing behind the hedge and because the agent was located centrally on the screen.
+We estimated the strength of this center bias (i.e., the standard deviation of a Normal distribution around the screen center) based on the data: \(P(x_c) \sim \mathcal{N}(960, \sigma^p)\).
+
+The width of this distribution is defined by \(\sigma^p\).
+For children, we assumed that the center bias changed with age and estimated \(\sigma^p\) via a linear regression as a function of the child's age (\(age_i\)): \(\sigma^p = \beta_0^{\sigma^p} + age_i \cdot \beta_1^{\sigma^p}\).
+Therefore, the participant-specific distribution for \(P(x_c)\) was constrained by the performance in the TANGO and the child's age.
+For the adults, \(\sigma^p\) was not age-specific.
+
+The main inferential task for the participant lay in estimating the pupil angles, i.e., sampling from the first term of the right-hand side equation above, \(P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta)\).
+For this, we assumed that the pair of estimated pupil angles were sampled from a probability distribution which is the product of two Normal distributions of equal variance, \(\sigma_v\), centered on the true pupil angles:
+
+\begin{equation}
+P(\hat{\alpha_l}, \hat{\alpha_r} | \alpha_l, \alpha_r, \theta) \propto \phi(\hat{\alpha}_l ; \alpha_l, \sigma_v)\phi(\hat{\alpha}_r ; \alpha_r, \sigma_v),
+\end{equation}
+
+As \(\sigma_v\) determined the level of accuracy with which participants estimated the pupil angles, it is the component of the model that defines \(\theta\).
+When \(\sigma_v\) is very small (i.e., the distribution around the pupil angle is narrow), clicks far away from the target are unlikely, as these would require estimated pupil angles very different from the true pupil angles.~When \(\sigma_v\) is very large (i.e., the distribution around the pupil angle is wide), almost any pupil angles may be sampled, corresponding to a roughly uniform distribution over click coordinates.
+We expected \(\sigma_v\) to vary between individuals.
+Consequently, individuals differed in the level of precision with which they can locate the target based on observing the agent's eyes.
+
+The shape of the \(P(x_c | \alpha_l, \alpha_r, \theta)\) distribution leads to a testable group-level prediction.
+As the pupil location varies, a fixed amount of uncertainty around the pupil angle corresponds to a varying degree of uncertainty in the estimated target location (see Figure \ref{fig:fig2}B \& C).
+When the agent directs their gaze toward the very left or right side, the distribution around the target location from which participants sample is comparatively wider than when the agent gazes centrally to the ground.
+For illustrative purposes, imagine a similar phenomenon: pointing a torch light to a flat surface on the ground.
+When one points the light cone directly at the surface, the light beam is concentrated in a clearly defined, small, symmetric area.
+When one points the light cone further away from oneself (shining at an angle), the light from one half of the cone must travel further to reach the surface than the light from the other half, resulting in an asymmetric light pattern.
+As the angle increases, the light is spread over a wider area, and the surface is illuminated less evenly.
+Consequently, for the same \(\sigma_v\), the further out a target coordinate lies, the wider and less symmetric the distribution.
+This increases both the variance and the bias in a participant's estimate of the agent's attentional focus, resulting in a decreased performance in the task.
+As \(\sigma_v\) decreases and the cone narrows, the extent to which performance varies at different angles decreases.
+
+In our screen-based study, this effect should decrease again towards the most outward sides.
+Since the computer screen has a natural border, trials in which the target lands furthest out to the left/right become slightly easier again.
+In these cases, the uncertainty about the pupil angle faces practically only the inner side (facing the center) of the screen, since the natural border of the screen limits where participants can click.
+In another adult sample with more trials, we could recover this pattern.
+For further elaboration, see Supplements.
+
 \end{document}

### 2024-03-27 stats/gazemodel.Rmd
prepare revision

@@
 saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")
+dev_plot <- readRDS("../saves/gazemodel_dev_plot.rds")
 
@@
 saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
-
+model_vs_data_plot <- readRDS("../saves/gazemodel_model_vs_data.rds")
 # ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
@@
 saveRDS(faceted_inf, "../saves/supplements_gazemodel_facetedinference.rds")
+faceted_inf <- readRDS("../saves/supplements_gazemodel_facetedinference.rds")
 
@@
 
-# saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
+saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
 # ind_sd_long <- readRDS("../saves/gazemodel_ind_sd_long.rds")
@@
 saveRDS(priorMode, file = "../saves/gazemodel_prior.rds")
+# priorMode <- readRDS("../saves/gazemodel_prior.rds")
 
@@
 
-# gen_model_clicks <- ind_sd_long %>%
-#   rowwise() %>%
-#   mutate(modelClick = get_click_prior(
-#           sdTol = sdTol,
-#           eyeCenterLY = eyeCenterLY,
-#           eyeCenterLX = eyeCenterLX, 
-#           eyeCenterRY = eyeCenterRY,
-#           eyeCenterRX = eyeCenterRX,
-#           targetCenterX = targetCenterX,
-#           pupilLX = pupilLX,
-#           pupilRX = pupilRX,
-#           targetCenterY = targetCenterY,
-#           priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
-#           priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
-#           age = age
-#           ))
-# 
-# modelpred_gaze <- gen_model_clicks %>%
-#   mutate(
-#     modelClickDist = abs(modelClick - targetCenterX),
-#     targetBin = cut(targetCenterX, 
-#                     breaks = seq(from = 0, to = 1920, by = 192),
-#                     labels = as.character(1:10))
-#   ) %>%
-#   group_by(age_group, targetBin) %>%
-#   summarise(
-#     data_mean = mean(clickDist) / 160, 
-#     model_mean = mean(modelClickDist) / 160,
-#   )
+gen_model_clicks <- ind_sd_long %>%
+  rowwise() %>%
+  mutate(modelClick = get_click_prior(
+          sdTol = sdTol,
+          eyeCenterLY = eyeCenterLY,
+          eyeCenterLX = eyeCenterLX,
+          eyeCenterRY = eyeCenterRY,
+          eyeCenterRX = eyeCenterRX,
+          targetCenterX = targetCenterX,
+          pupilLX = pupilLX,
+          pupilRX = pupilRX,
+          targetCenterY = targetCenterY,
+          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
+          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
+          age = age
+          ))
 
-# saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
+saveRDS(gen_model_clicks, file = "../saves/gazemodel_gen_model_clicks.rds")
+# gen_model_clicks <- readRDS("../saves/gazemodel_gen_model_clicks.rds")
+
+modelpred_gaze <- gen_model_clicks %>%
+  mutate(
+    modelClickDist = abs(modelClick - targetCenterX),
+    targetBin = cut(targetCenterX,
+                    breaks = seq(from = 0, to = 1920, by = 192),
+                    labels = as.character(1:10))
+  ) %>%
+  group_by(age_group, targetBin) %>%
+  summarise(
+    data_mean = mean(clickDist) / 160,
+    model_mean = mean(modelClickDist) / 160,
+  )
+
+saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
 modelpred_gaze <- readRDS("../saves/gazemodel_modelpred_gaze.rds")
@@
 saveRDS(u_data, "../saves/gazemodel_u_data.rds")
+# u_data <- readRDS("../saves/gazemodel_u_data.rds")
 
@@
 saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
+u_plot <- readRDS("../saves/gazemodel_u_plot.rds")
+
 # ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
@@
   ggplot(., aes(x = model_mean, y = data_mean)) +
-  geom_point(aes(col = targetBin)) +
+  geom_point(aes(col = targetBin, shape = as.factor(age_group))) +
   stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
@@
   scale_color_brewer(palette="BrBG") +
-  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
+  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin", shape = "Age group") + 
   scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
@@
   ggplot(., aes(x = model_mean, y = data_mean)) +
-  geom_point(aes(col = targetBin), size = 0.8) +
+  geom_point(aes(col = targetBin, shape = as.factor(age_group)), size = 0.8) +
   stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
@@
   modelpred_gaze_plot + 
-    theme(legend.position = c(0.85, 0.3), 
-          legend.title = element_text(size = 8),
-          legend.text = element_text(size = 8), 
+    theme(legend.position = c(0.85, 0.38), 
+          legend.title = element_text(size = 6),
+          legend.text = element_text(size = 6), 
           legend.box.background = element_rect(), 
-          legend.key.height = unit(0.3, "cm"),
-          legend.key.width = unit(-1.5, "cm"),
+          legend.key.height = unit(0.28, "cm"),
+          legend.key.width = unit(-1.8, "cm"),
           plot.margin = margin(0.2, -2, 0.1, 0.2, "cm") # t r b l
@@
 saveRDS(corr_model_pred_plot, file = "../saves/gazemodel_corr_model_pred_plot.rds")
+```
+
+```{r get_click_motornoise}
+get_click_motornoise <- function(targetCenterX){
+  xDist = dnorm(seq(1:1920), mean = targetCenterX, sd = 160)
+
+  click = sample(1:1920, prob = xDist, size = 1)-1
+
+  return(click)
+}
+```
+
+```{r get_click_linetracing}
+get_click_linetracing <- function(targetCenterX){
+  return(targetCenterX)
+}
 ```
@@
 ```{r get_dist}
-# get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){
-# 
-#   if(eyeCenterLX > pupilLX) {
-#     tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
-#   } else {
-#     tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
-#   }
-#   
-#   #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
-#   
-#   if(eyeCenterRX > pupilRX) {
-#     tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
-#   } else {
-#     tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
-#   }
-#   
-#   #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
-# 
-#   bRDist = c()
-#   
-#   bLDist = c()
-#   
-#   for (x in 1:1920){
-#     
-#   if(eyeCenterLX > x) {
-#     betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
-#   } else {
-#     betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
-#   }
-#     betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
-#     
-#   if(eyeCenterRX > x) {
-#     betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
-#   } else {
-#     betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
-#   }
-#     betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
-#     
-#     #betaDist = betaLDist + betaRDist
-#     
-#     #bDist[x] <- exp(betaDist)
-#     bRDist[x] <- betaRDist
-#     
-#     bLDist[x] <- betaLDist
-#     
-#   }
-#   
-#   xRDist = exp(bRDist-logSumExp(bRDist))
-#   
-#   xLDist = exp(bLDist-logSumExp(bLDist))
-#   
-#   xDist = xRDist * xLDist
-#   
-#   dist = xDist / sum(xDist)
-#   
-#   # click = sample(1:1920, prob = xDist, size = 1)-1
-#   
-#   return(dist)
-# }
+get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){
+
+  if(eyeCenterLX > pupilLX) {
+    tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+  } else {
+    tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
+  }
+
+  #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
+
+  if(eyeCenterRX > pupilRX) {
+    tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+  } else {
+    tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
+  }
+
+  #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
+
+  bRDist = c()
+
+  bLDist = c()
+
+  for (x in 1:1920){
+
+  if(eyeCenterLX > x) {
+    betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+  } else {
+    betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
+  }
+    betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
+
+  if(eyeCenterRX > x) {
+    betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+  } else {
+    betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
+  }
+    betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
+
+    #betaDist = betaLDist + betaRDist
+
+    #bDist[x] <- exp(betaDist)
+    bRDist[x] <- betaRDist
+
+    bLDist[x] <- betaLDist
+
+  }
+
+  xRDist = exp(bRDist-logSumExp(bRDist))
+
+  xLDist = exp(bLDist-logSumExp(bLDist))
+
+  xDist = xRDist * xLDist
+
+  dist = xDist / sum(xDist)
+
+  # click = sample(1:1920, prob = xDist, size = 1)-1
+
+  return(dist)
+}
 ```
@@
 ```{r headlight_dist}
-# headlight_df <- data.frame(
-#   coord = 1:1920,
-#   sdTol = "0.175"
-# )
-# 
-# for (i in c(960,1736)){
-#   
-#   probdist <-  get_dist(
-#     sdTol = 0.175,
-#     targetCenterX = i,
-#     eyeCenterLY = 937.8,
-#     eyeCenterLX = 872.12,
-#     eyeCenterRY = 937.8,
-#     eyeCenterRX = 1045.89,
-#     targetCenterY = 127.5,
-#     pupilLX = i-1,
-#     pupilRX = i-1)
-#   
-#     colname = as.character(i)
-#     
-#     headlight_df[, colname] <- probdist
-#   
-#   }
-# 
-# headlight_df %>%
-#   pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
-#   filter(target_coordinate == "960") %>%
-#   ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
-#   geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
-#   ylim(0, 0.006) +
-#   scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
-#   guides(fill = F) + 
-#   # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
-#   # labs(x = "Coordinate", y = "Probability") +
-#   # scale_fill_colorblind(name = "Inference SD") +
-#   theme_few() + 
-#   theme(
-#     panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
-#     panel.grid.minor = element_blank(), 
-#     panel.grid.major = element_blank(),
-#     plot.background = element_rect(fill = "transparent",colour = NA)
-# )
-# 
-# ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")
-# 
-# ##  Standard normal dist
-# dnorm_one_sd <- function(x){
-#   norm_one_sd <- dnorm(x)
-#   # Have NA values outside interval x in [-1, 1]:
-#   norm_one_sd[x <= -1 | x >= 1] <- NA
-#   return(norm_one_sd)
-# }
-# 
-# ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
-#   stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) + 
-#   stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
-#   # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
-#   theme_void()
-# 
-# ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
+headlight_df <- data.frame(
+  coord = 1:1920,
+  sdTol = "0.175"
+)
+
+for (i in c(960,1736)){
+
+  probdist <-  get_dist(
+    sdTol = 0.175,
+    targetCenterX = i,
+    eyeCenterLY = 937.8,
+    eyeCenterLX = 872.12,
+    eyeCenterRY = 937.8,
+    eyeCenterRX = 1045.89,
+    targetCenterY = 127.5,
+    pupilLX = i-1,
+    pupilRX = i-1)
+
+    colname = as.character(i)
+
+    headlight_df[, colname] <- probdist
+
+  }
+
+headlight_df %>%
+  pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
+  filter(target_coordinate == "1736") %>%
+  ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
+  geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
+  ylim(0, 0.006) +
+  scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
+  guides(fill = F) +
+  # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
+  # labs(x = "Coordinate", y = "Probability") +
+  # scale_fill_colorblind(name = "Inference SD") +
+  theme_few() +
+  theme(
+    panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_blank(),
+    plot.background = element_rect(fill = "transparent",colour = NA)
+)
+
+ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")
+
+##  Standard normal dist
+dnorm_one_sd <- function(x){
+  norm_one_sd <- dnorm(x)
+  # Have NA values outside interval x in [-1, 1]:
+  norm_one_sd[x <= -1 | x >= 1] <- NA
+  return(norm_one_sd)
+}
+
+ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
+  stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) +
+  stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
+  # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
+  theme_void()
+
+ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
 ```
+
+# Simulated clicks from alternative models
+
+```{r simulated_data}
+simulated_data <- gen_model_clicks %>% 
+  ungroup() %>%
+  mutate(
+    model_dist = modelClick - targetCenterX,
+  ) %>%
+  rename(target_center_x = targetCenterX) %>%
+  group_by(id, trial_nr, target_center_x) %>% 
+  summarize(
+    gazemodel_click = mean(modelClick),
+    gazemodel_dist = mean(model_dist),
+  ) %>% 
+  mutate(
+    # line_click = target_center_x,
+    linetracing_click = get_click_linetracing(target_center_x),
+    linetracing_dist = linetracing_click - target_center_x, # = 0
+
+    # motornoise_click = rnorm(n = n(), mean = target_center_x, sd = 160) %>% round(digits = 2),
+    motornoise_click = get_click_motornoise(target_center_x),
+    motornoise_dist = motornoise_click - target_center_x,
+
+    # random_click = runif(n = n(), min = 0, max = 1920) %>% round(digits = 2), 
+    random_click = get_click_random(),
+    random_dist = random_click - target_center_x,
+
+    # center_click = rnorm(n = n(), mean = 960, sd = 160) %>% round(digits = 2),
+    center_click = get_click_center(),
+    center_dist = center_click - target_center_x,
+  )
+
+simulated_data <- tango_kids %>% 
+  select(subj_id, age, age_group, trial_nr, target_position, target_center_x, click_scaled_x, click_dist_from_target_center_x) %>% 
+  rename(data_click = click_scaled_x, data_dist = click_dist_from_target_center_x) %>% 
+  full_join(simulated_data, by = c("subj_id" = "id", "trial_nr", "target_center_x"))
+
+simulated_wide <- simulated_data
+
+simulated_mean <- simulated_data %>% 
+    group_by(target_position) %>%
+  summarise(
+    data_click = mean(data_click), 
+    gazemodel_click = mean(gazemodel_click),
+    linetracing_click = mean(linetracing_click),
+    motornoise_click = mean(motornoise_click),
+    random_click = mean(random_click),
+    center_click = mean(center_click),
+
+    data_dist = mean(abs(data_dist)), 
+    gazemodel_dist = mean(abs(gazemodel_dist)),
+    motornoise_dist = mean(abs(motornoise_dist)),
+    linetracing_dist = mean(abs(linetracing_dist)),
+    random_dist = mean(abs(random_dist)),
+    center_dist = mean(abs(center_dist)),
+  ) %>% 
+    pivot_longer(
+    cols = -target_position,
+    names_to = c("model", ".value"),
+    names_sep = "_"
+  ) %>% 
+  mutate(
+    model = factor(model, levels = c("data", "gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Data", "Gaze model", "Line-of-Sight", "LoS w.
+motor noise", "Random guessing", "Center bias")),
+  )
+
+simulated_data <- simulated_data %>% 
+  pivot_longer(
+    cols = -c(subj_id, age, age_group, trial_nr, target_position, target_center_x),
+    names_to = c("model", ".value"),
+    names_sep = "_"
+  ) %>%
+  mutate(
+    model = factor(model, levels = c("data", "gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Data", "Gaze model", "Line-of-Sight", "LoS w.
+motor noise", "Random guessing", "Center bias")),
+  )
+
+saveRDS(simulated_data, file = "../saves/gazemodel_simulated_data.rds")
+```
+
+```{r simulated_data_plot}
+sim_u <- simulated_mean %>% 
+  ggplot(aes(x = target_position, y = dist, col = model, group = model)) +
+  geom_point(alpha = 0.8, size = 1.5) +
+  geom_line(alpha = 0.2) +
+  scale_y_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 320)) +
+  labs(x = "Target bin", y = "Imprecision", col = "Source") + 
+  scale_colour_viridis_d() +
+  theme_minimal()
+
+sim_cor <- simulated_wide %>% 
+  group_by(age_group, target_position) %>%
+  summarise(
+    data = mean(abs(data_dist)),
+    gazemodel = mean(abs(gazemodel_dist)),
+    linetracing = mean(abs(linetracing_dist)),
+    motornoise = mean(abs(motornoise_dist)),
+    random = mean(abs(random_dist)),
+    center = mean(abs(center_dist)),
+  ) %>% 
+  pivot_longer(cols = c(gazemodel, linetracing, motornoise, random, center), names_to = "model", values_to = "mean") %>% 
+  mutate(
+    model = factor(model, levels = c("gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Gaze model", "Line-of-Sight", "LoS w. motor noise", "Random guessing", "Center bias")), 
+  ) %>% 
+  ggplot(aes(x = mean, y = data)) +
+  geom_point(aes(color = target_position, shape = as.factor(age_group)), alpha = 0.8, size = 0.8) +
+  stat_cor(method = "pearson", label.x = 100, label.y = 960, aes(label = paste(..r.label..)), r.accuracy = 0.01, cor.coef.name = "r", size = 2.7, color = "black") +
+  geom_abline(intercept = 0, slope = 1, linetype = 3) +
+  labs(x = "Predicted imprecision", y = "Observed imprecision", color = "Target position", shape = "Age group") +
+  scale_color_brewer(palette="BrBG") +
+  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 960, 320)) +
+  scale_y_continuous(limits = c(0, 1000), breaks = seq(0, 960, 320)) +
+  facet_wrap(~model) + 
+  theme_minimal() +
+  theme(axis.title = element_text(size = 6), 
+        axis.text = element_text(size = 6), 
+        strip.text = element_text(size = 7), 
+        legend.title = element_text(size = 6),
+        legend.text = element_text(size = 6), 
+        legend.key.height = unit(0.3, "cm"),
+        legend.key.width = unit(-1.5, "cm"),
+        )
+sim_cor
+
+sim_click <- ggplot() +
+  geom_point(data = simulated_data, aes(x = target_position, y = click, col = model), alpha = 0.2, size = 0.75) +
+  geom_point(data = simulated_mean, aes(x = target_position, y = click, col = model), shape = 4, size = 2, stroke = 1.5) +
+  geom_line(data = simulated_mean, aes(x = target_position, y = click, col = model, group = model)) +
+  scale_y_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 320)) +
+  labs(x = "Target bin", y = "Click coordinate", col = "Source") + 
+  scale_colour_viridis_d(guide = "none") +
+  theme_minimal() + 
+  facet_wrap(~ model, nrow = 1)
+
+sim_arranged <- ggarrange(
+  ggarrange(sim_u, sim_cor, ncol = 2, widths = c(1, 1), labels = c("A", "B")),
+
+  sim_click,
+
+  nrow = 2, 
+  labels = c("", "C")
+)
+
+sim_arranged
+
+ggsave("../figures/gazemodel_simulated_u.png", width = 9, height = 5, bg = "white")
+```
+
+```{r inward_clicks}
+tango_kids %>% 
+  mutate(
+    dist = ifelse(target_center_x < 960, click_scaled_x - target_center_x, target_center_x - click_scaled_x),
+  ) %>% 
+  ggplot(aes(x = dist, y = target_position)) +
+  geom_density_ridges() + 
+  geom_point(stat = "summary", fun = "mean", shape = 4, size = 2.5, position = position_nudge(y = 0.1)) +
+  geom_vline(xintercept = 0, lty = 2, alpha = .25) +
+  scale_x_continuous(limits = c(-960, 1920), breaks = seq(-960, 1920, 320)) +
+  labs(x = "Distance from target center (higher: inward)", y = "Target bin")
+
+ggsave("../figures/gazemodel_inward_clicks.png", width = 8, height = 5, bg = "white", scale = 1.1)
+```

### 2024-03-27 stats/magnet.Rmd
major edits in intro & discussion
prepare revision

@@
 saveRDS(magnet_sample, "../saves/magnet_sample.rds")
+```
+
+```{r descriptives_table}
+magnet_descriptives <- magnet_data %>% 
+  select(-c(subj_id, gender, age_group, age, age_centered)) %>%
+  describe() %>% 
+  select(n, mean, sd, median, min, max)
+
+magnet_descriptives
+saveRDS(magnet_descriptives, "../saves/magnet_descriptives.rds")
 ```
@@
 
+```{r explorative}
+tango_tom_excl_perspective <- magnet_data %>% 
+  group_by(subj_id) %>% 
+  mutate(
+    tom_excl_perspective = sum(desires, knowledge, content, explicit)
+  ) %>% 
+  ungroup() %>% 
+  select(tango_mean, tom_excl_perspective) %>% 
+  corr.test(method = "spearman")
+
+tango_tom_excl_perspective$ci
+
+tom_perspective <- magnet_data %>% 
+  group_by(subj_id) %>% 
+  mutate(
+    tom_excl_perspective = sum(desires, knowledge, content, explicit)
+  ) %>% 
+  ungroup() %>% 
+  select(perspective_aggregate, tom_excl_perspective) %>% 
+  corr.test(method = "spearman")
+
+tom_perspective$ci
+```
+
 ```{r plot_cor_ci}
@@
 # ggsave("../figures/magnet_cor_ci.png", width = 5, height = 3)
+```
+
+```{r cor_triallevel}
+tango_trials <- read_csv("../data/magnet-tango-data.csv")
+magnet_trials <- read_csv("../data/magnet-tablet-data.csv")
+
+trials_bins <- tango_trials %>% 
+  group_by(subj_id, target_position) %>%
+  summarise(click_dist_tango = mean(click_dist_balloons, na.rm = T)) %>%
+
+  full_join(magnet_trials %>% 
+      rename(target_position = magnet_bin) %>%
+      group_by(subj_id, target_position) %>%
+      summarise(click_dist_magnet = mean(click_dist_magnets, na.rm = T)))
+
+trials_bins
+
+trials_bins_cor <- corr.test(trials_bins$click_dist_tango, trials_bins$click_dist_magnet, method = "pearson", use = "pairwise.complete.obs")
+
+trials_bins_cor$ci
+
+trials_bins_cov <- cov(trials_bins$click_dist_tango, trials_bins$click_dist_magnet, method = "pearson", use = "pairwise.complete.obs")
 ```
@@
 saveRDS(model_results, "../saves/magnet_modelresults.rds")
+model_results <- readRDS("../saves/magnet_modelresults.rds")
 
@@
 saveRDS(mmagnet_perspective, "../saves/magnet_winningmodel.rds")
+mmagnet_perspective <- readRDS("../saves/magnet_winningmodel.rds")
 ```

### 2024-03-27 supplements/supplements.Rmd
prepare revision

@@
 ---
-title             : "Supplements for the manuscript  'Variation in gaze understanding across the life span: A process-level perspective'"
+title             : "Supplements for the manuscript  'Variation in gaze following across the life span: A process-level perspective'"
 shorttitle        : "Supplements"
@@
   - name          : "Julia Prein"
-    affiliation   : "1"
+    affiliation   : "1,2"
   - name          : "Luke Maurits"
@@
 
+## Simulations
+
+In the manuscript, we have described the gaze model and two alternatives: random guessing and a center bias.
+Here, we consider two more alternatives.
+Let us consider a model that assumes participants can infer the agent’s focus without any noise (for example, by tracing the line of sight).
+A model like this would assume that participants follow gaze without any uncertainty.
+Therefore, no U curve would be predicted.
+Furthermore, let us assume another model in that participants still show no inferential noise, but they vary in their amount of motor noise, so how accurately participants then click at the corresponding location.
+A model like this would assume equal variance across the target locations, so we would not expect a U-shape here.
+
+Please note that our random guessing model acts like 100% noise: the predictions of a participant’s click on a trial level range uniformly from 0 to 1920 (the whole screen range).
+The mean comes down to the center, namely 960.
+However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A).
+Most importantly, note that this is only the case when you average across all the trials.
+When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C).
+In our correlational plots (Figure 5B), we see that the gaze model is clearly favored.
+This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.
+
+(ref:figlab5) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models.
+Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
+B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
+C: Predicted click coordinates (cf.
+not imprecision) by target position across the different models.
+
+```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
+knitr::include_graphics("../figures/gazemodel_simulated_u.png")
+```
+
 # Study 3: Components of gaze understanding

### 2024-03-27 supplements/supplements.tex
prepare revision

@@
 \hypersetup{
-  pdftitle={Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'},
-  pdfauthor={Julia Prein1, Luke Maurits1, Annika Werwach1, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
+  pdftitle={Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'},
+  pdfauthor={Julia Prein1,2, Luke Maurits1, Annika Werwach1, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
   pdflang={en-EN},
@@
 
-\title{Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'}
-\author{Julia Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
+\title{Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'}
+\author{Julia Prein\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
 \date{}
@@
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \begin{tabular}{rlrlr}
@@
 
+\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}}
+
+In the manuscript, we have described the gaze model and two alternatives: random guessing and a center bias.
+Here, we consider two more alternatives.
+Let us consider a model that assumes participants can infer the agent's focus without any noise (for example, by tracing the line of sight).
+A model like this would assume that participants follow gaze without any uncertainty.
+Therefore, no U curve would be predicted.
+Furthermore, let us assume another model in that participants still show no inferential noise, but they vary in their amount of motor noise, so how accurately participants then click at the corresponding location.
+A model like this would assume equal variance across the target locations, so we would not expect a U-shape here.
+
+Please note that our random guessing model acts like 100\% noise: the predictions of a participant's click on a trial level range uniformly from 0 to 1920 (the whole screen range).
+The mean comes down to the center, namely 960.
+However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A).
+Most importantly, note that this is only the case when you average across all the trials.
+When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C).
+In our correlational plots (Figure 5B), we see that the gaze model is clearly favored.
+This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.
+
+\begin{figure}[H]
+
+{\centering \includegraphics[width=1\linewidth]{../figures/gazemodel_simulated_u}
+
+}
+
+\caption{\textbf{Predictions of alternative models across target positions.} A: Predicted U-pattern across target positions by the different models.
+Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
+B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
+C: Predicted click coordinates (cf.~not imprecision) by target position across the different models.}\label{fig:fig5}
+\end{figure}
+
 \hypertarget{study-3-components-of-gaze-understanding}{%
@@
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \begin{tabular}{lrrrrr}

### 2024-04-17 paper/manuscript.Rmd
ready for revision

@@
 keywords          : "social-cognitive development, theory of mind, gaze following, individual differences, cognitive modeling, lifespan"
-wordcount         : "X"
+wordcount         : "10469"
 floatsintext      : yes
-figurelist        : no
+figurelist        : yes
 tablelist         : no
@@
 It guides us to "informational hotspots" [@meltzoff2010social, p.1] and can be used to identify internal states such as intentions or emotions [@corkum1998origins; @pfeiffer2013gaze].
-As one of the most fundamental social-cognitive abilities, gaze-following is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@emery2000eyes; @rakoczy2022foundations; @frith2012mechanisms; @tomasello2003makes; @bohn2019pervasive; @moore2008development; @hessels2020how], and has been extensively studied in infancy [for review, see @delbianco2019developmental].
+As one of the most fundamental social-cognitive abilities, gaze following is an integral part of almost every form of social interaction, including communication, collaboration, cultural and social learning [@emery2000eyes; @rakoczy2022foundations; @frith2012mechanisms; @tomasello2003makes; @bohn2019pervasive; @moore2008development; @hessels2020how], and has been extensively studied in infancy [for review, see @delbianco2019developmental].
 In the most commonly used paradigm [e.g., @astor2020social; @gredeback2010development; @byers-heinlein2021development; @ishikawa2022physiological], the experimenter looks directly at the infant before shifting their head and eyes to one of two objects.
@@
 
-Previous research has shown a refinement of gaze-following abilities in a child's first and second year of life [e.g., @astor2021gaze; @butterworth1991minds; @brooks2002importance].
+Previous research has shown a refinement of gaze following abilities in a child's first and second year of life [e.g., @astor2021gaze; @butterworth1991minds; @brooks2002importance].
 At the end of their first year of life, infants can follow gaze to locations outside their current visual field and move themselves to gain proper perceptual access [@moll200412; @deak2000effects; @butterworth1991minds; @corkum1995development].
@@
 It seems likely that children fine-tune their gaze following as they get older - presumably while using them in social interactions.
-To capture the development in gaze following beyond infancy, Study 1 was included participants from preschool to old age.
+To capture the development in gaze following beyond infancy, Study 1 included participants from preschool to old age.
 
@@
 
-Group-level analyses of gaze-following abilities (e.g., average age at which children as a group reach an above-chance performance) may mask individual differences between children.
+Group-level analyses of gaze following abilities (e.g., average age at which children as a group reach an above-chance performance) may mask individual differences between children.
 Measuring individual differences in basic aspects of social cognition is important to understand the underlying processes and to quantify the impact of environmental influences and other cognitive abilities [@birch2017perspectives; @delbianco2019developmental].
-Across the three studies, we measured gaze following continuously by using a task that is designed to capture individual-level variation [@prein2023tango]: the TANGO avoids floor and ceiling effects in children and adults and is thus particularly suited to examine how gaze following changes with age.
+Across the three studies, we measured gaze following continuously by using a task that is designed to capture individual-level variation [@prein2023tango]: the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) avoids floor and ceiling effects in children and adults and is thus particularly suited to examine how gaze following changes with age.
 
@@
 
-The study was pre-registered prior data collection: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
+The study was pre-registered prior to data collection: <https://osf.io/snju6> (child sample) and <https://osf.io/6yjz3> (adult sample).
 The study obtained ethical clearance by the MPG Ethics commission in Munich, Germany, falling under an umbrella ethics application (Appl.
@@
 Blue lines show 100 draws from the expectation of the posterior predictive distribution of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line.
-Vertical, black, dashed lines show the locations of the most prominent changes according to our Bayesian change point analysis.
+Vertical, black, dashed lines show the locations of the changes with the highest posterior probability according to our Bayesian change point analysis.
 
@@
 lifespan_cps <- readRDS("../saves/lifespan_ibeast_cps.rds") %>% round(2) %>% arrange(cp)
+lifespan_cps_descr <- readRDS("../saves/lifespan_cps_descr.rds")
 
@@
 Moreover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`).
-For the imprecision in gaze following, the standard deviation (*b* = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.
+For the imprecision in gaze following, the standard deviation of the Gaussian process (SD = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.
 
 The Bayesian change point analysis revealed `r lifespan_beast$trend$ncp_mode` major shifts in gaze following during the lifespan (MAP estimate with `r lifespan_beast$trend$ncpPr[lifespan_beast$trend$ncp_mode + 1] * 100 %>% round(2)`% probability).
-The change points occurred at `r lifespan_cps$cp[1]` (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`]); `r lifespan_cps$cp[2]` (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`]); `r lifespan_cps$cp[3]` (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`]); `r lifespan_cps$cp[4]` (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`]); `r lifespan_cps$cp[5]` (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`]); and `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`]).
+The change points occurred at `r lifespan_cps$cp[1]` years (95% CrI [`r lifespan_cps$lowerCrI[1]`; `r lifespan_cps$upperCrI[1]`], mean imprecision until change point = `r lifespan_cps_descr[1,]$mean`, SD = `r lifespan_cps_descr[1,]$sd`); `r lifespan_cps$cp[2]` years (95% CrI [`r lifespan_cps$lowerCrI[2]`; `r lifespan_cps$upperCrI[2]`], mean = `r lifespan_cps_descr[2,]$mean`, SD = `r lifespan_cps_descr[2,]$sd`); `r lifespan_cps$cp[3]` years (95% CrI [`r lifespan_cps$lowerCrI[3]`; `r lifespan_cps$upperCrI[3]`], mean = `r lifespan_cps_descr[3,]$mean`, SD = `r lifespan_cps_descr[3,]$sd`); `r lifespan_cps$cp[4]` years (95% CrI [`r lifespan_cps$lowerCrI[4]`; `r lifespan_cps$upperCrI[4]`], mean = `r lifespan_cps_descr[4,]$mean`, SD = `r lifespan_cps_descr[4,]$sd`); `r lifespan_cps$cp[5]` years (95% CrI [`r lifespan_cps$lowerCrI[5]`; `r lifespan_cps$upperCrI[5]`], mean = `r lifespan_cps_descr[5,]$mean`, SD = `r lifespan_cps_descr[5,]$sd`); and `r lifespan_cps$cp[6]` years (95% CrI [`r lifespan_cps$lowerCrI[6]`; `r lifespan_cps$upperCrI[6]`], mean = `r lifespan_cps_descr[6,]$mean`, SD = `r lifespan_cps_descr[6,]$sd`).
 In short: we found a rapid initial improvement in gaze following in early childhood, followed by a long period of minor, very slow change with slightly increasing levels of imprecision toward old age.
@@
 
-Previous studies found that already four-month-olds demonstrate basic gaze-following abilities [@delbianco2019developmental].
+Previous studies found that already four-month-olds demonstrate basic gaze following abilities [@delbianco2019developmental].
+Since we measured an active location choice on a touchscreen, we could not collect data from infants.
 In our sample, three-year-olds were still rather imprecise in their gaze following ability (average imprecision was approx.
@@
 Relying exclusively on eye movements might be more difficult for children than presenting them with a combined eye and head orientation [@carpenter1998social].
-@silverstein2021infants used a similar manipulation of gaze cues without head rotation and found that 6- to 18-month-olds were around or just above chance for gaze-following.
+@silverstein2021infants used a similar manipulation of gaze cues without head rotation and found that 6- to 18-month-olds were around or just above chance for gaze following.
 The authors argue that infants might fixate on another's face most of the time, while eye movement alone might not be strong enough to guide their attention.
@@
 We present a theory of gaze following that explains how participants process the available gaze information and trace a line-of-sight to identify the agent's focus.
-We formalized this inference process in a computational cognitive model that replicates a schematic representation of how participants make inferences in the task’s context (i.e., model of the task and not the data).
+We formalized this inference process in a computational cognitive model that replicates a schematic representation of how participants make inferences in the task’s context (i.e., a model of the task and not the data).
 
@@
 
-[^6]: In an exploratory analysis, we simulated data for two more alternatives: a line-of-sight tracing model that assumed no inferential noise in the participants' gaze-following ability, and a model building up on the line-of-sight tracing with added motor noise.
+[^6]: In an exploratory analysis, we simulated data for two more alternatives: a line-of-sight tracing model that assumed no inferential noise in the participants' gaze following ability, and a model building up on the line-of-sight tracing with added motor noise.
 Please note that these did not predict a U-shape pattern, since all target locations would be influenced by the motor noise equally.
@@
 We reasoned that the TANGO shares task demands with the non-social vector following task while it shares its social context with the ToM tasks.
-We could therefore imagine both an absence or presence of relationship betweenn gaze following and ToM.
+We could, therefore, imagine both an absence or presence of relationship between gaze following and ToM.
 As stated in our pre-registration, we further assessed whether the two perspective-taking tasks related to gaze following.
@@
 "emotional") aspects of social cognition.
-We added two perspective-taking level-2 tasks [@flavell1981development; @flavell1981younga; where children were asked whether a turtle appeared to be on its back or feet / a worm lay on a red or blue blanket from the experimenter's point of view] with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze following, both relying on another's person egocentric frame of reference.
+We added two perspective-taking level-2 tasks ([@flavell1981development; @flavell1981younga]; where children were asked whether a turtle appeared to be on its back or feet / a worm lay on a red or blue blanket from the experimenter's point of view) with the aim of increasing the variability we can capture between individuals, and since we hypothesized that perspective-taking would rely on similar mechanisms than gaze following, both relying on another's person egocentric frame of reference.
 
@@
 The left-hand side shows screenshots of the familiarization phase; right-hand side shows screenshots of the test phase.
-For illustrative purposes, transluscent targets are shown in the test phase.
+For illustrative purposes, translucent targets are shown in the test phase.
 Participants cannot see them.
@@
 Cultural variation has been found in many foundational aspects of cognition and socialization: for example, in parent-child interaction and communication [@nielsen2017persistent].
-First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts [@hernik2019infanta].
+First evidence suggests that cultural variation in face-to-face interactions does not influence infants' gaze shifts [@hernik2019infant].
 While we cannot generalize our here-reported developmental trajectory to different socio-environmental settings, we predict that our presented process-model of gaze following holds true across communities.
@@
 In Study 1, we recruited older participants online which might have selected a particular subgroup of this age range.
-Seventy-year-olds who have working WIFI connections, know how to use a computer, and are registered on *Prolific* might not be representative of their age group.
+Seventy-year-olds who have working Wi-Fi connections, know how to use a computer, and are registered on *Prolific* might not be representative of their age group.
 We can imagine that results from a more diverse, in-person data collection might show different developmental trajectories toward old age.
@@
 
-In three studies, we have illuminated the lifelong development of precisely estimating another's gaze direction, and the psychophysical process behind this.
+In three studies, we have illuminated the lifelong development of precisely estimating another's gaze direction, and the psycho-physical process behind this.
 We have shown that gaze following continues to develop beyond infancy, and that individuals differ in their precision levels to localize the gaze direction of an agent.

### 2024-04-17 stats/lifespan.Rmd
ready for revision

@@
 
+```{r changepoints_descr}
+cps <- readRDS("../saves/lifespan_ibeast_cps.rds") %>% 
+  arrange(cp)
+
+cps_descr <- mdata %>% 
+  mutate(
+   age_cp = case_when(
+     age < cps$cp[1] ~ "1",
+     age < cps$cp[2] ~ "2",
+     age < cps$cp[3] ~ "3",
+     age < cps$cp[4] ~ "4",
+     age < cps$cp[5] ~ "5",
+     age < cps$cp[6] ~ "6",
+     age > cps$cp[6] ~ "7",
+   ) 
+  ) %>% 
+  group_by(age_cp) %>%
+  summarize(
+    age_min = min(age, na.rm = T),
+    age_max = max(age, na.rm = T),
+    n = n(),
+    mean = mean(mean_imprecision, na.rm = T) %>% round(2),
+    sd = sd(mean_imprecision, na.rm = T) %>% round(2),
+  )
+
+saveRDS(cps_descr, "../saves/lifespan_cps_descr.rds")
+```
+
 # PLOT

### 2024-04-17 supplements/supplements.Rmd
ready for revision

@@
 Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).
+
 ```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/supplements_lifespan_modelstructure.pdf")
+knitr::include_graphics(c("../figures/lifespan_plot.png"))
 ```
@@
 In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage.
-She thinks her cat is in the garage.” (or vice versa) Then the child is asked the *target* question: “So where will Linda look for her cat?
+She thinks her cat is in the garage.” (or vice versa) | Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden)
+| | | Then the child is asked the *target* question: “So where will Linda look for her cat?
 in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question.
-| Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) |
 | Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
@@
 Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer.
-Now here comes Polly.
+| Toy figure of another girl, Plastic box with drawer, Toy dog |
+| | | Now here comes Polly.
 So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”.
-| Toy figure of another girl, Plastic box with drawer, Toy dog |
 | Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
@@
 Band-Aids or a pig?
-(the *target* question) ‘‘Did Peter see inside this box?’’ (the *memory* question).
-To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ | Toy figure of a boy, Band-aid box , Toy pig |
+(the *target* question) | Toy figure of a boy, Band-aid box , Toy pig |
+| | | ‘‘Did Peter see inside this box?’’ (the *memory* question). To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ 
 | Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
@@
 In his backpack or in the closet?’’ (the _reality_ question).
-To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
+| Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
+| | | To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ 
 | Perspective-Taking Level 2 | Flavell et al., 1981 | Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child’s side and right side up (or upside down) from the experimenter’s.

### 2024-04-17 supplements/supplements.tex
ready for revision

@@
 
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_lifespan_modelstructure}
+{\centering \includegraphics[width=1\linewidth]{../figures/lifespan_plot}
 
@@
 In the bushes or the garage?'' This is the \emph{own-belief} question., If the child chooses the bushes: ``Well, that's a good idea, but Linda thinks her cat is in the garage.
-She thinks her cat is in the garage.'' (or vice versa) Then the child is asked the \emph{target} question: ``So where will Linda look for her cat?
+She thinks her cat is in the garage.'' (or vice versa) & Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
+& & Then the child is asked the \emph{target} question: ``So where will Linda look for her cat?
 in the bushes or in the garage?'', To be correct, the child must answer the target question opposite from his/her answer to the \emph{own-belief} question.
-& Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
+& \\
 Knowledge Access & Wellman \& Liu, 2004 → Pratt \& Bryant (1990), Pillow (1989) & Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
@@
 Next, the drawer is opened and the child is shown the content of the drawer: ``Let's see\ldots it's really a dog inside!'' Close the drawer: ``Okay, what is in the drawer?'', Then a toy figure of a girl is produced: ``Polly has never ever seen inside this drawer.
-Now here comes Polly.
+& Toy figure of another girl, Plastic box with drawer, Toy dog \\
+& & Now here comes Polly.
 So, does Polly know what is inside the drawer?'' (\emph{target} question) ``Did Polly see inside this drawer?'' (\emph{memory} question'', To be correct, the child must answer the target question ``no'' and answer the memory control question ``no''.
-& Toy figure of another girl, Plastic box with drawer, Toy dog \\
+& \\
 Contents False Belief & Wellman \& Liu, 2004 → Perner, Leekam, \& Wimmer, 1987; see also Wellman et al., 2001 & The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
 ``Here's a band-aid box.
-What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: ``Peter has never ever seen inside this band-aid box.
+What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: '\,'Peter has never ever seen inside this band-aid box.
 Now here comes Peter.
@@
 Band-Aids or a pig?
-(the \emph{target} question) `\,`Did Peter see inside this box?'' (the \emph{memory} question).
-To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & Toy figure of a boy, Band-aid box , Toy pig \\
+(the \emph{target} question) & Toy figure of a boy, Band-aid box , Toy pig \\
+& & ``Did Peter see inside this box?'' (the \emph{memory} question). To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & \\
 Explicit False Belief & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Siegal \& Beattie, 1991 & Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
@@
 In his backpack or in the closet?'' (the \emph{reality} question).
-To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\
+& Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\
+& & To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & \\
 Perspective-Taking Level 2 & Flavell et al., 1981 & Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child's side and right side up (or upside down) from the experimenter's.

### 2024-04-19 paper/manuscript.Rmd
anonymize supplements, correct small mistakes

@@
 (ref:figlab1) **Developmental trajectory of gaze following across the lifespan**.
-Grey dots show the mean level of imprecision (ie., absolute distance between the target's center and the participant's click) for each subject averaged across trials.
+Grey dots show the mean level of imprecision (i.e., absolute distance between the target's center and the participant's click) for each subject averaged across trials.
 The unit of imprecision is counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center.
@@
 High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]).
-We found substantial evidence for a non-linear development in gaze following across the lifespan.
+We found substantial evidence for a non-linear development in gaze following across the lifespan (see Figure \@ref(fig:fig1)).
 The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model.
@@
 
-(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter.
+(ref:figlab3) **Gaze model results** (A) Developmental trajectory of the estimated model parameter.
 Grey dots show individual level parameter values.

### 2024-04-19 supplements/supplements.Rmd
anonymize supplements, correct small mistakes

--- 2024-03-27 supplements/supplements.Rmd
@@
 shorttitle        : "Supplements"
+
 author:
-
-  - name          : "Julia Prein"
+  - name          : "Julia Christin Prein"
     affiliation   : "1,2"
@@
   - name          : "Annika Werwach"
-    affiliation   : "1"
+    affiliation   : "3,4"
   - name          : "Daniel B. M. Haun"
@@
     institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
+  - id            : "3"
+    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
+  - id            : "4"
+    institution   : "Max Planck School of Cognition, Leipzig, Germany"
   - id            : "*"
-    institution   : "shared last authorship"  
+    institution   : "Shared senior authorship" 
 floatsintext      : yes
 bibliography      : ["../../references.bib"]
-figurelist        : no
-tablelist         : no
+figurelist        : yes
+tablelist         : yes
 footnotelist      : no
 linenumbers       : yes
-mask              : no
+mask              : yes
 draft             : no
-documentclass     : "apa7"
-classoption       : "man"
-output            : papaja::apa6_pdf
 header-includes:
   - \usepackage{setspace}
-  - \usepackage{float}
   - \captionsetup[figure]{font={stretch=1}}
+  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
+  - |
+    \makeatletter
+    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-1em}%
+      {\normalfont\normalsize\bfseries\typesectitle}}
+
+    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+      {-\z@\relax}%
+      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+    \makeatother
+
+csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
+documentclass     : "apa7"
+output            : papaja::apa6_pdf
 editor_options: 
@@
 ## Participants
-```{r lifespan_sample, include = T, out.width = "100%"}
-lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
-
-lifespan_table <- lifespan_sample %>% 
-  mutate(
-    n = str_glue_data(., "{n_total} ({n_females} female)"), 
-    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
-  ) %>% 
-  rename(
-    `Age group` = age_group,
-    `Age SD` = age_sd, 
-    `Age mean` = age_mean
-  ) %>% 
-  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
-
-knitr::kable(lifespan_table, format = "latex", booktabs = TRUE) %>% 
-  kable_styling(latex_options = c("scale_down", "HOLD_position"))
-```
+For further information on the participants in Study 1, please see Supplementary Table S1.
 
@@
 We then visually compared the model predictions of the original and the simplified models with each other.
-As you can see in Figure \@ref(fig:fig1), results of the two models did not differ notably.
-
-(ref:figlab1) **Comparison between models on a trial- or subject-level**.
-Grey dots show data of each trial.
-Solid lines show the mean predicted developmental trajectory for both models.
-Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).
-```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
-knitr::include_graphics("../figures/supplements_lifespan_modelstructure.pdf")
-```
+As you can see in Figure \@ref(fig:S1), results of the two models did not differ notably.
 
@@
 For previous reliability analyses [@prein2023tango], we had increased the trial number for an adult sample (N = 70; each 30 trials).
-Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \@ref(fig:fig2)).
-
-(ref:figlab2) **Gaze funnel for adult sample with higher trial number**.
-```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
-knitr::include_graphics("../figures/gazefunnel_adults.pdf")
-```
+Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \@ref(fig:S2)).
 
 ## Inference parameter estimates per individual
-As can be seen in Figure \@ref(fig:fig3) and Figure \@ref(fig:fig4), the gaze model estimated the inference parameter for each individual.
+As can be seen in Figure \@ref(fig:S3) and Figure \@ref(fig:S4), the gaze model estimated the inference parameter for each individual.
 Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty.
 In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.
-
-(ref:figlab3) **Gaze model estimates faceted by individual**.
-```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
-knitr::include_graphics("../figures/supplements_gazemodel_facetedinference.pdf")
-```
-
-(ref:figlab4) **Gaze model estimates ordered by descending inference parameter value**.
-```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
-knitr::include_graphics("../figures/supplements_gazemodel_indinference.pdf")
-```
 
@@
 The mean comes down to the center, namely 960.
-However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A).
+However, as you can see in Figure \@ref(fig:S5)A below, the U shape is weaker compared to the other models.
 Most importantly, note that this is only the case when you average across all the trials.
-When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C).
-In our correlational plots (Figure 5B), we see that the gaze model is clearly favored.
+When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure \@ref(fig:S5)C).
+In our correlational plots (Figure  S\@ref(fig:S5)B), we see that the gaze model is clearly favored.
 This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.
-
-(ref:figlab5) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models.
-Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
-B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
-C: Predicted click coordinates (cf.
-not imprecision) by target position across the different models.
-
-```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
-knitr::include_graphics("../figures/gazemodel_simulated_u.png")
-```
 
@@
 ## Procedure Theory of mind battery 
+For the Theory of Mind battery, we followed the standardized procedure as described below. The battery was administered in German and presented in the order as stated below.
 
-|     |     |     |     |
-| --- | --- | --- | --- |
-| **Task name** | **Author** | **Description** | **Material used** |
-| Diverse Beliefs | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Wellman et al., 1996 | Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it.
-“Here’s Linda.
+### (1) Diverse Beliefs [@wellman2004scaling]
+Material: Girl figure, leaf with garage & bush. 
+Experimenter (E): "Look, this is Linda.
 Linda wants to find her cat.
-Her cat might be hiding in the bushes or it might be hiding in the garage.
-Where do you think the cat is?
-In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage.
-She thinks her cat is in the garage.” (or vice versa) Then the child is asked the *target* question: “So where will Linda look for her cat?
-in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question.
-| Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) |
-| Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
-“Here’s a drawer.
-What do you think is inside the drawer?” (The child can give any answer she/he likes or indicate that she/he does not know).
-Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer.
-Now here comes Polly.
-So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”.
-| Toy figure of another girl, Plastic box with drawer, Toy dog |
-| Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
-‘‘Here’s a band-aid box.
-What do you think is inside the band-aid box?’’ Next, the band-aid box is opened: ‘‘Let’s see … it’s really a pig inside!’’ The band-aid box is closed: ‘‘Okay, what is in the band-aid box?’’ Then a toy figure of a boy is produced: ‘‘Peter has never ever seen inside this band-aid box.
-Now here comes Peter.
-So, what does Peter think is in the box?
-Band-Aids or a pig?
-(the *target* question) ‘‘Did Peter see inside this box?’’ (the *memory* question).
-To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ | Toy figure of a boy, Band-aid box , Toy pig |
-| Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
-‘‘Here’s Scott.
-Scott wants to find his mittens.
-His mittens might be in his backpack or they might be in the closet.
-Really, Scott’s mittens are in his backpack.
-But Scott thinks his mittens are in the closet.’’ ‘‘So, where will Scott look for his mittens?
-In his backpack or in the closet?’’ (the *target* question) ‘‘Where are Scott’s mittens really?
-In his backpack or in the closet?’’ (the _reality_ question).
-To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
-| Perspective-Taking Level 2 | Flavell et al., 1981 | Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child’s side and right side up (or upside down) from the experimenter’s.
-The child’s task is to indicate in which of these two orientations it appeared to the experimenter (“standing on its feet” or “lying on its back”).
-| Picture of a turtle |
-| Perspective-Taking Level 2 | Flavell et al., 1981 | Children are shown a horizontally placed picture of a worm lying between a red blanket and a blue blanket.
-The child was then asked if the worm appeared to the experimenter, seated opposite, to be lying on the red blanket or on the blue blanket.
-| Picture of a worm between two blankets |
+The cat is either hiding behind the bush or in the garage.
+Where do you think the cat is hiding?
+Behind the bush or in the garage?" (own-belief question).
+Child: "Garage".
+E: "That's a good idea!
+But Linda thinks her cat is behind the bush.
+She thinks her cat is behind the bush.
+So, where will Linda look for her cat?
+Behind the bush or in the garage?" (target question)
+
+### (2) Knowledge Access [@wellman2004scaling]
+Material: Yellow box, pig figure, female figure.
+E: "Look, here's a box.
+What do you think is in the box?" [Child answers] [Box opens] E: "Let's see...oh, there's actually a pig inside!" [Box is closed] E: "What's in the box?" [E pulls out figure] E: "That's Polly.
+Polly has never looked in the box.
+So, does Polly know what's in the box?
+(target question) Has Polly ever looked in the box?
+(control question)"
+
+### (3) Contents False Belief [@wellman2004scaling]
+Material: Smarties box, figure of a dog, figure of a boy. 
+E: "Here is a Smartie box.
+What do you think is inside?" [Smartie box is opened] E: "Let's see...there's actually a dog inside!" [Smartie box is closed] E: "Okay, what's in the Smartie box?" [Man's figure is taken out] E: "This is Peter.
+Peter has never looked inside the Smartie box.
+What does Peter think is in the box?
+Smarties or a dog?
+(target question) Has Peter ever looked in the box?
+(memory question)"
+
+### (4) Explicit False Belief [@wellman2004scaling]
+Material: Figure of a boy, sheet with cupboard & rucksack on it.
+E: "This is Scott.
+Scott wants to find his gloves.
+The gloves could be in his backpack or they could be in the closet.
+In reality, they are in the backpack.
+But Scott thinks his gloves are in the closet.
+So, where will Scott look for his gloves?
+In the backpack or in the closet?
+(target question) Where are his gloves really?
+In the backpack or in the closet?
+(reality question)"
+
+### (5) Perspective-Taking Level 2 version I [@flavell1981development; @flavell1981younga]
+Material: Picture of turtle. 
+E: "Look, here's a picture of a turtle.
+I'll put it between us.
+What does the turtle look like to you, is it standing on its feet or lying on its back?
+(own perspective question) And what does it look like to me?
+Does it stand on its feet for me or does it lie on its back?
+(other perspective question)."
+
+### (6) Perspective-Taking Level 2 version II [@flavell1981development; @flavell1981younga]
+Material: Picture of worm between two pillows.
+E: "Now we have a worm lying between two pillows.
+I'll put it between us again.
+How does it look to you, is the worm lying on the red or the blue cushion?
+(own perspective question) And what does it look like to me - is the worm lying on the red or the blue cushion?
+(other perspective question)"
 
@@
 For example, the model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`).
-The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results below.
+The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results shown in Supplementary Table S2.
 
-```{r magnet_modelcomparison}
-magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
-  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
-  mutate_if(is.numeric, round, 2)
-
-knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE) %>% 
-  kable_styling(latex_options = c("scale_down", "HOLD_position"))
-```
+\newpage
 
@@
 :::
-
 ```{=tex}
@@
 ```
+
+\newpage
+
+# Supplementary Tables
+
+(ref:tableS1-caption) **Participants in Study 1**. Age is given in years.
+
+```{r tableS1, include = T, out.width = "100%", caption = "(ref:tableS1-caption)"}
+lifespan_sample <- readRDS("../saves/lifespan_sample.rds")
+
+lifespan_table <- lifespan_sample %>% 
+  mutate(
+    n = str_glue_data(., "{n_total} ({n_females} female)"), 
+    `Age range` = str_glue_data(., "{age_min} - {age_max}"), 
+  ) %>% 
+  rename(
+    `Age group` = age_group,
+    `Age SD` = age_sd, 
+    `Age mean` = age_mean
+  ) %>% 
+  select(`Age group`, n, `Age mean`, `Age range`, `Age SD`)
+
+knitr::kable(lifespan_table, format = "latex", booktabs = TRUE, caption = "Participants in Study 1. Age is given in years.") %>% 
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
+
+```{r tableS2, include = T, out.width = "100%", caption = "(ref:tableS2-caption)"}
+magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
+  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
+  mutate_if(is.numeric, round, 2)
+
+knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE, caption = "Model comparisons ToM tasks.") %>% 
+  kable_styling(latex_options = c("scale_down", "HOLD_position"))
+```
+
+\newpage
+
+# Supplementary Figures
+
+(ref:S1-caption) **Comparison between models on a trial- or subject-level**.
+Grey dots show data of each trial.
+Solid lines show the mean predicted developmental trajectory for both models.
+Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).
+
+```{r S1, include = T, out.width = "100%", fig.cap = "(ref:S1-caption)"}
+knitr::include_graphics(c("../figures/lifespan_plot.png"))
+```
+
+\newpage
+
+(ref:S2-caption) **Gaze funnel for adult sample with higher trial number (30 trials)**.
+The x-axis shows the target position, binned into 10 sections.
+The y-axis shows participants' imprecision in target widths.
+
+```{r S2, include = T, out.width = "100%", fig.cap = "(ref:S2-caption)"}
+knitr::include_graphics("../figures/gazefunnel_adults.pdf")
+```
+
+\newpage
+
+(ref:S3-caption) **Gaze model estimates faceted by individual**. Density curves show the distribution of the inference parameter by individual.
+
+```{r S3, include = T, out.width = "100%", fig.cap = "(ref:S3-caption)"}
+knitr::include_graphics("../figures/supplements_gazemodel_facetedinference.pdf")
+```
+
+\newpage
+
+(ref:S4-caption) **Gaze model estimates ordered by descending inference parameter value**. Density curves show the distribution of the inference parameter across individuals.
+
+```{r S4, include = T, out.width = "100%",fig.cap = "(ref:S4-caption)"}
+knitr::include_graphics("../figures/supplements_gazemodel_indinference.pdf")
+```
+
+\newpage
+
+(ref:S5-caption) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models.
+Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
+B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
+C: Predicted click coordinates (cf.
+not imprecision) by target position across the different models.
+
+```{r S5, include = T, out.width = "100%",fig.cap = "(ref:S5-caption)"}
+knitr::include_graphics("../figures/gazemodel_simulated_u.png")
+```

### 2024-04-19 supplements/supplements.tex
anonymize supplements, correct small mistakes

--- 2024-03-27 supplements/supplements.tex
@@
 \documentclass[
-  man,floatsintext]{apa7}
+  man,mask,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \usepackage{setspace}
-\usepackage{float}
 \captionsetup[figure]{font={stretch=1}}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 \ifLuaTeX
@@
   pdftitle={Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'},
-  pdfauthor={Julia Prein1,2, Luke Maurits1, Annika Werwach1, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
   pdflang={en-EN},
@@
 \title{Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'}
-\author{Julia Prein\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
+\author{Julia Christin Prein\textsuperscript{1,2}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{3,4}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{*} shared last authorship}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{3} Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany\\\textsuperscript{4} Max Planck School of Cognition, Leipzig, Germany\\\textsuperscript{*} Shared senior authorship}
 
@@
 
+For further information on the participants in Study 1, please see Supplementary Table S1.
+
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
+
+\hypertarget{model-structures}{%
+\subsubsection{Model structures}\label{model-structures}}
+
+In the paper, we reported the following model structures: linear model: \texttt{mean\_imprecision\ \textasciitilde{}\ age\_centered}; quadratic model in \texttt{R:\ mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)}; cubic model: \texttt{mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)\ +\ I(age\_centered\^{}3);} Gaussian process model: \texttt{mean\_imprecision\ \textasciitilde{}\ gp(age\_centered,\ k=50,\ c=5/4,\ scale=TRUE)}.
+Note the additional parameters in the Gaussian process model.
+With the default settings, the underlying Gaussian process maths would get solved exactly.
+By providing the arguments \texttt{k} and \texttt{c}, we use an approximation process.
+The higher the value of k, the better the approximation: we have used \texttt{k=50} for faster processing speed and better diagnostics.
+\texttt{brms} suggests 5/4 as a value for \texttt{c}.
+Adding \texttt{scale=TRUE} is supposed to improve sampling speed and convergence.
+
+Originally, we fitted the models on a trial-by-trial basis with the following structure in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}.
+However, the Gaussian Process model was computationally heavy.
+Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
+We then visually compared the model predictions of the original and the simplified models with each other.
+As you can see in Figure \ref{fig:S1}, results of the two models did not differ notably.
+
+\hypertarget{changepoint-analysis}{%
+\subsubsection{Changepoint analysis}\label{changepoint-analysis}}
+
+In our Bayesian changepoint analysis, we restricted the model to a constant mean (i.e., a flat line with zero degree polynomial) within each segment, and to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade) to avoid ``overreactions'' to individual outlying data points.
+In a supplementary analysis, we assessed how different parameter settings effected of our changepoint analysis.
+We changed the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
+When the model had more explorative room, for example, by a greater number of change points, smaller minimum number of data points between change points, higher polynomial order, the model outputs showed more fine-grained change points.
+The exact location of the change points varied slightly.
+Overall, the interpretation stayed the same as the one we reported in the paper.
+While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
+There was a minor change in that elderly adults became slightly more imprecise again.
+If you are interested into the details, please have a look at the file \texttt{supplements\_changepoint\_parameters.html}, which you can find in the GitHub repository in the \texttt{stats} folder.
+
+\hypertarget{study-2-computational-cognitive-model}{%
+\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
+
+\hypertarget{analysis-1}{%
+\subsection{Analysis}\label{analysis-1}}
+
+\hypertarget{gaze-model-prediction}{%
+\subsubsection{Gaze model prediction}\label{gaze-model-prediction}}
+
+Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides).
+Since the task is presented on a screen, there is a natural border towards one side.
+Imagine the target lands to the very right side.
+Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now.
+Therefore, the predicted U-shaped pattern should decrease again towards the screen borders.
+For previous reliability analyses (Prein et al., 2023), we had increased the trial number for an adult sample (N = 70; each 30 trials).
+Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \ref{fig:S2}).
+
+\hypertarget{inference-parameter-estimates-per-individual}{%
+\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}}
+
+As can be seen in Figure \ref{fig:S3} and Figure \ref{fig:S4}, the gaze model estimated the inference parameter for each individual.
+Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty.
+In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.
+
+\newpage
+
+\hypertarget{simulations}{%
+\subsection{Simulations}\label{simulations}}
+
+In the manuscript, we have described the gaze model and two alternatives: random guessing and a center bias.
+Here, we consider two more alternatives.
+Let us consider a model that assumes participants can infer the agent's focus without any noise (for example, by tracing the line of sight).
+A model like this would assume that participants follow gaze without any uncertainty.
+Therefore, no U curve would be predicted.
+Furthermore, let us assume another model in that participants still show no inferential noise, but they vary in their amount of motor noise, so how accurately participants then click at the corresponding location.
+A model like this would assume equal variance across the target locations, so we would not expect a U-shape here.
+
+Please note that our random guessing model acts like 100\% noise: the predictions of a participant's click on a trial level range uniformly from 0 to 1920 (the whole screen range).
+The mean comes down to the center, namely 960.
+However, as you can see in Figure \ref{fig:S5}A below, the U shape is weaker compared to the other models.
+Most importantly, note that this is only the case when you average across all the trials.
+When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure \ref{fig:S5}C).
+In our correlational plots (Figure S\ref{fig:S5}B), we see that the gaze model is clearly favored.
+This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.
+
+\hypertarget{study-3-components-of-gaze-understanding}{%
+\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
+
+\hypertarget{procedure-theory-of-mind-battery}{%
+\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}}
+
+For the Theory of Mind battery, we followed the standardized procedure as described below. The battery was administered in German and presented in the order as stated below.
+
+\hypertarget{diverse-beliefs-wellman2004scaling}{%
+\subsubsection{(1) Diverse Beliefs (Wellman \& Liu, 2004)}\label{diverse-beliefs-wellman2004scaling}}
+
+Material: Girl figure, leaf with garage \& bush.
+Experimenter (E): ``Look, this is Linda.
+Linda wants to find her cat.
+The cat is either hiding behind the bush or in the garage.
+Where do you think the cat is hiding?
+Behind the bush or in the garage?'' (own-belief question).
+Child: ``Garage''.
+E: ``That's a good idea!
+But Linda thinks her cat is behind the bush.
+She thinks her cat is behind the bush.
+So, where will Linda look for her cat?
+Behind the bush or in the garage?'' (target question)
+
+\hypertarget{knowledge-access-wellman2004scaling}{%
+\subsubsection{(2) Knowledge Access (Wellman \& Liu, 2004)}\label{knowledge-access-wellman2004scaling}}
+
+Material: Yellow box, pig figure, female figure.
+E: ``Look, here's a box.
+What do you think is in the box?'' {[}Child answers{]} {[}Box opens{]} E: ``Let's see\ldots oh, there's actually a pig inside!'' {[}Box is closed{]} E: ``What's in the box?'' {[}E pulls out figure{]} E: ``That's Polly.
+Polly has never looked in the box.
+So, does Polly know what's in the box?
+(target question) Has Polly ever looked in the box?
+(control question)''
+
+\hypertarget{contents-false-belief-wellman2004scaling}{%
+\subsubsection{(3) Contents False Belief (Wellman \& Liu, 2004)}\label{contents-false-belief-wellman2004scaling}}
+
+Material: Smarties box, figure of a dog, figure of a boy.
+E: ``Here is a Smartie box.
+What do you think is inside?'' {[}Smartie box is opened{]} E: ``Let's see\ldots there's actually a dog inside!'' {[}Smartie box is closed{]} E: ``Okay, what's in the Smartie box?'' {[}Man's figure is taken out{]} E: ``This is Peter.
+Peter has never looked inside the Smartie box.
+What does Peter think is in the box?
+Smarties or a dog?
+(target question) Has Peter ever looked in the box?
+(memory question)''
+
+\hypertarget{explicit-false-belief-wellman2004scaling}{%
+\subsubsection{(4) Explicit False Belief (Wellman \& Liu, 2004)}\label{explicit-false-belief-wellman2004scaling}}
+
+Material: Figure of a boy, sheet with cupboard \& rucksack on it.
+E: ``This is Scott.
+Scott wants to find his gloves.
+The gloves could be in his backpack or they could be in the closet.
+In reality, they are in the backpack.
+But Scott thinks his gloves are in the closet.
+So, where will Scott look for his gloves?
+In the backpack or in the closet?
+(target question) Where are his gloves really?
+In the backpack or in the closet?
+(reality question)''
+
+\hypertarget{perspective-taking-level-2-version-i-flavell1981development-flavell1981younga}{%
+\subsubsection{(5) Perspective-Taking Level 2 version I (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-i-flavell1981development-flavell1981younga}}
+
+Material: Picture of turtle.
+E: ``Look, here's a picture of a turtle.
+I'll put it between us.
+What does the turtle look like to you, is it standing on its feet or lying on its back?
+(own perspective question) And what does it look like to me?
+Does it stand on its feet for me or does it lie on its back?
+(other perspective question).''
+
+\hypertarget{perspective-taking-level-2-version-ii-flavell1981development-flavell1981younga}{%
+\subsubsection{(6) Perspective-Taking Level 2 version II (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-ii-flavell1981development-flavell1981younga}}
+
+Material: Picture of worm between two pillows.
+E: ``Now we have a worm lying between two pillows.
+I'll put it between us again.
+How does it look to you, is the worm lying on the red or the blue cushion?
+(own perspective question) And what does it look like to me - is the worm lying on the red or the blue cushion?
+(other perspective question)''
+
+\hypertarget{analysis-2}{%
+\subsection{Analysis}\label{analysis-2}}
+
+\hypertarget{animal-vs.-human-faces}{%
+\subsubsection{Animal vs.~human faces}\label{animal-vs.-human-faces}}
+
+In Study 1 and Study 2, we presented the TANGO (Prein et al., 2023) with animal characters.
+For Study 3, we exchanged the animals with human faces, modelled in appearance after the local population.
+We decided to do so in order to enhance the social context of this task and to make it more comparable to the Theory of Mind task battery (where there is live interaction with the experimenter).
+To ensure the change from animal to human faces did not notably change children's responses, we conducted an exploratory analysis.
+We conducted a GLMM analysis with the following model structure in \texttt{R:\ click\ \textasciitilde{}\ age\_scaled\ +\ stimuli\ +\ symmetric\_position\ +\ trial\_nr\ +\ (1\ +\ symmetric\_position\ +\ trial\_nr\ \textbar{}\ subj\_id)}; where \texttt{stimuli} denoted either human or animal faces.
+The estimate for the fixed effect of \texttt{stimuli} was small and the 95\% CrI included zero: \(\beta\) = 0.16; 95\% CrI {[}-0.06; 0.37{]}).
+Therefore, we concluded that the animal vs.~human version of the TANGO did not differ substantially.
+
+\hypertarget{model-comparisons}{%
+\subsubsection{Model comparisons}\label{model-comparisons}}
+
+To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery).
+For example, the model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
+The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results shown in Supplementary Table S2.
+
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981younga}{}}%
+Flavell, J.
+H., Everett, B.
+A., Croft, K., \& Flavell, E.
+R.
+(1981).
+Young children's knowledge about visual perception: {Further} evidence for the {Level} 1--{Level} 2 distinction.
+\emph{Developmental Psychology}, \emph{17}, 99--103.
+\url{https://doi.org/10.1037/0012-1649.17.1.99}
+
+\leavevmode\vadjust pre{\hypertarget{ref-flavell1981development}{}}%
+Flavell, J.
+H., Flavell, E.
+R., Green, F.
+L., \& Wilcox, S.
+A.
+(1981).
+The {Development} of {Three Spatial Perspective-Taking Rules}.
+\emph{Child Development}, \emph{52}(1), 356--358.
+\url{https://doi.org/10.2307/1129250}
+
+\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
+Prein, J.
+C., Kalinke, S., Haun, D.
+B.
+M., \& Bohn, M.
+(2023).
+{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
+\emph{Behavior Research Methods}.
+\url{https://doi.org/10.3758/s13428-023-02159-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
+Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
+
+\end{CSLReferences}
+
+\endgroup
+
+\newpage
+
+\hypertarget{supplementary-tables}{%
+\section{Supplementary Tables}\label{supplementary-tables}}
+
 \begin{table}[H]
 \centering
+\caption{\label{tab:tableS1}Participants in Study 1. Age is given in years.}
+\centering
 \resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
-\begin{tabular}{rlrlr}
+\begin{tabular}[t]{rlrlr}
 \toprule
@@
 
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-\hypertarget{model-structures}{%
-\subsubsection{Model structures}\label{model-structures}}
-
-In the paper, we reported the following model structures: linear model: \texttt{mean\_imprecision\ \textasciitilde{}\ age\_centered}; quadratic model in \texttt{R:\ mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)}; cubic model: \texttt{mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)\ +\ I(age\_centered\^{}3);} Gaussian process model: \texttt{mean\_imprecision\ \textasciitilde{}\ gp(age\_centered,\ k=50,\ c=5/4,\ scale=TRUE)}.
-Note the additional parameters in the Gaussian process model.
-With the default settings, the underlying Gaussian process maths would get solved exactly.
-By providing the arguments \texttt{k} and \texttt{c}, we use an approximation process.
-The higher the value of k, the better the approximation: we have used \texttt{k=50} for faster processing speed and better diagnostics.
-\texttt{brms} suggests 5/4 as a value for \texttt{c}.
-Adding \texttt{scale=TRUE} is supposed to improve sampling speed and convergence.
-
-Originally, we fitted the models on a trial-by-trial basis with the following structure in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}.
-However, the Gaussian Process model was computationally heavy.
-Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect.
-We then visually compared the model predictions of the original and the simplified models with each other.
-As you can see in Figure \ref{fig:fig1}, results of the two models did not differ notably.
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_lifespan_modelstructure}
-
-}
-
-\caption{\textbf{Comparison between models on a trial- or subject-level}.
-Grey dots show data of each trial.
-Solid lines show the mean predicted developmental trajectory for both models.
-Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).}\label{fig:fig1}
-\end{figure}
-
-\hypertarget{changepoint-analysis}{%
-\subsubsection{Changepoint analysis}\label{changepoint-analysis}}
-
-In our Bayesian changepoint analysis, we restricted the model to a constant mean (i.e., a flat line with zero degree polynomial) within each segment, and to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade) to avoid ``overreactions'' to individual outlying data points.
-In a supplementary analysis, we assessed how different parameter settings effected of our changepoint analysis.
-We changed the number of allowed change points, the minimum number of data points between change points, and the polynomial order.
-When the model had more explorative room, for example, by a greater number of change points, smaller minimum number of data points between change points, higher polynomial order, the model outputs showed more fine-grained change points.
-The exact location of the change points varied slightly.
-Overall, the interpretation stayed the same as the one we reported in the paper.
-While early childhood was characterized by much change, adults showed a relatively stable level of imprecision.
-There was a minor change in that elderly adults became slightly more imprecise again.
-If you are interested into the details, please have a look at the file \texttt{supplements\_changepoint\_parameters.html}, which you can find in the GitHub repository in the \texttt{stats} folder.
-
-\hypertarget{study-2-computational-cognitive-model}{%
-\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
-
-\hypertarget{analysis-1}{%
-\subsection{Analysis}\label{analysis-1}}
-
-\hypertarget{gaze-model-prediction}{%
-\subsubsection{Gaze model prediction}\label{gaze-model-prediction}}
-
-Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides).
-Since the task is presented on a screen, there is a natural border towards one side.
-Imagine the target lands to the very right side.
-Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now.
-Therefore, the predicted U-shaped pattern should decrease again towards the screen borders.
-For previous reliability analyses (Prein, Kalinke, Haun, \& Bohn, 2023), we had increased the trial number for an adult sample (N = 70; each 30 trials).
-Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \ref{fig:fig2}).
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../figures/gazefunnel_adults}
-
-}
-
-\caption{\textbf{Gaze funnel for adult sample with higher trial number}.}\label{fig:fig2}
-\end{figure}
-
-\hypertarget{inference-parameter-estimates-per-individual}{%
-\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}}
-
-As can be seen in Figure \ref{fig:fig3} and Figure \ref{fig:fig4}, the gaze model estimated the inference parameter for each individual.
-Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty.
-In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_facetedinference}
-
-}
-
-\caption{\textbf{Gaze model estimates faceted by individual}.}\label{fig:fig3}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_indinference}
-
-}
-
-\caption{\textbf{Gaze model estimates ordered by descending inference parameter value}.}\label{fig:fig4}
-\end{figure}
-
-\newpage
-
-\hypertarget{simulations}{%
-\subsection{Simulations}\label{simulations}}
-
-In the manuscript, we have described the gaze model and two alternatives: random guessing and a center bias.
-Here, we consider two more alternatives.
-Let us consider a model that assumes participants can infer the agent's focus without any noise (for example, by tracing the line of sight).
-A model like this would assume that participants follow gaze without any uncertainty.
-Therefore, no U curve would be predicted.
-Furthermore, let us assume another model in that participants still show no inferential noise, but they vary in their amount of motor noise, so how accurately participants then click at the corresponding location.
-A model like this would assume equal variance across the target locations, so we would not expect a U-shape here.
-
-Please note that our random guessing model acts like 100\% noise: the predictions of a participant's click on a trial level range uniformly from 0 to 1920 (the whole screen range).
-The mean comes down to the center, namely 960.
-However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A).
-Most importantly, note that this is only the case when you average across all the trials.
-When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C).
-In our correlational plots (Figure 5B), we see that the gaze model is clearly favored.
-This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth]{../figures/gazemodel_simulated_u}
-
-}
-
-\caption{\textbf{Predictions of alternative models across target positions.} A: Predicted U-pattern across target positions by the different models.
-Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
-B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
-C: Predicted click coordinates (cf.~not imprecision) by target position across the different models.}\label{fig:fig5}
-\end{figure}
-
-\hypertarget{study-3-components-of-gaze-understanding}{%
-\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
-
-\hypertarget{procedure-theory-of-mind-battery}{%
-\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
-\toprule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-\textbf{Task name} & \textbf{Author} & \textbf{Description} & \textbf{Material used} \\
-Diverse Beliefs & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Wellman et al., 1996 & Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it.
-``Here's Linda.
-Linda wants to find her cat.
-Her cat might be hiding in the bushes or it might be hiding in the garage.
-Where do you think the cat is?
-In the bushes or the garage?'' This is the \emph{own-belief} question., If the child chooses the bushes: ``Well, that's a good idea, but Linda thinks her cat is in the garage.
-She thinks her cat is in the garage.'' (or vice versa) Then the child is asked the \emph{target} question: ``So where will Linda look for her cat?
-in the bushes or in the garage?'', To be correct, the child must answer the target question opposite from his/her answer to the \emph{own-belief} question.
-& Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) \\
-Knowledge Access & Wellman \& Liu, 2004 → Pratt \& Bryant (1990), Pillow (1989) & Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer.
-``Here's a drawer.
-What do you think is inside the drawer?'' (The child can give any answer she/he likes or indicate that she/he does not know).
-Next, the drawer is opened and the child is shown the content of the drawer: ``Let's see\ldots it's really a dog inside!'' Close the drawer: ``Okay, what is in the drawer?'', Then a toy figure of a girl is produced: ``Polly has never ever seen inside this drawer.
-Now here comes Polly.
-So, does Polly know what is inside the drawer?'' (\emph{target} question) ``Did Polly see inside this drawer?'' (\emph{memory} question'', To be correct, the child must answer the target question ``no'' and answer the memory control question ``no''.
-& Toy figure of another girl, Plastic box with drawer, Toy dog \\
-Contents False Belief & Wellman \& Liu, 2004 → Perner, Leekam, \& Wimmer, 1987; see also Wellman et al., 2001 & The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box.
-``Here's a band-aid box.
-What do you think is inside the band-aid box?'' Next, the band-aid box is opened: ``Let's see \ldots{} it's really a pig inside!'' The band-aid box is closed: ``Okay, what is in the band-aid box?'' Then a toy figure of a boy is produced: ``Peter has never ever seen inside this band-aid box.
-Now here comes Peter.
-So, what does Peter think is in the box?
-Band-Aids or a pig?
-(the \emph{target} question) `\,`Did Peter see inside this box?'' (the \emph{memory} question).
-To be correct the child must answer the target question ``band-aids'' and answer the memory question ``no.'' & Toy figure of a boy, Band-aid box , Toy pig \\
-Explicit False Belief & Wellman \& Liu, 2004 → Wellman \& Bartsch, 1989; Siegal \& Beattie, 1991 & Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it.
-``Here's Scott.
-Scott wants to find his mittens.
-His mittens might be in his backpack or they might be in the closet.
-Really, Scott's mittens are in his backpack.
-But Scott thinks his mittens are in the closet.'' ``So, where will Scott look for his mittens?
-In his backpack or in the closet?'' (the \emph{target} question) ``Where are Scott's mittens really?
-In his backpack or in the closet?'' (the \emph{reality} question).
-To be correct the child must answer the target question ``closet'' and answer the reality question ``backpack.'' & Toy figure of another boy, Sheet of paper with a children's room with a backpack and a clost on it \\
-Perspective-Taking Level 2 & Flavell et al., 1981 & Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child's side and right side up (or upside down) from the experimenter's.
-The child's task is to indicate in which of these two orientations it appeared to the experimenter (``standing on its feet'' or ``lying on its back'').
-& Picture of a turtle \\
-Perspective-Taking Level 2 & Flavell et al., 1981 & Children are shown a horizontally placed picture of a worm lying between a red blanket and a blue blanket.
-The child was then asked if the worm appeared to the experimenter, seated opposite, to be lying on the red blanket or on the blue blanket.
-& Picture of a worm between two blankets \\
-\end{longtable}
-
-\hypertarget{analysis-2}{%
-\subsection{Analysis}\label{analysis-2}}
-
-\hypertarget{animal-vs.-human-faces}{%
-\subsubsection{Animal vs.~human faces}\label{animal-vs.-human-faces}}
-
-In Study 1 and Study 2, we presented the TANGO (Prein et al., 2023) with animal characters.
-For Study 3, we exchanged the animals with human faces, modelled in appearance after the local population.
-We decided to do so in order to enhance the social context of this task and to make it more comparable to the Theory of Mind task battery (where there is live interaction with the experimenter).
-To ensure the change from animal to human faces did not notably change children's responses, we conducted an exploratory analysis.
-We conducted a GLMM analysis with the following model structure in \texttt{R:\ click\ \textasciitilde{}\ age\_scaled\ +\ stimuli\ +\ symmetric\_position\ +\ trial\_nr\ +\ (1\ +\ symmetric\_position\ +\ trial\_nr\ \textbar{}\ subj\_id)}; where \texttt{stimuli} denoted either human or animal faces.
-The estimate for the fixed effect of \texttt{stimuli} was small and the 95\% CrI included zero: \(\beta\) = 0.16; 95\% CrI {[}-0.06; 0.37{]}).
-Therefore, we concluded that the animal vs.~human version of the TANGO did not differ substantially.
-
-\hypertarget{model-comparisons}{%
-\subsubsection{Model comparisons}\label{model-comparisons}}
-
-To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery).
-For example, the model notation in \texttt{R:\ tango\_mean\ \textasciitilde{}\ age\_centered\ +\ magnet\_scaled\ +\ perspective\_scaled}).
-The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results below.
-
 \begin{table}[H]
 \centering
+\caption{\label{tab:tableS2}Model comparisons ToM tasks.}
+\centering
 \resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
-\begin{tabular}{lrrrrr}
+\begin{tabular}[t]{lrrrrr}
 \toprule
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\newpage
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\hypertarget{supplementary-figures}{%
+\section{Supplementary Figures}\label{supplementary-figures}}
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
-Prein, J.
-C., Kalinke, S., Haun, D.
-B.
-M., \& Bohn, M.
-(2023).
-{TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}.
-\url{https://doi.org/10.3758/s13428-023-02159-5}
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{../figures/lifespan_plot} \caption{\textbf{Comparison between models on a trial- or subject-level}.
+Grey dots show data of each trial.
+Solid lines show the mean predicted developmental trajectory for both models.
+Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).}\label{fig:S1}
+\end{figure}
 
-\end{CSLReferences}
+\newpage
 
-\endgroup
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{../figures/gazefunnel_adults} \caption{\textbf{Gaze funnel for adult sample with higher trial number (30 trials)}.
+The x-axis shows the target position, binned into 10 sections.
+The y-axis shows participants' imprecision in target widths.}\label{fig:S2}
+\end{figure}
+
+\newpage
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_facetedinference} \caption{\textbf{Gaze model estimates faceted by individual}.
+Density curves show the distribution of the inference parameter by individual.}\label{fig:S3}
+\end{figure}
+
+\newpage
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_indinference} \caption{\textbf{Gaze model estimates ordered by descending inference parameter value}.
+Density curves show the distribution of the inference parameter across individuals.}\label{fig:S4}
+\end{figure}
+
+\newpage
+
+\begin{figure}[H]
+\includegraphics[width=1\linewidth]{../figures/gazemodel_simulated_u} \caption{\textbf{Predictions of alternative models across target positions.} A: Predicted U-pattern across target positions by the different models.
+Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click.
+B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group.
+C: Predicted click coordinates (cf.~not imprecision) by target position across the different models.}\label{fig:S5}
+\end{figure}
+
+\clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
+\clearpage
+\renewcommand{\listtablename}{Table captions}
 

### 2024-05-14 paper/manuscript.Rmd
work on revisions round 2

@@
 Each of these gaze vectors results from connecting the center of the agent’s eyeball and the center of the pupil.
-Because the center of the eyeball is not directly observable, vector estimation happens with a degree of uncertainty.
+Because the center of the eyeball is not directly observable at that moment, vector estimation happens with a degree of uncertainty.
 Development of gaze following corresponds to a decrease in uncertainty.
@@
 We found very clear support for our gaze model, both in children as well as adults.
-A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`]).
+A strong correlation between the data mean and the gaze model estimate ($\sigma_v$) showed that the data mean is suitable to quantify individual differences: child sample *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "gazemodel_param_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_kids"]`]; adult sample *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "gazemodel_param_adults"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_param_adults"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_param_adults"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_param_adults"]`].
 The gaze model predicted a U-shaped pattern which we also observed in our data (see Figure \@ref(fig:fig3)C).
@@
 For the child sample, we went one step further into the analysis.
-When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r* = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
+When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "gazemodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "centermodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "randommodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
 The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
 For children, we estimated the width of the prior's distribution based on the participants' age.
-Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95% high-density interval (HDI) [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
 The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
 
-(ref:figlab3) **Gaze model results** (A) Developmental trajectory of the estimated model parameter.
+(ref:figlab3) **Gaze model results** (A) Developmental trajectory of th±e estimated model parameter.
 Grey dots show individual level parameter values.
@@
 Therefore, our model describes gaze following as a particular form of vector following in a social context.
+
+Previous models in the social- and non-social cognitive domain exist that rely on vector estimations (see @madl2015computational for a review of computational models for spatial memory).
+For example, @brom2012computational defined egocentric self-to-object vectors and allocentric object-to-object vectors where corresponding uncertainties due to memory and motor errors were modelled by vector weights and Gaussian noise.
+The counterfactual simulation model [@gerstenberg2021counterfactuala, @gerstenberg2021counterfactual, @gerstenberg2012noisy, @gerstenberg2014counterfactual] used vector calculations to model causal reasoning, for example, in estimating billiard ball trajectories and their collisions.
+Gaussian noise was added to the ball’s movement vector to represent people’s prior expectations, uncertainties, and expertise (the stronger the expectations, the less noise is added to the vector).
+
+In the social domain, there are additional examples of following vectors in space.
+Recent work on pointing gestures introduced the idea of a touch-line vector [@omadagain2019origin], see @li2023understanding for computational modeling.
+According to this hypothesis, humans directed their fingers not to construct an "arrow" pointing at the target, but rather as if they aimed to touch it directly.
+Consequently, the touch line is a vector that connects the eye and the pointed fingertip, and marks the object that the person's fingertip seems closest to touching from her perspective [@omadagain2019origin].
+This supports the idea that vector estimation is relevant for social-cognitive abilities.
 
@@
 
-Gaze following substantially correlated with the non-social vector following task, *r* = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
+Gaze following substantially correlated with the non-social vector following task, *r*(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Tango x Magnet"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Magnet"]`, *p* < .001, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Magnet"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Magnet"]`] (see Figure \@ref(fig:fig4)B).
 While the tasks highly overlap in task demands, their measures shared some, but not all of their variance.
 
-ToM abilities did not correlate with gaze following ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x ToM"]`]) or non-social vector following ($\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x ToM"]`]), and the correlations did not differ from each other, Williams' test *t*(`r magnet_williamsttest_tom$parameter`) = `r round(magnet_williamsttest_tom$statistic, 2)`, *p* = `r round(magnet_williamsttest_tom$p.value, 2)`.
+ToM abilities did not correlate with gaze following ($\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Tango x ToM"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x ToM"]`, *p* = `r magnet_cormatrix$p[magnet_cormatrix$Correlation == "Tango x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x ToM"]`]) or non-social vector following ($\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Magnet x ToM"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x ToM"]`,  *p* = `r magnet_cormatrix$p[magnet_cormatrix$Correlation == "Magnet x ToM"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x ToM"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x ToM"]`]), and the correlations did not differ from each other, Williams' test *t*(`r magnet_williamsttest_tom$parameter`) = `r round(magnet_williamsttest_tom$statistic, 2)`, *p* = `r round(magnet_williamsttest_tom$p.value, 3)`.
 
-Interestingly, gaze following and perspective-taking correlated with each other, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
+Interestingly, gaze following and perspective-taking correlated with each other, $\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, *p* = `r magnet_cormatrix$p[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
 Please note that the TANGO quantifies imprecision in gaze following.
 Therefore, a negative correlation suggests that imprecision in gaze following corresponds to less perspective-taking.
-Non-social vector following and perspective-taking did not correlate, $\rho$ = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
-However, according to the Williams' test, the two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 2)`.
+Non-social vector following and perspective-taking did not correlate, $\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, *p* = `r magnet_cormatrix$p[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Magnet x Perspective-taking"]`].
+However, according to the Williams' test, the two correlations did not differ significantly from each other, *t*(`r magnet_williamsttest_perspective$parameter`) = `r round(magnet_williamsttest_perspective$statistic, 2)`, *p* = `r round(magnet_williamsttest_perspective$p.value, 3)`.
 
@@
 In the TANGO, the agent’s eyes are big and round, with uniform colors, white sclera, fully visible iris and pupils, and continuous eye movement.
+The start position of the pupil is the center of the agent's eyeball -- which, later on, needs to be estimated.
 Eye gaze in natural social interactions often provides less information and is more ambiguous.

### 2024-05-14 stats/gazemodel.Rmd
work on revisions round 2

@@
 
-corrs <- rbind(corr_gazemodel_param_children$ci, corr_gazemodel_param_adults$ci, corr_gazemodel_pred$ci, corr_centermodel_pred$ci, corr_randommodel_pred$ci) %>% 
+corrs <- rbind(
+  cbind(corr_gazemodel_param_children$ci, n = corr_gazemodel_param_children$n), 
+  cbind(corr_gazemodel_param_adults$ci, n = corr_gazemodel_param_adults$n), 
+  cbind(corr_gazemodel_pred$ci, n = corr_gazemodel_pred$n), 
+  cbind(corr_centermodel_pred$ci, n = corr_centermodel_pred$n), 
+  cbind(corr_randommodel_pred$ci, n = corr_randommodel_pred$n)
+  ) %>% 
   rownames_to_column(var = "corr") %>% 
@@
             `mdl_m-dt_mn4` = "randommodel_pred_kids", 
-           )
-  ) %>% 
-  mutate(across(where(is.numeric), round, 2))
+           ), 
+  ) %>% 
+  mutate(across(2:4, ~round(.x, 2)))
 

### 2024-05-14 stats/magnet.Rmd
work on revisions round 2

@@
 
-cor_matrix <- rbind(tango_magnet$ci, tango_tom$ci, magnet_tom$ci) %>% 
+cor_matrix <- rbind(
+  cbind(tango_magnet$ci, n = tango_magnet$n),
+  cbind(tango_tom$ci, n = tango_tom$n), 
+  cbind(magnet_tom$ci, n = magnet_tom$n)
+  ) %>% 
   mutate(Correlation = rownames(.)) %>%
-  as.tibble()
+  as_tibble()
 
@@
                   `mgnt_-prsp_` = "Magnet x Perspective-taking", 
-                  `tm_gg-prsp_` = "ToM x Perspective-taking")
+                  `tm_gg-prsp_` = "ToM x Perspective-taking"), 
+    p = round(p, 3)
   ) %>% 
-  mutate(across(where(is.numeric), round, 2)) %>% 
-  select(Correlation, r, lower, upper, p)
+  mutate(across(1:3, ~round(.x, 2))) %>%
+  select(Correlation, r, lower, upper, p, n)
 

### 2024-05-14 paper/manuscript.Rmd
improve transition to non-social vector models

@@
 While the emergence of gaze following has been thoroughly studied on a group level, we know little about (a) the developmental trajectory beyond infancy and (b) the sources of individual differences.
-In Study 1, we examined gaze following across the lifespan (*N* = 471 3- to 80-year-olds; children from a mid-sized German city; international remotely tested adults).
+In Study 1, we examined gaze following across the lifespan (*N* = 478 3- to 19-year-olds from a mid-sized German city; and *N* = 240 20- to 80-year-old international, remotely tested adults).
 We found a steep performance improvement during preschool years, in which children became more precise in locating the attentional focus of an agent.
@@
 
-**Authors:** Julia Christin Prein^1^, Luke Maurits^1^, Annika Werwach^1,3,4^, Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
+**Authors:** Julia Christin Prein^1,2^, Luke Maurits^1^, Annika Werwach^1,3,4^, Daniel B. M. Haun^1,\*^, Manuel Bohn^1,2,\*^
 
@@
 We collected data online from 3- to 80- year-olds (see Supplements for further details).
-The child sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants and was recruited via an internal database of families in Leipzig, Germany, who volunteered to participate in child development studies.
+The child sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 20])` 3- to 19-year-olds and was recruited via an internal database of families in Leipzig, Germany, who volunteered to participate in child development studies.
 Participants came from ethnically homogeneous, mixed socioeconomic backgrounds with mid to high parental education levels.
@@
 *Prolific* is an online participant recruitment tool from the University of Oxford with predominantly European and US-American subjects.
-Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults who reported to have normal or corrected-to-normal vision.
+Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults between 20 and 80 years of age who reported to have normal or corrected-to-normal vision.
 For completing the study, subjects were paid above the fixed minimum wage (~£10.00/hour).
@@
 For the child sample, we went one step further into the analysis.
-When correlating the observed data across all target positions with the predictions of the three models, we found a high similarity for the gaze model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "gazemodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "centermodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "randommodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
+When correlating the observed data across all target positions and age groups with the predictions of the three models, we found a high similarity for the gaze model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "gazemodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "gazemodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "gazemodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "gazemodel_pred_kids"]`], while the correlations with the alternative models were smaller (center bias model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "centermodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "centermodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "centermodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "centermodel_pred_kids"]`]; random guessing model: *r*(`r gazemodel_corrs$n[gazemodel_corrs$corr == "randommodel_pred_kids"]`) = `r gazemodel_corrs$r[gazemodel_corrs$corr == "randommodel_pred_kids"]`,  *p* < .001, 95%CI [`r gazemodel_corrs$lower[gazemodel_corrs$corr == "randommodel_pred_kids"]`, `r gazemodel_corrs$upper[gazemodel_corrs$corr == "randommodel_pred_kids"]`]).
 The gaze model's prior over potential target locations assumed that participants' clicks would be skewed towards the screen center.
 For children, we estimated the width of the prior's distribution based on the participants' age.
-Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95% high-density interval (HDI) [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
+Interestingly, we found that the differential age effects on the center bias prior were minor (intercept = `r gazemodel_prior$mode[gazemodel_prior$type == "intercept"]`, 95% highest-density interval (HDI) [`r gazemodel_prior$lci[gazemodel_prior$type == "intercept"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "intercept"]`]; slope = `r gazemodel_prior$mode[gazemodel_prior$type == "slope"]`, 95%HDI [`r gazemodel_prior$lci[gazemodel_prior$type == "slope"]`; `r gazemodel_prior$uci[gazemodel_prior$type == "slope"]`]).
 The slope of the prior indicated that older children were only marginally less drawn towards the screen center compared to the younger children.
 
-(ref:figlab3) **Gaze model results** (A) Developmental trajectory of th±e estimated model parameter.
+(ref:figlab3) **Gaze model results** (A) Developmental trajectory of the estimated model parameter.
 Grey dots show individual level parameter values.
@@
 
-Previous models in the social- and non-social cognitive domain exist that rely on vector estimations (see @madl2015computational for a review of computational models for spatial memory).
-For example, @brom2012computational defined egocentric self-to-object vectors and allocentric object-to-object vectors where corresponding uncertainties due to memory and motor errors were modelled by vector weights and Gaussian noise.
-The counterfactual simulation model [@gerstenberg2021counterfactuala, @gerstenberg2021counterfactual, @gerstenberg2012noisy, @gerstenberg2014counterfactual] used vector calculations to model causal reasoning, for example, in estimating billiard ball trajectories and their collisions.
+Previous models in the social- and non-social cognitive domain exist that also make use of the concept of vector estimation (see @madl2015computational for a review of computational models for spatial memory).
+For example, @brom2012computational defined egocentric self-to-object vectors and allocentric object-to-object vectors where corresponding uncertainties due to memory and motor errors were modeled by vector weights and Gaussian noise.
+The counterfactual simulation model [@gerstenberg2021counterfactuala; @gerstenberg2021counterfactual; @gerstenberg2012noisy; @gerstenberg2014counterfactual] used vector calculations to model causal reasoning; for example, in estimating billiard ball trajectories and their collisions.
 Gaussian noise was added to the ball’s movement vector to represent people’s prior expectations, uncertainties, and expertise (the stronger the expectations, the less noise is added to the vector).
+Therefore, the way these models capture individual differences resembles the approach taken in the here-proposed gaze model.
 
-In the social domain, there are additional examples of following vectors in space.
-Recent work on pointing gestures introduced the idea of a touch-line vector [@omadagain2019origin], see @li2023understanding for computational modeling.
-According to this hypothesis, humans directed their fingers not to construct an "arrow" pointing at the target, but rather as if they aimed to touch it directly.
+The idea of gaze as vector following has recently been introduced to the study of pointing gestures (@omadagain2019origin, see @li2023understanding for computational modeling).
+According to this hypothesis, when humans use pointing gestures, the index finger does not constitute "arrow" pointing at the target, but is used to touch the object within one's visual field.
 Consequently, the touch line is a vector that connects the eye and the pointed fingertip, and marks the object that the person's fingertip seems closest to touching from her perspective [@omadagain2019origin].
@@
 
-Interestingly, gaze following and perspective-taking correlated with each other, $\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, *p* = `r magnet_cormatrix$p[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
+Interestingly, gaze following and perspective-taking correlated with each other, $\rho$(`r magnet_cormatrix$n[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`) = `r magnet_cormatrix$r[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, *p* < .01, 95%CI [`r magnet_cormatrix$lower[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`, `r magnet_cormatrix$upper[magnet_cormatrix$Correlation == "Tango x Perspective-taking"]`].
 Please note that the TANGO quantifies imprecision in gaze following.

### 2024-05-21 paper/manuscript.Rmd
preprint after second revision

@@
 The idea of gaze as vector following has recently been introduced to the study of pointing gestures (@omadagain2019origin, see @li2023understanding for computational modeling).
-According to this hypothesis, when humans use pointing gestures, the index finger does not constitute "arrow" pointing at the target, but is used to touch the object within one's visual field.
+According to this hypothesis, when humans use pointing gestures, the index finger does not constitute an "arrow" pointing at the target, but is used to touch the object within one's visual field.
 Consequently, the touch line is a vector that connects the eye and the pointed fingertip, and marks the object that the person's fingertip seems closest to touching from her perspective [@omadagain2019origin].

### 2024-06-24 supplements/supplements.Rmd
de-anonymize supplements

@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 draft             : no

### 2024-06-24 supplements/supplements.tex
de-anonymize supplements

@@
 \documentclass[
-  man,mask,floatsintext]{apa7}
+  man,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
   pdftitle={Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'},
+  pdfauthor={Julia Christin Prein1,2, Luke Maurits1, Annika Werwach3,4, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
   pdflang={en-EN},
@@
 
-\hypertarget{study-1-lifespan}{%
-\section{Study 1: Lifespan}\label{study-1-lifespan}}
+\section{Study 1: Lifespan}\label{study-1-lifespan}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
+\subsection{Analysis}\label{analysis}
 
-\hypertarget{model-structures}{%
-\subsubsection{Model structures}\label{model-structures}}
+\subsubsection{Model structures}\label{model-structures}
 
@@
 
-\hypertarget{changepoint-analysis}{%
-\subsubsection{Changepoint analysis}\label{changepoint-analysis}}
+\subsubsection{Changepoint analysis}\label{changepoint-analysis}
 
@@
 
-\hypertarget{study-2-computational-cognitive-model}{%
-\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}
+\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}
 
-\hypertarget{analysis-1}{%
-\subsection{Analysis}\label{analysis-1}}
+\subsection{Analysis}\label{analysis-1}
 
-\hypertarget{gaze-model-prediction}{%
-\subsubsection{Gaze model prediction}\label{gaze-model-prediction}}
+\subsubsection{Gaze model prediction}\label{gaze-model-prediction}
 
@@
 
-\hypertarget{inference-parameter-estimates-per-individual}{%
-\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}}
+\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}
 
@@
 
-\hypertarget{simulations}{%
-\subsection{Simulations}\label{simulations}}
+\subsection{Simulations}\label{simulations}
 
@@
 
-\hypertarget{study-3-components-of-gaze-understanding}{%
-\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}
+\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}
 
-\hypertarget{procedure-theory-of-mind-battery}{%
-\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}}
+\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}
 
@@
 
-\hypertarget{diverse-beliefs-wellman2004scaling}{%
-\subsubsection{(1) Diverse Beliefs (Wellman \& Liu, 2004)}\label{diverse-beliefs-wellman2004scaling}}
+\subsubsection{(1) Diverse Beliefs (Wellman \& Liu, 2004)}\label{diverse-beliefs-wellman2004scaling}
 
@@
 
-\hypertarget{knowledge-access-wellman2004scaling}{%
-\subsubsection{(2) Knowledge Access (Wellman \& Liu, 2004)}\label{knowledge-access-wellman2004scaling}}
+\subsubsection{(2) Knowledge Access (Wellman \& Liu, 2004)}\label{knowledge-access-wellman2004scaling}
 
@@
 
-\hypertarget{contents-false-belief-wellman2004scaling}{%
-\subsubsection{(3) Contents False Belief (Wellman \& Liu, 2004)}\label{contents-false-belief-wellman2004scaling}}
+\subsubsection{(3) Contents False Belief (Wellman \& Liu, 2004)}\label{contents-false-belief-wellman2004scaling}
 
@@
 
-\hypertarget{explicit-false-belief-wellman2004scaling}{%
-\subsubsection{(4) Explicit False Belief (Wellman \& Liu, 2004)}\label{explicit-false-belief-wellman2004scaling}}
+\subsubsection{(4) Explicit False Belief (Wellman \& Liu, 2004)}\label{explicit-false-belief-wellman2004scaling}
 
@@
 
-\hypertarget{perspective-taking-level-2-version-i-flavell1981development-flavell1981younga}{%
-\subsubsection{(5) Perspective-Taking Level 2 version I (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-i-flavell1981development-flavell1981younga}}
+\subsubsection{(5) Perspective-Taking Level 2 version I (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-i-flavell1981development-flavell1981younga}
 
@@
 
-\hypertarget{perspective-taking-level-2-version-ii-flavell1981development-flavell1981younga}{%
-\subsubsection{(6) Perspective-Taking Level 2 version II (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-ii-flavell1981development-flavell1981younga}}
+\subsubsection{(6) Perspective-Taking Level 2 version II (Flavell, Flavell, et al., 1981; Flavell, Everett, et al., 1981)}\label{perspective-taking-level-2-version-ii-flavell1981development-flavell1981younga}
 
@@
 
-\hypertarget{analysis-2}{%
-\subsection{Analysis}\label{analysis-2}}
+\subsection{Analysis}\label{analysis-2}
 
-\hypertarget{animal-vs.-human-faces}{%
-\subsubsection{Animal vs.~human faces}\label{animal-vs.-human-faces}}
+\subsubsection{Animal vs.~human faces}\label{animal-vs.-human-faces}
 
@@
 
-\hypertarget{model-comparisons}{%
-\subsubsection{Model comparisons}\label{model-comparisons}}
+\subsubsection{Model comparisons}\label{model-comparisons}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-flavell1981younga}{}}%
+\bibitem[\citeproctext]{ref-flavell1981younga}
 Flavell, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-flavell1981development}{}}%
+\bibitem[\citeproctext]{ref-flavell1981development}
 Flavell, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-prein2023tango}{}}%
+\bibitem[\citeproctext]{ref-prein2023tango}
 Prein, J.
@@
 {TANGO}: {A} reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults.
-\emph{Behavior Research Methods}.
+\emph{Behavior Research Methods}, \emph{56}(3), 2469--2485.
 \url{https://doi.org/10.3758/s13428-023-02159-5}
 
-\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scaling}{}}%
+\bibitem[\citeproctext]{ref-wellman2004scaling}
 Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}
@@
 
-\hypertarget{supplementary-tables}{%
-\section{Supplementary Tables}\label{supplementary-tables}}
+\section{Supplementary Tables}\label{supplementary-tables}
 
@@
 
-\hypertarget{supplementary-figures}{%
-\section{Supplementary Figures}\label{supplementary-figures}}
+\section{Supplementary Figures}\label{supplementary-figures}
 
